### 2019-08-01 data/reports.tex
writing reports

\subsection{A. K. Nandakumaran}

We have demonstrated the asymptotic analysis of a semi-linear optimal control problem posed on a smooth oscillating boundary domain in the present paper. We have considered a more general oscillating domain than the usual “pillar-type” domains. Consideration of such general domains will be useful in more realistic applications like circular domain with rugose boundary. We study the asymptotic behavior of the problem under consideration using a new generalized periodic unfolding operator. Further, we have studied the homogenization of a non-linear optimal control problem and such non-linear problems are limited in the literature despite the fact that they have enormous real-life applications. Among several other technical difficulties, the absence of a enough criteria for the optimal control is one of the most attention-grabbing issues in the current setting. We also obtain corrector results in this paper.  We considered an optimal control problem posed on a domain with a highly oscillating smooth boundary where the controls are applied on the oscillating part of the boundary. There are many results on domains with oscillating boundaries where the oscillations are pillar-type (non-smooth) while the literature on smooth oscillating boundary is very few. In this article, we use appropriate scaling on the controls acting on the oscillating boundary leading to different limit control problems; namely, boundary optimal control and interior optimal control problem. In the last part of the article, we visualize the domains as a branched structure, and we introduce unfolding operators to get contributions from each level at every branch.

\subsection{Apoorva Khare}

(1) A comprehensive, 40+ page paper treating distance matrices of trees. (2) An 80+ page survey on matrix positivity. (3) Extending results of Loewner, Horn, Cauchy, and Frobenius to new symmetric function identities and positivity conditions. (Among other works.)

\subsection{Arvind Ayyer}

Multispecies versions of random juggling models were studied and exact stationary distributions were obtained using combinatorial techniques [1]. For one variant, ultrafast convergence to stationarity was proved.  A new totally asymmetric exclusion process with two species of particles on a finite one-dimensional lattice in contact with reservoirs was introduced, where the second-class particle is impermeable to the right reservoir [2]. The stationary distribution was obtained using a matrix ansatz and the nonequilibrium phase diagram was computed in the thermodynamic limit. This was later extended to multiple species of particles and the phase diagram was computed.  A new interacting particle system called the Hilbert-Galton board was introduced and various theorems about this process were proved [3].  Random walks on noncommutative finite rings generated by both addition and multiplication were studied. Results were proven about the spectrum, stationary distribution and mixing time [4].  A new class of factorizations about characters of the general linear group, when the variables were specialised, were proved [5]. Somewhat surprisingly, the resulting objects are themselves characters of other classical groups. Some applications to enumerations of plane partitions and alternating sign matrices was given.  The combinatorics of a large class of cyclic orders were studied [6]. In particular, the enumeration of circular extensions of these cyclic orders was related to the enumeration of a family of polytopes made popular by R. Stanley.  Extending earlier work, odd and chiral representations were studied for all Coxeter groups [7].   [1] A. Ayyer, C. Finn and D. Roy, Matrix product solution of a left-permeable two-species asym- metric exclusion process, Phys. Rev. E, 97 no. 1 (2018) 012151, 10pp. [2] A. Ayyer, J. Bouttier, S. Corteel, S. Linusson and F. Nunzi, Bumping sequences and multi- species juggling, Advances in Applied Mathematics, 98 (2018) 100–126. [3] A. Ayyer and S. Ramassamy, The Hilbert-Galton board, Latin American Journal of Probability and Mathematical Statistics (ALEA), 15 no. 2 (2018), 755–774. [4] A. Ayyer and P. Singla, Random motion on finite rings, II: Noncommutative rings,  arXiv:1807.04082. [5] A. Ayyer and R. E. Behrend, Factorization theorems for classical group characters, with applications to alternating sign matrices and plane partitions, arXiv:1804.04514 [6]  A. Ayyer, M. Josuat-Vergès and S. Ramassamy, Extensions of partial cyclic orders and consecutive coordinate polytopes,  arXiv:1803.10351. [7]  A. Ayyer, A. Prasad and S. Spallone, Macdonald trees and determinants of representations for finite Coxeter groups, arXiv:1812.00608.

\subsection{Basudeb Datta}

We have shown that the boundary of the pseudorhombicuboctahedron is the only semi-equivelar map on the 2-sphere which is not vertex-transitive.   As a consequence, we show that each semi-equivelar map on the real projective plane is vertex-transitive.

\subsection{Dilip P Patil}

(1) During my sabbatical leave in IIT Bombay I have written the following two manuscripts (jointly with Prof. J. K. Verma):  [1] (Jointly with Kriti Goel and J. K. Verma ) Nullstellens\"atze and Applications, to appear in Conference Proceedings Published by Springer.   In this expository paper, we present simple proofs of the Classical, Real, Projective  and Combinatorial Nullstellens\"atze. Several applications are also presented such as a classical theorem of Stickelberger for solutions of polynomial equations in terms of eigenvalues of commuting operators, construction of a principal ideal domain which is not Euclidean, Hilbert's $17^{th}$ problem,  the Borsuk-Ulam theorem in topology and solutions of the conjectures of Dyson, Erd\"{o}s and Heilbronn.  [2]  (Jointly wit  J. K. Verma) Rational points and generalized trace forms on a finite algebra over a real closed field, to appear in Conference Proceedings Published by Springer.   The core of this article is the equality of the number of $K$-rational points  with the signature of the trace form of a finite $K$-algebra over a real closed field $K$. The main tools are symmetric bilinear forms, hermitian forms, trace forms, generalized trace forms and their types and signatures.  Further, we prove a criterion for the existence of $K$-rational points by using generalized trace forms. As an application we prove the Pederson-Roy-Szpirglas theorem  about counting common real zeros of  real polynomial equations. We also prove deduce this theorem as a special case of a similar classical theorem for real closed fields.  [3] On the connectedness of the fiber product of two connected finte free affine schemes. Preprint.  This article grew out while studying Burnside algebra of finite abelian groups.

\subsection{E. K. Narayanan}

Study of Heckman-Opdam hypergeometric functions associated to root systems of type $BC,$ where the associated multiplicity function was allowed to assume negative values, was continued.

\subsection{Gautam Bharali}

Further work was undertaken to investigate a weak form of negative curvature --- known as visibility --- exhibited by a range of domains in $\mathbb{C}^n$ equipped with the Kobayashi distance. The class of domains that are visibility domains with respect to the Kobayashi distance was significantly broadened in the preprint [1]. Furthermore, two Wolff--Denjoy-type theorems were established for the latter class of domains.  [1] Gautam Bharali and Anwoy Maitra, A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems.

\subsection{Govindan Rangarajan}

Detection of a causal relationship between two or more sets of data is an important problem across various scientific disciplines. Test statistics based on Granger causality ignore the effect of practical measurement impairments such as subsampling, additive noise, and finite sample effects. We modelled [1] the problem of detecting a causal relationship between two time series as a binary hypothesis test with the null and alternate hypotheses corresponding to the absence and presence of a causal relationship, respectively. We derived the distribution of the test statistic under the two hypotheses and show that measurement impairments can lead to suppression of a causal relationship between the signals, as well as false detection of a causal relationship, where there is none. We also used the derived results to propose two alternative test statistics for causality detection. These detectors are analytically tractable, which allowed us to design the detection threshold and determine the number of samples required to achieve a given missed detection and false alarm rate.   Prostate-associated gene 4 (PAGE4) is an intrinsically disordered protein implicated in prostate cancer. Experiments have shown that PAGE4 expands upon hyperphosphorylation and that this expansion is localized to its N-terminal half. To understand the interactions underlying this structural transition, we performed [2] molecular dynamics simulations using Atomistic AWSEM, a multi-scale molecular model that combines atomistic and coarse- grained simulation approaches. Our simulations show that electrostatic interactions drive transient formation of an N-terminal loop, the destabilization of which accounts for the dramatic change in size upon hyperphosphorylation. Finally, we construct a mechanism-based mathematical model that allows us to capture the interactions of different phosphoforms of PAGE4 with AP-1 and its downstream target, the androgen receptor (AR)—a key therapeutic target in prostate cancer. Our model predicts intracellular oscillatory dynamics indicating phenotypic heterogeneity in an isogenic cell population. Thus, conformational switching of PAGE4 may potentially affect the efficiency of therapeutically targeting AR activity.   We proposed [3] an application of the microtremor (ambient noise) H/V spectral ratio technique to identify significant rheological boundaries at shallow depths, estimate thickness of both lignite bearing Tertiary sedimentary sequence and late Cretaceous Deccan basalt flows and comprehend basinal geometry of Umarsar Basin (Babia syncline). Forty-six stations were gauged in a grid format at ~250 m resolution during the microtremor survey. We detected three rheological interfaces. Finally, we proposed the microtremor H/V spectral ratio technique as a tool to develop economical borehole plan with realistic reserve estimate and a step forward towards rapid economical assessment covering large mining lease areas.   [1] IEEE Trans Signal Proc. (2018) [2] J. Mol. Biol (2018) [3] J. Appl. Geophys. (2018)

\subsection{Manjunath Krishnapur}

Working on certain problems on nodal sets of Gaussian random functions and in random matrix theory.

\subsection{Mrinal Kanti Ghosh}

We analyze an augmented political business cycle model taking into account the effect of employment creation decisions by the ruling party jointly on inflation and growth. The objective is to maximize voter support in the next election that depends on the rate of unemployment as well as that of growth and inflation. We allow for randomness in the New Keynesian Phillips Curve (NKPC) model for the relationship between  inflation and unemployment as well as in a benchmark labour productivity function for   analyzing the growth rate. We provide explicit solution paths of the affine Markov   control problem that results from our formulation. We also provide numerical illustrations with plausible parametric configurations to generate more insight into our model. [1] G. K. Basak, M. K. Ghosh and D. Mukherjee, A Stochastic Model with Inflation, Growth and Technology  for the Political Business Cycle, J. Computational Economics, 53 (2019), 125-140.

\subsection{Pooja Singla}

In [1], We study some irreversible Markov chains on finite commutative rings randomly generated using both addition and multiplication. We describe the eigenvalues and their multiplicities. We also prove recursive formulas for stationary distribution. We extend this work to finite non-commutative rings in [2].   In [3], the Gelfand-Whittaker model for $GL_n(O)$ and $SL_n(O)$,where $O$ is a  compact discrete valuation ring is studied. We proved that this model is multiplicity free and describe its constituents.   In [4] We describe the abscissa of convergence of representation zeta function of $SL_2(O)$ for a compact discrete valuation ring $O$ with even characteristic. For this case, we also give construction of continuous primitive irreducible representations and study group algebra isomorphism problem.   [1]. Random motion on finite rings, I: commutative rings, Arvind Ayyer and Pooja Singla, to appear in Algebras and Representation Theory.  [2]. Random motion on finite rings, II: Non-commutative rings; Arvind Ayyer and Pooja Singla, preprint.   [3]. A multiplicity one theorem for groups of type $A_n$ over discrete valuation rings, Shiv Prakash Patel and Pooja Singla, preprint.  [4]. Representation Growth of Special Compact Linear Groups of Order Two,  M. Hassain and Pooja Singla, preprint.

\subsection{R. Venkatesh}

By improving some earlier work of Felikson, Retakh and Tumarkin, a classification of all the regular subalgebras of Affind Kac-Moody Lie algebras have been obtained. By continuing this classification problem to Extend Affine Lie Algebras which are natural generalizaion of Affine Kac-Moody algebras, a classification of all the maximal closed sub-root systems of Affine reflection systems has also been done. The question of when two tensor products of irreducible integrable representations would be isomorphic to another for Borcherds-KacMoody algebras has been investigated.

\subsection{SANCHAYAN SEN}

In [1], the critical behavior of the component sizes for the configuration model has been studied when the tail of the degree distribution of a uniform vertex is a regularly-varying function with exponent $\tau -1$, where $\tau\in (3, 4)$.   In [2], the metric space scaling limits of the minimal spanning trees of both the random (simple) 3-regular graph and the 3-regular configuration model have been established, and it has been shown that both these models belong to the universality class identified in the work of Addario-Berry, Broutin, Goldschmidt, and Miermont [Annals of Probability, 2017].   [1] Heavy-tailed configuration models at criticality.  Authors: Souvik Dhara, Remco van der Hofstad, Johan van Leeuwaarden, Sanchayan Sen.  Annales de l'Institut Henri Poincaré (B) Probabilités et Statistiques. Accepted in March 2019.  [2] Geometry of the minimal spanning tree of a random 3-regular graph.  Authors: Louigi Addario-Berry, Sanchayan Sen ArXiv preprint. Announced in October 2018.

\subsection{Siddhartha Gadgil}

We refined our previous results where, as part of the PolyMath 14 project, we had classified homogeneous length functions on groups. In particular we showed that quasi-homogeneous length functions on groups with vanishing commutator length (such as solvable groups) are bounded distance from pullbacks from Abelianizations.  We also replicated and made robust the computer-assisited proof we had found in the course of the above mentioned PolyMath project and investigated general principles involved. We further developed methods for computer assisted theorem proving.

\subsection{Soumya Das}

We continue our investigations on analytic aspects of Automorphic forms.

\subsection{Srikanth K. Iyer}

The random connection model is studied in the connectivity regime. Strong law results for the critical scaling parameter required to eliminate isolated nodes is derived. A sufficient condition for the graph to be connected with high probability is obtained. Other results include strong law results for the maximum and minimum vertex degrees [1]. The capacity of a wireless cellular network is defined and an exact characterization (non-asymptotic) of this natural capacity metric is derived. It is shown that that the capacity increases polynomially with the base station (BS) density in the low BS density regime and then scales inverse exponentially with the increasing BS density [2]. A model of merge and split group dynamics, also called fission-fusion dynamics, for heterogeneous populations that contain two types (or species) of individuals is proposed and analysed. It is predicted using the analytical model that there is a critical group size below which groups are more likely to be homogeneous and contain the abundant type or species. Despite the propensity of heterogeneous groups to split at higher rates, we find that groups are more likely to be heterogeneous but only above the critical group size. Monte Carlo simulation of the model show excellent agreement with these analytical model results. The implications of our results to empirical studies on flocking systems are discussed [3].

\subsection{Subhojoy Gupta}

The main focus of my research during this period was in developing a correspondence between meromorphic quadratic differentials and certain geometric structures on punctured Riemann surfaces. Some of this work arose out of an effort to understand how such ``meromorphic" geometric structures arise in degenerations, in the context of hyperbolic structures. Other collaborative projects during this period that resulted in papers include a project with Basudeb Datta (IISc), on understanding geometric tilings of the hyperbolic plane, and work with Indranil Biswas (TIFR Mumbai) and Sorin Dumitrescu (CNRS, France) that concerns branched projective structures on Riemann surfaces.   Papers written or published during this period:  [1]   (with Michael Wolf)  Meromorphic quadratic differentials and measured foliations on a Riemann surface, Mathematische Annalen, Vol. 373 1-2,  (February 2019), pg. 73-118.  [2]  Limits of harmonic maps and crowned hyperbolic surfaces, accepted for publication , Transactions of the AMS,  available at  https://doi.org/10.1090/tran/7777.   [3]  Holomorphic quadratic differentials in Teichmüller theory,  to appear, Handbook of Teichmüller theory Vol VII, available at  http://arxiv.org/abs/1902.06406.  [4] (with Basudeb Datta)  Uniform tilings of the hyperbolic plane,  submitted, available at http://arxiv.org/abs/1806.11393.  [5] (with Indranil Biswas and Sorin Dumitrescu) Branched projective structures on a Riemann surface and logarithmic connections, submitted, available at http://arxiv.org/abs/1808.04555.

\subsection{Sundaram Thangavelu}

We have obtained sparse bounds for the lacunary maximal function associated to spherical means on the Heisenberg group [1]. As a consequence we have obtained an analogue of a result of C. P. Calderon for the lacunary spherical maximal function on Euclidean spaces.

\subsection{Tirthankar Bhattacharyya}

My research for the relevant period has been on Toeplitz operators.  An easily computable and simple condition which is necessary and sufficient for a commuting tuple of contractions to possess a non-zero Toeplitz operator has been found.  This condition is just that the adjoint of the product of the contractions is not pure. On one hand, this brings out the importance of the product of the contractions and on the other hand, the non-pureness turns out to be equivalent to the existence of a pseudo-extension to a tuple of commuting unitaries. A commutant pseudo-extension theorem has been obtained by studying the unique canonical unitary pseudo-extension of a tuple of commuting contractions. Also, with the help of a special completely positive map, a different proof of the existence of the unique canonical unitary pseudo-extension is given. On a different note, an extensive theory of Toeplitz operators on the symmetrized bidisc has been developed.

\subsection{Vamsi Pritham Pingali}

I worked on three themes : 1) Connections on holomorphic vector bundles : Along with I. Biswas [1], I studied the differential geometry of parabolic ample bundles and connected it with the known algebro-geometric results.  I introduced a vector bundle Monge-Ampere equation in a preprint [2] and proved some existence results for it. 2) Coupled PDE on Kahler manifolds : Along with Ved Datar, I studied coupled cscK equations and provided a moment map interpretation in a preprint [3]. 3) Interpolation : D. Varolin and I [4] provided examples and counterexamples of affine algebraic interpolating manifolds.  [1] I. Biswas and V. Pingali. Metric properties of parabolic ample bundles, International Mathematical Research Notices, Nov 2018 (published online - doi:10.1093/imrn/rny259). [2] V. Pingali. A vector bundle version of the Monge-Ampere equation, arXiv : 1804.03934, Apr 2018. [3] V. Datar and V. Pingali. On coupled constant scalar curvature Kahler metrics (with Ved Datar), arXiv : 1901.10454, Jan 2019. [4] V. Pingali and D. Varolin. Nonuniformly flat affine algebraic hypersurfaces, arXiv : 1810.00895, Oct 2018. (Accepted for publication in Nagoya Mathematical Journal -  https://doi.org/10.1017/nmj.2019.2)

### 2019-08-01 ugc/src/Data.scala

@@ -23,6 +23,11 @@ object Data{
     lazy val summerStudents = data.map(l => SummerStudent.getAll(l))
 
     lazy val facultyData = data.map(l => FacultyData.get(l)).sortBy(_.name)
+
+    lazy val reports = facultyData.map(d =>
+    s"\\subsection{${d.name}}\n\n${d.research}").mkString("\n\n\n")
+
+    def writeReport() = os.write.over(os.pwd / "data" / "reports.tex", reports)
 }
 
 case class FacultyData(

### 2019-08-02 ugc/src/Data.scala
many latex outputs

@@ -1,33 +1,70 @@
 package ugc
 import Data._
 
-object Data{
-    val paperInit = 2
-    val numPapers = 7
-    val confInit = paperInit + (numPapers * 8)
-    val numConfs = 5
-    val bookInit = confInit + (numConfs * 5)
-    val numBooks = 4
-    val summerInit = bookInit + (numBooks * 8)
-    val numSummer = 6
-    val grantInit = summerInit + (numSummer * 4)
-    val numGrants = 4
-    val awardsPos = grantInit + (numGrants * 6)
-    val fullSize = awardsPos + 3
-    def pad(v: Vector[String]) = v ++ Vector.fill(fullSize - v.size)("")
+object Data {
+  val paperInit = 2
+  val numPapers = 7
+  val confInit = paperInit + (numPapers * 8)
+  val numConfs = 5
+  val bookInit = confInit + (numConfs * 5)
+  val numBooks = 4
+  val summerInit = bookInit + (numBooks * 8)
+  val numSummer = 6
+  val grantInit = summerInit + (numSummer * 4)
+  val numGrants = 4
+  val awardsPos = grantInit + (numGrants * 6)
+  val fullSize = awardsPos + 3
+  def pad(v: Vector[String]) = v ++ Vector.fill(fullSize - v.size)("")
 
-    lazy val data = os.read.lines(os.resource / "ugc2019.tsv").toVector.tail.map(_.split("\t").toVector.tail).map(pad)
+  lazy val data = os.read
+    .lines(os.resource / "ugc2019.tsv")
+    .toVector
+    .tail
+    .map(_.split("\t").toVector.tail)
+    .map(pad)
 
-    lazy val papers = data.map(l => Paper.getAll(l))
+  lazy val papers = data.map(l => Paper.getAll(l))
 
-    lazy val summerStudents = data.map(l => SummerStudent.getAll(l))
+  lazy val summerStudents = data.flatMap(
+    l =>
+      SummerStudent.getAll(l).map { stu =>
+        stu.text(l(0))
+      }
+  )
 
-    lazy val facultyData = data.map(l => FacultyData.get(l)).sortBy(_.name)
+  lazy val summerTeX =
+    s"""
+\\subsection{Summer Students}
 
-    lazy val reports = facultyData.map(d =>
-    s"\\subsection{${d.name}}\n\n${d.research}").mkString("\n\n\n")
+\\begin{enumerate}
[…]

### 2019-08-02 ugc/src/Publications.scala
pubs from data

@@ -1,0 +1,50 @@
+package ugc
+import os.remove.all
+
+object Publications {
+  import org.jbibtex._
+  import scala.collection.JavaConverters._
+
+  import java.io._
+  val parser = new BibTeXParser()
+  def reader = new java.io.FileReader("data/publications.bib")
+
+  def db = parser.parse(reader)
+
+  lazy val mp = db.getEntries.asScala.toMap.values
+    .map(_.getFields.asScala.toMap.map {
+      case (k, v) => k.getValue.toLowerCase -> v.toUserString
+    })
+    .toVector
+    .filter(m => Set("2018", "2019").contains(m("year")))
+
+  import net.jcazevedo.moultingyaml._
+  import net.jcazevedo.moultingyaml.DefaultYamlProtocol._
+  lazy val txt = os.read(os.pwd / "data" / "extrapubs.yaml").replace("\t", " ")
+  lazy val yamlAst = txt.parseYaml
+  lazy val data =
+    yamlAst.convertTo[Vector[Map[String, YamlValue]]]
+
+  def getString(y: YamlValue): String = y match {
+      case YamlNumber(value) => value.toString()
+      case YamlString(value) => value
+      case YamlBoolean(boolean) => boolean.toString()
+      case _ => ""
+  }
+
+  lazy val allPubs : Vector[Map[String,String]] = (mp ++ (data.map(m => m.mapValues(getString(_))))).sortBy(m => m("author"))
+
+  def tex(m: Map[String, String]) = {
+      val author = m("author")
+      val title  = m("title")
+      val journal = m.get("journal").orElse(m.get("booktitle")).getOrElse("")
+      val pages = m.getOrElse("pages", "")
+      val volume = m.getOrElse("volume", "")
+      val year = m("year")
+      s"\\item $author, $title {\\em $journal} {\\bf $volume} ($year), $pages."
+  }
+
+  lazy val pubItems = allPubs.map(tex)
+
+
+}

### 2019-08-03 data/reports.tex
code for draft files

@@
 
+\subsection{Tirthankar Bhattacharyya}
+
+Have given this a few days back. Please keep that. The purpose of submitting the form again is to mention some preprints in addition to the one mentioned when I submitted the form a few days ago.
+
 \subsection{Vamsi Pritham Pingali}
@@
 (Accepted for publication in Nagoya Mathematical Journal -  https://doi.org/10.1017/nmj.2019.2)
+
+\subsection{Ved Datar}
+
+In collaboration with Adam Jacob and Yuguang Zhang [1], we solved a conjecture of Fukaya's in dimension two, on adiabatic limits of anti-self dual connections on collapsing Calabi-Yau manifolds.
+I am also working with Vamsi Pingali on the problem of existence of coupled K\"ahler-Einstein metrics on Fano manifolds.
+Our preliminary investigations [2] into the problem resulted in the introduction of a more general system of differential equations, christened coupled constant scalar curvature K\"ahler metrics.
+[1] Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces.
+(with Adam Jacob and Yuguang Zhang), preprint,  arXiv:1809.08583, submitted to Journal of Differential Geometry [2]  On coupled constant scalar curvature Kähler metrics (with Vamsi Pingali), preprint,  arXiv:1901.10454, submitted to Journal of Symplectic Geometry

### 2019-08-03 ugc/src/Data.scala

@@ -23,8 +23,6 @@ object Data {
     .map(_.split("\t").toVector.tail)
     .map(pad)
 
-  lazy val papers = data.map(l => Paper.getAll(l))
-
   lazy val summerStudents = data.flatMap(
     l =>
       SummerStudent.getAll(l).map { stu =>
@@ -64,7 +62,94 @@ ${grantsItems.mkString("\n")}
 
   lazy val editors = facultyData.flatMap(f => f.awards.edOpt(f.name))
 
+  lazy val draftSections =
+    s"""
+$summerTeX
+
+$grants
+
+\\subsection{Awards}
+
+\\begin{enumerate}
+${awards.mkString("\n")}
+\\end{enumerate}
+
+\\subsection{Fellowships of Academies}
+
+\\begin{enumerate}
+${fellows.mkString("\n")}
+\\end{enumerate}
+
+\\subsection{Editorial boards}
+\\begin{enumerate}
+${editors.mkString("\n")}
+\\end{enumerate}
+"""
+
+  lazy val papers = facultyData
+    .flatMap(f => f.papers)
+    .filter(
+      p => Set("Published", "Accepted for publication").contains(p.status)
+    )
+    .map(_.tex)
+
+  lazy val preprints = facultyData
+    .flatMap(f => f.papers)
+    .filter(
+      p => Set("Preprint", "Submitted").contains(p.status)
+    )
+    .map(_.tex)
+
+  lazy val confPapers = facultyData.flatMap(f => f.confs.map(_.tex))
+
+  lazy val books = facultyData.flatMap(f => f.books.map(_.tex))
+
+  lazy val draftPubs =
+    s"""
+\\subsection{Papers in Journals}
+
+\\begin{enumerate}
+${papers.mkString("\n")}
+\\end{enumerate}
+
+\\subsection{Papers in Conference proceedings}
+
+\\begin{enumerate}
+${confPapers.mkString("\n")}
+\\end{enumerate}
+
+\\subsection{Books and book chapters}
+
+\\begin{enumerate}
+${books.mkString("\n")}
+\\end{enumerate}
+
+\\subsection{Preprints}
+
+\\begin{enumerate}
+${preprints.mkString("\n")}
+\\end{enumerate}
+
+% from web page
+
+\\subsection{Publications (all kinds) from web page}
+
+\\begin{enumerate}
+${Publications.pubItems.mkString("\n")}
+\\end{enumerate}
+"""
+
[…]

### 2019-08-08 data/draft-publications.tex
filter correction

\subsection{Papers in Journals}

\begin{enumerate}
\item 2. S. Aiyappan, A. K. Nandakumaran and Ravi Prakash, Semi-linear optimal control problem on a smooth oscillating domain Communications in Contemporary Mathematics, {\em Communications in Contemporary Mathematics} {\bf } (2019), 26 pages.
\item 1. S. Aiyappan, A. K. Nandakumaran and Abu Sufian, Asymptotic Analysis of a Boundary Optimal Control Problem on a General Branched Structure, to appear in Mathematical Methods in Applied Sciences (MMAS).
\item Benedetti, Carolina and González D’León, Rafael S. and Hanusa, Christopher R.H. and Harris, Pamela E. and Khare, Apoorva and Morales, Alejandro H. and Yip, Martha, A combinatorial model for computing volumes of flow polytopes, {\em Transactions of the American Mathematical Society} {\bf 372} (2019), 3369-3404.
\item Subhajit Ghosh, Total variation cutoff for the transpose top-2 with random shuffle, to appear in Journal of Theoretical Probability.
\item G. K. Basak, M. K. Ghosh and D. Mukherjee, A Stochastic Model with Inflation, Growth and Technology for the Political Business Cycle, {\em Journal of Computational Economics} {\bf 53} (2019), 125-140.
\item Arvind Ayyer and Pooja Singla, Random motion on finite rings, I: commutative rings, {\em Algebras and Representation theory} {\bf } (), .
\item E.K.Narayanan and Pooja Singla, On monomial representations of finitely generated nilpotent groups, {\em Communications in Algebra} {\bf 46} (2018), 2319–2331.
\item Souvik Dhara, Remco van der Hofstad, Johan S.H. van Leeuwaarden, Sanchayan Sen, Heavy-tailed configuration models at criticality, to appear in Annales de l'Institut Henri Poincaré (B) Probabilités et Statistiques.
\item Siddhartha Gadgil, Homogeneous Length Functions on Groups: Intertwined Computer and Human Proofs, to appear in Journal of Automated Reasoning.
\item Srikanth K. Iyer, The Random Connection Model - Connectivity, Edge Lengths and Degree Distributions, {\em Random Structures and Algorithms} {\bf 52} (2018), 283-300.
\item Rahul Vaze, Srikanth K. Iyer, Capacity of Cellular Wireless Networks, {\em IEEE Transactions on Wireless Communications} {\bf 18} (2019), 1490 - 1503.
\item Gokul Nair, Senthil Athmanathan,, Srikanth K. Iyer  and Vishwesha Guttal, Fission-fusion dynamics and group-size-dependent composition in heterogeneous populations, {\em Physical Review E} {\bf 99} (2019), .
\item Subhojoy Gupta, Meromorphic quadratic differentials and measured foliations on a Riemann surface, {\em Mathematische Annalen} {\bf 373} (2019), 73-118.
\item Subhojoy Gupta and Harish Seshadri, On domains biholomorphic to Teichmüller spaces, to appear in International Mathematics Research Notices.
\item Subhojoy Gupta, Harmonic maps and wild Teichmüller spaces, to appear in ournal of Topology and Analysis.
\item Subhojoy Gupta, Limits of harmonic maps and crowned hyperbolic surfaces, to appear in Transactions of the AMS.
\item Luz Roncal and Sundaram Thangavelu, An extension problem and trace Hardy inequality for the sublaplacian on H-type groups, to appear in IMRN.
\item Pradeep Boggarapu, Luz Roncal and Sundaram Thangavelu, On extension problem, trace Hardy and Hardy's inequalities for some fractional Laplacians, to appear in Communications in Pure and Applied Analysis..
\item Indranil Biswas and Vamsi Pritham Pingali, Metric properties of parabolic ample bundles, to appear in International Mathematical Research Notices.
\item Vamsi Pingali and Dror Varolin, Non-uniformly flat affine algebraic hypersurfaces, to appear in Nagoya mathematical journal.
\end{enumerate}

\subsection{Papers in Conference proceedings}

\begin{enumerate}
\item Kriti Goel, Dilip Patil and Jugal Verma, Nullstellens\"atze and Applications {\em } ().
\item Dilip P Patil and Jugal Verma, Rational points and generalized trace forms on a finite algebra over a real closed field {\em } ().
\end{enumerate}

\subsection{Books and book chapters}

\begin{enumerate}
\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva and Putinar, Mihai, A panorama of positivity: I. Dimension free in {\em Birkhauser, Trends in Mathematics}{f } (2019), 117-165.
\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva and Putinar, Mihai, A panorama of positivity: II. Fixed dimension in {\em American Mathematical Society, Contemporary Mathematics}{f } (), .
\item Subhojoy Gupta and Harish Seshadri , Complex geometry of Teichmüller domains in {\em EMS, Handbook of Teichmüller theory}{f 7} (), .
\item Subhojoy Gupta, Holomorphic quadratic differentials in Teichmüller theory in {\em EMS, Handbook of Teichmüller Theory}{f 7} (), .
\end{enumerate}

\subsection{Preprints}

\begin{enumerate}
\item Apoorva Khare, Smooth entrywise positivity preservers, a Horn–Loewner master theorem, and Schur polynomial identities, preprint.
\item Apoorva Khare, The non-compact normed space of norms on a finite-dimensional Banach space, preprint.
\item Projesh Nath Choudhury and Apoorva Khare, Distance matrices of a tree: two more invariants, and in a unified framework, preprint.
\item Arvind Ayyer, Matthieu Josuat-Vergès, Sanjay Ramassamy, Extensions of partial cyclic orders and consecutive coordinate polytopes , preprint.
\item Arvind Ayyer, Pooja Singla, Random motion on finite rings, II: Noncommutative rings , preprint.
\item Arvind Ayyer, Amritanshu Prasad, Steven Spallone, Macdonald trees and determinants of representations for finite Coxeter groups , preprint.
\item Dilip P. Patil, On the connectedness of the fiber product of two connected finte free affine schemes. , preprint.
\item Gautam Bharali and Anwoy Maitra, A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, submitted for publication.
\item Arvind Ayyer and Pooja Singla, Random motion on finite rings, II: Noncommutative rings, preprint.
\item M. Hassain and Pooja Singla, Representation Growth of Special Compact Linear Groups of Order Two, preprint.
\item Shiv Prakash Patel and Pooja Singla, A multiplicity one theorem for groups of type $A_n$ over discrete valuation rings, preprint.
\item Shifra Reif, R. Venkatesh, On tensor products of irreducible integrable representations, preprint.
\item Deniz Kus, R. Venkatesh, Borel-de Siebenthal theory for affine reflection systems, preprint.
\item Louigi Addario-Berry, Sanchayan Sen, Geometry of the minimal spanning tree of a random 3-regular graph, preprint.
\item Sourav Hait, Sayan Bagchi, Luz Roncal and Sundaram Thangavelu, On the lacunary spherical maximal function on the Heisenberg group, preprint.
\item TIRTHANKAR BHATTACHARYYA, SUBRATA SHYAM ROY, AND TAPESH YADAV, THE AGLER-YOUNG CLASS, submitted for publication.
\item Tirthankar Bhattacharyya, B. Krishna Das, Haripada Sau, Toeplitz operators and pseudo-extensions, submitted for publication.
\item Tirthankar Bhattacharyya, Anindya Biswas, Vikramjeet Singh Chandel, On the Nevanlinna problem - Characterization of all Schur-Agler class solutions affiliated with a given kernel, submitted for publication.
\item Tirthankar Bhattacharyya, B. Krishna Das, Haripada Sau, Toeplitz operators on the symmetrized bidisc, submitted for publication.
\item Vamsi Pritham Pingali, A vector bundle version of the Monge-Ampere equation, preprint.
\item Ved V. Datar and Vamsi Pritham Pingali, On coupled constant scalar curvature Kaehler metrics, preprint.
\item Ved Datar, Adam Jacob, Yuguang Zhang, Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces, preprint.
\item Ved V. Datar, Vamsi Pritham Pingali, On coupled constant scalar curvature K\"ahler metrics, preprint.
\end{enumerate}

% from web page

\subsection{Publications (all kinds) from web page}

\begin{enumerate}
\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, Generalization of unfolding operator for highly oscillating
smooth boundary domains and homogenization {\em Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30.
\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish, A gap theorem for positive {E}instein metrics on the
four-sphere {\em Math. Ann.} {\bf 373} (2019), 1329--1339.
\item Amritkar, R. E. and Rangarajan, G., Spatially synchronous extinction of species under external forcing {\em Physical Review Letters} {\bf 96} (2006), 258102.
\item Anamby, Pramath and Das, Soumya, Distinguishing {H}ermitian cusp forms of degree 2 by a certain
subset of all {F}ourier coefficients {\em Publ. Mat.} {\bf 63} (2019), 307--341.
\item Anamby, Pramath and Das, Soumya, Bounds for the {P}etersson norms of the pullbacks of
{S}aito-{K}urokawa lifts {\em J. Number Theory} {\bf 191} (2018), 289--304.
\item Arunkumar, G. and Kus, Deniz and Venkatesh, R., Root multiplicities for {B}orcherds algebras and graph
coloring {\em J. Algebra} {\bf 499} (2018), 538--569.
\item Ayyer, A. and Finn, C. and Roy, D., Matrix product solution of a left-permeable two-species asymmetric exclusion process {\em Physical Review E} {\bf 97} (2018), 5225.
\item Ayyer, Arvind and Behrend, Roger E., Factorization theorems for classical group characters, with
applications to alternating sign matrices and plane
partitions {\em J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.
\item Ayyer, Arvind and Bouttier, J\'{e}r\'{e}mie and Corteel, Sylvie and
Linusson, Svante and Nunzi, Fran\c{c}ois, Bumping sequences and multispecies juggling {\em Adv. in Appl. Math.} {\bf 98} (2018), 100--126.
\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, Matrix product solution of a left-permeable two-species
asymmetric exclusion process {\em Phys. Rev. E} {\bf 97} (2018), 012151, 10.
\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, The phase diagram for a multispecies left-permeable asymmetric
exclusion process {\em J. Stat. Phys.} {\bf 174} (2019), 605--621.
\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, Odd partitions in {Y}oung's lattice {\em S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
\item Ayyer, Arvind and Ramassamy, Sanjay, The {H}ilbert-{G}alton board {\em ALEA Lat. Am. J. Probab. Math. Stat.} {\bf 15} (2018), 755--774.
\item B\"{o}cherer, Siegfried and Das, Soumya, Cuspidality and the growth of {F}ourier coefficients of
modular forms {\em J. Reine Angew. Math.} {\bf 741} (2018), 161--178.
\item B\"{o}cherer, Siegfried and Das, Soumya, Petersson norms of not necessarily cuspidal {J}acobi modular
forms and applications {\em Adv. Math.} {\bf 336} (2018), 335--376.
\item Bagchi, Sayan and Thangavelu, Sundaram, Weighted norm inequalities for {W}eyl multipliers and fourier
multipliers on the {H}eisenberg group {\em J. Anal. Math.} {\bf 136} (2018), 1--29.
\item Baklouti, Ali and Thangavelu, Sundaram, Hardy and {M}iyachi theorems for {H}eisenberg motion groups {\em Nagoya Math. J.} {\bf 229} (2018), 1--20.
\item Balhara, Rakesh, Hardy's inequality for the fractional powers of the {G}rushin
operator {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25.
\item Balodi, Mamta and Palcoux, Sebastien, On {B}oolean intervals of finite groups {\em J. Combin. Theory Ser. A} {\bf 157} (2018), 49--69.
\item Banerjee, Abhishek, On {A}uslander's formula and cohereditary torsion pairs {\em Commun. Contemp. Math.} {\bf 20} (2018), 1750071, 27.
\item Banerjee, Abhishek, Modular {H}ecke algebras over {M}\"{o}bius categories {\em J. Geom. Phys.} {\bf 131} (2018), 23--40.
\item Banerjee, Abhishek, A topological {N}ullstellensatz for tensor-triangulated
categories {\em C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375.
\item Banerjee, Abhishek, Quasimodular {H}ecke algebras and {H}opf actions {\em J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080.
\item Banerjee, Abhishek, Completions of monoid objects and descent results {\em J. Algebra} {\bf 507} (2018), 362--399.
\item Basu, Arnab and Ghosh, Mrinal K., Nonzero-sum risk-sensitive stochastic games on a countable
state space {\em Math. Oper. Res.} {\bf 43} (2018), 516--532.
\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
and Putinar, Mihai, Simultaneous kernels of matrix {H}adamard powers {\em Linear Algebra Appl.} {\bf 576} (2019), 142--157.
\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
Morales, Alejandro H. and Yip, Martha, The volume of the caracol polytope {\em S\'{e}m. Lothar. Combin.} {\bf 80B} (2018), Art. 87, 12.
\item Bera, Sayani and Verma, Kaushal, Some aspects of shift-like automorphisms of {$\Bbb C^k$} {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 128} (2018), Art. 10, 48.
\item Bharali, Gautam and Biswas, Indranil and Divakaran, Divakaran
and Janardhanan, Jaikrishnan, Proper holomorphic mappings onto symmetric products of a
{R}iemann surface {\em Doc. Math.} {\bf 23} (2018), 1291--1311.
\item Bhattacharyya, Tirthankar and Sau, Haripada, Holomorphic functions on the symmetrized bidisk---realization,
interpolation and extension {\em J. Funct. Anal.} {\bf 274} (2018), 504--524.
\item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
Sundaram, Hermite multipliers on modulation spaces {\em Analysis and partial differential equations: perspectives from
developing countries} {\bf 275} (2019), 42--64.
\item Bhosle, Usha N., Hitchin pairs on reducible curves {\em Internat. J. Math.} {\bf 29} (2018), 1850015, 49.
\item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and
Pingali, Vamsi P., Rational cuspidal curves on del-{P}ezzo surfaces {\em J. Singul.} {\bf 17} (2018), 91--107.
\item Biswas, Indranil and Pingali, Vamsi Pritham, A characterization of finite vector bundles on {G}auduchon
astheno-{K}\"{a}hler manifolds {\em \'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art. 6, 13.
\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi, Edge patch-wise local projection stabilized nonconforming
{FEM} for the {O}seen problem {\em Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214.
\item Biswas, Shibananda and Ghosh, Gargi and Misra, Gadadhar and
Shyam Roy, Subrata, On reducing submodules of {H}ilbert modules with
{${S}_n$}-invariant kernels {\em J. Funct. Anal.} {\bf 276} (2019), 751--784.
\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal, Comments on the {G}reen's function of a planar domain {\em Anal. Math. Phys.} {\bf 8} (2018), 383--414.
\item Borkar, V. S and Jain, S and Rangarajan, G., Dynamics of individual specialization and global diversification in   communities {\em Complexity} {\bf 3} (1998), 50.
\item Borkar, V. S. and Jain, S. and Rangarajan, G., Generalized replicator dynamics as a model of specialization and   diversity in societies {\em Advances in Complex Systems} {\bf 1} (1998), 325.
\item Borkar, V. S. and Jain, S. and Rangarajan, G., Collective behaviour and diversity in economic communities: Some insights from an evolutionary game {\em The Application of Econophysics} {\bf } (2003), .
\item Borkar, V. S. and Jain, S. and Rangarajan, G., Evolutionary mechanisms of organization in complex systems {\em Mathematical Models for Bioengineering and Probabilistic Systems} {\bf } (2005), 323.
\item Brenner, Susanne C. and Gudi, Thirupathi and Porwal, Kamana
and Sung, Li-Yeng, A {M}orley finite element method for an elliptic distributed
optimal control problem with pointwise state and control
constraints {\em ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206.
\item Burton, Benjamin A. and Datta, Basudeb and Singh, Nitin and
Spreer, Jonathan, A construction principle for tight and minimal triangulations
of manifolds {\em Exp. Math.} {\bf 27} (2018), 22--36.
\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella, Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
indefinite second-order linear elliptic problems {\em Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.
\item Chandel, Vikramjeet Singh, The three-point {P}ick-{N}evanlinna interpolation problem on
the polydisc {\em Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352.
\item Chatterjee, Esha and Hassan, Sk. Sarif, On the asymptotic character of a generalized rational
difference equation {\em Discrete Contin. Dyn. Syst.} {\bf 38} (2018), 1707--1718.
\item Chen, Y. and Rangarajan, G. and Ding,. M., General stability analysis of synchronized dynamics in coupled systems {\em Physical Review E} {\bf 67} (2003), 26209.0.
\item Chopra, R. and Murthy, C. R. and Rangarajan, G., Statistical tests for detecting Granger causality {\em IEEE Transactions on Signal Processing} {\bf } (2018), 5803.
\item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
K. C., A note on linear preservers of semipositive and minimally
semipositive matrices {\em Electron. J. Linear Algebra} {\bf 34} (2018), 687--694.
\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram, Hardy-type inequalities for fractional powers of the
{D}unkl-{H}ermite operator {\em Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544.
\item Das, Soumya and Khan, Rizwanur, The third moment of symmetric square {$L$}-functions {\em Q. J. Math.} {\bf 69} (2018), 1063--1087.
\item Das, Soumya and Kohnen, Winfried, On sign changes of eigenvalues of {S}iegel cusp forms of genus
2 in prime powers {\em Acta Arith.} {\bf 183} (2018), 167--172.
\item Datta, Basudeb and Maity, Dipendu, Semi-equivelar maps on the torus and the {K}lein bottle are
{A}rchimedean {\em Discrete Math.} {\bf 341} (2018), 3296--3309.
\item Daya Sagar B. S. and Rangarajan, G. and Veneziano, D., Fractals in Geophysics {\em Chaos, Solitons and Fractals} {\bf 19} (2004), 237.
\item Dhamala, M. and Rangarajan, G. and Ding, M., Estimating Granger causality from Fourier and wavelet transforms of time series data {\em Physical Review Letters} {\bf 100} (2008), 18701.0.
\item Dhamala, M. and Rangarajan, G. and Ding, M., Analyzing information flow in brain networks with nonparametric Granger causality {\em NeuroImage} {\bf 41} (2008), 354.
\item Ding. M and Rangarajan. G, Parametric spectral analysis {\em Encyclopedia of Computational Neuroscience: Springer Reference} {\bf } (2015), .
\item Dond, Asha K. and Gudi, Thirupathi, Patch-wise local projection stabilized finite element methods
for convection-diffusion-reaction problems {\em Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663.
\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH., An error analysis of discontinuous finite element methods for
the optimal control problems governed by {S}tokes equation {\em Numer. Funct. Anal. Optim.} {\bf 40} (2019), 421--460.
\item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P. and Silberman, Lior and Tao, Terence, Homogeneous length functions on groups {\em Algebra Number Theory} {\bf 12} (2018), 1773--1786.
\item Gaddam, Sharat and Gudi, Thirupathi, Inhomogeneous {D}irichlet boundary condition in the {\it a
posteriori} error control of the obstacle problem {\em Comput. Math. Appl.} {\bf 75} (2018), 2311--2327.
\item Gaddam, Sharat and Gudi, Thirupathi, Bubbles enriched quadratic finite element method for the
3{D}-elliptic obstacle problem {\em Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236.
\item Gade, P. and Rangarajan, G., Frustration induced oscillator death on networks {\em Chaos} {\bf 23} (2013), 13892.
\item Ganapathy, R. and Rangarajan, G. and Sood A. K., Granger causality and cross recurrence plots in rheochaos {\em Physical Review E} {\bf 75} (2007), 7305.
\item Gaussier, Herv\'{e} and Seshadri, Harish, Holomorphic motions and complex geometry {\em Proc. Amer. Math. Soc.} {\bf 147} (2019), 301--313.
\item Gaussier, Herv\'{e} and Seshadri, Harish, On the {G}romov hyperbolicity of convex domains in {$\Bbb
C^n$} {\em Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641.
\item Ghara, Soumitra and Kumar, Surjit, On the sum of two subnormal kernels {\em J. Math. Anal. Appl.} {\bf 469} (2019), 1015--1027.
\item Ghosh, A. and Paria, D. and Rangarajan, G. and Ghosh, A., Velocity fluctuations in helical propulsion: How small can a propeller be {\em Journal of Physical Chemistry Letters} {\bf 5} (2014), 62.
\item Ghosh, Mrinal K. and Pradhan, Somnath, Risk-sensitive stochastic differential games with reflecting
diffusions {\em Stoch. Anal. Appl.} {\bf 36} (2018), 1--27.
\item Ghosh, S. and Rangarajan, G. and Sinha, S., Stability of synchronization in a multi-cellular system {\em European Physics Letters} {\bf 92} (2010), 40012.
\item Gudi, Thirupathi and Majumder, Papri, Convergence analysis of finite element method for a parabolic
obstacle problem {\em J. Comput. Appl. Math.} {\bf 357} (2019), 85--102.
\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh, Von {N}eumann's inequality for commuting operator-valued
multishifts {\em Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.
\item Gupta, Rajeev and Ramiz Reza, Md., Operator space structures on {$\ell^1(n)$} {\em Houston J. Math.} {\bf 44} (2018), 1205--1212.
\item Gupta, S. C., The classical {S}tefan problem {\em } {\bf } (2018), xxiii+726.
\item Hazra, Somnath, Homogeneous 2-shifts {\em Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.
\item Iyer, Srikanth K., The random connection model: connectivity, edge lengths, and
degree distributions {\em Random Structures Algorithms} {\bf 52} (2018), 283--300.
\item Jha, Abhash Kumar and Sahu, Brundaban, Rankin-{C}ohen brackets on {J}acobi forms of several variables
and special values of certain {D}irichlet series {\em Int. J. Number Theory} {\bf 15} (2019), 925--933.
\item Joshi, A. U. and Sant, D. A. and Parvez, I. A. and Rangarajan, G. and Limaye, M. A. and Mukherjee, S. and Charola, M. J. and Bhatt, M. N. and Mistry, S. P., Sub-surface profiling of granite pluton using microtremor method: southern Aravalli, Gujarat, India {\em International Journal of Earth Sciences} {\bf 106} (2017), 0.
\item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
Sekar, Sruthi, Non-malleable randomness encoders and their applications {\em Advances in cryptology---{EUROCRYPT} 2018. {P}art {III}} {\bf 10822} (2018), 589--617.
\item Kashyap, G. A. R. S. R. K. and Bapat, D. and Das, D. and Gowaikar, R. D. and  Amritkar, R. E. and Rangarajan, G. and V. Ravindranath and G. Ambika, Synapse loss and progress of Alzheimer&rsquo;s disease - A network model {\em Scientific Reports} {\bf 9} (2019), .
\item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan, On the convolution of {M}ittag-{L}effler distributions and its
applications to fractional point processes {\em Stoch. Anal. Appl.} {\bf 37} (2019), 115--122.
\item Khare, Apoorva, Generalized nil-{C}oxeter algebras over discrete complex
reflection groups {\em Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999.
\item Khare, Apoorva, Generalized nil-Coxeter algebras {\em S&eacute;m. Lothar. Combin.} {\bf 80B,} (2018), .
\item Khare, Apoorva and Tao, Terence., Schur polynomials, entrywise positivity preservers, and weak majorization. {\em S&eacute;m. Lothar. Combin.} {\bf 80B,} (2018), .
\item Khare, Apoorva and Tikaradze, Akaki, A {C}arlitz--von {S}taudt type theorem for finite rings {\em Linear Algebra Appl.} {\bf 568} (2019), 106--126.
\item Krakovski, Roi and Onn, Uri and Singla, Pooja, Regular characters of groups of type {$\ssf A_n$} over
discrete valuation rings {\em J. Algebra} {\bf 496} (2018), 116--137.
\item Lin, X. and Kulkarni, P. and Bocci, F. and Schafer, N. and Roy, S. and Tsai, M-Y. and He, Y. and Chen, Y and Rajagopalan, K. and Mooney, S. and Zeng, Y. and Weninger, K. and Grishaev, A. and Onuchic, J. and Levine, H. and Wolynes, P. and Salgia, R. and Rangarajan, G. and Uversky, V. and Orban, J. and Jolly, M. K., Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level {\em Biomolecules} {\bf 9} (2019), 77.
\item Lin, X. and Roy, S. and Jolly, M. K. and Bocci, F. and Schafer, N. P. and Tsai, M.-Y. and Chen, Y. and He, Y. and Grishaev, A. and Weninger, K. and Orban, J. and Kulkarni, P. and Rangarajan, G. and Levine, H. and J. N. Onuchic, PAGE4 and conformational switching: Insights from molecular dynamics simulations and implications for prostate cancer {\em Journal of Molecular Biology} {\bf 430} (2018), 2422.
\item Mahajan, Prachi and Verma, Kaushal, A comparison of two biholomorphic invariants {\em Internat. J. Math.} {\bf 30} (2019), 1950012, 16.
\item Mahmoudabadi, G. and Rajagopalan, K. and Getzenberg, R. H. and Hannenhalli, S. and Rangarajan, G. and Kulkarni, P., Intrinsically disordered proteins and conformational noise: Implications in cancer {\em Cell Cycle} {\bf 12} (2013), 26.
\item Maity, Dipendu, Pentagonal maps on the torus and the plane {\em Beitr. Algebra Geom.} {\bf 60} (2019), 17--37.
\item Maity, Dipendu and Upadhyay, Ashish Kumar, On centrally symmetric manifolds {\em J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.
\item Mal, Arpita and Sain, Debmalya and Paul, Kallol, On some geometric properties of operator spaces {\em Banach J. Math. Anal.} {\bf 13} (2019), 174--191.
\item Manfio, F. and Turgay, N. C. and Upadhyay, A., Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
{$\Bbb{H}^n\times\Bbb{R}$} {\em J. Geom. Anal.} {\bf 29} (2019), 283--298.
\item Manikandan, K. and Vishnu Priya, N. and Senthilvelan, M. and
Sankaranarayanan, R., Deformation of dark solitons in a {$\Cal{PT}$}-invariant
variable coefficients nonlocal nonlinear {S}chr\"{o}dinger
equation {\em Chaos} {\bf 28} (2018), 083103, 12.
\item Misra, Gadadhar and Pal, Avijit, Curvature inequalities for operators in the {C}owen-{D}ouglas
class and localization of the {W}allach set {\em J. Anal. Math.} {\bf 136} (2018), 31--54.
\item Mooney, S. M. and Rajagopalan, K. and Rangarajan, G. and Kulkarni, P., Cancer/testis antigens and obligate participation in multiple hallmarks of cancer: an update {\em Asian Journal of Andrology} {\bf 18} (2016), 711.
\item Mukherjee, Sajal Kumar and Bera, Sudip, Combinatorial proofs of the {N}ewton-{G}irard and
{C}hapman-{C}ostas-{S}antos identities {\em Discrete Math.} {\bf 342} (2019), 1577--1580.
\item Nalatore, H. and Ding, M. and Rangarajan, G., Mitigating the effects of measurement noise on Granger causality {\em Physical Review E} {\bf 75} (2007), 12883.
\item Nalatore, H. and Ding, M. and Rangarajan, G., Denoising neural data with state-space smoothing: Method and application {\em Journal of Neuroscience Methods} {\bf 179} (2009), 131.
\item Nalatore, H. and Rangarajan, G., Short-window spectral analysis using AMVAR and multitaper methods: A comparison {\em Biological Cybernetics} {\bf 101} (2009), 71.
\item Nalatore. H. and Sasikumar, N. and Rangarajan, G., Effect of measurement noise on Granger causality {\em Physical Review E} {\bf 90} (2014), 25687.
\item Narayanan, E. K. and Singla, Pooja, On monomial representations of finitely generated nilpotent
groups {\em Comm. Algebra} {\bf 46} (2018), 2319--2331.
\item Pal, Chandan and Pradhan, Somnath, Risk sensitive control of pure jump processes on a general
state space {\em Stochastics} {\bf 91} (2019), 155--174.
\item Pal, Ratna and Verma, Kaushal, Ergodic properties of families of {H}\'{e}non maps {\em Ann. Polon. Math.} {\bf 121} (2018), 45--71.
\item Palaniyandi, P. and Rangarajan, G., Critical lattice size limit for synchronized chaotic state in one- and  two-dimensional diffusively coupled map lattices {\em Physical Review E} {\bf 76} (2007), 11906.
\item Palaniyandi, P. and Rangarajan, G., A mathematical model for storage and recall of images using targeted synchronization of coupled maps {\em Scientific Reports} {\bf 7} (2017), 8921.
\item Paul, Kallol and Sain, Debmalya, Birkhoff-{J}ames orthogonality and its application in the
study of geometry of {B}anach space {\em Advanced topics in mathematical analysis} {\bf } (2019), 245--284.
\item Paul, Kallol and Sain, Debmalya and Mal, Arpita, Approximate {B}irkhoff-{J}ames orthogonality in the space of
bounded linear operators {\em Linear Algebra Appl.} {\bf 537} (2018), 348--357.
\item Paul, Kallol and Sain, Debmalya and Mal, Arpita and Mandal,
Kalidas, Orthogonality of bounded linear operators on complex {B}anach
spaces {\em Adv. Oper. Theory} {\bf 3} (2018), 699--709.
\item Pingali, Vamsi P., A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE} {\em Complex Var. Elliptic Equ.} {\bf 64} (2019), 503--518.
\item Pingali, Vamsi Pritham, A note on higher extremal metrics {\em Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010.
\item Pingali, Vamsi Pritham, Representability of {C}hern-{W}eil forms {\em Math. Z.} {\bf 288} (2018), 629--641.
\item Pritham Pingali, Vamsi, Existence of coupled {K}\"{a}hler-{E}instein metrics using the
continuity method {\em Internat. J. Math.} {\bf 29} (2018), 1850041, 8.
\item Quddus, Safdar, Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
spheres {\em J. Noncommut. Geom.} {\bf 13} (2019), 257--267.
\item Rangarajan, G., Symplectic integration of nonlinear Hamiltonian systems {\em Pramana -- Journal of Physics} {\bf 48} (1997), 129.
\item Rangarajan, G., Fractals in geophysics {\em “Application of Fractals in Earth Sciences"} {\bf } (2000), .
\item Rangarajan, G., Applications of Lie algebraic techniques to nonlinear Hamiltoniansystems {\em Nonlinear Phenomena} {\bf } (2000), .
\item Rangarajan, G., Polynomial map factorization of symplectic maps {\em International Journal of Modern Physics C} {\bf 14} (2003), 847.
\item Rangarajan, G. and Ding, M., Integrated approach to the assessment of long range correlation in time series data {\em Physical Review E} {\bf 61} (2000), 4991.
\item Rangarajan, G. and Ding, M., First passage time problem for biased continuous-time random walks {\em Fractals} {\bf 8.0} (2000), 139.
\item Rangarajan, G. and Ding, M., First passage distributions for long memory processes {\em Lecture Notes in Physics} {\bf 621} (2003), 167.
\item Rangarajan, G. and Habib, S. and Ryne, R. D., Lyapunov exponents without rescaling and reorthogonalization {\em Physical Review Letters} {\bf 80} (1998), 3747.
\item Rangarajan, G. and Sachidanand, M., Spherical aberration and its correction using Lie algebraic techniques {\em Pramana - Journal of Physics} {\bf 49} (1997), 635.
\item Rangarajan, G. and Sachidanand, M., Invariant metric for nonlinear symplectic maps {\em Pramana - Journal of Physics} {\bf 58} (2002), 477.
\item Rangarajan, G. and Sant, D. A., A climate predictability index and its applications {\em Geophysical Research Letters} {\bf 24} (1997), 1239.
\item Rangarajan, G. and Sant, D. A., Paleoclimatic data from 74KL and Guliya cores: New insights {\em Geophysical Research Letters} {\bf 27} (2000), 787.
\item Rangarajan, G. and Sant, D. A., Fractal dimensional analysis of Indian climatic dynamics {\em Chaos, Solitons and Fractals} {\bf 19} (2004), 285.
\item Rangarajan, N. and Fox, Z. and Singh, A. and Kulkarni, P. and Rangarajan, G., Disorder, Oscillatory Dynamics and State Switching: The Role of c-Myc {\em Journal of Theoretical Biology} {\bf 386} (2015), 105.
\item Ray, A. and Sehgal, N. and Karunakaran, S. and Rangarajan, G. and  Ravindranath, V., MPTP activates ASK1-p38 MAPK signaling pathway through TNF-dependent Trx1 oxidation in Parkinsonism mouse model {\em Free Radical Biology & Medicine} {\bf 87} (2015), 312.
\item Reddy, Nanda Kishore, Equality of {L}yapunov and stability exponents for products of
isotropic random matrices {\em Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624.
\item Resmi, V. and Ambika, G. and Amritkar, R. E. and Rangarajan, G., Amplitude death in complex networks induced by environment {\em Physical Review E} {\bf 85} (2012), 19593.
\item Reza, Md. Ramiz, Curvature inequalities for operators in the {C}owen-{D}ouglas
class of a planar domain {\em Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279.
\item Sain, Debmalya, On extreme contractions and the norm attainment set of a
bounded linear operator {\em Ann. Funct. Anal.} {\bf 10} (2019), 135--143.
\item Sain, Debmalya, On the norm attainment set of a bounded linear operator {\em J. Math. Anal. Appl.} {\bf 457} (2018), 67--76.
\item Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag,
Santanu, On the numerical index of polyhedral {B}anach spaces {\em Linear Algebra Appl.} {\bf 577} (2019), 121--133.
\item Sain, Debmalya and Paul, Kallol and Mal, Arpita, A complete characterization of {B}irkhoff-{J}ames
orthogonality in infinite dimensional normed space {\em J. Operator Theory} {\bf 80} (2018), 399--413.
\item Sain, Debmalya and Paul, Kallol and Mal, Arpita, On approximate {B}irkhoff-{J}ames orthogonality and normal
cones in a normed space {\em J. Convex Anal.} {\bf 26} (2019), 341--351.
\item Sampath, D. and Sabitha, K. R. and Hegde, P. and Jayakrishnan, H. R. and Kutty, B.M. and Chattarji, S. and Rangarajan, G. and Laxmi, T.R., A study on fear memory retrieval and REM sleep in maternal separation and isolation stressed rats {\em Behavioural Brain Research} {\bf 273} (2014), 144.
\item Sanki, Bidyut, Filling of closed surfaces {\em J. Topol. Anal.} {\bf 10} (2018), 897--913.
\item Sanki, Bidyut and Gadgil, Siddhartha, Graphs of systoles on hyperbolic surfaces {\em J. Topol. Anal.} {\bf 11} (2019), 1--20.
\item Sant D. A and Parvez, I. A. and Rangarajan, G. and Patel, J. and Bhatt, M. N. and Salam, T. A. S., Subsurface profiling along Banni Plains and bounding faults, Kachchh, Western India using Microtremors method {\em Journal of Asian Earth Sciences} {\bf 146} (2017), 326.
\item Sant, D. A. and Krishnan, K. and Rangarajan, G. and Basavaiah, N. and Pandya and C.,Sharma, M. and Trivedi, Y., Characterization of flood plain and climate change using multi-proxy records {\em Journal of Indian Geophysical Union} {\bf 8.0} (2004), 39.
\item Sant, D. A. and Rangarajan, G., Onset of climate change at last Glacial-Holocene transition: Role of the tropical Pacific {\em Current Science} {\bf 83} (2002), 1398.
\item Sant, D. A. and Rangarajan, G., Study of Indian climate variability using predictability indices {\em Modern Applied Mathematics} {\bf } (2005), 145.
\item Sant, D. A. and Rangarajan, G. and Krishnan, K. and Basavaiah, N. and Pandya, C. and Sharma, M. and Trivedi, Y., “ Flood plain record of southwest Indian monsoon during the last glacial" {\em Man and Environment} {\bf 31} (2006), 9.0.
\item Sant, D.A. and Parvez, I. A. and Rangarajan, G. and Patel, S. J. and Salam, T. A. S. and Bhatt, M. N., Subsurface imaging of brown coal bearing Tertiary sedimentaries - Deccan Trap interface using microtremor method {\em Journal of Applied Geophysics} {\bf 159} (2018), 362.
\item Seshadri, Harish and Verma, Kaushal, Some aspects of the automorphism groups of domains {\em Handbook of group actions. {V}ol. {III}} {\bf 40} (2018), 145--174.
\item Sukumaran, P. and Parvez, I. A. and Sant, D. A. and Rangarajan, G. and Krishnan, K., Profiling of Late Tertiary - Early Quaternary surface in the lower reaches of Narmada Valley using microtremors {\em Journal of Asian Earth Sciences} {\bf 41} (2011), 325.
\item Sukumaran, P. and Sant, D. A. and Krishnan, K. and Rangarajan, G., High resolution facies record on Late Holocene flood plain sediments from lower reaches of Narmada Valley, Western India {\em Journal of the Geological Society of India} {\bf 79} (2012), 41.
\item Thangavelu, Sundaram, An analogue of {P}fannschmidt's theorem for the {H}eisenberg
group {\em J. Anal.} {\bf 26} (2018), 235--244.
\item Thangavelu, Sundaram and Naidu Dogga, Venku, {$L^p$}-{$L^2$} estimates for solutions of the wave equation
associated to the {G}rushin operator {\em Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92.
\item Truccolo, W. A. and Rangarajan, G. and Chen, Y. and Ding, M., Analyzing stability of equilibrium points in neural networks: A general approach {\em Neural Networks} {\bf 16} (2003), 1453.
\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh, On biconservative hypersurfaces in 4-dimensional {R}iemannian
space forms {\em Math. Nachr.} {\bf 292} (2019), 905--921.
\item Verma, Kaushal, Notes on the boundaries of quadrature domains {\em Anal. Math. Phys.} {\bf 9} (2019), 617--638.
\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, Govindan
and Lakshmanan, M., On symmetry preserving and symmetry broken bright, dark and
antidark soliton solutions of nonlocal nonlinear {S}chr\"{o}dinger
equation {\em Phys. Lett. A} {\bf 383} (2019), 15--26.
\item Wen. X. and Rangarajan, G. and Ding, M., Is Granger causality a viable technique for analyzing fMRI data? {\em PLoS One} {\bf 8.0} (2013), e67428.
\item “Albo, Z. and Di Prisco, G. V. and Chen, Y. and Rangarajan, G. and Truccolo, W. and Feng, J. and Vertes, R. P. and Ding, M.", Is partial coherence a viable technique for identifying generators of neural oscillations? {\em Biological Cybernetics} {\bf 90} (2004), 318.
\item “Rangarajan, G. and Habib, S. and Ryne, R. D.", A new method for computing Lyapunov exponents {\em Nonlinear Dynamics and Brain Functioning} {\bf } (1999), .
\end{enumerate}

### 2019-08-08 data/draft-sections.tex
filter correction

\subsection{Summer Students}

\begin{enumerate}
\item K Philip Thomas, IISc-Bangalore did his/her  summer project under the guidance of R. Venkatesh during May 1--31, 2018
\item Rati Ludhani, IIT Bombay did his/her  summer project under the guidance of R. Venkatesh during May 6--31, 2018
\item Nazia V from IISER Pune did his/her  summer project under the guidance of Pooja Singla during 1st June-30th July, 2018
\item      Ms. Meghna, first year BSc,Christ University, Bangalore did his/her  summer project under the guidance of A. K. Nandakumaran during April 11 – May 10, 2018. 
\item Deeparaj Bhat did his/her KVPY summer project under the guidance of Subhojoy Gupta during May - July 2018
\item Arka Ghosh did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May-June 2018
\item Chinmaya Kausik did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May-June 2018
\item Nishit Pandya did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May-June 2018
\item Julian D'Costa did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May-June 2018
\item Vrunda Rathi did his/her KVPY summer project under the guidance of Arvind Ayyer during May-July
\item KARTIK SINGH did his/her KVPY summer project under the guidance of Arvind Ayyer during May-July
\item ADITHYA UPADHYA  did his/her KVPY summer project under the guidance of Arvind Ayyer during May-July
\item MANISH PANDEY did his/her KVPY summer project under the guidance of Arvind Ayyer during May - July
\item Nandan Malhotra, IISER Mohali did his/her  summer project under the guidance of Srikanth K. Iyer during May - July 2018
\end{enumerate}

\section{Resource Generation}

\begin{enumerate}

\item {\bf A. K. Nandakumaran\,:} A. K. Nandakumaran in a DST-SERB (Matrics) project
\begin{description}
  \item[Project Title\,:] Unfolding Operators to Study Homogenization Problems in Domains with Highly Oscillating Structures
  \item[Duration\,:] 2018-2021
  \item[Grant\,:] 6.6 Lakhs
\end{description}

\item {\bf A. K. Nandakumaran\,:} A. K. Nandakumaran in a DST(SERB) project
\begin{description}
  \item[Project Title\,:] Homogenization of Partial Dierential Equations in Certain Complex Domains
  \item[Duration\,:] 2017-2020
  \item[Grant\,:] Rs. 19.316 Lakhs
\end{description}

\item {\bf Apoorva Khare\,:} Sole PI in an Infosys Foundation project (Young Investigator Award) in a Infosys Foundation, India project
\begin{description}
  \item[Project Title\,:] N/A
  \item[Duration\,:] 2017-2019
  \item[Grant\,:] 600,000 per year
\end{description}

\item {\bf Apoorva Khare\,:} Sole PI in a SERB project (Ramanujan Fellowship) in a SERB, DST, Govt. of India project
\begin{description}
  \item[Project Title\,:] N/A
  \item[Duration\,:] 2018-2023
  \item[Grant\,:] 700000 per year
\end{description}

\item {\bf Apoorva Khare\,:} Sole PI an a SERB project (MATRICS grant) in a SERB, DST, Govt. of India project
\begin{description}
  \item[Project Title\,:] Entrywise powers and power series preserving positivity in fixed dimension
  \item[Duration\,:] 2018-2021
  \item[Grant\,:] 200000 per year
\end{description}

\item {\bf Arvind Ayyer\,:} Sole investigator in an SERB project in a SERB project
\begin{description}
  \item[Project Title\,:]  Exactly solvable exclusion processes
  \item[Duration\,:] 2018--2020
  \item[Grant\,:] Rs. 19,30,490/-
\end{description}

\item {\bf Basudeb Datta\,:} Basudeb Datta, Sole investigator in a SERB, DST project
\begin{description}
  \item[Project Title\,:] Minimal and tight triangulations of some pl manifolds
  \item[Duration\,:] May 13, 2018 to May 12, 2021
  \item[Grant\,:] Rs.660,000
\end{description}

\item {\bf Dilip P Patil\,:} Principal Investigator in a SERB Matrics Project in a DST-SERB project
\begin{description}
  \item[Project Title\,:] Burnside Algebras --- Computational Aspects
  \item[Duration\,:] Oct 2018 to Oct 2021
  \item[Grant\,:] 200000 Per year
\end{description}

\item {\bf Gautam Bharali\,:} Sole investigator in a DST project in a DST project
\begin{description}
  \item[Project Title\,:] Swarnajayanti Fellowship
  \item[Duration\,:] 2015--2020
  \item[Grant\,:] Rs. 56.7 lakhs
\end{description}

\item {\bf Govindan Rangarajan\,:} Sole Investigator in a SERB project
\begin{description}
  \item[Project Title\,:] JC Bose Fellowship
  \item[Duration\,:] 2011-present
  \item[Grant\,:] 1,59,85,000
\end{description}

\item {\bf Govindan Rangarajan\,:} Director in a DST-CNRS project
\begin{description}
  \item[Project Title\,:] Indo-French Centre for Applied Matheamtics
  \item[Duration\,:] 2018-present
  \item[Grant\,:] 6,83,00,000 + matching grant from CNRS
\end{description}

\item {\bf Govindan Rangarajan\,:} Principal Investigator in a Broadcom Foundation project
\begin{description}
  \item[Project Title\,:] EMEA Workshops
  \item[Duration\,:] 2017-present
  \item[Grant\,:] 1,35,00,000
\end{description}

\item {\bf Govindan Rangarajan\,:} Co-Principal Investigator in a Tata Trusts project
\begin{description}
  \item[Project Title\,:] Alzheimer's Research
  \item[Duration\,:] 2014-present
  \item[Grant\,:] 75,00,00,000
\end{description}

\item {\bf Manjunath Krishnapur\,:} Manjunath Krishnapur (PI) in a SERB project
\begin{description}
  \item[Project Title\,:] Zeros of random functions and anti-concentration phenomena
  \item[Duration\,:] 2018-2021
  \item[Grant\,:] 6,60,000
\end{description}

\item {\bf Pooja Singla\,:} Pooja Singla and Sole-investigator in a SERB-MATRICS project
\begin{description}
  \item[Project Title\,:] "Representations of Linear Groups over Local Rings : Gelfand Models "
  \item[Duration\,:] March 2019-March 2022
  \item[Grant\,:] 6,00,000
\end{description}

\item {\bf Pooja Singla\,:} Amritanshu Prasad, Uri Onn, James Borger, Pooja Singla and PI, PI, Co-PI, Co-PI  in a MHRD-SPARC  project
\begin{description}
  \item[Project Title\,:] Representation Zeta Functions
  \item[Duration\,:] March 2019 to march 2021
  \item[Grant\,:] 71,46,350
\end{description}

\item {\bf R. Venkatesh\,:} Investigator in a DST project
\begin{description}
  \item[Project Title\,:] Inspire
  \item[Duration\,:] 2016--2020
  \item[Grant\,:] 35 Lakhs
\end{description}

\item {\bf R. Venkatesh\,:} Investigator in a DST-SERB project
\begin{description}
  \item[Project Title\,:] Study on the structure theory of Borcherds-Kac-Moody algebras and their subalgebras
  \item[Duration\,:] 2018-2020
  \item[Grant\,:] 6 Lakhs
\end{description}

\item {\bf Siddhartha Gadgil\,:} Sole investigator in a SERB project
\begin{description}
  \item[Project Title\,:] Homotopy Type theory and Natural langauge processing for Computer-Assisted Mathematics
  \item[Duration\,:] 2018-2021
  \item[Grant\,:] Rs. 19 lakhs
\end{description}

\item {\bf Srikanth K. Iyer\,:} Sole investigator in a SERB project in a SERB project
\begin{description}
  \item[Project Title\,:] Percolation at Criticality and Connectivity in the Random Connection Model
  \item[Duration\,:] 2019-2022
  \item[Grant\,:] six lakhs
\end{description}

\item {\bf Subhojoy Gupta\,:} Sole Investigator in SERB project in a SERB project
\begin{description}
  \item[Project Title\,:] Degenerations of geometric structures and meromorphic differentials on Riemann surfaces
  \item[Duration\,:] 2018-2020
  \item[Grant\,:] 660000
\end{description}

\item {\bf Sundaram Thangavelu\,:} Principal Investigator in a SERB project
\begin{description}
  \item[Project Title\,:] JC Bose National Fellowship
  \item[Duration\,:] 2018-2022
  \item[Grant\,:] 
\end{description}

\item {\bf Vamsi Pritham Pingali\,:} Vamsi Pritham Pingali (Principal Investigator) in a SERB project
\begin{description}
  \item[Project Title\,:] A study of some analytic and computational aspects of Chern-Weil theory
  \item[Duration\,:] 2017-2020
  \item[Grant\,:] 5,42,290 INR
\end{description}

\item {\bf Vamsi Pritham Pingali\,:} Vamsi Pritham Pingali (Principal Investigator) in a Infosys foundation project
\begin{description}
  \item[Project Title\,:] Young Investigator Award (No title)
  \item[Duration\,:] 2017-2019
  \item[Grant\,:] 600000 INR 
\end{description}

\end{enumerate}

\subsection{Awards}

\begin{enumerate}
\item Apoorva Khare was awarded Ramanujan Fellowship (Apr 2018), ICM Satellite Conference invited talk (Aug 2018), Tarun Tejankit Puraskar from Loksatta newspaper (Mar 2019)
\item R. Venkatesh was awarded Associate of the Indian Academy of Sciences 2018-2022
\item Subhojoy Gupta was awarded Simons Visiting Professorship grant to support a visit to Heidelberg University (September 10-17, 2018) following participation at the Oberwolfach workshop
\item Sundaram Thangavelu was awarded V.V. Narlikar Memorial lecture award from INSA
\end{enumerate}

\subsection{Fellowships of Academies}

\begin{enumerate}
\item Apoorva Khare was elected a N/A
\end{enumerate}

\subsection{Editorial boards}
\begin{enumerate}
\item A. K. Nandakumaran, Editorial Member, TMC Bulletin
\item Apoorva Khare, TRIM Series (Hindustan Book Agency); Sao Paulo Journal of Mathematical Sciences
\item Gautam Bharali, Newsletter of the Ramanujan Mathematical Society
\item Sundaram Thangavelu, Proceedings of the Indian Academy of Sciences
\end{enumerate}

### 2019-08-08 ugc/src/Publications.scala

@@ -32,7 +32,9 @@ object Publications {
       case _ => ""
   }
 
-  lazy val allPubs : Vector[Map[String,String]] = (mp ++ (data.map(m => m.mapValues(getString(_))))).sortBy(m => m("author"))
+  lazy val allPubs : Vector[Map[String,String]] = (mp ++ 
+    (data.map(m => m.mapValues(getString(_)))).filter(m => Set("2018", "2019").contains(m("year")))
+    ).sortBy(m => m("author"))
 
   def tex(m: Map[String, String]) = {
       val author = m("author")

### 2020-08-05 ugc/src/Data.scala
better formatting of output

@@ -19,6 +19,7 @@ object Data {
   val activiesInit = awardsPos + 3  
   val fullSize = activiesInit + (2 * activitiesSize) // because of old activities
   def pad(v: Vector[String]) = v ++ Vector.fill(fullSize - v.size)("")
+  def preComma(s: String) = if (s.trim() == "") "" else s", $s"
 
   lazy val data = os.read
     .lines(os.resource / "ugc2020.tsv")
@@ -203,15 +204,17 @@ case class Paper(
     doi: String,
     url: String
 ) {
+  val doiText = if (doi.trim() == "") "" else s", DOI $doi"
+  val urlText = if (url.trim() == "") "" else s", \\url{$url}"
   val tail = status match {
-    case "Preprint"                 => "preprint."
-    case "Submitted"                => "submitted for publication."
-    case "Accepted for publication" => s"to appear in $journal."
-    case "Published"                => s"{\\em $journal} {\\bf $volume} ($year), $pages."
+    case "Preprint"                 => "preprint"
+    case "Submitted"                => "submitted for publication"
+    case "Accepted for publication" => s"to appear in $journal"
+    case "Published"                => s"$journal {\\bf $volume} ($year), $pages"
     case _                          => ""
   }
 
-  val tex = s"\\item $author, $title, $tail"
+  val tex = s"\\item $author, \\emph{$title}, $tail$doiText$urlText."
 }
 
 object Paper {
@@ -247,7 +250,7 @@ case class ConfPaper(
     year: String,
     pages: String
 ) {
-  val tex = s"\\item $author, $title {\\em $conf} ($year)."
+  val tex = s"\\item $author, \\emph{$title} in $volumeEditors (ed.), {\\em $volumeTitle} ${preComma(conf)} ${preComma(publisher)} ($year)${preComma(pages)}."
 }
 
 object ConfPaper {
@@ -282,7 +285,7 @@ case class Book(
     year: String
 ) {
   val tex =
-    s"\\item $author, $title in {\\em $publisher}{\bf $volume} ($year)."
+    s"\\item $author, \\emph{$title} ${preComma(series)} $volume ${preComma(publisher)} ($year)."
 }
 
 object Book {

### 2020-08-05 ugc/src/Publications.scala

@@ -46,7 +46,11 @@ object Publications {
     val pages = m.getOrElse("pages", "")
     val volume = m.getOrElse("volume", "")
     val year = m("year")
-    s"\\item $author, $title {\\em $journal} {\\bf $volume} ($year), $pages."
+    val doiOpt = m.get("doi")
+    val urlOpt = m.get("url")
+    val doiText = doiOpt.map(s =>s", DOI $s").getOrElse("")
+    val urlText = urlOpt.map(s => s", \\url{$s}").getOrElse("")
+    s"\\item $author, {\\em $title}, $journal} {\\bf $volume} ($year), $pages$doiText$urlText."
   }
 
   lazy val pubItems = allPubs.map(tex)

### 2020-08-05 data/draft-publications.tex
postdocs code, data; first generation

@@
 \begin{enumerate}
-\item 2.
+\item S Aiyappan, A.
+K.
+Nandakumaran and Abu Sufian, \emph{Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure},  Mathematical Methods in the Applied Sciences {\bf 42} (2019.
+DOI: 10.1002/mma.5748), 6407-6434 , DOI 10.1002/mma.5748.
+\item K.
+Murali, A.
+K.
+Nandakumaran, Turgurt Durduran, Hari M Varma, \emph{Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements}, Biomedical Optics Express 5395 {\bf 10} (2019), .
+\item S Aiyappan, A.
+K.
+Nandakumaran and Ravi Prakash, \emph{Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains}, Annali di Matematica Pura ed Applicata {\bf 198} (2019), 1931-1954, DOI 10.1007/s10231-019-00848-7.
+\item S Aiyappan, A.
+K.
+Nandakumaran and Ravi Prakash, \emph{Semi-linear optimal control problem on a smooth oscillating domain}, Communications in Contemporary Mathematics {\bf } (2019), 1-26, DOI 10.1142/S0219199719500299.
+\item S Aiyappan, Editha C.
+Jose, Ivy Carol B.
+Lomerio and A.
+K.
+Nandakumaran, \emph{ Control Problem on a Rough Circular Domain and Homogenization}, Asymptotic Analysis {\bf 115} (2019),  19-46, DOI 10.3233/ASY-191526.
+\item Khare, Apoorva and Rajaratnam, Bala, \emph{Probability inequalities and tail estimates for metric semigroups}, Advances in Operator Theory (Special issue in honor of Rajendra Bhatia) {\bf 5} (2020), 779-795, DOI 10.1007/s43036-020-00048-8, \url{https://link.springer.com/article/10.1007%2Fs43036-020-00048-8}.
+\item Ghosh, Subhajit, \emph{Total Variation Cutoff for the Transpose Top-2 with Random Shuffle}, to appear in Journal of Theoretical Probability, DOI 10.1007/s10959-019-00945-6, \url{https://link.springer.com/article/10.1007%2Fs10959-019-00945-6}.
+\item Datta, B.
+and Gupta, S., \emph{Semi-regular tilings of the hyperbolic plane \label{bdsg_2019} }, to appear in Discrete Comput Geom, DOI https://doi.org/10.1007/s00454-019-00156-0, \url{https://doi.org/10.1007/s00454-019-00156-0}.
+\item Datta, B. and Sarkar, S., \emph{Equilibrium triangulations of some quasitoric 4-manifolds}, Southeast Asian Bull. Math. {\bf 44} (2020), 57--78.
+\item Datta, B. and Maity, D., \emph{Correction to: Semi-equivelar and vertex-transitive maps on the torus}, Beitr Algebra Geom {\bf 61} (2020), 187--188.
+\item Martin Kreuzer and Dilip P.
+Patil , \emph{COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS}, to appear in Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry.
+\item Bharali, Gautam and Maitra, Anwoy, \emph{A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems}, to appear in Annali della Scuola Normale Superiore di Pisa, DOI 10.2422/2036-2145.201906_007, \url{http://annaliscienze.sns.it/index.php?page=ForthcomingArticles}.
+\item Maitra, Anwoy, \emph{On the continuous extension of Kobayashi isometries}, Proc.
+Amer.
+Math.
+Soc.
+{\bf 148} (2020), 3437--3451, \url{https://www.ams.org/journals/proc/2020-148-08/S0002-9939-2020-15038-1/}.
+\item Vishnu Priya, N.
+and Senthilvelan, M.
+and  Rangarajan, G.
+and Lakshmanan, M, \emph{On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation}, Physics Letters A {\bf 383} (2019), 15-26.
+\item Kashyap, G.
+A.
+R.
 S.
-Aiyappan, A.
+R.
 K.
-Nandakumaran and Ravi Prakash, Semi-linear optimal control problem on a smooth oscillating domain Communications in Contemporary Mathematics, {\em Communications in Contemporary Mathematics} {\bf } (2019), 26 pages.
-\item 1.
-S.
-Aiyappan, A.
+and Bapat, D.
+and Das, D.
+and Gowaikar, R.
+D.
+and Amritkar, R.
+E.
+and Rangarajan, G.
+and Ravindranath, V.
+and Ambika, G, \emph{Synapse loss and progress of Alzheimer’s disease - A network model}, Scientific Reports {\bf 9} (2019), 6555.
+\item Vishnu Priya, N.
+and Senthilvelan, M.
+and Rangarajan, G., \emph{On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation}, Chaos {\bf 29} (2019), 123135.
+\item Sarkar, Amar Deep and Verma, Kaushal, \emph{A submultiplicative property of the Carath\'{e}odory metric on planar domains}, Proc.
+Indian Acad.
+Sci.
+(Math.
+Sci.) {\bf } (), , \url{https://www.ias.ac.in/article/fulltext/pmsc/130/0035}.
+\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor, \emph{Higher Chern Classes in Iwasawa Theory}, American Journal of Mathematics {\bf 142} (2020), 627-682, \url{https://muse.jhu.edu/issue/42062}.
+\item Basu, R.
+and Ganguly, S.
+and Hegde, M.
+and Krishnapur, M., \emph{Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation}, to appear in Israel Journal of Mathematics.
+\item M.
 K.
-Nandakumaran and Abu Sufian, Asymptotic Analysis of a Boundary Optimal Control Problem on a General Branched Structure, to appear in Mathematical Methods in Applied Sciences (MMAS).
-\item Benedetti, Carolina and González D’León, Rafael S.
-and Hanusa, Christopher R.H.
-and Harris, Pamela E.
-and Khare, Apoorva and Morales, Alejandro H.
-and Yip, Martha, A combinatorial model for computing volumes of flow polytopes, {\em Transactions of the American Mathematical Society} {\bf 372} (2019), 3369-3404.
-\item Subhajit Ghosh, Total variation cutoff for the transpose top-2 with random shuffle, to appear in Journal of Theoretical Probability.
-\item G.
+Ghosh and S.
+Pradhan, \emph{Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant}, to appear in ESIAM: Control, Optimization and Calculus of Variations , DOI Doi:10.105/cocv/2020029.
+\item M.
 K.
-Basak, M.
+Ghosh, K.
+Suresh Kumar, C.
+Pal and S.
+Pradhan, \emph{Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications}, to appear in Stochastic Analysis and Applications, DOI Doi: 10.1080/07362994.2020.1796707.
+\item Iyer, S.
 K.
-Ghosh and D.
-Mukherjee, A Stochastic Model with Inflation, Growth and Technology for the Political Business Cycle, {\em Journal of Computational Economics} {\bf 53} (2019), 125-140.
-\item Arvind Ayyer and Pooja Singla, Random motion on finite rings, I: commutative rings, {\em Algebras and Representation theory} {\bf } (), .
-\item E.K.Narayanan and Pooja Singla, On monomial representations of finitely generated nilpotent groups, {\em Communications in Algebra} {\bf 46} (2018), 2319–2331.
-\item Souvik Dhara, Remco van der Hofstad, Johan S.H.
-van Leeuwaarden, Sanchayan Sen, Heavy-tailed configuration models at criticality, to appear in Annales de l'Institut Henri Poincaré (B) Probabilités et Statistiques.
-\item Siddhartha Gadgil, Homogeneous Length Functions on Groups: Intertwined Computer and Human Proofs, to appear in Journal of Automated Reasoning.
-\item Srikanth K. Iyer, The Random Connection Model - Connectivity, Edge Lengths and Degree Distributions, {\em Random Structures and Algorithms} {\bf 52} (2018), 283-300.
-\item Rahul Vaze, Srikanth K. Iyer, Capacity of Cellular Wireless Networks, {\em IEEE Transactions on Wireless Communications} {\bf 18} (2019), 1490 - 1503.
-\item Gokul Nair, Senthil Athmanathan,, Srikanth K.
-Iyer  and Vishwesha Guttal, Fission-fusion dynamics and group-size-dependent composition in heterogeneous populations, {\em Physical Review E} {\bf 99} (2019), .
-\item Subhojoy Gupta, Meromorphic quadratic differentials and measured foliations on a Riemann surface, {\em Mathematische Annalen} {\bf 373} (2019), 73-118.
-\item Subhojoy Gupta and Harish Seshadri, On domains biholomorphic to Teichmüller spaces, to appear in International Mathematics Research Notices.
-\item Subhojoy Gupta, Harmonic maps and wild Teichmüller spaces, to appear in ournal of Topology and Analysis.
-\item Subhojoy Gupta, Limits of harmonic maps and crowned hyperbolic surfaces, to appear in Transactions of the AMS.
-\item Luz Roncal and Sundaram Thangavelu, An extension problem and trace Hardy inequality for the sublaplacian on H-type groups, to appear in IMRN.
-\item Pradeep Boggarapu, Luz Roncal and Sundaram Thangavelu, On extension problem, trace Hardy and Hardy's inequalities for some fractional Laplacians, to appear in Communications in Pure and Applied Analysis..
-\item Indranil Biswas and Vamsi Pritham Pingali, Metric properties of parabolic ample bundles, to appear in International Mathematical Research Notices.
-\item Vamsi Pingali and Dror Varolin, Non-uniformly flat affine algebraic hypersurfaces, to appear in Nagoya mathematical journal.
+and Yogeshwaran, D., \emph{Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes}, Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques {\bf 56} (2020), 1869-1897, \url{https://doi.org/10.1214/19-AIHP1020}.
+\item Datta, Basudeb and Gupta, Subhojoy, \emph{Semi-regular tilings of the hyperbolic plane}, to appear in Discrete and Computational Geometry, DOI https://doi.org/10.1007/s00454-019-00156-0.
+\item Thirupathi Gudi, Ramesh Ch.
+Sau, \emph{Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem}, to appear in ESAIM: Control, Optim.
+Calc.
+Var, DOI doi: 10.1051/cocv/2019068..
+\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh, \emph{On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel},  Studia Math.
+{\bf 255} (2020), 83–107., DOI 10.4064/sm190505-8-10.
+\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada, \emph{Toeplitz operators on the symmetrized bidisc}, International Mathematics Research Notices (IMRN) {\bf } (), , DOI 10.1093/imrn/rnz333.
+\item Pingali, Vamsi Pritham and Varolin, Dror, \emph{Nonuniformly flat affine algebraic hypersurfaces}, to appear in Nagoya Mathematical Journal, DOI https://doi.org/10.1017/nmj.2019.2, \url{https://www.cambridge.org/core/journals/nagoya-mathematical-journal/article/nonuniformly-flat-affine-algebraic-hypersurfaces/3704C1133CB22A05D7FB13765156FC4E}.
+\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham , \emph{Gravitating vortices and the Einstein–Bogomol’nyi equations}, to appear in Mathematische Annalen, DOI https://doi.org/10.1007/s00208-020-01964-z, \url{https://link.springer.com/content/pdf/10.1007/s00208-020-01964-z.pdf}.
+\item Datar, Ved and Jacob,Adam and Zhang, Yuguang, \emph{Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces}, to appear in Journal of differential geometry, \url{https://arxiv.org/pdf/1809.08583.pdf}.
+\item Datar, Ved and Pingali, Vamsi Pritham, \emph{On coupled constant scalar curvature Kaehler metrics}, to appear in Journal of symplectic geometry, \url{https://arxiv.org/pdf/1901.10454v2.pdf}.
+\item Pradhan, P.
+and Sahu, B., \emph{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, Discrete Mathematics {\bf 343} (2020), , DOI 10.1016/j.disc.2020.112044, \url{https://doi.org/10.1016/j.disc.2020.112044}.
+\item Arun Maiti, \emph{Quasi-vertex-transitive maps on the plane}, Discrete Mathematics {\bf 343} (2020), 111911-111917, \url{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}.
+\item Datt, Gopal and Kumar, Sanjay, \emph{A criterion for quasinormality in $\mathbb{C}^n$},  Proc.
+Indian Acad.
+Sci.
+Math.
+Sci.
+{\bf 129} (2019), Paper No.
+11, 13 pp., DOI https://doi.org/10.1007/s12044-018-0449-5     (This article was published before the review period i.e., April 1, 2019, BUT this is not yet included on the page  https://siddhartha-gadgil.github.io/DeptWeb/pubs.html), \url{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}.
+\item Hatui, Sumana, \emph{Schur multipliers of special p-groups of rank 2}, Journal of Group Theory {\bf 23} (2020), 85-95, DOI https://doi.org/10.1515/jgth-2019-0045, \url{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}.
+\item Choudhury, Projesh Nath and Tsatsomeros Michael J., \emph{Algorithmic Detection and Construction of N-matrices}, Linear Algebra and Its Applications {\bf 602} (2020), 46-56, DOI 10.1016/j.laa.2020.04.028, \url{https://doi.org/10.1016/j.laa.2020.04.028}.
+\item Choudhury, Projesh Nath and Sivakumar, K.C., \emph{Matrices with Positive Semidefinite Real Part}, to appear in Linear and Multilinear Algebra, DOI 10.1080/03081087.2019.1602588, \url{https://doi.org/10.1080/03081087.2019.1602588}.
+\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala , \emph{On Baker's explicit abc-conjecture},  Publ. Math. Debrecen {\bf 94} (2019), 435–453.
+\item Carstensen, C.
+and Mallik, G.
+and Nataraj, N., \emph{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, IMA Journal of Numerical Analysis {\bf } (2020), , DOI https://doi.org/10.1093/imanum/drz071, \url{https://doi.org/10.1093/imanum/drz071}.
+\item Mal, Arpita and Sain, Debmalya and Paul, Kallol, \emph{On some geometric properties of operator spaces}, Banach J.
+Math.
+Anal.
+{\bf 13} (2019), 174-191, \url{https://projecteuclid.org/euclid.bjma/1543914019}.
 \end{enumerate}
@@
 \begin{enumerate}
-\item Kriti Goel, Dilip Patil and Jugal Verma, Nullstellens\"atze and Applications {\em } ().
-\item Dilip P Patil and Jugal Verma, Rational points and generalized trace forms on a finite algebra over a real closed field {\em } ().
+
 \end{enumerate}
@@
 \begin{enumerate}
-\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva and Putinar, Mihai, A panorama of positivity: I. Dimension free in {\em Birkhauser, Trends in Mathematics}{f } (2019), 117-165.
-\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva and Putinar, Mihai, A panorama of positivity: II.
-Fixed dimension in {\em American Mathematical Society, Contemporary Mathematics}{f } (), .
-\item Subhojoy Gupta and Harish Seshadri , Complex geometry of Teichmüller domains in {\em EMS, Handbook of Teichmüller theory}{f 7} (), .
-\item Subhojoy Gupta, Holomorphic quadratic differentials in Teichmüller theory in {\em EMS, Handbook of Teichmüller Theory}{f 7} (), .
+
 \end{enumerate}
@@
 \begin{enumerate}
-\item Apoorva Khare, Smooth entrywise positivity preservers, a Horn–Loewner master theorem, and Schur polynomial identities, preprint.
-\item Apoorva Khare, The non-compact normed space of norms on a finite-dimensional Banach space, preprint.
-\item Projesh Nath Choudhury and Apoorva Khare, Distance matrices of a tree: two more invariants, and in a unified framework, preprint.
-\item Arvind Ayyer, Matthieu Josuat-Vergès, Sanjay Ramassamy, Extensions of partial cyclic orders and consecutive coordinate polytopes , preprint.
-\item Arvind Ayyer, Pooja Singla, Random motion on finite rings, II: Noncommutative rings , preprint.
-\item Arvind Ayyer, Amritanshu Prasad, Steven Spallone, Macdonald trees and determinants of representations for finite Coxeter groups , preprint.
-\item Dilip P. Patil, On the connectedness of the fiber product of two connected finte free affine schemes. , preprint.
-\item Gautam Bharali and Anwoy Maitra, A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, submitted for publication.
-\item Arvind Ayyer and Pooja Singla, Random motion on finite rings, II: Noncommutative rings, preprint.
-\item M. Hassain and Pooja Singla, Representation Growth of Special Compact Linear Groups of Order Two, preprint.
-\item Shiv Prakash Patel and Pooja Singla, A multiplicity one theorem for groups of type $A_n$ over discrete valuation rings, preprint.
-\item Shifra Reif, R. Venkatesh, On tensor products of irreducible integrable representations, preprint.
-\item Deniz Kus, R. Venkatesh, Borel-de Siebenthal theory for affine reflection systems, preprint.
-\item Louigi Addario-Berry, Sanchayan Sen, Geometry of the minimal spanning tree of a random 3-regular graph, preprint.
-\item Sourav Hait, Sayan Bagchi, Luz Roncal and Sundaram Thangavelu, On the lacunary spherical maximal function on the Heisenberg group, preprint.
-\item TIRTHANKAR BHATTACHARYYA, SUBRATA SHYAM ROY, AND TAPESH YADAV, THE AGLER-YOUNG CLASS, submitted for publication.
-\item Tirthankar Bhattacharyya, B. Krishna Das, Haripada Sau, Toeplitz operators and pseudo-extensions, submitted for publication.
-\item Tirthankar Bhattacharyya, Anindya Biswas, Vikramjeet Singh Chandel, On the Nevanlinna problem - Characterization of all Schur-Agler class solutions affiliated with a given kernel, submitted for publication.
-\item Tirthankar Bhattacharyya, B. Krishna Das, Haripada Sau, Toeplitz operators on the symmetrized bidisc, submitted for publication.
-\item Vamsi Pritham Pingali, A vector bundle version of the Monge-Ampere equation, preprint.
-\item Ved V. Datar and Vamsi Pritham Pingali, On coupled constant scalar curvature Kaehler metrics, preprint.
-\item Ved Datar, Adam Jacob, Yuguang Zhang, Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces, preprint.
-\item Ved V. Datar, Vamsi Pritham Pingali, On coupled constant scalar curvature K\"ahler metrics, preprint.
+\item Khare, Apoorva, \emph{Sharp nonzero lower bounds for the Schur product theorem}, submitted for publication, \url{https://arxiv.org/abs/1910.03537}.
+\item Lübeck, Frank and Prasad, Dipendra and Ayyer, Arvind, \emph{A character relationship between symmetric group and hyperoctahedral group }, preprint, \url{https://arxiv.org/abs/1912.08576}.
+\item Ayyer, Arvind and Sinha, Shubham , \emph{The size of t-cores and hook lengths of random cells in random partitions }, preprint, \url{https://arxiv.org/abs/1911.03135}.
+\item Ayyer, Arvind, \emph{ A simple symmetric exclusion process driven by an asymmetric tracer particle }, preprint, \url{https://arxiv.org/abs/2001.02425}.
+\item David Burns, Mahesh Kakde, \emph{On Weil-Etale Cohomology and Artin L-series}, preprint, \url{https://nms.kcl.ac.uk/david.burns/web_page/bk.pdf}.
+\item Gupta, Purvi and Wawrzyniak, Chloe Urbanski, \emph{STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$}, submitted for publication, \url{https://arxiv.org/pdf/2002.08699.pdf}.
+\item Radhika Ganapathy, \emph{A Hecke algebra isomorphism over close local fields}, preprint.
+\item Miermont, Grégory and Sen, Sanchayan , \emph{On breadth-first constructions of scaling limits of random graphs and random unicellular maps}, submitted for publication, \url{https://arxiv.org/abs/1908.04403}.
+\item Gupta, Subhojoy and Mj, Mahan, \emph{Meromorphic projective structures, grafting and the monodromy map}, preprint, \url{http://arxiv.org/abs/1904.03804}.
+\item Gupta, Subhojoy, \emph{Monodromy groups of CP^1-structures on punctured surfaces}, preprint, \url{https://arxiv.org/abs/1909.10771}.
+\item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter, \emph{Surface group representations in SL(2,C) with finite mapping class orbits}, preprint, \url{https://arxiv.org/abs/1707.00071}.
+\item Ganguly, Pritam and Thangavelu,Sundaram, \emph{On lacunary spherical maximal function on Heisenberg groups}, preprint.
+\item Bhattacharyya, Tirthankar and Kumar, Poornendu and Sau, Haripada, \emph{Distinguished Varieties Through the Berger--Coburn--Lebow Theorem}, submitted for publication, \url{https://arxiv.org/pdf/2001.01410.pdf}.
+\item Bhattacharyya, T. and  Biswas, A. and Maitra, A., \emph{An unbounded realization of the symmetrized bidisc}, submitted for publication, \url{https://arxiv.org/pdf/2005.00289.pdf }.
+\item Pingali, Vamsi Pritham, \emph{The deformed Hermitian Yang-Mills equation on three-folds}, preprint, \url{https://arxiv.org/abs/1910.01870}.
+\item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian , \emph{Gravitating vortices with positive curvature}, preprint, \url{https://arxiv.org/abs/1911.09616}.
+\item Quddus, Safdar, \emph{Equivariant Cartan Homotopy Formula for $DG$-algebra.}, preprint, \url{https://arxiv.org/abs/2002.02192}.
+\item Arun Maiti, \emph{OPTIMAL INDEX GROWTH OF CLOSED GEODESICS}, submitted for publication.
+\item  Poria, Anirudha, \emph{Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms}, submitted for publication, \url{https://arxiv.org/abs/2004.04184}.
+\item Poria, Anirudha, \emph{Uncertainty principles for the Opdam-Cherednik transform on modulation spaces}, submitted for publication, \url{https://arxiv.org/abs/2005.14274}.
+\item Bera, Sudip, \emph{ENUMERATION OF WEIGHTED PATHS ON A DIGRAPH AND BLOCK HOOK DETERMINANT}, submitted for publication.
+\item Behera, Kiran Kumar, \emph{Self-inversive polynomials from rational transformation of linear functionals}, submitted for publication, \url{https://arxiv.org/abs/1909.12548}.
+\item Hatui, Sumana and Singla Pooja, \emph{On Schur multiplier and Projective representations of Heisenberg groups}, submitted for publication, \url{https://arxiv.org/abs/1909.06589}.
+\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan, \emph{Multiplicities, invariant subspaces and an additive formula.}, preprint, \url{https://arxiv.org/abs/1812.05435}.
+\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita, \emph{$K$-homogeneous tuple of operators on bounded symmetric domains}, preprint.
 \end{enumerate}
@@
 \begin{enumerate}
-\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, Generalization of unfolding operator for highly oscillating
-smooth boundary domains and homogenization {\em Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30.
-\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish, A gap theorem for positive {E}instein metrics on the
-four-sphere {\em Math. Ann.} {\bf 373} (2019), 1329--1339.
-\item Amritkar, R. E. and Rangarajan, G., Spatially synchronous extinction of species under external forcing {\em Physical Review Letters} {\bf 96} (2006), 258102.
-\item Anamby, Pramath and Das, Soumya, Distinguishing {H}ermitian cusp forms of degree 2 by a certain
-subset of all {F}ourier coefficients {\em Publ. Mat.} {\bf 63} (2019), 307--341.
-\item Anamby, Pramath and Das, Soumya, Bounds for the {P}etersson norms of the pullbacks of
-{S}aito-{K}urokawa lifts {\em J. Number Theory} {\bf 191} (2018), 289--304.
-\item Arunkumar, G. and Kus, Deniz and Venkatesh, R., Root multiplicities for {B}orcherds algebras and graph
-coloring {\em J. Algebra} {\bf 499} (2018), 538--569.
-\item Ayyer, A. and Finn, C. and Roy, D., Matrix product solution of a left-permeable two-species asymmetric exclusion process {\em Physical Review E} {\bf 97} (2018), 5225.
-\item Ayyer, Arvind and Behrend, Roger E., Factorization theorems for classical group characters, with
+\item Aas, Erik and Ayyer, Arvind and Linusson, Svante and Potka,
+Samu, {\em The exact phase diagram for a semipermeable {TASEP} with
+nonlocal boundary jumps}, J. Phys. A} {\bf 52} (2019), 355001, 19, DOI 10.1088/1751-8121/ab2e96, \url{https://doi.org/10.1088/1751-8121/ab2e96}.
+\item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
+Nandakumaran, A. K., {\em Control problem on a rough circular domain and homogenization}, Asymptot. Anal.} {\bf 115} (2019), 19--46, DOI 10.3233/asy-191526, \url{https://doi.org/10.3233/asy-191526}.
+\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Locally periodic unfolding operator for highly oscillating
+rough domains}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954, DOI 10.1007/s10231-019-00848-7, \url{https://doi.org/10.1007/s10231-019-00848-7}.
+\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Generalization of unfolding operator for highly oscillating
+smooth boundary domains and homogenization}, Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30, DOI 10.1007/s00526-018-1354-6, \url{https://doi.org/10.1007/s00526-018-1354-6}.
+\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu, {\em Asymptotic analysis of a boundary optimal control problem on a
+general branched structure}, Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434, DOI 10.1002/mma.5748, \url{https://doi.org/10.1002/mma.5748}.
+\item Aiyappan, S. and Sardar, Bidhan Chandra, {\em Biharmonic equation in a highly oscillating domain and
+homogenization of an associated control problem}, Appl. Anal.} {\bf 98} (2019), 2783--2801, DOI 10.1080/00036811.2018.1471207, \url{https://doi.org/10.1080/00036811.2018.1471207}.
+\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish, {\em A gap theorem for positive {E}instein metrics on the
+four-sphere}, Math. Ann.} {\bf 373} (2019), 1329--1339, DOI 10.1007/s00208-018-1749-x, \url{https://doi.org/10.1007/s00208-018-1749-x}.
+\item Anamby, Pramath and Das, Soumya, {\em Distinguishing {H}ermitian cusp forms of degree 2 by a certain
+subset of all {F}ourier coefficients}, Publ. Mat.} {\bf 63} (2019), 307--341, DOI 10.5565/PUBLMAT6311911, \url{https://doi.org/10.5565/PUBLMAT6311911}.
+\item Anamby, Pramath and Das, Soumya, {\em Bounds for the {P}etersson norms of the pullbacks of
+{S}aito-{K}urokawa lifts}, J. Number Theory} {\bf 191} (2018), 289--304, DOI 10.1016/j.jnt.2018.03.011, \url{https://doi.org/10.1016/j.jnt.2018.03.011}.
+\item Arunkumar, G. and Kus, Deniz and Venkatesh, R., {\em Root multiplicities for {B}orcherds algebras and graph
+coloring}, J. Algebra} {\bf 499} (2018), 538--569, DOI 10.1016/j.jalgebra.2017.11.050, \url{https://doi.org/10.1016/j.jalgebra.2017.11.050}.
+\item Ayyer, Arvind and Behrend, Roger E., {\em Factorization theorems for classical group characters, with
 applications to alternating sign matrices and plane
-partitions {\em J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.
+partitions}, J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105, DOI 10.1016/j.jcta.2019.01.001, \url{https://doi.org/10.1016/j.jcta.2019.01.001}.
 \item Ayyer, Arvind and Bouttier, J\'{e}r\'{e}mie and Corteel, Sylvie and
-Linusson, Svante and Nunzi, Fran\c{c}ois, Bumping sequences and multispecies juggling {\em Adv. in Appl. Math.} {\bf 98} (2018), 100--126.
-\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, Matrix product solution of a left-permeable two-species
-asymmetric exclusion process {\em Phys. Rev. E} {\bf 97} (2018), 012151, 10.
-\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, The phase diagram for a multispecies left-permeable asymmetric
-exclusion process {\em J. Stat. Phys.} {\bf 174} (2019), 605--621.
-\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, Odd partitions in {Y}oung's lattice {\em S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
-\item Ayyer, Arvind and Ramassamy, Sanjay, The {H}ilbert-{G}alton board {\em ALEA Lat. Am. J. Probab. Math. Stat.} {\bf 15} (2018), 755--774.
-\item B\"{o}cherer, Siegfried and Das, Soumya, Cuspidality and the growth of {F}ourier coefficients of
-modular forms {\em J. Reine Angew. Math.} {\bf 741} (2018), 161--178.
-\item B\"{o}cherer, Siegfried and Das, Soumya, Petersson norms of not necessarily cuspidal {J}acobi modular
-forms and applications {\em Adv. Math.} {\bf 336} (2018), 335--376.
-\item Bagchi, Sayan and Thangavelu, Sundaram, Weighted norm inequalities for {W}eyl multipliers and fourier
-multipliers on the {H}eisenberg group {\em J. Anal. Math.} {\bf 136} (2018), 1--29.
-\item Baklouti, Ali and Thangavelu, Sundaram, Hardy and {M}iyachi theorems for {H}eisenberg motion groups {\em Nagoya Math. J.} {\bf 229} (2018), 1--20.
-\item Balhara, Rakesh, Hardy's inequality for the fractional powers of the {G}rushin
-operator {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25.
-\item Balodi, Mamta and Palcoux, Sebastien, On {B}oolean intervals of finite groups {\em J. Combin. Theory Ser. A} {\bf 157} (2018), 49--69.
-\item Banerjee, Abhishek, On {A}uslander's formula and cohereditary torsion pairs {\em Commun. Contemp. Math.} {\bf 20} (2018), 1750071, 27.
-\item Banerjee, Abhishek, Modular {H}ecke algebras over {M}\"{o}bius categories {\em J. Geom. Phys.} {\bf 131} (2018), 23--40.
-\item Banerjee, Abhishek, A topological {N}ullstellensatz for tensor-triangulated
-categories {\em C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375.
-\item Banerjee, Abhishek, Quasimodular {H}ecke algebras and {H}opf actions {\em J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080.
-\item Banerjee, Abhishek, Completions of monoid objects and descent results {\em J. Algebra} {\bf 507} (2018), 362--399.
-\item Basu, Arnab and Ghosh, Mrinal K., Nonzero-sum risk-sensitive stochastic games on a countable
-state space {\em Math. Oper. Res.} {\bf 43} (2018), 516--532.
+Linusson, Svante and Nunzi, Fran\c{c}ois, {\em Bumping sequences and multispecies juggling}, Adv.
+in Appl.
+Math.} {\bf 98} (2018), 100--126, DOI 10.1016/j.aam.2018.03.001, \url{https://doi.org/10.1016/j.aam.2018.03.001}.
+\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, {\em Matrix product solution of a left-permeable two-species
+asymmetric exclusion process}, Phys. Rev. E} {\bf 97} (2018), 012151, 10, DOI 10.1103/physreve.97.012151, \url{https://doi.org/10.1103/physreve.97.012151}.
+\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, {\em The phase diagram for a multispecies left-permeable asymmetric
+exclusion process}, J. Stat. Phys.} {\bf 174} (2019), 605--621, DOI 10.1007/s10955-018-2183-x, \url{https://doi.org/10.1007/s10955-018-2183-x}.
+\item Ayyer, Arvind and Linusson, Svante, {\em Reverse juggling processes}, Random Structures Algorithms} {\bf 55} (2019), 56--72, DOI 10.1002/rsa.20825, \url{https://doi.org/10.1002/rsa.20825}.
+\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, {\em Odd partitions in {Y}oung's lattice}, S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
+\item Ayyer, Arvind and Ramassamy, Sanjay, {\em The {H}ilbert-{G}alton board}, ALEA Lat.
+Am.
+J.
+Probab.
+Math.
+Stat.} {\bf 15} (2018), 755--774, DOI 10.30757/alea.v15-28, \url{https://doi.org/10.30757/alea.v15-28}.
+\item B\"{o}cherer, Siegfried and Das, Soumya, {\em Cuspidality and the growth of {F}ourier coefficients of
+modular forms}, J. Reine Angew. Math.} {\bf 741} (2018), 161--178, DOI 10.1515/crelle-2015-0075, \url{https://doi.org/10.1515/crelle-2015-0075}.
+\item B\"{o}cherer, Siegfried and Das, Soumya, {\em Petersson norms of not necessarily cuspidal {J}acobi modular
+forms and applications}, Adv. Math.} {\bf 336} (2018), 335--376, DOI 10.1016/j.aim.2018.07.033, \url{https://doi.org/10.1016/j.aim.2018.07.033}.
+\item Bagchi, Sayan and Thangavelu, Sundaram, {\em Weighted norm inequalities for {W}eyl multipliers and fourier
+multipliers on the {H}eisenberg group}, J. Anal. Math.} {\bf 136} (2018), 1--29, DOI 10.1007/s11854-018-0053-8, \url{https://doi.org/10.1007/s11854-018-0053-8}.
+\item Baklouti, Ali and Thangavelu, Sundaram, {\em Hardy and {M}iyachi theorems for {H}eisenberg motion groups}, Nagoya Math.
+J.} {\bf 229} (2018), 1--20, DOI 10.1017/nmj.2016.58, \url{https://doi.org/10.1017/nmj.2016.58}.
+\item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
+Verma, Kaushal, {\em Remarks on the higher dimensional {S}uita conjecture}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411, DOI 10.1090/proc/14421, \url{https://doi.org/10.1090/proc/14421}.
+\item Balhara, Rakesh, {\em Hardy's inequality for the fractional powers of the {G}rushin
+operator}, Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25, DOI 10.1007/s12044-019-0471-2, \url{https://doi.org/10.1007/s12044-019-0471-2}.
+\item Balodi, Mamta and Palcoux, Sebastien, {\em On {B}oolean intervals of finite groups}, J.
+Combin.
+Theory Ser.
+A} {\bf 157} (2018), 49--69, DOI 10.1016/j.jcta.2018.02.004, \url{https://doi.org/10.1016/j.jcta.2018.02.004}.
+\item Banerjee, Abhishek, {\em On {A}uslander's formula and cohereditary torsion pairs}, Commun.
+Contemp.
+Math.} {\bf 20} (2018), 1750071, 27, DOI 10.1142/S0219199717500717, \url{https://doi.org/10.1142/S0219199717500717}.
+\item Banerjee, Abhishek, {\em Modular {H}ecke algebras over {M}\"{o}bius categories}, J.
+Geom.
+Phys.} {\bf 131} (2018), 23--40, DOI 10.1016/j.geomphys.2018.04.008, \url{https://doi.org/10.1016/j.geomphys.2018.04.008}.
+\item Banerjee, Abhishek, {\em On differential torsion theories and rings with several
+objects}, Canad. Math. Bull.} {\bf 62} (2019), 703--714, DOI 10.4153/s0008439518000656, \url{https://doi.org/10.4153/s0008439518000656}.
+\item Banerjee, Abhishek, {\em A topological {N}ullstellensatz for tensor-triangulated
+categories}, C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375, DOI 10.1016/j.crma.2018.02.012, \url{https://doi.org/10.1016/j.crma.2018.02.012}.
+\item Banerjee, Abhishek, {\em Quasimodular {H}ecke algebras and {H}opf actions}, J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080, DOI 10.4171/JNCG/297, \url{https://doi.org/10.4171/JNCG/297}.
+\item Banerjee, Abhishek, {\em Completions of monoid objects and descent results}, J.
+Algebra} {\bf 507} (2018), 362--399, DOI 10.1016/j.jalgebra.2018.04.022, \url{https://doi.org/10.1016/j.jalgebra.2018.04.022}.
+\item Banerjee, Abhishek and Kour, Surjeet, {\em {$(A,\delta)$}-modules, {H}ochschild homology and higher
+derivations}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802, DOI 10.1007/s10231-019-00844-x, \url{https://doi.org/10.1007/s10231-019-00844-x}.
+\item Basu, Arnab and Ghosh, Mrinal K., {\em Nonzero-sum risk-sensitive stochastic games on a countable
+state space}, Math. Oper. Res.} {\bf 43} (2018), 516--532, DOI 10.1287/moor.2017.0870, \url{https://doi.org/10.1287/moor.2017.0870}.
 \item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
-and Putinar, Mihai, Simultaneous kernels of matrix {H}adamard powers {\em Linear Algebra Appl.} {\bf 576} (2019), 142--157.
+and Putinar, Mihai, {\em Simultaneous kernels of matrix {H}adamard powers}, Linear Algebra Appl.} {\bf 576} (2019), 142--157, DOI 10.1016/j.laa.2018.03.035, \url{https://doi.org/10.1016/j.laa.2018.03.035}.
 \item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
 Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
-Morales, Alejandro H. and Yip, Martha, The volume of the caracol polytope {\em S\'{e}m. Lothar. Combin.} {\bf 80B} (2018), Art. 87, 12.
-\item Bera, Sayani and Verma, Kaushal, Some aspects of shift-like automorphisms of {$\Bbb C^k$} {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 128} (2018), Art. 10, 48.
+Morales, Alejandro H. and Yip, Martha, {\em The volume of the caracol polytope}, S\'{e}m. Lothar. Combin.} {\bf 80B} (2018), Art. 87, 12.
+\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
+Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
+Morales, Alejandro H.
+and Yip, Martha, {\em A combinatorial model for computing volumes of flow polytopes}, Trans.
+Amer.
+Math.
+Soc.} {\bf 372} (2019), 3369--3404, DOI 10.1090/tran/7743, \url{https://doi.org/10.1090/tran/7743}.
+\item Bera, Sayani and Verma, Kaushal, {\em Some aspects of shift-like automorphisms of {$\Bbb C^k$}}, Proc.
+Indian Acad.
+Sci.
+Math.
+Sci.} {\bf 128} (2018), Art.
+10, 48, DOI 10.1007/s12044-018-0388-1, \url{https://doi.org/10.1007/s12044-018-0388-1}.
 \item Bharali, Gautam and Biswas, Indranil and Divakaran, Divakaran
-and Janardhanan, Jaikrishnan, Proper holomorphic mappings onto symmetric products of a
-{R}iemann surface {\em Doc. Math.} {\bf 23} (2018), 1291--1311.
-\item Bhattacharyya, Tirthankar and Sau, Haripada, Holomorphic functions on the symmetrized bidisk---realization,
-interpolation and extension {\em J. Funct. Anal.} {\bf 274} (2018), 504--524.
+and Janardhanan, Jaikrishnan, {\em Proper holomorphic mappings onto symmetric products of a
+{R}iemann surface}, Doc. Math.} {\bf 23} (2018), 1291--1311.
+\item Bharali, Gautam and Chandel, Vikramjeet Singh, {\em Pick interpolation on the polydisc: small families of
+sufficient kernels}, Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093, DOI 10.1007/s11785-017-0701-5, \url{https://doi.org/10.1007/s11785-017-0701-5}.
+\item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K., {\em Survey of last ten years of work done in {I}ndia in some
+selected areas of functional analysis and operator theory}, Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617, DOI 10.1007/s13226-019-0345-4, \url{https://doi.org/10.1007/s13226-019-0345-4}.
+\item Bhattacharyya, Tirthankar and Sau, Haripada, {\em Holomorphic functions on the symmetrized bidisk---realization,
+interpolation and extension}, J. Funct. Anal.} {\bf 274} (2018), 504--524, DOI 10.1016/j.jfa.2017.09.013, \url{https://doi.org/10.1016/j.jfa.2017.09.013}.
 \item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
-Sundaram, Hermite multipliers on modulation spaces {\em Analysis and partial differential equations: perspectives from
+Sundaram, {\em Hermite multipliers on modulation spaces}, Analysis and partial differential equations: perspectives from
 developing countries} {\bf 275} (2019), 42--64.
-\item Bhosle, Usha N., Hitchin pairs on reducible curves {\em Internat. J. Math.} {\bf 29} (2018), 1850015, 49.
+\item Bhosle, Usha N., {\em Hitchin pairs on reducible curves}, Internat. J. Math.} {\bf 29} (2018), 1850015, 49, DOI 10.1142/S0129167X18500155, \url{https://doi.org/10.1142/S0129167X18500155}.
 \item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and
-Pingali, Vamsi P., Rational cuspidal curves on del-{P}ezzo surfaces {\em J. Singul.} {\bf 17} (2018), 91--107.
-\item Biswas, Indranil and Pingali, Vamsi Pritham, A characterization of finite vector bundles on {G}auduchon
-astheno-{K}\"{a}hler manifolds {\em \'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art. 6, 13.
-\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi, Edge patch-wise local projection stabilized nonconforming
-{FEM} for the {O}seen problem {\em Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214.
+Pingali, Vamsi P., {\em Rational cuspidal curves on del-{P}ezzo surfaces}, J. Singul.} {\bf 17} (2018), 91--107.
+\item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy, {\em Branched projective structures on a {R}iemann surface and
+logarithmic connections}, Doc. Math.} {\bf 24} (2019), 2299--2337.
+\item Biswas, Indranil and Pingali, Vamsi Pritham, {\em A characterization of finite vector bundles on {G}auduchon
+astheno-{K}\"{a}hler manifolds}, \'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art. 6, 13.
+\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi, {\em Edge patch-wise local projection stabilized nonconforming
+{FEM} for the {O}seen problem}, Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214, DOI 10.1515/cmam-2018-0020, \url{https://doi.org/10.1515/cmam-2018-0020}.
 \item Biswas, Shibananda and Ghosh, Gargi and Misra, Gadadhar and
-Shyam Roy, Subrata, On reducing submodules of {H}ilbert modules with
-{${S}_n$}-invariant kernels {\em J. Funct. Anal.} {\bf 276} (2019), 751--784.
-\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal, Comments on the {G}reen's function of a planar domain {\em Anal. Math. Phys.} {\bf 8} (2018), 383--414.
-\item Borkar, V. S and Jain, S and Rangarajan, G., Dynamics of individual specialization and global diversification in   communities {\em Complexity} {\bf 3} (1998), 50.
-\item Borkar, V. S. and Jain, S. and Rangarajan, G., Generalized replicator dynamics as a model of specialization and   diversity in societies {\em Advances in Complex Systems} {\bf 1} (1998), 325.
-\item Borkar, V.
-S.
-and Jain, S.
-and Rangarajan, G., Collective behaviour and diversity in economic communities: Some insights from an evolutionary game {\em The Application of Econophysics} {\bf } (2003), .
-\item Borkar, V.
-S.
-and Jain, S.
-and Rangarajan, G., Evolutionary mechanisms of organization in complex systems {\em Mathematical Models for Bioengineering and Probabilistic Systems} {\bf } (2005), 323.
+Shyam Roy, Subrata, {\em On reducing submodules of {H}ilbert modules with
+{${S}_n$}-invariant kernels}, J. Funct. Anal.} {\bf 276} (2019), 751--784, DOI 10.1016/j.jfa.2018.10.025, \url{https://doi.org/10.1016/j.jfa.2018.10.025}.
+\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram, {\em On extension problem, trace {H}ardy and {H}ardy's inequalities
+for some fractional {L}aplacians}, Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605, DOI 10.3934/cpaa.2019116, \url{https://doi.org/10.3934/cpaa.2019116}.
+\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal, {\em Comments on the {G}reen's function of a planar domain}, Anal.
+Math.
+Phys.} {\bf 8} (2018), 383--414, DOI 10.1007/s13324-017-0177-5, \url{https://doi.org/10.1007/s13324-017-0177-5}.
 \item Brenner, Susanne C. and Gudi, Thirupathi and Porwal, Kamana
-and Sung, Li-Yeng, A {M}orley finite element method for an elliptic distributed
+and Sung, Li-Yeng, {\em A {M}orley finite element method for an elliptic distributed
 optimal control problem with pointwise state and control
-constraints {\em ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206.
+constraints}, ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206, DOI 10.1051/cocv/2017031, \url{https://doi.org/10.1051/cocv/2017031}.
 \item Burton, Benjamin A. and Datta, Basudeb and Singh, Nitin and
-Spreer, Jonathan, A construction principle for tight and minimal triangulations
-of manifolds {\em Exp. Math.} {\bf 27} (2018), 22--36.
-\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella, Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
-indefinite second-order linear elliptic problems {\em Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.
-\item Chandel, Vikramjeet Singh, The three-point {P}ick-{N}evanlinna interpolation problem on
-the polydisc {\em Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352.
-\item Chatterjee, Esha and Hassan, Sk. Sarif, On the asymptotic character of a generalized rational
-difference equation {\em Discrete Contin. Dyn. Syst.} {\bf 38} (2018), 1707--1718.
-\item Chen, Y. and Rangarajan, G. and Ding,. M., General stability analysis of synchronized dynamics in coupled systems {\em Physical Review E} {\bf 67} (2003), 26209.0.
-\item Chopra, R. and Murthy, C. R. and Rangarajan, G., Statistical tests for detecting Granger causality {\em IEEE Transactions on Signal Processing} {\bf } (2018), 5803.
+Spreer, Jonathan, {\em A construction principle for tight and minimal triangulations
+of manifolds}, Exp. Math.} {\bf 27} (2018), 22--36, DOI 10.1080/10586458.2016.1212747, \url{https://doi.org/10.1080/10586458.2016.1212747}.
+\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella, {\em Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
+indefinite second-order linear elliptic problems}, Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250, DOI 10.1515/cmam-2019-0034, \url{https://doi.org/10.1515/cmam-2019-0034}.
+\item Chandel, Vikramjeet Singh, {\em The three-point {P}ick-{N}evanlinna interpolation problem on
+the polydisc}, Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352, DOI 10.1080/17476933.2017.1370461, \url{https://doi.org/10.1080/17476933.2017.1370461}.
+\item Chatterjee, Esha and Hassan, Sk. Sarif, {\em On the asymptotic character of a generalized rational
+difference equation}, Discrete Contin. Dyn. Syst.} {\bf 38} (2018), 1707--1718, DOI 10.3934/dcds.2018070, \url{https://doi.org/10.3934/dcds.2018070}.
 \item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
-K. C., A note on linear preservers of semipositive and minimally
-semipositive matrices {\em Electron. J. Linear Algebra} {\bf 34} (2018), 687--694.
-\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram, Hardy-type inequalities for fractional powers of the
-{D}unkl-{H}ermite operator {\em Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544.
-\item Das, Soumya and Khan, Rizwanur, The third moment of symmetric square {$L$}-functions {\em Q. J. Math.} {\bf 69} (2018), 1063--1087.
-\item Das, Soumya and Kohnen, Winfried, On sign changes of eigenvalues of {S}iegel cusp forms of genus
-2 in prime powers {\em Acta Arith.} {\bf 183} (2018), 167--172.
-\item Datta, Basudeb and Maity, Dipendu, Semi-equivelar maps on the torus and the {K}lein bottle are
-{A}rchimedean {\em Discrete Math.} {\bf 341} (2018), 3296--3309.
-\item Daya Sagar B. S. and Rangarajan, G. and Veneziano, D., Fractals in Geophysics {\em Chaos, Solitons and Fractals} {\bf 19} (2004), 237.
-\item Dhamala, M. and Rangarajan, G. and Ding, M., Estimating Granger causality from Fourier and wavelet transforms of time series data {\em Physical Review Letters} {\bf 100} (2008), 18701.0.
-\item Dhamala, M. and Rangarajan, G. and Ding, M., Analyzing information flow in brain networks with nonparametric Granger causality {\em NeuroImage} {\bf 41} (2008), 354.
-\item Ding. M and Rangarajan. G, Parametric spectral analysis {\em Encyclopedia of Computational Neuroscience: Springer Reference} {\bf } (2015), .
-\item Dond, Asha K. and Gudi, Thirupathi, Patch-wise local projection stabilized finite element methods
-for convection-diffusion-reaction problems {\em Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663.
-\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH., An error analysis of discontinuous finite element methods for
-the optimal control problems governed by {S}tokes equation {\em Numer. Funct. Anal. Optim.} {\bf 40} (2019), 421--460.
+K. C., {\em A note on linear preservers of semipositive and minimally
+semipositive matrices}, Electron. J. Linear Algebra} {\bf 34} (2018), 687--694, DOI 10.13001/1081-3810.3864, \url{https://doi.org/10.13001/1081-3810.3864}.
+\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram, {\em Hardy-type inequalities for fractional powers of the
+{D}unkl-{H}ermite operator}, Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544, DOI 10.1017/s0013091517000311, \url{https://doi.org/10.1017/s0013091517000311}.
+\item Das, Soumya and Jha, Abhash Kumar, {\em Analytic properties of twisted real-analytic {H}ermitian
+{K}lingen type {E}isenstein series and applications}, Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116, DOI 10.1007/s12188-019-00206-7, \url{https://doi.org/10.1007/s12188-019-00206-7}.
+\item Das, Soumya and Khan, Rizwanur, {\em The third moment of symmetric square {$L$}-functions}, Q.
+J.
+Math.} {\bf 69} (2018), 1063--1087, DOI 10.1093/qmath/hay012, \url{https://doi.org/10.1093/qmath/hay012}.
+\item Das, Soumya and Kohnen, Winfried, {\em On sign changes of eigenvalues of {S}iegel cusp forms of genus
+2 in prime powers}, Acta Arith.} {\bf 183} (2018), 167--172, DOI 10.4064/aa170419-4-11, \url{https://doi.org/10.4064/aa170419-4-11}.
+\item Das, Soumya and Pal, Ritwik, {\em The first negative eigenvalue of {Y}oshida lifts}, Res.
+Number Theory} {\bf 5} (2019), Paper No.
+20, 9, DOI 10.1007/s40993-019-0158-x, \url{https://doi.org/10.1007/s40993-019-0158-x}.
+\item Datta, Basudeb and Maity, Dipendu, {\em Semi-equivelar maps on the torus and the {K}lein bottle are
+{A}rchimedean}, Discrete Math.} {\bf 341} (2018), 3296--3309, DOI 10.1016/j.disc.2018.08.016, \url{https://doi.org/10.1016/j.disc.2018.08.016}.
+\item Dond, Asha K. and Gudi, Thirupathi, {\em Patch-wise local projection stabilized finite element methods
+for convection-diffusion-reaction problems}, Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663, DOI 10.1002/num.22317, \url{https://doi.org/10.1002/num.22317}.
+\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH., {\em An error analysis of discontinuous finite element methods for
+the optimal control problems governed by {S}tokes equation}, Numer.
+Funct.
+Anal.
+Optim.} {\bf 40} (2019), 421--460, DOI 10.1080/01630563.2018.1538158, \url{https://doi.org/10.1080/01630563.2018.1538158}.
 \item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P.
-and Silberman, Lior and Tao, Terence, Homogeneous length functions on groups {\em Algebra Number Theory} {\bf 12} (2018), 1773--1786.
-\item Gaddam, Sharat and Gudi, Thirupathi, Inhomogeneous {D}irichlet boundary condition in the {\it a
-posteriori} error control of the obstacle problem {\em Comput. Math. Appl.} {\bf 75} (2018), 2311--2327.
-\item Gaddam, Sharat and Gudi, Thirupathi, Bubbles enriched quadratic finite element method for the
-3{D}-elliptic obstacle problem {\em Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236.
-\item Gade, P. and Rangarajan, G., Frustration induced oscillator death on networks {\em Chaos} {\bf 23} (2013), 13892.
-\item Ganapathy, R. and Rangarajan, G. and Sood A. K., Granger causality and cross recurrence plots in rheochaos {\em Physical Review E} {\bf 75} (2007), 7305.
-\item Gaussier, Herv\'{e} and Seshadri, Harish, Holomorphic motions and complex geometry {\em Proc. Amer. Math. Soc.} {\bf 147} (2019), 301--313.
-\item Gaussier, Herv\'{e} and Seshadri, Harish, On the {G}romov hyperbolicity of convex domains in {$\Bbb
-C^n$} {\em Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641.
-\item Ghara, Soumitra and Kumar, Surjit, On the sum of two subnormal kernels {\em J. Math. Anal. Appl.} {\bf 469} (2019), 1015--1027.
-\item Ghosh, A.
-and Paria, D.
-and Rangarajan, G.
-and Ghosh, A., Velocity fluctuations in helical propulsion: How small can a propeller be {\em Journal of Physical Chemistry Letters} {\bf 5} (2014), 62.
-\item Ghosh, Mrinal K. and Pradhan, Somnath, Risk-sensitive stochastic differential games with reflecting
-diffusions {\em Stoch. Anal. Appl.} {\bf 36} (2018), 1--27.
-\item Ghosh, S. and Rangarajan, G. and Sinha, S., Stability of synchronization in a multi-cellular system {\em European Physics Letters} {\bf 92} (2010), 40012.
-\item Gudi, Thirupathi and Majumder, Papri, Convergence analysis of finite element method for a parabolic
-obstacle problem {\em J. Comput. Appl. Math.} {\bf 357} (2019), 85--102.
-\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh, Von {N}eumann's inequality for commuting operator-valued
-multishifts {\em Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.
-\item Gupta, Rajeev and Ramiz Reza, Md., Operator space structures on {$\ell^1(n)$} {\em Houston J. Math.} {\bf 44} (2018), 1205--1212.
-\item Gupta, S. C., The classical {S}tefan problem {\em } {\bf } (2018), xxiii+726.
-\item Hazra, Somnath, Homogeneous 2-shifts {\em Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.
-\item Iyer, Srikanth K., The random connection model: connectivity, edge lengths, and
-degree distributions {\em Random Structures Algorithms} {\bf 52} (2018), 283--300.
-\item Jha, Abhash Kumar and Sahu, Brundaban, Rankin-{C}ohen brackets on {J}acobi forms of several variables
-and special values of certain {D}irichlet series {\em Int. J. Number Theory} {\bf 15} (2019), 925--933.
-\item Joshi, A.
-U.
-and Sant, D.
-A.
-and Parvez, I.
-A.
-and Rangarajan, G.
-and Limaye, M.
-A.
-and Mukherjee, S.
-and Charola, M.
-J.
-and Bhatt, M.
-N.
-and Mistry, S.
-P., Sub-surface profiling of granite pluton using microtremor method: southern Aravalli, Gujarat, India {\em International Journal of Earth Sciences} {\bf 106} (2017), 0.
+and Silberman, Lior and Tao, Terence, {\em Homogeneous length functions on groups}, Algebra Number Theory} {\bf 12} (2018), 1773--1786, DOI 10.2140/ant.2018.12.1773, \url{https://doi.org/10.2140/ant.2018.12.1773}.
+\item Gaddam, Sharat and Gudi, Thirupathi, {\em Inhomogeneous {D}irichlet boundary condition in the {\it a
+posteriori} error control of the obstacle problem}, Comput. Math. Appl.} {\bf 75} (2018), 2311--2327, DOI 10.1016/j.camwa.2017.12.010, \url{https://doi.org/10.1016/j.camwa.2017.12.010}.
+\item Gaddam, Sharat and Gudi, Thirupathi, {\em Bubbles enriched quadratic finite element method for the
+3{D}-elliptic obstacle problem}, Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236, DOI 10.1515/cmam-2017-0018, \url{https://doi.org/10.1515/cmam-2017-0018}.
+\item Garani, Shayan Srinivasa and Seshadri, Harish, {\em An algorithmic approach to {S}outh {I}ndian classical music}, J.
+Math.
+Music} {\bf 13} (2019), 107--134, DOI 10.1080/17459737.2019.1604845, \url{https://doi.org/10.1080/17459737.2019.1604845}.
+\item Gaussier, Herv\'{e} and Seshadri, Harish, {\em Holomorphic motions and complex geometry}, Proc.
+Amer.
+Math.
+Soc.} {\bf 147} (2019), 301--313, DOI 10.1090/proc/14217, \url{https://doi.org/10.1090/proc/14217}.
+\item Gaussier, Herv\'{e} and Seshadri, Harish, {\em On the {G}romov hyperbolicity of convex domains in {$\Bbb
+C^n$}}, Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641, DOI 10.1007/s40315-018-0243-5, \url{https://doi.org/10.1007/s40315-018-0243-5}.
+\item Ghara, Soumitra and Kumar, Surjit, {\em On the sum of two subnormal kernels}, J.
+Math.
+Anal.
+Appl.} {\bf 469} (2019), 1015--1027, DOI 10.1016/j.jmaa.2018.09.048, \url{https://doi.org/10.1016/j.jmaa.2018.09.048}.
+\item Ghosh, Mrinal K. and Pradhan, Somnath, {\em Risk-sensitive stochastic differential games with reflecting
+diffusions}, Stoch. Anal. Appl.} {\bf 36} (2018), 1--27, DOI 10.1080/07362994.2017.1356732, \url{https://doi.org/10.1080/07362994.2017.1356732}.
+\item Gudi, Thirupathi and Majumder, Papri, {\em Convergence analysis of finite element method for a parabolic
+obstacle problem}, J. Comput. Appl. Math.} {\bf 357} (2019), 85--102, DOI 10.1016/j.cam.2019.02.026, \url{https://doi.org/10.1016/j.cam.2019.02.026}.
+\item Gudi, Thirupathi and Majumder, Papri, {\em Conforming and discontinuous {G}alerkin {FEM} in space for
+solving parabolic obstacle problem}, Comput. Math. Appl.} {\bf 78} (2019), 3896--3915, DOI 10.1016/j.camwa.2019.06.022, \url{https://doi.org/10.1016/j.camwa.2019.06.022}.
+\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh, {\em Von {N}eumann's inequality for commuting operator-valued
+multishifts}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608, DOI 10.1090/proc/14410, \url{https://doi.org/10.1090/proc/14410}.
+\item Gupta, Rajeev and Ramiz Reza, Md., {\em Operator space structures on {$\ell^1(n)$}}, Houston J. Math.} {\bf 44} (2018), 1205--1212.
+\item Gupta, S. C., {\em The classical {S}tefan problem}, } {\bf } (2018), xxiii+726.
+\item Gupta, Subhojoy, {\em Limits of harmonic maps and crowned hyperbolic surfaces}, Trans.
+Amer.
+Math.
+Soc.} {\bf 372} (2019), 7573--7596, DOI 10.1090/tran/7777, \url{https://doi.org/10.1090/tran/7777}.
+\item Gupta, Subhojoy and Wolf, Michael, {\em Meromorphic quadratic differentials and measured foliations on
+a {R}iemann surface}, Math. Ann.} {\bf 373} (2019), 73--118, DOI 10.1007/s00208-018-1674-z, \url{https://doi.org/10.1007/s00208-018-1674-z}.
+\item Hazra, Somnath, {\em Homogeneous 2-shifts}, Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763, DOI 10.1007/s11785-018-0822-5, \url{https://doi.org/10.1007/s11785-018-0822-5}.
+\item Iyer, Srikanth K., {\em The random connection model: connectivity, edge lengths, and
+degree distributions}, Random Structures Algorithms} {\bf 52} (2018), 283--300, DOI 10.1002/rsa.20741, \url{https://doi.org/10.1002/rsa.20741}.
+\item Jha, Abhash Kumar and Juyal, Abhishek and Pandey, Manish
+Kumar, {\em On simultaneous non-vanishing of twisted {$L$}-functions
+associated to newforms on {$\Gamma_0(N)$}}, J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.
+\item Jha, Abhash Kumar and Sahu, Brundaban, {\em Rankin-{C}ohen brackets on {J}acobi forms of several variables
+and special values of certain {D}irichlet series}, Int. J. Number Theory} {\bf 15} (2019), 925--933, DOI 10.1142/S1793042119500490, \url{https://doi.org/10.1142/S1793042119500490}.
+\item Jha, Abhash Kumar and Sahu, Brundaban, {\em Differential operators on {J}acobi forms and special values of
+certain {D}irichlet series}, Automorphic forms and related topics} {\bf 732} (2019), 91--99, DOI 10.1090/conm/732/14793, \url{https://doi.org/10.1090/conm/732/14793}.
 \item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
-Sekar, Sruthi, Non-malleable randomness encoders and their applications {\em Advances in cryptology---{EUROCRYPT} 2018. {P}art {III}} {\bf 10822} (2018), 589--617.
+Sekar, Sruthi, {\em Non-malleable randomness encoders and their applications}, Advances in cryptology---{EUROCRYPT} 2018. {P}art {III}} {\bf 10822} (2018), 589--617.
 \item Kashyap, G.
@@
 Ravindranath and G.
-Ambika, Synapse loss and progress of Alzheimer&rsquo;s disease - A network model {\em Scientific Reports} {\bf 9} (2019), .
-\item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan, On the convolution of {M}ittag-{L}effler distributions and its
-applications to fractional point processes {\em Stoch. Anal. Appl.} {\bf 37} (2019), 115--122.
-\item Khare, Apoorva, Generalized nil-{C}oxeter algebras over discrete complex
-reflection groups {\em Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999.
-\item Khare, Apoorva, Generalized nil-Coxeter algebras {\em S&eacute;m. Lothar. Combin.} {\bf 80B,} (2018), .
-\item Khare, Apoorva and Tao, Terence., Schur polynomials, entrywise positivity preservers, and weak majorization. {\em S&eacute;m. Lothar. Combin.} {\bf 80B,} (2018), .
-\item Khare, Apoorva and Tikaradze, Akaki, A {C}arlitz--von {S}taudt type theorem for finite rings {\em Linear Algebra Appl.} {\bf 568} (2019), 106--126.
-\item Krakovski, Roi and Onn, Uri and Singla, Pooja, Regular characters of groups of type {$\ssf A_n$} over
-discrete valuation rings {\em J. Algebra} {\bf 496} (2018), 116--137.
+Ambika, {\em Synapse loss and progress of Alzheimer&rsquo;s disease - A network model}, Scientific Reports} {\bf 9} (2019), .
+\item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan, {\em On the convolution of {M}ittag-{L}effler distributions and its
+applications to fractional point processes}, Stoch. Anal. Appl.} {\bf 37} (2019), 115--122, DOI 10.1080/07362994.2018.1538803, \url{https://doi.org/10.1080/07362994.2018.1538803}.
+\item Khan, Mohammad Yasir Feroz and Biswas, Rahul and Sau, Ramesh
+Chandra, {\em Instability of {L}agrange interpolation on {$H^1(\Omega)\cap
+C(\overline\Omega)$}}, Math. Student} {\bf 88} (2019), 153--158.
+\item Khare, Apoorva, {\em Generalized nil-{C}oxeter algebras over discrete complex
+reflection groups}, Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999, DOI 10.1090/tran/7304, \url{https://doi.org/10.1090/tran/7304}.
+\item Khare, Apoorva and Tikaradze, Akaki, {\em A {C}arlitz--von {S}taudt type theorem for finite rings}, Linear Algebra Appl.} {\bf 568} (2019), 106--126, DOI 10.1016/j.laa.2018.05.035, \url{https://doi.org/10.1016/j.laa.2018.05.035}.
+\item Krakovski, Roi and Onn, Uri and Singla, Pooja, {\em Regular characters of groups of type {$\ssf A_n$} over
+discrete valuation rings}, J. Algebra} {\bf 496} (2018), 116--137, DOI 10.1016/j.jalgebra.2017.10.018, \url{https://doi.org/10.1016/j.jalgebra.2017.10.018}.
 \item Lin, X.
@@
 and Jolly, M.
-K., Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level {\em Biomolecules} {\bf 9} (2019), 77.
-\item Lin, X.
-and Roy, S.
-and Jolly, M.
-K.
-and Bocci, F.
-and Schafer, N.
-P.
-and Tsai, M.-Y.
-and Chen, Y.
-and He, Y.
-and Grishaev, A.
-and Weninger, K.
-and Orban, J.
-and Kulkarni, P.
-and Rangarajan, G.
-and Levine, H.
-and J.
-N.
-Onuchic, PAGE4 and conformational switching: Insights from molecular dynamics simulations and implications for prostate cancer {\em Journal of Molecular Biology} {\bf 430} (2018), 2422.
-\item Mahajan, Prachi and Verma, Kaushal, A comparison of two biholomorphic invariants {\em Internat. J. Math.} {\bf 30} (2019), 1950012, 16.
-\item Mahmoudabadi, G.
-and Rajagopalan, K.
-and Getzenberg, R.
-H.
-and Hannenhalli, S.
-and Rangarajan, G.
-and Kulkarni, P., Intrinsically disordered proteins and conformational noise: Implications in cancer {\em Cell Cycle} {\bf 12} (2013), 26.
-\item Maity, Dipendu, Pentagonal maps on the torus and the plane {\em Beitr. Algebra Geom.} {\bf 60} (2019), 17--37.
-\item Maity, Dipendu and Upadhyay, Ashish Kumar, On centrally symmetric manifolds {\em J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.
-\item Mal, Arpita and Sain, Debmalya and Paul, Kallol, On some geometric properties of operator spaces {\em Banach J. Math. Anal.} {\bf 13} (2019), 174--191.
-\item Manfio, F. and Turgay, N. C. and Upadhyay, A., Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
-{$\Bbb{H}^n\times\Bbb{R}$} {\em J. Geom. Anal.} {\bf 29} (2019), 283--298.
+K., {\em Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level}, Biomolecules} {\bf 9} (2019), 77.
+\item Mahajan, Prachi and Verma, Kaushal, {\em A comparison of two biholomorphic invariants}, Internat.
+J.
+Math.} {\bf 30} (2019), 1950012, 16, DOI 10.1142/S0129167X19500125, \url{https://doi.org/10.1142/S0129167X19500125}.
+\item Maity, Dipendu, {\em Pentagonal maps on the torus and the plane}, Beitr. Algebra Geom.} {\bf 60} (2019), 17--37, DOI 10.1007/s13366-018-0405-7, \url{https://doi.org/10.1007/s13366-018-0405-7}.
+\item Maity, Dipendu and Upadhyay, Ashish Kumar, {\em On centrally symmetric manifolds}, J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.
+\item Mal, Arpita and Paul, Kallol and Rao, T. S. S. R. K. and Sain,
+Debmalya, {\em Approximate {B}irkhoff-{J}ames orthogonality and smoothness in
+the space of bounded linear operators}, Monatsh. Math.} {\bf 190} (2019), 549--558, DOI 10.1007/s00605-019-01289-3, \url{https://doi.org/10.1007/s00605-019-01289-3}.
+\item Mal, Arpita and Sain, Debmalya and Paul, Kallol, {\em On some geometric properties of operator spaces}, Banach J.
+Math.
+Anal.} {\bf 13} (2019), 174--191, DOI 10.1215/17358787-2018-0021, \url{https://doi.org/10.1215/17358787-2018-0021}.
+\item Manfio, F. and Turgay, N. C. and Upadhyay, A., {\em Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
+{$\Bbb{H}^n\times\Bbb{R}$}}, J. Geom. Anal.} {\bf 29} (2019), 283--298, DOI 10.1007/s12220-018-9990-9, \url{https://doi.org/10.1007/s12220-018-9990-9}.
 \item Manikandan, K. and Vishnu Priya, N. and Senthilvelan, M. and
-Sankaranarayanan, R., Deformation of dark solitons in a {$\Cal{PT}$}-invariant
+Sankaranarayanan, R., {\em Deformation of dark solitons in a {$\Cal{PT}$}-invariant
 variable coefficients nonlocal nonlinear {S}chr\"{o}dinger
-equation {\em Chaos} {\bf 28} (2018), 083103, 12.
-\item Misra, Gadadhar and Pal, Avijit, Curvature inequalities for operators in the {C}owen-{D}ouglas
-class and localization of the {W}allach set {\em J. Anal. Math.} {\bf 136} (2018), 31--54.
-\item Mooney, S.
-M.
-and Rajagopalan, K.
-and Rangarajan, G.
-and Kulkarni, P., Cancer/testis antigens and obligate participation in multiple hallmarks of cancer: an update {\em Asian Journal of Andrology} {\bf 18} (2016), 711.
-\item Mukherjee, Sajal Kumar and Bera, Sudip, Combinatorial proofs of the {N}ewton-{G}irard and
-{C}hapman-{C}ostas-{S}antos identities {\em Discrete Math.} {\bf 342} (2019), 1577--1580.
-\item Nalatore, H. and Ding, M. and Rangarajan, G., Mitigating the effects of measurement noise on Granger causality {\em Physical Review E} {\bf 75} (2007), 12883.
-\item Nalatore, H. and Ding, M. and Rangarajan, G., Denoising neural data with state-space smoothing: Method and application {\em Journal of Neuroscience Methods} {\bf 179} (2009), 131.
-\item Nalatore, H. and Rangarajan, G., Short-window spectral analysis using AMVAR and multitaper methods: A comparison {\em Biological Cybernetics} {\bf 101} (2009), 71.
-\item Nalatore. H. and Sasikumar, N. and Rangarajan, G., Effect of measurement noise on Granger causality {\em Physical Review E} {\bf 90} (2014), 25687.
-\item Narayanan, E. K. and Singla, Pooja, On monomial representations of finitely generated nilpotent
-groups {\em Comm. Algebra} {\bf 46} (2018), 2319--2331.
-\item Pal, Chandan and Pradhan, Somnath, Risk sensitive control of pure jump processes on a general
-state space {\em Stochastics} {\bf 91} (2019), 155--174.
-\item Pal, Ratna and Verma, Kaushal, Ergodic properties of families of {H}\'{e}non maps {\em Ann. Polon. Math.} {\bf 121} (2018), 45--71.
-\item Palaniyandi, P.
-and Rangarajan, G., Critical lattice size limit for synchronized chaotic state in one- and  two-dimensional diffusively coupled map lattices {\em Physical Review E} {\bf 76} (2007), 11906.
-\item Palaniyandi, P. and Rangarajan, G., A mathematical model for storage and recall of images using targeted synchronization of coupled maps {\em Scientific Reports} {\bf 7} (2017), 8921.
-\item Paul, Kallol and Sain, Debmalya, Birkhoff-{J}ames orthogonality and its application in the
-study of geometry of {B}anach space {\em Advanced topics in mathematical analysis} {\bf } (2019), 245--284.
-\item Paul, Kallol and Sain, Debmalya and Mal, Arpita, Approximate {B}irkhoff-{J}ames orthogonality in the space of
-bounded linear operators {\em Linear Algebra Appl.} {\bf 537} (2018), 348--357.
+equation}, Chaos} {\bf 28} (2018), 083103, 12, DOI 10.1063/1.5039901, \url{https://doi.org/10.1063/1.5039901}.
+\item Misra, Gadadhar, {\em Operators in the {C}owen-{D}ouglas class and related topics}, Handbook of analytic operator theory} {\bf } (2019), 87--137.
+\item Misra, Gadadhar and Pal, Avijit, {\em Curvature inequalities for operators in the {C}owen-{D}ouglas
+class and localization of the {W}allach set}, J. Anal. Math.} {\bf 136} (2018), 31--54, DOI 10.1007/s11854-018-0054-7, \url{https://doi.org/10.1007/s11854-018-0054-7}.
+\item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian, {\em Contractivity and complete contractivity for finite
+dimensional {B}anach spaces}, J. Operator Theory} {\bf 82} (2019), 23--47, DOI 10.7900/jot.2018jun13.2225, \url{https://doi.org/10.7900/jot.2018jun13.2225}.
+\item Misra, Gadadhar and Reza, Md.
+Ramiz, {\em Curvature inequalities and extremal operators}, Illinois J.
+Math.} {\bf 63} (2019), 193--217, DOI 10.1215/00192082-7768711, \url{https://doi.org/10.1215/00192082-7768711}.
+\item Mukherjee, Sajal Kumar and Bera, Sudip, {\em Combinatorial proofs of the {N}ewton-{G}irard and
+{C}hapman-{C}ostas-{S}antos identities}, Discrete Math.} {\bf 342} (2019), 1577--1580, DOI 10.1016/j.disc.2019.02.013, \url{https://doi.org/10.1016/j.disc.2019.02.013}.
+\item Narayanan, E. K. and Singla, Pooja, {\em On monomial representations of finitely generated nilpotent
+groups}, Comm. Algebra} {\bf 46} (2018), 2319--2331, DOI 10.1080/00927872.2017.1378894, \url{https://doi.org/10.1080/00927872.2017.1378894}.
+\item Pal, Chandan and Pradhan, Somnath, {\em Risk sensitive control of pure jump processes on a general
+state space}, Stochastics} {\bf 91} (2019), 155--174, DOI 10.1080/17442508.2018.1521413, \url{https://doi.org/10.1080/17442508.2018.1521413}.
+\item Pal, Ratna and Verma, Kaushal, {\em Ergodic properties of families of {H}\'{e}non maps}, Ann.
+Polon.
+Math.} {\bf 121} (2018), 45--71, DOI 10.4064/ap170928-2-4, \url{https://doi.org/10.4064/ap170928-2-4}.
+\item Paul, Kallol and Sain, Debmalya, {\em Birkhoff-{J}ames orthogonality and its application in the
+study of geometry of {B}anach space}, Advanced topics in mathematical analysis} {\bf } (2019), 245--284.
+\item Paul, Kallol and Sain, Debmalya and Ghosh, Puja, {\em Symmetry of {B}irkhoff-{J}ames orthogonality of bounded linear
+operators}, Ulam type stability} {\bf } (2019), 331--344.
+\item Paul, Kallol and Sain, Debmalya and Mal, Arpita, {\em Approximate {B}irkhoff-{J}ames orthogonality in the space of
+bounded linear operators}, Linear Algebra Appl.} {\bf 537} (2018), 348--357, DOI 10.1016/j.laa.2017.10.008, \url{https://doi.org/10.1016/j.laa.2017.10.008}.
 \item Paul, Kallol and Sain, Debmalya and Mal, Arpita and Mandal,
-Kalidas, Orthogonality of bounded linear operators on complex {B}anach
-spaces {\em Adv. Oper. Theory} {\bf 3} (2018), 699--709.
-\item Pingali, Vamsi P., A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE} {\em Complex Var. Elliptic Equ.} {\bf 64} (2019), 503--518.
-\item Pingali, Vamsi Pritham, A note on higher extremal metrics {\em Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010.
-\item Pingali, Vamsi Pritham, Representability of {C}hern-{W}eil forms {\em Math. Z.} {\bf 288} (2018), 629--641.
-\item Pritham Pingali, Vamsi, Existence of coupled {K}\"{a}hler-{E}instein metrics using the
-continuity method {\em Internat. J. Math.} {\bf 29} (2018), 1850041, 8.
-\item Quddus, Safdar, Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
-spheres {\em J. Noncommut. Geom.} {\bf 13} (2019), 257--267.
-\item Rangarajan, G., Symplectic integration of nonlinear Hamiltonian systems {\em Pramana -- Journal of Physics} {\bf 48} (1997), 129.
-\item Rangarajan, G., Fractals in geophysics {\em “Application of Fractals in Earth Sciences"} {\bf } (2000), .
-\item Rangarajan, G., Applications of Lie algebraic techniques to nonlinear Hamiltoniansystems {\em Nonlinear Phenomena} {\bf } (2000), .
-\item Rangarajan, G., Polynomial map factorization of symplectic maps {\em International Journal of Modern Physics C} {\bf 14} (2003), 847.
-\item Rangarajan, G. and Ding, M., Integrated approach to the assessment of long range correlation in time series data {\em Physical Review E} {\bf 61} (2000), 4991.
-\item Rangarajan, G. and Ding, M., First passage time problem for biased continuous-time random walks {\em Fractals} {\bf 8.0} (2000), 139.
-\item Rangarajan, G. and Ding, M., First passage distributions for long memory processes {\em Lecture Notes in Physics} {\bf 621} (2003), 167.
-\item Rangarajan, G. and Habib, S. and Ryne, R. D., Lyapunov exponents without rescaling and reorthogonalization {\em Physical Review Letters} {\bf 80} (1998), 3747.
-\item Rangarajan, G. and Sachidanand, M., Spherical aberration and its correction using Lie algebraic techniques {\em Pramana - Journal of Physics} {\bf 49} (1997), 635.
-\item Rangarajan, G. and Sachidanand, M., Invariant metric for nonlinear symplectic maps {\em Pramana - Journal of Physics} {\bf 58} (2002), 477.
-\item Rangarajan, G. and Sant, D. A., A climate predictability index and its applications {\em Geophysical Research Letters} {\bf 24} (1997), 1239.
-\item Rangarajan, G. and Sant, D. A., Paleoclimatic data from 74KL and Guliya cores: New insights {\em Geophysical Research Letters} {\bf 27} (2000), 787.
-\item Rangarajan, G. and Sant, D. A., Fractal dimensional analysis of Indian climatic dynamics {\em Chaos, Solitons and Fractals} {\bf 19} (2004), 285.
-\item Rangarajan, N.
-and Fox, Z.
-and Singh, A.
-and Kulkarni, P.
-and Rangarajan, G., Disorder, Oscillatory Dynamics and State Switching: The Role of c-Myc {\em Journal of Theoretical Biology} {\bf 386} (2015), 105.
-\item Ray, A.
-and Sehgal, N.
-and Karunakaran, S.
-and Rangarajan, G.
-and  Ravindranath, V., MPTP activates ASK1-p38 MAPK signaling pathway through TNF-dependent Trx1 oxidation in Parkinsonism mouse model {\em Free Radical Biology & Medicine} {\bf 87} (2015), 312.
-\item Reddy, Nanda Kishore, Equality of {L}yapunov and stability exponents for products of
-isotropic random matrices {\em Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624.
-\item Resmi, V. and Ambika, G. and Amritkar, R. E. and Rangarajan, G., Amplitude death in complex networks induced by environment {\em Physical Review E} {\bf 85} (2012), 19593.
-\item Reza, Md. Ramiz, Curvature inequalities for operators in the {C}owen-{D}ouglas
-class of a planar domain {\em Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279.
-\item Sain, Debmalya, On extreme contractions and the norm attainment set of a
-bounded linear operator {\em Ann. Funct. Anal.} {\bf 10} (2019), 135--143.
-\item Sain, Debmalya, On the norm attainment set of a bounded linear operator {\em J. Math. Anal. Appl.} {\bf 457} (2018), 67--76.
+Kalidas, {\em Orthogonality of bounded linear operators on complex {B}anach
+spaces}, Adv. Oper. Theory} {\bf 3} (2018), 699--709, DOI 10.15352/aot.1712-1268, \url{https://doi.org/10.15352/aot.1712-1268}.
+\item Pingali, Vamsi P., {\em A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE}}, Complex Var.
+Elliptic Equ.} {\bf 64} (2019), 503--518, DOI 10.1080/17476933.2018.1454914, \url{https://doi.org/10.1080/17476933.2018.1454914}.
+\item Pingali, Vamsi Pritham, {\em A note on higher extremal metrics}, Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010, DOI 10.1090/tran/7416, \url{https://doi.org/10.1090/tran/7416}.
+\item Pingali, Vamsi Pritham, {\em Representability of {C}hern-{W}eil forms}, Math. Z.} {\bf 288} (2018), 629--641, DOI 10.1007/s00209-017-1903-2, \url{https://doi.org/10.1007/s00209-017-1903-2}.
+\item Pritham Pingali, Vamsi, {\em Existence of coupled {K}\"{a}hler-{E}instein metrics using the
+continuity method}, Internat. J. Math.} {\bf 29} (2018), 1850041, 8, DOI 10.1142/S0129167X18500416, \url{https://doi.org/10.1142/S0129167X18500416}.
+\item Quddus, Safdar, {\em Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
+spheres}, J. Noncommut. Geom.} {\bf 13} (2019), 257--267, DOI 10.4171/JNCG/320, \url{https://doi.org/10.4171/JNCG/320}.
+\item Reddy, Nanda Kishore, {\em Equality of {L}yapunov and stability exponents for products of
+isotropic random matrices}, Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624, DOI 10.1093/imrn/rnx134, \url{https://doi.org/10.1093/imrn/rnx134}.
+\item Reza, Md. Ramiz, {\em Curvature inequalities for operators in the {C}owen-{D}ouglas
+class of a planar domain}, Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279, DOI 10.1512/iumj.2018.67.7320, \url{https://doi.org/10.1512/iumj.2018.67.7320}.
+\item Roth, Julien and Upadhyay, Abhitosh, {\em On compact anisotropic {W}eingarten hypersurfaces in
+{E}uclidean space}, Arch. Math. (Basel)} {\bf 113} (2019), 213--224, DOI 10.1007/s00013-019-01315-8, \url{https://doi.org/10.1007/s00013-019-01315-8}.
+\item Roy, Krishanu and Venkatesh, R., {\em Maximal closed subroot systems of real affine root systems}, Transform.
+Groups} {\bf 24} (2019), 1261--1308, DOI 10.1007/s00031-018-9510-9, \url{https://doi.org/10.1007/s00031-018-9510-9}.
+\item Sain, Debmalya, {\em On extreme contractions and the norm attainment set of a
+bounded linear operator}, Ann. Funct. Anal.} {\bf 10} (2019), 135--143, DOI 10.1215/20088752-2018-0014, \url{https://doi.org/10.1215/20088752-2018-0014}.
+\item Sain, Debmalya, {\em On the norm attainment set of a bounded linear operator}, J.
+Math.
+Anal.
+Appl.} {\bf 457} (2018), 67--76, DOI 10.1016/j.jmaa.2017.07.070, \url{https://doi.org/10.1016/j.jmaa.2017.07.070}.
+\item Sain, Debmalya, {\em Smooth points in operator spaces and some
+{B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces}, Oper. Matrices} {\bf 13} (2019), 433--445, DOI 10.7153/oam-2019-13-32, \url{https://doi.org/10.7153/oam-2019-13-32}.
 \item Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag,
-Santanu, On the numerical index of polyhedral {B}anach spaces {\em Linear Algebra Appl.} {\bf 577} (2019), 121--133.
-\item Sain, Debmalya and Paul, Kallol and Mal, Arpita, A complete characterization of {B}irkhoff-{J}ames
-orthogonality in infinite dimensional normed space {\em J. Operator Theory} {\bf 80} (2018), 399--413.
-\item Sain, Debmalya and Paul, Kallol and Mal, Arpita, On approximate {B}irkhoff-{J}ames orthogonality and normal
-cones in a normed space {\em J. Convex Anal.} {\bf 26} (2019), 341--351.
-\item Sampath, D.
-and Sabitha, K.
-R.
-and Hegde, P.
-and Jayakrishnan, H.
-R.
-and Kutty, B.M.
-and Chattarji, S.
-and Rangarajan, G.
-and Laxmi, T.R., A study on fear memory retrieval and REM sleep in maternal separation and isolation stressed rats {\em Behavioural Brain Research} {\bf 273} (2014), 144.
-\item Sanki, Bidyut, Filling of closed surfaces {\em J. Topol. Anal.} {\bf 10} (2018), 897--913.
-\item Sanki, Bidyut and Gadgil, Siddhartha, Graphs of systoles on hyperbolic surfaces {\em J. Topol. Anal.} {\bf 11} (2019), 1--20.
-\item Sant D.
-A and Parvez, I.
-A.
-and Rangarajan, G.
-and Patel, J.
-and Bhatt, M.
-N.
-and Salam, T.
-A.
-S., Subsurface profiling along Banni Plains and bounding faults, Kachchh, Western India using Microtremors method {\em Journal of Asian Earth Sciences} {\bf 146} (2017), 326.
-\item Sant, D.
-A.
-and Krishnan, K.
-and Rangarajan, G.
-and Basavaiah, N.
-and Pandya and C.,Sharma, M.
-and Trivedi, Y., Characterization of flood plain and climate change using multi-proxy records {\em Journal of Indian Geophysical Union} {\bf 8.0} (2004), 39.
-\item Sant, D. A. and Rangarajan, G., Onset of climate change at last Glacial-Holocene transition: Role of the tropical Pacific {\em Current Science} {\bf 83} (2002), 1398.
-\item Sant, D. A. and Rangarajan, G., Study of Indian climate variability using predictability indices {\em Modern Applied Mathematics} {\bf } (2005), 145.
-\item Sant, D.
-A.
-and Rangarajan, G.
-and Krishnan, K.
-and Basavaiah, N.
-and Pandya, C.
-and Sharma, M.
-and Trivedi, Y., “ Flood plain record of southwest Indian monsoon during the last glacial" {\em Man and Environment} {\bf 31} (2006), 9.0.
-\item Sant, D.A.
-and Parvez, I.
-A.
-and Rangarajan, G.
-and Patel, S.
-J.
-and Salam, T.
-A.
-S.
-and Bhatt, M.
-N., Subsurface imaging of brown coal bearing Tertiary sedimentaries - Deccan Trap interface using microtremor method {\em Journal of Applied Geophysics} {\bf 159} (2018), 362.
-\item Seshadri, Harish and Verma, Kaushal, Some aspects of the automorphism groups of domains {\em Handbook of group actions. {V}ol. {III}} {\bf 40} (2018), 145--174.
-\item Sukumaran, P.
-and Parvez, I.
-A.
-and Sant, D.
-A.
-and Rangarajan, G.
-and Krishnan, K., Profiling of Late Tertiary - Early Quaternary surface in the lower reaches of Narmada Valley using microtremors {\em Journal of Asian Earth Sciences} {\bf 41} (2011), 325.
-\item Sukumaran, P.
-and Sant, D.
-A.
-and Krishnan, K.
-and Rangarajan, G., High resolution facies record on Late Holocene flood plain sediments from lower reaches of Narmada Valley, Western India {\em Journal of the Geological Society of India} {\bf 79} (2012), 41.
-\item Thangavelu, Sundaram, An analogue of {P}fannschmidt's theorem for the {H}eisenberg
-group {\em J. Anal.} {\bf 26} (2018), 235--244.
-\item Thangavelu, Sundaram and Naidu Dogga, Venku, {$L^p$}-{$L^2$} estimates for solutions of the wave equation
-associated to the {G}rushin operator {\em Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92.
-\item Truccolo, W. A. and Rangarajan, G. and Chen, Y. and Ding, M., Analyzing stability of equilibrium points in neural networks: A general approach {\em Neural Networks} {\bf 16} (2003), 1453.
-\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh, On biconservative hypersurfaces in 4-dimensional {R}iemannian
-space forms {\em Math. Nachr.} {\bf 292} (2019), 905--921.
-\item Verma, Kaushal, Notes on the boundaries of quadrature domains {\em Anal. Math. Phys.} {\bf 9} (2019), 617--638.
+Santanu, {\em On the numerical index of polyhedral {B}anach spaces}, Linear Algebra Appl.} {\bf 577} (2019), 121--133, DOI 10.1016/j.laa.2019.04.024, \url{https://doi.org/10.1016/j.laa.2019.04.024}.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita, {\em A complete characterization of {B}irkhoff-{J}ames
+orthogonality in infinite dimensional normed space}, J. Operator Theory} {\bf 80} (2018), 399--413.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita, {\em On approximate {B}irkhoff-{J}ames orthogonality and normal
+cones in a normed space}, J. Convex Anal.} {\bf 26} (2019), 341--351.
+\item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas, {\em On two extremum problems related to the norm of a bounded
+linear operator}, Oper. Matrices} {\bf 13} (2019), 421--432, DOI 10.7153/oam-2019-13-31, \url{https://doi.org/10.7153/oam-2019-13-31}.
+\item Sain, Debmalya and Ray, Anubhab and Paul, Kallol, {\em Extreme contractions on finite-dimensional polygonal {B}anach
+spaces}, J. Convex Anal.} {\bf 26} (2019), 877--885.
+\item Sanki, Bidyut, {\em Filling of closed surfaces}, J. Topol. Anal.} {\bf 10} (2018), 897--913, DOI 10.1142/S1793525318500309, \url{https://doi.org/10.1142/S1793525318500309}.
+\item Sanki, Bidyut and Gadgil, Siddhartha, {\em Graphs of systoles on hyperbolic surfaces}, J.
+Topol.
+Anal.} {\bf 11} (2019), 1--20, DOI 10.1142/S1793525319500018, \url{https://doi.org/10.1142/S1793525319500018}.
+\item Seshadri, Harish, {\em Differential geometry in {I}ndia}, Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799, DOI 10.1007/s13226-019-0355-2, \url{https://doi.org/10.1007/s13226-019-0355-2}.
+\item Seshadri, Harish and Verma, Kaushal, {\em Some aspects of the automorphism groups of domains}, Handbook of group actions. {V}ol. {III}} {\bf 40} (2018), 145--174.
+\item Thangavelu, Sundaram, {\em An analogue of {P}fannschmidt's theorem for the {H}eisenberg
+group}, J. Anal.} {\bf 26} (2018), 235--244, DOI 10.1007/s41478-018-0147-9, \url{https://doi.org/10.1007/s41478-018-0147-9}.
+\item Thangavelu, Sundaram and Naidu Dogga, Venku, {\em {$L^p$}-{$L^2$} estimates for solutions of the wave equation
+associated to the {G}rushin operator}, Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92, DOI 10.1515/apam-2017-0042, \url{https://doi.org/10.1515/apam-2017-0042}.
+\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh, {\em On biconservative hypersurfaces in 4-dimensional {R}iemannian
+space forms}, Math. Nachr.} {\bf 292} (2019), 905--921, DOI 10.1002/mana.201700328, \url{https://doi.org/10.1002/mana.201700328}.
+\item Urbina-Romero, Wilfredo, {\em Gaussian harmonic analysis}, } {\bf } (2019), xix+477, DOI 10.1007/978-3-030-05597-4, \url{https://doi.org/10.1007/978-3-030-05597-4}.
+\item Verma, Kaushal, {\em Notes on the boundaries of quadrature domains}, Anal. Math. Phys.} {\bf 9} (2019), 617--638, DOI 10.1007/s13324-018-0221-0, \url{https://doi.org/10.1007/s13324-018-0221-0}.
+\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan,
+Govindan, {\em On the role of four-wave mixing effect in the interactions
+between nonlinear modes of coupled generalized nonlinear
+{S}chr\"{o}dinger equation}, Chaos} {\bf 29} (2019), 123135, 14, DOI 10.1063/1.5121245, \url{https://doi.org/10.1063/1.5121245}.
 \item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, Govindan
-and Lakshmanan, M., On symmetry preserving and symmetry broken bright, dark and
+and Lakshmanan, M., {\em On symmetry preserving and symmetry broken bright, dark and
 antidark soliton solutions of nonlocal nonlinear {S}chr\"{o}dinger
-equation {\em Phys. Lett. A} {\bf 383} (2019), 15--26.
-\item Wen. X. and Rangarajan, G. and Ding, M., Is Granger causality a viable technique for analyzing fMRI data? {\em PLoS One} {\bf 8.0} (2013), e67428.
-\item “Albo, Z.
-and Di Prisco, G.
-V.
-and Chen, Y.
-and Rangarajan, G.
-and Truccolo, W.
-and Feng, J.
-and Vertes, R.
-P.
-and Ding, M.", Is partial coherence a viable technique for identifying generators of neural oscillations?
-{\em Biological Cybernetics} {\bf 90} (2004), 318.
-\item “Rangarajan, G. and Habib, S. and Ryne, R. D.", A new method for computing Lyapunov exponents {\em Nonlinear Dynamics and Brain Functioning} {\bf } (1999), .
+equation}, Phys. Lett. A} {\bf 383} (2019), 15--26, DOI 10.1016/j.physleta.2018.10.011, \url{https://doi.org/10.1016/j.physleta.2018.10.011}.
 \end{enumerate}

### 2020-08-05 data/draft-sections.tex
postdocs code, data; first generation

@@
 \begin{enumerate}
-\item K Philip Thomas, IISc-Bangalore did his/her  summer project under the guidance of R. Venkatesh during May 1--31, 2018
-\item Rati Ludhani, IIT Bombay did his/her  summer project under the guidance of R. Venkatesh during May 6--31, 2018
-\item Nazia V from IISER Pune did his/her  summer project under the guidance of Pooja Singla during 1st June-30th July, 2018
-\item      Ms. Meghna, first year BSc,Christ University, Bangalore did his/her  summer project under the guidance of A. K. Nandakumaran during April 11 – May 10, 2018. 
-\item Deeparaj Bhat did his/her KVPY summer project under the guidance of Subhojoy Gupta during May - July 2018
-\item Arka Ghosh did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May-June 2018
-\item Chinmaya Kausik did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May-June 2018
-\item Nishit Pandya did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May-June 2018
-\item Julian D'Costa did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May-June 2018
-\item Vrunda Rathi did his/her KVPY summer project under the guidance of Arvind Ayyer during May-July
-\item KARTIK SINGH did his/her KVPY summer project under the guidance of Arvind Ayyer during May-July
-\item ADITHYA UPADHYA  did his/her KVPY summer project under the guidance of Arvind Ayyer during May-July
-\item MANISH PANDEY did his/her KVPY summer project under the guidance of Arvind Ayyer during May - July
-\item Nandan Malhotra, IISER Mohali did his/her  summer project under the guidance of Srikanth K. Iyer during May - July 2018
+\item Rohit Kumar, Indian Institute of Science  did his/her KVPY summer project under the guidance of R. Venkatesh during May–June 2019
+\item Gobinda Debnath, NIT Agartala did his/her IASc-INSA-NASI Focus Area Science Technology Summer Fellowship summer project under the guidance of Ved Datar during May 15, 2019 - July 15, 2020
+\item Arnab Roy, Ramakrishna Mission Residential College did his/her Fellowship from the Indian Academy of Sciences summer project under the guidance of Vamsi Pritham Pingali during 26 May - 19 July
+\item Ms. Sradha R Bhat, IISER, Thiruvananthapuram did his/her DST Inspire Fellow summer project under the guidance of A. K. Nandakumaran during May 04 – July 04, 2019
+\item Ms. Indulekha, IISER, Thiruvananthapuram did his/her May 04 – July 04, 2019 summer project under the guidance of A. K. Nandakumaran during DST Inspire Fellow
+\item Ms. Muskan Agarwal, Mount Carmel College, Bangalore did his/her General summer project under the guidance of A. K. Nandakumaran during May 01 – June 09, 2019
+\item Ms. Rajashree Dahal, Mount Carmel College, Bangalore did his/her General summer project under the guidance of A. K. Nandakumaran during May 01 – June 09, 2019
+\item Mr. Arya Samanta, IISER, Pune did his/her General summer project under the guidance of A. K. Nandakumaran during June-July, 2019
+\item Ms Nirmala Aurad, Dept of Mathematics, Gulbarga University did his/her Academy summer project under the guidance of A. K. Nandakumaran during July 03 – August 30, 2019
+\item Susheel Shankar, Indian Institute of Science did his/her KVPY summer project under the guidance of Gautam Bharali during May--July, 2019
+\item Aritra Das, IISc did his/her KVPY summer project under the guidance of Arvind Ayyer during May-July
+\item Mrinmoy Karmakar, IISc did his/her KVPY summer project under the guidance of Arvind Ayyer during May-Jun
+\item Omkar Bhalchandra Baraskar, IISc did his/her KVPY summer project under the guidance of Arvind Ayyer during May-Jun
+\item Susheel Shankar, IISc did his/her KVPY summer project under the guidance of Arvind Ayyer during May-June
+\item Dhanus M Lal, IISc did his/her KVPY summer project under the guidance of Arvind Ayyer during May-June
+\item Prathamesh Gajanan Patil, IISc did his/her KVPY summer project under the guidance of Arvind Ayyer during May-June
+\item Achal Kumar, IISc did his/her KVPY summer project under the guidance of Arvind Ayyer during May-June
+\item Matthew Honnor did his/her  summer project under the guidance of Mahesh Kakde during 1 month
+\item Saptarsi Ghosal, CMI did his/her  summer project under the guidance of Manjunath Krishnapur during June-July 2019
+\item Deep Ghoshal, ISI Kolkata did his/her  summer project under the guidance of Manjunath Krishnapur during June-July 
+\item Arghya Chakraborty, ISI Kolkata did his/her  summer project under the guidance of Manjunath Krishnapur during June-July 
+\item Somak Laha, ISI Kolkata did his/her  summer project under the guidance of Manjunath Krishnapur during June-July
+\item Sayak Chatterjee did his/her  summer project under the guidance of Manjunath Krishnapur during June-July
+\item Anirban Basak, IISER Kolkata did his/her  summer project under the guidance of Manjunath Krishnapur during June-July
+\item Nafia Saleem, IIT Madras did his/her SRFP of IAS summer project under the guidance of Manjunath Krishnapur during June-July
+\item Rohit Kumar, IISc did his/her KVPY summer project under the guidance of R VENKATESH during May-June 2019
+\item Aman Agrawal, IISc did his/her  summer project under the guidance of Apoorva Khare during May-July 2019
+\item Sutanay Bhattacharya, IISc did his/her  summer project under the guidance of Apoorva Khare during May-July 2019
+\item Samarth Hawaldar, IISc did his/her  summer project under the guidance of Apoorva Khare during May-July 2019
+\item Swaroop Hegde, NISER Bhubaneswar did his/her  summer project under the guidance of Apoorva Khare during May-July 2019
+\item Anant Mudgal, CMI did his/her  summer project under the guidance of Apoorva Khare during May-July 2019
+\item Abhilash Mukherjee, IISc did his/her  summer project under the guidance of Apoorva Khare during May-July 2019
+\item Pulkit Sinha, IISc did his/her  summer project under the guidance of Apoorva Khare during May-July 2019
+\item Chinmaya Kausik, IISc did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May-June 2019
+\item Nilendu Das, IISER Mohali did his/her Academy summer programme summer project under the guidance of Siddhartha Gadgil during May, June 2019
+\item Nishit Pandya, IISc did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May, June 2019
+\item Julian D'Costa, IISc did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May, June 2019
 \end{enumerate}
@@
 
-\item {\bf A. K. Nandakumaran\,:} A. K. Nandakumaran in a DST-SERB (Matrics) project
+\item {\bf A. K. Nandakumaran\,:} Sole investigator in a DST (Matrix) project
 \begin{description}
@@
   \item[Duration\,:] 2018-2021
-  \item[Grant\,:] 6.6 Lakhs
+  \item[Grant\,:] 6.6 lakhs
 \end{description}
 
-\item {\bf A. K. Nandakumaran\,:} A. K. Nandakumaran in a DST(SERB) project
+\item {\bf A. K. Nandakumaran\,:} Sole investigator in a DST project
 \begin{description}
-  \item[Project Title\,:] Homogenization of Partial Dierential Equations in Certain Complex Domains
+  \item[Project Title\,:] Homogenization of Partial Differential Equations in Certain Complex Domains
   \item[Duration\,:] 2017-2020
-  \item[Grant\,:] Rs. 19.316 Lakhs
+  \item[Grant\,:] 19.316 Lakhs
 \end{description}
 
-\item {\bf Apoorva Khare\,:} Sole PI in an Infosys Foundation project (Young Investigator Award) in a Infosys Foundation, India project
+\item {\bf Apoorva Khare\,:} Sole investigator in a Infosys Foundation project
 \begin{description}
-  \item[Project Title\,:] N/A
+  \item[Project Title\,:] Young Investigator Award
   \item[Duration\,:] 2017-2019
-  \item[Grant\,:] 600,000 per year
+  \item[Grant\,:] 12 lakhs
 \end{description}
 
-\item {\bf Apoorva Khare\,:} Sole PI in a SERB project (Ramanujan Fellowship) in a SERB, DST, Govt. of India project
+\item {\bf Apoorva Khare\,:} Sole investigator in a SERB project
 \begin{description}
-  \item[Project Title\,:] N/A
+  \item[Project Title\,:] Ramanujan Fellowship
   \item[Duration\,:] 2018-2023
-  \item[Grant\,:] 700000 per year
+  \item[Grant\,:] 35 lakhs
 \end{description}
 
-\item {\bf Apoorva Khare\,:} Sole PI an a SERB project (MATRICS grant) in a SERB, DST, Govt. of India project
+\item {\bf Apoorva Khare\,:} Sole investigator in a SERB project
 \begin{description}
-  \item[Project Title\,:] Entrywise powers and power series preserving positivity in fixed dimension
+  \item[Project Title\,:] MATRICS: Entrywise Powers and Power Series Preserving Positivity in Fixed Dimension
   \item[Duration\,:] 2018-2021
-  \item[Grant\,:] 200000 per year
+  \item[Grant\,:] 6.6 lakhs
 \end{description}
 
-\item {\bf Arvind Ayyer\,:} Sole investigator in an SERB project in a SERB project
+\item {\bf Apoorva Khare\,:} Sole investigator in a DST and SERB project
+\begin{description}
+  \item[Project Title\,:] SwarnaJayanti Fellowship: Transformations preserving positivity in analysis, and connections to algebra and combinatorics
+  \item[Duration\,:] 2020-2025
+  \item[Grant\,:] Rs. 1,24,88,260
+\end{description}
+
+\item {\bf Arvind Ayyer\,:} Sole investigator in a SERB project
 \begin{description}
   \item[Project Title\,:]  Exactly solvable exclusion processes
-  \item[Duration\,:] 2018--2020
-  \item[Grant\,:] Rs. 19,30,490/-
+  \item[Duration\,:] 2017--2020
+  \item[Grant\,:] 19,30,490
 \end{description}
 
-\item {\bf Basudeb Datta\,:} Basudeb Datta, Sole investigator in a SERB, DST project
+\item {\bf Arvind Ayyer\,:} Co-investigator in a The Royal Society, UK project
 \begin{description}
-  \item[Project Title\,:] Minimal and tight triangulations of some pl manifolds
-  \item[Duration\,:] May 13, 2018 to May 12, 2021
-  \item[Grant\,:] Rs.660,000
+  \item[Project Title\,:] Determinantal Formulas for Multispecies ASEP  
+  \item[Duration\,:] 2019--2021
+  \item[Grant\,:] 11,759 pounds
 \end{description}
 
-\item {\bf Dilip P Patil\,:} Principal Investigator in a SERB Matrics Project in a DST-SERB project
+\item {\bf Basudeb Datta\,:} Sole investigator in a SERB, DST project
 \begin{description}
-  \item[Project Title\,:] Burnside Algebras --- Computational Aspects
-  \item[Duration\,:] Oct 2018 to Oct 2021
-  \item[Grant\,:] 200000 Per year
+  \item[Project Title\,:] Minimal and Tight Triangulations of some PL Manifolds
+  \item[Duration\,:] 2018--2021
+  \item[Grant\,:] 660,000
 \end{description}
 
-\item {\bf Gautam Bharali\,:} Sole investigator in a DST project in a DST project
+\item {\bf Dilip P. Patil\,:} Sole investigator in a DST-SERB project
+\begin{description}
+  \item[Project Title\,:] Burnside Algebras-Computational Aspects of Commutative Algebra and Algebraic Geometry
+  \item[Duration\,:] 2018 to 2021
+  \item[Grant\,:] 2 Lakhs per year
+\end{description}
+
+\item {\bf E K Narayanan\,:} Sole investigator in a SERB project
+\begin{description}
+  \item[Project Title\,:] Heckman-Opdam hypergeometric functions and harmonic analysis
+  \item[Duration\,:] 2019-2022
+  \item[Grant\,:] Six lakhs
+\end{description}
+
+\item {\bf Gautam Bharali\,:} Sole investigator in a DST project
 \begin{description}
@@
 
-\item {\bf Govindan Rangarajan\,:} Sole Investigator in a SERB project
+\item {\bf Govindan Rangarajan\,:} Sole investigator in a SERB project
 \begin{description}
@@
   \item[Duration\,:] 2011-present
-  \item[Grant\,:] 1,59,85,000
+  \item[Grant\,:] 80,00,000
 \end{description}
 
-\item {\bf Govindan Rangarajan\,:} Director in a DST-CNRS project
+\item {\bf Govindan Rangarajan\,:} Sole investigator in a Broadcom Corporation project
 \begin{description}
-  \item[Project Title\,:] Indo-French Centre for Applied Matheamtics
-  \item[Duration\,:] 2018-present
-  \item[Grant\,:] 6,83,00,000 + matching grant from CNRS
+  \item[Project Title\,:] Brain Inspired Computing
+  \item[Duration\,:] 2017-present
+  \item[Grant\,:] Rs. 1,37,00,000
 \end{description}
 
-\item {\bf Govindan Rangarajan\,:} Principal Investigator in a Broadcom Foundation project
+\item {\bf Govindan Rangarajan\,:} Sole investigator in a DST project
 \begin{description}
-  \item[Project Title\,:] EMEA Workshops
-  \item[Duration\,:] 2017-present
-  \item[Grant\,:] 1,35,00,000
+  \item[Project Title\,:] Indo-French Centre for Applied Mathematics Phase II
+  \item[Duration\,:] 2018-present
+  \item[Grant\,:] 1,03,77,511
 \end{description}
 
-\item {\bf Govindan Rangarajan\,:} Co-Principal Investigator in a Tata Trusts project
+\item {\bf Govindan Rangarajan\,:} Principal investigator in a CNRS, France project
 \begin{description}
-  \item[Project Title\,:] Alzheimer's Research
-  \item[Duration\,:] 2014-present
-  \item[Grant\,:] 75,00,00,000
+  \item[Project Title\,:] Indo-French Centre for Applied Mathematics Phase II
+  \item[Duration\,:] 2018-present
+  \item[Grant\,:] Euros 1,68,000 (Rs. 1,34,40,000)
 \end{description}
 
-\item {\bf Manjunath Krishnapur\,:} Manjunath Krishnapur (PI) in a SERB project
+\item {\bf Manjunath Krishnapur\,:} Principal investigator in a SERB project
 \begin{description}
-  \item[Project Title\,:] Zeros of random functions and anti-concentration phenomena
-  \item[Duration\,:] 2018-2021
-  \item[Grant\,:] 6,60,000
+  \item[Project Title\,:] Zeros of random.functions and anti-concentration phenomena
+  \item[Duration\,:] 2018-21
+  \item[Grant\,:] 200000
 \end{description}
 
-\item {\bf Pooja Singla\,:} Pooja Singla and Sole-investigator in a SERB-MATRICS project
+\item {\bf R VENKATESH\,:} Sole investigator in a DST-SERB (MATRICS) project
 \begin{description}
-  \item[Project Title\,:] "Representations of Linear Groups over Local Rings : Gelfand Models "
-  \item[Duration\,:] March 2019-March 2022
-  \item[Grant\,:] 6,00,000
+  \item[Project Title\,:] Study on the structure theory of Borcherds-Kac-Moody algebras and their subalgebras
+  \item[Duration\,:] 2019-2021
+  \item[Grant\,:] 6,60,000/-
 \end{description}
 
-\item {\bf Pooja Singla\,:} Amritanshu Prasad, Uri Onn, James Borger, Pooja Singla and PI, PI, Co-PI, Co-PI  in a MHRD-SPARC  project
+\item {\bf R VENKATESH\,:} Sole investigator in a DST project
 \begin{description}
-  \item[Project Title\,:] Representation Zeta Functions
-  \item[Duration\,:] March 2019 to march 2021
-  \item[Grant\,:] 71,46,350
+  \item[Project Title\,:] INSPIRE Faculty award
+  \item[Duration\,:] 2016-2021
+  \item[Grant\,:] 35,00,000/-
 \end{description}
 
-\item {\bf R. Venkatesh\,:} Investigator in a DST project
+\item {\bf R VENKATESH\,:} Sole investigator in a Infosys foundation project
 \begin{description}
-  \item[Project Title\,:] Inspire
-  \item[Duration\,:] 2016--2020
+  \item[Project Title\,:] Infosys Young Investigator award 
+  \item[Duration\,:] 2020-2021
+  \item[Grant\,:] 6,00,000/-
+\end{description}
+
+\item {\bf R. Venkatesh\,:} Sole investigator in a  SERB-MATRICS project
+\begin{description}
+  \item[Project Title\,:] Study on the structure theory of Borcherds-Kac-Moody algebras and their subalgebras.
+  \item[Duration\,:] 2019-2021
+  \item[Grant\,:] 6 Lakhs
+\end{description}
+
+\item {\bf R. Venkatesh\,:} Sole investigator in a DST-INPIRE project
+\begin{description}
+  \item[Project Title\,:] Inspire faculty award
+  \item[Duration\,:] 2016-2021
   \item[Grant\,:] 35 Lakhs
@@
 
-\item {\bf R. Venkatesh\,:} Investigator in a DST-SERB project
+\item {\bf R. Venkatesh\,:} Sole investigator in a  Infosys foundation project
 \begin{description}
-  \item[Project Title\,:] Study on the structure theory of Borcherds-Kac-Moody algebras and their subalgebras
-  \item[Duration\,:] 2018-2020
+  \item[Project Title\,:] Infosys Young Investigator award 
+  \item[Duration\,:] 2020-2021
   \item[Grant\,:] 6 Lakhs
+\end{description}
+
+\item {\bf RADHIKA GANAPATHY\,:} Sole investigator in a Infosys Foundation project
+\begin{description}
+  \item[Project Title\,:] Young Investigator
+  \item[Duration\,:] 2019-2021
+  \item[Grant\,:] Rs. 3,00,000 p.a.+ Rs. 25,000 monthly salary top-up
+\end{description}
+
+\item {\bf SANCHAYAN SEN\,:} Sole investigator in a Science & Engineering Research Board (SERB) project
+\begin{description}
+  \item[Project Title\,:] Geometry of random discrete structures
+  \item[Duration\,:] 2020--2023
+  \item[Grant\,:] 220,000 per annum
+\end{description}
+
+\item {\bf SANCHAYAN SEN\,:} Sole investigator in a Infosys Foundation, Bangalore project
+\begin{description}
+  \item[Project Title\,:] 
+  \item[Duration\,:] 2019--2021
+  \item[Grant\,:] 600,000 per annum
 \end{description}
@@
 \begin{description}
-  \item[Project Title\,:] Homotopy Type theory and Natural langauge processing for Computer-Assisted Mathematics
+  \item[Project Title\,:] Homotopy Type Theory and Natural Language Processing for Computer-Assisted mathematics
   \item[Duration\,:] 2018-2021
-  \item[Grant\,:] Rs. 19 lakhs
+  \item[Grant\,:] 1898700
 \end{description}
 
-\item {\bf Srikanth K. Iyer\,:} Sole investigator in a SERB project in a SERB project
+\item {\bf Srikanth Krishnan Iyer\,:} Sole investigator in a SERB project
 \begin{description}
   \item[Project Title\,:] Percolation at Criticality and Connectivity in the Random Connection Model
-  \item[Duration\,:] 2019-2022
-  \item[Grant\,:] six lakhs
+  \item[Duration\,:] March 22, 2019 - March 22, 2022
+  \item[Grant\,:] 6,60,000
 \end{description}
 
-\item {\bf Subhojoy Gupta\,:} Sole Investigator in SERB project in a SERB project
+\item {\bf Subhojoy Gupta\,:} Sole investigator in a SERB, DST project
 \begin{description}
   \item[Project Title\,:] Degenerations of geometric structures and meromorphic differentials on Riemann surfaces
-  \item[Duration\,:] 2018-2020
-  \item[Grant\,:] 660000
+  \item[Duration\,:] 2018-2021
+  \item[Grant\,:] 6 lakhs
 \end{description}
 
-\item {\bf Sundaram Thangavelu\,:} Principal Investigator in a SERB project
+\item {\bf Subhojoy Gupta\,:} Co-investigator in a Université Côte-D'azur and IISc  project
 \begin{description}
-  \item[Project Title\,:] JC Bose National Fellowship
-  \item[Duration\,:] 2018-2022
+  \item[Project Title\,:] Branched projective structures
+  \item[Duration\,:] 2019-2021
+  \item[Grant\,:] 6 lakhs
+\end{description}
+
+\item {\bf Sundaram Thangavelu\,:} Sole investigator in a DST project
+\begin{description}
+  \item[Project Title\,:] J.C.Bose Fellowship
+  \item[Duration\,:] 2008-2022
   \item[Grant\,:] 
@@
 
-\item {\bf Vamsi Pritham Pingali\,:} Vamsi Pritham Pingali (Principal Investigator) in a SERB project
+\item {\bf Thirupathi Gudi\,:} Sole investigator in a DST project
+\begin{description}
+  \item[Project Title\,:] Approximation Theory for PDEconstrained optimization and Variational Inequalities
+  \item[Duration\,:] 2019-2022
+  \item[Grant\,:] 600000
+\end{description}
+
+\item {\bf Vamsi Pritham Pingali\,:} Sole investigator in a SERB project
 \begin{description}
@@
   \item[Duration\,:] 2017-2020
-  \item[Grant\,:] 5,42,290 INR
+  \item[Grant\,:] 542290
 \end{description}
 
-\item {\bf Vamsi Pritham Pingali\,:} Vamsi Pritham Pingali (Principal Investigator) in a Infosys foundation project
+\item {\bf Vamsi Pritham Pingali\,:} Sole investigator in a Infosys Foundation project
 \begin{description}
-  \item[Project Title\,:] Young Investigator Award (No title)
+  \item[Project Title\,:] Infosys Young Investigator Award
   \item[Duration\,:] 2017-2019
-  \item[Grant\,:] 600000 INR 
+  \item[Grant\,:] 600000
 \end{description}
@@
 \begin{enumerate}
-\item Apoorva Khare was awarded Ramanujan Fellowship (Apr 2018), ICM Satellite Conference invited talk (Aug 2018), Tarun Tejankit Puraskar from Loksatta newspaper (Mar 2019)
-\item R. Venkatesh was awarded Associate of the Indian Academy of Sciences 2018-2022
-\item Subhojoy Gupta was awarded Simons Visiting Professorship grant to support a visit to Heidelberg University (September 10-17, 2018) following participation at the Oberwolfach workshop
-\item Sundaram Thangavelu was awarded V.V. Narlikar Memorial lecture award from INSA
+\item Apoorva Khare was awarded (1) Delivered a Plenary talk at the 2019 ILAS (International Linear Algebra Society) meeting in Rio de Janeiro, Brazil.
+Also selected as the LAMA Lecturer.
+(2) Delivered the 20th Professor Wazir Hasan Abdi Memorial Lecture, in Cochin University of Science and Technology (CUSAT).
+(3) Awarded the SwarnaJayanti Fellowship for 2018-19, in Mathematics.
+\item Arvind Ayyer was awarded My student, Surjadipta De Sarkar received a fellowship and travel grant to attend a program on Algebraic and Enumerative Combinatorics at the Mittag-Leffler Institute from 13 January - 30 April 2020.
+\item R VENKATESH was awarded   Infosys Young Investigator award from the Infosys foundation, 2020.
+\item R. Venkatesh was awarded Associate of the Indian Academy of Sciences (2018-2022), Infosys Young Investigator award from the Infosys foundation, 2020.
+\item Ved Datar was awarded Infosys Young Investigator Award
 \end{enumerate}
@@
 \begin{enumerate}
-\item Apoorva Khare was elected a N/A
+
 \end{enumerate}
@@
 \begin{enumerate}
-\item A. K. Nandakumaran, Editorial Member, TMC Bulletin
-\item Apoorva Khare, TRIM Series (Hindustan Book Agency); Sao Paulo Journal of Mathematical Sciences
+\item Apoorva Khare, Journals: (1) Indian Journal of Pure and Applied Mathematics (2) Linear and Multilinear Algebra (3) Sao Paulo Journal of Mathematical Sciences.
+Book Series: (4) TRIM (Texts and Readings in Mathematics)
+\item Arvind Ayyer, Indian Journal of Pure and Applied Mathematics, Algebraic Combinatorics
+\item E K Narayanan, Editorial board of the Indian Journal of Pure and Applied Mathematics
 \item Gautam Bharali, Newsletter of the Ramanujan Mathematical Society 
-\item Sundaram Thangavelu, Proceedings of the Indian Academy of Sciences
+\item Mrinal Kanti Ghosh, Associate Editor, Stochastic Analysis and Applications
+\item Sundaram Thangavelu, Proceedings of the Indian Academy of Sciences (Math.), Journal of Ramanujan Mathematical Society, Journal of Analysis, Tunisian Journal of Mathematics, Journal of Fourier Analysis and Applications.
 \end{enumerate}
+
+\subsection{Other Activities: 2018-19}
+\begin{enumerate}
+A. K. Nandakumaran was Member, Core Committee, KVPY
+A. K. Nandakumaran was Member, Library Committee
+Apoorva Khare was Talks: (1) 2019-04-12: Eigenfunctions Seminar, titled "Schoenberg: from metric geometry to matrix positivity" (2) 2019-11-06: 1st Math Symposium of Infosys Young Investigators: Talk, titled "Groups with norms; distance matrices and Zariski density"
+Apoorva Khare was Organizer of Eigenfunctions,  APRG Seminar, Algebra-Combinatorics Seminar, (co-organiser)
+Apoorva Khare was Contributed in preparing the PhD Qualifiers in Algebra
+Apoorva Khare was Student thesis/project supervision: (1) Swarnalipa Datta, MS Thesis (2) Soumik Dutta, BS Project
+Arvind Ayyer was Organised ICTS workshop on "Universality in random structures: Interfaces, Matrices, Sandpiles" from 14/01 -08/02/2019 jointly with Riddhipratim Basu and Manjunath Krishnapur.
+Basudeb Datta was B.
+Datta was an member of the Committees for the following: (i)  Promotion of Professor in Mathematics in HAG scale in NIT, Rourkela in November 2018, (ii) Faculty selection for the post of Associate and Assistant Professors in the Department of Mathematics of IIT, Delhi in May, 2019, (iii) Faculty selection in mathematics at NISER, Bhubaneswar in June, 2019.
+Basudeb Datta was B.
+Datta was  examiner for the following PhD theses:  (i) ``Dynamics of maps possessing the almost average shadowing property and variants of transitivity" of Mukta Garg, Univ of Delhi in 2018, (ii) ``On some problems in Algebraic Combinatorics" of Sajal K.
+Mukherjee, Visva-Bharati University, Santiniketan in 2018 (also the external examiner for the viva-voce examination  in June 2019), (iii) ``Group actions on Dold and Milnor manifolds" of Pinka Dey, IISER Mohali in 2019 (also the external examiner for the viva-voce examination in December 2019), (iv) ``Variants of transitivity, sensitivity and expansivity in non-autonomous discrete systems" of Radhika Vashisht,  Univ.
+of Delhi in 2020.
+Dilip P. Patil was Taught the course: MA 312 Commutative Algebra course during Jan-April 2020
+Dilip P. Patil was Taught  (12 Week long)  NPTEL Course during Jan-April 2020
+Gautam Bharali was Member of the Faculty Selection Committee at IIIT Guwahati in June 2018
+Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)  
+R VENKATESH was We hosted 70 students and 5 faculty members from Madras Christian College as a part of their Educational visit to IISc, Bangalore on 16th October 2018.
+Two lectures were arranged for them on 16th October 2018.
+R. Venkatesh was Algebra Symposium, Department of Mathematics, IISc, Bangalore, India (February 12, 2020).
+R.
+Venkatesh was Discussion Meeting on Representation Theory 2019, Department of Mathematics, IISc, Bangalore (December 14 - 16, 2019).
+Partially funded by the UGC-CAS grant.
+Two lecture series was delivered by Professor Vyjayanthi Chari (UC Riverside, USA) and Professor Anne Schilling (UC Davis, USA) as part of this discussion meeting.
+R. Venkatesh was NCM - Instructional School for Teachers on Analysis and PDE, Department of Mathematics, IISc, Bangalore (May 6 - 18, 2019). 
+Srikanth Krishnan Iyer was Gave a series of ten lectures in the Advanced Instructional School on Stochastic Processes, June 2019 organized by NICER, Bhubaneshwar on Probability Theory.
+Srikanth Krishnan Iyer was Gave a series of eight lectures in the annual Lecture Series in Probability XIV held at ISI-Delhi between December 2 - 6, 2019 on Limit Theorems in Stochastic Geometry.
+Srikanth Krishnan Iyer was Gave a talk titled :Random Connection Models" at the RBI, Mumbai on the occasion of Statistics day, June 26, 2019.
+Srikanth Krishnan Iyer was Gave a talk titled "Phase Transitions in Random Networks" at the FLAIR 4 Big Data Summer School on July 6, 2019.
+Subhojoy Gupta was Co-organized a discussion meeting at ICTS Bangalore in December 2018, on “Surface-Group Representations and Projective Structures".
+Website: https://www.icts.res.in/discussion-meeting/SGPS2018.
+Subhojoy Gupta was Referee for “Memoirs of the American Mathematical Society",  “Indian Journal of Pure and Applied Mathematics"
+Subhojoy Gupta was M.Sc. thesis referee for a student of Chennai Mathematical Institute,  Satyajit Maity
+Subhojoy Gupta was Member of Research Advisory Committee for Ramya Nair, a PhD student at IISER Pune. 
+Thirupathi Gudi was Organized Workshop on Finite Elements for Nonlinear and Multiscale Problems during Feb 28 – Mar 03, 2020.
+Vamsi Pritham Pingali was Guided the Master's Thesis ("Kahler geometry with a view towards the Calabi conjecture") of Vishnu Nandakumaran of IISER Pune (academic year of 2019-2020)
+Vamsi Pritham Pingali was Visited ICTP as a junior associate during May 2019 and delivered a talk ("A vector bundle version of the Monge-Ampere equation")
+\end{enumerate}
+
+\subsection{Other Activities: 2019-20}
+\begin{enumerate}
+A. K. Nandakumaran was Convener, KVPY
+A. K. Nandakumaran was Member, Library Committee
+Apoorva Khare was Member of two UG Project Presentation Evaluation Committees
+Apoorva Khare was Pre-RMO (Regional Mathematics Olympiad) - helped in setting the question paper
+Apoorva Khare was Senate nominee for Comprehensive Exam of Vinayak Ramkumar (student of P. Vijay Kumar, ECE)
+Apoorva Khare was Advising: (1) Prateek Kumar Vishwakarma, Int-PhD (passed his Comprehensive Exam) (2) Babhrubahan Bose, Int-PhD (passed his Comprehensive Exam) (3) G.V.K.
+Teja, PhD (passed his Comprehensive Exam) (4) Swarnalipa Datta, Int-PhD (downgraded to MS) Mentoring: (5) Dr.
+Projesh Nath Choudhury, NBHM postdoc
+Arvind Ayyer was Referee for the thesis of Majil Pratim Saikia at University of Vienna.
+Arvind Ayyer was Referee for the thesis of Mr. Jyotirmoy Ganguly at IISER Pune.
+Arvind Ayyer was Thesis examiner for Mr. Sudip Bera, Visva-Bharati University.
+Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)
+Gautam Bharali was Served as an independent expert for the Swiss National Science Foundation for the review of project proposals in pure mathematics in 2019.
+R VENKATESH was Algebra Symposium, Department of Mathematics, IISc, Bangalore, India (February 12, 2020).
+R VENKATESH was Discussion Meeting on Representation Theory 2019, Department of Mathematics, IISc, Bangalore (December 14 - 16, 2019).
+Partially funded by the UGC-CAS grant.
+Two lecture series was delivered by Professor Vyjayanthi Chari (UC Riverside, USA) and Professor Anne Schilling (UC Davis, USA) as part of this discussion meeting.
+R VENKATESH was NCM - Instructional School for Teachers on Analysis and PDE, Department of Mathematics, IISc, Bangalore (May 6 - 18, 2019). 
+Siddhartha Gadgil was thesis examiner for a thesis at IIT, Kanpur
+Siddhartha Gadgil was thesis examiner for a thesis at Delhi University
+Siddhartha Gadgil was thesis examiner for a thesis for TIFR, Mumbai
+Siddhartha Gadgil was member of selection committee at BHU
+Subhojoy Gupta was Member of Research Advisory Committee for Ramya Nair, a PhD student at IISER Pune. 
+Subhojoy Gupta was Co-organizer of an Advanced Instructional School on Riemannian Geometry, sponsored by the National Centre for Mathematics, held in July 2019.
+Subhojoy Gupta was Referee for "Proceedings of the London Mathematical Society", "Journal of Topology", "Manuscripta Mathematica" and reviewer for AMS and Zentralblatt Math Reviews
+Subhojoy Gupta was Supervised UG final year project of Shabarish Chenakkod
+\end{enumerate}

### 2020-08-05 data/reports.tex
postdocs code, data; first generation

--- 2019-08-01 data/reports.tex
@@
 
-We have demonstrated the asymptotic analysis of a semi-linear optimal control problem posed on a smooth oscillating boundary domain in the present paper.
-We have considered a more general oscillating domain than the usual “pillar-type” domains.
-Consideration of such general domains will be useful in more realistic applications like circular domain with rugose boundary.
-We study the asymptotic behavior of the problem under consideration using a new generalized periodic unfolding operator.
-Further, we have studied the homogenization of a non-linear optimal control problem and such non-linear problems are limited in the literature despite the fact that they have enormous real-life applications.
-Among several other technical difficulties, the absence of a enough criteria for the optimal control is one of the most attention-grabbing issues in the current setting.
-We also obtain corrector results in this paper.
-We considered an optimal control problem posed on a domain with a highly oscillating smooth boundary where the controls are applied on the oscillating part of the boundary.
-There are many results on domains with oscillating boundaries where the oscillations are pillar-type (non-smooth) while the literature on smooth oscillating boundary is very few.
-In this article, we use appropriate scaling on the controls acting on the oscillating boundary leading to different limit control problems; namely, boundary optimal control and interior optimal control problem.
-In the last part of the article, we visualize the domains as a branched structure, and we introduce unfolding operators to get contributions from each level at every branch.
+The main theme of the research is to understand the asymptotic analysis of  PDE problems and related optimal control problems in some complex domains.
+We consider domains whose boundary is rapidly oscillating which  leads to multi-scales in the problem.
+One of the major issue is the development of the so called unfolding operators which contains information about both scales.
+We have ingeniously used the unfolding operators not only to carry out the limiting behaviour of the problem under study, it is used to characterize the optimal controls.
+One needs to construct suitable such operators according to the type of domain and the problem [1], [3-5].
+On a completely different direction, a multi-step Volterra integral equation-based algorithm was developed to measure the electric field auto-correlation function from multi-exposure speckle contrast data.
+This enabled us to derive an estimate of the full diffuse correlation spectroscopy data-type from a low-cost, camera-based system.
+This method is equally applicable for both single and multiple scattering field auto-correlation models.
+The feasibility of the system and method was verified using simulation studies, tissue mimicking phantoms and subsequently in in vivo experiments [2].
 
@@
 
-(1) A comprehensive, 40+ page paper treating distance matrices of trees.
-(2) An 80+ page survey on matrix positivity.
-(3) Extending results of Loewner, Horn, Cauchy, and Frobenius to new symmetric function identities and positivity conditions.
-(Among other works.)
+(1) I extended a fundamental matrix inequality, the Schur Product Theorem, for positive definite matrices, by providing nonzero, tight lower bounds.
+(2) I improved and updated several preprints - notably, a comprehensive work titled "Moment-sequence transforms" with Belton-Guillot-Putinar.
 
@@
 
-Multispecies versions of random juggling models were studied and exact stationary distributions were obtained using combinatorial techniques [1].
-For one variant, ultrafast convergence to stationarity was proved.
-A new totally asymmetric exclusion process with two species of particles on a finite one-dimensional lattice in contact with reservoirs was introduced, where the second-class particle is impermeable to the right reservoir [2].
-The stationary distribution was obtained using a matrix ansatz and the nonequilibrium phase diagram was computed in the thermodynamic limit.
-This was later extended to multiple species of particles and the phase diagram was computed.
-A new interacting particle system called the Hilbert-Galton board was introduced and various theorems about this process were proved [3].
-Random walks on noncommutative finite rings generated by both addition and multiplication were studied.
-Results were proven about the spectrum, stationary distribution and mixing time [4].
-A new class of factorizations about characters of the general linear group, when the variables were specialised, were proved [5].
-Somewhat surprisingly, the resulting objects are themselves characters of other classical groups.
-Some applications to enumerations of plane partitions and alternating sign matrices was given.
-The combinatorics of a large class of cyclic orders were studied [6].
-In particular, the enumeration of circular extensions of these cyclic orders was related to the enumeration of a family of polytopes made popular by R.
-Stanley.
-Extending earlier work, odd and chiral representations were studied for all Coxeter groups [7].
-[1] A.
-Ayyer, C.
-Finn and D.
-Roy, Matrix product solution of a left-permeable two-species asym- metric exclusion process, Phys.
-Rev.
-E, 97 no.
-1 (2018) 012151, 10pp.
-[2] A.
-Ayyer, J.
-Bouttier, S.
-Corteel, S.
-Linusson and F.
-Nunzi, Bumping sequences and multi- species juggling, Advances in Applied Mathematics, 98 (2018) 100–126.
-[3] A.
-Ayyer and S.
-Ramassamy, The Hilbert-Galton board, Latin American Journal of Probability and Mathematical Statistics (ALEA), 15 no.
-2 (2018), 755–774.
-[4] A.
-Ayyer and P.
-Singla, Random motion on finite rings, II: Noncommutative rings,  arXiv:1807.04082.
-[5] A.
-Ayyer and R.
-E.
-Behrend, Factorization theorems for classical group characters, with applications to alternating sign matrices and plane partitions, arXiv:1804.04514 [6]  A.
-Ayyer, M.
-Josuat-Vergès and S.
-Ramassamy, Extensions of partial cyclic orders and consecutive coordinate polytopes,  arXiv:1803.10351.
-[7]  A.
-Ayyer, A.
-Prasad and S.
-Spallone, Macdonald trees and determinants of representations for finite Coxeter groups, arXiv:1812.00608.
+In joint work with Aas, Linusson and Potka [1], the exact phase diagram for a semipermeable TASEP with nonlocal boundary jumps was obtained.
+In joint work with Behrend [2], new factorization theorems for classical group characters were proved.
+Applications to alternating sign matrices and plane partitions were given.
+In joint work with Finn and Roy [3], the phase diagram for a multispecies left-permeable asymmetric exclusion process was derived.
+In joint work with Linusson [4], a new class of reverse juggling processes was defined and their stationary distributions were computed.
 
@@
 
-We have shown that the boundary of the pseudorhombicuboctahedron is the only semi-equivelar map on the 2-sphere which is not vertex-transitive.
-As a consequence, we show that each semi-equivelar map on the real projective plane is vertex-transitive.
+A semi-regular tiling of the hyperbolic plane is a tessellation by regular geodesic polygons with the property that each vertex has the same vertex-type.
+Determined combinatorial criteria for the existence, and uniqueness, of a semi-regular tiling with a given vertex-type \ref{bdsg_2019} .
 
-\subsection{Dilip P Patil}
+\subsection{Dilip P. Patil}
 
-(1) During my sabbatical leave in IIT Bombay I have written the following two manuscripts (jointly with Prof.
-J.
-K.
-Verma):  [1] (Jointly with Kriti Goel and J.
-K.
-Verma ) Nullstellens\"atze and Applications, to appear in Conference Proceedings Published by Springer.
-In this expository paper, we present simple proofs of the Classical, Real, Projective  and Combinatorial Nullstellens\"atze.
-Several applications are also presented such as a classical theorem of Stickelberger for solutions of polynomial equations in terms of eigenvalues of commuting operators, construction of a principal ideal domain which is not Euclidean, Hilbert's $17^{th}$ problem,  the Borsuk-Ulam theorem in topology and solutions of the conjectures of Dyson, Erd\"{o}s and Heilbronn.
-[2]  (Jointly wit  J.
-K.
-Verma) Rational points and generalized trace forms on a finite algebra over a real closed field, to appear in Conference Proceedings Published by Springer.
-The core of this article is the equality of the number of $K$-rational points  with the signature of the trace form of a finite $K$-algebra over a real closed field $K$.
-The main tools are symmetric bilinear forms, hermitian forms, trace forms, generalized trace forms and their types and signatures.
-Further, we prove a criterion for the existence of $K$-rational points by using generalized trace forms.
-As an application we prove the Pederson-Roy-Szpirglas theorem  about counting common real zeros of  real polynomial equations.
-We also prove deduce this theorem as a special case of a similar classical theorem for real closed fields.
-[3] On the connectedness of the fiber product of two connected finte free affine schemes.
-Preprint.
-This article grew out while studying Burnside algebra of finite abelian groups.
+COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS (Jointly Martin  Kreuzer)   The Burnside ring B(G) of a finite group G, a classical tool in the representation theory of finite groups, is studied from the point of view of computational algebra.
+In the rst part (cf.
+[8]) we examined the ring theoretic properties of B(G) using the methods of computer algebra.
+In this part we shift our focus to important maps between two Burnside rings and make several well-known maps of representation theory explicitly computable.
+The inputs of all our algorithms are the tables of marks of the two groups, and the outputs are matrices of integers representing the maps via their image in the ghost ring.
+All algorithms have been implemented in the computer algebra system ApCoCoA and are illustrated by applying them to explicit examples.
+Especially, we study the restriction and induction maps, the projection and in ation maps, the conjugation isomorphism, and the Frobenius-Wielandt homomorphism.
 
-\subsection{E. K. Narayanan}
+\subsection{E K Narayanan}
 
-Study of Heckman-Opdam hypergeometric functions associated to root systems of type $BC,$ where the associated multiplicity function was allowed to assume negative values, was continued.
+Positivity properties and asymptotics of Heckman-Opdam hypergeometric functions associated to root system to type BC with non-positive multiplicity functions were studied in detail.
 
@@
 
-Further work was undertaken to investigate a weak form of negative curvature --- known as visibility --- exhibited by a range of domains in $\mathbb{C}^n$ equipped with the Kobayashi distance.
-The class of domains that are visibility domains with respect to the Kobayashi distance was significantly broadened in the preprint [1].
-Furthermore, two Wolff--Denjoy-type theorems were established for the latter class of domains.
-[1] Gautam Bharali and Anwoy Maitra, A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems.
+A detailed investigation of the Bergman geometry of domains whose boundaries have isolated infinite-type points was completed.
+Optimal estimates, from above and below, for the growth of the Bergman kernel (on the diagonal) and the Bergman metric, as one approaches an infinite-type boundary point, were obtained.
+The class of domains that were studied subsumes all classes of domains that have previously been considered in the literature.
+These results have appeared in the paper [1].
+[1] Bharali, Gautam, On the growth of the Bergman metric near a point of infinite type, J.
+Geom.
+Anal.
+, 30 (2020), 1238-1258.
 
@@
 
-Detection of a causal relationship between two or more sets of data is an important problem across various scientific disciplines.
-Test statistics based on Granger causality ignore the effect of practical measurement impairments such as subsampling, additive noise, and finite sample effects.
-We modelled [1] the problem of detecting a causal relationship between two time series as a binary hypothesis test with the null and alternate hypotheses corresponding to the absence and presence of a causal relationship, respectively.
-We derived the distribution of the test statistic under the two hypotheses and show that measurement impairments can lead to suppression of a causal relationship between the signals, as well as false detection of a causal relationship, where there is none.
-We also used the derived results to propose two alternative test statistics for causality detection.
-These detectors are analytically tractable, which allowed us to design the detection threshold and determine the number of samples required to achieve a given missed detection and false alarm rate.
-Prostate-associated gene 4 (PAGE4) is an intrinsically disordered protein implicated in prostate cancer.
-Experiments have shown that PAGE4 expands upon hyperphosphorylation and that this expansion is localized to its N-terminal half.
-To understand the interactions underlying this structural transition, we performed [2] molecular dynamics simulations using Atomistic AWSEM, a multi-scale molecular model that combines atomistic and coarse- grained simulation approaches.
-Our simulations show that electrostatic interactions drive transient formation of an N-terminal loop, the destabilization of which accounts for the dramatic change in size upon hyperphosphorylation.
-Finally, we construct a mechanism-based mathematical model that allows us to capture the interactions of different phosphoforms of PAGE4 with AP-1 and its downstream target, the androgen receptor (AR)—a key therapeutic target in prostate cancer.
-Our model predicts intracellular oscillatory dynamics indicating phenotypic heterogeneity in an isogenic cell population.
-Thus, conformational switching of PAGE4 may potentially affect the efficiency of therapeutically targeting AR activity.
-We proposed [3] an application of the microtremor (ambient noise) H/V spectral ratio technique to identify significant rheological boundaries at shallow depths, estimate thickness of both lignite bearing Tertiary sedimentary sequence and late Cretaceous Deccan basalt flows and comprehend basinal geometry of Umarsar Basin (Babia syncline).
-Forty-six stations were gauged in a grid format at ~250 m resolution during the microtremor survey.
-We detected three rheological interfaces.
-Finally, we proposed the microtremor H/V spectral ratio technique as a tool to develop economical borehole plan with realistic reserve estimate and a step forward towards rapid economical assessment covering large mining lease areas.
-[1] IEEE Trans Signal Proc.
-(2018) [2] J.
-Mol.
-Biol (2018) [3] J.
-Appl.
-Geophys.
-(2018)
+We constructed [1] symmetry preserving and symmetry broken N-bright, dark and antidark soliton solutions of a nonlocal nonlinear Schrödinger equation.
+To obtain these solutions, we used appropriate eigenfunctions in Darboux transformation (DT) method.
+Further, we derived two dark/antidark soliton solution with the help of DT method.
+In the dark/antidark soliton solution case we observed a contrasting behaviour between the envelope of the ﬁeld and parity transformed complex conjugate envelope of the ﬁeld.
+For a particular parametric choice, we got dark (antidark) soliton for the ﬁeld while the parity transformed complex conjugate ﬁeld exhibits antidark (dark) soliton.
+Due to this surprising result, both the ﬁeld and PT transformed complex conjugate ﬁeld exhibit sixteen different combinations of collision scenario.
+We presented observational evidence [2] from studies on primary cortical cultures from AD transgenic mice for significant decrease in total spine density at DIV-15 and onward.
+This indicates reduction in potential healthy synapses and strength of connections among neurons.
+Based on this, a network model of neurons was developed, that explains the consequent loss of coordinated activity and transmission efficiency among neurons that manifests over time.
+The critical time when structural connectivity in the brain undergoes a phase-transition, from initial robustness to irreparable breakdown, is estimated from this model.
+We also showed how the global efficiency of signal transmission in the network decreases over time.
+Moreover, the number of multiple paths of high efficiency decreased rapidly as the disease progresses, indicating loss of structural plasticity and inefficiency in choosing alternate paths or desired paths for any pattern of activity.
+Thus loss of spines caused by β-Amyloid (Aβ) peptide results in disintegration of the neuronal network over time with consequent cognitive dysfunctions in Alzheimer’s Disease (AD).
+We investigated [3] the effect of four-wave mixing in the interactions among nonlinear waves such as solitons, breathers, and rogue waves of a coupled generalized nonlinear Schrodinger equation.
+We explored several interesting results including superposition of breather pulses, increment in the number of breather pulses and in amplitudes of breathers, and rogue waves.
+By strengthening the four-wave mixing parameter, we observed different transformations that occur between different localized structures.
+For instance, we visualized a transformation from bright soliton to breather form, bright and dark rogue wave to four-petaled rogue wave structures, four-petaled rogue wave to other rogue wave forms, and so on.
+Another important observation was that the interaction of a bright soliton with a rogue wave in the presence of the four-wave mixing effect provides interaction between a dark oscillatory soliton and a rogue wave.
+[1] Vishnu Priya, N., Senthilvelan, M.,  Rangarajan, G.
+& Lakshmanan, M.
+On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation, Physics Letters A, 383, 15 (2019).
+[2] Kashyap, G.
+A.
+R.
+S.
+R.
+K., Bapat, D., Das, D., Gowaikar, R.
+D., Amritkar, R.
+E., Rangarajan, G., Ravindranath, V.
+& Ambika, G., Synapse loss and progress of Alzheimer’s disease - A network model, Scientific Reports, 9, 6555 (2019).
+[3] Vishnu Priya, N., Senthilvelan, M.
+&  Rangarajan, G, On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, Chaos, 29, 123135 (2019).
+
+\subsection{Hrish Seshadri}
+
+\subsection{Kaushal Verma}
+
+For a given pair of smoothly bounded planar domains $D_1, D_2$, it was shown in \cite{1} that the product of the Carath\'{e}odory metrics on them is bounded from below by the product of the Carath\'{e}odory metrics on their union and intersection up to a multiplicative factor.
+This shows that the S\"{z}ego kernels on $D_1, D_2, D_1 \cap D_2$ and $D_1 \cup D_2$ are related by the same inequality.
+The Suita conjecture in higher dimensions is a paradigm that asks for the limiting boundary values of the product of the Bergman kernel (on the diagonal) and the volume of the Kobayashi indicatrix.
+This object is a biholomorphic invariant and is known to admit universal bounds on convex domains.
+Its limiting behaviour was clarified on strongly peudoconvex domains and egg domains in $\mathbb C^2$.
+See \cite{2}.
+The boundary behaviour of several classical conformal invariants were studied in \cite{3}.
+The relationship between the Fridman invariant and the Squeezing function was clarified in \cite{4}.
+The relation between a pair of H\'{e}non maps that share the same forward and backward Julia sets was clarified in \cite{5}.
+
+\subsection{Mahesh Kakde}
+
+Jointly with Samit Dasgupta from Duke University I resolved the Brumer-Stark conjecture during the said period.
+We spoke about it at the "International Colloquium" in January 2020 in TIFR.
+Further, a paper on higher Chern classes written a while ago (jointly with Frauke Bleher, Ted Chinburg,  Ralph Greenberg, George Pappas, Romyar Sharifi and Martin Taylor) was accepted for publication in American Journal of Mathematics.
 
@@
 
-Working on certain problems on nodal sets of Gaussian random functions and in random matrix theory.
+Completed a study of law of iterated logarithm for last passage percolating on the two dimensional integer lattice [1].
+Other studies on absolute continuity of limiting spectral distributions, a proof of KMT theorems, study of discrete nodal length, a problem on amplitude constrained Gaussian channel and some problems on nodal domains of random functions are in various stages of completion.
+[1] Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation.
+Authors: Riddhipratim Basu, Shirshendu Ganguly, Milind Hegde, Manjunath Krishnapur.
+arXiv:1909.01333
 
@@
 
-We analyze an augmented political business cycle model taking into account the effect of employment creation decisions by the ruling party jointly on inflation and growth.
-The objective is to maximize voter support in the next election that depends on the rate of unemployment as well as that of growth and inflation.
-We allow for randomness in the New Keynesian Phillips Curve (NKPC) model for the relationship between  inflation and unemployment as well as in a benchmark labour productivity function for   analyzing the growth rate.
-We provide explicit solution paths of the affine Markov   control problem that results from our formulation.
-We also provide numerical illustrations with plausible parametric configurations to generate more insight into our model.
-[1] G.
-K.
-Basak, M.
-K.
-Ghosh and D.
-Mukherjee, A Stochastic Model with Inflation, Growth and Technology  for the Political Business Cycle, J.
-Computational Economics, 53 (2019), 125-140.
+Risk-sensitive stochastic differential games have been studied in the nonnegative orthant [1] and the whole space [2]. Existence of saddle point/Nash equilibria for relevant cases have been derived.
 
-\subsection{Pooja Singla}
+\subsection{Purvi Gupta}
 
-In [1], We study some irreversible Markov chains on finite commutative rings randomly generated using both addition and multiplication.
-We describe the eigenvalues and their multiplicities.
-We also prove recursive formulas for stationary distribution.
-We extend this work to finite non-commutative rings in [2].
-In [3], the Gelfand-Whittaker model for $GL_n(O)$ and $SL_n(O)$,where $O$ is a  compact discrete valuation ring is studied.
-We proved that this model is multiplicity free and describe its constituents.
-In [4] We describe the abscissa of convergence of representation zeta function of $SL_2(O)$ for a compact discrete valuation ring $O$ with even characteristic.
-For this case, we also give construction of continuous primitive irreducible representations and study group algebra isomorphism problem.
-[1].
-Random motion on finite rings, I: commutative rings, Arvind Ayyer and Pooja Singla, to appear in Algebras and Representation Theory.
-[2].
-Random motion on finite rings, II: Non-commutative rings; Arvind Ayyer and Pooja Singla, preprint.
-[3].
-A multiplicity one theorem for groups of type $A_n$ over discrete valuation rings, Shiv Prakash Patel and Pooja Singla, preprint.
-[4].
-Representation Growth of Special Compact Linear Groups of Order Two,  M.
-Hassain and Pooja Singla, preprint.
+Note: this description is for research carried out during the period February 11, 2020 (date of joining) to March 31, 2020.
+In this period,  I completed and submitted a manuscript ([1]),  based on joint work with C.
+U.
+Wawrzyniak.
+This work studies the stability of the solution of the so-called global Bishop problem (a plateau-type problem) for a model real $n$-dimensional sphere in $\mathbb{C}^n$, $n\geq 2$.
+In this problem, the solution is required, among other things, to be foliated by holomorphic disks (i.e., Levi-flat) attached to the given sphere.
+This structure is significant in complex analysis for multiple reasons.
+The general Bishop problem, although very well-understood in two (complex) dimensions, is wide open in dimensions three and higher, and our work is the first global result in this direction.
+References [1] Gupta, Purvi and Wawrzyniak, Chloe Urbanski, Stability of the hull(s) of an $n$-sphere in $\mathbb{C}^n$.
+Submitted.
+
+\subsection{R VENKATESH}
+
+(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases G = E_6,7,8 and F_4 and thus completed the main theorems of the papers of V.
+Chari and et al., (J.
+Algebra, 2016) and Deniz Kus and et al., (Represent.
+Theory., 2016).
+Obtained a new combinatorial proof for the key fact that was used in  V.
+Chari and et al., (J.
+Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules.
+This key fact was proved only for the cases when G is the classical type and G_2 in their paper and they also proved it by analysing case-by-case.
+Our proof is uniform avoids the case-by-case analysis and works for all finite-dimensional simple Lie algebras.
+(b) Simplified the presentation of all affine Demazure modules of untwisted affine Kac–Moody Lie algebras.
+Simplifying the generators and relations of these modules is very crucial in their study.
+We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.
+(c) A number of conjectures made about the graded characters affine Demazure modules of affine sl_3 using data obtained from SAGE.
 
@@
 
-By improving some earlier work of Felikson, Retakh and Tumarkin, a classification of all the regular subalgebras of Affind Kac-Moody Lie algebras have been obtained.
-By continuing this classification problem to Extend Affine Lie Algebras which are natural generalizaion of Affine Kac-Moody algebras, a classification of all the maximal closed sub-root systems of Affine reflection systems has also been done.
-The question of when two tensor products of irreducible integrable representations would be isomorphic to another for Borcherds-KacMoody algebras has been investigated.
+(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases G = E_6,7,8 and F_4 and thus completed the main theorem of the paper of V.
+Chari and et al., (J.
+Algebra, 2016).
+Obtained a new combinatorial proof for the key fact that was used in  V.
+Chari and et al., (J.
+Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules.
+This key fact was proved by V.
+Chari and et al., (J.
+Algebra, 2016) only for the cases when G is the classical types and G_2 and they did a case-by-case analysis to prove this.
+Our new proof is very uniform and avoids the case-by-case analysis and works in general.
+(b) Simplified the presentation of all affine Demazure modules of untwisted affine Kac–Moody Lie algebras.
+Simplifying the generators and relations of these modules is very crucial in their study.
+We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.
+(c) A number of conjectures made about the graded characters affine Demazure modules of affine sl_3 using data obtained from SAGE.
+
+\subsection{RADHIKA GANAPATHY}
+
+1) Let $G$ be a split connected reductive group over $\mathbb{Z}$.
+Let $F$ be a non-archimedean local field.
+With $K_m := Ker(G(O_F ) → G(O_F /p_{m,F} ))$, Kazhdan proved that for a field $F′$ sufficiently close to $F$, the Hecke algebras $\mathcal{H}(G(F), K_m)$ and $\mathcal{H}(G(F′), K_m′ )$ are isomorphic, where $K_m′$ denotes the corresponding object over $F′$.
+I have generalized this result to general connected reductive groups [1].
+2) In my earlier work, I had established  a variant of the Kazhdan isomorphism for split reductive groups (by replacing $K_m$ replaced by the $m$-th filtration subgroup of the Iwahori subgroup).
+I have been working on generalising this result to general connected reductive groups.
+As part of this work, I have chosen a nice set of representatives in $G(F)$ for the elements of the extended affine Weyl group.
+This set of representatives has some very interesting properties (for instance, it is compatible with unramified descent), and is useful in the study of representation theory of $p$-adic groups.
+[1] A Hecke algebra isomorphism over close local fields, preprint, 12 pages.
 
@@
 
-In [1], the critical behavior of the component sizes for the configuration model has been studied when the tail of the degree distribution of a uniform vertex is a regularly-varying function with exponent $\tau -1$, where $\tau\in (3, 4)$.
-In [2], the metric space scaling limits of the minimal spanning trees of both the random (simple) 3-regular graph and the 3-regular configuration model have been established, and it has been shown that both these models belong to the universality class identified in the work of Addario-Berry, Broutin, Goldschmidt, and Miermont [Annals of Probability, 2017].
-[1] Heavy-tailed configuration models at criticality.
-Authors: Souvik Dhara, Remco van der Hofstad, Johan van Leeuwaarden, Sanchayan Sen.
-Annales de l'Institut Henri Poincaré (B) Probabilités et Statistiques.
-Accepted in March 2019.
-[2] Geometry of the minimal spanning tree of a random 3-regular graph.
-Authors: Louigi Addario-Berry, Sanchayan Sen ArXiv preprint.
-Announced in October 2018.
+In [1], we provide an explicit algorithm for sampling a uniform simple connected random graph with a given degree sequence.
+By products of this central result includes scaling limits for the metric space structure of the maximal components in the critical regime of both the configuration model and the uniform simple random graph model with prescribed degree sequence under finite third moment assumption on the degree sequence.
+As a substantive application we answer a question raised by Černý and Teixeira, Random Structures Algorithms (2013), by obtaining the metric space scaling limit of maximal components in the vacant set left by random walks on random regular graphs.
+In [2], we study limits of the largest connected components (viewed as metric spaces) obtained by critical percolation on uniformly chosen graphs and configuration models with heavy-tailed degrees.
+We develop general principles under which the scaling limits can be obtained.
+Of independent interest, we derive refined asymptotics for various susceptibility functions and the maximal diameter in the barely subcritical regime.
+In [3], we give alternate constructions of (i) the scaling limit of the uniform connected graphs with given fixed surplus, and (ii) the continuum random unicellular map of a given genus that start with a suitably tilted Brownian continuum random tree and make `horizontal' point identifications, at random heights, using the local time measures.
+In particular, this yields a breadth-first construction of the scaling limit of the critical Erdős-Rényi random graph which answers a question posed by Addario-Berry, Broutin, and Goldschmidt, Probab.
+Theory Related Fields (2012).
+As a consequence of this breadth-first construction we obtain descriptions of the radii, the distance profiles, and the two point functions of these spaces in terms of functionals of tilted Brownian excursions.
+[1] Geometry of the vacant set left by random walk on random graphs, Wright's constants, and critical random graphs with prescribed degrees Authors: Shankar Bhamidi, Sanchayan Sen Journal: Random Structures & Algorithms (First published on 25 July 2019)  [2] Universality for critical heavy-tailed network models: Metric structure of maximal components Authors: Shankar Bhamidi, Souvik Dhara, Remco van der Hofstad, Sanchayan Sen Journal: Electronic Journal of Probability (Accepted in December 2019)  [3] On breadth-first constructions of scaling limits of random graphs and random unicellular maps Authors: Grégory Miermont, Sanchayan Sen ArXiv preprint https://arxiv.org/abs/1908.04403 (Announced in August 2019)
 
@@
 
-We refined our previous results where, as part of the PolyMath 14 project, we had classified homogeneous length functions on groups.
-In particular we showed that quasi-homogeneous length functions on groups with vanishing commutator length (such as solvable groups) are bounded distance from pullbacks from Abelianizations.
-We also replicated and made robust the computer-assisited proof we had found in the course of the above mentioned PolyMath project and investigated general principles involved.
-We further developed methods for computer assisted theorem proving.
+We continued our development of automated theorem proving systems.
+Specifically, we developed a framework based on equation terms to allow accumulation of knowledge and facilitate deep learning and hybrid autonomous/interactive execution.
 
@@
 
-We continue our investigations on analytic aspects of Automorphic forms.
+Work on the determination of Siegel modular forms by their fundamental Fourier coefficients was done including a mod p version.
+Study of Fourier coefficients and sup-norms of modular forms was continued.
 
-\subsection{Srikanth K. Iyer}
+\subsection{Srikanth Krishnan Iyer}
 
-The random connection model is studied in the connectivity regime.
-Strong law results for the critical scaling parameter required to eliminate isolated nodes is derived.
-A sufficient condition for the graph to be connected with high probability is obtained.
-Other results include strong law results for the maximum and minimum vertex degrees [1].
-The capacity of a wireless cellular network is defined and an exact characterization (non-asymptotic) of this natural capacity metric is derived.
-It is shown that that the capacity increases polynomially with the base station (BS) density in the low BS density regime and then scales inverse exponentially with the increasing BS density [2].
-A model of merge and split group dynamics, also called fission-fusion dynamics, for heterogeneous populations that contain two types (or species) of individuals is proposed and analysed.
-It is predicted using the analytical model that there is a critical group size below which groups are more likely to be homogeneous and contain the abundant type or species.
-Despite the propensity of heterogeneous groups to split at higher rates, we find that groups are more likely to be heterogeneous but only above the critical group size.
-Monte Carlo simulation of the model show excellent agreement with these analytical model results.
-The implications of our results to empirical studies on flocking systems are discussed [3].
+We study combinatorial connectivity for two models of random geometric complexes.
+These two models - \v{C}ech and Vietoris-Rips complexes - are built on a homogeneous Poisson point process of intensity $n$ on a $d$-dimensional torus, $d > 1$, using balls of radius $r_n$.
+Given a (simplicial) complex (i.e., a collection of $k$-simplices for all $k \geq 1$), we can connect $k$-simplices via $(k+1)$-simplices (`up-connectivity') or via $(k-1)$-simplices (`down-connectivity).
+Our interest is to understand these two combinatorial notions of connectivity for the random \v{C}ech and Vietoris-Rips complexes asymptotically as $n \to \infty$.
+Our results give tighter bounds on the constants in the logarithmic scale as well as shed light on the possible second-order correction factors.
+Further, they also reveal interesting differences between the phase transition in the \v{C}ech and Vietoris-Rips cases.
+The analysis is interesting due to non-monotonicity of the number of isolated $k$-faces (as a function of the radius) and leads one to consider `monotonic' vanishing of isolated $k$-faces.
+The latter coincides with the vanishing threshold mentioned above at a coarse scale (i.e., $\log n$ scale) but differs in the $\log \log n$ scale for the \v{C}ech complex with $k = 1$ in the up-connected case.
+For the case of up-connectivity in the Vietoris-Rips complex and for $r_n$ in the critical window, we also show a Poisson convergence for the number of isolated $k$-faces when $k \leq d$.
+[1]
 
@@
 
-The main focus of my research during this period was in developing a correspondence between meromorphic quadratic differentials and certain geometric structures on punctured Riemann surfaces.
-Some of this work arose out of an effort to understand how such ``meromorphic" geometric structures arise in degenerations, in the context of hyperbolic structures. Other collaborative projects during this period that resulted in papers include a project with Basudeb Datta (IISc), on understanding geometric tilings of the hyperbolic plane, and work with Indranil Biswas (TIFR Mumbai) and Sorin Dumitrescu (CNRS, France) that concerns branched projective structures on Riemann surfaces.   Papers written or published during this period:  [1]   (with Michael Wolf)  Meromorphic quadratic differentials and measured foliations on a Riemann surface, Mathematische Annalen, Vol.
-373 1-2,  (February 2019), pg.
-73-118.
-[2]  Limits of harmonic maps and crowned hyperbolic surfaces, accepted for publication , Transactions of the AMS,  available at  https://doi.org/10.1090/tran/7777.
-[3]  Holomorphic quadratic differentials in Teichmüller theory,  to appear, Handbook of Teichmüller theory Vol VII, available at  http://arxiv.org/abs/1902.06406.
-[4] (with Basudeb Datta)  Uniform tilings of the hyperbolic plane,  submitted, available at http://arxiv.org/abs/1806.11393.
-[5] (with Indranil Biswas and Sorin Dumitrescu) Branched projective structures on a Riemann surface and logarithmic connections, submitted, available at http://arxiv.org/abs/1808.04555.
+(1) With Mahan Mj (TIFR)  we completed a  research program concerning meromorphic projective structures on surfaces and their monodromy representations.
+We used new  work of Allegretti-Bridgeland, together with older ideas of Thurston, to develop a geometric understanding of these structures on punctured surfaces, and prove analogues of results of Hejhal and Gallo-Kapovich-Marden -- see [1] and [2].
+In an independent paper [3], I used our the techniques we had developed, to shed light on a remark of Poincaré in 1883.
+This complemented other projects concerning meromorphic quadratic differentials (see [8] and [10]).
+(2) In joint work [4] with Indranil Biswas (TIFR), Mahan Mj (TIFR) and Junho Whang (MIT), we classified the finite mapping class group orbits in the PSL(2,C) character variety.
+(3) In a project with Basudeb Datta (IISc) we revised and published a paper [5] developing an algorithmic technique of constructing semi-regular tilings of the hyperbolic plane.
+We expect this to have an impact on tilings-related research, which is an active area that has an intersection with several fields like combinatorics, computational geometry and group theory.
+(4)  With Harish Seshadri (IISc) we wrote a paper [6], and a survey [7], concerning the complex geometry of Teichmüller spaces, where we investigated the convexity (or lack thereof) of the boundary of complex domains biholomorphic to Teichmüller space.
+We have ongoing conversations regarding other questions that lie at the intersection of several complex variables, differential geometry and Teichmüller theory.
+(5) A paper with Indranil Biswas (TIFR) and Sorin Dumitrescu (UCA)  concerning branched projective structures on surfaces was published [9].
+In an ongoing project, we aim to understand the symplectic geometry of the space of such structures better.
+[1] Meromorphic projective structures, grafting and the monodromy map, submitted, available at http://arxiv.org/abs/1904.03804.
+[2] Monodromy representations of meromorphic projective structures, Proc.
+Amer.
+Math.
+Soc.
+148 (2020), no.
+5, 2069–2078.
+[3] Monodromy groups of CP1-structures on punctured surfaces, submitted, available at https: //arxiv.org/abs/1909.10771.
+[4] Surface group representations in SL(2,C) with finite mapping class orbits, submitted, available at https://arxiv.org/ abs/1707.00071.
+[5] Semi-regular tilings of the hyperbolic plane, to appear, Discrete and Computational Geometry (2019), available at https://doi.org/10.1007/s00454-019-00156-0.
+[6] On domains biholomorphic to Teichmüller spaces, International Mathematics Research Notices, Volume 2020, Issue 8, (2020), 2542–2560.
+[7] Complex geometry of Teichmüller domains, Handbook of Teichmüller theory Vol VII, 63–88, IRMA Lect.
+Math.
+Theor.
+Phys., 30, Eur.
+Math.
+Soc., Zürich, 2020.
+[8] Holomorphic quadratic differentials in Teichmüller theory, Handbook of Teichmü ller theory Vol VII, 2020.
+[9] Branched projective structures on a Riemann surface and logarithmic connections, Documenta Mathematica 24 (2019), 2299–2337.
+[10] Limits of harmonic maps and crowned hyperbolic surfaces, Trans.
+Amer.
+Math.
+Soc.
+372 (2019), no.
+11, 7573–7596.
 
@@
 
-We have obtained sparse bounds for the lacunary maximal function associated to spherical means on the Heisenberg group [1].
-As a consequence we have obtained an analogue of a result of C.
-P.
-Calderon for the lacunary spherical maximal function on Euclidean spaces.
+In a joint work with Pritam Ganguly  we have investigated the $ L^p $  boundedness of the lacunary maximal function $ M_{\H^n}^\lac $ associated to the spherical means $ A_r f$  taken over Koranyi spheres on the Heisenberg group.
+Closely following an approach used by M.
+Lacey in the Euclidean case, we obtain sparse bounds for these maximal functions leading to new unweighted and weighted estimates.
+The key ingredients in the proof are the $L^p$  improving property of the operator $ A_r $  and a continuity property of the difference $ A_r f−\tau_y A_r f,$ where $\tau_yf(x)=f(xy−1) $ is the right translation operator.
+
+\subsection{Thirupathi Gudi}
+
+We have developed a Hybrid High Order methods for elliptic obstacle problem in both two and three space dimensions allowing general meshes.
+The gap in literature of developing an optimal order convergent method using quadratic finite element method is resolved under the realistic regularity.
+In another work, we derived optimal order finite element analysis for constrained Dirichlet boundary optimal control problem.
+We have also studied numerous finite element methods for parabolic obstacle problem under the realistic regularity.
 
@@
 
-My research for the relevant period has been on Toeplitz operators.
-An easily computable and simple condition which is necessary and sufficient for a commuting tuple of contractions to possess a non-zero Toeplitz operator has been found.
-This condition is just that the adjoint of the product of the contractions is not pure.
-On one hand, this brings out the importance of the product of the contractions and on the other hand, the non-pureness turns out to be equivalent to the existence of a pseudo-extension to a tuple of commuting unitaries.
-A commutant pseudo-extension theorem has been obtained by studying the unique canonical unitary pseudo-extension of a tuple of commuting contractions.
-Also, with the help of a special completely positive map, a different proof of the existence of the unique canonical unitary pseudo-extension is given.
-On a different note, an extensive theory of Toeplitz operators on the symmetrized bidisc has been developed.
+1.
+Distinguished varieties:  A distinguished algebraic variety in $\mathbb{C}^2$ has been the focus of much research in recent years because of good reasons.
+We have given a different perspective.
+\begin{enumerate}  \item We have found a new characterization of an algebraic variety $\mathcal W$ which is distinguished with respect to the bidisc.
+It is in terms of the joint spectrum of a pair of commuting linear matrix pencils.
+\item There is a characterization known of $\mathbb{D}^2\cap\mathcal{W}$ due to a seminal work of Agler and McCarthy.
+We have shown that Agler--McCarthy characterization can be obtained from the new one and vice versa.
+\item En route, we develop a new realization formula for operator-valued contractive analytic functions on the unit disc.
+\item There is a one-to-one correspondence between operator-valued contractive holomorphic functions and {\em canonical model triples}.
+This pertains to the new realization formula mentioned above.
+\item Pal and Shalit gave a characterization of an algebraic variety, which is distinguished with respect to the symmetrized bidisc, in terms of a matrix of numerical radius no larger than $1$.
+We refine their result by making the class of matrices strictly smaller.
+\item In a generalization in the direction of more than two variables, we have characterized all one-dimensional algebraic  varieties which are distinguished  with respect to the polydisc.
+\end{enumerate} At the root of our work is the Berger--Coburn--Lebow theorem characterizing a commuting tuple of isometries.
+This work is in [1].
+2.
+We have studied the action of the automorphism group of the $2$ complex dimensional manifold symmetrized bidisc $\mathbb G$ on itself.
+The automorphism group is $3$ real dimensional.
+It foliates $\mathbb G$ into leaves all of which are $3$ real dimensional hypersurfaces except one, viz., the royal variety.
+This leads us to investigate Isaev's classification of all Kobayashi-hyperbolic $2$ complex dimensional  manifolds for which the group of holomorphic automorphisms has real dimension $3$ studied by Isaev.
+Indeed, we produce a biholomorphism between the symmetrized bidisc and the domain  \[\{(z_1,z_2)\in \mathbb{C} ^2 : 1+|z_1|^2-|z_2|^2>|1+ z_1 ^2 -z_2 ^2|, Im(z_1 (1+\overline{z_2}))>0\}\]  in Isaev's list.
+Isaev calls it $\mathcal D_1$.
+The road to the biholomorphism is paved with various geometric insights about $\mathbb G$.
+Several consequences of the biholomorphism follow including two new characterizations of the symmetrized bidisc and several new characterizations of $\mathcal D_1$.
+Among the results on $\mathcal D_1$, of particular interest is the fact that $\mathcal D_1$ is a ``symmetrization''.
+When we symmetrize (appropriately defined in this context) either $\Omega_1$ or $\mathcal{D}^{(2)} _1$ (Isaev's notation), we get $\mathcal D_1$.
+These two domains $\Omega_1$ and $\mathcal{D}^{(2)} _1$ are in Isaev's list and he mentioned that these are biholomorphic to $\mathbb D \times \mathbb D$.
+We produce explicit biholomorphisms between these domains and $\mathbb D \times \mathbb D$.
+This work is in [2].
+[1]  Distinguished Varieties Through the Berger--Coburn--Lebow Theorem,  co-authored with P.
+Kumar and H.
+Sau.
+Submitted to journal and arXiv link is https://arxiv.org/pdf/2001.01410.pdf   [2] An unbounded realization of the symmetrized bidisc, co-authored with A.
+Biswas and A.
+Maitra.
+Submitted to journal and arXiv link is  https://arxiv.org/pdf/2005.00289.pdf
 
@@
 
-I worked on three themes : 1) Connections on holomorphic vector bundles : Along with I.
-Biswas [1], I studied the differential geometry of parabolic ample bundles and connected it with the known algebro-geometric results.
-I introduced a vector bundle Monge-Ampere equation in a preprint [2] and proved some existence results for it.
-2) Coupled PDE on Kahler manifolds : Along with Ved Datar, I studied coupled cscK equations and provided a moment map interpretation in a preprint [3].
-3) Interpolation : D.
-Varolin and I [4] provided examples and counterexamples of affine algebraic interpolating manifolds.
-[1] I.
-Biswas and V.
-Pingali.
-Metric properties of parabolic ample bundles, International Mathematical Research Notices, Nov 2018 (published online - doi:10.1093/imrn/rny259).
-[2] V.
-Pingali.
-A vector bundle version of the Monge-Ampere equation, arXiv : 1804.03934, Apr 2018.
-[3] V.
-Datar and V.
-Pingali.
-On coupled constant scalar curvature Kahler metrics (with Ved Datar), arXiv : 1901.10454, Jan 2019.
-[4] V.
-Pingali and D.
-Varolin.
-Nonuniformly flat affine algebraic hypersurfaces, arXiv : 1810.00895, Oct 2018.
-(Accepted for publication in Nagoya Mathematical Journal -  https://doi.org/10.1017/nmj.2019.2)
+My research during this period involved proving existence results for geometric PDE conditioned on some necessary and sufficient conditions.
+In [1], the dHYM equation on three-folds was studied, and in [2] we proved an existence result for the gravitating vortex equation conditioned on a GIT stability condition.
+In addition, some earlier works [3],[4],[5],[6] were accepted/published during this period.
+[1] Pingali, Vamsi Pritham.
+"The deformed Hermitian Yang-Mills equation on three-folds." arXiv preprint arXiv:1910.01870 (2019).
+[2] Garcia-Fernandez, Mario, Vamsi Pritham Pingali, and Chengjian Yao.
+"Gravitating vortices with positive curvature." arXiv preprint arXiv:1911.09616 (2019).
+[3] PINGALI, V., & VAROLIN, D.
+(2019).
+NONUNIFORMLY FLAT AFFINE ALGEBRAIC HYPERSURFACES.
+Nagoya Mathematical Journal, 1-43.
+doi:10.1017/nmj.2019.2 (Published online on 2 April  2019) [4] Pingali, Vamsi Pritham.
+"A vector bundle version of the Monge-Ampère equation." Advances in Mathematics 360 (2020): 106921.
+(Published online on 22 January 2020) [5] Álvarez-Cónsul, Luis, Mario Garcia-Fernandez, Oscar García-Prada, and Vamsi Pritham Pingali.
+"Gravitating vortices and the Einstein–Bogomol’nyi equations." Mathematische Annalen (2020): 1-34.
+(Published online on 20 February 2020) [6] Pingali, Vamsi Pritham.
+"Quillen metrics and perturbed equations." Letters in Mathematical Physics (2020): 1-15.
+(Published online on 5 March 2020)
+
+\subsection{Ved Datar}
+
+In collaboration with Vamsi Pingali [1],  a numerical criteria for the existence of solutions to generalised Monge-Ampere equations is obtained  on projective manifolds.
+The class of equations studied encompasses certain well known equations such as the $J$-equation and the inverse Hessian equations.
+In particular, this extends and strengthens the deep result of Gao Chen on the $J$-equation, and also resolves a well-known conjecture of Gabor Szekelyhidi.
+In a collaboration with Xin Fu and Jian Song [2], Kahler-Einstein metrics were constructed in the neighbourhoods of isolated log-canonical singularities, and the asymptotics to certain local models were studied.
+This builds on a program initiated by Kobayashi and others.
+In a joint project with Harish Seshadri, a conjecture on the almost rigidity of the complex projective space has been formulated, and is being studied.
+If solved, this would be a Kahler analog of a famous theorem of Tobias Colding on the almost rigidity of the sphere.
+While some preliminary results have been obtained, this is still work in progress.
+[1] (with Vamsi Pingali) A numerical criterion for generalised Monge-Ampere equations on projective manifolds, arXiv:2006.01530 [2] (with Xin Fu and Jian Song) On the Kahler-Einstein metric near isolated log-canonical singularity,  in  preparation\subsection{Ramesh Manna}
+
+\subsection{Safdar Quddus}
+
+Working on Equivariant Gauss Manin connection(joint with Chakraborty and Tang), one preprint.
+
+\subsection{Bikramaditya Sahu}
+
+A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd [1]  [1] P.
+Pradhan and Bikramaditya Sahu, A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q),q odd, Discrete Mathematics 343, (2020), 112044.
+(LINC) https://www.sciencedirect.com/science/article/pii/S0012365X20302302?dgcid=author
+
+\subsection{Arun Maiti}
+
+Tiling of hyperbolic surfaces
+
+\subsection{Anirudha Poria}
+
+Given a positive weight function and an isometry map on a Hilbert spaces $\mathcal{H}$, we studied a class of linear maps which is a $g$-frame, $g$-Riesz basis and a $g$-orthonormal basis for  $\mathcal{H}$ with respect to $\mathbb{C}$ in terms of the weight function.
+We applied these results to study the frame for shift-invariant subspaces on the Heisenberg group in [1].
+We established a few uncertainty principles for the Fourier and the short-time Fourier transforms.
+Also, we discussed an analogue of Donoho--Stark uncertainty principle and provided some estimates for the size of the essential support of the short-time Fourier transform in  [2].
+We established the Cowling-Price's, Hardy's and Morgan's uncertainty principles for the Opdam-Cherednik transform on modulation spaces associated with this transform in [3].
+[1] A.
+Poria, Positive weight function and classification of g-frames, Numer.
+Funct.
+Anal.
+Optim.
+41(8): 950--968 (2020).
+[2] A.
+Poria, Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms, preprint arXiv:2004.04184 (2020).
+[3] A.
+Poria, Uncertainty principles for the Opdam-Cherednik transform on modulation spaces, preprint arXiv:2005.14274 (2020).
+
+\subsection{Gopal Datt}
+
+The concept of meromorphic normality was studied with the aim of improving known results and establishing new sufficient conditions for a family of meromorphic mappings on a domain in $\mathbb{C}^m$ into some complex projective space to be meromorphically normal.
+Meromorphic normality is a notion of sequential compactness, introduced by Fujimoto, for the space of meromorphic mappings of a domain in $\mathbb{C}^m$ into a complex projective space.
+One of the central results of our paper [1], currently under peer-review, is as follows:  \begin{theorem}  Let $D$ be a domain in $\mathbb{C}^m$.
+Let $\mathcal{F}$ be a family of meromorphic mappings from $D$ into $\mathbb{P}^n$, $\mathcal{G}$ a family of holomorphic mappings from $D$ into $\mathbb{P}^n$, and $\mathcal{H}$ a collection of hyperplanes in $\mathbb{P}^n$.
+Suppose that, for each $f\in\mathcal{F}$, there exist a $g_f\in\mathcal{G}$ and a subset  $\{H_{1,\,f},\ldots,\,H_{2n+1,\,f}\}\subset \mathcal{H}$ such that   \begin{enumerate}    \item[$(a)$]  $f(D)\not\subset H_{k,\,f}$ for $k=\,1,\ldots,\,2n+1$;       \item[$(b)$] $\inf\{D(H_{1,\,f},\dots, H_{2n+1,\,f}): f\in\mathcal{F}\}>0$; and       \item[$(c)$] $\mathsf{supp}\,\nu(f, H_{k,\,f})\subseteq g_f^{-1}(H_{k,\,f})$        for $k=\,1,\ldots,\,2n+1$.
+\end{enumerate} Furthermore, assume that for any mapping in the closure of $\mathcal{G}$, its range is not a subset of any hyperplane in the closure of $\mathcal{H}$.
+If $\mathcal{G}$ is normal, then $\mathcal{F}$ is meromorphically normal.
+\end{theorem}  The objects $\mathsf{supp}\,\nu(f, H_{k,\,f})$ refer to the support of certain non-negative divisors; these can be thought of as the sets $f^{-1}(H_{k,\,f}); g^{-1}(H_{k,\,f})" respectively.
+1.
+G.
+Datt, Meromorphically normal families in several variables, submitted for publication.
+(A version of this article is available in arXiv with the title "Meromorphically normal families and a meromorphic Montel--Carath{\'e}odory theorem", arXiv:1812.0581)
+
+\subsection{Sudip Bera}
+
+Combinatorics
+
+\subsection{Kiran Kumar Behera}
+
+I worked on linear combinations of certain class of orthogonal polynomials called polynomials of $R_I$ type.
+Conditions were derived under which these linear combinations are again of $R_I$ type.
+In case they are not, they are shown to be related to another class of polynomials which are orthogonal with respect to a measure supported on the unit circle and having zeros of modulus one [1].
+Thereafter, I began work on linear pencil matrix with Dr.
+Maxim Derevyagin  (University of Connecticut, USA) with a goal to obtain finite and infinite generalizations of a scalar parameter used in the theory of orthogonal polynomials.
+This manuscript is in progress.
+[1].
+K.
+K.
+B., Self-inversive polynomials from rational transformation of linear         functionals.
+Communicated.
+Available at arxiv.org/abs/1909.12548
+
+\subsection{Sumana Hatui}
+
+In [1], we explicitly computed Schur multiplier of special p-groups of rank 2.
+In [2], we study the Schur multiplier of the discrete as well as the finite Heisenberg groups and their t-variants.
+We describe the representation groups of these Heisenberg groups and through these give a construction of their finite dimensional complex projective irreducible representations.
+[1] Sumana Hatui, Schur multipliers of special p-groups of rank 2, Journal of Group Theory, 23 (2020), 85-95.
+doi: 10.1515/jgth-2019-0045 [2] Sumana Hatui, Pooja Singla, On Schur multiplier and Projective representations of Heisenberg groups, (Submitted) arXiv:1909.06589 .
+
+\subsection{Anwoy Maitra}
+
+I worked on the problem of the continuous extension of isometries with respect to the Kobayashi distance in several complex variables.
+In particular, in the paper [1], I proved a generalization of an existing result [2, Theorem 2.18] of A.
+Zimmer.
+[1] Anwoy Maitra, On the continuous extension of Kobayashi isometries, Proc.
+Amer.
+Math.
+Soc.
+148 (2020), 3437--3451.
+[2] Andrew M.
+Zimmer, Characterizing domains by the limit set of their automorphism group, Adv.
+Math.
+308 (2017), 438--482.
+
+\subsection{Samrat Sen}
+
+I have worked on generalizing a kernel decomposition theorem of Hilbert modules in $\mathcal{B}_1(\Omega)$.
+With this generalization, I have produced geometric(unitary) invariants of a certain class of submodules of analytic Hilbert modules.
+I have also shown that an alternating sum of currents is a similarity invariant of these classes of submodules.
+
+\subsection{Dr. Srijan Sarkar}
+
+\begin{document}  Let $T = (T_1, \ldots, T_n)$ be a commuting tuple of bounded linear operators on a Hilbert space $\mathcal{H}$.
+The multiplicity of $T$ is the cardinality of a minimal generating set with respect to $T$ and is denoted by $\mbox{mult}_{T}(\mathcal{H})$.
+In the paper \cite{CSS}, we have established an additive formula for multiplicities of a class of commuting tuples of operators.
+A special case of the main result states the following: Let $n \geq 2$, and let $\mathcal{Q}_i$, $i = 1, \ldots, n$, be a proper closed shift co-invariant subspaces of the Dirichlet space or the Hardy space over the unit disc in $\mathbb{C}$.
+If $\mathcal{Q}_i^{\perp}$, $i = 1, \ldots, n$, is a zero-based shift invariant subspace, then the multiplicity of the joint $M_{\bm z} = (M_{z_1}, \ldots, M_{z_n})$-invariant subspace $(\mathcal{Q}_1 \otimes \cdots \otimes \mathcal{Q}_n)^{\perp}$ of the Dirichlet space or the Hardy space over the unit polydisc in $\mathbb{C}^n$ is given by \[ \mbox{mult}_{M_{\bm z}|_{ (\mathcal{Q}_1 \otimes \cdots \otimes \mathcal{Q}_n)^\perp}} \big((\mathcal{Q}_1 \otimes \cdots \otimes \mathcal{Q}_n)^\perp \big) = \sum_{i=1}^n (\mbox{mult}_{M_z|_{\mathcal{Q}_i^{\perp}}} (\mathcal{Q}_i^{\perp})) = n.
+\] A similar result holds for the Bergman space over the unit polydisc.
+\begin{thebibliography}{99}  \bibitem{CSS} Chattopadhyay A., Sarkar J.
+and Sarkar S., {\em Multiplicities, invariant subspaces and an additive formula}, https://arxiv.org/abs/1812.05435.
+\end{thebibliography}   \end{document}
+
+\subsection{Projesh Nath Choudhury}
+
+(1)  N-matrices are real $n\times n$ matrices all of whose principal  minors are negative.
+We provide (i) an $O(2^n)$ test to detect whether or not a given matrix is an N-matrix, and (ii) a characterization of N-matrices, leading to the recursive construction of every N-matrix.
+(2) Matrices with the property that the real part is positive definite, have been studied for the past five decades or more.
+Many results in the form of inequalities have been obtained for matrices possessing this property.
+In this joint work, a new class of matrices, viz., matrices whose real part is positive semidefinite, is considered, wherein extensions of the results in the literature are obtained.
+
+\subsection{Sneh Bala Sinha}
+
+[1] Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala ,On Baker's Explicit $abc$-conjecture,  Publ.
+Math.
+Debrecen 94 (2019), no.
+3-4, 435–453.
+We derived from Baker's explicit $abc$-conjecture that $a+b=c$ where $a$, $b$ and $c$ are relatively prime positive integers %\eqref{eq_OM}  implies that $c < N^{1.72}$ for $N \geq 1$ and $c < 32 N^{1.6}$ for $N \geq 1$.
+This sharpens an estimate of Laishram and Shorey.
+We also show that it implies $c < \frac{6}{5}N^{1+G(N)} $ for $N \geq 3$ and $c < \frac{6}{5}N^{1+G_1(N)}$ for $N \geq 297856$ where $G(N)$ and $G_1(N)$ are explicitly given positive valued decreasing functions of $N$ tending to zero as $N$ tends to infinity.
+Finally we give applications of our estimates on  triples of consecutive powerful integers and generalized Fermat equation.
+
+\subsection{Gouranga Mallik}
+
+The Morley finite element method (FEM) is attractive for semilinear problems with the biharmonic operator as a leading term in the stream function vorticity formulation of two-dimensional Navier–Stokes problem and in the von Kármán equations.
+This paper establishes a best-approximation a priori error analysis and an a posteriori error analysis of discrete solutions close to an arbitrary regular solution on the continuous level to semilinear problems with a trilinear nonlinearity.
+The analysis avoids any smallness assumptions on the data, and so has to provide discrete stability by a perturbation analysis before the Newton–Kantorovich theorem can provide the existence of discrete solutions.
+An abstract framework for the stability analysis in terms of discrete operators from the medius analysis leads to new results on the nonconforming Crouzeix–Raviart FEM for second-order linear nonselfadjoint and indefinite elliptic problems.
+The paper identifies six parameters and sufficient conditions for the local a priori and a posteriori error control of conforming and nonconforming discretizations of a class of semilinear elliptic problems first in an abstract framework and then in the two semilinear applications.
+This leads to new best-approximation error estimates and to a posteriori error estimates in terms of explicit residual-based error control for the conforming and Morley FEM.
+For more details see [1].
+Lower-order quadratic finite elements are popular for solving fourth-order elliptic PDEs when the solution has limited regularity.
+A priori and a posteriori error estimates are considered in Carstensen et al.
+[1] with respect to different mesh dependent norms which involve different jump and penalization terms.
+This work addresses the question, whether they are comparable with respect to a common norm.
+This article  establishes that the errors for the quadratic symmetric interior discontinuous Galerkin, C0 interior penalty and nonconforming Morley finite element methods are equivalent upto some higher-order oscillation term with respect to a unified norm.
+Numerical experiments are performed to substantiate the comparison results.
+Paper under preparation.
+A unified framework for goal-oriented a posteriori error estimation is derived for the biharmonic problem.
+In particular, C0IP and discontinuous Galerkin finite element methods are considered.
+The quantity of interest is given by a functional composed of a volumetric weighted mean value.
+The estimator is based on potential reconstruction and equilibrated moment tensor that gives a  guaranteed upper bound of error.
+Paper under preparation.
+1.
+Carsten Carstensen, Gouranga Mallik and Neela Nataraj, Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity, IMA Journal of Numerical Analysis, 2020.
+
+\subsection{Surjit Kumar}
+
+In a continuation of the project "Operator valued multishifts" together with Rajeev Gupta and Shailesh Trivedi , we establish circularity, analyticity and wandering subspace property of these multishifts.
+Further, we study the function theoretic behaviour of operator-valued multishifts.
+We determine the bounded point evaluation, reproducing kernel structure and the unitary equivalence of operator-valued multishifts with invertible operator weights (see [2]).
+In a joint work with Soumitra Ghara and Paramita Pramanick, we have generalized the notion of so called Spherical tuple of operators, namely $K$-homogeneous operator tuple, where $K$ is the maximal compact subgroup of the identity component of the biholomorphic automorphism group of irreducible bounded symmetric domain.
+In this work [2], we obtain a model for a certain class of $K$-homogeneous operator tuple as the operators of multiplication by the coordinate on a reproducing kernel Hilbert space of holomorphic functions.
+Using this model, we obtain a criterion for boundedness, membership in the Cowen-Douglas class, unitary equivalence and similarity of these tuples.
+[1] Rajeev Gupta, Surjit Kumar and Shailesh Trivedi “Unitary equivalence of Operator-Valued Multishifts “, J.
+Math.
+Anal.
+Appl.
+(2020).
+[2] Soumitra Ghara, Surjit Kumar and Paramita Pramanick “$K$-homogeneous tuple of operators on bounded symmetric domains, preprint.
+
+\subsection{Debmalya Sain}
+
+Possible applications of the approximate version of the Birkhoff-James orthogonality have been explored in [1].
+In [2], we have conducted a study of the geometric properties, including parallelism and orthogonality, in operator spaces.
+Various analytic applications of the concept of orthogonality have been presented in the Book Chapter [3].
+Symmetry of Birkhoff-James orthogonality in operator spaces has been discussed in the Book Chapter [4].
+Extreme contractions and their connection with the operator norm attainment set is the subject matter of [5].
+The article [6] deals with Bishop-Phelps-Bolloboas type theorems in operator spaces.
+The numerical index of polyhedral banach spaces is the main object of study in [7].
+The article [8] is concerned with approximate Birkhoff-James orthogonality and normal cones in a normed space.
+Norm optimization problems in operator spaces have been investigated in [9].
+We have studied geometric properties of extreme contractions between polygonal Banach spaces in [10].
+A complete characterization of the operator norm attainment set has been obtained in [11].
+Bhatia-Semrl type theorems have been studied in the general setting of Banach spaces in [12].
+[1] Mal, Arpita and Paul, Kallol and Rao, T.
+S.
+S.
+R.
+K.
+and Sain, Debmalya, Approximate Birkhoff-James orthogonality and smoothness in the space of bounded linear operators, Monatsh.
+Math.
+, 190 (2019), 549-558.
+[2] Mal, Arpita and Sain, Debmalya and Paul, Kallol, On some geometric properties of operator spaces, Banach J.
+Math.
+Anal.
+, 13 (2019), 174-191.
+[3] Paul, Kallol and Sain, Debmalya, Birkhoff-James orthogonality and its application in the study of geometry of Banach space, Advanced topics in mathematical analysis , (2019), 245-284.
+[4] Paul, Kallol and Sain, Debmalya and Ghosh, Puja, Symmetry of Birkhoff-James orthogonality of bounded linear operators, Ulam type stability , (2019), 331-344.
+[5] Sain, Debmalya, On extreme contractions and the norm attainment set of a bounded linear operator, Ann.
+Funct.
+Anal.
+, 10 (2019), 135-143.
+[6] Sain, Debmalya, Smooth points in operator spaces and some Bishop-Phelps-Bollobás type theorems in Banach spaces, Oper.
+Matrices , 13 (2019), 433-445.
+[7] Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag, Santanu, On the numerical index of polyhedral Banach spaces, Linear Algebra Appl.
+, 577 (2019), 121-133.
+[8] Sain, Debmalya and Paul, Kallol and Mal, Arpita, On approximate Birkhoff-James orthogonality and normal cones in a normed space, J.
+Convex Anal.
+, 26 (2019), 341-351.
+[9] Sain, Debmalya and Paul, Kallol and Mandal, Kalidas, On two extremum problems related to the norm of a bounded linear operator, Oper.
+Matrices , 13 (2019), 421-432.
+[10] Sain, Debmalya and Ray, Anubhab and Paul, Kallol, Extreme contractions on finite-dimensional polygonal Banach spaces, J.
+Convex Anal.
+, 26 (2019), 877-885.
+[11] Sain, Debmalya, On the norm attainment set of a bounded linear operator and semi-inner-products in normed spaces, Indian J.
+Pure Appl.
+Math.
+, 51 (2020), 179-186.
+[12] Sain, Debmalya and Mal, Arpita and Paul, Kallol, Some remarks on Birkhoff-James orthogonality of linear operators, Expo.
+Math.
+, 38 (2020), 138-147.

### 2020-08-05 ugc/src/Data.scala

@@ -16,9 +16,11 @@ object Data {
   val numGrants = 4
   val awardsPos = grantInit + (numGrants * 6)
   val activitiesSize = 4
-  val activiesInit = awardsPos + 3  
+  val activiesInit = awardsPos + 3
   val fullSize = activiesInit + (2 * activitiesSize) // because of old activities
-  def pad(v: Vector[String]) = v ++ Vector.fill(fullSize - v.size)("")
+  val postDocSize = grantInit + 9 + 1 // joining-leaving and awards
+  def pad(v: Vector[String], full: Int = fullSize) =
+    v ++ Vector.fill(full - v.size)("")
   def preComma(s: String) = if (s.trim() == "") "" else s", $s"
 
   lazy val data = os.read
@@ -26,7 +28,7 @@ object Data {
     .toVector
     .tail
     .map(_.split("\t").toVector.tail)
-    .map(pad)
+    .map(pad(_))
 
   lazy val summerStudents = data.flatMap(
     l =>
@@ -34,6 +36,24 @@ object Data {
         stu.text(l(0))
       }
   )
+
+  lazy val postDocRaw = os.read
+    .lines(os.resource / "ugc2020-postdocs.tsv")
+    .toVector
+    .tail
+    .map(_.split("\t").toVector.tail)
+    .map(pad(_, postDocSize))
+
+  lazy val postDocTriple
+      : Vector[(Vector[String], Vector[String], Vector[String])] =
+    postDocRaw.map(
+      v =>
+        (
+          v.take(2) ++ v.drop(11).dropRight(2),
+          v.drop(2).take(9),
+          v.takeRight(2)
+        )
+    )
 
   lazy val summerTeX =
     s"""
@@ -45,6 +65,11 @@ ${summerStudents.map(s => "\\item " + s).mkString("\n")}
 """
   lazy val facultyData: Vector[FacultyData] =
     data.map(l => FacultyData.get(l)).sortBy(_.name)
+
+  lazy val postDocData: Vector[PostDocData] =
+    postDocTriple.map {
+      case (data, fel, aws) => PostDocData.get(data, fel, aws)
+    }
 
   lazy val grantsItems = facultyData.flatMap(f => f.grantTeX)
 
@@ -59,13 +84,21 @@ ${grantsItems.mkString("\n")}
 
   lazy val reports = facultyData
     .map(d => s"\\subsection{${d.name}}\n\n${d.researchHighlights}")
[…]

### 2020-08-05 data/draft-sections.tex
added \item to activities

@@
 \begin{enumerate}
-A. K. Nandakumaran was Member, Core Committee, KVPY
-A. K. Nandakumaran was Member, Library Committee
-Apoorva Khare was Talks: (1) 2019-04-12: Eigenfunctions Seminar, titled "Schoenberg: from metric geometry to matrix positivity" (2) 2019-11-06: 1st Math Symposium of Infosys Young Investigators: Talk, titled "Groups with norms; distance matrices and Zariski density"
-Apoorva Khare was Organizer of Eigenfunctions,  APRG Seminar, Algebra-Combinatorics Seminar, (co-organiser)
-Apoorva Khare was Contributed in preparing the PhD Qualifiers in Algebra
-Apoorva Khare was Student thesis/project supervision: (1) Swarnalipa Datta, MS Thesis (2) Soumik Dutta, BS Project
-Arvind Ayyer was Organised ICTS workshop on "Universality in random structures: Interfaces, Matrices, Sandpiles" from 14/01 -08/02/2019 jointly with Riddhipratim Basu and Manjunath Krishnapur.
-Basudeb Datta was B.
+\item A. K. Nandakumaran was Member, Core Committee, KVPY
+\item A. K. Nandakumaran was Member, Library Committee
+\item Apoorva Khare was Talks: (1) 2019-04-12: Eigenfunctions Seminar, titled "Schoenberg: from metric geometry to matrix positivity" (2) 2019-11-06: 1st Math Symposium of Infosys Young Investigators: Talk, titled "Groups with norms; distance matrices and Zariski density"
+\item Apoorva Khare was Organizer of Eigenfunctions,  APRG Seminar, Algebra-Combinatorics Seminar, (co-organiser)
+\item Apoorva Khare was Contributed in preparing the PhD Qualifiers in Algebra
+\item Apoorva Khare was Student thesis/project supervision: (1) Swarnalipa Datta, MS Thesis (2) Soumik Dutta, BS Project
+\item Arvind Ayyer was Organised ICTS workshop on "Universality in random structures: Interfaces, Matrices, Sandpiles" from 14/01 -08/02/2019 jointly with Riddhipratim Basu and Manjunath Krishnapur.
+\item Basudeb Datta was B.
 Datta was an member of the Committees for the following: (i)  Promotion of Professor in Mathematics in HAG scale in NIT, Rourkela in November 2018, (ii) Faculty selection for the post of Associate and Assistant Professors in the Department of Mathematics of IIT, Delhi in May, 2019, (iii) Faculty selection in mathematics at NISER, Bhubaneswar in June, 2019.
-Basudeb Datta was B.
+\item Basudeb Datta was B.
 Datta was  examiner for the following PhD theses:  (i) ``Dynamics of maps possessing the almost average shadowing property and variants of transitivity" of Mukta Garg, Univ of Delhi in 2018, (ii) ``On some problems in Algebraic Combinatorics" of Sajal K.
@@
 of Delhi in 2020.
-Dilip P. Patil was Taught the course: MA 312 Commutative Algebra course during Jan-April 2020
-Dilip P. Patil was Taught  (12 Week long)  NPTEL Course during Jan-April 2020
-Gautam Bharali was Member of the Faculty Selection Committee at IIIT Guwahati in June 2018
-Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)  
-R VENKATESH was We hosted 70 students and 5 faculty members from Madras Christian College as a part of their Educational visit to IISc, Bangalore on 16th October 2018.
+\item Dilip P. Patil was Taught the course: MA 312 Commutative Algebra course during Jan-April 2020
+\item Dilip P. Patil was Taught  (12 Week long)  NPTEL Course during Jan-April 2020
+\item Gautam Bharali was Member of the Faculty Selection Committee at IIIT Guwahati in June 2018
+\item Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)  
+\item R VENKATESH was We hosted 70 students and 5 faculty members from Madras Christian College as a part of their Educational visit to IISc, Bangalore on 16th October 2018.
 Two lectures were arranged for them on 16th October 2018.
-R. Venkatesh was Algebra Symposium, Department of Mathematics, IISc, Bangalore, India (February 12, 2020).
-R.
+\item R. Venkatesh was Algebra Symposium, Department of Mathematics, IISc, Bangalore, India (February 12, 2020).
+\item R.
 Venkatesh was Discussion Meeting on Representation Theory 2019, Department of Mathematics, IISc, Bangalore (December 14 - 16, 2019).
@@
 Two lecture series was delivered by Professor Vyjayanthi Chari (UC Riverside, USA) and Professor Anne Schilling (UC Davis, USA) as part of this discussion meeting.
-R. Venkatesh was NCM - Instructional School for Teachers on Analysis and PDE, Department of Mathematics, IISc, Bangalore (May 6 - 18, 2019). 
-Srikanth Krishnan Iyer was Gave a series of ten lectures in the Advanced Instructional School on Stochastic Processes, June 2019 organized by NICER, Bhubaneshwar on Probability Theory.
-Srikanth Krishnan Iyer was Gave a series of eight lectures in the annual Lecture Series in Probability XIV held at ISI-Delhi between December 2 - 6, 2019 on Limit Theorems in Stochastic Geometry.
-Srikanth Krishnan Iyer was Gave a talk titled :Random Connection Models" at the RBI, Mumbai on the occasion of Statistics day, June 26, 2019.
-Srikanth Krishnan Iyer was Gave a talk titled "Phase Transitions in Random Networks" at the FLAIR 4 Big Data Summer School on July 6, 2019.
-Subhojoy Gupta was Co-organized a discussion meeting at ICTS Bangalore in December 2018, on “Surface-Group Representations and Projective Structures".
+\item R. Venkatesh was NCM - Instructional School for Teachers on Analysis and PDE, Department of Mathematics, IISc, Bangalore (May 6 - 18, 2019). 
+\item Srikanth Krishnan Iyer was Gave a series of ten lectures in the Advanced Instructional School on Stochastic Processes, June 2019 organized by NICER, Bhubaneshwar on Probability Theory.
+\item Srikanth Krishnan Iyer was Gave a series of eight lectures in the annual Lecture Series in Probability XIV held at ISI-Delhi between December 2 - 6, 2019 on Limit Theorems in Stochastic Geometry.
+\item Srikanth Krishnan Iyer was Gave a talk titled :Random Connection Models" at the RBI, Mumbai on the occasion of Statistics day, June 26, 2019.
+\item Srikanth Krishnan Iyer was Gave a talk titled "Phase Transitions in Random Networks" at the FLAIR 4 Big Data Summer School on July 6, 2019.
+\item Subhojoy Gupta was Co-organized a discussion meeting at ICTS Bangalore in December 2018, on “Surface-Group Representations and Projective Structures".
 Website: https://www.icts.res.in/discussion-meeting/SGPS2018.
-Subhojoy Gupta was Referee for “Memoirs of the American Mathematical Society",  “Indian Journal of Pure and Applied Mathematics"
-Subhojoy Gupta was M.Sc. thesis referee for a student of Chennai Mathematical Institute,  Satyajit Maity
-Subhojoy Gupta was Member of Research Advisory Committee for Ramya Nair, a PhD student at IISER Pune. 
-Thirupathi Gudi was Organized Workshop on Finite Elements for Nonlinear and Multiscale Problems during Feb 28 – Mar 03, 2020.
-Vamsi Pritham Pingali was Guided the Master's Thesis ("Kahler geometry with a view towards the Calabi conjecture") of Vishnu Nandakumaran of IISER Pune (academic year of 2019-2020)
-Vamsi Pritham Pingali was Visited ICTP as a junior associate during May 2019 and delivered a talk ("A vector bundle version of the Monge-Ampere equation")
+\item Subhojoy Gupta was Referee for “Memoirs of the American Mathematical Society",  “Indian Journal of Pure and Applied Mathematics"
+\item Subhojoy Gupta was M.Sc. thesis referee for a student of Chennai Mathematical Institute,  Satyajit Maity
+\item Subhojoy Gupta was Member of Research Advisory Committee for Ramya Nair, a PhD student at IISER Pune. 
+\item Thirupathi Gudi was Organized Workshop on Finite Elements for Nonlinear and Multiscale Problems during Feb 28 – Mar 03, 2020.
+\item Vamsi Pritham Pingali was Guided the Master's Thesis ("Kahler geometry with a view towards the Calabi conjecture") of Vishnu Nandakumaran of IISER Pune (academic year of 2019-2020)
+\item Vamsi Pritham Pingali was Visited ICTP as a junior associate during May 2019 and delivered a talk ("A vector bundle version of the Monge-Ampere equation")
 \end{enumerate}

### 2020-08-05 ugc/src/Data.scala

@@ -95,7 +95,7 @@ ${grantsItems.mkString("\n")}
   lazy val editors = facultyData.flatMap(f => f.awards.edOpt(f.name))
 
   lazy val otherOld = facultyData.flatMap(f => 
-    f.otherOld.map(act => s"${f.name} was $act"))
+    f.otherOld.map(act => s"\\item ${f.name} was $act"))
 
   lazy val other  = facultyData.flatMap(f => 
     f.otherActivities.map(act => s"${f.name} was $act"))

### 2020-08-05 ugc/src/Data.scala
added \item to activities

@@ -98,7 +98,7 @@ ${grantsItems.mkString("\n")}
     f.otherOld.map(act => s"\\item ${f.name} was $act"))
 
   lazy val other  = facultyData.flatMap(f => 
-    f.otherActivities.map(act => s"${f.name} was $act"))
+    f.otherActivities.map(act => s"\\item ${f.name} was $act"))
 
   lazy val draftSections =
     s"""

### 2020-08-05 data/draft-sections.tex
added \item to activities

@@
 \begin{enumerate}
-A. K. Nandakumaran was Convener, KVPY
-A. K. Nandakumaran was Member, Library Committee
-Apoorva Khare was Member of two UG Project Presentation Evaluation Committees
-Apoorva Khare was Pre-RMO (Regional Mathematics Olympiad) - helped in setting the question paper
-Apoorva Khare was Senate nominee for Comprehensive Exam of Vinayak Ramkumar (student of P. Vijay Kumar, ECE)
-Apoorva Khare was Advising: (1) Prateek Kumar Vishwakarma, Int-PhD (passed his Comprehensive Exam) (2) Babhrubahan Bose, Int-PhD (passed his Comprehensive Exam) (3) G.V.K.
+\item A. K. Nandakumaran was Convener, KVPY
+\item A. K. Nandakumaran was Member, Library Committee
+\item Apoorva Khare was Member of two UG Project Presentation Evaluation Committees
+\item Apoorva Khare was Pre-RMO (Regional Mathematics Olympiad) - helped in setting the question paper
+\item Apoorva Khare was Senate nominee for Comprehensive Exam of Vinayak Ramkumar (student of P. Vijay Kumar, ECE)
+\item Apoorva Khare was Advising: (1) Prateek Kumar Vishwakarma, Int-PhD (passed his Comprehensive Exam) (2) Babhrubahan Bose, Int-PhD (passed his Comprehensive Exam) (3) G.V.K.
 Teja, PhD (passed his Comprehensive Exam) (4) Swarnalipa Datta, Int-PhD (downgraded to MS) Mentoring: (5) Dr.
 Projesh Nath Choudhury, NBHM postdoc
-Arvind Ayyer was Referee for the thesis of Majil Pratim Saikia at University of Vienna.
-Arvind Ayyer was Referee for the thesis of Mr. Jyotirmoy Ganguly at IISER Pune.
-Arvind Ayyer was Thesis examiner for Mr. Sudip Bera, Visva-Bharati University.
-Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)
-Gautam Bharali was Served as an independent expert for the Swiss National Science Foundation for the review of project proposals in pure mathematics in 2019.
-R VENKATESH was Algebra Symposium, Department of Mathematics, IISc, Bangalore, India (February 12, 2020).
-R VENKATESH was Discussion Meeting on Representation Theory 2019, Department of Mathematics, IISc, Bangalore (December 14 - 16, 2019).
+\item Arvind Ayyer was Referee for the thesis of Majil Pratim Saikia at University of Vienna.
+\item Arvind Ayyer was Referee for the thesis of Mr. Jyotirmoy Ganguly at IISER Pune.
+\item Arvind Ayyer was Thesis examiner for Mr. Sudip Bera, Visva-Bharati University.
+\item Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)
+\item Gautam Bharali was Served as an independent expert for the Swiss National Science Foundation for the review of project proposals in pure mathematics in 2019.
+\item R VENKATESH was Algebra Symposium, Department of Mathematics, IISc, Bangalore, India (February 12, 2020).
+\item R VENKATESH was Discussion Meeting on Representation Theory 2019, Department of Mathematics, IISc, Bangalore (December 14 - 16, 2019).
 Partially funded by the UGC-CAS grant.
 Two lecture series was delivered by Professor Vyjayanthi Chari (UC Riverside, USA) and Professor Anne Schilling (UC Davis, USA) as part of this discussion meeting.
-R VENKATESH was NCM - Instructional School for Teachers on Analysis and PDE, Department of Mathematics, IISc, Bangalore (May 6 - 18, 2019). 
-Siddhartha Gadgil was thesis examiner for a thesis at IIT, Kanpur
-Siddhartha Gadgil was thesis examiner for a thesis at Delhi University
-Siddhartha Gadgil was thesis examiner for a thesis for TIFR, Mumbai
-Siddhartha Gadgil was member of selection committee at BHU
-Subhojoy Gupta was Member of Research Advisory Committee for Ramya Nair, a PhD student at IISER Pune. 
-Subhojoy Gupta was Co-organizer of an Advanced Instructional School on Riemannian Geometry, sponsored by the National Centre for Mathematics, held in July 2019.
-Subhojoy Gupta was Referee for "Proceedings of the London Mathematical Society", "Journal of Topology", "Manuscripta Mathematica" and reviewer for AMS and Zentralblatt Math Reviews
-Subhojoy Gupta was Supervised UG final year project of Shabarish Chenakkod
+\item R VENKATESH was NCM - Instructional School for Teachers on Analysis and PDE, Department of Mathematics, IISc, Bangalore (May 6 - 18, 2019). 
+\item Siddhartha Gadgil was thesis examiner for a thesis at IIT, Kanpur
+\item Siddhartha Gadgil was thesis examiner for a thesis at Delhi University
+\item Siddhartha Gadgil was thesis examiner for a thesis for TIFR, Mumbai
+\item Siddhartha Gadgil was member of selection committee at BHU
+\item Subhojoy Gupta was Member of Research Advisory Committee for Ramya Nair, a PhD student at IISER Pune. 
+\item Subhojoy Gupta was Co-organizer of an Advanced Instructional School on Riemannian Geometry, sponsored by the National Centre for Mathematics, held in July 2019.
+\item Subhojoy Gupta was Referee for "Proceedings of the London Mathematical Society", "Journal of Topology", "Manuscripta Mathematica" and reviewer for AMS and Zentralblatt Math Reviews
+\item Subhojoy Gupta was Supervised UG final year project of Shabarish Chenakkod
 \end{enumerate}

### 2020-08-06 data/draft-publications.tex
clean generation

@@
 Patil , \emph{COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS}, to appear in Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry.
-\item Bharali, Gautam and Maitra, Anwoy, \emph{A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems}, to appear in Annali della Scuola Normale Superiore di Pisa, DOI 10.2422/2036-2145.201906_007, \url{http://annaliscienze.sns.it/index.php?page=ForthcomingArticles}.
+\item Bharali, Gautam and Maitra, Anwoy, \emph{A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems}, to appear in Annali della Scuola Normale Superiore di Pisa, DOI 10.2422/2036-2145.201906\_007, \url{http://annaliscienze.sns.it/index.php?page=ForthcomingArticles}.
 \item Maitra, Anwoy, \emph{On the continuous extension of Kobayashi isometries}, Proc.
@@
 
-\begin{enumerate}
+\subsection{Books}
 
-\end{enumerate}
-
-\subsection{Books and book chapters}
+\subsection{Book Chapters}
 
 \begin{enumerate}
-
+\item Gupta, Subhojoy and Seshadri, Harish, \emph{Complex geometry of Teichmüller domains} in Papadopoulos, Athanase (ed.) (ed.), {\em Handbook of Teichmüller theory} , IRMA Lect.
+Math.
+Theor.
+Phys , Eur.
+Math.
+Soc., Zürich (2020), 26.
+\item Gupta, Subhojoy, \emph{Holomorphic quadratic differentials in Teichmüller theory} in Papadopoulos, Athanase (ed.) (ed.), {\em Handbook of Teichmüller theory} , IRMA Lect.
+Math.
+Theor.
+Phys.
+, Eur.
+Math.
+Soc., Zürich (2020), 36.
 \end{enumerate}
@@
 \item Gupta, Subhojoy and Mj, Mahan, \emph{Meromorphic projective structures, grafting and the monodromy map}, preprint, \url{http://arxiv.org/abs/1904.03804}.
-\item Gupta, Subhojoy, \emph{Monodromy groups of CP^1-structures on punctured surfaces}, preprint, \url{https://arxiv.org/abs/1909.10771}.
+\item Gupta, Subhojoy, \emph{Monodromy groups of $CP^1$-structures on punctured surfaces}, preprint, \url{https://arxiv.org/abs/1909.10771}.
 \item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter, \emph{Surface group representations in SL(2,C) with finite mapping class orbits}, preprint, \url{https://arxiv.org/abs/1707.00071}.
@@
 Samu, {\em The exact phase diagram for a semipermeable {TASEP} with
-nonlocal boundary jumps}, J. Phys. A} {\bf 52} (2019), 355001, 19, DOI 10.1088/1751-8121/ab2e96, \url{https://doi.org/10.1088/1751-8121/ab2e96}.
+nonlocal boundary jumps}, J. Phys. A {\bf 52} (2019), 355001, 19, DOI 10.1088/1751-8121/ab2e96, \url{https://doi.org/10.1088/1751-8121/ab2e96}.
 \item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
-Nandakumaran, A. K., {\em Control problem on a rough circular domain and homogenization}, Asymptot. Anal.} {\bf 115} (2019), 19--46, DOI 10.3233/asy-191526, \url{https://doi.org/10.3233/asy-191526}.
+Nandakumaran, A. K., {\em Control problem on a rough circular domain and homogenization}, Asymptot. Anal. {\bf 115} (2019), 19--46, DOI 10.3233/asy-191526, \url{https://doi.org/10.3233/asy-191526}.
 \item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Locally periodic unfolding operator for highly oscillating
-rough domains}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954, DOI 10.1007/s10231-019-00848-7, \url{https://doi.org/10.1007/s10231-019-00848-7}.
+rough domains}, Ann. Mat. Pura Appl. (4) {\bf 198} (2019), 1931--1954, DOI 10.1007/s10231-019-00848-7, \url{https://doi.org/10.1007/s10231-019-00848-7}.
 \item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Generalization of unfolding operator for highly oscillating
-smooth boundary domains and homogenization}, Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30, DOI 10.1007/s00526-018-1354-6, \url{https://doi.org/10.1007/s00526-018-1354-6}.
+smooth boundary domains and homogenization}, Calc. Var. Partial Differential Equations {\bf 57} (2018), Art. 86, 30, DOI 10.1007/s00526-018-1354-6, \url{https://doi.org/10.1007/s00526-018-1354-6}.
 \item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu, {\em Asymptotic analysis of a boundary optimal control problem on a
-general branched structure}, Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434, DOI 10.1002/mma.5748, \url{https://doi.org/10.1002/mma.5748}.
+general branched structure}, Math. Methods Appl. Sci. {\bf 42} (2019), 6407--6434, DOI 10.1002/mma.5748, \url{https://doi.org/10.1002/mma.5748}.
 \item Aiyappan, S. and Sardar, Bidhan Chandra, {\em Biharmonic equation in a highly oscillating domain and
-homogenization of an associated control problem}, Appl. Anal.} {\bf 98} (2019), 2783--2801, DOI 10.1080/00036811.2018.1471207, \url{https://doi.org/10.1080/00036811.2018.1471207}.
+homogenization of an associated control problem}, Appl. Anal. {\bf 98} (2019), 2783--2801, DOI 10.1080/00036811.2018.1471207, \url{https://doi.org/10.1080/00036811.2018.1471207}.
 \item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish, {\em A gap theorem for positive {E}instein metrics on the
-four-sphere}, Math. Ann.} {\bf 373} (2019), 1329--1339, DOI 10.1007/s00208-018-1749-x, \url{https://doi.org/10.1007/s00208-018-1749-x}.
+four-sphere}, Math. Ann. {\bf 373} (2019), 1329--1339, DOI 10.1007/s00208-018-1749-x, \url{https://doi.org/10.1007/s00208-018-1749-x}.
 \item Anamby, Pramath and Das, Soumya, {\em Distinguishing {H}ermitian cusp forms of degree 2 by a certain
-subset of all {F}ourier coefficients}, Publ. Mat.} {\bf 63} (2019), 307--341, DOI 10.5565/PUBLMAT6311911, \url{https://doi.org/10.5565/PUBLMAT6311911}.
+subset of all {F}ourier coefficients}, Publ. Mat. {\bf 63} (2019), 307--341, DOI 10.5565/PUBLMAT6311911, \url{https://doi.org/10.5565/PUBLMAT6311911}.
 \item Anamby, Pramath and Das, Soumya, {\em Bounds for the {P}etersson norms of the pullbacks of
-{S}aito-{K}urokawa lifts}, J. Number Theory} {\bf 191} (2018), 289--304, DOI 10.1016/j.jnt.2018.03.011, \url{https://doi.org/10.1016/j.jnt.2018.03.011}.
+{S}aito-{K}urokawa lifts}, J. Number Theory {\bf 191} (2018), 289--304, DOI 10.1016/j.jnt.2018.03.011, \url{https://doi.org/10.1016/j.jnt.2018.03.011}.
 \item Arunkumar, G. and Kus, Deniz and Venkatesh, R., {\em Root multiplicities for {B}orcherds algebras and graph
-coloring}, J. Algebra} {\bf 499} (2018), 538--569, DOI 10.1016/j.jalgebra.2017.11.050, \url{https://doi.org/10.1016/j.jalgebra.2017.11.050}.
+coloring}, J. Algebra {\bf 499} (2018), 538--569, DOI 10.1016/j.jalgebra.2017.11.050, \url{https://doi.org/10.1016/j.jalgebra.2017.11.050}.
 \item Ayyer, Arvind and Behrend, Roger E., {\em Factorization theorems for classical group characters, with
 applications to alternating sign matrices and plane
-partitions}, J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105, DOI 10.1016/j.jcta.2019.01.001, \url{https://doi.org/10.1016/j.jcta.2019.01.001}.
+partitions}, J. Combin. Theory Ser. A {\bf 165} (2019), 78--105, DOI 10.1016/j.jcta.2019.01.001, \url{https://doi.org/10.1016/j.jcta.2019.01.001}.
 \item Ayyer, Arvind and Bouttier, J\'{e}r\'{e}mie and Corteel, Sylvie and
@@
 in Appl.
-Math.} {\bf 98} (2018), 100--126, DOI 10.1016/j.aam.2018.03.001, \url{https://doi.org/10.1016/j.aam.2018.03.001}.
+Math.
+{\bf 98} (2018), 100--126, DOI 10.1016/j.aam.2018.03.001, \url{https://doi.org/10.1016/j.aam.2018.03.001}.
 \item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, {\em Matrix product solution of a left-permeable two-species
-asymmetric exclusion process}, Phys. Rev. E} {\bf 97} (2018), 012151, 10, DOI 10.1103/physreve.97.012151, \url{https://doi.org/10.1103/physreve.97.012151}.
+asymmetric exclusion process}, Phys. Rev. E {\bf 97} (2018), 012151, 10, DOI 10.1103/physreve.97.012151, \url{https://doi.org/10.1103/physreve.97.012151}.
 \item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, {\em The phase diagram for a multispecies left-permeable asymmetric
-exclusion process}, J. Stat. Phys.} {\bf 174} (2019), 605--621, DOI 10.1007/s10955-018-2183-x, \url{https://doi.org/10.1007/s10955-018-2183-x}.
-\item Ayyer, Arvind and Linusson, Svante, {\em Reverse juggling processes}, Random Structures Algorithms} {\bf 55} (2019), 56--72, DOI 10.1002/rsa.20825, \url{https://doi.org/10.1002/rsa.20825}.
-\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, {\em Odd partitions in {Y}oung's lattice}, S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
+exclusion process}, J. Stat. Phys. {\bf 174} (2019), 605--621, DOI 10.1007/s10955-018-2183-x, \url{https://doi.org/10.1007/s10955-018-2183-x}.
+\item Ayyer, Arvind and Linusson, Svante, {\em Reverse juggling processes}, Random Structures Algorithms {\bf 55} (2019), 56--72, DOI 10.1002/rsa.20825, \url{https://doi.org/10.1002/rsa.20825}.
+\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, {\em Odd partitions in {Y}oung's lattice}, S\'{e}m. Lothar. Combin. {\bf 75} (2018), Art. B75g, 13.
 \item Ayyer, Arvind and Ramassamy, Sanjay, {\em The {H}ilbert-{G}alton board}, ALEA Lat.
@@
 Math.
-Stat.} {\bf 15} (2018), 755--774, DOI 10.30757/alea.v15-28, \url{https://doi.org/10.30757/alea.v15-28}.
+Stat.
+{\bf 15} (2018), 755--774, DOI 10.30757/alea.v15-28, \url{https://doi.org/10.30757/alea.v15-28}.
 \item B\"{o}cherer, Siegfried and Das, Soumya, {\em Cuspidality and the growth of {F}ourier coefficients of
-modular forms}, J. Reine Angew. Math.} {\bf 741} (2018), 161--178, DOI 10.1515/crelle-2015-0075, \url{https://doi.org/10.1515/crelle-2015-0075}.
+modular forms}, J. Reine Angew. Math. {\bf 741} (2018), 161--178, DOI 10.1515/crelle-2015-0075, \url{https://doi.org/10.1515/crelle-2015-0075}.
 \item B\"{o}cherer, Siegfried and Das, Soumya, {\em Petersson norms of not necessarily cuspidal {J}acobi modular
-forms and applications}, Adv. Math.} {\bf 336} (2018), 335--376, DOI 10.1016/j.aim.2018.07.033, \url{https://doi.org/10.1016/j.aim.2018.07.033}.
+forms and applications}, Adv. Math. {\bf 336} (2018), 335--376, DOI 10.1016/j.aim.2018.07.033, \url{https://doi.org/10.1016/j.aim.2018.07.033}.
 \item Bagchi, Sayan and Thangavelu, Sundaram, {\em Weighted norm inequalities for {W}eyl multipliers and fourier
-multipliers on the {H}eisenberg group}, J. Anal. Math.} {\bf 136} (2018), 1--29, DOI 10.1007/s11854-018-0053-8, \url{https://doi.org/10.1007/s11854-018-0053-8}.
+multipliers on the {H}eisenberg group}, J. Anal. Math. {\bf 136} (2018), 1--29, DOI 10.1007/s11854-018-0053-8, \url{https://doi.org/10.1007/s11854-018-0053-8}.
 \item Baklouti, Ali and Thangavelu, Sundaram, {\em Hardy and {M}iyachi theorems for {H}eisenberg motion groups}, Nagoya Math.
-J.} {\bf 229} (2018), 1--20, DOI 10.1017/nmj.2016.58, \url{https://doi.org/10.1017/nmj.2016.58}.
+J.
+{\bf 229} (2018), 1--20, DOI 10.1017/nmj.2016.58, \url{https://doi.org/10.1017/nmj.2016.58}.
 \item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
-Verma, Kaushal, {\em Remarks on the higher dimensional {S}uita conjecture}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411, DOI 10.1090/proc/14421, \url{https://doi.org/10.1090/proc/14421}.
+Verma, Kaushal, {\em Remarks on the higher dimensional {S}uita conjecture}, Proc. Amer. Math. Soc. {\bf 147} (2019), 3401--3411, DOI 10.1090/proc/14421, \url{https://doi.org/10.1090/proc/14421}.
 \item Balhara, Rakesh, {\em Hardy's inequality for the fractional powers of the {G}rushin
-operator}, Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25, DOI 10.1007/s12044-019-0471-2, \url{https://doi.org/10.1007/s12044-019-0471-2}.
+operator}, Proc. Indian Acad. Sci. Math. Sci. {\bf 129} (2019), Art. 33, 25, DOI 10.1007/s12044-019-0471-2, \url{https://doi.org/10.1007/s12044-019-0471-2}.
 \item Balodi, Mamta and Palcoux, Sebastien, {\em On {B}oolean intervals of finite groups}, J.
@@
 Theory Ser.
-A} {\bf 157} (2018), 49--69, DOI 10.1016/j.jcta.2018.02.004, \url{https://doi.org/10.1016/j.jcta.2018.02.004}.
+A {\bf 157} (2018), 49--69, DOI 10.1016/j.jcta.2018.02.004, \url{https://doi.org/10.1016/j.jcta.2018.02.004}.
 \item Banerjee, Abhishek, {\em On {A}uslander's formula and cohereditary torsion pairs}, Commun.
 Contemp.
-Math.} {\bf 20} (2018), 1750071, 27, DOI 10.1142/S0219199717500717, \url{https://doi.org/10.1142/S0219199717500717}.
+Math.
+{\bf 20} (2018), 1750071, 27, DOI 10.1142/S0219199717500717, \url{https://doi.org/10.1142/S0219199717500717}.
 \item Banerjee, Abhishek, {\em Modular {H}ecke algebras over {M}\"{o}bius categories}, J.
 Geom.
-Phys.} {\bf 131} (2018), 23--40, DOI 10.1016/j.geomphys.2018.04.008, \url{https://doi.org/10.1016/j.geomphys.2018.04.008}.
+Phys.
+{\bf 131} (2018), 23--40, DOI 10.1016/j.geomphys.2018.04.008, \url{https://doi.org/10.1016/j.geomphys.2018.04.008}.
 \item Banerjee, Abhishek, {\em On differential torsion theories and rings with several
-objects}, Canad. Math. Bull.} {\bf 62} (2019), 703--714, DOI 10.4153/s0008439518000656, \url{https://doi.org/10.4153/s0008439518000656}.
+objects}, Canad. Math. Bull. {\bf 62} (2019), 703--714, DOI 10.4153/s0008439518000656, \url{https://doi.org/10.4153/s0008439518000656}.
 \item Banerjee, Abhishek, {\em A topological {N}ullstellensatz for tensor-triangulated
-categories}, C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375, DOI 10.1016/j.crma.2018.02.012, \url{https://doi.org/10.1016/j.crma.2018.02.012}.
-\item Banerjee, Abhishek, {\em Quasimodular {H}ecke algebras and {H}opf actions}, J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080, DOI 10.4171/JNCG/297, \url{https://doi.org/10.4171/JNCG/297}.
+categories}, C. R. Math. Acad. Sci. Paris {\bf 356} (2018), 365--375, DOI 10.1016/j.crma.2018.02.012, \url{https://doi.org/10.1016/j.crma.2018.02.012}.
+\item Banerjee, Abhishek, {\em Quasimodular {H}ecke algebras and {H}opf actions}, J. Noncommut. Geom. {\bf 12} (2018), 1041--1080, DOI 10.4171/JNCG/297, \url{https://doi.org/10.4171/JNCG/297}.
 \item Banerjee, Abhishek, {\em Completions of monoid objects and descent results}, J.
-Algebra} {\bf 507} (2018), 362--399, DOI 10.1016/j.jalgebra.2018.04.022, \url{https://doi.org/10.1016/j.jalgebra.2018.04.022}.
+Algebra {\bf 507} (2018), 362--399, DOI 10.1016/j.jalgebra.2018.04.022, \url{https://doi.org/10.1016/j.jalgebra.2018.04.022}.
 \item Banerjee, Abhishek and Kour, Surjeet, {\em {$(A,\delta)$}-modules, {H}ochschild homology and higher
-derivations}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802, DOI 10.1007/s10231-019-00844-x, \url{https://doi.org/10.1007/s10231-019-00844-x}.
+derivations}, Ann. Mat. Pura Appl. (4) {\bf 198} (2019), 1781--1802, DOI 10.1007/s10231-019-00844-x, \url{https://doi.org/10.1007/s10231-019-00844-x}.
 \item Basu, Arnab and Ghosh, Mrinal K., {\em Nonzero-sum risk-sensitive stochastic games on a countable
-state space}, Math. Oper. Res.} {\bf 43} (2018), 516--532, DOI 10.1287/moor.2017.0870, \url{https://doi.org/10.1287/moor.2017.0870}.
+state space}, Math. Oper. Res. {\bf 43} (2018), 516--532, DOI 10.1287/moor.2017.0870, \url{https://doi.org/10.1287/moor.2017.0870}.
 \item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
-and Putinar, Mihai, {\em Simultaneous kernels of matrix {H}adamard powers}, Linear Algebra Appl.} {\bf 576} (2019), 142--157, DOI 10.1016/j.laa.2018.03.035, \url{https://doi.org/10.1016/j.laa.2018.03.035}.
+and Putinar, Mihai, {\em Simultaneous kernels of matrix {H}adamard powers}, Linear Algebra Appl.
+{\bf 576} (2019), 142--157, DOI 10.1016/j.laa.2018.03.035, \url{https://doi.org/10.1016/j.laa.2018.03.035}.
 \item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
 Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
-Morales, Alejandro H. and Yip, Martha, {\em The volume of the caracol polytope}, S\'{e}m. Lothar. Combin.} {\bf 80B} (2018), Art. 87, 12.
+Morales, Alejandro H. and Yip, Martha, {\em The volume of the caracol polytope}, S\'{e}m. Lothar. Combin. {\bf 80B} (2018), Art. 87, 12.
 \item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
@@
 Math.
-Soc.} {\bf 372} (2019), 3369--3404, DOI 10.1090/tran/7743, \url{https://doi.org/10.1090/tran/7743}.
+Soc.
+{\bf 372} (2019), 3369--3404, DOI 10.1090/tran/7743, \url{https://doi.org/10.1090/tran/7743}.
 \item Bera, Sayani and Verma, Kaushal, {\em Some aspects of shift-like automorphisms of {$\Bbb C^k$}}, Proc.
@@
 Math.
-Sci.} {\bf 128} (2018), Art.
+Sci.
+{\bf 128} (2018), Art.
 10, 48, DOI 10.1007/s12044-018-0388-1, \url{https://doi.org/10.1007/s12044-018-0388-1}.
@@
 and Janardhanan, Jaikrishnan, {\em Proper holomorphic mappings onto symmetric products of a
-{R}iemann surface}, Doc. Math.} {\bf 23} (2018), 1291--1311.
+{R}iemann surface}, Doc. Math. {\bf 23} (2018), 1291--1311.
 \item Bharali, Gautam and Chandel, Vikramjeet Singh, {\em Pick interpolation on the polydisc: small families of
-sufficient kernels}, Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093, DOI 10.1007/s11785-017-0701-5, \url{https://doi.org/10.1007/s11785-017-0701-5}.
+sufficient kernels}, Complex Anal. Oper. Theory {\bf 13} (2019), 2069--2093, DOI 10.1007/s11785-017-0701-5, \url{https://doi.org/10.1007/s11785-017-0701-5}.
 \item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K., {\em Survey of last ten years of work done in {I}ndia in some
-selected areas of functional analysis and operator theory}, Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617, DOI 10.1007/s13226-019-0345-4, \url{https://doi.org/10.1007/s13226-019-0345-4}.
+selected areas of functional analysis and operator theory}, Indian J. Pure Appl. Math. {\bf 50} (2019), 599--617, DOI 10.1007/s13226-019-0345-4, \url{https://doi.org/10.1007/s13226-019-0345-4}.
 \item Bhattacharyya, Tirthankar and Sau, Haripada, {\em Holomorphic functions on the symmetrized bidisk---realization,
-interpolation and extension}, J. Funct. Anal.} {\bf 274} (2018), 504--524, DOI 10.1016/j.jfa.2017.09.013, \url{https://doi.org/10.1016/j.jfa.2017.09.013}.
+interpolation and extension}, J. Funct. Anal. {\bf 274} (2018), 504--524, DOI 10.1016/j.jfa.2017.09.013, \url{https://doi.org/10.1016/j.jfa.2017.09.013}.
 \item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
 Sundaram, {\em Hermite multipliers on modulation spaces}, Analysis and partial differential equations: perspectives from
-developing countries} {\bf 275} (2019), 42--64.
-\item Bhosle, Usha N., {\em Hitchin pairs on reducible curves}, Internat. J. Math.} {\bf 29} (2018), 1850015, 49, DOI 10.1142/S0129167X18500155, \url{https://doi.org/10.1142/S0129167X18500155}.
+developing countries {\bf 275} (2019), 42--64.
+\item Bhosle, Usha N., {\em Hitchin pairs on reducible curves}, Internat. J. Math. {\bf 29} (2018), 1850015, 49, DOI 10.1142/S0129167X18500155, \url{https://doi.org/10.1142/S0129167X18500155}.
 \item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and
-Pingali, Vamsi P., {\em Rational cuspidal curves on del-{P}ezzo surfaces}, J. Singul.} {\bf 17} (2018), 91--107.
+Pingali, Vamsi P., {\em Rational cuspidal curves on del-{P}ezzo surfaces}, J. Singul. {\bf 17} (2018), 91--107.
 \item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy, {\em Branched projective structures on a {R}iemann surface and
-logarithmic connections}, Doc. Math.} {\bf 24} (2019), 2299--2337.
+logarithmic connections}, Doc. Math. {\bf 24} (2019), 2299--2337.
 \item Biswas, Indranil and Pingali, Vamsi Pritham, {\em A characterization of finite vector bundles on {G}auduchon
-astheno-{K}\"{a}hler manifolds}, \'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art. 6, 13.
+astheno-{K}\"{a}hler manifolds}, \'{E}pijournal Geom. Alg\'{e}brique {\bf 2} (2018), Art. 6, 13.
 \item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi, {\em Edge patch-wise local projection stabilized nonconforming
-{FEM} for the {O}seen problem}, Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214, DOI 10.1515/cmam-2018-0020, \url{https://doi.org/10.1515/cmam-2018-0020}.
+{FEM} for the {O}seen problem}, Comput. Methods Appl. Math. {\bf 19} (2019), 189--214, DOI 10.1515/cmam-2018-0020, \url{https://doi.org/10.1515/cmam-2018-0020}.
 \item Biswas, Shibananda and Ghosh, Gargi and Misra, Gadadhar and
 Shyam Roy, Subrata, {\em On reducing submodules of {H}ilbert modules with
-{${S}_n$}-invariant kernels}, J. Funct. Anal.} {\bf 276} (2019), 751--784, DOI 10.1016/j.jfa.2018.10.025, \url{https://doi.org/10.1016/j.jfa.2018.10.025}.
+{${S}_n$}-invariant kernels}, J. Funct. Anal. {\bf 276} (2019), 751--784, DOI 10.1016/j.jfa.2018.10.025, \url{https://doi.org/10.1016/j.jfa.2018.10.025}.
 \item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram, {\em On extension problem, trace {H}ardy and {H}ardy's inequalities
-for some fractional {L}aplacians}, Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605, DOI 10.3934/cpaa.2019116, \url{https://doi.org/10.3934/cpaa.2019116}.
+for some fractional {L}aplacians}, Commun. Pure Appl. Anal. {\bf 18} (2019), 2575--2605, DOI 10.3934/cpaa.2019116, \url{https://doi.org/10.3934/cpaa.2019116}.
 \item Borah, Diganta and Haridas, Pranav and Verma, Kaushal, {\em Comments on the {G}reen's function of a planar domain}, Anal.
 Math.
-Phys.} {\bf 8} (2018), 383--414, DOI 10.1007/s13324-017-0177-5, \url{https://doi.org/10.1007/s13324-017-0177-5}.
+Phys.
+{\bf 8} (2018), 383--414, DOI 10.1007/s13324-017-0177-5, \url{https://doi.org/10.1007/s13324-017-0177-5}.
 \item Brenner, Susanne C. and Gudi, Thirupathi and Porwal, Kamana
@@
 optimal control problem with pointwise state and control
-constraints}, ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206, DOI 10.1051/cocv/2017031, \url{https://doi.org/10.1051/cocv/2017031}.
+constraints}, ESAIM Control Optim. Calc. Var. {\bf 24} (2018), 1181--1206, DOI 10.1051/cocv/2017031, \url{https://doi.org/10.1051/cocv/2017031}.
 \item Burton, Benjamin A. and Datta, Basudeb and Singh, Nitin and
 Spreer, Jonathan, {\em A construction principle for tight and minimal triangulations
-of manifolds}, Exp. Math.} {\bf 27} (2018), 22--36, DOI 10.1080/10586458.2016.1212747, \url{https://doi.org/10.1080/10586458.2016.1212747}.
+of manifolds}, Exp. Math. {\bf 27} (2018), 22--36, DOI 10.1080/10586458.2016.1212747, \url{https://doi.org/10.1080/10586458.2016.1212747}.
 \item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella, {\em Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
-indefinite second-order linear elliptic problems}, Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250, DOI 10.1515/cmam-2019-0034, \url{https://doi.org/10.1515/cmam-2019-0034}.
+indefinite second-order linear elliptic problems}, Comput. Methods Appl. Math. {\bf 19} (2019), 233--250, DOI 10.1515/cmam-2019-0034, \url{https://doi.org/10.1515/cmam-2019-0034}.
 \item Chandel, Vikramjeet Singh, {\em The three-point {P}ick-{N}evanlinna interpolation problem on
-the polydisc}, Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352, DOI 10.1080/17476933.2017.1370461, \url{https://doi.org/10.1080/17476933.2017.1370461}.
+the polydisc}, Complex Var. Elliptic Equ. {\bf 63} (2018), 1341--1352, DOI 10.1080/17476933.2017.1370461, \url{https://doi.org/10.1080/17476933.2017.1370461}.
 \item Chatterjee, Esha and Hassan, Sk. Sarif, {\em On the asymptotic character of a generalized rational
-difference equation}, Discrete Contin. Dyn. Syst.} {\bf 38} (2018), 1707--1718, DOI 10.3934/dcds.2018070, \url{https://doi.org/10.3934/dcds.2018070}.
+difference equation}, Discrete Contin. Dyn. Syst. {\bf 38} (2018), 1707--1718, DOI 10.3934/dcds.2018070, \url{https://doi.org/10.3934/dcds.2018070}.
 \item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
 K. C., {\em A note on linear preservers of semipositive and minimally
-semipositive matrices}, Electron. J. Linear Algebra} {\bf 34} (2018), 687--694, DOI 10.13001/1081-3810.3864, \url{https://doi.org/10.13001/1081-3810.3864}.
+semipositive matrices}, Electron. J. Linear Algebra {\bf 34} (2018), 687--694, DOI 10.13001/1081-3810.3864, \url{https://doi.org/10.13001/1081-3810.3864}.
 \item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram, {\em Hardy-type inequalities for fractional powers of the
-{D}unkl-{H}ermite operator}, Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544, DOI 10.1017/s0013091517000311, \url{https://doi.org/10.1017/s0013091517000311}.
+{D}unkl-{H}ermite operator}, Proc. Edinb. Math. Soc. (2) {\bf 61} (2018), 513--544, DOI 10.1017/s0013091517000311, \url{https://doi.org/10.1017/s0013091517000311}.
 \item Das, Soumya and Jha, Abhash Kumar, {\em Analytic properties of twisted real-analytic {H}ermitian
-{K}lingen type {E}isenstein series and applications}, Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116, DOI 10.1007/s12188-019-00206-7, \url{https://doi.org/10.1007/s12188-019-00206-7}.
+{K}lingen type {E}isenstein series and applications}, Abh. Math. Semin. Univ. Hambg. {\bf 89} (2019), 105--116, DOI 10.1007/s12188-019-00206-7, \url{https://doi.org/10.1007/s12188-019-00206-7}.
 \item Das, Soumya and Khan, Rizwanur, {\em The third moment of symmetric square {$L$}-functions}, Q.
 J.
-Math.} {\bf 69} (2018), 1063--1087, DOI 10.1093/qmath/hay012, \url{https://doi.org/10.1093/qmath/hay012}.
+Math.
+{\bf 69} (2018), 1063--1087, DOI 10.1093/qmath/hay012, \url{https://doi.org/10.1093/qmath/hay012}.
 \item Das, Soumya and Kohnen, Winfried, {\em On sign changes of eigenvalues of {S}iegel cusp forms of genus
-2 in prime powers}, Acta Arith.} {\bf 183} (2018), 167--172, DOI 10.4064/aa170419-4-11, \url{https://doi.org/10.4064/aa170419-4-11}.
+2 in prime powers}, Acta Arith. {\bf 183} (2018), 167--172, DOI 10.4064/aa170419-4-11, \url{https://doi.org/10.4064/aa170419-4-11}.
 \item Das, Soumya and Pal, Ritwik, {\em The first negative eigenvalue of {Y}oshida lifts}, Res.
-Number Theory} {\bf 5} (2019), Paper No.
+Number Theory {\bf 5} (2019), Paper No.
 20, 9, DOI 10.1007/s40993-019-0158-x, \url{https://doi.org/10.1007/s40993-019-0158-x}.
 \item Datta, Basudeb and Maity, Dipendu, {\em Semi-equivelar maps on the torus and the {K}lein bottle are
-{A}rchimedean}, Discrete Math.} {\bf 341} (2018), 3296--3309, DOI 10.1016/j.disc.2018.08.016, \url{https://doi.org/10.1016/j.disc.2018.08.016}.
+{A}rchimedean}, Discrete Math. {\bf 341} (2018), 3296--3309, DOI 10.1016/j.disc.2018.08.016, \url{https://doi.org/10.1016/j.disc.2018.08.016}.
 \item Dond, Asha K. and Gudi, Thirupathi, {\em Patch-wise local projection stabilized finite element methods
-for convection-diffusion-reaction problems}, Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663, DOI 10.1002/num.22317, \url{https://doi.org/10.1002/num.22317}.
+for convection-diffusion-reaction problems}, Numer. Methods Partial Differential Equations {\bf 35} (2019), 638--663, DOI 10.1002/num.22317, \url{https://doi.org/10.1002/num.22317}.
 \item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH., {\em An error analysis of discontinuous finite element methods for
@@
 Anal.
-Optim.} {\bf 40} (2019), 421--460, DOI 10.1080/01630563.2018.1538158, \url{https://doi.org/10.1080/01630563.2018.1538158}.
+Optim.
+{\bf 40} (2019), 421--460, DOI 10.1080/01630563.2018.1538158, \url{https://doi.org/10.1080/01630563.2018.1538158}.
 \item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P.
-and Silberman, Lior and Tao, Terence, {\em Homogeneous length functions on groups}, Algebra Number Theory} {\bf 12} (2018), 1773--1786, DOI 10.2140/ant.2018.12.1773, \url{https://doi.org/10.2140/ant.2018.12.1773}.
+and Silberman, Lior and Tao, Terence, {\em Homogeneous length functions on groups}, Algebra Number Theory {\bf 12} (2018), 1773--1786, DOI 10.2140/ant.2018.12.1773, \url{https://doi.org/10.2140/ant.2018.12.1773}.
 \item Gaddam, Sharat and Gudi, Thirupathi, {\em Inhomogeneous {D}irichlet boundary condition in the {\it a
-posteriori} error control of the obstacle problem}, Comput. Math. Appl.} {\bf 75} (2018), 2311--2327, DOI 10.1016/j.camwa.2017.12.010, \url{https://doi.org/10.1016/j.camwa.2017.12.010}.
+posteriori} error control of the obstacle problem}, Comput. Math. Appl. {\bf 75} (2018), 2311--2327, DOI 10.1016/j.camwa.2017.12.010, \url{https://doi.org/10.1016/j.camwa.2017.12.010}.
 \item Gaddam, Sharat and Gudi, Thirupathi, {\em Bubbles enriched quadratic finite element method for the
-3{D}-elliptic obstacle problem}, Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236, DOI 10.1515/cmam-2017-0018, \url{https://doi.org/10.1515/cmam-2017-0018}.
+3{D}-elliptic obstacle problem}, Comput. Methods Appl. Math. {\bf 18} (2018), 223--236, DOI 10.1515/cmam-2017-0018, \url{https://doi.org/10.1515/cmam-2017-0018}.
 \item Garani, Shayan Srinivasa and Seshadri, Harish, {\em An algorithmic approach to {S}outh {I}ndian classical music}, J.
 Math.
-Music} {\bf 13} (2019), 107--134, DOI 10.1080/17459737.2019.1604845, \url{https://doi.org/10.1080/17459737.2019.1604845}.
+Music {\bf 13} (2019), 107--134, DOI 10.1080/17459737.2019.1604845, \url{https://doi.org/10.1080/17459737.2019.1604845}.
 \item Gaussier, Herv\'{e} and Seshadri, Harish, {\em Holomorphic motions and complex geometry}, Proc.
@@
 Math.
-Soc.} {\bf 147} (2019), 301--313, DOI 10.1090/proc/14217, \url{https://doi.org/10.1090/proc/14217}.
+Soc.
+{\bf 147} (2019), 301--313, DOI 10.1090/proc/14217, \url{https://doi.org/10.1090/proc/14217}.
 \item Gaussier, Herv\'{e} and Seshadri, Harish, {\em On the {G}romov hyperbolicity of convex domains in {$\Bbb
-C^n$}}, Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641, DOI 10.1007/s40315-018-0243-5, \url{https://doi.org/10.1007/s40315-018-0243-5}.
+C^n$}}, Comput. Methods Funct. Theory {\bf 18} (2018), 617--641, DOI 10.1007/s40315-018-0243-5, \url{https://doi.org/10.1007/s40315-018-0243-5}.
 \item Ghara, Soumitra and Kumar, Surjit, {\em On the sum of two subnormal kernels}, J.
@@
 Anal.
-Appl.} {\bf 469} (2019), 1015--1027, DOI 10.1016/j.jmaa.2018.09.048, \url{https://doi.org/10.1016/j.jmaa.2018.09.048}.
+Appl.
+{\bf 469} (2019), 1015--1027, DOI 10.1016/j.jmaa.2018.09.048, \url{https://doi.org/10.1016/j.jmaa.2018.09.048}.
 \item Ghosh, Mrinal K. and Pradhan, Somnath, {\em Risk-sensitive stochastic differential games with reflecting
-diffusions}, Stoch. Anal. Appl.} {\bf 36} (2018), 1--27, DOI 10.1080/07362994.2017.1356732, \url{https://doi.org/10.1080/07362994.2017.1356732}.
+diffusions}, Stoch. Anal. Appl. {\bf 36} (2018), 1--27, DOI 10.1080/07362994.2017.1356732, \url{https://doi.org/10.1080/07362994.2017.1356732}.
 \item Gudi, Thirupathi and Majumder, Papri, {\em Convergence analysis of finite element method for a parabolic
-obstacle problem}, J. Comput. Appl. Math.} {\bf 357} (2019), 85--102, DOI 10.1016/j.cam.2019.02.026, \url{https://doi.org/10.1016/j.cam.2019.02.026}.
+obstacle problem}, J. Comput. Appl. Math. {\bf 357} (2019), 85--102, DOI 10.1016/j.cam.2019.02.026, \url{https://doi.org/10.1016/j.cam.2019.02.026}.
 \item Gudi, Thirupathi and Majumder, Papri, {\em Conforming and discontinuous {G}alerkin {FEM} in space for
-solving parabolic obstacle problem}, Comput. Math. Appl.} {\bf 78} (2019), 3896--3915, DOI 10.1016/j.camwa.2019.06.022, \url{https://doi.org/10.1016/j.camwa.2019.06.022}.
+solving parabolic obstacle problem}, Comput. Math. Appl. {\bf 78} (2019), 3896--3915, DOI 10.1016/j.camwa.2019.06.022, \url{https://doi.org/10.1016/j.camwa.2019.06.022}.
 \item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh, {\em Von {N}eumann's inequality for commuting operator-valued
-multishifts}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608, DOI 10.1090/proc/14410, \url{https://doi.org/10.1090/proc/14410}.
-\item Gupta, Rajeev and Ramiz Reza, Md., {\em Operator space structures on {$\ell^1(n)$}}, Houston J. Math.} {\bf 44} (2018), 1205--1212.
-\item Gupta, S. C., {\em The classical {S}tefan problem}, } {\bf } (2018), xxiii+726.
+multishifts}, Proc. Amer. Math. Soc. {\bf 147} (2019), 2599--2608, DOI 10.1090/proc/14410, \url{https://doi.org/10.1090/proc/14410}.
+\item Gupta, Rajeev and Ramiz Reza, Md., {\em Operator space structures on {$\ell^1(n)$}}, Houston J. Math. {\bf 44} (2018), 1205--1212.
+\item Gupta, S. C., {\em The classical {S}tefan problem},  {\bf } (2018), xxiii+726.
 \item Gupta, Subhojoy, {\em Limits of harmonic maps and crowned hyperbolic surfaces}, Trans.
@@
 Math.
-Soc.} {\bf 372} (2019), 7573--7596, DOI 10.1090/tran/7777, \url{https://doi.org/10.1090/tran/7777}.
+Soc.
+{\bf 372} (2019), 7573--7596, DOI 10.1090/tran/7777, \url{https://doi.org/10.1090/tran/7777}.
 \item Gupta, Subhojoy and Wolf, Michael, {\em Meromorphic quadratic differentials and measured foliations on
-a {R}iemann surface}, Math. Ann.} {\bf 373} (2019), 73--118, DOI 10.1007/s00208-018-1674-z, \url{https://doi.org/10.1007/s00208-018-1674-z}.
-\item Hazra, Somnath, {\em Homogeneous 2-shifts}, Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763, DOI 10.1007/s11785-018-0822-5, \url{https://doi.org/10.1007/s11785-018-0822-5}.
+a {R}iemann surface}, Math. Ann. {\bf 373} (2019), 73--118, DOI 10.1007/s00208-018-1674-z, \url{https://doi.org/10.1007/s00208-018-1674-z}.
+\item Hazra, Somnath, {\em Homogeneous 2-shifts}, Complex Anal. Oper. Theory {\bf 13} (2019), 1729--1763, DOI 10.1007/s11785-018-0822-5, \url{https://doi.org/10.1007/s11785-018-0822-5}.
 \item Iyer, Srikanth K., {\em The random connection model: connectivity, edge lengths, and
-degree distributions}, Random Structures Algorithms} {\bf 52} (2018), 283--300, DOI 10.1002/rsa.20741, \url{https://doi.org/10.1002/rsa.20741}.
+degree distributions}, Random Structures Algorithms {\bf 52} (2018), 283--300, DOI 10.1002/rsa.20741, \url{https://doi.org/10.1002/rsa.20741}.
 \item Jha, Abhash Kumar and Juyal, Abhishek and Pandey, Manish
 Kumar, {\em On simultaneous non-vanishing of twisted {$L$}-functions
-associated to newforms on {$\Gamma_0(N)$}}, J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.
+associated to newforms on {$\Gamma_0(N)$}}, J. Ramanujan Math. Soc. {\bf 34} (2019), 245--252.
 \item Jha, Abhash Kumar and Sahu, Brundaban, {\em Rankin-{C}ohen brackets on {J}acobi forms of several variables
-and special values of certain {D}irichlet series}, Int. J. Number Theory} {\bf 15} (2019), 925--933, DOI 10.1142/S1793042119500490, \url{https://doi.org/10.1142/S1793042119500490}.
+and special values of certain {D}irichlet series}, Int. J. Number Theory {\bf 15} (2019), 925--933, DOI 10.1142/S1793042119500490, \url{https://doi.org/10.1142/S1793042119500490}.
 \item Jha, Abhash Kumar and Sahu, Brundaban, {\em Differential operators on {J}acobi forms and special values of
-certain {D}irichlet series}, Automorphic forms and related topics} {\bf 732} (2019), 91--99, DOI 10.1090/conm/732/14793, \url{https://doi.org/10.1090/conm/732/14793}.
+certain {D}irichlet series}, Automorphic forms and related topics {\bf 732} (2019), 91--99, DOI 10.1090/conm/732/14793, \url{https://doi.org/10.1090/conm/732/14793}.
 \item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
-Sekar, Sruthi, {\em Non-malleable randomness encoders and their applications}, Advances in cryptology---{EUROCRYPT} 2018. {P}art {III}} {\bf 10822} (2018), 589--617.
+Sekar, Sruthi, {\em Non-malleable randomness encoders and their applications}, Advances in cryptology---{EUROCRYPT} 2018. {P}art {III} {\bf 10822} (2018), 589--617.
 \item Kashyap, G.
@@
 Ravindranath and G.
-Ambika, {\em Synapse loss and progress of Alzheimer&rsquo;s disease - A network model}, Scientific Reports} {\bf 9} (2019), .
+Ambika, {\em Synapse loss and progress of Alzheimers disease - A network model}, Scientific Reports {\bf 9} (2019), .
 \item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan, {\em On the convolution of {M}ittag-{L}effler distributions and its
-applications to fractional point processes}, Stoch. Anal. Appl.} {\bf 37} (2019), 115--122, DOI 10.1080/07362994.2018.1538803, \url{https://doi.org/10.1080/07362994.2018.1538803}.
+applications to fractional point processes}, Stoch. Anal. Appl. {\bf 37} (2019), 115--122, DOI 10.1080/07362994.2018.1538803, \url{https://doi.org/10.1080/07362994.2018.1538803}.
 \item Khan, Mohammad Yasir Feroz and Biswas, Rahul and Sau, Ramesh
 Chandra, {\em Instability of {L}agrange interpolation on {$H^1(\Omega)\cap
-C(\overline\Omega)$}}, Math. Student} {\bf 88} (2019), 153--158.
+C(\overline\Omega)$}}, Math. Student {\bf 88} (2019), 153--158.
 \item Khare, Apoorva, {\em Generalized nil-{C}oxeter algebras over discrete complex
-reflection groups}, Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999, DOI 10.1090/tran/7304, \url{https://doi.org/10.1090/tran/7304}.
-\item Khare, Apoorva and Tikaradze, Akaki, {\em A {C}arlitz--von {S}taudt type theorem for finite rings}, Linear Algebra Appl.} {\bf 568} (2019), 106--126, DOI 10.1016/j.laa.2018.05.035, \url{https://doi.org/10.1016/j.laa.2018.05.035}.
+reflection groups}, Trans. Amer. Math. Soc. {\bf 370} (2018), 2971--2999, DOI 10.1090/tran/7304, \url{https://doi.org/10.1090/tran/7304}.
+\item Khare, Apoorva and Tikaradze, Akaki, {\em A {C}arlitz--von {S}taudt type theorem for finite rings}, Linear Algebra Appl.
+{\bf 568} (2019), 106--126, DOI 10.1016/j.laa.2018.05.035, \url{https://doi.org/10.1016/j.laa.2018.05.035}.
 \item Krakovski, Roi and Onn, Uri and Singla, Pooja, {\em Regular characters of groups of type {$\ssf A_n$} over
-discrete valuation rings}, J. Algebra} {\bf 496} (2018), 116--137, DOI 10.1016/j.jalgebra.2017.10.018, \url{https://doi.org/10.1016/j.jalgebra.2017.10.018}.
+discrete valuation rings}, J. Algebra {\bf 496} (2018), 116--137, DOI 10.1016/j.jalgebra.2017.10.018, \url{https://doi.org/10.1016/j.jalgebra.2017.10.018}.
 \item Lin, X.
@@
 and Jolly, M.
-K., {\em Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level}, Biomolecules} {\bf 9} (2019), 77.
+K., {\em Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level}, Biomolecules {\bf 9} (2019), 77.
 \item Mahajan, Prachi and Verma, Kaushal, {\em A comparison of two biholomorphic invariants}, Internat.
 J.
-Math.} {\bf 30} (2019), 1950012, 16, DOI 10.1142/S0129167X19500125, \url{https://doi.org/10.1142/S0129167X19500125}.
-\item Maity, Dipendu, {\em Pentagonal maps on the torus and the plane}, Beitr. Algebra Geom.} {\bf 60} (2019), 17--37, DOI 10.1007/s13366-018-0405-7, \url{https://doi.org/10.1007/s13366-018-0405-7}.
-\item Maity, Dipendu and Upadhyay, Ashish Kumar, {\em On centrally symmetric manifolds}, J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.
+Math.
+{\bf 30} (2019), 1950012, 16, DOI 10.1142/S0129167X19500125, \url{https://doi.org/10.1142/S0129167X19500125}.
+\item Maity, Dipendu, {\em Pentagonal maps on the torus and the plane}, Beitr. Algebra Geom. {\bf 60} (2019), 17--37, DOI 10.1007/s13366-018-0405-7, \url{https://doi.org/10.1007/s13366-018-0405-7}.
+\item Maity, Dipendu and Upadhyay, Ashish Kumar, {\em On centrally symmetric manifolds}, J. Ramanujan Math. Soc. {\bf 34} (2019), 21--27.
 \item Mal, Arpita and Paul, Kallol and Rao, T. S. S. R. K. and Sain,
 Debmalya, {\em Approximate {B}irkhoff-{J}ames orthogonality and smoothness in
-the space of bounded linear operators}, Monatsh. Math.} {\bf 190} (2019), 549--558, DOI 10.1007/s00605-019-01289-3, \url{https://doi.org/10.1007/s00605-019-01289-3}.
+the space of bounded linear operators}, Monatsh. Math. {\bf 190} (2019), 549--558, DOI 10.1007/s00605-019-01289-3, \url{https://doi.org/10.1007/s00605-019-01289-3}.
 \item Mal, Arpita and Sain, Debmalya and Paul, Kallol, {\em On some geometric properties of operator spaces}, Banach J.
 Math.
-Anal.} {\bf 13} (2019), 174--191, DOI 10.1215/17358787-2018-0021, \url{https://doi.org/10.1215/17358787-2018-0021}.
+Anal.
+{\bf 13} (2019), 174--191, DOI 10.1215/17358787-2018-0021, \url{https://doi.org/10.1215/17358787-2018-0021}.
 \item Manfio, F. and Turgay, N. C. and Upadhyay, A., {\em Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
-{$\Bbb{H}^n\times\Bbb{R}$}}, J. Geom. Anal.} {\bf 29} (2019), 283--298, DOI 10.1007/s12220-018-9990-9, \url{https://doi.org/10.1007/s12220-018-9990-9}.
+{$\Bbb{H}^n\times\Bbb{R}$}}, J. Geom. Anal. {\bf 29} (2019), 283--298, DOI 10.1007/s12220-018-9990-9, \url{https://doi.org/10.1007/s12220-018-9990-9}.
 \item Manikandan, K. and Vishnu Priya, N. and Senthilvelan, M. and
@@
 variable coefficients nonlocal nonlinear {S}chr\"{o}dinger
-equation}, Chaos} {\bf 28} (2018), 083103, 12, DOI 10.1063/1.5039901, \url{https://doi.org/10.1063/1.5039901}.
-\item Misra, Gadadhar, {\em Operators in the {C}owen-{D}ouglas class and related topics}, Handbook of analytic operator theory} {\bf } (2019), 87--137.
+equation}, Chaos {\bf 28} (2018), 083103, 12, DOI 10.1063/1.5039901, \url{https://doi.org/10.1063/1.5039901}.
+\item Misra, Gadadhar, {\em Operators in the {C}owen-{D}ouglas class and related topics}, Handbook of analytic operator theory {\bf } (2019), 87--137.
 \item Misra, Gadadhar and Pal, Avijit, {\em Curvature inequalities for operators in the {C}owen-{D}ouglas
-class and localization of the {W}allach set}, J. Anal. Math.} {\bf 136} (2018), 31--54, DOI 10.1007/s11854-018-0054-7, \url{https://doi.org/10.1007/s11854-018-0054-7}.
+class and localization of the {W}allach set}, J. Anal. Math. {\bf 136} (2018), 31--54, DOI 10.1007/s11854-018-0054-7, \url{https://doi.org/10.1007/s11854-018-0054-7}.
 \item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian, {\em Contractivity and complete contractivity for finite
-dimensional {B}anach spaces}, J. Operator Theory} {\bf 82} (2019), 23--47, DOI 10.7900/jot.2018jun13.2225, \url{https://doi.org/10.7900/jot.2018jun13.2225}.
+dimensional {B}anach spaces}, J. Operator Theory {\bf 82} (2019), 23--47, DOI 10.7900/jot.2018jun13.2225, \url{https://doi.org/10.7900/jot.2018jun13.2225}.
 \item Misra, Gadadhar and Reza, Md.
 Ramiz, {\em Curvature inequalities and extremal operators}, Illinois J.
-Math.} {\bf 63} (2019), 193--217, DOI 10.1215/00192082-7768711, \url{https://doi.org/10.1215/00192082-7768711}.
+Math.
+{\bf 63} (2019), 193--217, DOI 10.1215/00192082-7768711, \url{https://doi.org/10.1215/00192082-7768711}.
 \item Mukherjee, Sajal Kumar and Bera, Sudip, {\em Combinatorial proofs of the {N}ewton-{G}irard and
-{C}hapman-{C}ostas-{S}antos identities}, Discrete Math.} {\bf 342} (2019), 1577--1580, DOI 10.1016/j.disc.2019.02.013, \url{https://doi.org/10.1016/j.disc.2019.02.013}.
+{C}hapman-{C}ostas-{S}antos identities}, Discrete Math. {\bf 342} (2019), 1577--1580, DOI 10.1016/j.disc.2019.02.013, \url{https://doi.org/10.1016/j.disc.2019.02.013}.
 \item Narayanan, E. K. and Singla, Pooja, {\em On monomial representations of finitely generated nilpotent
-groups}, Comm. Algebra} {\bf 46} (2018), 2319--2331, DOI 10.1080/00927872.2017.1378894, \url{https://doi.org/10.1080/00927872.2017.1378894}.
+groups}, Comm. Algebra {\bf 46} (2018), 2319--2331, DOI 10.1080/00927872.2017.1378894, \url{https://doi.org/10.1080/00927872.2017.1378894}.
 \item Pal, Chandan and Pradhan, Somnath, {\em Risk sensitive control of pure jump processes on a general
-state space}, Stochastics} {\bf 91} (2019), 155--174, DOI 10.1080/17442508.2018.1521413, \url{https://doi.org/10.1080/17442508.2018.1521413}.
+state space}, Stochastics {\bf 91} (2019), 155--174, DOI 10.1080/17442508.2018.1521413, \url{https://doi.org/10.1080/17442508.2018.1521413}.
 \item Pal, Ratna and Verma, Kaushal, {\em Ergodic properties of families of {H}\'{e}non maps}, Ann.
 Polon.
-Math.} {\bf 121} (2018), 45--71, DOI 10.4064/ap170928-2-4, \url{https://doi.org/10.4064/ap170928-2-4}.
+Math.
+{\bf 121} (2018), 45--71, DOI 10.4064/ap170928-2-4, \url{https://doi.org/10.4064/ap170928-2-4}.
 \item Paul, Kallol and Sain, Debmalya, {\em Birkhoff-{J}ames orthogonality and its application in the
-study of geometry of {B}anach space}, Advanced topics in mathematical analysis} {\bf } (2019), 245--284.
+study of geometry of {B}anach space}, Advanced topics in mathematical analysis {\bf } (2019), 245--284.
 \item Paul, Kallol and Sain, Debmalya and Ghosh, Puja, {\em Symmetry of {B}irkhoff-{J}ames orthogonality of bounded linear
-operators}, Ulam type stability} {\bf } (2019), 331--344.
+operators}, Ulam type stability {\bf } (2019), 331--344.
 \item Paul, Kallol and Sain, Debmalya and Mal, Arpita, {\em Approximate {B}irkhoff-{J}ames orthogonality in the space of
-bounded linear operators}, Linear Algebra Appl.} {\bf 537} (2018), 348--357, DOI 10.1016/j.laa.2017.10.008, \url{https://doi.org/10.1016/j.laa.2017.10.008}.
+bounded linear operators}, Linear Algebra Appl. {\bf 537} (2018), 348--357, DOI 10.1016/j.laa.2017.10.008, \url{https://doi.org/10.1016/j.laa.2017.10.008}.
 \item Paul, Kallol and Sain, Debmalya and Mal, Arpita and Mandal,
 Kalidas, {\em Orthogonality of bounded linear operators on complex {B}anach
-spaces}, Adv. Oper. Theory} {\bf 3} (2018), 699--709, DOI 10.15352/aot.1712-1268, \url{https://doi.org/10.15352/aot.1712-1268}.
+spaces}, Adv. Oper. Theory {\bf 3} (2018), 699--709, DOI 10.15352/aot.1712-1268, \url{https://doi.org/10.15352/aot.1712-1268}.
 \item Pingali, Vamsi P., {\em A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE}}, Complex Var.
-Elliptic Equ.} {\bf 64} (2019), 503--518, DOI 10.1080/17476933.2018.1454914, \url{https://doi.org/10.1080/17476933.2018.1454914}.
-\item Pingali, Vamsi Pritham, {\em A note on higher extremal metrics}, Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010, DOI 10.1090/tran/7416, \url{https://doi.org/10.1090/tran/7416}.
-\item Pingali, Vamsi Pritham, {\em Representability of {C}hern-{W}eil forms}, Math. Z.} {\bf 288} (2018), 629--641, DOI 10.1007/s00209-017-1903-2, \url{https://doi.org/10.1007/s00209-017-1903-2}.
+Elliptic Equ.
+{\bf 64} (2019), 503--518, DOI 10.1080/17476933.2018.1454914, \url{https://doi.org/10.1080/17476933.2018.1454914}.
+\item Pingali, Vamsi Pritham, {\em A note on higher extremal metrics}, Trans. Amer. Math. Soc. {\bf 370} (2018), 6995--7010, DOI 10.1090/tran/7416, \url{https://doi.org/10.1090/tran/7416}.
+\item Pingali, Vamsi Pritham, {\em Representability of {C}hern-{W}eil forms}, Math. Z. {\bf 288} (2018), 629--641, DOI 10.1007/s00209-017-1903-2, \url{https://doi.org/10.1007/s00209-017-1903-2}.
 \item Pritham Pingali, Vamsi, {\em Existence of coupled {K}\"{a}hler-{E}instein metrics using the
-continuity method}, Internat. J. Math.} {\bf 29} (2018), 1850041, 8, DOI 10.1142/S0129167X18500416, \url{https://doi.org/10.1142/S0129167X18500416}.
+continuity method}, Internat. J. Math. {\bf 29} (2018), 1850041, 8, DOI 10.1142/S0129167X18500416, \url{https://doi.org/10.1142/S0129167X18500416}.
 \item Quddus, Safdar, {\em Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
-spheres}, J. Noncommut. Geom.} {\bf 13} (2019), 257--267, DOI 10.4171/JNCG/320, \url{https://doi.org/10.4171/JNCG/320}.
+spheres}, J. Noncommut. Geom. {\bf 13} (2019), 257--267, DOI 10.4171/JNCG/320, \url{https://doi.org/10.4171/JNCG/320}.
 \item Reddy, Nanda Kishore, {\em Equality of {L}yapunov and stability exponents for products of
-isotropic random matrices}, Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624, DOI 10.1093/imrn/rnx134, \url{https://doi.org/10.1093/imrn/rnx134}.
+isotropic random matrices}, Int. Math. Res. Not. IMRN {\bf } (2019), 606--624, DOI 10.1093/imrn/rnx134, \url{https://doi.org/10.1093/imrn/rnx134}.
 \item Reza, Md. Ramiz, {\em Curvature inequalities for operators in the {C}owen-{D}ouglas
-class of a planar domain}, Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279, DOI 10.1512/iumj.2018.67.7320, \url{https://doi.org/10.1512/iumj.2018.67.7320}.
+class of a planar domain}, Indiana Univ. Math. J. {\bf 67} (2018), 1255--1279, DOI 10.1512/iumj.2018.67.7320, \url{https://doi.org/10.1512/iumj.2018.67.7320}.
 \item Roth, Julien and Upadhyay, Abhitosh, {\em On compact anisotropic {W}eingarten hypersurfaces in
-{E}uclidean space}, Arch. Math. (Basel)} {\bf 113} (2019), 213--224, DOI 10.1007/s00013-019-01315-8, \url{https://doi.org/10.1007/s00013-019-01315-8}.
+{E}uclidean space}, Arch. Math. (Basel) {\bf 113} (2019), 213--224, DOI 10.1007/s00013-019-01315-8, \url{https://doi.org/10.1007/s00013-019-01315-8}.
 \item Roy, Krishanu and Venkatesh, R., {\em Maximal closed subroot systems of real affine root systems}, Transform.
-Groups} {\bf 24} (2019), 1261--1308, DOI 10.1007/s00031-018-9510-9, \url{https://doi.org/10.1007/s00031-018-9510-9}.
+Groups {\bf 24} (2019), 1261--1308, DOI 10.1007/s00031-018-9510-9, \url{https://doi.org/10.1007/s00031-018-9510-9}.
 \item Sain, Debmalya, {\em On extreme contractions and the norm attainment set of a
-bounded linear operator}, Ann. Funct. Anal.} {\bf 10} (2019), 135--143, DOI 10.1215/20088752-2018-0014, \url{https://doi.org/10.1215/20088752-2018-0014}.
+bounded linear operator}, Ann. Funct. Anal. {\bf 10} (2019), 135--143, DOI 10.1215/20088752-2018-0014, \url{https://doi.org/10.1215/20088752-2018-0014}.
 \item Sain, Debmalya, {\em On the norm attainment set of a bounded linear operator}, J.
@@
 Anal.
-Appl.} {\bf 457} (2018), 67--76, DOI 10.1016/j.jmaa.2017.07.070, \url{https://doi.org/10.1016/j.jmaa.2017.07.070}.
+Appl.
+{\bf 457} (2018), 67--76, DOI 10.1016/j.jmaa.2017.07.070, \url{https://doi.org/10.1016/j.jmaa.2017.07.070}.
 \item Sain, Debmalya, {\em Smooth points in operator spaces and some
-{B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces}, Oper. Matrices} {\bf 13} (2019), 433--445, DOI 10.7153/oam-2019-13-32, \url{https://doi.org/10.7153/oam-2019-13-32}.
+{B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces}, Oper. Matrices {\bf 13} (2019), 433--445, DOI 10.7153/oam-2019-13-32, \url{https://doi.org/10.7153/oam-2019-13-32}.
 \item Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag,
-Santanu, {\em On the numerical index of polyhedral {B}anach spaces}, Linear Algebra Appl.} {\bf 577} (2019), 121--133, DOI 10.1016/j.laa.2019.04.024, \url{https://doi.org/10.1016/j.laa.2019.04.024}.
+Santanu, {\em On the numerical index of polyhedral {B}anach spaces}, Linear Algebra Appl. {\bf 577} (2019), 121--133, DOI 10.1016/j.laa.2019.04.024, \url{https://doi.org/10.1016/j.laa.2019.04.024}.
 \item Sain, Debmalya and Paul, Kallol and Mal, Arpita, {\em A complete characterization of {B}irkhoff-{J}ames
-orthogonality in infinite dimensional normed space}, J. Operator Theory} {\bf 80} (2018), 399--413.
+orthogonality in infinite dimensional normed space}, J. Operator Theory {\bf 80} (2018), 399--413.
 \item Sain, Debmalya and Paul, Kallol and Mal, Arpita, {\em On approximate {B}irkhoff-{J}ames orthogonality and normal
-cones in a normed space}, J. Convex Anal.} {\bf 26} (2019), 341--351.
+cones in a normed space}, J. Convex Anal. {\bf 26} (2019), 341--351.
 \item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas, {\em On two extremum problems related to the norm of a bounded
-linear operator}, Oper. Matrices} {\bf 13} (2019), 421--432, DOI 10.7153/oam-2019-13-31, \url{https://doi.org/10.7153/oam-2019-13-31}.
+linear operator}, Oper. Matrices {\bf 13} (2019), 421--432, DOI 10.7153/oam-2019-13-31, \url{https://doi.org/10.7153/oam-2019-13-31}.
 \item Sain, Debmalya and Ray, Anubhab and Paul, Kallol, {\em Extreme contractions on finite-dimensional polygonal {B}anach
-spaces}, J. Convex Anal.} {\bf 26} (2019), 877--885.
-\item Sanki, Bidyut, {\em Filling of closed surfaces}, J. Topol. Anal.} {\bf 10} (2018), 897--913, DOI 10.1142/S1793525318500309, \url{https://doi.org/10.1142/S1793525318500309}.
+spaces}, J. Convex Anal. {\bf 26} (2019), 877--885.
+\item Sanki, Bidyut, {\em Filling of closed surfaces}, J. Topol. Anal. {\bf 10} (2018), 897--913, DOI 10.1142/S1793525318500309, \url{https://doi.org/10.1142/S1793525318500309}.
 \item Sanki, Bidyut and Gadgil, Siddhartha, {\em Graphs of systoles on hyperbolic surfaces}, J.
 Topol.
-Anal.} {\bf 11} (2019), 1--20, DOI 10.1142/S1793525319500018, \url{https://doi.org/10.1142/S1793525319500018}.
-\item Seshadri, Harish, {\em Differential geometry in {I}ndia}, Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799, DOI 10.1007/s13226-019-0355-2, \url{https://doi.org/10.1007/s13226-019-0355-2}.
-\item Seshadri, Harish and Verma, Kaushal, {\em Some aspects of the automorphism groups of domains}, Handbook of group actions. {V}ol. {III}} {\bf 40} (2018), 145--174.
+Anal.
+{\bf 11} (2019), 1--20, DOI 10.1142/S1793525319500018, \url{https://doi.org/10.1142/S1793525319500018}.
+\item Seshadri, Harish, {\em Differential geometry in {I}ndia}, Indian J. Pure Appl. Math. {\bf 50} (2019), 795--799, DOI 10.1007/s13226-019-0355-2, \url{https://doi.org/10.1007/s13226-019-0355-2}.
+\item Seshadri, Harish and Verma, Kaushal, {\em Some aspects of the automorphism groups of domains}, Handbook of group actions. {V}ol. {III} {\bf 40} (2018), 145--174.
 \item Thangavelu, Sundaram, {\em An analogue of {P}fannschmidt's theorem for the {H}eisenberg
-group}, J. Anal.} {\bf 26} (2018), 235--244, DOI 10.1007/s41478-018-0147-9, \url{https://doi.org/10.1007/s41478-018-0147-9}.
+group}, J. Anal. {\bf 26} (2018), 235--244, DOI 10.1007/s41478-018-0147-9, \url{https://doi.org/10.1007/s41478-018-0147-9}.
 \item Thangavelu, Sundaram and Naidu Dogga, Venku, {\em {$L^p$}-{$L^2$} estimates for solutions of the wave equation
-associated to the {G}rushin operator}, Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92, DOI 10.1515/apam-2017-0042, \url{https://doi.org/10.1515/apam-2017-0042}.
+associated to the {G}rushin operator}, Adv. Pure Appl. Math. {\bf 9} (2018), 85--92, DOI 10.1515/apam-2017-0042, \url{https://doi.org/10.1515/apam-2017-0042}.
 \item Turgay, Nurettin Cenk and Upadhyay, Abhitosh, {\em On biconservative hypersurfaces in 4-dimensional {R}iemannian
-space forms}, Math. Nachr.} {\bf 292} (2019), 905--921, DOI 10.1002/mana.201700328, \url{https://doi.org/10.1002/mana.201700328}.
-\item Urbina-Romero, Wilfredo, {\em Gaussian harmonic analysis}, } {\bf } (2019), xix+477, DOI 10.1007/978-3-030-05597-4, \url{https://doi.org/10.1007/978-3-030-05597-4}.
-\item Verma, Kaushal, {\em Notes on the boundaries of quadrature domains}, Anal. Math. Phys.} {\bf 9} (2019), 617--638, DOI 10.1007/s13324-018-0221-0, \url{https://doi.org/10.1007/s13324-018-0221-0}.
+space forms}, Math. Nachr. {\bf 292} (2019), 905--921, DOI 10.1002/mana.201700328, \url{https://doi.org/10.1002/mana.201700328}.
+\item Urbina-Romero, Wilfredo, {\em Gaussian harmonic analysis},  {\bf } (2019), xix+477, DOI 10.1007/978-3-030-05597-4, \url{https://doi.org/10.1007/978-3-030-05597-4}.
+\item Verma, Kaushal, {\em Notes on the boundaries of quadrature domains}, Anal. Math. Phys. {\bf 9} (2019), 617--638, DOI 10.1007/s13324-018-0221-0, \url{https://doi.org/10.1007/s13324-018-0221-0}.
 \item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan,
@@
 between nonlinear modes of coupled generalized nonlinear
-{S}chr\"{o}dinger equation}, Chaos} {\bf 29} (2019), 123135, 14, DOI 10.1063/1.5121245, \url{https://doi.org/10.1063/1.5121245}.
+{S}chr\"{o}dinger equation}, Chaos {\bf 29} (2019), 123135, 14, DOI 10.1063/1.5121245, \url{https://doi.org/10.1063/1.5121245}.
 \item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, Govindan
@@
 antidark soliton solutions of nonlocal nonlinear {S}chr\"{o}dinger
-equation}, Phys. Lett. A} {\bf 383} (2019), 15--26, DOI 10.1016/j.physleta.2018.10.011, \url{https://doi.org/10.1016/j.physleta.2018.10.011}.
+equation}, Phys. Lett. A {\bf 383} (2019), 15--26, DOI 10.1016/j.physleta.2018.10.011, \url{https://doi.org/10.1016/j.physleta.2018.10.011}.
 \end{enumerate}

### 2020-08-06 ugc/src/Data.scala

@@ -78,7 +78,7 @@ ${summerStudents.map(s => "\\item " + s).mkString("\n")}
 \\section{Resource Generation}
 
 \\begin{enumerate}
-${grantsItems.mkString("\n")}
+${grantsItems.mkString("\n").replace("&", "\\&")}
 \\end{enumerate}
 """
 
@@ -88,17 +88,27 @@ ${grantsItems.mkString("\n")}
     .map(d => s"\\subsection{${d.name}}\n\n${d.researchHighlights}")
     .mkString("\n\n\n")
 
-  lazy val awards = facultyData.flatMap(f => f.awards.awardOpt(f.name)) ++ postDocData.flatMap(f => f.awards)
+  lazy val awards = facultyData.flatMap(f => f.awards.awardOpt(f.name)) ++ (postDocData.flatMap(f => f.awardOpt(f.name)))
 
-  lazy val fellows = facultyData.flatMap(f => f.awards.fellowOpt(f.name)) ++ postDocData.flatMap(f => f.assoc)
+  lazy val fellows = facultyData.flatMap(f => f.awards.fellowOpt(f.name)) ++ postDocData
+    .flatMap(f => f.fellowOpt(f.name))
 
   lazy val editors = facultyData.flatMap(f => f.awards.edOpt(f.name))
 
-  lazy val otherOld = facultyData.flatMap(f => 
-    f.otherOld.map(act => s"\\item ${f.name} was $act"))
+  lazy val otherOld = facultyData.flatMap(
+    f => f.otherOld.map(act => s"\\item ${f.name} was $act")
+  )
 
-  lazy val other  = facultyData.flatMap(f => 
-    f.otherActivities.map(act => s"\\item ${f.name} was $act"))
+  lazy val other = facultyData.flatMap(
+    f => f.otherActivities.map(act => s"\\item ${f.name} was $act")
+  )
+
+  def enumString(v: Vector[String]) =
+    if (v.isEmpty) ""
+    else s"""|\\begin{enumerate}
+             |${v.mkString("\n")}
+             |\\end{enumerate}
+             |""".stripMargin
 
   lazy val draftSections =
     s"""
@@ -108,30 +118,20 @@ $grants
 
 \\subsection{Awards}
 
-\\begin{enumerate}
-${awards.mkString("\n")}
-\\end{enumerate}
+${enumString(awards)}
 
 \\subsection{Fellowships of Academies}
 
-\\begin{enumerate}
-${fellows.mkString("\n")}
-\\end{enumerate}
[…]

### 2020-08-06 ugc/src/Publications.scala

@@ -46,11 +46,11 @@ object Publications {
     val pages = m.getOrElse("pages", "")
     val volume = m.getOrElse("volume", "")
     val year = m("year")
-    val doiOpt = m.get("doi")
+    val doiOpt = m.get("doi").map(_.replace("_", "\\_"))
     val urlOpt = m.get("url")
     val doiText = doiOpt.map(s =>s", DOI $s").getOrElse("")
     val urlText = urlOpt.map(s => s", \\url{$s}").getOrElse("")
-    s"\\item $author, {\\em $title}, $journal} {\\bf $volume} ($year), $pages$doiText$urlText."
+    s"\\item $author, {\\em $title}, $journal {\\bf $volume} ($year), $pages$doiText$urlText."
   }
 
   lazy val pubItems = allPubs.map(tex)

### 2020-08-07 data/draft-publications.tex
code for visitors, generating

--- 2020-08-05 data/draft-publications.tex
@@
 K.
-Nandakumaran and Abu Sufian, \emph{Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure},  Mathematical Methods in the Applied Sciences {\bf 42} (2019.
-DOI: 10.1002/mma.5748), 6407-6434 , DOI 10.1002/mma.5748.
+Nandakumaran and Abu Sufian: Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure, \emph{Mathematical Methods in the Applied Sciences} {\bf 42} (2019.
+DOI: 10.1002/mma.5748), 6407-6434, DOI 10.1002/mma.5748.
 \item K.
@@
 K.
-Nandakumaran, Turgurt Durduran, Hari M Varma, \emph{Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements}, Biomedical Optics Express 5395 {\bf 10} (2019), .
+Nandakumaran, Turgurt Durduran, Hari M Varma: Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements, \emph{Biomedical Optics Express 5395} {\bf 10} (2019).
 \item S Aiyappan, A.
 K.
-Nandakumaran and Ravi Prakash, \emph{Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains}, Annali di Matematica Pura ed Applicata {\bf 198} (2019), 1931-1954, DOI 10.1007/s10231-019-00848-7.
+Nandakumaran and Ravi Prakash: Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains, \emph{Annali di Matematica Pura ed Applicata} {\bf 198} (2019), 1931-1954, DOI 10.1007/s10231-019-00848-7.
 \item S Aiyappan, A.
 K.
-Nandakumaran and Ravi Prakash, \emph{Semi-linear optimal control problem on a smooth oscillating domain}, Communications in Contemporary Mathematics {\bf } (2019), 1-26, DOI 10.1142/S0219199719500299.
+Nandakumaran and Ravi Prakash: Semi-linear optimal control problem on a smooth oscillating domain, \emph{Communications in Contemporary Mathematics} {\bf } (2019), 1-26, DOI 10.1142/S0219199719500299.
 \item S Aiyappan, Editha C.
@@
 K.
-Nandakumaran, \emph{ Control Problem on a Rough Circular Domain and Homogenization}, Asymptotic Analysis {\bf 115} (2019),  19-46, DOI 10.3233/ASY-191526.
-\item Khare, Apoorva and Rajaratnam, Bala, \emph{Probability inequalities and tail estimates for metric semigroups}, Advances in Operator Theory (Special issue in honor of Rajendra Bhatia) {\bf 5} (2020), 779-795, DOI 10.1007/s43036-020-00048-8, \url{https://link.springer.com/article/10.1007%2Fs43036-020-00048-8}.
-\item Ghosh, Subhajit, \emph{Total Variation Cutoff for the Transpose Top-2 with Random Shuffle}, to appear in Journal of Theoretical Probability, DOI 10.1007/s10959-019-00945-6, \url{https://link.springer.com/article/10.1007%2Fs10959-019-00945-6}.
+Nandakumaran: Control Problem on a Rough Circular Domain and Homogenization, \emph{Asymptotic Analysis} {\bf 115} (2019), 19-46, DOI 10.3233/ASY-191526.
+\item M. Balodi, A. Banerjee, S. Ray: Cohomology of modules over H-categories and co-H-categories, to appear in \emph{Canadian Journal of Mathematics}, \url{https://doi.org/10.4153/S0008414X19000403}.
+\item M.
+Balodi, A.
+Banerjee, S.
+Ray: Entwined modules over linear categories and Galois extensions, to appear in \emph{Israel Journal of Mathematics (Accepted)}, DOI (accepted), \url{https://arxiv.org/abs/1901.00323}.
+\item A.
+Banerjee: On Noetherian schemes over $(\mathcal C,\otimes,1)$ and the category of quasi-coherent sheaves, to appear in \emph{Indiana University Mathematics Journal}, \url{http://www.iumj.indiana.edu/IUMJ/Preprints/8267.pdf}.
+\item A.
+Banerjee: On differential torsion theories and rings with several objects, \emph{Canadian Math Bulletin} {\bf 62} (2019), 703--714, \url{https://www.cambridge.org/core/journals/canadian-mathematical-bulletin/article/on-differential-torsion-theories-and-rings-with-several-objects/574D81145FAAAD6B7C5648253FA41833}.
+\item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric semigroups, \emph{Advances in Operator Theory (Special issue in honor of Rajendra Bhatia)} {\bf 5} (2020), 779-795, DOI 10.1007/s43036-020-00048-8, \url{https://link.springer.com/article/10.1007%2Fs43036-020-00048-8}.
+\item Ghosh, Subhajit: Total Variation Cutoff for the Transpose Top-2 with Random Shuffle, to appear in \emph{Journal of Theoretical Probability}, DOI 10.1007/s10959-019-00945-6, \url{https://link.springer.com/article/10.1007%2Fs10959-019-00945-6}.
 \item Datta, B.
-and Gupta, S., \emph{Semi-regular tilings of the hyperbolic plane \label{bdsg_2019} }, to appear in Discrete Comput Geom, DOI https://doi.org/10.1007/s00454-019-00156-0, \url{https://doi.org/10.1007/s00454-019-00156-0}.
-\item Datta, B. and Sarkar, S., \emph{Equilibrium triangulations of some quasitoric 4-manifolds}, Southeast Asian Bull. Math. {\bf 44} (2020), 57--78.
-\item Datta, B. and Maity, D., \emph{Correction to: Semi-equivelar and vertex-transitive maps on the torus}, Beitr Algebra Geom {\bf 61} (2020), 187--188.
+and Gupta, S.: Semi-regular tilings of the hyperbolic plane \label{bdsg_2019}, to appear in \emph{Discrete Comput Geom}, DOI https://doi.org/10.1007/s00454-019-00156-0, \url{https://doi.org/10.1007/s00454-019-00156-0}.
+\item Datta, B. and Sarkar, S.: Equilibrium triangulations of some quasitoric 4-manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57--78.
+\item Datta, B. and Maity, D.: Correction to: Semi-equivelar and vertex-transitive maps on the torus, \emph{Beitr Algebra Geom} {\bf 61} (2020), 187--188.
 \item Martin Kreuzer and Dilip P.
-Patil , \emph{COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS}, to appear in Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry.
-\item Bharali, Gautam and Maitra, Anwoy, \emph{A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems}, to appear in Annali della Scuola Normale Superiore di Pisa, DOI 10.2422/2036-2145.201906_007, \url{http://annaliscienze.sns.it/index.php?page=ForthcomingArticles}.
-\item Maitra, Anwoy, \emph{On the continuous extension of Kobayashi isometries}, Proc.
+Patil: COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS, to appear in \emph{Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry}.
+\item Gadadhar Misra: Professor, \emph{Adv. Math.} {\bf 351} (2019), 1105 - 1138, \url{https://www.sciencedirect.com/science/article/abs/pii/S0001870819302609}.
+\item Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}, DOI 10.2422/2036-2145.201906\_007, \url{http://annaliscienze.sns.it/index.php?page=ForthcomingArticles}.
+\item Maitra, Anwoy: On the continuous extension of Kobayashi isometries, \emph{Proc.
 Amer.
 Math.
-Soc.
-{\bf 148} (2020), 3437--3451, \url{https://www.ams.org/journals/proc/2020-148-08/S0002-9939-2020-15038-1/}.
+Soc.} {\bf 148} (2020), 3437--3451, \url{https://www.ams.org/journals/proc/2020-148-08/S0002-9939-2020-15038-1/}.
 \item Vishnu Priya, N.
@@
 and  Rangarajan, G.
-and Lakshmanan, M, \emph{On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation}, Physics Letters A {\bf 383} (2019), 15-26.
+and Lakshmanan, M: On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation, \emph{Physics Letters A} {\bf 383} (2019), 15-26.
 \item Kashyap, G.
@@
 and Ravindranath, V.
-and Ambika, G, \emph{Synapse loss and progress of Alzheimer’s disease - A network model}, Scientific Reports {\bf 9} (2019), 6555.
+and Ambika, G: Synapse loss and progress of Alzheimer’s disease - A network model, \emph{Scientific Reports} {\bf 9} (2019), 6555.
 \item Vishnu Priya, N.
 and Senthilvelan, M.
-and Rangarajan, G., \emph{On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation}, Chaos {\bf 29} (2019), 123135.
-\item Sarkar, Amar Deep and Verma, Kaushal, \emph{A submultiplicative property of the Carath\'{e}odory metric on planar domains}, Proc.
+and Rangarajan, G.: On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, \emph{Chaos} {\bf 29} (2019), 123135.
+\item Sarkar, Amar Deep and Verma, Kaushal: A submultiplicative property of the Carath\'{e}odory metric on planar domains, \emph{Proc.
 Indian Acad.
@@
 (Math.
-Sci.) {\bf } (), , \url{https://www.ias.ac.in/article/fulltext/pmsc/130/0035}.
-\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor, \emph{Higher Chern Classes in Iwasawa Theory}, American Journal of Mathematics {\bf 142} (2020), 627-682, \url{https://muse.jhu.edu/issue/42062}.
+Sci.)} {\bf } (), \url{https://www.ias.ac.in/article/fulltext/pmsc/130/0035}.
+\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor: Higher Chern Classes in Iwasawa Theory, \emph{American Journal of Mathematics} {\bf 142} (2020), 627-682, \url{https://muse.jhu.edu/issue/42062}.
 \item Basu, R.
@@
 and Hegde, M.
-and Krishnapur, M., \emph{Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation}, to appear in Israel Journal of Mathematics.
+and Krishnapur, M.: Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation, to appear in \emph{Israel Journal of Mathematics}.
 \item M.
@@
 Ghosh and S.
-Pradhan, \emph{Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant}, to appear in ESIAM: Control, Optimization and Calculus of Variations , DOI Doi:10.105/cocv/2020029.
+Pradhan: Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant, to appear in \emph{ESIAM: Control, Optimization and Calculus of Variations}, DOI Doi:10.105/cocv/2020029.
 \item M.
@@
 Pal and S.
-Pradhan, \emph{Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications}, to appear in Stochastic Analysis and Applications, DOI Doi: 10.1080/07362994.2020.1796707.
+Pradhan: Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications, to appear in \emph{Stochastic Analysis and Applications}, DOI Doi: 10.1080/07362994.2020.1796707.
 \item Iyer, S.
 K.
-and Yogeshwaran, D., \emph{Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes}, Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques {\bf 56} (2020), 1869-1897, \url{https://doi.org/10.1214/19-AIHP1020}.
-\item Datta, Basudeb and Gupta, Subhojoy, \emph{Semi-regular tilings of the hyperbolic plane}, to appear in Discrete and Computational Geometry, DOI https://doi.org/10.1007/s00454-019-00156-0.
+and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897, \url{https://doi.org/10.1214/19-AIHP1020}.
+\item Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane, to appear in \emph{Discrete and Computational Geometry}, DOI https://doi.org/10.1007/s00454-019-00156-0.
 \item Thirupathi Gudi, Ramesh Ch.
-Sau, \emph{Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem}, to appear in ESAIM: Control, Optim.
+Sau: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim.
 Calc.
-Var, DOI doi: 10.1051/cocv/2019068..
-\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh, \emph{On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel},  Studia Math.
-{\bf 255} (2020), 83–107., DOI 10.4064/sm190505-8-10.
-\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada, \emph{Toeplitz operators on the symmetrized bidisc}, International Mathematics Research Notices (IMRN) {\bf } (), , DOI 10.1093/imrn/rnz333.
-\item Pingali, Vamsi Pritham and Varolin, Dror, \emph{Nonuniformly flat affine algebraic hypersurfaces}, to appear in Nagoya Mathematical Journal, DOI https://doi.org/10.1017/nmj.2019.2, \url{https://www.cambridge.org/core/journals/nagoya-mathematical-journal/article/nonuniformly-flat-affine-algebraic-hypersurfaces/3704C1133CB22A05D7FB13765156FC4E}.
-\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham , \emph{Gravitating vortices and the Einstein–Bogomol’nyi equations}, to appear in Mathematische Annalen, DOI https://doi.org/10.1007/s00208-020-01964-z, \url{https://link.springer.com/content/pdf/10.1007/s00208-020-01964-z.pdf}.
-\item Datar, Ved and Jacob,Adam and Zhang, Yuguang, \emph{Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces}, to appear in Journal of differential geometry, \url{https://arxiv.org/pdf/1809.08583.pdf}.
-\item Datar, Ved and Pingali, Vamsi Pritham, \emph{On coupled constant scalar curvature Kaehler metrics}, to appear in Journal of symplectic geometry, \url{https://arxiv.org/pdf/1901.10454v2.pdf}.
+Var}, DOI doi: 10.1051/cocv/2019068..
+\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107., DOI 10.4064/sm190505-8-10.
+\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} {\bf } (), DOI 10.1093/imrn/rnz333.
+\item Pingali, Vamsi Pritham and Varolin, Dror: Nonuniformly flat affine algebraic hypersurfaces, to appear in \emph{Nagoya Mathematical Journal}, DOI https://doi.org/10.1017/nmj.2019.2, \url{https://www.cambridge.org/core/journals/nagoya-mathematical-journal/article/nonuniformly-flat-affine-algebraic-hypersurfaces/3704C1133CB22A05D7FB13765156FC4E}.
+\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein–Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}, DOI https://doi.org/10.1007/s00208-020-01964-z, \url{https://link.springer.com/content/pdf/10.1007/s00208-020-01964-z.pdf}.
+\item Datar, Ved and Jacob,Adam and Zhang, Yuguang: Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces, to appear in \emph{Journal of differential geometry}, \url{https://arxiv.org/pdf/1809.08583.pdf}.
+\item Datar, Ved and Pingali, Vamsi Pritham: On coupled constant scalar curvature Kaehler metrics, to appear in \emph{Journal of symplectic geometry}, \url{https://arxiv.org/pdf/1901.10454v2.pdf}.
 \item Pradhan, P.
-and Sahu, B., \emph{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, Discrete Mathematics {\bf 343} (2020), , DOI 10.1016/j.disc.2020.112044, \url{https://doi.org/10.1016/j.disc.2020.112044}.
-\item Arun Maiti, \emph{Quasi-vertex-transitive maps on the plane}, Discrete Mathematics {\bf 343} (2020), 111911-111917, \url{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}.
-\item Datt, Gopal and Kumar, Sanjay, \emph{A criterion for quasinormality in $\mathbb{C}^n$},  Proc.
+and Sahu, B.: A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd, \emph{Discrete Mathematics} {\bf 343} (2020), DOI 10.1016/j.disc.2020.112044, \url{https://doi.org/10.1016/j.disc.2020.112044}.
+\item Arun Maiti: Quasi-vertex-transitive maps on the plane, \emph{Discrete Mathematics} {\bf 343} (2020), 111911-111917, \url{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}.
+\item Datt, Gopal and Kumar, Sanjay: A criterion for quasinormality in $\mathbb{C}^n$, \emph{Proc.
 Indian Acad.
@@
 Math.
-Sci.
-{\bf 129} (2019), Paper No.
+Sci.} {\bf 129} (2019), Paper No.
 11, 13 pp., DOI https://doi.org/10.1007/s12044-018-0449-5     (This article was published before the review period i.e., April 1, 2019, BUT this is not yet included on the page  https://siddhartha-gadgil.github.io/DeptWeb/pubs.html), \url{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}.
-\item Hatui, Sumana, \emph{Schur multipliers of special p-groups of rank 2}, Journal of Group Theory {\bf 23} (2020), 85-95, DOI https://doi.org/10.1515/jgth-2019-0045, \url{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}.
-\item Choudhury, Projesh Nath and Tsatsomeros Michael J., \emph{Algorithmic Detection and Construction of N-matrices}, Linear Algebra and Its Applications {\bf 602} (2020), 46-56, DOI 10.1016/j.laa.2020.04.028, \url{https://doi.org/10.1016/j.laa.2020.04.028}.
-\item Choudhury, Projesh Nath and Sivakumar, K.C., \emph{Matrices with Positive Semidefinite Real Part}, to appear in Linear and Multilinear Algebra, DOI 10.1080/03081087.2019.1602588, \url{https://doi.org/10.1080/03081087.2019.1602588}.
-\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala , \emph{On Baker's explicit abc-conjecture},  Publ. Math. Debrecen {\bf 94} (2019), 435–453.
+\item Hatui, Sumana: Schur multipliers of special p-groups of rank 2, \emph{Journal of Group Theory} {\bf 23} (2020), 85-95, DOI https://doi.org/10.1515/jgth-2019-0045, \url{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}.
+\item Choudhury, Projesh Nath and Tsatsomeros Michael J.: Algorithmic Detection and Construction of N-matrices, \emph{Linear Algebra and Its Applications} {\bf 602} (2020), 46-56, DOI 10.1016/j.laa.2020.04.028, \url{https://doi.org/10.1016/j.laa.2020.04.028}.
+\item Choudhury, Projesh Nath and Sivakumar, K.C.: Matrices with Positive Semidefinite Real Part, to appear in \emph{Linear and Multilinear Algebra}, DOI 10.1080/03081087.2019.1602588, \url{https://doi.org/10.1080/03081087.2019.1602588}.
+\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala: On Baker's explicit abc-conjecture, \emph{Publ. Math. Debrecen} {\bf 94} (2019), 435–453.
 \item Carstensen, C.
 and Mallik, G.
-and Nataraj, N., \emph{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, IMA Journal of Numerical Analysis {\bf } (2020), , DOI https://doi.org/10.1093/imanum/drz071, \url{https://doi.org/10.1093/imanum/drz071}.
-\item Mal, Arpita and Sain, Debmalya and Paul, Kallol, \emph{On some geometric properties of operator spaces}, Banach J.
+and Nataraj, N.: Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity, \emph{IMA Journal of Numerical Analysis} {\bf } (2020), DOI https://doi.org/10.1093/imanum/drz071, \url{https://doi.org/10.1093/imanum/drz071}.
+\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: On some geometric properties of operator spaces, \emph{Banach J.
 Math.
-Anal.
-{\bf 13} (2019), 174-191, \url{https://projecteuclid.org/euclid.bjma/1543914019}.
+Anal.} {\bf 13} (2019), 174-191, \url{https://projecteuclid.org/euclid.bjma/1543914019}.
+\item Roth, Julien and Upadhyay, Abhitosh: On almost stable CMC hypersurfaces in manifolds of bounded sectional curvature, \emph{Bulletin of the Australian Mathematical Society} {\bf 101} (2020), 333-338, DOI https://doi.org/10.1017/S0004972719000935, \url{https://www.cambridge.org/core/journals/bulletin-of-the-australian-mathematical-society/article/on-almost-stable-cmc-hypersurfaces-in-manifolds-of-bounded-sectional-curvature/E0BF84D4D46C82F6D75CDCEAAF5DEE94}.
+\item Roth, Julien and Upadhyay, Abhitosh: f-Biharmonic Submanifolds of Generalized Space Forms, \emph{Results in Mathematics} {\bf 75} (2020), DOI https://doi.org/10.1007/s00025-019-1142-4, \url{https://link.springer.com/article/10.1007/s00025-019-1142-4?shared-article-renderer#citeas}.
+\item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable CMC free-boundary surfaces in a strictly convex domain of a bi-invariant Lie group, to appear in \emph{International Journal of Mathematics}, DOI https://doi.org/10.1142/S0129167X2050086X.
 \end{enumerate}
@@
 \begin{enumerate}
-
+\item A.
+Banerjee: Spectra as universal objects in categories of supports in {\em Banach Center Publications(Quantum Dynamics Proceedings)} Ludwik Dabrowski, Ryszard Nest, Adam Skalski (ed.) , Banach Center Publications , IMPAN, Warsaw, Poland (2020), (accepted).
+\item IMPAN, Warsaw, Poland: 2020 in {\em (accepted)} No (ed.)   ().
+\item S.
+Ghara and G.
+Misra: Decomposition of the tensor product of two Hilbert modules in {\em Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G.
+Douglas Memorial Volume} Curto, R.E., Helton, W., Lin, H., Tang, X., Yang, R., Yu, G.
+(ed.) , Operator Theory: Advances and Applications , Birkhauser (2020).
+\item Birkhauser: 2020 in {\em } Yes (ed.) , Gadadhar Misra , Decomposition of the tensor product of two Hilbert modules (Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G.
+Douglas Memorial Volume), R.
+Curto, W.
+Helton, H.
+Lin, X.
+Tang, R.
+Yang, G.
+Yu.
+\item Decomposition of the tensor product of two Hilbert modules: Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G.
+Douglas Memorial Volume in {\em R.
+Curto, W.
+Helton, H.
+Lin, X.
+Tang, R.
+Yang, G.
+Yu} Operator Theory: Advances and Applications (ed.) , Birkhauser , 2020 (), No.
+\item 2020:  in {\em No}  (ed.)   ().
 \end{enumerate}
 
-\subsection{Books and book chapters}
+\subsection{Books}
+
+\subsection{Book Chapters}
 
 \begin{enumerate}
-
+\item Gupta, Subhojoy and Seshadri, Harish: Complex geometry of Teichmüller domains in {\em Handbook of Teichmüller theory} Papadopoulos, Athanase (ed.), IRMA Lect.
+Math.
+Theor.
+Phys, Eur.
+Math.
+Soc., Zürich (2020), 26.
+\item Gupta, Subhojoy: Holomorphic quadratic differentials in Teichmüller theory in {\em Handbook of Teichmüller theory} Papadopoulos, Athanase (ed.), IRMA Lect.
+Math.
+Theor.
+Phys., Eur.
+Math.
+Soc., Zürich (2020), 36.
 \end{enumerate}
@@
 \begin{enumerate}
-\item Khare, Apoorva, \emph{Sharp nonzero lower bounds for the Schur product theorem}, submitted for publication, \url{https://arxiv.org/abs/1910.03537}.
-\item Lübeck, Frank and Prasad, Dipendra and Ayyer, Arvind, \emph{A character relationship between symmetric group and hyperoctahedral group }, preprint, \url{https://arxiv.org/abs/1912.08576}.
-\item Ayyer, Arvind and Sinha, Shubham , \emph{The size of t-cores and hook lengths of random cells in random partitions }, preprint, \url{https://arxiv.org/abs/1911.03135}.
-\item Ayyer, Arvind, \emph{ A simple symmetric exclusion process driven by an asymmetric tracer particle }, preprint, \url{https://arxiv.org/abs/2001.02425}.
-\item David Burns, Mahesh Kakde, \emph{On Weil-Etale Cohomology and Artin L-series}, preprint, \url{https://nms.kcl.ac.uk/david.burns/web_page/bk.pdf}.
-\item Gupta, Purvi and Wawrzyniak, Chloe Urbanski, \emph{STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$}, submitted for publication, \url{https://arxiv.org/pdf/2002.08699.pdf}.
-\item Radhika Ganapathy, \emph{A Hecke algebra isomorphism over close local fields}, preprint.
-\item Miermont, Grégory and Sen, Sanchayan , \emph{On breadth-first constructions of scaling limits of random graphs and random unicellular maps}, submitted for publication, \url{https://arxiv.org/abs/1908.04403}.
-\item Gupta, Subhojoy and Mj, Mahan, \emph{Meromorphic projective structures, grafting and the monodromy map}, preprint, \url{http://arxiv.org/abs/1904.03804}.
-\item Gupta, Subhojoy, \emph{Monodromy groups of CP^1-structures on punctured surfaces}, preprint, \url{https://arxiv.org/abs/1909.10771}.
-\item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter, \emph{Surface group representations in SL(2,C) with finite mapping class orbits}, preprint, \url{https://arxiv.org/abs/1707.00071}.
-\item Ganguly, Pritam and Thangavelu,Sundaram, \emph{On lacunary spherical maximal function on Heisenberg groups}, preprint.
-\item Bhattacharyya, Tirthankar and Kumar, Poornendu and Sau, Haripada, \emph{Distinguished Varieties Through the Berger--Coburn--Lebow Theorem}, submitted for publication, \url{https://arxiv.org/pdf/2001.01410.pdf}.
-\item Bhattacharyya, T. and  Biswas, A. and Maitra, A., \emph{An unbounded realization of the symmetrized bidisc}, submitted for publication, \url{https://arxiv.org/pdf/2005.00289.pdf }.
-\item Pingali, Vamsi Pritham, \emph{The deformed Hermitian Yang-Mills equation on three-folds}, preprint, \url{https://arxiv.org/abs/1910.01870}.
-\item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian , \emph{Gravitating vortices with positive curvature}, preprint, \url{https://arxiv.org/abs/1911.09616}.
-\item Quddus, Safdar, \emph{Equivariant Cartan Homotopy Formula for $DG$-algebra.}, preprint, \url{https://arxiv.org/abs/2002.02192}.
-\item Arun Maiti, \emph{OPTIMAL INDEX GROWTH OF CLOSED GEODESICS}, submitted for publication.
-\item  Poria, Anirudha, \emph{Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms}, submitted for publication, \url{https://arxiv.org/abs/2004.04184}.
-\item Poria, Anirudha, \emph{Uncertainty principles for the Opdam-Cherednik transform on modulation spaces}, submitted for publication, \url{https://arxiv.org/abs/2005.14274}.
-\item Bera, Sudip, \emph{ENUMERATION OF WEIGHTED PATHS ON A DIGRAPH AND BLOCK HOOK DETERMINANT}, submitted for publication.
-\item Behera, Kiran Kumar, \emph{Self-inversive polynomials from rational transformation of linear functionals}, submitted for publication, \url{https://arxiv.org/abs/1909.12548}.
-\item Hatui, Sumana and Singla Pooja, \emph{On Schur multiplier and Projective representations of Heisenberg groups}, submitted for publication, \url{https://arxiv.org/abs/1909.06589}.
-\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan, \emph{Multiplicities, invariant subspaces and an additive formula.}, preprint, \url{https://arxiv.org/abs/1812.05435}.
-\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita, \emph{$K$-homogeneous tuple of operators on bounded symmetric domains}, preprint.
+\item Khare, Apoorva: Sharp nonzero lower bounds for the Schur product theorem, submitted for publication, \url{https://arxiv.org/abs/1910.03537}.
+\item Lübeck, Frank and Prasad, Dipendra and Ayyer, Arvind: A character relationship between symmetric group and hyperoctahedral group, preprint, \url{https://arxiv.org/abs/1912.08576}.
+\item Ayyer, Arvind and Sinha, Shubham: The size of t-cores and hook lengths of random cells in random partitions, preprint, \url{https://arxiv.org/abs/1911.03135}.
+\item Ayyer, Arvind: A simple symmetric exclusion process driven by an asymmetric tracer particle, preprint, \url{https://arxiv.org/abs/2001.02425}.
+\item David Burns, Mahesh Kakde: On Weil-Etale Cohomology and Artin L-series, preprint, \url{https://nms.kcl.ac.uk/david.burns/web_page/bk.pdf}.
+\item Gupta, Purvi and Wawrzyniak, Chloe Urbanski: STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$, submitted for publication, \url{https://arxiv.org/pdf/2002.08699.pdf}.
+\item Radhika Ganapathy: A Hecke algebra isomorphism over close local fields, preprint.
+\item Miermont, Grégory and Sen, Sanchayan: On breadth-first constructions of scaling limits of random graphs and random unicellular maps, submitted for publication, \url{https://arxiv.org/abs/1908.04403}.
+\item Gupta, Subhojoy and Mj, Mahan: Meromorphic projective structures, grafting and the monodromy map, preprint, \url{http://arxiv.org/abs/1904.03804}.
+\item Gupta, Subhojoy: Monodromy groups of $CP^1$-structures on punctured surfaces, preprint, \url{https://arxiv.org/abs/1909.10771}.
+\item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter: Surface group representations in SL(2,C) with finite mapping class orbits, preprint, \url{https://arxiv.org/abs/1707.00071}.
+\item Ganguly, Pritam and Thangavelu,Sundaram: On lacunary spherical maximal function on Heisenberg groups, preprint.
+\item Bhattacharyya, Tirthankar and Kumar, Poornendu and Sau, Haripada: Distinguished Varieties Through the Berger--Coburn--Lebow Theorem, submitted for publication, \url{https://arxiv.org/pdf/2001.01410.pdf}.
+\item Bhattacharyya, T. and  Biswas, A. and Maitra, A.: An unbounded realization of the symmetrized bidisc, submitted for publication, \url{https://arxiv.org/pdf/2005.00289.pdf}.
+\item Pingali, Vamsi Pritham: The deformed Hermitian Yang-Mills equation on three-folds, preprint, \url{https://arxiv.org/abs/1910.01870}.
+\item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian: Gravitating vortices with positive curvature, preprint, \url{https://arxiv.org/abs/1911.09616}.
+\item Quddus, Safdar: Equivariant Cartan Homotopy Formula for $DG$-algebra., preprint, \url{https://arxiv.org/abs/2002.02192}.
+\item Arun Maiti: OPTIMAL INDEX GROWTH OF CLOSED GEODESICS, submitted for publication.
+\item Poria, Anirudha: Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms, submitted for publication, \url{https://arxiv.org/abs/2004.04184}.
+\item Poria, Anirudha: Uncertainty principles for the Opdam-Cherednik transform on modulation spaces, submitted for publication, \url{https://arxiv.org/abs/2005.14274}.
+\item Bera, Sudip: ENUMERATION OF WEIGHTED PATHS ON A DIGRAPH AND BLOCK HOOK DETERMINANT, submitted for publication.
+\item Behera, Kiran Kumar: Self-inversive polynomials from rational transformation of linear functionals, submitted for publication, \url{https://arxiv.org/abs/1909.12548}.
+\item Hatui, Sumana and Singla Pooja: On Schur multiplier and Projective representations of Heisenberg groups, submitted for publication, \url{https://arxiv.org/abs/1909.06589}.
+\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: Multiplicities, invariant subspaces and an additive formula., preprint, \url{https://arxiv.org/abs/1812.05435}.
+\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita: $K$-homogeneous tuple of operators on bounded symmetric domains, preprint.
+\item Toft, J. and Gumber, A. and Manna, R. and Ratnakumar, P. K.: Translation and modulation invariant Hilbert spaces, submitted for publication, \url{https://arxiv.org/abs/2004.02430v1}.
 \end{enumerate}
@@
 \item Aas, Erik and Ayyer, Arvind and Linusson, Svante and Potka,
-Samu, {\em The exact phase diagram for a semipermeable {TASEP} with
-nonlocal boundary jumps}, J. Phys. A} {\bf 52} (2019), 355001, 19, DOI 10.1088/1751-8121/ab2e96, \url{https://doi.org/10.1088/1751-8121/ab2e96}.
+Samu: The exact phase diagram for a semipermeable {TASEP} with
+nonlocal boundary jumps, \emph{J. Phys. A} {\bf 52} (2019), 355001, 19, DOI 10.1088/1751-8121/ab2e96, \url{https://doi.org/10.1088/1751-8121/ab2e96}.
 \item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
-Nandakumaran, A. K., {\em Control problem on a rough circular domain and homogenization}, Asymptot. Anal.} {\bf 115} (2019), 19--46, DOI 10.3233/asy-191526, \url{https://doi.org/10.3233/asy-191526}.
-\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Locally periodic unfolding operator for highly oscillating
-rough domains}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954, DOI 10.1007/s10231-019-00848-7, \url{https://doi.org/10.1007/s10231-019-00848-7}.
-\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Generalization of unfolding operator for highly oscillating
-smooth boundary domains and homogenization}, Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30, DOI 10.1007/s00526-018-1354-6, \url{https://doi.org/10.1007/s00526-018-1354-6}.
-\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu, {\em Asymptotic analysis of a boundary optimal control problem on a
-general branched structure}, Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434, DOI 10.1002/mma.5748, \url{https://doi.org/10.1002/mma.5748}.
-\item Aiyappan, S. and Sardar, Bidhan Chandra, {\em Biharmonic equation in a highly oscillating domain and
-homogenization of an associated control problem}, Appl. Anal.} {\bf 98} (2019), 2783--2801, DOI 10.1080/00036811.2018.1471207, \url{https://doi.org/10.1080/00036811.2018.1471207}.
-\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish, {\em A gap theorem for positive {E}instein metrics on the
-four-sphere}, Math. Ann.} {\bf 373} (2019), 1329--1339, DOI 10.1007/s00208-018-1749-x, \url{https://doi.org/10.1007/s00208-018-1749-x}.
-\item Anamby, Pramath and Das, Soumya, {\em Distinguishing {H}ermitian cusp forms of degree 2 by a certain
-subset of all {F}ourier coefficients}, Publ. Mat.} {\bf 63} (2019), 307--341, DOI 10.5565/PUBLMAT6311911, \url{https://doi.org/10.5565/PUBLMAT6311911}.
-\item Anamby, Pramath and Das, Soumya, {\em Bounds for the {P}etersson norms of the pullbacks of
-{S}aito-{K}urokawa lifts}, J. Number Theory} {\bf 191} (2018), 289--304, DOI 10.1016/j.jnt.2018.03.011, \url{https://doi.org/10.1016/j.jnt.2018.03.011}.
-\item Arunkumar, G. and Kus, Deniz and Venkatesh, R., {\em Root multiplicities for {B}orcherds algebras and graph
-coloring}, J. Algebra} {\bf 499} (2018), 538--569, DOI 10.1016/j.jalgebra.2017.11.050, \url{https://doi.org/10.1016/j.jalgebra.2017.11.050}.
-\item Ayyer, Arvind and Behrend, Roger E., {\em Factorization theorems for classical group characters, with
+Nandakumaran, A. K.: Control problem on a rough circular domain and homogenization, \emph{Asymptot. Anal.} {\bf 115} (2019), 19--46, DOI 10.3233/asy-191526, \url{https://doi.org/10.3233/asy-191526}.
+\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: Locally periodic unfolding operator for highly oscillating
+rough domains, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954, DOI 10.1007/s10231-019-00848-7, \url{https://doi.org/10.1007/s10231-019-00848-7}.
+\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: Generalization of unfolding operator for highly oscillating
+smooth boundary domains and homogenization, \emph{Calc.
+Var.
+Partial Differential Equations} {\bf 57} (2018), Art.
+86, 30, DOI 10.1007/s00526-018-1354-6, \url{https://doi.org/10.1007/s00526-018-1354-6}.
+\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu: Asymptotic analysis of a boundary optimal control problem on a
+general branched structure, \emph{Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434, DOI 10.1002/mma.5748, \url{https://doi.org/10.1002/mma.5748}.
+\item Aiyappan, S. and Sardar, Bidhan Chandra: Biharmonic equation in a highly oscillating domain and
+homogenization of an associated control problem, \emph{Appl. Anal.} {\bf 98} (2019), 2783--2801, DOI 10.1080/00036811.2018.1471207, \url{https://doi.org/10.1080/00036811.2018.1471207}.
+\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish: A gap theorem for positive {E}instein metrics on the
+four-sphere, \emph{Math. Ann.} {\bf 373} (2019), 1329--1339, DOI 10.1007/s00208-018-1749-x, \url{https://doi.org/10.1007/s00208-018-1749-x}.
+\item Anamby, Pramath and Das, Soumya: Distinguishing {H}ermitian cusp forms of degree 2 by a certain
+subset of all {F}ourier coefficients, \emph{Publ. Mat.} {\bf 63} (2019), 307--341, DOI 10.5565/PUBLMAT6311911, \url{https://doi.org/10.5565/PUBLMAT6311911}.
+\item Anamby, Pramath and Das, Soumya: Bounds for the {P}etersson norms of the pullbacks of
+{S}aito-{K}urokawa lifts, \emph{J. Number Theory} {\bf 191} (2018), 289--304, DOI 10.1016/j.jnt.2018.03.011, \url{https://doi.org/10.1016/j.jnt.2018.03.011}.
+\item Arunkumar, G. and Kus, Deniz and Venkatesh, R.: Root multiplicities for {B}orcherds algebras and graph
+coloring, \emph{J. Algebra} {\bf 499} (2018), 538--569, DOI 10.1016/j.jalgebra.2017.11.050, \url{https://doi.org/10.1016/j.jalgebra.2017.11.050}.
+\item Ayyer, Arvind and Behrend, Roger E.: Factorization theorems for classical group characters, with
 applications to alternating sign matrices and plane
-partitions}, J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105, DOI 10.1016/j.jcta.2019.01.001, \url{https://doi.org/10.1016/j.jcta.2019.01.001}.
+partitions, \emph{J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105, DOI 10.1016/j.jcta.2019.01.001, \url{https://doi.org/10.1016/j.jcta.2019.01.001}.
 \item Ayyer, Arvind and Bouttier, J\'{e}r\'{e}mie and Corteel, Sylvie and
-Linusson, Svante and Nunzi, Fran\c{c}ois, {\em Bumping sequences and multispecies juggling}, Adv.
+Linusson, Svante and Nunzi, Fran\c{c}ois: Bumping sequences and multispecies juggling, \emph{Adv.
 in Appl.
 Math.} {\bf 98} (2018), 100--126, DOI 10.1016/j.aam.2018.03.001, \url{https://doi.org/10.1016/j.aam.2018.03.001}.
-\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, {\em Matrix product solution of a left-permeable two-species
-asymmetric exclusion process}, Phys. Rev. E} {\bf 97} (2018), 012151, 10, DOI 10.1103/physreve.97.012151, \url{https://doi.org/10.1103/physreve.97.012151}.
-\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, {\em The phase diagram for a multispecies left-permeable asymmetric
-exclusion process}, J. Stat. Phys.} {\bf 174} (2019), 605--621, DOI 10.1007/s10955-018-2183-x, \url{https://doi.org/10.1007/s10955-018-2183-x}.
-\item Ayyer, Arvind and Linusson, Svante, {\em Reverse juggling processes}, Random Structures Algorithms} {\bf 55} (2019), 56--72, DOI 10.1002/rsa.20825, \url{https://doi.org/10.1002/rsa.20825}.
-\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, {\em Odd partitions in {Y}oung's lattice}, S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
-\item Ayyer, Arvind and Ramassamy, Sanjay, {\em The {H}ilbert-{G}alton board}, ALEA Lat.
+\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar: Matrix product solution of a left-permeable two-species
+asymmetric exclusion process, \emph{Phys. Rev. E} {\bf 97} (2018), 012151, 10, DOI 10.1103/physreve.97.012151, \url{https://doi.org/10.1103/physreve.97.012151}.
+\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar: The phase diagram for a multispecies left-permeable asymmetric
+exclusion process, \emph{J. Stat. Phys.} {\bf 174} (2019), 605--621, DOI 10.1007/s10955-018-2183-x, \url{https://doi.org/10.1007/s10955-018-2183-x}.
+\item Ayyer, Arvind and Linusson, Svante: Reverse juggling processes, \emph{Random Structures Algorithms} {\bf 55} (2019), 56--72, DOI 10.1002/rsa.20825, \url{https://doi.org/10.1002/rsa.20825}.
+\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven: Odd partitions in {Y}oung's lattice, \emph{S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
+\item Ayyer, Arvind and Ramassamy, Sanjay: The {H}ilbert-{G}alton board, \emph{ALEA Lat.
 Am.
@@
 Stat.} {\bf 15} (2018), 755--774, DOI 10.30757/alea.v15-28, \url{https://doi.org/10.30757/alea.v15-28}.
-\item B\"{o}cherer, Siegfried and Das, Soumya, {\em Cuspidality and the growth of {F}ourier coefficients of
-modular forms}, J. Reine Angew. Math.} {\bf 741} (2018), 161--178, DOI 10.1515/crelle-2015-0075, \url{https://doi.org/10.1515/crelle-2015-0075}.
-\item B\"{o}cherer, Siegfried and Das, Soumya, {\em Petersson norms of not necessarily cuspidal {J}acobi modular
-forms and applications}, Adv. Math.} {\bf 336} (2018), 335--376, DOI 10.1016/j.aim.2018.07.033, \url{https://doi.org/10.1016/j.aim.2018.07.033}.
-\item Bagchi, Sayan and Thangavelu, Sundaram, {\em Weighted norm inequalities for {W}eyl multipliers and fourier
-multipliers on the {H}eisenberg group}, J. Anal. Math.} {\bf 136} (2018), 1--29, DOI 10.1007/s11854-018-0053-8, \url{https://doi.org/10.1007/s11854-018-0053-8}.
-\item Baklouti, Ali and Thangavelu, Sundaram, {\em Hardy and {M}iyachi theorems for {H}eisenberg motion groups}, Nagoya Math.
+\item B\"{o}cherer, Siegfried and Das, Soumya: Cuspidality and the growth of {F}ourier coefficients of
+modular forms, \emph{J. Reine Angew. Math.} {\bf 741} (2018), 161--178, DOI 10.1515/crelle-2015-0075, \url{https://doi.org/10.1515/crelle-2015-0075}.
+\item B\"{o}cherer, Siegfried and Das, Soumya: Petersson norms of not necessarily cuspidal {J}acobi modular
+forms and applications, \emph{Adv. Math.} {\bf 336} (2018), 335--376, DOI 10.1016/j.aim.2018.07.033, \url{https://doi.org/10.1016/j.aim.2018.07.033}.
+\item Bagchi, Sayan and Thangavelu, Sundaram: Weighted norm inequalities for {W}eyl multipliers and fourier
+multipliers on the {H}eisenberg group, \emph{J. Anal. Math.} {\bf 136} (2018), 1--29, DOI 10.1007/s11854-018-0053-8, \url{https://doi.org/10.1007/s11854-018-0053-8}.
+\item Baklouti, Ali and Thangavelu, Sundaram: Hardy and {M}iyachi theorems for {H}eisenberg motion groups, \emph{Nagoya Math.
 J.} {\bf 229} (2018), 1--20, DOI 10.1017/nmj.2016.58, \url{https://doi.org/10.1017/nmj.2016.58}.
 \item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
-Verma, Kaushal, {\em Remarks on the higher dimensional {S}uita conjecture}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411, DOI 10.1090/proc/14421, \url{https://doi.org/10.1090/proc/14421}.
-\item Balhara, Rakesh, {\em Hardy's inequality for the fractional powers of the {G}rushin
-operator}, Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25, DOI 10.1007/s12044-019-0471-2, \url{https://doi.org/10.1007/s12044-019-0471-2}.
-\item Balodi, Mamta and Palcoux, Sebastien, {\em On {B}oolean intervals of finite groups}, J.
+Verma, Kaushal: Remarks on the higher dimensional {S}uita conjecture, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411, DOI 10.1090/proc/14421, \url{https://doi.org/10.1090/proc/14421}.
+\item Balhara, Rakesh: Hardy's inequality for the fractional powers of the {G}rushin
+operator, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25, DOI 10.1007/s12044-019-0471-2, \url{https://doi.org/10.1007/s12044-019-0471-2}.
+\item Balodi, Mamta and Palcoux, Sebastien: On {B}oolean intervals of finite groups, \emph{J.
 Combin.
@@
 A} {\bf 157} (2018), 49--69, DOI 10.1016/j.jcta.2018.02.004, \url{https://doi.org/10.1016/j.jcta.2018.02.004}.
-\item Banerjee, Abhishek, {\em On {A}uslander's formula and cohereditary torsion pairs}, Commun.
+\item Banerjee, Abhishek: On {A}uslander's formula and cohereditary torsion pairs, \emph{Commun.
 Contemp.
 Math.} {\bf 20} (2018), 1750071, 27, DOI 10.1142/S0219199717500717, \url{https://doi.org/10.1142/S0219199717500717}.
-\item Banerjee, Abhishek, {\em Modular {H}ecke algebras over {M}\"{o}bius categories}, J.
+\item Banerjee, Abhishek: Modular {H}ecke algebras over {M}\"{o}bius categories, \emph{J.
 Geom.
 Phys.} {\bf 131} (2018), 23--40, DOI 10.1016/j.geomphys.2018.04.008, \url{https://doi.org/10.1016/j.geomphys.2018.04.008}.
-\item Banerjee, Abhishek, {\em On differential torsion theories and rings with several
-objects}, Canad. Math. Bull.} {\bf 62} (2019), 703--714, DOI 10.4153/s0008439518000656, \url{https://doi.org/10.4153/s0008439518000656}.
-\item Banerjee, Abhishek, {\em A topological {N}ullstellensatz for tensor-triangulated
-categories}, C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375, DOI 10.1016/j.crma.2018.02.012, \url{https://doi.org/10.1016/j.crma.2018.02.012}.
-\item Banerjee, Abhishek, {\em Quasimodular {H}ecke algebras and {H}opf actions}, J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080, DOI 10.4171/JNCG/297, \url{https://doi.org/10.4171/JNCG/297}.
-\item Banerjee, Abhishek, {\em Completions of monoid objects and descent results}, J.
+\item Banerjee, Abhishek: On differential torsion theories and rings with several
+objects, \emph{Canad. Math. Bull.} {\bf 62} (2019), 703--714, DOI 10.4153/s0008439518000656, \url{https://doi.org/10.4153/s0008439518000656}.
+\item Banerjee, Abhishek: A topological {N}ullstellensatz for tensor-triangulated
+categories, \emph{C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375, DOI 10.1016/j.crma.2018.02.012, \url{https://doi.org/10.1016/j.crma.2018.02.012}.
+\item Banerjee, Abhishek: Quasimodular {H}ecke algebras and {H}opf actions, \emph{J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080, DOI 10.4171/JNCG/297, \url{https://doi.org/10.4171/JNCG/297}.
+\item Banerjee, Abhishek: Completions of monoid objects and descent results, \emph{J.
 Algebra} {\bf 507} (2018), 362--399, DOI 10.1016/j.jalgebra.2018.04.022, \url{https://doi.org/10.1016/j.jalgebra.2018.04.022}.
-\item Banerjee, Abhishek and Kour, Surjeet, {\em {$(A,\delta)$}-modules, {H}ochschild homology and higher
-derivations}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802, DOI 10.1007/s10231-019-00844-x, \url{https://doi.org/10.1007/s10231-019-00844-x}.
-\item Basu, Arnab and Ghosh, Mrinal K., {\em Nonzero-sum risk-sensitive stochastic games on a countable
-state space}, Math. Oper. Res.} {\bf 43} (2018), 516--532, DOI 10.1287/moor.2017.0870, \url{https://doi.org/10.1287/moor.2017.0870}.
+\item Banerjee, Abhishek and Kour, Surjeet: {$(A,\delta)$}-modules, {H}ochschild homology and higher
+derivations, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802, DOI 10.1007/s10231-019-00844-x, \url{https://doi.org/10.1007/s10231-019-00844-x}.
+\item Basu, Arnab and Ghosh, Mrinal K.: Nonzero-sum risk-sensitive stochastic games on a countable
+state space, \emph{Math. Oper. Res.} {\bf 43} (2018), 516--532, DOI 10.1287/moor.2017.0870, \url{https://doi.org/10.1287/moor.2017.0870}.
 \item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
-and Putinar, Mihai, {\em Simultaneous kernels of matrix {H}adamard powers}, Linear Algebra Appl.} {\bf 576} (2019), 142--157, DOI 10.1016/j.laa.2018.03.035, \url{https://doi.org/10.1016/j.laa.2018.03.035}.
+and Putinar, Mihai: Simultaneous kernels of matrix {H}adamard powers, \emph{Linear Algebra Appl.} {\bf 576} (2019), 142--157, DOI 10.1016/j.laa.2018.03.035, \url{https://doi.org/10.1016/j.laa.2018.03.035}.
 \item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
 Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
-Morales, Alejandro H. and Yip, Martha, {\em The volume of the caracol polytope}, S\'{e}m. Lothar. Combin.} {\bf 80B} (2018), Art. 87, 12.
+Morales, Alejandro H. and Yip, Martha: The volume of the caracol polytope, \emph{S\'{e}m. Lothar. Combin.} {\bf 80B} (2018), Art. 87, 12.
 \item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
@@
 Morales, Alejandro H.
-and Yip, Martha, {\em A combinatorial model for computing volumes of flow polytopes}, Trans.
+and Yip, Martha: A combinatorial model for computing volumes of flow polytopes, \emph{Trans.
 Amer.
@@
 Soc.} {\bf 372} (2019), 3369--3404, DOI 10.1090/tran/7743, \url{https://doi.org/10.1090/tran/7743}.
-\item Bera, Sayani and Verma, Kaushal, {\em Some aspects of shift-like automorphisms of {$\Bbb C^k$}}, Proc.
+\item Bera, Sayani and Verma, Kaushal: Some aspects of shift-like automorphisms of {$\Bbb C^k$}, \emph{Proc.
 Indian Acad.
@@
 \item Bharali, Gautam and Biswas, Indranil and Divakaran, Divakaran
-and Janardhanan, Jaikrishnan, {\em Proper holomorphic mappings onto symmetric products of a
-{R}iemann surface}, Doc. Math.} {\bf 23} (2018), 1291--1311.
-\item Bharali, Gautam and Chandel, Vikramjeet Singh, {\em Pick interpolation on the polydisc: small families of
-sufficient kernels}, Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093, DOI 10.1007/s11785-017-0701-5, \url{https://doi.org/10.1007/s11785-017-0701-5}.
-\item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K., {\em Survey of last ten years of work done in {I}ndia in some
-selected areas of functional analysis and operator theory}, Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617, DOI 10.1007/s13226-019-0345-4, \url{https://doi.org/10.1007/s13226-019-0345-4}.
-\item Bhattacharyya, Tirthankar and Sau, Haripada, {\em Holomorphic functions on the symmetrized bidisk---realization,
-interpolation and extension}, J. Funct. Anal.} {\bf 274} (2018), 504--524, DOI 10.1016/j.jfa.2017.09.013, \url{https://doi.org/10.1016/j.jfa.2017.09.013}.
+and Janardhanan, Jaikrishnan: Proper holomorphic mappings onto symmetric products of a
+{R}iemann surface, \emph{Doc. Math.} {\bf 23} (2018), 1291--1311.
+\item Bharali, Gautam and Chandel, Vikramjeet Singh: Pick interpolation on the polydisc: small families of
+sufficient kernels, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093, DOI 10.1007/s11785-017-0701-5, \url{https://doi.org/10.1007/s11785-017-0701-5}.
+\item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K.: Survey of last ten years of work done in {I}ndia in some
+selected areas of functional analysis and operator theory, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617, DOI 10.1007/s13226-019-0345-4, \url{https://doi.org/10.1007/s13226-019-0345-4}.
+\item Bhattacharyya, Tirthankar and Sau, Haripada: Holomorphic functions on the symmetrized bidisk---realization,
+interpolation and extension, \emph{J. Funct. Anal.} {\bf 274} (2018), 504--524, DOI 10.1016/j.jfa.2017.09.013, \url{https://doi.org/10.1016/j.jfa.2017.09.013}.
 \item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
-Sundaram, {\em Hermite multipliers on modulation spaces}, Analysis and partial differential equations: perspectives from
+Sundaram: Hermite multipliers on modulation spaces, \emph{Analysis and partial differential equations: perspectives from
 developing countries} {\bf 275} (2019), 42--64.
-\item Bhosle, Usha N., {\em Hitchin pairs on reducible curves}, Internat. J. Math.} {\bf 29} (2018), 1850015, 49, DOI 10.1142/S0129167X18500155, \url{https://doi.org/10.1142/S0129167X18500155}.
+\item Bhosle, Usha N.: Hitchin pairs on reducible curves, \emph{Internat. J. Math.} {\bf 29} (2018), 1850015, 49, DOI 10.1142/S0129167X18500155, \url{https://doi.org/10.1142/S0129167X18500155}.
 \item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and
-Pingali, Vamsi P., {\em Rational cuspidal curves on del-{P}ezzo surfaces}, J. Singul.} {\bf 17} (2018), 91--107.
-\item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy, {\em Branched projective structures on a {R}iemann surface and
-logarithmic connections}, Doc. Math.} {\bf 24} (2019), 2299--2337.
-\item Biswas, Indranil and Pingali, Vamsi Pritham, {\em A characterization of finite vector bundles on {G}auduchon
-astheno-{K}\"{a}hler manifolds}, \'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art. 6, 13.
-\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi, {\em Edge patch-wise local projection stabilized nonconforming
-{FEM} for the {O}seen problem}, Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214, DOI 10.1515/cmam-2018-0020, \url{https://doi.org/10.1515/cmam-2018-0020}.
+Pingali, Vamsi P.: Rational cuspidal curves on del-{P}ezzo surfaces, \emph{J. Singul.} {\bf 17} (2018), 91--107.
+\item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy: Branched projective structures on a {R}iemann surface and
+logarithmic connections, \emph{Doc. Math.} {\bf 24} (2019), 2299--2337.
+\item Biswas, Indranil and Pingali, Vamsi Pritham: A characterization of finite vector bundles on {G}auduchon
+astheno-{K}\"{a}hler manifolds, \emph{\'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art. 6, 13.
+\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi: Edge patch-wise local projection stabilized nonconforming
+{FEM} for the {O}seen problem, \emph{Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214, DOI 10.1515/cmam-2018-0020, \url{https://doi.org/10.1515/cmam-2018-0020}.
 \item Biswas, Shibananda and Ghosh, Gargi and Misra, Gadadhar and
-Shyam Roy, Subrata, {\em On reducing submodules of {H}ilbert modules with
-{${S}_n$}-invariant kernels}, J. Funct. Anal.} {\bf 276} (2019), 751--784, DOI 10.1016/j.jfa.2018.10.025, \url{https://doi.org/10.1016/j.jfa.2018.10.025}.
-\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram, {\em On extension problem, trace {H}ardy and {H}ardy's inequalities
-for some fractional {L}aplacians}, Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605, DOI 10.3934/cpaa.2019116, \url{https://doi.org/10.3934/cpaa.2019116}.
-\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal, {\em Comments on the {G}reen's function of a planar domain}, Anal.
+Shyam Roy, Subrata: On reducing submodules of {H}ilbert modules with
+{${S}_n$}-invariant kernels, \emph{J. Funct. Anal.} {\bf 276} (2019), 751--784, DOI 10.1016/j.jfa.2018.10.025, \url{https://doi.org/10.1016/j.jfa.2018.10.025}.
+\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram: On extension problem, trace {H}ardy and {H}ardy's inequalities
+for some fractional {L}aplacians, \emph{Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605, DOI 10.3934/cpaa.2019116, \url{https://doi.org/10.3934/cpaa.2019116}.
+\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal: Comments on the {G}reen's function of a planar domain, \emph{Anal.
 Math.
@@
 \item Brenner, Susanne C. and Gudi, Thirupathi and Porwal, Kamana
-and Sung, Li-Yeng, {\em A {M}orley finite element method for an elliptic distributed
+and Sung, Li-Yeng: A {M}orley finite element method for an elliptic distributed
 optimal control problem with pointwise state and control
-constraints}, ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206, DOI 10.1051/cocv/2017031, \url{https://doi.org/10.1051/cocv/2017031}.
+constraints, \emph{ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206, DOI 10.1051/cocv/2017031, \url{https://doi.org/10.1051/cocv/2017031}.
 \item Burton, Benjamin A. and Datta, Basudeb and Singh, Nitin and
-Spreer, Jonathan, {\em A construction principle for tight and minimal triangulations
-of manifolds}, Exp. Math.} {\bf 27} (2018), 22--36, DOI 10.1080/10586458.2016.1212747, \url{https://doi.org/10.1080/10586458.2016.1212747}.
-\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella, {\em Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
-indefinite second-order linear elliptic problems}, Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250, DOI 10.1515/cmam-2019-0034, \url{https://doi.org/10.1515/cmam-2019-0034}.
-\item Chandel, Vikramjeet Singh, {\em The three-point {P}ick-{N}evanlinna interpolation problem on
-the polydisc}, Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352, DOI 10.1080/17476933.2017.1370461, \url{https://doi.org/10.1080/17476933.2017.1370461}.
-\item Chatterjee, Esha and Hassan, Sk. Sarif, {\em On the asymptotic character of a generalized rational
-difference equation}, Discrete Contin. Dyn. Syst.} {\bf 38} (2018), 1707--1718, DOI 10.3934/dcds.2018070, \url{https://doi.org/10.3934/dcds.2018070}.
+Spreer, Jonathan: A construction principle for tight and minimal triangulations
+of manifolds, \emph{Exp. Math.} {\bf 27} (2018), 22--36, DOI 10.1080/10586458.2016.1212747, \url{https://doi.org/10.1080/10586458.2016.1212747}.
+\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella: Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
+indefinite second-order linear elliptic problems, \emph{Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250, DOI 10.1515/cmam-2019-0034, \url{https://doi.org/10.1515/cmam-2019-0034}.
+\item Chandel, Vikramjeet Singh: The three-point {P}ick-{N}evanlinna interpolation problem on
+the polydisc, \emph{Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352, DOI 10.1080/17476933.2017.1370461, \url{https://doi.org/10.1080/17476933.2017.1370461}.
+\item Chatterjee, Esha and Hassan, Sk. Sarif: On the asymptotic character of a generalized rational
+difference equation, \emph{Discrete Contin. Dyn. Syst.} {\bf 38} (2018), 1707--1718, DOI 10.3934/dcds.2018070, \url{https://doi.org/10.3934/dcds.2018070}.
 \item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
-K. C., {\em A note on linear preservers of semipositive and minimally
-semipositive matrices}, Electron. J. Linear Algebra} {\bf 34} (2018), 687--694, DOI 10.13001/1081-3810.3864, \url{https://doi.org/10.13001/1081-3810.3864}.
-\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram, {\em Hardy-type inequalities for fractional powers of the
-{D}unkl-{H}ermite operator}, Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544, DOI 10.1017/s0013091517000311, \url{https://doi.org/10.1017/s0013091517000311}.
-\item Das, Soumya and Jha, Abhash Kumar, {\em Analytic properties of twisted real-analytic {H}ermitian
-{K}lingen type {E}isenstein series and applications}, Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116, DOI 10.1007/s12188-019-00206-7, \url{https://doi.org/10.1007/s12188-019-00206-7}.
-\item Das, Soumya and Khan, Rizwanur, {\em The third moment of symmetric square {$L$}-functions}, Q.
+K. C.: A note on linear preservers of semipositive and minimally
+semipositive matrices, \emph{Electron. J. Linear Algebra} {\bf 34} (2018), 687--694, DOI 10.13001/1081-3810.3864, \url{https://doi.org/10.13001/1081-3810.3864}.
+\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram: Hardy-type inequalities for fractional powers of the
+{D}unkl-{H}ermite operator, \emph{Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544, DOI 10.1017/s0013091517000311, \url{https://doi.org/10.1017/s0013091517000311}.
+\item Das, Soumya and Jha, Abhash Kumar: Analytic properties of twisted real-analytic {H}ermitian
+{K}lingen type {E}isenstein series and applications, \emph{Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116, DOI 10.1007/s12188-019-00206-7, \url{https://doi.org/10.1007/s12188-019-00206-7}.
+\item Das, Soumya and Khan, Rizwanur: The third moment of symmetric square {$L$}-functions, \emph{Q.
 J.
 Math.} {\bf 69} (2018), 1063--1087, DOI 10.1093/qmath/hay012, \url{https://doi.org/10.1093/qmath/hay012}.
-\item Das, Soumya and Kohnen, Winfried, {\em On sign changes of eigenvalues of {S}iegel cusp forms of genus
-2 in prime powers}, Acta Arith.} {\bf 183} (2018), 167--172, DOI 10.4064/aa170419-4-11, \url{https://doi.org/10.4064/aa170419-4-11}.
-\item Das, Soumya and Pal, Ritwik, {\em The first negative eigenvalue of {Y}oshida lifts}, Res.
+\item Das, Soumya and Kohnen, Winfried: On sign changes of eigenvalues of {S}iegel cusp forms of genus
+2 in prime powers, \emph{Acta Arith.} {\bf 183} (2018), 167--172, DOI 10.4064/aa170419-4-11, \url{https://doi.org/10.4064/aa170419-4-11}.
+\item Das, Soumya and Pal, Ritwik: The first negative eigenvalue of {Y}oshida lifts, \emph{Res.
 Number Theory} {\bf 5} (2019), Paper No.
 20, 9, DOI 10.1007/s40993-019-0158-x, \url{https://doi.org/10.1007/s40993-019-0158-x}.
-\item Datta, Basudeb and Maity, Dipendu, {\em Semi-equivelar maps on the torus and the {K}lein bottle are
-{A}rchimedean}, Discrete Math.} {\bf 341} (2018), 3296--3309, DOI 10.1016/j.disc.2018.08.016, \url{https://doi.org/10.1016/j.disc.2018.08.016}.
-\item Dond, Asha K. and Gudi, Thirupathi, {\em Patch-wise local projection stabilized finite element methods
-for convection-diffusion-reaction problems}, Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663, DOI 10.1002/num.22317, \url{https://doi.org/10.1002/num.22317}.
-\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH., {\em An error analysis of discontinuous finite element methods for
-the optimal control problems governed by {S}tokes equation}, Numer.
+\item Datta, Basudeb and Maity, Dipendu: Semi-equivelar maps on the torus and the {K}lein bottle are
+{A}rchimedean, \emph{Discrete Math.} {\bf 341} (2018), 3296--3309, DOI 10.1016/j.disc.2018.08.016, \url{https://doi.org/10.1016/j.disc.2018.08.016}.
+\item Dond, Asha K. and Gudi, Thirupathi: Patch-wise local projection stabilized finite element methods
+for convection-diffusion-reaction problems, \emph{Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663, DOI 10.1002/num.22317, \url{https://doi.org/10.1002/num.22317}.
+\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH.: An error analysis of discontinuous finite element methods for
+the optimal control problems governed by {S}tokes equation, \emph{Numer.
 Funct.
@@
 \item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P.
-and Silberman, Lior and Tao, Terence, {\em Homogeneous length functions on groups}, Algebra Number Theory} {\bf 12} (2018), 1773--1786, DOI 10.2140/ant.2018.12.1773, \url{https://doi.org/10.2140/ant.2018.12.1773}.
-\item Gaddam, Sharat and Gudi, Thirupathi, {\em Inhomogeneous {D}irichlet boundary condition in the {\it a
-posteriori} error control of the obstacle problem}, Comput. Math. Appl.} {\bf 75} (2018), 2311--2327, DOI 10.1016/j.camwa.2017.12.010, \url{https://doi.org/10.1016/j.camwa.2017.12.010}.
-\item Gaddam, Sharat and Gudi, Thirupathi, {\em Bubbles enriched quadratic finite element method for the
-3{D}-elliptic obstacle problem}, Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236, DOI 10.1515/cmam-2017-0018, \url{https://doi.org/10.1515/cmam-2017-0018}.
-\item Garani, Shayan Srinivasa and Seshadri, Harish, {\em An algorithmic approach to {S}outh {I}ndian classical music}, J.
+and Silberman, Lior and Tao, Terence: Homogeneous length functions on groups, \emph{Algebra Number Theory} {\bf 12} (2018), 1773--1786, DOI 10.2140/ant.2018.12.1773, \url{https://doi.org/10.2140/ant.2018.12.1773}.
+\item Gaddam, Sharat and Gudi, Thirupathi: Inhomogeneous {D}irichlet boundary condition in the {\it a
+posteriori} error control of the obstacle problem, \emph{Comput. Math. Appl.} {\bf 75} (2018), 2311--2327, DOI 10.1016/j.camwa.2017.12.010, \url{https://doi.org/10.1016/j.camwa.2017.12.010}.
+\item Gaddam, Sharat and Gudi, Thirupathi: Bubbles enriched quadratic finite element method for the
+3{D}-elliptic obstacle problem, \emph{Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236, DOI 10.1515/cmam-2017-0018, \url{https://doi.org/10.1515/cmam-2017-0018}.
+\item Garani, Shayan Srinivasa and Seshadri, Harish: An algorithmic approach to {S}outh {I}ndian classical music, \emph{J.
 Math.
 Music} {\bf 13} (2019), 107--134, DOI 10.1080/17459737.2019.1604845, \url{https://doi.org/10.1080/17459737.2019.1604845}.
-\item Gaussier, Herv\'{e} and Seshadri, Harish, {\em Holomorphic motions and complex geometry}, Proc.
+\item Gaussier, Herv\'{e} and Seshadri, Harish: Holomorphic motions and complex geometry, \emph{Proc.
 Amer.
@@
 Soc.} {\bf 147} (2019), 301--313, DOI 10.1090/proc/14217, \url{https://doi.org/10.1090/proc/14217}.
-\item Gaussier, Herv\'{e} and Seshadri, Harish, {\em On the {G}romov hyperbolicity of convex domains in {$\Bbb
-C^n$}}, Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641, DOI 10.1007/s40315-018-0243-5, \url{https://doi.org/10.1007/s40315-018-0243-5}.
-\item Ghara, Soumitra and Kumar, Surjit, {\em On the sum of two subnormal kernels}, J.
+\item Gaussier, Herv\'{e} and Seshadri, Harish: On the {G}romov hyperbolicity of convex domains in {$\Bbb
+C^n$}, \emph{Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641, DOI 10.1007/s40315-018-0243-5, \url{https://doi.org/10.1007/s40315-018-0243-5}.
+\item Ghara, Soumitra and Kumar, Surjit: On the sum of two subnormal kernels, \emph{J.
 Math.
@@
 Appl.} {\bf 469} (2019), 1015--1027, DOI 10.1016/j.jmaa.2018.09.048, \url{https://doi.org/10.1016/j.jmaa.2018.09.048}.
-\item Ghosh, Mrinal K. and Pradhan, Somnath, {\em Risk-sensitive stochastic differential games with reflecting
-diffusions}, Stoch. Anal. Appl.} {\bf 36} (2018), 1--27, DOI 10.1080/07362994.2017.1356732, \url{https://doi.org/10.1080/07362994.2017.1356732}.
-\item Gudi, Thirupathi and Majumder, Papri, {\em Convergence analysis of finite element method for a parabolic
-obstacle problem}, J. Comput. Appl. Math.} {\bf 357} (2019), 85--102, DOI 10.1016/j.cam.2019.02.026, \url{https://doi.org/10.1016/j.cam.2019.02.026}.
-\item Gudi, Thirupathi and Majumder, Papri, {\em Conforming and discontinuous {G}alerkin {FEM} in space for
-solving parabolic obstacle problem}, Comput. Math. Appl.} {\bf 78} (2019), 3896--3915, DOI 10.1016/j.camwa.2019.06.022, \url{https://doi.org/10.1016/j.camwa.2019.06.022}.
-\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh, {\em Von {N}eumann's inequality for commuting operator-valued
-multishifts}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608, DOI 10.1090/proc/14410, \url{https://doi.org/10.1090/proc/14410}.
-\item Gupta, Rajeev and Ramiz Reza, Md., {\em Operator space structures on {$\ell^1(n)$}}, Houston J. Math.} {\bf 44} (2018), 1205--1212.
-\item Gupta, S. C., {\em The classical {S}tefan problem}, } {\bf } (2018), xxiii+726.
-\item Gupta, Subhojoy, {\em Limits of harmonic maps and crowned hyperbolic surfaces}, Trans.
+\item Ghosh, Mrinal K. and Pradhan, Somnath: Risk-sensitive stochastic differential games with reflecting
+diffusions, \emph{Stoch. Anal. Appl.} {\bf 36} (2018), 1--27, DOI 10.1080/07362994.2017.1356732, \url{https://doi.org/10.1080/07362994.2017.1356732}.
+\item Gudi, Thirupathi and Majumder, Papri: Convergence analysis of finite element method for a parabolic
+obstacle problem, \emph{J. Comput. Appl. Math.} {\bf 357} (2019), 85--102, DOI 10.1016/j.cam.2019.02.026, \url{https://doi.org/10.1016/j.cam.2019.02.026}.
+\item Gudi, Thirupathi and Majumder, Papri: Conforming and discontinuous {G}alerkin {FEM} in space for
+solving parabolic obstacle problem, \emph{Comput. Math. Appl.} {\bf 78} (2019), 3896--3915, DOI 10.1016/j.camwa.2019.06.022, \url{https://doi.org/10.1016/j.camwa.2019.06.022}.
+\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: Von {N}eumann's inequality for commuting operator-valued
+multishifts, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608, DOI 10.1090/proc/14410, \url{https://doi.org/10.1090/proc/14410}.
+\item Gupta, Rajeev and Ramiz Reza, Md.: Operator space structures on {$\ell^1(n)$}, \emph{Houston J. Math.} {\bf 44} (2018), 1205--1212.
+\item Gupta, S. C.: The classical {S}tefan problem, \emph{} {\bf } (2018), xxiii+726.
+\item Gupta, Subhojoy: Limits of harmonic maps and crowned hyperbolic surfaces, \emph{Trans.
 Amer.
@@
 Soc.} {\bf 372} (2019), 7573--7596, DOI 10.1090/tran/7777, \url{https://doi.org/10.1090/tran/7777}.
-\item Gupta, Subhojoy and Wolf, Michael, {\em Meromorphic quadratic differentials and measured foliations on
-a {R}iemann surface}, Math. Ann.} {\bf 373} (2019), 73--118, DOI 10.1007/s00208-018-1674-z, \url{https://doi.org/10.1007/s00208-018-1674-z}.
-\item Hazra, Somnath, {\em Homogeneous 2-shifts}, Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763, DOI 10.1007/s11785-018-0822-5, \url{https://doi.org/10.1007/s11785-018-0822-5}.
-\item Iyer, Srikanth K., {\em The random connection model: connectivity, edge lengths, and
-degree distributions}, Random Structures Algorithms} {\bf 52} (2018), 283--300, DOI 10.1002/rsa.20741, \url{https://doi.org/10.1002/rsa.20741}.
+\item Gupta, Subhojoy and Wolf, Michael: Meromorphic quadratic differentials and measured foliations on
+a {R}iemann surface, \emph{Math. Ann.} {\bf 373} (2019), 73--118, DOI 10.1007/s00208-018-1674-z, \url{https://doi.org/10.1007/s00208-018-1674-z}.
+\item Hazra, Somnath: Homogeneous 2-shifts, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763, DOI 10.1007/s11785-018-0822-5, \url{https://doi.org/10.1007/s11785-018-0822-5}.
+\item Iyer, Srikanth K.: The random connection model: connectivity, edge lengths, and
+degree distributions, \emph{Random Structures Algorithms} {\bf 52} (2018), 283--300, DOI 10.1002/rsa.20741, \url{https://doi.org/10.1002/rsa.20741}.
 \item Jha, Abhash Kumar and Juyal, Abhishek and Pandey, Manish
-Kumar, {\em On simultaneous non-vanishing of twisted {$L$}-functions
-associated to newforms on {$\Gamma_0(N)$}}, J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.
-\item Jha, Abhash Kumar and Sahu, Brundaban, {\em Rankin-{C}ohen brackets on {J}acobi forms of several variables
-and special values of certain {D}irichlet series}, Int. J. Number Theory} {\bf 15} (2019), 925--933, DOI 10.1142/S1793042119500490, \url{https://doi.org/10.1142/S1793042119500490}.
-\item Jha, Abhash Kumar and Sahu, Brundaban, {\em Differential operators on {J}acobi forms and special values of
-certain {D}irichlet series}, Automorphic forms and related topics} {\bf 732} (2019), 91--99, DOI 10.1090/conm/732/14793, \url{https://doi.org/10.1090/conm/732/14793}.
+Kumar: On simultaneous non-vanishing of twisted {$L$}-functions
+associated to newforms on {$\Gamma_0(N)$}, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.
+\item Jha, Abhash Kumar and Sahu, Brundaban: Rankin-{C}ohen brackets on {J}acobi forms of several variables
+and special values of certain {D}irichlet series, \emph{Int. J. Number Theory} {\bf 15} (2019), 925--933, DOI 10.1142/S1793042119500490, \url{https://doi.org/10.1142/S1793042119500490}.
+\item Jha, Abhash Kumar and Sahu, Brundaban: Differential operators on {J}acobi forms and special values of
+certain {D}irichlet series, \emph{Automorphic forms and related topics} {\bf 732} (2019), 91--99, DOI 10.1090/conm/732/14793, \url{https://doi.org/10.1090/conm/732/14793}.
 \item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
-Sekar, Sruthi, {\em Non-malleable randomness encoders and their applications}, Advances in cryptology---{EUROCRYPT} 2018. {P}art {III}} {\bf 10822} (2018), 589--617.
+Sekar, Sruthi: Non-malleable randomness encoders and their applications, \emph{Advances in cryptology---{EUROCRYPT} 2018. {P}art {III}} {\bf 10822} (2018), 589--617.
 \item Kashyap, G.
@@
 Ravindranath and G.
-Ambika, {\em Synapse loss and progress of Alzheimer&rsquo;s disease - A network model}, Scientific Reports} {\bf 9} (2019), .
-\item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan, {\em On the convolution of {M}ittag-{L}effler distributions and its
-applications to fractional point processes}, Stoch. Anal. Appl.} {\bf 37} (2019), 115--122, DOI 10.1080/07362994.2018.1538803, \url{https://doi.org/10.1080/07362994.2018.1538803}.
+Ambika: Synapse loss and progress of Alzheimers disease - A network model, \emph{Scientific Reports} {\bf 9} (2019).
+\item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan: On the convolution of {M}ittag-{L}effler distributions and its
+applications to fractional point processes, \emph{Stoch. Anal. Appl.} {\bf 37} (2019), 115--122, DOI 10.1080/07362994.2018.1538803, \url{https://doi.org/10.1080/07362994.2018.1538803}.
 \item Khan, Mohammad Yasir Feroz and Biswas, Rahul and Sau, Ramesh
-Chandra, {\em Instability of {L}agrange interpolation on {$H^1(\Omega)\cap
-C(\overline\Omega)$}}, Math. Student} {\bf 88} (2019), 153--158.
-\item Khare, Apoorva, {\em Generalized nil-{C}oxeter algebras over discrete complex
-reflection groups}, Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999, DOI 10.1090/tran/7304, \url{https://doi.org/10.1090/tran/7304}.
-\item Khare, Apoorva and Tikaradze, Akaki, {\em A {C}arlitz--von {S}taudt type theorem for finite rings}, Linear Algebra Appl.} {\bf 568} (2019), 106--126, DOI 10.1016/j.laa.2018.05.035, \url{https://doi.org/10.1016/j.laa.2018.05.035}.
-\item Krakovski, Roi and Onn, Uri and Singla, Pooja, {\em Regular characters of groups of type {$\ssf A_n$} over
-discrete valuation rings}, J. Algebra} {\bf 496} (2018), 116--137, DOI 10.1016/j.jalgebra.2017.10.018, \url{https://doi.org/10.1016/j.jalgebra.2017.10.018}.
+Chandra: Instability of {L}agrange interpolation on {$H^1(\Omega)\cap
+C(\overline\Omega)$}, \emph{Math. Student} {\bf 88} (2019), 153--158.
+\item Khare, Apoorva: Generalized nil-{C}oxeter algebras over discrete complex
+reflection groups, \emph{Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999, DOI 10.1090/tran/7304, \url{https://doi.org/10.1090/tran/7304}.
+\item Khare, Apoorva and Tikaradze, Akaki: A {C}arlitz--von {S}taudt type theorem for finite rings, \emph{Linear Algebra Appl.} {\bf 568} (2019), 106--126, DOI 10.1016/j.laa.2018.05.035, \url{https://doi.org/10.1016/j.laa.2018.05.035}.
+\item Krakovski, Roi and Onn, Uri and Singla, Pooja: Regular characters of groups of type {$\ssf A_n$} over
+discrete valuation rings, \emph{J. Algebra} {\bf 496} (2018), 116--137, DOI 10.1016/j.jalgebra.2017.10.018, \url{https://doi.org/10.1016/j.jalgebra.2017.10.018}.
 \item Lin, X.
@@
 and Jolly, M.
-K., {\em Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level}, Biomolecules} {\bf 9} (2019), 77.
-\item Mahajan, Prachi and Verma, Kaushal, {\em A comparison of two biholomorphic invariants}, Internat.
+K.: Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level, \emph{Biomolecules} {\bf 9} (2019), 77.
+\item Mahajan, Prachi and Verma, Kaushal: A comparison of two biholomorphic invariants, \emph{Internat.
 J.
 Math.} {\bf 30} (2019), 1950012, 16, DOI 10.1142/S0129167X19500125, \url{https://doi.org/10.1142/S0129167X19500125}.
-\item Maity, Dipendu, {\em Pentagonal maps on the torus and the plane}, Beitr. Algebra Geom.} {\bf 60} (2019), 17--37, DOI 10.1007/s13366-018-0405-7, \url{https://doi.org/10.1007/s13366-018-0405-7}.
-\item Maity, Dipendu and Upadhyay, Ashish Kumar, {\em On centrally symmetric manifolds}, J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.
+\item Maity, Dipendu: Pentagonal maps on the torus and the plane, \emph{Beitr. Algebra Geom.} {\bf 60} (2019), 17--37, DOI 10.1007/s13366-018-0405-7, \url{https://doi.org/10.1007/s13366-018-0405-7}.
+\item Maity, Dipendu and Upadhyay, Ashish Kumar: On centrally symmetric manifolds, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.
 \item Mal, Arpita and Paul, Kallol and Rao, T. S. S. R. K. and Sain,
-Debmalya, {\em Approximate {B}irkhoff-{J}ames orthogonality and smoothness in
-the space of bounded linear operators}, Monatsh. Math.} {\bf 190} (2019), 549--558, DOI 10.1007/s00605-019-01289-3, \url{https://doi.org/10.1007/s00605-019-01289-3}.
-\item Mal, Arpita and Sain, Debmalya and Paul, Kallol, {\em On some geometric properties of operator spaces}, Banach J.
+Debmalya: Approximate {B}irkhoff-{J}ames orthogonality and smoothness in
+the space of bounded linear operators, \emph{Monatsh. Math.} {\bf 190} (2019), 549--558, DOI 10.1007/s00605-019-01289-3, \url{https://doi.org/10.1007/s00605-019-01289-3}.
+\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: On some geometric properties of operator spaces, \emph{Banach J.
 Math.
 Anal.} {\bf 13} (2019), 174--191, DOI 10.1215/17358787-2018-0021, \url{https://doi.org/10.1215/17358787-2018-0021}.
-\item Manfio, F. and Turgay, N. C. and Upadhyay, A., {\em Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
-{$\Bbb{H}^n\times\Bbb{R}$}}, J. Geom. Anal.} {\bf 29} (2019), 283--298, DOI 10.1007/s12220-018-9990-9, \url{https://doi.org/10.1007/s12220-018-9990-9}.
+\item Manfio, F. and Turgay, N. C. and Upadhyay, A.: Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
+{$\Bbb{H}^n\times\Bbb{R}$}, \emph{J. Geom. Anal.} {\bf 29} (2019), 283--298, DOI 10.1007/s12220-018-9990-9, \url{https://doi.org/10.1007/s12220-018-9990-9}.
 \item Manikandan, K. and Vishnu Priya, N. and Senthilvelan, M. and
-Sankaranarayanan, R., {\em Deformation of dark solitons in a {$\Cal{PT}$}-invariant
+Sankaranarayanan, R.: Deformation of dark solitons in a {$\Cal{PT}$}-invariant
 variable coefficients nonlocal nonlinear {S}chr\"{o}dinger
-equation}, Chaos} {\bf 28} (2018), 083103, 12, DOI 10.1063/1.5039901, \url{https://doi.org/10.1063/1.5039901}.
-\item Misra, Gadadhar, {\em Operators in the {C}owen-{D}ouglas class and related topics}, Handbook of analytic operator theory} {\bf } (2019), 87--137.
-\item Misra, Gadadhar and Pal, Avijit, {\em Curvature inequalities for operators in the {C}owen-{D}ouglas
-class and localization of the {W}allach set}, J. Anal. Math.} {\bf 136} (2018), 31--54, DOI 10.1007/s11854-018-0054-7, \url{https://doi.org/10.1007/s11854-018-0054-7}.
-\item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian, {\em Contractivity and complete contractivity for finite
-dimensional {B}anach spaces}, J. Operator Theory} {\bf 82} (2019), 23--47, DOI 10.7900/jot.2018jun13.2225, \url{https://doi.org/10.7900/jot.2018jun13.2225}.
+equation, \emph{Chaos} {\bf 28} (2018), 083103, 12, DOI 10.1063/1.5039901, \url{https://doi.org/10.1063/1.5039901}.
+\item Misra, Gadadhar: Operators in the {C}owen-{D}ouglas class and related topics, \emph{Handbook of analytic operator theory} {\bf } (2019), 87--137.
+\item Misra, Gadadhar and Pal, Avijit: Curvature inequalities for operators in the {C}owen-{D}ouglas
+class and localization of the {W}allach set, \emph{J. Anal. Math.} {\bf 136} (2018), 31--54, DOI 10.1007/s11854-018-0054-7, \url{https://doi.org/10.1007/s11854-018-0054-7}.
+\item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian: Contractivity and complete contractivity for finite
+dimensional {B}anach spaces, \emph{J. Operator Theory} {\bf 82} (2019), 23--47, DOI 10.7900/jot.2018jun13.2225, \url{https://doi.org/10.7900/jot.2018jun13.2225}.
 \item Misra, Gadadhar and Reza, Md.
-Ramiz, {\em Curvature inequalities and extremal operators}, Illinois J.
+Ramiz: Curvature inequalities and extremal operators, \emph{Illinois J.
 Math.} {\bf 63} (2019), 193--217, DOI 10.1215/00192082-7768711, \url{https://doi.org/10.1215/00192082-7768711}.
-\item Mukherjee, Sajal Kumar and Bera, Sudip, {\em Combinatorial proofs of the {N}ewton-{G}irard and
-{C}hapman-{C}ostas-{S}antos identities}, Discrete Math.} {\bf 342} (2019), 1577--1580, DOI 10.1016/j.disc.2019.02.013, \url{https://doi.org/10.1016/j.disc.2019.02.013}.
-\item Narayanan, E. K. and Singla, Pooja, {\em On monomial representations of finitely generated nilpotent
-groups}, Comm. Algebra} {\bf 46} (2018), 2319--2331, DOI 10.1080/00927872.2017.1378894, \url{https://doi.org/10.1080/00927872.2017.1378894}.
-\item Pal, Chandan and Pradhan, Somnath, {\em Risk sensitive control of pure jump processes on a general
-state space}, Stochastics} {\bf 91} (2019), 155--174, DOI 10.1080/17442508.2018.1521413, \url{https://doi.org/10.1080/17442508.2018.1521413}.
-\item Pal, Ratna and Verma, Kaushal, {\em Ergodic properties of families of {H}\'{e}non maps}, Ann.
+\item Mukherjee, Sajal Kumar and Bera, Sudip: Combinatorial proofs of the {N}ewton-{G}irard and
+{C}hapman-{C}ostas-{S}antos identities, \emph{Discrete Math.} {\bf 342} (2019), 1577--1580, DOI 10.1016/j.disc.2019.02.013, \url{https://doi.org/10.1016/j.disc.2019.02.013}.
+\item Narayanan, E. K. and Singla, Pooja: On monomial representations of finitely generated nilpotent
+groups, \emph{Comm. Algebra} {\bf 46} (2018), 2319--2331, DOI 10.1080/00927872.2017.1378894, \url{https://doi.org/10.1080/00927872.2017.1378894}.
+\item Pal, Chandan and Pradhan, Somnath: Risk sensitive control of pure jump processes on a general
+state space, \emph{Stochastics} {\bf 91} (2019), 155--174, DOI 10.1080/17442508.2018.1521413, \url{https://doi.org/10.1080/17442508.2018.1521413}.
+\item Pal, Ratna and Verma, Kaushal: Ergodic properties of families of {H}\'{e}non maps, \emph{Ann.
 Polon.
 Math.} {\bf 121} (2018), 45--71, DOI 10.4064/ap170928-2-4, \url{https://doi.org/10.4064/ap170928-2-4}.
-\item Paul, Kallol and Sain, Debmalya, {\em Birkhoff-{J}ames orthogonality and its application in the
-study of geometry of {B}anach space}, Advanced topics in mathematical analysis} {\bf } (2019), 245--284.
-\item Paul, Kallol and Sain, Debmalya and Ghosh, Puja, {\em Symmetry of {B}irkhoff-{J}ames orthogonality of bounded linear
-operators}, Ulam type stability} {\bf } (2019), 331--344.
-\item Paul, Kallol and Sain, Debmalya and Mal, Arpita, {\em Approximate {B}irkhoff-{J}ames orthogonality in the space of
-bounded linear operators}, Linear Algebra Appl.} {\bf 537} (2018), 348--357, DOI 10.1016/j.laa.2017.10.008, \url{https://doi.org/10.1016/j.laa.2017.10.008}.
+\item Paul, Kallol and Sain, Debmalya: Birkhoff-{J}ames orthogonality and its application in the
+study of geometry of {B}anach space, \emph{Advanced topics in mathematical analysis} {\bf } (2019), 245--284.
+\item Paul, Kallol and Sain, Debmalya and Ghosh, Puja: Symmetry of {B}irkhoff-{J}ames orthogonality of bounded linear
+operators, \emph{Ulam type stability} {\bf } (2019), 331--344.
+\item Paul, Kallol and Sain, Debmalya and Mal, Arpita: Approximate {B}irkhoff-{J}ames orthogonality in the space of
+bounded linear operators, \emph{Linear Algebra Appl.} {\bf 537} (2018), 348--357, DOI 10.1016/j.laa.2017.10.008, \url{https://doi.org/10.1016/j.laa.2017.10.008}.
 \item Paul, Kallol and Sain, Debmalya and Mal, Arpita and Mandal,
-Kalidas, {\em Orthogonality of bounded linear operators on complex {B}anach
-spaces}, Adv. Oper. Theory} {\bf 3} (2018), 699--709, DOI 10.15352/aot.1712-1268, \url{https://doi.org/10.15352/aot.1712-1268}.
-\item Pingali, Vamsi P., {\em A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE}}, Complex Var.
+Kalidas: Orthogonality of bounded linear operators on complex {B}anach
+spaces, \emph{Adv. Oper. Theory} {\bf 3} (2018), 699--709, DOI 10.15352/aot.1712-1268, \url{https://doi.org/10.15352/aot.1712-1268}.
+\item Pingali, Vamsi P.: A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE}, \emph{Complex Var.
 Elliptic Equ.} {\bf 64} (2019), 503--518, DOI 10.1080/17476933.2018.1454914, \url{https://doi.org/10.1080/17476933.2018.1454914}.
-\item Pingali, Vamsi Pritham, {\em A note on higher extremal metrics}, Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010, DOI 10.1090/tran/7416, \url{https://doi.org/10.1090/tran/7416}.
-\item Pingali, Vamsi Pritham, {\em Representability of {C}hern-{W}eil forms}, Math. Z.} {\bf 288} (2018), 629--641, DOI 10.1007/s00209-017-1903-2, \url{https://doi.org/10.1007/s00209-017-1903-2}.
-\item Pritham Pingali, Vamsi, {\em Existence of coupled {K}\"{a}hler-{E}instein metrics using the
-continuity method}, Internat. J. Math.} {\bf 29} (2018), 1850041, 8, DOI 10.1142/S0129167X18500416, \url{https://doi.org/10.1142/S0129167X18500416}.
-\item Quddus, Safdar, {\em Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
-spheres}, J. Noncommut. Geom.} {\bf 13} (2019), 257--267, DOI 10.4171/JNCG/320, \url{https://doi.org/10.4171/JNCG/320}.
-\item Reddy, Nanda Kishore, {\em Equality of {L}yapunov and stability exponents for products of
-isotropic random matrices}, Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624, DOI 10.1093/imrn/rnx134, \url{https://doi.org/10.1093/imrn/rnx134}.
-\item Reza, Md. Ramiz, {\em Curvature inequalities for operators in the {C}owen-{D}ouglas
-class of a planar domain}, Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279, DOI 10.1512/iumj.2018.67.7320, \url{https://doi.org/10.1512/iumj.2018.67.7320}.
-\item Roth, Julien and Upadhyay, Abhitosh, {\em On compact anisotropic {W}eingarten hypersurfaces in
-{E}uclidean space}, Arch. Math. (Basel)} {\bf 113} (2019), 213--224, DOI 10.1007/s00013-019-01315-8, \url{https://doi.org/10.1007/s00013-019-01315-8}.
-\item Roy, Krishanu and Venkatesh, R., {\em Maximal closed subroot systems of real affine root systems}, Transform.
+\item Pingali, Vamsi Pritham: A note on higher extremal metrics, \emph{Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010, DOI 10.1090/tran/7416, \url{https://doi.org/10.1090/tran/7416}.
+\item Pingali, Vamsi Pritham: Representability of {C}hern-{W}eil forms, \emph{Math. Z.} {\bf 288} (2018), 629--641, DOI 10.1007/s00209-017-1903-2, \url{https://doi.org/10.1007/s00209-017-1903-2}.
+\item Pritham Pingali, Vamsi: Existence of coupled {K}\"{a}hler-{E}instein metrics using the
+continuity method, \emph{Internat. J. Math.} {\bf 29} (2018), 1850041, 8, DOI 10.1142/S0129167X18500416, \url{https://doi.org/10.1142/S0129167X18500416}.
+\item Quddus, Safdar: Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
+spheres, \emph{J. Noncommut. Geom.} {\bf 13} (2019), 257--267, DOI 10.4171/JNCG/320, \url{https://doi.org/10.4171/JNCG/320}.
+\item Reddy, Nanda Kishore: Equality of {L}yapunov and stability exponents for products of
+isotropic random matrices, \emph{Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624, DOI 10.1093/imrn/rnx134, \url{https://doi.org/10.1093/imrn/rnx134}.
+\item Reza, Md. Ramiz: Curvature inequalities for operators in the {C}owen-{D}ouglas
+class of a planar domain, \emph{Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279, DOI 10.1512/iumj.2018.67.7320, \url{https://doi.org/10.1512/iumj.2018.67.7320}.
+\item Roth, Julien and Upadhyay, Abhitosh: On compact anisotropic {W}eingarten hypersurfaces in
+{E}uclidean space, \emph{Arch. Math. (Basel)} {\bf 113} (2019), 213--224, DOI 10.1007/s00013-019-01315-8, \url{https://doi.org/10.1007/s00013-019-01315-8}.
+\item Roy, Krishanu and Venkatesh, R.: Maximal closed subroot systems of real affine root systems, \emph{Transform.
 Groups} {\bf 24} (2019), 1261--1308, DOI 10.1007/s00031-018-9510-9, \url{https://doi.org/10.1007/s00031-018-9510-9}.
-\item Sain, Debmalya, {\em On extreme contractions and the norm attainment set of a
-bounded linear operator}, Ann. Funct. Anal.} {\bf 10} (2019), 135--143, DOI 10.1215/20088752-2018-0014, \url{https://doi.org/10.1215/20088752-2018-0014}.
-\item Sain, Debmalya, {\em On the norm attainment set of a bounded linear operator}, J.
+\item Sain, Debmalya: On extreme contractions and the norm attainment set of a
+bounded linear operator, \emph{Ann. Funct. Anal.} {\bf 10} (2019), 135--143, DOI 10.1215/20088752-2018-0014, \url{https://doi.org/10.1215/20088752-2018-0014}.
+\item Sain, Debmalya: On the norm attainment set of a bounded linear operator, \emph{J.
 Math.
@@
 Appl.} {\bf 457} (2018), 67--76, DOI 10.1016/j.jmaa.2017.07.070, \url{https://doi.org/10.1016/j.jmaa.2017.07.070}.
-\item Sain, Debmalya, {\em Smooth points in operator spaces and some
-{B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces}, Oper. Matrices} {\bf 13} (2019), 433--445, DOI 10.7153/oam-2019-13-32, \url{https://doi.org/10.7153/oam-2019-13-32}.
+\item Sain, Debmalya: Smooth points in operator spaces and some
+{B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces, \emph{Oper. Matrices} {\bf 13} (2019), 433--445, DOI 10.7153/oam-2019-13-32, \url{https://doi.org/10.7153/oam-2019-13-32}.
 \item Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag,
-Santanu, {\em On the numerical index of polyhedral {B}anach spaces}, Linear Algebra Appl.} {\bf 577} (2019), 121--133, DOI 10.1016/j.laa.2019.04.024, \url{https://doi.org/10.1016/j.laa.2019.04.024}.
-\item Sain, Debmalya and Paul, Kallol and Mal, Arpita, {\em A complete characterization of {B}irkhoff-{J}ames
-orthogonality in infinite dimensional normed space}, J. Operator Theory} {\bf 80} (2018), 399--413.
-\item Sain, Debmalya and Paul, Kallol and Mal, Arpita, {\em On approximate {B}irkhoff-{J}ames orthogonality and normal
-cones in a normed space}, J. Convex Anal.} {\bf 26} (2019), 341--351.
-\item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas, {\em On two extremum problems related to the norm of a bounded
-linear operator}, Oper. Matrices} {\bf 13} (2019), 421--432, DOI 10.7153/oam-2019-13-31, \url{https://doi.org/10.7153/oam-2019-13-31}.
-\item Sain, Debmalya and Ray, Anubhab and Paul, Kallol, {\em Extreme contractions on finite-dimensional polygonal {B}anach
-spaces}, J. Convex Anal.} {\bf 26} (2019), 877--885.
-\item Sanki, Bidyut, {\em Filling of closed surfaces}, J. Topol. Anal.} {\bf 10} (2018), 897--913, DOI 10.1142/S1793525318500309, \url{https://doi.org/10.1142/S1793525318500309}.
-\item Sanki, Bidyut and Gadgil, Siddhartha, {\em Graphs of systoles on hyperbolic surfaces}, J.
+Santanu: On the numerical index of polyhedral {B}anach spaces, \emph{Linear Algebra Appl.} {\bf 577} (2019), 121--133, DOI 10.1016/j.laa.2019.04.024, \url{https://doi.org/10.1016/j.laa.2019.04.024}.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: A complete characterization of {B}irkhoff-{J}ames
+orthogonality in infinite dimensional normed space, \emph{J. Operator Theory} {\bf 80} (2018), 399--413.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: On approximate {B}irkhoff-{J}ames orthogonality and normal
+cones in a normed space, \emph{J. Convex Anal.} {\bf 26} (2019), 341--351.
+\item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas: On two extremum problems related to the norm of a bounded
+linear operator, \emph{Oper. Matrices} {\bf 13} (2019), 421--432, DOI 10.7153/oam-2019-13-31, \url{https://doi.org/10.7153/oam-2019-13-31}.
+\item Sain, Debmalya and Ray, Anubhab and Paul, Kallol: Extreme contractions on finite-dimensional polygonal {B}anach
+spaces, \emph{J. Convex Anal.} {\bf 26} (2019), 877--885.
+\item Sanki, Bidyut: Filling of closed surfaces, \emph{J. Topol. Anal.} {\bf 10} (2018), 897--913, DOI 10.1142/S1793525318500309, \url{https://doi.org/10.1142/S1793525318500309}.
+\item Sanki, Bidyut and Gadgil, Siddhartha: Graphs of systoles on hyperbolic surfaces, \emph{J.
 Topol.
 Anal.} {\bf 11} (2019), 1--20, DOI 10.1142/S1793525319500018, \url{https://doi.org/10.1142/S1793525319500018}.
-\item Seshadri, Harish, {\em Differential geometry in {I}ndia}, Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799, DOI 10.1007/s13226-019-0355-2, \url{https://doi.org/10.1007/s13226-019-0355-2}.
-\item Seshadri, Harish and Verma, Kaushal, {\em Some aspects of the automorphism groups of domains}, Handbook of group actions. {V}ol. {III}} {\bf 40} (2018), 145--174.
-\item Thangavelu, Sundaram, {\em An analogue of {P}fannschmidt's theorem for the {H}eisenberg
-group}, J. Anal.} {\bf 26} (2018), 235--244, DOI 10.1007/s41478-018-0147-9, \url{https://doi.org/10.1007/s41478-018-0147-9}.
-\item Thangavelu, Sundaram and Naidu Dogga, Venku, {\em {$L^p$}-{$L^2$} estimates for solutions of the wave equation
-associated to the {G}rushin operator}, Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92, DOI 10.1515/apam-2017-0042, \url{https://doi.org/10.1515/apam-2017-0042}.
-\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh, {\em On biconservative hypersurfaces in 4-dimensional {R}iemannian
-space forms}, Math. Nachr.} {\bf 292} (2019), 905--921, DOI 10.1002/mana.201700328, \url{https://doi.org/10.1002/mana.201700328}.
-\item Urbina-Romero, Wilfredo, {\em Gaussian harmonic analysis}, } {\bf } (2019), xix+477, DOI 10.1007/978-3-030-05597-4, \url{https://doi.org/10.1007/978-3-030-05597-4}.
-\item Verma, Kaushal, {\em Notes on the boundaries of quadrature domains}, Anal. Math. Phys.} {\bf 9} (2019), 617--638, DOI 10.1007/s13324-018-0221-0, \url{https://doi.org/10.1007/s13324-018-0221-0}.
+\item Seshadri, Harish: Differential geometry in {I}ndia, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799, DOI 10.1007/s13226-019-0355-2, \url{https://doi.org/10.1007/s13226-019-0355-2}.
+\item Seshadri, Harish and Verma, Kaushal: Some aspects of the automorphism groups of domains, \emph{Handbook of group actions. {V}ol. {III}} {\bf 40} (2018), 145--174.
+\item Thangavelu, Sundaram: An analogue of {P}fannschmidt's theorem for the {H}eisenberg
+group, \emph{J. Anal.} {\bf 26} (2018), 235--244, DOI 10.1007/s41478-018-0147-9, \url{https://doi.org/10.1007/s41478-018-0147-9}.
+\item Thangavelu, Sundaram and Naidu Dogga, Venku: {$L^p$}-{$L^2$} estimates for solutions of the wave equation
+associated to the {G}rushin operator, \emph{Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92, DOI 10.1515/apam-2017-0042, \url{https://doi.org/10.1515/apam-2017-0042}.
+\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh: On biconservative hypersurfaces in 4-dimensional {R}iemannian
+space forms, \emph{Math. Nachr.} {\bf 292} (2019), 905--921, DOI 10.1002/mana.201700328, \url{https://doi.org/10.1002/mana.201700328}.
+\item Urbina-Romero, Wilfredo: Gaussian harmonic analysis, \emph{} {\bf } (2019), xix+477, DOI 10.1007/978-3-030-05597-4, \url{https://doi.org/10.1007/978-3-030-05597-4}.
+\item Verma, Kaushal: Notes on the boundaries of quadrature domains, \emph{Anal. Math. Phys.} {\bf 9} (2019), 617--638, DOI 10.1007/s13324-018-0221-0, \url{https://doi.org/10.1007/s13324-018-0221-0}.
 \item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan,
-Govindan, {\em On the role of four-wave mixing effect in the interactions
+Govindan: On the role of four-wave mixing effect in the interactions
 between nonlinear modes of coupled generalized nonlinear
-{S}chr\"{o}dinger equation}, Chaos} {\bf 29} (2019), 123135, 14, DOI 10.1063/1.5121245, \url{https://doi.org/10.1063/1.5121245}.
+{S}chr\"{o}dinger equation, \emph{Chaos} {\bf 29} (2019), 123135, 14, DOI 10.1063/1.5121245, \url{https://doi.org/10.1063/1.5121245}.
 \item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, Govindan
-and Lakshmanan, M., {\em On symmetry preserving and symmetry broken bright, dark and
+and Lakshmanan, M.: On symmetry preserving and symmetry broken bright, dark and
 antidark soliton solutions of nonlocal nonlinear {S}chr\"{o}dinger
-equation}, Phys. Lett. A} {\bf 383} (2019), 15--26, DOI 10.1016/j.physleta.2018.10.011, \url{https://doi.org/10.1016/j.physleta.2018.10.011}.
+equation, \emph{Phys. Lett. A} {\bf 383} (2019), 15--26, DOI 10.1016/j.physleta.2018.10.011, \url{https://doi.org/10.1016/j.physleta.2018.10.011}.
 \end{enumerate}
+
+\subsection{List of Visitors to the Department}
+
+\begin{enumerate}
+\item Dr.R.
+Venkatesh, (a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases $G = E_6,7,8$ and $F_4$ and thus completed the main theorem of the paper of V.
+Chari and et al., (J.
+Algebra, 2016).
+Obtained a new combinatorial proof for the key fact that was used in  V.
+Chari and et al., (J.
+Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules.
+This key fact was proved by V.
+Chari and et al., (J.
+Algebra, 2016) only for the cases when G is the classical types and $G_2$ and they did a case-by-case analysis to prove this.
+Our new proof is very uniform and avoids the case-by-case analysis and works in general.
+(b) Simplified the presentation of all affine Demazure modules of untwisted affine Kac–Moody Lie algebras.
+Simplifying the generators and relations of these modules is very crucial in their study.
+We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.
+(c) A number of conjectures made about the graded characters affine Demazure modules of affine $sl_3$ using data obtained from SAGE. , --
+\item Dr.Govindan Rangarajan, We constructed [1] symmetry preserving and symmetry broken N-bright, dark and antidark soliton solutions of a nonlocal nonlinear Schrödinger equation.
+To obtain these solutions, we used appropriate eigenfunctions in Darboux transformation (DT) method.
+Further, we derived two dark/antidark soliton solution with the help of DT method.
+In the dark/antidark soliton solution case we observed a contrasting behaviour between the envelope of the ﬁeld and parity transformed complex conjugate envelope of the ﬁeld.
+For a particular parametric choice, we got dark (antidark) soliton for the ﬁeld while the parity transformed complex conjugate ﬁeld exhibits antidark (dark) soliton.
+Due to this surprising result, both the ﬁeld and PT transformed complex conjugate ﬁeld exhibit sixteen different combinations of collision scenario.
+We presented observational evidence [2] from studies on primary cortical cultures from AD transgenic mice for significant decrease in total spine density at DIV-15 and onward.
+This indicates reduction in potential healthy synapses and strength of connections among neurons.
+Based on this, a network model of neurons was developed, that explains the consequent loss of coordinated activity and transmission efficiency among neurons that manifests over time.
+The critical time when structural connectivity in the brain undergoes a phase-transition, from initial robustness to irreparable breakdown, is estimated from this model.
+We also showed how the global efficiency of signal transmission in the network decreases over time.
+Moreover, the number of multiple paths of high efficiency decreased rapidly as the disease progresses, indicating loss of structural plasticity and inefficiency in choosing alternate paths or desired paths for any pattern of activity.
+Thus loss of spines caused by β-Amyloid (Aβ) peptide results in disintegration of the neuronal network over time with consequent cognitive dysfunctions in Alzheimer’s Disease (AD).
+We investigated [3] the effect of four-wave mixing in the interactions among nonlinear waves such as solitons, breathers, and rogue waves of a coupled generalized nonlinear Schrodinger equation.
+We explored several interesting results including superposition of breather pulses, increment in the number of breather pulses and in amplitudes of breathers, and rogue waves.
+By strengthening the four-wave mixing parameter, we observed different transformations that occur between different localized structures.
+For instance, we visualized a transformation from bright soliton to breather form, bright and dark rogue wave to four-petaled rogue wave structures, four-petaled rogue wave to other rogue wave forms, and so on.
+Another important observation was that the interaction of a bright soliton with a rogue wave in the presence of the four-wave mixing effect provides interaction between a dark oscillatory soliton and a rogue wave.
+[1] Vishnu Priya, N., Senthilvelan, M.,  Rangarajan, G.
+& Lakshmanan, M.
+On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation, Physics Letters A, 383, 15 (2019).
+[2] Kashyap, G.
+A.
+R.
+S.
+R.
+K., Bapat, D., Das, D., Gowaikar, R.
+D., Amritkar, R.
+E., Rangarajan, G., Ravindranath, V.
+& Ambika, G., Synapse loss and progress of Alzheimer’s disease - A network model, Scientific Reports, 9, 6555 (2019).
+[3] Vishnu Priya, N., Senthilvelan, M.
+&  Rangarajan, G, On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, Chaos, 29, 123135 (2019)., On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation--Published
+\item Dr.Ved Datar, In collaboration with Vamsi Pingali [1],  a numerical criteria for the existence of solutions to generalised Monge-Ampere equations is obtained  on projective manifolds.
+The class of equations studied encompasses certain well known equations such as the $J$-equation and the inverse Hessian equations.
+In particular, this extends and strengthens the deep result of Gao Chen on the $J$-equation, and also resolves a well-known conjecture of Gabor Szekelyhidi.
+In a collaboration with Xin Fu and Jian Song [2], Kahler-Einstein metrics were constructed in the neighbourhoods of isolated log-canonical singularities, and the asymptotics to certain local models were studied.
+This builds on a program initiated by Kobayashi and others.
+In a joint project with Harish Seshadri, a conjecture on the almost rigidity of the complex projective space has been formulated, and is being studied.
+If solved, this would be a Kahler analog of a famous theorem of Tobias Colding on the almost rigidity of the sphere.
+While some preliminary results have been obtained, this is still work in progress.
+[1] (with Vamsi Pingali) A numerical criterion for generalised Monge-Ampere equations on projective manifolds, arXiv:2006.01530 [2] (with Xin Fu and Jian Song) On the Kahler-Einstein metric near isolated log-canonical singularity,  in  preparation, Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces--Accepted for publication
+\item Dr.Vamsi Pritham Pingali, My research during this period involved proving existence results for geometric PDE conditioned on some necessary and sufficient conditions.
+In [1], the dHYM equation on three-folds was studied, and in [2] we proved an existence result for the gravitating vortex equation conditioned on a GIT stability condition.
+In addition, some earlier works [3],[4],[5],[6] were accepted/published during this period.
+[1] Pingali, Vamsi Pritham.
+"The deformed Hermitian Yang-Mills equation on three-folds." arXiv preprint arXiv:1910.01870 (2019).
+[2] Garcia-Fernandez, Mario, Vamsi Pritham Pingali, and Chengjian Yao.
+"Gravitating vortices with positive curvature." arXiv preprint arXiv:1911.09616 (2019).
+[3] PINGALI, V., & VAROLIN, D.
+(2019).
+NONUNIFORMLY FLAT AFFINE ALGEBRAIC HYPERSURFACES.
+Nagoya Mathematical Journal, 1-43.
+doi:10.1017/nmj.2019.2 (Published online on 2 April  2019) [4] Pingali, Vamsi Pritham.
+"A vector bundle version of the Monge-Ampère equation." Advances in Mathematics 360 (2020): 106921.
+(Published online on 22 January 2020) [5] Álvarez-Cónsul, Luis, Mario Garcia-Fernandez, Oscar García-Prada, and Vamsi Pritham Pingali.
+"Gravitating vortices and the Einstein–Bogomol’nyi equations." Mathematische Annalen (2020): 1-34.
+(Published online on 20 February 2020) [6] Pingali, Vamsi Pritham.
+"Quillen metrics and perturbed equations." Letters in Mathematical Physics (2020): 1-15.
+(Published online on 5 March 2020), The deformed Hermitian Yang-Mills equation on three-folds--Preprint
+\item Dr.Basudeb Datta, A semi-regular tiling of the hyperbolic plane is a tessellation by regular geodesic polygons with the property that each vertex has the same vertex-type.
+Determined combinatorial criteria for the existence, and uniqueness, of a semi-regular tiling with a given vertex-type \ref{bdsg_2019} ., Semi-regular tilings of the hyperbolic plane \label{bdsg_2019}--Accepted for publication
+\item Dr.E K Narayanan, Positivity properties and asymptotics of Heckman-Opdam hypergeometric functions associated to root system to type BC with non-positive multiplicity functions were studied in detail., --
+\item Dr.Soumya Das, Work on the determination of Siegel modular forms by their fundamental Fourier coefficients was done including a mod p version.
+Study of Fourier coefficients and sup-norms of modular forms was continued., --
+\item Dr.Dilip P.
+Patil, COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS (Jointly Martin  Kreuzer)   The Burnside ring B(G) of a finite group G, a classical tool in the representation theory of finite groups, is studied from the point of view of computational algebra.
+In the rst part (cf.
+[8]) we examined the ring theoretic properties of B(G) using the methods of computer algebra.
+In this part we shift our focus to important maps between two Burnside rings and make several well-known maps of representation theory explicitly computable.
+The inputs of all our algorithms are the tables of marks of the two groups, and the outputs are matrices of integers representing the maps via their image in the ghost ring.
+All algorithms have been implemented in the computer algebra system ApCoCoA and are illustrated by applying them to explicit examples.
+Especially, we study the restriction and induction maps, the projection and in ation maps, the conjugation isomorphism, and the Frobenius-Wielandt homomorphism., COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS--Accepted for publication
+\item Dr.A.
+K.
+Nandakumaran, The main theme of the research is to understand the asymptotic analysis of  PDE problems and related optimal control problems in some complex domains.
+We consider domains whose boundary is rapidly oscillating which  leads to multi-scales in the problem.
+One of the major issue is the development of the so called unfolding operators which contains information about both scales.
+We have ingeniously used the unfolding operators not only to carry out the limiting behaviour of the problem under study, it is used to characterize the optimal controls.
+One needs to construct suitable such operators according to the type of domain and the problem [1], [3-5].
+On a completely different direction, a multi-step Volterra integral equation-based algorithm was developed to measure the electric field auto-correlation function from multi-exposure speckle contrast data.
+This enabled us to derive an estimate of the full diffuse correlation spectroscopy data-type from a low-cost, camera-based system.
+This method is equally applicable for both single and multiple scattering field auto-correlation models.
+The feasibility of the system and method was verified using simulation studies, tissue mimicking phantoms and subsequently in in vivo experiments [2]., Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure--Published
+\item Dr.Gautam Bharali, A detailed investigation of the Bergman geometry of domains whose boundaries have isolated infinite-type points was completed.
+Optimal estimates, from above and below, for the growth of the Bergman kernel (on the diagonal) and the Bergman metric, as one approaches an infinite-type boundary point, were obtained.
+The class of domains that were studied subsumes all classes of domains that have previously been considered in the literature.
+These results have appeared in the paper [1].
+[1] Bharali, Gautam, On the growth of the Bergman metric near a point of infinite type, J.
+Geom.
+Anal.
+, 30 (2020), 1238-1258., A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems--Accepted for publication
+\item Dr.SANCHAYAN SEN, In [1], we provide an explicit algorithm for sampling a uniform simple connected random graph with a given degree sequence.
+By products of this central result includes scaling limits for the metric space structure of the maximal components in the critical regime of both the configuration model and the uniform simple random graph model with prescribed degree sequence under finite third moment assumption on the degree sequence.
+As a substantive application we answer a question raised by Černý and Teixeira, Random Structures Algorithms (2013), by obtaining the metric space scaling limit of maximal components in the vacant set left by random walks on random regular graphs.
+In [2], we study limits of the largest connected components (viewed as metric spaces) obtained by critical percolation on uniformly chosen graphs and configuration models with heavy-tailed degrees.
+We develop general principles under which the scaling limits can be obtained.
+Of independent interest, we derive refined asymptotics for various susceptibility functions and the maximal diameter in the barely subcritical regime.
+In [3], we give alternate constructions of (i) the scaling limit of the uniform connected graphs with given fixed surplus, and (ii) the continuum random unicellular map of a given genus that start with a suitably tilted Brownian continuum random tree and make `horizontal' point identifications, at random heights, using the local time measures.
+In particular, this yields a breadth-first construction of the scaling limit of the critical Erdős-Rényi random graph which answers a question posed by Addario-Berry, Broutin, and Goldschmidt, Probab.
+Theory Related Fields (2012).
+As a consequence of this breadth-first construction we obtain descriptions of the radii, the distance profiles, and the two point functions of these spaces in terms of functionals of tilted Brownian excursions.
+[1] Geometry of the vacant set left by random walk on random graphs, Wright's constants, and critical random graphs with prescribed degrees Authors: Shankar Bhamidi, Sanchayan Sen Journal: Random Structures & Algorithms (First published on 25 July 2019)  [2] Universality for critical heavy-tailed network models: Metric structure of maximal components Authors: Shankar Bhamidi, Souvik Dhara, Remco van der Hofstad, Sanchayan Sen Journal: Electronic Journal of Probability (Accepted in December 2019)  [3] On breadth-first constructions of scaling limits of random graphs and random unicellular maps Authors: Grégory Miermont, Sanchayan Sen ArXiv preprint https://arxiv.org/abs/1908.04403 (Announced in August 2019), On breadth-first constructions of scaling limits of random graphs and random unicellular maps--Submitted
+\item Dr.Arvind Ayyer, In joint work with Aas, Linusson and Potka [1], the exact phase diagram for a semipermeable TASEP with nonlocal boundary jumps was obtained.
+In joint work with Behrend [2], new factorization theorems for classical group characters were proved.
+Applications to alternating sign matrices and plane partitions were given.
+In joint work with Finn and Roy [3], the phase diagram for a multispecies left-permeable asymmetric exclusion process was derived.
+In joint work with Linusson [4], a new class of reverse juggling processes was defined and their stationary distributions were computed., Total Variation Cutoff for the Transpose Top-2 with Random Shuffle--Accepted for publication
+\item Dr.Subhojoy Gupta, (1) With Mahan Mj (TIFR)  we completed a  research program concerning meromorphic projective structures on surfaces and their monodromy representations.
+We used new  work of Allegretti-Bridgeland, together with older ideas of Thurston, to develop a geometric understanding of these structures on punctured surfaces, and prove analogues of results of Hejhal and Gallo-Kapovich-Marden -- see [1] and [2].
+In an independent paper [3], I used our the techniques we had developed, to shed light on a remark of Poincaré in 1883.
+This complemented other projects concerning meromorphic quadratic differentials (see [8] and [10]).
+(2) In joint work [4] with Indranil Biswas (TIFR), Mahan Mj (TIFR) and Junho Whang (MIT), we classified the finite mapping class group orbits in the PSL(2,C) character variety.
+(3) In a project with Basudeb Datta (IISc) we revised and published a paper [5] developing an algorithmic technique of constructing semi-regular tilings of the hyperbolic plane.
+We expect this to have an impact on tilings-related research, which is an active area that has an intersection with several fields like combinatorics, computational geometry and group theory.
+(4)  With Harish Seshadri (IISc) we wrote a paper [6], and a survey [7], concerning the complex geometry of Teichmüller spaces, where we investigated the convexity (or lack thereof) of the boundary of complex domains biholomorphic to Teichmüller space.
+We have ongoing conversations regarding other questions that lie at the intersection of several complex variables, differential geometry and Teichmüller theory.
+(5) A paper with Indranil Biswas (TIFR) and Sorin Dumitrescu (UCA)  concerning branched projective structures on surfaces was published [9].
+In an ongoing project, we aim to understand the symplectic geometry of the space of such structures better.
+[1] Meromorphic projective structures, grafting and the monodromy map, submitted, available at http://arxiv.org/abs/1904.03804.
+[2] Monodromy representations of meromorphic projective structures, Proc.
+Amer.
+Math.
+Soc.
+148 (2020), no.
+5, 2069–2078.
+[3] Monodromy groups of CP1-structures on punctured surfaces, submitted, available at https: //arxiv.org/abs/1909.10771.
+[4] Surface group representations in SL(2,C) with finite mapping class orbits, submitted, available at https://arxiv.org/ abs/1707.00071.
+[5] Semi-regular tilings of the hyperbolic plane, to appear, Discrete and Computational Geometry (2019), available at https://doi.org/10.1007/s00454-019-00156-0.
+[6] On domains biholomorphic to Teichmüller spaces, International Mathematics Research Notices, Volume 2020, Issue 8, (2020), 2542–2560.
+[7] Complex geometry of Teichmüller domains, Handbook of Teichmüller theory Vol VII, 63–88, IRMA Lect.
+Math.
+Theor.
+Phys., 30, Eur.
+Math.
+Soc., Zürich, 2020.
+[8] Holomorphic quadratic differentials in Teichmüller theory, Handbook of Teichmü ller theory Vol VII, 2020.
+[9] Branched projective structures on a Riemann surface and logarithmic connections, Documenta Mathematica 24 (2019), 2299–2337.
+[10] Limits of harmonic maps and crowned hyperbolic surfaces, Trans.
+Amer.
+Math.
+Soc.
+372 (2019), no.
+11, 7573–7596., Meromorphic projective structures, grafting and the monodromy map--Preprint
+\item Dr.Mahesh Kakde, Jointly with Samit Dasgupta from Duke University I resolved the Brumer-Stark conjecture during the said period.
+We spoke about it at the "International Colloquium" in January 2020 in TIFR.
+Further, a paper on higher Chern classes written a while ago (jointly with Frauke Bleher, Ted Chinburg,  Ralph Greenberg, George Pappas, Romyar Sharifi and Martin Taylor) was accepted for publication in American Journal of Mathematics., Higher Chern Classes in Iwasawa Theory--Published
+\item Dr.RADHIKA GANAPATHY, 1) Let $G$ be a split connected reductive group over $\mathbb{Z}$.
+Let $F$ be a non-archimedean local field.
+With $K_m := Ker(G(O_F ) → G(O_F /p_{m,F} ))$, Kazhdan proved that for a field $F′$ sufficiently close to $F$, the Hecke algebras $\mathcal{H}(G(F), K_m)$ and $\mathcal{H}(G(F′), K_m′ )$ are isomorphic, where $K_m′$ denotes the corresponding object over $F′$.
+I have generalized this result to general connected reductive groups [1].
+2) In my earlier work, I had established  a variant of the Kazhdan isomorphism for split reductive groups (by replacing $K_m$ replaced by the $m$-th filtration subgroup of the Iwahori subgroup).
+I have been working on generalising this result to general connected reductive groups.
+As part of this work, I have chosen a nice set of representatives in $G(F)$ for the elements of the extended affine Weyl group.
+This set of representatives has some very interesting properties (for instance, it is compatible with unramified descent), and is useful in the study of representation theory of $p$-adic groups.
+[1] A Hecke algebra isomorphism over close local fields, preprint, 12 pages., A Hecke algebra isomorphism over close local fields--Preprint
+\item Dr.Manjunath Krishnapur, Completed a study of law of iterated logarithm for last passage percolating on the two dimensional integer lattice [1].
+Other studies on absolute continuity of limiting spectral distributions, a proof of KMT theorems, study of discrete nodal length, a problem on amplitude constrained Gaussian channel and some problems on nodal domains of random functions are in various stages of completion.
+[1] Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation.
+Authors: Riddhipratim Basu, Shirshendu Ganguly, Milind Hegde, Manjunath Krishnapur.
+arXiv:1909.01333, Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation--Accepted for publication
+\item Dr.Sundaram Thangavelu, In a joint work with Pritam Ganguly  we have investigated the $ L^p $  boundedness of the lacunary maximal function $ M_{\H^n}^\lac $ associated to the spherical means $ A_r f$  taken over Koranyi spheres on the Heisenberg group.
+Closely following an approach used by M.
+Lacey in the Euclidean case, we obtain sparse bounds for these maximal functions leading to new unweighted and weighted estimates.
+The key ingredients in the proof are the $L^p$  improving property of the operator $ A_r $  and a continuity property of the difference $ A_r f−\tau_y A_r f,$ where $\tau_yf(x)=f(xy−1) $ is the right translation operator., On lacunary spherical maximal function on Heisenberg groups--Preprint
+\item Dr.R VENKATESH, (a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases $G = E_6,7,8$ and $F_4$ and thus completed the main theorems of the papers of V.
+Chari and et al., (J.
+Algebra, 2016) and Deniz Kus and et al., (Represent.
+Theory., 2016).
+Obtained a new combinatorial proof for the key fact that was used in  V.
+Chari and et al., (J.
+Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules.
+This key fact was proved only for the cases when G is the classical type and $G_2$ in their paper and they also proved it by analysing case-by-case.
+Our proof is uniform avoids the case-by-case analysis and works for all finite-dimensional simple Lie algebras.
+(b) Simplified the presentation of all affine Demazure modules of untwisted affine Kac–Moody Lie algebras.
+Simplifying the generators and relations of these modules is very crucial in their study.
+We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.
+(c) A number of conjectures made about the graded characters affine Demazure modules of affine $sl_3$ using data obtained from SAGE. , --
+\item Dr.Apoorva Khare, (1) I extended a fundamental matrix inequality, the Schur Product Theorem, for positive definite matrices, by providing nonzero, tight lower bounds.
+(2) I improved and updated several preprints - notably, a comprehensive work titled "Moment-sequence transforms" with Belton-Guillot-Putinar., Probability inequalities and tail estimates for metric semigroups--Published
+\item Dr.Siddhartha Gadgil, We continued our development of automated theorem proving systems.
+Specifically, we developed a framework based on equation terms to allow accumulation of knowledge and facilitate deep learning and hybrid autonomous/interactive execution., --
+\item Dr.Tirthankar Bhattacharyya, 1.
+Distinguished varieties:  A distinguished algebraic variety in $\mathbb{C}^2$ has been the focus of much research in recent years because of good reasons.
+We have given a different perspective.
+\begin{enumerate}  \item We have found a new characterization of an algebraic variety $\mathcal W$ which is distinguished with respect to the bidisc.
+It is in terms of the joint spectrum of a pair of commuting linear matrix pencils.
+\item There is a characterization known of $\mathbb{D}^2\cap\mathcal{W}$ due to a seminal work of Agler and McCarthy.
+We have shown that Agler--McCarthy characterization can be obtained from the new one and vice versa.
+\item En route, we develop a new realization formula for operator-valued contractive analytic functions on the unit disc.
+\item There is a one-to-one correspondence between operator-valued contractive holomorphic functions and {\em canonical model triples}.
+This pertains to the new realization formula mentioned above.
+\item Pal and Shalit gave a characterization of an algebraic variety, which is distinguished with respect to the symmetrized bidisc, in terms of a matrix of numerical radius no larger than $1$.
+We refine their result by making the class of matrices strictly smaller.
+\item In a generalization in the direction of more than two variables, we have characterized all one-dimensional algebraic  varieties which are distinguished  with respect to the polydisc.
+\end{enumerate} At the root of our work is the Berger--Coburn--Lebow theorem characterizing a commuting tuple of isometries.
+This work is in [1].
+2.
+We have studied the action of the automorphism group of the $2$ complex dimensional manifold symmetrized bidisc $\mathbb G$ on itself.
+The automorphism group is $3$ real dimensional.
+It foliates $\mathbb G$ into leaves all of which are $3$ real dimensional hypersurfaces except one, viz., the royal variety.
+This leads us to investigate Isaev's classification of all Kobayashi-hyperbolic $2$ complex dimensional  manifolds for which the group of holomorphic automorphisms has real dimension $3$ studied by Isaev.
+Indeed, we produce a biholomorphism between the symmetrized bidisc and the domain  \[\{(z_1,z_2)\in \mathbb{C} ^2 : 1+|z_1|^2-|z_2|^2>|1+ z_1 ^2 -z_2 ^2|, Im(z_1 (1+\overline{z_2}))>0\}\]  in Isaev's list.
+Isaev calls it $\mathcal D_1$.
+The road to the biholomorphism is paved with various geometric insights about $\mathbb G$.
+Several consequences of the biholomorphism follow including two new characterizations of the symmetrized bidisc and several new characterizations of $\mathcal D_1$.
+Among the results on $\mathcal D_1$, of particular interest is the fact that $\mathcal D_1$ is a ``symmetrization''.
+When we symmetrize (appropriately defined in this context) either $\Omega_1$ or $\mathcal{D}^{(2)} _1$ (Isaev's notation), we get $\mathcal D_1$.
+These two domains $\Omega_1$ and $\mathcal{D}^{(2)} _1$ are in Isaev's list and he mentioned that these are biholomorphic to $\mathbb D \times \mathbb D$.
+We produce explicit biholomorphisms between these domains and $\mathbb D \times \mathbb D$.
+This work is in [2].
+[1]  Distinguished Varieties Through the Berger--Coburn--Lebow Theorem,  co-authored with P.
+Kumar and H.
+Sau.
+Submitted to journal and arXiv link is https://arxiv.org/pdf/2001.01410.pdf   [2] An unbounded realization of the symmetrized bidisc, co-authored with A.
+Biswas and A.
+Maitra.
+Submitted to journal and arXiv link is  https://arxiv.org/pdf/2005.00289.pdf, On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel--Published
+\item Dr.Purvi Gupta, Note: this description is for research carried out during the period February 11, 2020 (date of joining) to March 31, 2020.
+In this period,  I completed and submitted a manuscript ([1]),  based on joint work with C.
+U.
+Wawrzyniak.
+This work studies the stability of the solution of the so-called global Bishop problem (a plateau-type problem) for a model real $n$-dimensional sphere in $\mathbb{C}^n$, $n\geq 2$.
+In this problem, the solution is required, among other things, to be foliated by holomorphic disks (i.e., Levi-flat) attached to the given sphere.
+This structure is significant in complex analysis for multiple reasons.
+The general Bishop problem, although very well-understood in two (complex) dimensions, is wide open in dimensions three and higher, and our work is the first global result in this direction.
+References [1] Gupta, Purvi and Wawrzyniak, Chloe Urbanski, Stability of the hull(s) of an $n$-sphere in $\mathbb{C}^n$.
+Submitted., STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$--Submitted
+\item Dr.Kaushal Verma, For a given pair of smoothly bounded planar domains $D_1, D_2$, it was shown in \cite{1} that the product of the Carath\'{e}odory metrics on them is bounded from below by the product of the Carath\'{e}odory metrics on their union and intersection up to a multiplicative factor.
+This shows that the S\"{z}ego kernels on $D_1, D_2, D_1 \cap D_2$ and $D_1 \cup D_2$ are related by the same inequality.
+The Suita conjecture in higher dimensions is a paradigm that asks for the limiting boundary values of the product of the Bergman kernel (on the diagonal) and the volume of the Kobayashi indicatrix.
+This object is a biholomorphic invariant and is known to admit universal bounds on convex domains.
+Its limiting behaviour was clarified on strongly peudoconvex domains and egg domains in $\mathbb C^2$.
+See \cite{2}.
+The boundary behaviour of several classical conformal invariants were studied in \cite{3}.
+The relationship between the Fridman invariant and the Squeezing function was clarified in \cite{4}.
+The relation between a pair of H\'{e}non maps that share the same forward and backward Julia sets was clarified in \cite{5}., A submultiplicative property of the Carath\'{e}odory metric on planar domains--Published
+\item Dr.Srikanth Krishnan Iyer, We study combinatorial connectivity for two models of random geometric complexes.
+These two models - \v{C}ech and Vietoris-Rips complexes - are built on a homogeneous Poisson point process of intensity $n$ on a $d$-dimensional torus, $d > 1$, using balls of radius $r_n$.
+Given a (simplicial) complex (i.e., a collection of $k$-simplices for all $k \geq 1$), we can connect $k$-simplices via $(k+1)$-simplices (`up-connectivity') or via $(k-1)$-simplices (`down-connectivity).
+Our interest is to understand these two combinatorial notions of connectivity for the random \v{C}ech and Vietoris-Rips complexes asymptotically as $n \to \infty$.
+Our results give tighter bounds on the constants in the logarithmic scale as well as shed light on the possible second-order correction factors.
+Further, they also reveal interesting differences between the phase transition in the \v{C}ech and Vietoris-Rips cases.
+The analysis is interesting due to non-monotonicity of the number of isolated $k$-faces (as a function of the radius) and leads one to consider `monotonic' vanishing of isolated $k$-faces.
+The latter coincides with the vanishing threshold mentioned above at a coarse scale (i.e., $\log n$ scale) but differs in the $\log \log n$ scale for the \v{C}ech complex with $k = 1$ in the up-connected case.
+For the case of up-connectivity in the Vietoris-Rips complex and for $r_n$ in the critical window, we also show a Poisson convergence for the number of isolated $k$-faces when $k \leq d$.
+[1], Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes--Published
+\item Dr.Thirupathi Gudi, We have developed a Hybrid High Order methods for elliptic obstacle problem in both two and three space dimensions allowing general meshes.
+The gap in literature of developing an optimal order convergent method using quadratic finite element method is resolved under the realistic regularity.
+In another work, we derived optimal order finite element analysis for constrained Dirichlet boundary optimal control problem.
+We have also studied numerous finite element methods for parabolic obstacle problem under the realistic regularity., Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem--Accepted for publication
+\item Dr.Hrish Seshadri, , Professor--
+\item Dr.Mrinal Kanti Ghosh, Risk-sensitive stochastic differential games have been studied in the nonnegative orthant [1] and the whole space [2].
+Existence of saddle point/Nash equilibria for relevant cases have been derived., Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant--Accepted for publication
+\item Dr.Gadadhar Misra, There is a one to one correspondence between holomorphic imprimitivities and the holomomorphic hermitian homogeneous vector bundles on a bounded symmetric domain D.
+The homogeneous bundles can be obtained by holomorphic induction from representations of a certain parabolic Lie algebra on finite dimensional inner product spaces.
+The representations, and the induced bundles, have composition series with irreducible factors.
+In joint work with A.
+Koranyi, our first main result is the construction of an explicit differential operator intertwining the bundle with the direct sum of its factors.
+Next, we study Hilbert spaces of sections of these bundles.
+We use this to get, in particular, a full description and a similarity theorem for homogeneous n-tuples of operators in the Cowen-Douglas class of the Euclidean unit ball.
+Beurling’s theorem shows that all submodules of the Hardy module are isomorphic leading to the question of rigidity of submodules in multi-variate operator theory.
+The submodules of analytic Hilbert modules defined over certain algebraic varieties in bounded symmetric domains, the so-called Jordan-Kepler varieties X of arbitrary rank r have been studied.
+For r > 1, the singular set of X is not a complete intersection.
+Hence the usual monoidal transformations do not suffice for the resolution of the singularities.
+Instead (joint with Upmeier), we describe a new higher rank version of the blow-up process, defined in terms of Jordan algebraic determinants, and apply this resolution to obtain the rigidity of the sub-modules vanishing on the singular set.
+(with Koranyi) Homogeneous Hermitian holomorphic vector bundles and the Cowen-Douglas class over bounded symmetric domains, Adv.
+Math., 351 (2019), 1105 - 1138.
+(with Upmeier)  Singular Hilbert modules on Jordan-Kepler varieties, To appear, Proceedings of IWOTA 2018, in memory of R.
+G.
+Douglas., Professor--Published
+\item Dr.Abhishek Banerjee, , Cohomology of modules over H-categories and co-H-categories--Accepted for publication
+\end{enumerate}

### 2020-08-07 data/draft-sections.tex
clean generation
code for visitors, generating

@@
   \item[Grant\,:] 19.316 Lakhs
+\end{description}
+
+\item {\bf Abhishek Banerjee\,:} Sole investigator in a SERB project
+\begin{description}
+  \item[Project Title\,:] MATRICS Grant : MTR/2017/000112("Algebraic Geometry over symmetric monoidal categories and tensor triangular geometry")
+  \item[Duration\,:] 2018-2021
+  \item[Grant\,:] Rs 6.6 lakh
 \end{description}
@@
   \item[Grant\,:] Six lakhs
+\end{description}
+
+\item {\bf Gadadhar Misra\,:} Sole investigator in a SERB project
+\begin{description}
+  \item[Project Title\,:] The role of curvature in Operator Theory
+  \item[Duration\,:] 2018 - 2021
+  \item[Grant\,:] 660000
+\end{description}
+
+\item {\bf Gadadhar Misra\,:} Sole investigator in a SERB project
+\begin{description}
+  \item[Project Title\,:] J C Bose Fellowship
+  \item[Duration\,:] 2018 - 2021
+  \item[Grant\,:] 
 \end{description}
@@
 
-\item {\bf SANCHAYAN SEN\,:} Sole investigator in a Science & Engineering Research Board (SERB) project
+\item {\bf SANCHAYAN SEN\,:} Sole investigator in a Science \& Engineering Research Board (SERB) project
 \begin{description}
@@
 
-\begin{enumerate}
-
-\end{enumerate}
-
 \subsection{Editorial boards}
@@
 \item Dilip P. Patil was Taught  (12 Week long)  NPTEL Course during Jan-April 2020
+\item Gadadhar Misra was Convener, Symposium: Mathematics and Society, INSA Anniversary Conference, Dec 2019
 \item Gautam Bharali was Member of the Faculty Selection Committee at IIIT Guwahati in June 2018
@@
 \item Arvind Ayyer was Thesis examiner for Mr. Sudip Bera, Visva-Bharati University.
+\item Gadadhar Misra was Member, Scientific Committee, Hilbert Modules in Analytic Function Spaces workshop,     Tsinghua Sanya International Mathematics Forum (TSIMF), Sanya, China, Dec 30, 2019 - Jan 3, 2020
 \item Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)

### 2020-08-07 data/reports.tex
code for visitors, generating

@@
 The feasibility of the system and method was verified using simulation studies, tissue mimicking phantoms and subsequently in in vivo experiments [2].
+
+\subsection{Abhishek Banerjee}
 
@@
 Positivity properties and asymptotics of Heckman-Opdam hypergeometric functions associated to root system to type BC with non-positive multiplicity functions were studied in detail.
+
+\subsection{Gadadhar Misra}
+
+There is a one to one correspondence between holomorphic imprimitivities and the holomomorphic hermitian homogeneous vector bundles on a bounded symmetric domain D.
+The homogeneous bundles can be obtained by holomorphic induction from representations of a certain parabolic Lie algebra on finite dimensional inner product spaces.
+The representations, and the induced bundles, have composition series with irreducible factors.
+In joint work with A.
+Koranyi, our first main result is the construction of an explicit differential operator intertwining the bundle with the direct sum of its factors.
+Next, we study Hilbert spaces of sections of these bundles.
+We use this to get, in particular, a full description and a similarity theorem for homogeneous n-tuples of operators in the Cowen-Douglas class of the Euclidean unit ball.
+Beurling’s theorem shows that all submodules of the Hardy module are isomorphic leading to the question of rigidity of submodules in multi-variate operator theory.
+The submodules of analytic Hilbert modules defined over certain algebraic varieties in bounded symmetric domains, the so-called Jordan-Kepler varieties X of arbitrary rank r have been studied.
+For r > 1, the singular set of X is not a complete intersection.
+Hence the usual monoidal transformations do not suffice for the resolution of the singularities.
+Instead (joint with Upmeier), we describe a new higher rank version of the blow-up process, defined in terms of Jordan algebraic determinants, and apply this resolution to obtain the rigidity of the sub-modules vanishing on the singular set.
+(with Koranyi) Homogeneous Hermitian holomorphic vector bundles and the Cowen-Douglas class over bounded symmetric domains, Adv.
+Math., 351 (2019), 1105 - 1138.
+(with Upmeier)  Singular Hilbert modules on Jordan-Kepler varieties, To appear, Proceedings of IWOTA 2018, in memory of R.
+G.
+Douglas.
 
@@
 
-(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases G = E_6,7,8 and F_4 and thus completed the main theorems of the papers of V.
+(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases $G = E_6,7,8$ and $F_4$ and thus completed the main theorems of the papers of V.
 Chari and et al., (J.
@@
 Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules.
-This key fact was proved only for the cases when G is the classical type and G_2 in their paper and they also proved it by analysing case-by-case.
+This key fact was proved only for the cases when G is the classical type and $G_2$ in their paper and they also proved it by analysing case-by-case.
 Our proof is uniform avoids the case-by-case analysis and works for all finite-dimensional simple Lie algebras.
@@
 We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.
-(c) A number of conjectures made about the graded characters affine Demazure modules of affine sl_3 using data obtained from SAGE.
+(c) A number of conjectures made about the graded characters affine Demazure modules of affine $sl_3$ using data obtained from SAGE.
 
@@
 
-(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases G = E_6,7,8 and F_4 and thus completed the main theorem of the paper of V.
+(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases $G = E_6,7,8$ and $F_4$ and thus completed the main theorem of the paper of V.
 Chari and et al., (J.
@@
 Chari and et al., (J.
-Algebra, 2016) only for the cases when G is the classical types and G_2 and they did a case-by-case analysis to prove this.
+Algebra, 2016) only for the cases when G is the classical types and $G_2$ and they did a case-by-case analysis to prove this.
 Our new proof is very uniform and avoids the case-by-case analysis and works in general.
@@
 , 38 (2020), 138-147.
+
+\subsection{Dr. Abhitosh Upadhyay}
+
+\subsection{Anupam Gumber}
+
+I have been working as a NBHM-postdoctoral fellow at IISc Bangalore under the mentorship of  Prof.
+S.
+Thangavelu since March 28, 2019.
+During the period between April 01, 2019-March 31, 2020 at IISc, along with some research discussions with Prof.
+S.
+Thangavelu, I was also involved in working on research problems jointly with Prof.
+P.
+K.
+Ratnakumar (HRI Prayagraj, India), Prof.
+Joachim Toft (Linnaeus Univ., Sweden) and Prof.
+Hans G.
+Feichtinger (NuHAG Group Leader, Univ.
+Vienna, Austria).
+The questions considered require the interplay between harmonic analysis, time-frequency analysis and approximation theory.
+The following is a brief detailed report of my research work during the above mentioned period at IISc:   \begin{itemize} \item [(I)] {\large{\bf Translation and modulation invariant Hilbert spaces:}} In a joint work with Prof.
+Joachim Toft and other collaborators, we have investigated the translation and modulation invariant Hilbert spaces.
+In this regard, we have shown that any Hilbert space of distributions on $\mathbb{R}^d$ which is translation and modulation invariant, also in the sense of its norm, is equal to $L^2(\mathbb{R}^d)$, with the same norm apart from a multiplicative constant.
+The manuscript has been communicated to a journal.
+\item [(II)] {\large{\bf On Weyl multipliers and twisted modulation spaces:}} In a joint collaboration with Prof.
+P.
+K.
+Ratnakumar, we have studied the twisted modulation spaces and characterise the Weyl multipliers on them.
+The analysis also leads to the characterisation of multiplication operators on certain non-commutative amalgam spaces.
+The technical work relies on the harmonic analysis of special Hermite operator, also called the twisted Laplacian on $\mathbb{C}^n$.
+The manuscript is to be submitted soon.
+\item [(III)] {\large{\bf{Completeness of shifted dilates in invariant Banach spaces of distributions:}}} Jointly with Prof.
+Hans G.
+Feichtinger,  we  show that the well established methods from the theory of Banach modules and time-frequency analysis allow to derive completeness results for the collection of shifted and dilated version of a given (test) function in a quite general setting.
+While the basic ideas show strong similarity to the arguments used in a recent paper by V.
+Katsnelson [1], we extend his results in several directions, both relaxing the assumptions (instead of a Gauss function any function with non-vanishing integral can be used), and widening the range of applications considerably.
+There is no need for the Banach spaces considered to be embedded into $(L^2(\mathbb{R}), ||\cdot{}||_2 )$, nor is the Hilbert space structure relevant.
+We choose to present the results in the setting of the Euclidean spaces, because then the  space of tempered distributions $S^{\prime}(\mathbb{R}^d) (d \geq 1)$  provides a well-established environment for mathematical analysis.
+In addition, we establish connections to modulation spaces, and specifically to the Shubin classes $(Q_s(\mathbb{R}^d), ||\cdot{}||_{Q_s})$, by showing that they are indeed special cases of Katsnelson's setting.
+The technical work for the results involved is almost done.
+The final writing of the manuscript is in progress.
+\end{itemize}  References: [1] V.
+Katsnelson, On the completeness of Gaussians in a Hilbert functional space, {\em Complex Anal.
+Oper.
+Theory}, 13(3) (2019) 637-658.

### 2020-08-07 ugc/src/Data.scala

@@ -27,8 +27,15 @@ object Data {
     .lines(os.resource / "ugc2020.tsv")
     .toVector
     .tail
-    .map(_.split("\t").toVector.tail)
+    .map(_.split("\t").toVector.tail.map(_.trim))
     .map(pad(_))
+
+  lazy val visitorData = os.read
+    .lines(os.resource / "ugc2020.tsv")
+    .toVector
+    .tail
+    .map(_.split("\t").toVector.tail.map(_.trim))
+    .map(pad(_, 5))
 
   lazy val summerStudents = data.flatMap(
     l =>
@@ -41,7 +48,7 @@ object Data {
     .lines(os.resource / "ugc2020-postdocs.tsv")
     .toVector
     .tail
-    .map(_.split("\t").toVector.tail)
+    .map(_.split("\t").toVector.tail.map(_.trim))
     .map(pad(_, postDocSize))
 
   lazy val postDocTriple
@@ -167,6 +174,8 @@ ${enumString(other)}
   lazy val bookChapters = facultyData.flatMap(f => f.bookChapters.map(_.tex)) ++ postDocData
     .flatMap(f => f.bookChapters.map(_.tex))
 
+  lazy val visitors = visitorData.map(Visitor.get(_).tex)
+
   lazy val draftPubs =
     s"""
 \\subsection{Papers in Journals}
@@ -200,6 +209,10 @@ ${preprints.mkString("\n")}
 \\begin{enumerate}
 ${Publications.pubItems.mkString("\n")}
 \\end{enumerate}
+
+\\subsection{List of Visitors to the Department}
+
+${enumString(visitors)}
 """
 
   def writeReport() = os.write.over(os.pwd / "data" / "reports.tex", reports)
@@ -266,6 +279,19 @@ object Fellowship {
       .toVector
 }
 
+case class Visitor(
+  name: String,
+  affiliation: String,
+  from: String,
+  till: String
+){
+  val tex = s"\\item Dr.$name, $affiliation, $from--$till"
+}
+
+object Visitor{
+  def get(v: Vector[String]) = Visitor(v(0), v(1), v(3), v(4))
+}
+
 case class PostDocData(
     name: String,
     researchHighlights: String,
@@ -319,12 +345,12 @@ case class Paper(
   val tail = status match {
     case "Preprint"                 => "preprint"
     case "Submitted"                => "submitted for publication"
-    case "Accepted for publication" => s"to appear in $journal"
[…]

### 2020-08-07 ugc/src/Publications.scala

@@ -1,5 +1,6 @@
 package ugc
 import os.remove.all
+import Data.preComma
 
 object Publications {
   import org.jbibtex._
@@ -27,7 +28,7 @@ object Publications {
 
   def getString(y: YamlValue): String = y match {
     case YamlNumber(value)    => value.toString()
-    case YamlString(value)    => value
+    case YamlString(value)    => value.trim()
     case YamlBoolean(boolean) => boolean.toString()
     case _                    => ""
   }
@@ -50,7 +51,7 @@ object Publications {
     val urlOpt = m.get("url")
     val doiText = doiOpt.map(s =>s", DOI $s").getOrElse("")
     val urlText = urlOpt.map(s => s", \\url{$s}").getOrElse("")
-    s"\\item $author, {\\em $title}, $journal {\\bf $volume} ($year), $pages$doiText$urlText."
+    s"\\item $author: $title, \\emph{$journal} {\\bf $volume} ($year)${preComma(pages)}$doiText$urlText."
   }
 
   lazy val pubItems = allPubs.map(tex)

### 2020-08-10 data/draft-publications.tex
hyperlinks with title

--- 2020-08-05 data/draft-publications.tex
@@
 K.
-Nandakumaran and Abu Sufian, \emph{Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure},  Mathematical Methods in the Applied Sciences {\bf 42} (2019.
-DOI: 10.1002/mma.5748), 6407-6434 , DOI 10.1002/mma.5748.
+Nandakumaran and Abu Sufian: Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure, \emph{Mathematical Methods in the Applied Sciences} {\bf 42} (2019.
+DOI: 10.1002/mma.5748), 6407-6434.
 \item K.
@@
 K.
-Nandakumaran, Turgurt Durduran, Hari M Varma, \emph{Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements}, Biomedical Optics Express 5395 {\bf 10} (2019), .
+Nandakumaran, Turgurt Durduran, Hari M Varma: Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements, \emph{Biomedical Optics Express 5395} {\bf 10} (2019).
 \item S Aiyappan, A.
 K.
-Nandakumaran and Ravi Prakash, \emph{Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains}, Annali di Matematica Pura ed Applicata {\bf 198} (2019), 1931-1954, DOI 10.1007/s10231-019-00848-7.
-\item S Aiyappan, A.
-K.
-Nandakumaran and Ravi Prakash, \emph{Semi-linear optimal control problem on a smooth oscillating domain}, Communications in Contemporary Mathematics {\bf } (2019), 1-26, DOI 10.1142/S0219199719500299.
-\item S Aiyappan, Editha C.
-Jose, Ivy Carol B.
-Lomerio and A.
-K.
-Nandakumaran, \emph{ Control Problem on a Rough Circular Domain and Homogenization}, Asymptotic Analysis {\bf 115} (2019),  19-46, DOI 10.3233/ASY-191526.
-\item Khare, Apoorva and Rajaratnam, Bala, \emph{Probability inequalities and tail estimates for metric semigroups}, Advances in Operator Theory (Special issue in honor of Rajendra Bhatia) {\bf 5} (2020), 779-795, DOI 10.1007/s43036-020-00048-8, \url{https://link.springer.com/article/10.1007%2Fs43036-020-00048-8}.
-\item Ghosh, Subhajit, \emph{Total Variation Cutoff for the Transpose Top-2 with Random Shuffle}, to appear in Journal of Theoretical Probability, DOI 10.1007/s10959-019-00945-6, \url{https://link.springer.com/article/10.1007%2Fs10959-019-00945-6}.
-\item Datta, B.
-and Gupta, S., \emph{Semi-regular tilings of the hyperbolic plane \label{bdsg_2019} }, to appear in Discrete Comput Geom, DOI https://doi.org/10.1007/s00454-019-00156-0, \url{https://doi.org/10.1007/s00454-019-00156-0}.
-\item Datta, B. and Sarkar, S., \emph{Equilibrium triangulations of some quasitoric 4-manifolds}, Southeast Asian Bull. Math. {\bf 44} (2020), 57--78.
-\item Datta, B. and Maity, D., \emph{Correction to: Semi-equivelar and vertex-transitive maps on the torus}, Beitr Algebra Geom {\bf 61} (2020), 187--188.
+Nandakumaran and Ravi Prakash: Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains, \emph{Annali di Matematica Pura ed Applicata} {\bf 198} (2019), 1931-1954.
+\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash: Semi-linear optimal control problem on a smooth oscillating domain, \emph{Communications in Contemporary Mathematics} {\bf } (2019), 1-26.
+\item S Aiyappan, Editha C. Jose, Ivy Carol B. Lomerio and A. K. Nandakumaran: Control Problem on a Rough Circular Domain and Homogenization, \emph{Asymptotic Analysis} {\bf 115} (2019), 19-46.
+\item M. Balodi, A. Banerjee, S. Ray: Cohomology of modules over H-categories and co-H-categories, to appear in \emph{Canadian Journal of Mathematics}.
+\item M. Balodi, A. Banerjee, S. Ray: Entwined modules over linear categories and Galois extensions, to appear in \emph{Israel Journal of Mathematics (Accepted)}.
+\item A. Banerjee: On Noetherian schemes over $(\mathcal C,\otimes,1)$ and the category of quasi-coherent sheaves, to appear in \emph{Indiana University Mathematics Journal}.
+\item A. Banerjee: On differential torsion theories and rings with several objects, \emph{Canadian Math Bulletin} {\bf 62} (2019), 703--714.
+\item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric semigroups, \emph{Advances in Operator Theory (Special issue in honor of Rajendra Bhatia)} {\bf 5} (2020), 779-795.
+\item Ghosh, Subhajit: Total Variation Cutoff for the Transpose Top-2 with Random Shuffle, to appear in \emph{Journal of Theoretical Probability}.
+\item Datta, B. and Gupta, S.: Semi-regular tilings of the hyperbolic plane \label{bdsg_2019}, to appear in \emph{Discrete Comput Geom}.
+\item Datta, B. and Sarkar, S.: Equilibrium triangulations of some quasitoric 4-manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57--78.
+\item Datta, B. and Maity, D.: Correction to: Semi-equivelar and vertex-transitive maps on the torus, \emph{Beitr Algebra Geom} {\bf 61} (2020), 187--188.
 \item Martin Kreuzer and Dilip P.
-Patil , \emph{COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS}, to appear in Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry.
-\item Bharali, Gautam and Maitra, Anwoy, \emph{A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems}, to appear in Annali della Scuola Normale Superiore di Pisa, DOI 10.2422/2036-2145.201906_007, \url{http://annaliscienze.sns.it/index.php?page=ForthcomingArticles}.
-\item Maitra, Anwoy, \emph{On the continuous extension of Kobayashi isometries}, Proc.
-Amer.
-Math.
-Soc.
-{\bf 148} (2020), 3437--3451, \url{https://www.ams.org/journals/proc/2020-148-08/S0002-9939-2020-15038-1/}.
+Patil: COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS, to appear in \emph{Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry}.
+\item Gadadhar Misra: Professor, \emph{Adv. Math.} {\bf 351} (2019), 1105 - 1138.
+\item Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}.
+\item Maitra, Anwoy: On the continuous extension of Kobayashi isometries, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.
 \item Vishnu Priya, N.
@@
 and Ravindranath, V.
-and Ambika, G, \emph{Synapse loss and progress of Alzheimer’s disease - A network model}, Scientific Reports {\bf 9} (2019), 6555.
+and Ambika, G: Synapse loss and progress of Alzheimer’s disease - A network model, \emph{Scientific Reports} {\bf 9} (2019), 6555.
 \item Vishnu Priya, N.
 and Senthilvelan, M.
-and Rangarajan, G., \emph{On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation}, Chaos {\bf 29} (2019), 123135.
-\item Sarkar, Amar Deep and Verma, Kaushal, \emph{A submultiplicative property of the Carath\'{e}odory metric on planar domains}, Proc.
-Indian Acad.
-Sci.
-(Math.
-Sci.) {\bf } (), , \url{https://www.ias.ac.in/article/fulltext/pmsc/130/0035}.
-\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor, \emph{Higher Chern Classes in Iwasawa Theory}, American Journal of Mathematics {\bf 142} (2020), 627-682, \url{https://muse.jhu.edu/issue/42062}.
+and Rangarajan, G.: On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, \emph{Chaos} {\bf 29} (2019), 123135.
+\item Sarkar, Amar Deep and Verma, Kaushal: A submultiplicative property of the Carath\'{e}odory metric on planar domains, \emph{Proc. Indian Acad. Sci. (Math. Sci.)} {\bf } ().
+\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor: Higher Chern Classes in Iwasawa Theory, \emph{American Journal of Mathematics} {\bf 142} (2020), 627-682.
 \item Basu, R.
@@
 Ghosh and S.
-Pradhan, \emph{Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant}, to appear in ESIAM: Control, Optimization and Calculus of Variations , DOI Doi:10.105/cocv/2020029.
+Pradhan: Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant, to appear in \emph{ESIAM: Control, Optimization and Calculus of Variations}.
 \item M.
@@
 Pal and S.
-Pradhan, \emph{Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications}, to appear in Stochastic Analysis and Applications, DOI Doi: 10.1080/07362994.2020.1796707.
+Pradhan: Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications, to appear in \emph{Stochastic Analysis and Applications}.
 \item Iyer, S.
 K.
-and Yogeshwaran, D., \emph{Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes}, Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques {\bf 56} (2020), 1869-1897, \url{https://doi.org/10.1214/19-AIHP1020}.
-\item Datta, Basudeb and Gupta, Subhojoy, \emph{Semi-regular tilings of the hyperbolic plane}, to appear in Discrete and Computational Geometry, DOI https://doi.org/10.1007/s00454-019-00156-0.
+and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897.
+\item Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane, to appear in \emph{Discrete and Computational Geometry}.
 \item Thirupathi Gudi, Ramesh Ch.
-Sau, \emph{Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem}, to appear in ESAIM: Control, Optim.
+Sau: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim.
 Calc.
-Var, DOI doi: 10.1051/cocv/2019068..
-\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh, \emph{On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel},  Studia Math.
-{\bf 255} (2020), 83–107., DOI 10.4064/sm190505-8-10.
-\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada, \emph{Toeplitz operators on the symmetrized bidisc}, International Mathematics Research Notices (IMRN) {\bf } (), , DOI 10.1093/imrn/rnz333.
-\item Pingali, Vamsi Pritham and Varolin, Dror, \emph{Nonuniformly flat affine algebraic hypersurfaces}, to appear in Nagoya Mathematical Journal, DOI https://doi.org/10.1017/nmj.2019.2, \url{https://www.cambridge.org/core/journals/nagoya-mathematical-journal/article/nonuniformly-flat-affine-algebraic-hypersurfaces/3704C1133CB22A05D7FB13765156FC4E}.
-\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham , \emph{Gravitating vortices and the Einstein–Bogomol’nyi equations}, to appear in Mathematische Annalen, DOI https://doi.org/10.1007/s00208-020-01964-z, \url{https://link.springer.com/content/pdf/10.1007/s00208-020-01964-z.pdf}.
-\item Datar, Ved and Jacob,Adam and Zhang, Yuguang, \emph{Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces}, to appear in Journal of differential geometry, \url{https://arxiv.org/pdf/1809.08583.pdf}.
-\item Datar, Ved and Pingali, Vamsi Pritham, \emph{On coupled constant scalar curvature Kaehler metrics}, to appear in Journal of symplectic geometry, \url{https://arxiv.org/pdf/1901.10454v2.pdf}.
+Var}.
+\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107..
+\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} {\bf } ().
+\item Pingali, Vamsi Pritham and Varolin, Dror: Nonuniformly flat affine algebraic hypersurfaces, to appear in \emph{Nagoya Mathematical Journal}.
+\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein–Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.
+\item Datar, Ved and Jacob,Adam and Zhang, Yuguang: Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces, to appear in \emph{Journal of differential geometry}.
+\item Datar, Ved and Pingali, Vamsi Pritham: On coupled constant scalar curvature Kaehler metrics, to appear in \emph{Journal of symplectic geometry}.
+\item Pradhan, P. and Sahu, B.: A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd, \emph{Discrete Mathematics} {\bf 343} (2020).
+\item Arun Maiti: Quasi-vertex-transitive maps on the plane, \emph{Discrete Mathematics} {\bf 343} (2020), 111911-111917.
+\item Datt, Gopal and Kumar, Sanjay: A criterion for quasinormality in $\mathbb{C}^n$, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Paper No. 11, 13 pp..
+\item Hatui, Sumana: Schur multipliers of special p-groups of rank 2, \emph{Journal of Group Theory} {\bf 23} (2020), 85-95.
+\item Choudhury, Projesh Nath and Tsatsomeros Michael J.: Algorithmic Detection and Construction of N-matrices, \emph{Linear Algebra and Its Applications} {\bf 602} (2020), 46-56.
+\item Choudhury, Projesh Nath and Sivakumar, K.C.: Matrices with Positive Semidefinite Real Part, to appear in \emph{Linear and Multilinear Algebra}.
+\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala: On Baker's explicit abc-conjecture, \emph{Publ. Math. Debrecen} {\bf 94} (2019), 435–453.
+\item Carstensen, C.
+and Mallik, G.
+and Nataraj, N.: Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity, \emph{IMA Journal of Numerical Analysis} {\bf } (2020).
+\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: On some geometric properties of operator spaces, \emph{Banach J. Math. Anal.} {\bf 13} (2019), 174-191.
+\item Roth, Julien and Upadhyay, Abhitosh: On almost stable CMC hypersurfaces in manifolds of bounded sectional curvature, \emph{Bulletin of the Australian Mathematical Society} {\bf 101} (2020), 333-338.
+\item Roth, Julien and Upadhyay, Abhitosh: f-Biharmonic Submanifolds of Generalized Space Forms, \emph{Results in Mathematics} {\bf 75} (2020).
+\item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable CMC free-boundary surfaces in a strictly convex domain of a bi-invariant Lie group, to appear in \emph{International Journal of Mathematics}.
+\end{enumerate}
+
+\subsection{Papers in Journals with links}
+
+\begin{enumerate}
+\item S Aiyappan, A.
+K.
+Nandakumaran and Abu Sufian: Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure, \emph{Mathematical Methods in the Applied Sciences} {\bf 42} (2019.
+DOI: 10.1002/mma.5748), 6407-6434.
+\item K.
+Murali, A.
+K.
+Nandakumaran, Turgurt Durduran, Hari M Varma: Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements, \emph{Biomedical Optics Express 5395} {\bf 10} (2019).
+\item S Aiyappan, A.
+K.
+Nandakumaran and Ravi Prakash: Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains, \emph{Annali di Matematica Pura ed Applicata} {\bf 198} (2019), 1931-1954.
+\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash: Semi-linear optimal control problem on a smooth oscillating domain, \emph{Communications in Contemporary Mathematics} {\bf } (2019), 1-26.
+\item S Aiyappan, Editha C. Jose, Ivy Carol B. Lomerio and A. K. Nandakumaran: Control Problem on a Rough Circular Domain and Homogenization, \emph{Asymptotic Analysis} {\bf 115} (2019), 19-46.
+\item M. Balodi, A. Banerjee, S. Ray: Cohomology of modules over H-categories and co-H-categories, to appear in \emph{Canadian Journal of Mathematics}.
+\item M. Balodi, A. Banerjee, S. Ray: Entwined modules over linear categories and Galois extensions, to appear in \emph{Israel Journal of Mathematics (Accepted)}.
+\item A. Banerjee: On Noetherian schemes over $(\mathcal C,\otimes,1)$ and the category of quasi-coherent sheaves, to appear in \emph{Indiana University Mathematics Journal}.
+\item A. Banerjee: On differential torsion theories and rings with several objects, \emph{Canadian Math Bulletin} {\bf 62} (2019), 703--714.
+\item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric semigroups, \emph{Advances in Operator Theory (Special issue in honor of Rajendra Bhatia)} {\bf 5} (2020), 779-795.
+\item Ghosh, Subhajit: Total Variation Cutoff for the Transpose Top-2 with Random Shuffle, to appear in \emph{Journal of Theoretical Probability}.
+\item Datta, B. and Gupta, S.: Semi-regular tilings of the hyperbolic plane \label{bdsg_2019}, to appear in \emph{Discrete Comput Geom}.
+\item Datta, B. and Sarkar, S.: Equilibrium triangulations of some quasitoric 4-manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57--78.
+\item Datta, B. and Maity, D.: Correction to: Semi-equivelar and vertex-transitive maps on the torus, \emph{Beitr Algebra Geom} {\bf 61} (2020), 187--188.
+\item Martin Kreuzer and Dilip P.
+Patil: COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS, to appear in \emph{Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry}.
+\item Gadadhar Misra: Professor, \emph{Adv. Math.} {\bf 351} (2019), 1105 - 1138.
+\item Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}.
+\item Maitra, Anwoy: On the continuous extension of Kobayashi isometries, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.
+\item Vishnu Priya, N.
+and Senthilvelan, M.
+and  Rangarajan, G.
+and Lakshmanan, M: On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation, \emph{Physics Letters A} {\bf 383} (2019), 15-26.
+\item Kashyap, G.
+A.
+R.
+S.
+R.
+K.
+and Bapat, D.
+and Das, D.
+and Gowaikar, R.
+D.
+and Amritkar, R.
+E.
+and Rangarajan, G.
+and Ravindranath, V.
+and Ambika, G: Synapse loss and progress of Alzheimer’s disease - A network model, \emph{Scientific Reports} {\bf 9} (2019), 6555.
+\item Vishnu Priya, N.
+and Senthilvelan, M.
+and Rangarajan, G.: On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, \emph{Chaos} {\bf 29} (2019), 123135.
+\item Sarkar, Amar Deep and Verma, Kaushal: A submultiplicative property of the Carath\'{e}odory metric on planar domains, \emph{Proc. Indian Acad. Sci. (Math. Sci.)} {\bf } ().
+\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor: Higher Chern Classes in Iwasawa Theory, \emph{American Journal of Mathematics} {\bf 142} (2020), 627-682.
+\item Basu, R.
+and Ganguly, S.
+and Hegde, M.
+and Krishnapur, M.: Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation, to appear in \emph{Israel Journal of Mathematics}.
+\item M.
+K.
+Ghosh and S.
+Pradhan: Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant, to appear in \emph{ESIAM: Control, Optimization and Calculus of Variations}.
+\item M.
+K.
+Ghosh, K.
+Suresh Kumar, C.
+Pal and S.
+Pradhan: Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications, to appear in \emph{Stochastic Analysis and Applications}.
+\item Iyer, S.
+K.
+and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897.
+\item Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane, to appear in \emph{Discrete and Computational Geometry}.
+\item Thirupathi Gudi, Ramesh Ch.
+Sau: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim.
+Calc.
+Var}.
+\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107..
+\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} {\bf } ().
+\item Pingali, Vamsi Pritham and Varolin, Dror: Nonuniformly flat affine algebraic hypersurfaces, to appear in \emph{Nagoya Mathematical Journal}.
+\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein–Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.
+\item Datar, Ved and Jacob,Adam and Zhang, Yuguang: Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces, to appear in \emph{Journal of differential geometry}.
+\item Datar, Ved and Pingali, Vamsi Pritham: On coupled constant scalar curvature Kaehler metrics, to appear in \emph{Journal of symplectic geometry}.
 \item Pradhan, P.
-and Sahu, B., \emph{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, Discrete Mathematics {\bf 343} (2020), , DOI 10.1016/j.disc.2020.112044, \url{https://doi.org/10.1016/j.disc.2020.112044}.
-\item Arun Maiti, \emph{Quasi-vertex-transitive maps on the plane}, Discrete Mathematics {\bf 343} (2020), 111911-111917, \url{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}.
-\item Datt, Gopal and Kumar, Sanjay, \emph{A criterion for quasinormality in $\mathbb{C}^n$},  Proc.
+and Sahu, B.: \href{https://doi.org/10.1016/j.disc.2020.112044}{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, \emph{Discrete Mathematics} {\bf 343} (2020).
+\item Arun Maiti: \href{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}{Quasi-vertex-transitive maps on the plane}, \emph{Discrete Mathematics} {\bf 343} (2020), 111911-111917.
+\item Datt, Gopal and Kumar, Sanjay: \href{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}{A criterion for quasinormality in $\mathbb{C}^n$}, \emph{Proc.
 Indian Acad.
@@
 Math.
-Sci.
-{\bf 129} (2019), Paper No.
-11, 13 pp., DOI https://doi.org/10.1007/s12044-018-0449-5     (This article was published before the review period i.e., April 1, 2019, BUT this is not yet included on the page  https://siddhartha-gadgil.github.io/DeptWeb/pubs.html), \url{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}.
-\item Hatui, Sumana, \emph{Schur multipliers of special p-groups of rank 2}, Journal of Group Theory {\bf 23} (2020), 85-95, DOI https://doi.org/10.1515/jgth-2019-0045, \url{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}.
-\item Choudhury, Projesh Nath and Tsatsomeros Michael J., \emph{Algorithmic Detection and Construction of N-matrices}, Linear Algebra and Its Applications {\bf 602} (2020), 46-56, DOI 10.1016/j.laa.2020.04.028, \url{https://doi.org/10.1016/j.laa.2020.04.028}.
-\item Choudhury, Projesh Nath and Sivakumar, K.C., \emph{Matrices with Positive Semidefinite Real Part}, to appear in Linear and Multilinear Algebra, DOI 10.1080/03081087.2019.1602588, \url{https://doi.org/10.1080/03081087.2019.1602588}.
-\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala , \emph{On Baker's explicit abc-conjecture},  Publ. Math. Debrecen {\bf 94} (2019), 435–453.
+Sci.} {\bf 129} (2019), Paper No.
+11, 13 pp..
+\item Hatui, Sumana: \href{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}{Schur multipliers of special p-groups of rank 2}, \emph{Journal of Group Theory} {\bf 23} (2020), 85-95.
+\item Choudhury, Projesh Nath and Tsatsomeros Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic Detection and Construction of N-matrices}, \emph{Linear Algebra and Its Applications} {\bf 602} (2020), 46-56.
+\item Choudhury, Projesh Nath and Sivakumar, K.C.: \href{https://doi.org/10.1080/03081087.2019.1602588}{Matrices with Positive Semidefinite Real Part}, to appear in \emph{Linear and Multilinear Algebra}.
+\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala: On Baker's explicit abc-conjecture, \emph{Publ. Math. Debrecen} {\bf 94} (2019), 435–453.
 \item Carstensen, C.
 and Mallik, G.
-and Nataraj, N., \emph{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, IMA Journal of Numerical Analysis {\bf } (2020), , DOI https://doi.org/10.1093/imanum/drz071, \url{https://doi.org/10.1093/imanum/drz071}.
-\item Mal, Arpita and Sain, Debmalya and Paul, Kallol, \emph{On some geometric properties of operator spaces}, Banach J.
+and Nataraj, N.: \href{https://doi.org/10.1093/imanum/drz071}{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, \emph{IMA Journal of Numerical Analysis} {\bf } (2020).
+\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: \href{https://projecteuclid.org/euclid.bjma/1543914019}{On some geometric properties of operator spaces}, \emph{Banach J.
 Math.
-Anal.
-{\bf 13} (2019), 174-191, \url{https://projecteuclid.org/euclid.bjma/1543914019}.
+Anal.} {\bf 13} (2019), 174-191.
+\item Roth, Julien and Upadhyay, Abhitosh: \href{https://www.cambridge.org/core/journals/bulletin-of-the-australian-mathematical-society/article/on-almost-stable-cmc-hypersurfaces-in-manifolds-of-bounded-sectional-curvature/E0BF84D4D46C82F6D75CDCEAAF5DEE94}{On almost stable CMC hypersurfaces in manifolds of bounded sectional curvature}, \emph{Bulletin of the Australian Mathematical Society} {\bf 101} (2020), 333-338.
+\item Roth, Julien and Upadhyay, Abhitosh: \href{https://link.springer.com/article/10.1007/s00025-019-1142-4?shared-article-renderer#citeas}{f-Biharmonic Submanifolds of Generalized Space Forms}, \emph{Results in Mathematics} {\bf 75} (2020).
+\item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable CMC free-boundary surfaces in a strictly convex domain of a bi-invariant Lie group, to appear in \emph{International Journal of Mathematics}.
 \end{enumerate}
@@
 \begin{enumerate}
-\item Khare, Apoorva, \emph{Sharp nonzero lower bounds for the Schur product theorem}, submitted for publication, \url{https://arxiv.org/abs/1910.03537}.
-\item Lübeck, Frank and Prasad, Dipendra and Ayyer, Arvind, \emph{A character relationship between symmetric group and hyperoctahedral group }, preprint, \url{https://arxiv.org/abs/1912.08576}.
-\item Ayyer, Arvind and Sinha, Shubham , \emph{The size of t-cores and hook lengths of random cells in random partitions }, preprint, \url{https://arxiv.org/abs/1911.03135}.
-\item Ayyer, Arvind, \emph{ A simple symmetric exclusion process driven by an asymmetric tracer particle }, preprint, \url{https://arxiv.org/abs/2001.02425}.
-\item David Burns, Mahesh Kakde, \emph{On Weil-Etale Cohomology and Artin L-series}, preprint, \url{https://nms.kcl.ac.uk/david.burns/web_page/bk.pdf}.
-\item Gupta, Purvi and Wawrzyniak, Chloe Urbanski, \emph{STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$}, submitted for publication, \url{https://arxiv.org/pdf/2002.08699.pdf}.
-\item Radhika Ganapathy, \emph{A Hecke algebra isomorphism over close local fields}, preprint.
-\item Miermont, Grégory and Sen, Sanchayan , \emph{On breadth-first constructions of scaling limits of random graphs and random unicellular maps}, submitted for publication, \url{https://arxiv.org/abs/1908.04403}.
-\item Gupta, Subhojoy and Mj, Mahan, \emph{Meromorphic projective structures, grafting and the monodromy map}, preprint, \url{http://arxiv.org/abs/1904.03804}.
-\item Gupta, Subhojoy, \emph{Monodromy groups of CP^1-structures on punctured surfaces}, preprint, \url{https://arxiv.org/abs/1909.10771}.
-\item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter, \emph{Surface group representations in SL(2,C) with finite mapping class orbits}, preprint, \url{https://arxiv.org/abs/1707.00071}.
-\item Ganguly, Pritam and Thangavelu,Sundaram, \emph{On lacunary spherical maximal function on Heisenberg groups}, preprint.
-\item Bhattacharyya, Tirthankar and Kumar, Poornendu and Sau, Haripada, \emph{Distinguished Varieties Through the Berger--Coburn--Lebow Theorem}, submitted for publication, \url{https://arxiv.org/pdf/2001.01410.pdf}.
-\item Bhattacharyya, T. and  Biswas, A. and Maitra, A., \emph{An unbounded realization of the symmetrized bidisc}, submitted for publication, \url{https://arxiv.org/pdf/2005.00289.pdf }.
-\item Pingali, Vamsi Pritham, \emph{The deformed Hermitian Yang-Mills equation on three-folds}, preprint, \url{https://arxiv.org/abs/1910.01870}.
-\item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian , \emph{Gravitating vortices with positive curvature}, preprint, \url{https://arxiv.org/abs/1911.09616}.
-\item Quddus, Safdar, \emph{Equivariant Cartan Homotopy Formula for $DG$-algebra.}, preprint, \url{https://arxiv.org/abs/2002.02192}.
-\item Arun Maiti, \emph{OPTIMAL INDEX GROWTH OF CLOSED GEODESICS}, submitted for publication.
-\item  Poria, Anirudha, \emph{Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms}, submitted for publication, \url{https://arxiv.org/abs/2004.04184}.
-\item Poria, Anirudha, \emph{Uncertainty principles for the Opdam-Cherednik transform on modulation spaces}, submitted for publication, \url{https://arxiv.org/abs/2005.14274}.
-\item Bera, Sudip, \emph{ENUMERATION OF WEIGHTED PATHS ON A DIGRAPH AND BLOCK HOOK DETERMINANT}, submitted for publication.
-\item Behera, Kiran Kumar, \emph{Self-inversive polynomials from rational transformation of linear functionals}, submitted for publication, \url{https://arxiv.org/abs/1909.12548}.
-\item Hatui, Sumana and Singla Pooja, \emph{On Schur multiplier and Projective representations of Heisenberg groups}, submitted for publication, \url{https://arxiv.org/abs/1909.06589}.
-\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan, \emph{Multiplicities, invariant subspaces and an additive formula.}, preprint, \url{https://arxiv.org/abs/1812.05435}.
-\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita, \emph{$K$-homogeneous tuple of operators on bounded symmetric domains}, preprint.
+\item Khare, Apoorva: Sharp nonzero lower bounds for the Schur product theorem, submitted for publication.
+\item Lübeck, Frank and Prasad, Dipendra and Ayyer, Arvind: A character relationship between symmetric group and hyperoctahedral group, preprint.
+\item Ayyer, Arvind and Sinha, Shubham: The size of t-cores and hook lengths of random cells in random partitions, preprint.
+\item Ayyer, Arvind: A simple symmetric exclusion process driven by an asymmetric tracer particle, preprint.
+\item David Burns, Mahesh Kakde: On Weil-Etale Cohomology and Artin L-series, preprint.
+\item Gupta, Purvi and Wawrzyniak, Chloe Urbanski: STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$, submitted for publication.
+\item Radhika Ganapathy: A Hecke algebra isomorphism over close local fields, preprint.
+\item Miermont, Grégory and Sen, Sanchayan: On breadth-first constructions of scaling limits of random graphs and random unicellular maps, submitted for publication.
+\item Gupta, Subhojoy and Mj, Mahan: Meromorphic projective structures, grafting and the monodromy map, preprint.
+\item Gupta, Subhojoy: Monodromy groups of $CP^1$-structures on punctured surfaces, preprint.
+\item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter: Surface group representations in SL(2,C) with finite mapping class orbits, preprint.
+\item Ganguly, Pritam and Thangavelu,Sundaram: On lacunary spherical maximal function on Heisenberg groups, preprint.
+\item Bhattacharyya, Tirthankar and Kumar, Poornendu and Sau, Haripada: Distinguished Varieties Through the Berger--Coburn--Lebow Theorem, submitted for publication.
+\item Bhattacharyya, T. and  Biswas, A. and Maitra, A.: An unbounded realization of the symmetrized bidisc, submitted for publication.
+\item Pingali, Vamsi Pritham: The deformed Hermitian Yang-Mills equation on three-folds, preprint.
+\item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian: Gravitating vortices with positive curvature, preprint.
+\item Quddus, Safdar: Equivariant Cartan Homotopy Formula for $DG$-algebra., preprint.
+\item Arun Maiti: OPTIMAL INDEX GROWTH OF CLOSED GEODESICS, submitted for publication.
+\item Poria, Anirudha: Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms, submitted for publication.
+\item Poria, Anirudha: Uncertainty principles for the Opdam-Cherednik transform on modulation spaces, submitted for publication.
+\item Bera, Sudip: ENUMERATION OF WEIGHTED PATHS ON A DIGRAPH AND BLOCK HOOK DETERMINANT, submitted for publication.
+\item Behera, Kiran Kumar: Self-inversive polynomials from rational transformation of linear functionals, submitted for publication.
+\item Hatui, Sumana and Singla Pooja: On Schur multiplier and Projective representations of Heisenberg groups, submitted for publication.
+\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: Multiplicities, invariant subspaces and an additive formula., preprint.
+\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita: $K$-homogeneous tuple of operators on bounded symmetric domains, preprint.
+\item Toft, J. and Gumber, A. and Manna, R. and Ratnakumar, P. K.: Translation and modulation invariant Hilbert spaces, submitted for publication.
+\end{enumerate}
+
+\subsection{Preprints with links}
+
+\begin{enumerate}
+\item Khare, Apoorva: Sharp nonzero lower bounds for the Schur product theorem, submitted for publication.
+\item Lübeck, Frank and Prasad, Dipendra and Ayyer, Arvind: A character relationship between symmetric group and hyperoctahedral group, preprint.
+\item Ayyer, Arvind and Sinha, Shubham: The size of t-cores and hook lengths of random cells in random partitions, preprint.
+\item Ayyer, Arvind: A simple symmetric exclusion process driven by an asymmetric tracer particle, preprint.
+\item David Burns, Mahesh Kakde: On Weil-Etale Cohomology and Artin L-series, preprint.
+\item Gupta, Purvi and Wawrzyniak, Chloe Urbanski: STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$, submitted for publication.
+\item Radhika Ganapathy: A Hecke algebra isomorphism over close local fields, preprint.
+\item Miermont, Grégory and Sen, Sanchayan: On breadth-first constructions of scaling limits of random graphs and random unicellular maps, submitted for publication.
+\item Gupta, Subhojoy and Mj, Mahan: Meromorphic projective structures, grafting and the monodromy map, preprint.
+\item Gupta, Subhojoy: Monodromy groups of $CP^1$-structures on punctured surfaces, preprint.
+\item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter: Surface group representations in SL(2,C) with finite mapping class orbits, preprint.
+\item Ganguly, Pritam and Thangavelu,Sundaram: On lacunary spherical maximal function on Heisenberg groups, preprint.
+\item Bhattacharyya, Tirthankar and Kumar, Poornendu and Sau, Haripada: Distinguished Varieties Through the Berger--Coburn--Lebow Theorem, submitted for publication.
+\item Bhattacharyya, T. and  Biswas, A. and Maitra, A.: An unbounded realization of the symmetrized bidisc, submitted for publication.
+\item Pingali, Vamsi Pritham: The deformed Hermitian Yang-Mills equation on three-folds, preprint.
+\item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian: Gravitating vortices with positive curvature, preprint.
+\item Quddus, Safdar: \href{https://arxiv.org/abs/2002.02192}{Equivariant Cartan Homotopy Formula for $DG$-algebra.}, preprint.
+\item Arun Maiti: OPTIMAL INDEX GROWTH OF CLOSED GEODESICS, submitted for publication.
+\item Poria, Anirudha: \href{https://arxiv.org/abs/2004.04184}{Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms}, submitted for publication.
+\item Poria, Anirudha: \href{https://arxiv.org/abs/2005.14274}{Uncertainty principles for the Opdam-Cherednik transform on modulation spaces}, submitted for publication.
+\item Bera, Sudip: ENUMERATION OF WEIGHTED PATHS ON A DIGRAPH AND BLOCK HOOK DETERMINANT, submitted for publication.
+\item Behera, Kiran Kumar: \href{https://arxiv.org/abs/1909.12548}{Self-inversive polynomials from rational transformation of linear functionals}, submitted for publication.
+\item Hatui, Sumana and Singla Pooja: \href{https://arxiv.org/abs/1909.06589}{On Schur multiplier and Projective representations of Heisenberg groups}, submitted for publication.
+\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: \href{https://arxiv.org/abs/1812.05435}{Multiplicities, invariant subspaces and an additive formula.}, preprint.
+\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita: $K$-homogeneous tuple of operators on bounded symmetric domains, preprint.
+\item Toft, J. and Gumber, A. and Manna, R. and Ratnakumar, P. K.: \href{https://arxiv.org/abs/2004.02430v1}{Translation and modulation invariant Hilbert spaces}, submitted for publication.
 \end{enumerate}
@@
 \item Aas, Erik and Ayyer, Arvind and Linusson, Svante and Potka,
-Samu, {\em The exact phase diagram for a semipermeable {TASEP} with
-nonlocal boundary jumps}, J. Phys. A} {\bf 52} (2019), 355001, 19, DOI 10.1088/1751-8121/ab2e96, \url{https://doi.org/10.1088/1751-8121/ab2e96}.
+Samu: The exact phase diagram for a semipermeable {TASEP} with
+nonlocal boundary jumps, \emph{J. Phys. A} {\bf 52} (2019), 355001, 19.
 \item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
-Nandakumaran, A. K., {\em Control problem on a rough circular domain and homogenization}, Asymptot. Anal.} {\bf 115} (2019), 19--46, DOI 10.3233/asy-191526, \url{https://doi.org/10.3233/asy-191526}.
-\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Locally periodic unfolding operator for highly oscillating
-rough domains}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954, DOI 10.1007/s10231-019-00848-7, \url{https://doi.org/10.1007/s10231-019-00848-7}.
-\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Generalization of unfolding operator for highly oscillating
-smooth boundary domains and homogenization}, Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30, DOI 10.1007/s00526-018-1354-6, \url{https://doi.org/10.1007/s00526-018-1354-6}.
-\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu, {\em Asymptotic analysis of a boundary optimal control problem on a
-general branched structure}, Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434, DOI 10.1002/mma.5748, \url{https://doi.org/10.1002/mma.5748}.
-\item Aiyappan, S. and Sardar, Bidhan Chandra, {\em Biharmonic equation in a highly oscillating domain and
-homogenization of an associated control problem}, Appl. Anal.} {\bf 98} (2019), 2783--2801, DOI 10.1080/00036811.2018.1471207, \url{https://doi.org/10.1080/00036811.2018.1471207}.
-\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish, {\em A gap theorem for positive {E}instein metrics on the
-four-sphere}, Math. Ann.} {\bf 373} (2019), 1329--1339, DOI 10.1007/s00208-018-1749-x, \url{https://doi.org/10.1007/s00208-018-1749-x}.
-\item Anamby, Pramath and Das, Soumya, {\em Distinguishing {H}ermitian cusp forms of degree 2 by a certain
-subset of all {F}ourier coefficients}, Publ. Mat.} {\bf 63} (2019), 307--341, DOI 10.5565/PUBLMAT6311911, \url{https://doi.org/10.5565/PUBLMAT6311911}.
-\item Anamby, Pramath and Das, Soumya, {\em Bounds for the {P}etersson norms of the pullbacks of
-{S}aito-{K}urokawa lifts}, J. Number Theory} {\bf 191} (2018), 289--304, DOI 10.1016/j.jnt.2018.03.011, \url{https://doi.org/10.1016/j.jnt.2018.03.011}.
-\item Arunkumar, G. and Kus, Deniz and Venkatesh, R., {\em Root multiplicities for {B}orcherds algebras and graph
-coloring}, J. Algebra} {\bf 499} (2018), 538--569, DOI 10.1016/j.jalgebra.2017.11.050, \url{https://doi.org/10.1016/j.jalgebra.2017.11.050}.
-\item Ayyer, Arvind and Behrend, Roger E., {\em Factorization theorems for classical group characters, with
+Nandakumaran, A. K.: Control problem on a rough circular domain and homogenization, \emph{Asymptot. Anal.} {\bf 115} (2019), 19--46.
+\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: Semi-linear optimal control problem on a smooth oscillating
+domain, \emph{Commun. Contemp. Math.} {\bf 22} (2020), 1950029, 26.
+\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: Locally periodic unfolding operator for highly oscillating
+rough domains, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954.
+\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu: Asymptotic analysis of a boundary optimal control problem on a
+general branched structure, \emph{Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434.
+\item Aiyappan, S. and Sardar, Bidhan Chandra: Biharmonic equation in a highly oscillating domain and
+homogenization of an associated control problem, \emph{Appl. Anal.} {\bf 98} (2019), 2783--2801.
+\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish: A gap theorem for positive {E}instein metrics on the
+four-sphere, \emph{Math. Ann.} {\bf 373} (2019), 1329--1339.
+\item Anamby, Pramath and Das, Soumya: Distinguishing {H}ermitian cusp forms of degree 2 by a certain
+subset of all {F}ourier coefficients, \emph{Publ. Mat.} {\bf 63} (2019), 307--341.
+\item Anand, Jatin and Bhattacharyya, Tirthankar and Srivastava,
+Sachi: Some thoughts on composition operators on subspaces of the
+{H}ardy space, \emph{Arch. Math. (Basel)} {\bf 114} (2020), 431--444.
+\item Ayyer, Arvind: Squareness for the {M}onopole-{D}imer model, \emph{Ann. Comb.} {\bf 24} (2020), 237--255.
+\item Ayyer, Arvind and Behrend, Roger E.: Factorization theorems for classical group characters, with
 applications to alternating sign matrices and plane
-partitions}, J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105, DOI 10.1016/j.jcta.2019.01.001, \url{https://doi.org/10.1016/j.jcta.2019.01.001}.
-\item Ayyer, Arvind and Bouttier, J\'{e}r\'{e}mie and Corteel, Sylvie and
-Linusson, Svante and Nunzi, Fran\c{c}ois, {\em Bumping sequences and multispecies juggling}, Adv.
-in Appl.
-Math.} {\bf 98} (2018), 100--126, DOI 10.1016/j.aam.2018.03.001, \url{https://doi.org/10.1016/j.aam.2018.03.001}.
-\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, {\em Matrix product solution of a left-permeable two-species
-asymmetric exclusion process}, Phys. Rev. E} {\bf 97} (2018), 012151, 10, DOI 10.1103/physreve.97.012151, \url{https://doi.org/10.1103/physreve.97.012151}.
-\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, {\em The phase diagram for a multispecies left-permeable asymmetric
-exclusion process}, J. Stat. Phys.} {\bf 174} (2019), 605--621, DOI 10.1007/s10955-018-2183-x, \url{https://doi.org/10.1007/s10955-018-2183-x}.
-\item Ayyer, Arvind and Linusson, Svante, {\em Reverse juggling processes}, Random Structures Algorithms} {\bf 55} (2019), 56--72, DOI 10.1002/rsa.20825, \url{https://doi.org/10.1002/rsa.20825}.
-\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, {\em Odd partitions in {Y}oung's lattice}, S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
-\item Ayyer, Arvind and Ramassamy, Sanjay, {\em The {H}ilbert-{G}alton board}, ALEA Lat.
-Am.
-J.
-Probab.
-Math.
-Stat.} {\bf 15} (2018), 755--774, DOI 10.30757/alea.v15-28, \url{https://doi.org/10.30757/alea.v15-28}.
-\item B\"{o}cherer, Siegfried and Das, Soumya, {\em Cuspidality and the growth of {F}ourier coefficients of
-modular forms}, J. Reine Angew. Math.} {\bf 741} (2018), 161--178, DOI 10.1515/crelle-2015-0075, \url{https://doi.org/10.1515/crelle-2015-0075}.
-\item B\"{o}cherer, Siegfried and Das, Soumya, {\em Petersson norms of not necessarily cuspidal {J}acobi modular
-forms and applications}, Adv. Math.} {\bf 336} (2018), 335--376, DOI 10.1016/j.aim.2018.07.033, \url{https://doi.org/10.1016/j.aim.2018.07.033}.
-\item Bagchi, Sayan and Thangavelu, Sundaram, {\em Weighted norm inequalities for {W}eyl multipliers and fourier
-multipliers on the {H}eisenberg group}, J. Anal. Math.} {\bf 136} (2018), 1--29, DOI 10.1007/s11854-018-0053-8, \url{https://doi.org/10.1007/s11854-018-0053-8}.
-\item Baklouti, Ali and Thangavelu, Sundaram, {\em Hardy and {M}iyachi theorems for {H}eisenberg motion groups}, Nagoya Math.
-J.} {\bf 229} (2018), 1--20, DOI 10.1017/nmj.2016.58, \url{https://doi.org/10.1017/nmj.2016.58}.
+partitions, \emph{J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.
+\item Ayyer, Arvind and Behrend, Roger E. and Fischer, Ilse: Extreme diagonally and antidiagonally symmetric alternating
+sign matrices of odd order, \emph{Adv. Math.} {\bf 367} (2020), 107125, 56.
+\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar: The phase diagram for a multispecies left-permeable asymmetric
+exclusion process, \emph{J. Stat. Phys.} {\bf 174} (2019), 605--621.
+\item Ayyer, Arvind and Fischer, Ilse: Bijective proofs of skew {S}chur polynomial factorizations, \emph{J. Combin. Theory Ser. A} {\bf 174} (2020), 105241, 40.
+\item Ayyer, Arvind and Linusson, Svante: Reverse juggling processes, \emph{Random Structures Algorithms} {\bf 55} (2019), 56--72.
+\item Ayyer, Arvind and Singla, Pooja: Random motion on finite rings, {I}: commutative rings, \emph{Algebr. Represent. Theory} {\bf 23} (2020), 583--604.
 \item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
-Verma, Kaushal, {\em Remarks on the higher dimensional {S}uita conjecture}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411, DOI 10.1090/proc/14421, \url{https://doi.org/10.1090/proc/14421}.
-\item Balhara, Rakesh, {\em Hardy's inequality for the fractional powers of the {G}rushin
-operator}, Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25, DOI 10.1007/s12044-019-0471-2, \url{https://doi.org/10.1007/s12044-019-0471-2}.
-\item Balodi, Mamta and Palcoux, Sebastien, {\em On {B}oolean intervals of finite groups}, J.
-Combin.
-Theory Ser.
-A} {\bf 157} (2018), 49--69, DOI 10.1016/j.jcta.2018.02.004, \url{https://doi.org/10.1016/j.jcta.2018.02.004}.
-\item Banerjee, Abhishek, {\em On {A}uslander's formula and cohereditary torsion pairs}, Commun.
-Contemp.
-Math.} {\bf 20} (2018), 1750071, 27, DOI 10.1142/S0219199717500717, \url{https://doi.org/10.1142/S0219199717500717}.
-\item Banerjee, Abhishek, {\em Modular {H}ecke algebras over {M}\"{o}bius categories}, J.
-Geom.
-Phys.} {\bf 131} (2018), 23--40, DOI 10.1016/j.geomphys.2018.04.008, \url{https://doi.org/10.1016/j.geomphys.2018.04.008}.
-\item Banerjee, Abhishek, {\em On differential torsion theories and rings with several
-objects}, Canad. Math. Bull.} {\bf 62} (2019), 703--714, DOI 10.4153/s0008439518000656, \url{https://doi.org/10.4153/s0008439518000656}.
-\item Banerjee, Abhishek, {\em A topological {N}ullstellensatz for tensor-triangulated
-categories}, C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375, DOI 10.1016/j.crma.2018.02.012, \url{https://doi.org/10.1016/j.crma.2018.02.012}.
-\item Banerjee, Abhishek, {\em Quasimodular {H}ecke algebras and {H}opf actions}, J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080, DOI 10.4171/JNCG/297, \url{https://doi.org/10.4171/JNCG/297}.
-\item Banerjee, Abhishek, {\em Completions of monoid objects and descent results}, J.
-Algebra} {\bf 507} (2018), 362--399, DOI 10.1016/j.jalgebra.2018.04.022, \url{https://doi.org/10.1016/j.jalgebra.2018.04.022}.
-\item Banerjee, Abhishek and Kour, Surjeet, {\em {$(A,\delta)$}-modules, {H}ochschild homology and higher
-derivations}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802, DOI 10.1007/s10231-019-00844-x, \url{https://doi.org/10.1007/s10231-019-00844-x}.
-\item Basu, Arnab and Ghosh, Mrinal K., {\em Nonzero-sum risk-sensitive stochastic games on a countable
-state space}, Math. Oper. Res.} {\bf 43} (2018), 516--532, DOI 10.1287/moor.2017.0870, \url{https://doi.org/10.1287/moor.2017.0870}.
+Verma, Kaushal: Remarks on the higher dimensional {S}uita conjecture, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411.
+\item Balhara, Rakesh: Hardy's inequality for the fractional powers of the {G}rushin
+operator, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25.
+\item Banerjee, Abhishek: On differential torsion theories and rings with several
+objects, \emph{Canad. Math. Bull.} {\bf 62} (2019), 703--714.
+\item Banerjee, Abhishek and Kour, Surjeet: {$(A,\delta)$}-modules, {H}ochschild homology and higher
+derivations, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802.
 \item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
-and Putinar, Mihai, {\em Simultaneous kernels of matrix {H}adamard powers}, Linear Algebra Appl.} {\bf 576} (2019), 142--157, DOI 10.1016/j.laa.2018.03.035, \url{https://doi.org/10.1016/j.laa.2018.03.035}.
+and Putinar, Mihai: Simultaneous kernels of matrix {H}adamard powers, \emph{Linear Algebra Appl.} {\bf 576} (2019), 142--157.
 \item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
 Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
-Morales, Alejandro H. and Yip, Martha, {\em The volume of the caracol polytope}, S\'{e}m. Lothar. Combin.} {\bf 80B} (2018), Art. 87, 12.
-\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
-Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
-Morales, Alejandro H.
-and Yip, Martha, {\em A combinatorial model for computing volumes of flow polytopes}, Trans.
-Amer.
-Math.
-Soc.} {\bf 372} (2019), 3369--3404, DOI 10.1090/tran/7743, \url{https://doi.org/10.1090/tran/7743}.
-\item Bera, Sayani and Verma, Kaushal, {\em Some aspects of shift-like automorphisms of {$\Bbb C^k$}}, Proc.
-Indian Acad.
-Sci.
-Math.
-Sci.} {\bf 128} (2018), Art.
-10, 48, DOI 10.1007/s12044-018-0388-1, \url{https://doi.org/10.1007/s12044-018-0388-1}.
-\item Bharali, Gautam and Biswas, Indranil and Divakaran, Divakaran
-and Janardhanan, Jaikrishnan, {\em Proper holomorphic mappings onto symmetric products of a
-{R}iemann surface}, Doc. Math.} {\bf 23} (2018), 1291--1311.
-\item Bharali, Gautam and Chandel, Vikramjeet Singh, {\em Pick interpolation on the polydisc: small families of
-sufficient kernels}, Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093, DOI 10.1007/s11785-017-0701-5, \url{https://doi.org/10.1007/s11785-017-0701-5}.
-\item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K., {\em Survey of last ten years of work done in {I}ndia in some
-selected areas of functional analysis and operator theory}, Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617, DOI 10.1007/s13226-019-0345-4, \url{https://doi.org/10.1007/s13226-019-0345-4}.
-\item Bhattacharyya, Tirthankar and Sau, Haripada, {\em Holomorphic functions on the symmetrized bidisk---realization,
-interpolation and extension}, J. Funct. Anal.} {\bf 274} (2018), 504--524, DOI 10.1016/j.jfa.2017.09.013, \url{https://doi.org/10.1016/j.jfa.2017.09.013}.
+Morales, Alejandro H. and Yip, Martha: A combinatorial model for computing volumes of flow polytopes, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 3369--3404.
+\item Bera, Sayani and Pal, Ratna and Verma, Kaushal: A rigidity theorem for {H}\'{e}non maps, \emph{Eur. J. Math.} {\bf 6} (2020), 508--532.
+\item Bharali, Gautam: On the growth of the {B}ergman metric near a point of infinite
+type, \emph{J. Geom. Anal.} {\bf 30} (2020), 1238--1258.
+\item Bharali, Gautam and Chandel, Vikramjeet Singh: Pick interpolation on the polydisc: small families of
+sufficient kernels, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093.
+\item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K.: Survey of last ten years of work done in {I}ndia in some
+selected areas of functional analysis and operator theory, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617.
 \item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
-Sundaram, {\em Hermite multipliers on modulation spaces}, Analysis and partial differential equations: perspectives from
+Sundaram: Hermite multipliers on modulation spaces, \emph{Analysis and partial differential equations: perspectives from
 developing countries} {\bf 275} (2019), 42--64.
-\item Bhosle, Usha N., {\em Hitchin pairs on reducible curves}, Internat. J. Math.} {\bf 29} (2018), 1850015, 49, DOI 10.1142/S0129167X18500155, \url{https://doi.org/10.1142/S0129167X18500155}.
-\item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and
-Pingali, Vamsi P., {\em Rational cuspidal curves on del-{P}ezzo surfaces}, J. Singul.} {\bf 17} (2018), 91--107.
-\item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy, {\em Branched projective structures on a {R}iemann surface and
-logarithmic connections}, Doc. Math.} {\bf 24} (2019), 2299--2337.
-\item Biswas, Indranil and Pingali, Vamsi Pritham, {\em A characterization of finite vector bundles on {G}auduchon
-astheno-{K}\"{a}hler manifolds}, \'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art. 6, 13.
-\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi, {\em Edge patch-wise local projection stabilized nonconforming
-{FEM} for the {O}seen problem}, Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214, DOI 10.1515/cmam-2018-0020, \url{https://doi.org/10.1515/cmam-2018-0020}.
+\item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy: Branched projective structures on a {R}iemann surface and
+logarithmic connections, \emph{Doc. Math.} {\bf 24} (2019), 2299--2337.
+\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi: Edge patch-wise local projection stabilized nonconforming
+{FEM} for the {O}seen problem, \emph{Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214.
 \item Biswas, Shibananda and Ghosh, Gargi and Misra, Gadadhar and
-Shyam Roy, Subrata, {\em On reducing submodules of {H}ilbert modules with
-{${S}_n$}-invariant kernels}, J. Funct. Anal.} {\bf 276} (2019), 751--784, DOI 10.1016/j.jfa.2018.10.025, \url{https://doi.org/10.1016/j.jfa.2018.10.025}.
-\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram, {\em On extension problem, trace {H}ardy and {H}ardy's inequalities
-for some fractional {L}aplacians}, Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605, DOI 10.3934/cpaa.2019116, \url{https://doi.org/10.3934/cpaa.2019116}.
-\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal, {\em Comments on the {G}reen's function of a planar domain}, Anal.
-Math.
-Phys.} {\bf 8} (2018), 383--414, DOI 10.1007/s13324-017-0177-5, \url{https://doi.org/10.1007/s13324-017-0177-5}.
-\item Brenner, Susanne C. and Gudi, Thirupathi and Porwal, Kamana
-and Sung, Li-Yeng, {\em A {M}orley finite element method for an elliptic distributed
-optimal control problem with pointwise state and control
-constraints}, ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206, DOI 10.1051/cocv/2017031, \url{https://doi.org/10.1051/cocv/2017031}.
-\item Burton, Benjamin A. and Datta, Basudeb and Singh, Nitin and
-Spreer, Jonathan, {\em A construction principle for tight and minimal triangulations
-of manifolds}, Exp. Math.} {\bf 27} (2018), 22--36, DOI 10.1080/10586458.2016.1212747, \url{https://doi.org/10.1080/10586458.2016.1212747}.
-\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella, {\em Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
-indefinite second-order linear elliptic problems}, Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250, DOI 10.1515/cmam-2019-0034, \url{https://doi.org/10.1515/cmam-2019-0034}.
-\item Chandel, Vikramjeet Singh, {\em The three-point {P}ick-{N}evanlinna interpolation problem on
-the polydisc}, Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352, DOI 10.1080/17476933.2017.1370461, \url{https://doi.org/10.1080/17476933.2017.1370461}.
-\item Chatterjee, Esha and Hassan, Sk. Sarif, {\em On the asymptotic character of a generalized rational
-difference equation}, Discrete Contin. Dyn. Syst.} {\bf 38} (2018), 1707--1718, DOI 10.3934/dcds.2018070, \url{https://doi.org/10.3934/dcds.2018070}.
-\item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
-K. C., {\em A note on linear preservers of semipositive and minimally
-semipositive matrices}, Electron. J. Linear Algebra} {\bf 34} (2018), 687--694, DOI 10.13001/1081-3810.3864, \url{https://doi.org/10.13001/1081-3810.3864}.
-\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram, {\em Hardy-type inequalities for fractional powers of the
-{D}unkl-{H}ermite operator}, Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544, DOI 10.1017/s0013091517000311, \url{https://doi.org/10.1017/s0013091517000311}.
-\item Das, Soumya and Jha, Abhash Kumar, {\em Analytic properties of twisted real-analytic {H}ermitian
-{K}lingen type {E}isenstein series and applications}, Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116, DOI 10.1007/s12188-019-00206-7, \url{https://doi.org/10.1007/s12188-019-00206-7}.
-\item Das, Soumya and Khan, Rizwanur, {\em The third moment of symmetric square {$L$}-functions}, Q.
-J.
-Math.} {\bf 69} (2018), 1063--1087, DOI 10.1093/qmath/hay012, \url{https://doi.org/10.1093/qmath/hay012}.
-\item Das, Soumya and Kohnen, Winfried, {\em On sign changes of eigenvalues of {S}iegel cusp forms of genus
-2 in prime powers}, Acta Arith.} {\bf 183} (2018), 167--172, DOI 10.4064/aa170419-4-11, \url{https://doi.org/10.4064/aa170419-4-11}.
-\item Das, Soumya and Pal, Ritwik, {\em The first negative eigenvalue of {Y}oshida lifts}, Res.
-Number Theory} {\bf 5} (2019), Paper No.
-20, 9, DOI 10.1007/s40993-019-0158-x, \url{https://doi.org/10.1007/s40993-019-0158-x}.
-\item Datta, Basudeb and Maity, Dipendu, {\em Semi-equivelar maps on the torus and the {K}lein bottle are
-{A}rchimedean}, Discrete Math.} {\bf 341} (2018), 3296--3309, DOI 10.1016/j.disc.2018.08.016, \url{https://doi.org/10.1016/j.disc.2018.08.016}.
-\item Dond, Asha K. and Gudi, Thirupathi, {\em Patch-wise local projection stabilized finite element methods
-for convection-diffusion-reaction problems}, Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663, DOI 10.1002/num.22317, \url{https://doi.org/10.1002/num.22317}.
-\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH., {\em An error analysis of discontinuous finite element methods for
-the optimal control problems governed by {S}tokes equation}, Numer.
-Funct.
-Anal.
-Optim.} {\bf 40} (2019), 421--460, DOI 10.1080/01630563.2018.1538158, \url{https://doi.org/10.1080/01630563.2018.1538158}.
-\item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P.
-and Silberman, Lior and Tao, Terence, {\em Homogeneous length functions on groups}, Algebra Number Theory} {\bf 12} (2018), 1773--1786, DOI 10.2140/ant.2018.12.1773, \url{https://doi.org/10.2140/ant.2018.12.1773}.
-\item Gaddam, Sharat and Gudi, Thirupathi, {\em Inhomogeneous {D}irichlet boundary condition in the {\it a
-posteriori} error control of the obstacle problem}, Comput. Math. Appl.} {\bf 75} (2018), 2311--2327, DOI 10.1016/j.camwa.2017.12.010, \url{https://doi.org/10.1016/j.camwa.2017.12.010}.
-\item Gaddam, Sharat and Gudi, Thirupathi, {\em Bubbles enriched quadratic finite element method for the
-3{D}-elliptic obstacle problem}, Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236, DOI 10.1515/cmam-2017-0018, \url{https://doi.org/10.1515/cmam-2017-0018}.
-\item Garani, Shayan Srinivasa and Seshadri, Harish, {\em An algorithmic approach to {S}outh {I}ndian classical music}, J.
-Math.
-Music} {\bf 13} (2019), 107--134, DOI 10.1080/17459737.2019.1604845, \url{https://doi.org/10.1080/17459737.2019.1604845}.
-\item Gaussier, Herv\'{e} and Seshadri, Harish, {\em Holomorphic motions and complex geometry}, Proc.
-Amer.
-Math.
-Soc.} {\bf 147} (2019), 301--313, DOI 10.1090/proc/14217, \url{https://doi.org/10.1090/proc/14217}.
-\item Gaussier, Herv\'{e} and Seshadri, Harish, {\em On the {G}romov hyperbolicity of convex domains in {$\Bbb
-C^n$}}, Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641, DOI 10.1007/s40315-018-0243-5, \url{https://doi.org/10.1007/s40315-018-0243-5}.
-\item Ghara, Soumitra and Kumar, Surjit, {\em On the sum of two subnormal kernels}, J.
-Math.
-Anal.
-Appl.} {\bf 469} (2019), 1015--1027, DOI 10.1016/j.jmaa.2018.09.048, \url{https://doi.org/10.1016/j.jmaa.2018.09.048}.
-\item Ghosh, Mrinal K. and Pradhan, Somnath, {\em Risk-sensitive stochastic differential games with reflecting
-diffusions}, Stoch. Anal. Appl.} {\bf 36} (2018), 1--27, DOI 10.1080/07362994.2017.1356732, \url{https://doi.org/10.1080/07362994.2017.1356732}.
-\item Gudi, Thirupathi and Majumder, Papri, {\em Convergence analysis of finite element method for a parabolic
-obstacle problem}, J. Comput. Appl. Math.} {\bf 357} (2019), 85--102, DOI 10.1016/j.cam.2019.02.026, \url{https://doi.org/10.1016/j.cam.2019.02.026}.
-\item Gudi, Thirupathi and Majumder, Papri, {\em Conforming and discontinuous {G}alerkin {FEM} in space for
-solving parabolic obstacle problem}, Comput. Math. Appl.} {\bf 78} (2019), 3896--3915, DOI 10.1016/j.camwa.2019.06.022, \url{https://doi.org/10.1016/j.camwa.2019.06.022}.
-\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh, {\em Von {N}eumann's inequality for commuting operator-valued
-multishifts}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608, DOI 10.1090/proc/14410, \url{https://doi.org/10.1090/proc/14410}.
-\item Gupta, Rajeev and Ramiz Reza, Md., {\em Operator space structures on {$\ell^1(n)$}}, Houston J. Math.} {\bf 44} (2018), 1205--1212.
-\item Gupta, S. C., {\em The classical {S}tefan problem}, } {\bf } (2018), xxiii+726.
-\item Gupta, Subhojoy, {\em Limits of harmonic maps and crowned hyperbolic surfaces}, Trans.
-Amer.
-Math.
-Soc.} {\bf 372} (2019), 7573--7596, DOI 10.1090/tran/7777, \url{https://doi.org/10.1090/tran/7777}.
-\item Gupta, Subhojoy and Wolf, Michael, {\em Meromorphic quadratic differentials and measured foliations on
-a {R}iemann surface}, Math. Ann.} {\bf 373} (2019), 73--118, DOI 10.1007/s00208-018-1674-z, \url{https://doi.org/10.1007/s00208-018-1674-z}.
-\item Hazra, Somnath, {\em Homogeneous 2-shifts}, Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763, DOI 10.1007/s11785-018-0822-5, \url{https://doi.org/10.1007/s11785-018-0822-5}.
-\item Iyer, Srikanth K., {\em The random connection model: connectivity, edge lengths, and
-degree distributions}, Random Structures Algorithms} {\bf 52} (2018), 283--300, DOI 10.1002/rsa.20741, \url{https://doi.org/10.1002/rsa.20741}.
+Shyam Roy, Subrata: On reducing submodules of {H}ilbert modules with
+{${S}_n$}-invariant kernels, \emph{J. Funct. Anal.} {\bf 276} (2019), 751--784.
+\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram: On extension problem, trace {H}ardy and {H}ardy's inequalities
+for some fractional {L}aplacians, \emph{Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605.
+\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella: Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
+indefinite second-order linear elliptic problems, \emph{Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.
+\item Chakraborty, Atlanta and Chandru, Vijay and Rao, M. R.: A linear programming primer: from {F}ourier to {K}armarkar, \emph{Ann. Oper. Res.} {\bf 287} (2020), 593--616.
+\item Chandel, Vikramjeet Singh: The 3-point spectral pick interpolation problem and an
+application to holomorphic correspondences, \emph{J. Geom. Anal.} {\bf 30} (2020), 551--572.
+\item Choudhury, Projesh Nath and Tsatsomeros, Michael J.: Algorithmic detection and construction of {N}-matrices, \emph{Linear Algebra Appl.} {\bf 602} (2020), 46--56.
+\item Cicuttin, Matteo and Ern, Alexandre and Gudi, Thirupathi: Hybrid high-order methods for the elliptic obstacle problem, \emph{J. Sci. Comput.} {\bf 83} (2020), Paper No. 8, 18.
+\item Das, Soumya and Jha, Abhash Kumar: Analytic properties of twisted real-analytic {H}ermitian
+{K}lingen type {E}isenstein series and applications, \emph{Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116.
+\item Das, Soumya and Pal, Ritwik: The first negative eigenvalue of {Y}oshida lifts, \emph{Res. Number Theory} {\bf 5} (2019), Paper No. 20, 9.
+\item Dond, Asha K. and Gudi, Thirupathi: Patch-wise local projection stabilized finite element methods
+for convection-diffusion-reaction problems, \emph{Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663.
+\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH.: An error analysis of discontinuous finite element methods for
+the optimal control problems governed by {S}tokes equation, \emph{Numer. Funct. Anal. Optim.} {\bf 40} (2019), 421--460.
+\item Gadgil, Siddhartha: Homogeneous {L}ength {F}unctions on {G}roups: {I}ntertwined
+{C}omputer and {H}uman {P}roofs, \emph{J. Automat. Reason.} {\bf 64} (2020), 677--688.
+\item Garani, Shayan Srinivasa and Seshadri, Harish: An algorithmic approach to {S}outh {I}ndian classical music, \emph{J. Math. Music} {\bf 13} (2019), 107--134.
+\item Gaussier, Herv\'{e} and Seshadri, Harish: Holomorphic motions and complex geometry, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 301--313.
+\item Ghara, Soumitra and Kumar, Surjit: On the sum of two subnormal kernels, \emph{J. Math. Anal. Appl.} {\bf 469} (2019), 1015--1027.
+\item Gudi, Thirupathi and Majumder, Papri: Crouzeix-{R}aviart finite element approximation for the
+parabolic obstacle problem, \emph{Comput. Methods Appl. Math.} {\bf 20} (2020), 273--292.
+\item Gudi, Thirupathi and Majumder, Papri: Convergence analysis of finite element method for a parabolic
+obstacle problem, \emph{J. Comput. Appl. Math.} {\bf 357} (2019), 85--102.
+\item Gudi, Thirupathi and Majumder, Papri: Conforming and discontinuous {G}alerkin {FEM} in space for
+solving parabolic obstacle problem, \emph{Comput. Math. Appl.} {\bf 78} (2019), 3896--3915.
+\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: Unitary equivalence of operator-valued multishifts, \emph{J. Math. Anal. Appl.} {\bf 487} (2020), 124032, 23.
+\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: Von {N}eumann's inequality for commuting operator-valued
+multishifts, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.
+\item Gupta, Subhojoy: Limits of harmonic maps and crowned hyperbolic surfaces, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 7573--7596.
+\item Gupta, Subhojoy and Mj, Mahan: Monodromy representations of meromorphic projective
+structures, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 2069--2078.
+\item Gupta, Subhojoy and Seshadri, Harish: On domains biholomorphic to {T}eichm\"{u}ller spaces, \emph{Int. Math. Res. Not. IMRN} {\bf } (2020), 2542--2560.
+\item Gupta, Subhojoy and Wolf, Michael: Meromorphic quadratic differentials and measured foliations on
+a {R}iemann surface, \emph{Math. Ann.} {\bf 373} (2019), 73--118.
+\item Hatui, Sumana: Schur multipliers of special {$p$}-groups of rank 2, \emph{J. Group Theory} {\bf 23} (2020), 85--95.
+\item Hazra, Somnath: Homogeneous 2-shifts, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.
 \item Jha, Abhash Kumar and Juyal, Abhishek and Pandey, Manish
-Kumar, {\em On simultaneous non-vanishing of twisted {$L$}-functions
-associated to newforms on {$\Gamma_0(N)$}}, J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.
-\item Jha, Abhash Kumar and Sahu, Brundaban, {\em Rankin-{C}ohen brackets on {J}acobi forms of several variables
-and special values of certain {D}irichlet series}, Int. J. Number Theory} {\bf 15} (2019), 925--933, DOI 10.1142/S1793042119500490, \url{https://doi.org/10.1142/S1793042119500490}.
-\item Jha, Abhash Kumar and Sahu, Brundaban, {\em Differential operators on {J}acobi forms and special values of
-certain {D}irichlet series}, Automorphic forms and related topics} {\bf 732} (2019), 91--99, DOI 10.1090/conm/732/14793, \url{https://doi.org/10.1090/conm/732/14793}.
-\item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
-Sekar, Sruthi, {\em Non-malleable randomness encoders and their applications}, Advances in cryptology---{EUROCRYPT} 2018. {P}art {III}} {\bf 10822} (2018), 589--617.
+Kumar: On simultaneous non-vanishing of twisted {$L$}-functions
+associated to newforms on {$\Gamma_0(N)$}, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.
+\item Jha, Abhash Kumar and Sahu, Brundaban: Rankin-{C}ohen brackets on {J}acobi forms of several variables
+and special values of certain {D}irichlet series, \emph{Int. J. Number Theory} {\bf 15} (2019), 925--933.
+\item Jha, Abhash Kumar and Sahu, Brundaban: Differential operators on {J}acobi forms and special values of
+certain {D}irichlet series, \emph{Automorphic forms and related topics} {\bf 732} (2019), 91--99.
 \item Kashyap, G.
@@
 Ravindranath and G.
-Ambika, {\em Synapse loss and progress of Alzheimer&rsquo;s disease - A network model}, Scientific Reports} {\bf 9} (2019), .
-\item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan, {\em On the convolution of {M}ittag-{L}effler distributions and its
-applications to fractional point processes}, Stoch. Anal. Appl.} {\bf 37} (2019), 115--122, DOI 10.1080/07362994.2018.1538803, \url{https://doi.org/10.1080/07362994.2018.1538803}.
+Ambika: Synapse loss and progress of Alzheimers disease - A network model, \emph{Scientific Reports} {\bf 9} (2019).
+\item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan: On the convolution of {M}ittag-{L}effler distributions and its
+applications to fractional point processes, \emph{Stoch. Anal. Appl.} {\bf 37} (2019), 115--122.
 \item Khan, Mohammad Yasir Feroz and Biswas, Rahul and Sau, Ramesh
-Chandra, {\em Instability of {L}agrange interpolation on {$H^1(\Omega)\cap
-C(\overline\Omega)$}}, Math. Student} {\bf 88} (2019), 153--158.
-\item Khare, Apoorva, {\em Generalized nil-{C}oxeter algebras over discrete complex
-reflection groups}, Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999, DOI 10.1090/tran/7304, \url{https://doi.org/10.1090/tran/7304}.
-\item Khare, Apoorva and Tikaradze, Akaki, {\em A {C}arlitz--von {S}taudt type theorem for finite rings}, Linear Algebra Appl.} {\bf 568} (2019), 106--126, DOI 10.1016/j.laa.2018.05.035, \url{https://doi.org/10.1016/j.laa.2018.05.035}.
-\item Krakovski, Roi and Onn, Uri and Singla, Pooja, {\em Regular characters of groups of type {$\ssf A_n$} over
-discrete valuation rings}, J. Algebra} {\bf 496} (2018), 116--137, DOI 10.1016/j.jalgebra.2017.10.018, \url{https://doi.org/10.1016/j.jalgebra.2017.10.018}.
+Chandra: Instability of {L}agrange interpolation on {$H^1(\Omega)\cap
+C(\overline\Omega)$}, \emph{Math. Student} {\bf 88} (2019), 153--158.
+\item Khare, Apoorva and Tikaradze, Akaki: A {C}arlitz--von {S}taudt type theorem for finite rings, \emph{Linear Algebra Appl.} {\bf 568} (2019), 106--126.
 \item Lin, X.
@@
 and Jolly, M.
-K., {\em Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level}, Biomolecules} {\bf 9} (2019), 77.
-\item Mahajan, Prachi and Verma, Kaushal, {\em A comparison of two biholomorphic invariants}, Internat.
-J.
-Math.} {\bf 30} (2019), 1950012, 16, DOI 10.1142/S0129167X19500125, \url{https://doi.org/10.1142/S0129167X19500125}.
-\item Maity, Dipendu, {\em Pentagonal maps on the torus and the plane}, Beitr. Algebra Geom.} {\bf 60} (2019), 17--37, DOI 10.1007/s13366-018-0405-7, \url{https://doi.org/10.1007/s13366-018-0405-7}.
-\item Maity, Dipendu and Upadhyay, Ashish Kumar, {\em On centrally symmetric manifolds}, J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.
+K.: Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level, \emph{Biomolecules} {\bf 9} (2019), 77.
+\item Mahajan, Prachi and Verma, Kaushal: A comparison of two biholomorphic invariants, \emph{Internat. J. Math.} {\bf 30} (2019), 1950012, 16.
+\item Maiti, Arun: Quasi-vertex-transitive maps on the plane, \emph{Discrete Math.} {\bf 343} (2020), 111911, 7.
+\item Maitra, Anwoy: On the continuous extension of {K}obayashi isometries, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.
+\item Maitra, Anwoy: A form of {S}chwarz's lemma and a bound for the {K}obayashi
+metric on convex domains, \emph{J. Math. Anal. Appl.} {\bf 484} (2020), 123694, 16.
+\item Maity, Dipendu: Pentagonal maps on the torus and the plane, \emph{Beitr. Algebra Geom.} {\bf 60} (2019), 17--37.
+\item Maity, Dipendu and Upadhyay, Ashish Kumar: On centrally symmetric manifolds, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.
 \item Mal, Arpita and Paul, Kallol and Rao, T. S. S. R. K. and Sain,
-Debmalya, {\em Approximate {B}irkhoff-{J}ames orthogonality and smoothness in
-the space of bounded linear operators}, Monatsh. Math.} {\bf 190} (2019), 549--558, DOI 10.1007/s00605-019-01289-3, \url{https://doi.org/10.1007/s00605-019-01289-3}.
-\item Mal, Arpita and Sain, Debmalya and Paul, Kallol, {\em On some geometric properties of operator spaces}, Banach J.
+Debmalya: Approximate {B}irkhoff-{J}ames orthogonality and smoothness in
+the space of bounded linear operators, \emph{Monatsh. Math.} {\bf 190} (2019), 549--558.
+\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: On some geometric properties of operator spaces, \emph{Banach J. Math. Anal.} {\bf 13} (2019), 174--191.
+\item Manfio, F. and Turgay, N. C. and Upadhyay, A.: Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
+{$\Bbb{H}^n\times\Bbb{R}$}, \emph{J. Geom. Anal.} {\bf 29} (2019), 283--298.
+\item Misra, Gadadhar: Operators in the {C}owen-{D}ouglas class and related topics, \emph{Handbook of analytic operator theory} {\bf } (2019), 87--137.
+\item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian: Contractivity and complete contractivity for finite
+dimensional {B}anach spaces, \emph{J. Operator Theory} {\bf 82} (2019), 23--47.
+\item Misra, Gadadhar and Reza, Md. Ramiz: Curvature inequalities and extremal operators, \emph{Illinois J. Math.} {\bf 63} (2019), 193--217.
+\item Mukherjee, Sajal Kumar and Bera, Sudip: Combinatorial proofs of the {N}ewton-{G}irard and
+{C}hapman-{C}ostas-{S}antos identities, \emph{Discrete Math.} {\bf 342} (2019), 1577--1580.
+\item Nikolov, Nikolai and Verma, Kaushal: On the squeezing function and {F}ridman invariants, \emph{J. Geom. Anal.} {\bf 30} (2020), 1218--1225.
+\item Pal, Chandan and Pradhan, Somnath: Risk sensitive control of pure jump processes on a general
+state space, \emph{Stochastics} {\bf 91} (2019), 155--174.
+\item Paul, Kallol and Sain, Debmalya: Birkhoff-{J}ames orthogonality and its application in the
+study of geometry of {B}anach space, \emph{Advanced topics in mathematical analysis} {\bf } (2019), 245--284.
+\item Paul, Kallol and Sain, Debmalya and Ghosh, Puja: Symmetry of {B}irkhoff-{J}ames orthogonality of bounded linear
+operators, \emph{Ulam type stability} {\bf } (2019), 331--344.
+\item Pingali, Vamsi P.: A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE}, \emph{Complex Var. Elliptic Equ.} {\bf 64} (2019), 503--518.
+\item Pingali, Vamsi Pritham: A vector bundle version of the {M}onge-{A}mp\`ere equation, \emph{Adv. Math.} {\bf 360} (2020), 106921, 40.
+\item Pingali, Vamsi Pritham: Quillen metrics and perturbed equations, \emph{Lett. Math. Phys.} {\bf 110} (2020), 1861--1875.
+\item Poria, Anirudha: Positive weight function and classification of {$g$}-frames, \emph{Numer. Funct. Anal. Optim.} {\bf 41} (2020), 950--968.
+\item Quddus, Safdar: Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
+spheres, \emph{J. Noncommut. Geom.} {\bf 13} (2019), 257--267.
+\item Reddy, Nanda Kishore: Equality of {L}yapunov and stability exponents for products of
+isotropic random matrices, \emph{Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624.
+\item Roth, Julien and Upadhyay, Abhitosh: On compact anisotropic {W}eingarten hypersurfaces in
+{E}uclidean space, \emph{Arch. Math. (Basel)} {\bf 113} (2019), 213--224.
+\item Roth, Julien and Upadhyay, Abhitosh: On almost stable {CMC} hypersurfaces in manifolds of bounded
+sectional curvature, \emph{Bull. Aust. Math. Soc.} {\bf 101} (2020), 333--338.
+\item Roy, Krishanu and Venkatesh, R.: Maximal closed subroot systems of real affine root systems, \emph{Transform. Groups} {\bf 24} (2019), 1261--1308.
+\item Sain, Debmalya: On extreme contractions and the norm attainment set of a
+bounded linear operator, \emph{Ann. Funct. Anal.} {\bf 10} (2019), 135--143.
+\item Sain, Debmalya: On the norm attainment set of a bounded linear operator and
+semi-inner-products in normed spaces, \emph{Indian J. Pure Appl. Math.} {\bf 51} (2020), 179--186.
+\item Sain, Debmalya: Smooth points in operator spaces and some
+{B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces, \emph{Oper. Matrices} {\bf 13} (2019), 433--445.
+\item Sain, Debmalya and Mal, Arpita and Paul, Kallol: Some remarks on {B}irkhoff-{J}ames orthogonality of linear
+operators, \emph{Expo. Math.} {\bf 38} (2020), 138--147.
+\item Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag,
+Santanu: On the numerical index of polyhedral {B}anach spaces, \emph{Linear Algebra Appl.} {\bf 577} (2019), 121--133.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: On approximate {B}irkhoff-{J}ames orthogonality and normal
+cones in a normed space, \emph{J. Convex Anal.} {\bf 26} (2019), 341--351.
+\item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas: On two extremum problems related to the norm of a bounded
+linear operator, \emph{Oper. Matrices} {\bf 13} (2019), 421--432.
+\item Sain, Debmalya and Ray, Anubhab and Paul, Kallol: Extreme contractions on finite-dimensional polygonal {B}anach
+spaces, \emph{J. Convex Anal.} {\bf 26} (2019), 877--885.
+\item Sanki, Bidyut and Gadgil, Siddhartha: Graphs of systoles on hyperbolic surfaces, \emph{J. Topol. Anal.} {\bf 11} (2019), 1--20.
+\item Sarkar, Amar Deep and Verma, Kaushal: Boundary behaviour of some conformal invariants on planar
+domains, \emph{Comput. Methods Funct. Theory} {\bf 20} (2020), 145--158.
+\item Seshadri, Harish: Differential geometry in {I}ndia, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799.
+\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh: On biconservative hypersurfaces in 4-dimensional {R}iemannian
+space forms, \emph{Math. Nachr.} {\bf 292} (2019), 905--921.
+\item Urbina-Romero, Wilfredo: Gaussian harmonic analysis, \emph{} {\bf } (2019), xix+477.
+\item Verma, Kaushal: Notes on the boundaries of quadrature domains, \emph{Anal. Math. Phys.} {\bf 9} (2019), 617--638.
+\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan,
+Govindan: On the role of four-wave mixing effect in the interactions
+between nonlinear modes of coupled generalized nonlinear
+{S}chr\"{o}dinger equation, \emph{Chaos} {\bf 29} (2019), 123135, 14.
+\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, Govindan
+and Lakshmanan, M.: On symmetry preserving and symmetry broken bright, dark and
+antidark soliton solutions of nonlocal nonlinear {S}chr\"{o}dinger
+equation, \emph{Phys. Lett. A} {\bf 383} (2019), 15--26.
+\end{enumerate}
+
+\subsection{Publications (all kinds) from web page with hyperlinks}
+
+\begin{enumerate}
+\item Aas, Erik and Ayyer, Arvind and Linusson, Svante and Potka,
+Samu: \href{https://doi.org/10.1088/1751-8121/ab2e96}{The exact phase diagram for a semipermeable {TASEP} with
+nonlocal boundary jumps}, \emph{J. Phys. A} {\bf 52} (2019), 355001, 19.
+\item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
+Nandakumaran, A. K.: \href{https://doi.org/10.3233/asy-191526}{Control problem on a rough circular domain and homogenization}, \emph{Asymptot. Anal.} {\bf 115} (2019), 19--46.
+\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1142/S0219199719500299}{Semi-linear optimal control problem on a smooth oscillating
+domain}, \emph{Commun. Contemp. Math.} {\bf 22} (2020), 1950029, 26.
+\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1007/s10231-019-00848-7}{Locally periodic unfolding operator for highly oscillating
+rough domains}, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954.
+\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu: \href{https://doi.org/10.1002/mma.5748}{Asymptotic analysis of a boundary optimal control problem on a
+general branched structure}, \emph{Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434.
+\item Aiyappan, S. and Sardar, Bidhan Chandra: \href{https://doi.org/10.1080/00036811.2018.1471207}{Biharmonic equation in a highly oscillating domain and
+homogenization of an associated control problem}, \emph{Appl. Anal.} {\bf 98} (2019), 2783--2801.
+\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish: \href{https://doi.org/10.1007/s00208-018-1749-x}{A gap theorem for positive {E}instein metrics on the
+four-sphere}, \emph{Math. Ann.} {\bf 373} (2019), 1329--1339.
+\item Anamby, Pramath and Das, Soumya: \href{https://doi.org/10.5565/PUBLMAT6311911}{Distinguishing {H}ermitian cusp forms of degree 2 by a certain
+subset of all {F}ourier coefficients}, \emph{Publ. Mat.} {\bf 63} (2019), 307--341.
+\item Anand, Jatin and Bhattacharyya, Tirthankar and Srivastava,
+Sachi: \href{https://doi.org/10.1007/s00013-019-01406-6}{Some thoughts on composition operators on subspaces of the
+{H}ardy space}, \emph{Arch. Math. (Basel)} {\bf 114} (2020), 431--444.
+\item Ayyer, Arvind: \href{https://doi.org/10.1007/s00026-019-00480-5}{Squareness for the {M}onopole-{D}imer model}, \emph{Ann. Comb.} {\bf 24} (2020), 237--255.
+\item Ayyer, Arvind and Behrend, Roger E.: \href{https://doi.org/10.1016/j.jcta.2019.01.001}{Factorization theorems for classical group characters, with
+applications to alternating sign matrices and plane
+partitions}, \emph{J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.
+\item Ayyer, Arvind and Behrend, Roger E. and Fischer, Ilse: \href{https://doi.org/10.1016/j.aim.2020.107125}{Extreme diagonally and antidiagonally symmetric alternating
+sign matrices of odd order}, \emph{Adv. Math.} {\bf 367} (2020), 107125, 56.
+\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar: \href{https://doi.org/10.1007/s10955-018-2183-x}{The phase diagram for a multispecies left-permeable asymmetric
+exclusion process}, \emph{J. Stat. Phys.} {\bf 174} (2019), 605--621.
+\item Ayyer, Arvind and Fischer, Ilse: \href{https://doi.org/10.1016/j.jcta.2020.105241}{Bijective proofs of skew {S}chur polynomial factorizations}, \emph{J.
+Combin.
+Theory Ser.
+A} {\bf 174} (2020), 105241, 40.
+\item Ayyer, Arvind and Linusson, Svante: \href{https://doi.org/10.1002/rsa.20825}{Reverse juggling processes}, \emph{Random Structures Algorithms} {\bf 55} (2019), 56--72.
+\item Ayyer, Arvind and Singla, Pooja: \href{https://doi.org/10.1007/s10468-019-09864-w}{Random motion on finite rings, {I}: commutative rings}, \emph{Algebr.
+Represent.
+Theory} {\bf 23} (2020), 583--604.
+\item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
+Verma, Kaushal: \href{https://doi.org/10.1090/proc/14421}{Remarks on the higher dimensional {S}uita conjecture}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411.
+\item Balhara, Rakesh: \href{https://doi.org/10.1007/s12044-019-0471-2}{Hardy's inequality for the fractional powers of the {G}rushin
+operator}, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25.
+\item Banerjee, Abhishek: \href{https://doi.org/10.4153/s0008439518000656}{On differential torsion theories and rings with several
+objects}, \emph{Canad. Math. Bull.} {\bf 62} (2019), 703--714.
+\item Banerjee, Abhishek and Kour, Surjeet: \href{https://doi.org/10.1007/s10231-019-00844-x}{{$(A,\delta)$}-modules, {H}ochschild homology and higher
+derivations}, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802.
+\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
+and Putinar, Mihai: \href{https://doi.org/10.1016/j.laa.2018.03.035}{Simultaneous kernels of matrix {H}adamard powers}, \emph{Linear Algebra Appl.} {\bf 576} (2019), 142--157.
+\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
+Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
+Morales, Alejandro H.
+and Yip, Martha: \href{https://doi.org/10.1090/tran/7743}{A combinatorial model for computing volumes of flow polytopes}, \emph{Trans.
+Amer.
 Math.
-Anal.} {\bf 13} (2019), 174--191, DOI 10.1215/17358787-2018-0021, \url{https://doi.org/10.1215/17358787-2018-0021}.
-\item Manfio, F. and Turgay, N. C. and Upadhyay, A., {\em Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
-{$\Bbb{H}^n\times\Bbb{R}$}}, J. Geom. Anal.} {\bf 29} (2019), 283--298, DOI 10.1007/s12220-018-9990-9, \url{https://doi.org/10.1007/s12220-018-9990-9}.
-\item Manikandan, K. and Vishnu Priya, N. and Senthilvelan, M. and
-Sankaranarayanan, R., {\em Deformation of dark solitons in a {$\Cal{PT}$}-invariant
-variable coefficients nonlocal nonlinear {S}chr\"{o}dinger
-equation}, Chaos} {\bf 28} (2018), 083103, 12, DOI 10.1063/1.5039901, \url{https://doi.org/10.1063/1.5039901}.
-\item Misra, Gadadhar, {\em Operators in the {C}owen-{D}ouglas class and related topics}, Handbook of analytic operator theory} {\bf } (2019), 87--137.
-\item Misra, Gadadhar and Pal, Avijit, {\em Curvature inequalities for operators in the {C}owen-{D}ouglas
-class and localization of the {W}allach set}, J. Anal. Math.} {\bf 136} (2018), 31--54, DOI 10.1007/s11854-018-0054-7, \url{https://doi.org/10.1007/s11854-018-0054-7}.
-\item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian, {\em Contractivity and complete contractivity for finite
-dimensional {B}anach spaces}, J. Operator Theory} {\bf 82} (2019), 23--47, DOI 10.7900/jot.2018jun13.2225, \url{https://doi.org/10.7900/jot.2018jun13.2225}.
-\item Misra, Gadadhar and Reza, Md.
-Ramiz, {\em Curvature inequalities and extremal operators}, Illinois J.
-Math.} {\bf 63} (2019), 193--217, DOI 10.1215/00192082-7768711, \url{https://doi.org/10.1215/00192082-7768711}.
-\item Mukherjee, Sajal Kumar and Bera, Sudip, {\em Combinatorial proofs of the {N}ewton-{G}irard and
-{C}hapman-{C}ostas-{S}antos identities}, Discrete Math.} {\bf 342} (2019), 1577--1580, DOI 10.1016/j.disc.2019.02.013, \url{https://doi.org/10.1016/j.disc.2019.02.013}.
-\item Narayanan, E. K. and Singla, Pooja, {\em On monomial representations of finitely generated nilpotent
-groups}, Comm. Algebra} {\bf 46} (2018), 2319--2331, DOI 10.1080/00927872.2017.1378894, \url{https://doi.org/10.1080/00927872.2017.1378894}.
-\item Pal, Chandan and Pradhan, Somnath, {\em Risk sensitive control of pure jump processes on a general
-state space}, Stochastics} {\bf 91} (2019), 155--174, DOI 10.1080/17442508.2018.1521413, \url{https://doi.org/10.1080/17442508.2018.1521413}.
-\item Pal, Ratna and Verma, Kaushal, {\em Ergodic properties of families of {H}\'{e}non maps}, Ann.
-Polon.
-Math.} {\bf 121} (2018), 45--71, DOI 10.4064/ap170928-2-4, \url{https://doi.org/10.4064/ap170928-2-4}.
-\item Paul, Kallol and Sain, Debmalya, {\em Birkhoff-{J}ames orthogonality and its application in the
-study of geometry of {B}anach space}, Advanced topics in mathematical analysis} {\bf } (2019), 245--284.
-\item Paul, Kallol and Sain, Debmalya and Ghosh, Puja, {\em Symmetry of {B}irkhoff-{J}ames orthogonality of bounded linear
-operators}, Ulam type stability} {\bf } (2019), 331--344.
-\item Paul, Kallol and Sain, Debmalya and Mal, Arpita, {\em Approximate {B}irkhoff-{J}ames orthogonality in the space of
-bounded linear operators}, Linear Algebra Appl.} {\bf 537} (2018), 348--357, DOI 10.1016/j.laa.2017.10.008, \url{https://doi.org/10.1016/j.laa.2017.10.008}.
-\item Paul, Kallol and Sain, Debmalya and Mal, Arpita and Mandal,
-Kalidas, {\em Orthogonality of bounded linear operators on complex {B}anach
-spaces}, Adv. Oper. Theory} {\bf 3} (2018), 699--709, DOI 10.15352/aot.1712-1268, \url{https://doi.org/10.15352/aot.1712-1268}.
-\item Pingali, Vamsi P., {\em A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE}}, Complex Var.
-Elliptic Equ.} {\bf 64} (2019), 503--518, DOI 10.1080/17476933.2018.1454914, \url{https://doi.org/10.1080/17476933.2018.1454914}.
-\item Pingali, Vamsi Pritham, {\em A note on higher extremal metrics}, Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010, DOI 10.1090/tran/7416, \url{https://doi.org/10.1090/tran/7416}.
-\item Pingali, Vamsi Pritham, {\em Representability of {C}hern-{W}eil forms}, Math. Z.} {\bf 288} (2018), 629--641, DOI 10.1007/s00209-017-1903-2, \url{https://doi.org/10.1007/s00209-017-1903-2}.
-\item Pritham Pingali, Vamsi, {\em Existence of coupled {K}\"{a}hler-{E}instein metrics using the
-continuity method}, Internat. J. Math.} {\bf 29} (2018), 1850041, 8, DOI 10.1142/S0129167X18500416, \url{https://doi.org/10.1142/S0129167X18500416}.
-\item Quddus, Safdar, {\em Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
-spheres}, J. Noncommut. Geom.} {\bf 13} (2019), 257--267, DOI 10.4171/JNCG/320, \url{https://doi.org/10.4171/JNCG/320}.
-\item Reddy, Nanda Kishore, {\em Equality of {L}yapunov and stability exponents for products of
-isotropic random matrices}, Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624, DOI 10.1093/imrn/rnx134, \url{https://doi.org/10.1093/imrn/rnx134}.
-\item Reza, Md. Ramiz, {\em Curvature inequalities for operators in the {C}owen-{D}ouglas
-class of a planar domain}, Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279, DOI 10.1512/iumj.2018.67.7320, \url{https://doi.org/10.1512/iumj.2018.67.7320}.
-\item Roth, Julien and Upadhyay, Abhitosh, {\em On compact anisotropic {W}eingarten hypersurfaces in
-{E}uclidean space}, Arch. Math. (Basel)} {\bf 113} (2019), 213--224, DOI 10.1007/s00013-019-01315-8, \url{https://doi.org/10.1007/s00013-019-01315-8}.
-\item Roy, Krishanu and Venkatesh, R., {\em Maximal closed subroot systems of real affine root systems}, Transform.
-Groups} {\bf 24} (2019), 1261--1308, DOI 10.1007/s00031-018-9510-9, \url{https://doi.org/10.1007/s00031-018-9510-9}.
-\item Sain, Debmalya, {\em On extreme contractions and the norm attainment set of a
-bounded linear operator}, Ann. Funct. Anal.} {\bf 10} (2019), 135--143, DOI 10.1215/20088752-2018-0014, \url{https://doi.org/10.1215/20088752-2018-0014}.
-\item Sain, Debmalya, {\em On the norm attainment set of a bounded linear operator}, J.
+Soc.} {\bf 372} (2019), 3369--3404.
+\item Bera, Sayani and Pal, Ratna and Verma, Kaushal: \href{https://doi.org/10.1007/s40879-019-00326-7}{A rigidity theorem for {H}\'{e}non maps}, \emph{Eur. J. Math.} {\bf 6} (2020), 508--532.
+\item Bharali, Gautam: \href{https://doi.org/10.1007/s12220-019-00342-9}{On the growth of the {B}ergman metric near a point of infinite
+type}, \emph{J. Geom. Anal.} {\bf 30} (2020), 1238--1258.
+\item Bharali, Gautam and Chandel, Vikramjeet Singh: \href{https://doi.org/10.1007/s11785-017-0701-5}{Pick interpolation on the polydisc: small families of
+sufficient kernels}, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093.
+\item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K.: \href{https://doi.org/10.1007/s13226-019-0345-4}{Survey of last ten years of work done in {I}ndia in some
+selected areas of functional analysis and operator theory}, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617.
+\item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
+Sundaram: Hermite multipliers on modulation spaces, \emph{Analysis and partial differential equations: perspectives from
+developing countries} {\bf 275} (2019), 42--64.
+\item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy: Branched projective structures on a {R}iemann surface and
+logarithmic connections, \emph{Doc. Math.} {\bf 24} (2019), 2299--2337.
+\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi: \href{https://doi.org/10.1515/cmam-2018-0020}{Edge patch-wise local projection stabilized nonconforming
+{FEM} for the {O}seen problem}, \emph{Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214.
+\item Biswas, Shibananda and Ghosh, Gargi and Misra, Gadadhar and
+Shyam Roy, Subrata: \href{https://doi.org/10.1016/j.jfa.2018.10.025}{On reducing submodules of {H}ilbert modules with
+{${S}_n$}-invariant kernels}, \emph{J. Funct. Anal.} {\bf 276} (2019), 751--784.
+\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram: \href{https://doi.org/10.3934/cpaa.2019116}{On extension problem, trace {H}ardy and {H}ardy's inequalities
+for some fractional {L}aplacians}, \emph{Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605.
+\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella: \href{https://doi.org/10.1515/cmam-2019-0034}{Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
+indefinite second-order linear elliptic problems}, \emph{Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.
+\item Chakraborty, Atlanta and Chandru, Vijay and Rao, M.
+R.: \href{https://doi.org/10.1007/s10479-019-03186-2}{A linear programming primer: from {F}ourier to {K}armarkar}, \emph{Ann.
+Oper.
+Res.} {\bf 287} (2020), 593--616.
+\item Chandel, Vikramjeet Singh: \href{https://doi.org/10.1007/s12220-018-00123-w}{The 3-point spectral pick interpolation problem and an
+application to holomorphic correspondences}, \emph{J. Geom. Anal.} {\bf 30} (2020), 551--572.
+\item Choudhury, Projesh Nath and Tsatsomeros, Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic detection and construction of {N}-matrices}, \emph{Linear Algebra Appl.} {\bf 602} (2020), 46--56.
+\item Cicuttin, Matteo and Ern, Alexandre and Gudi, Thirupathi: \href{https://doi.org/10.1007/s10915-020-01195-z}{Hybrid high-order methods for the elliptic obstacle problem}, \emph{J.
+Sci.
+Comput.} {\bf 83} (2020), Paper No.
+8, 18.
+\item Das, Soumya and Jha, Abhash Kumar: \href{https://doi.org/10.1007/s12188-019-00206-7}{Analytic properties of twisted real-analytic {H}ermitian
+{K}lingen type {E}isenstein series and applications}, \emph{Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116.
+\item Das, Soumya and Pal, Ritwik: \href{https://doi.org/10.1007/s40993-019-0158-x}{The first negative eigenvalue of {Y}oshida lifts}, \emph{Res. Number Theory} {\bf 5} (2019), Paper No. 20, 9.
+\item Dond, Asha K. and Gudi, Thirupathi: \href{https://doi.org/10.1002/num.22317}{Patch-wise local projection stabilized finite element methods
+for convection-diffusion-reaction problems}, \emph{Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663.
+\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH.: \href{https://doi.org/10.1080/01630563.2018.1538158}{An error analysis of discontinuous finite element methods for
+the optimal control problems governed by {S}tokes equation}, \emph{Numer. Funct. Anal. Optim.} {\bf 40} (2019), 421--460.
+\item Gadgil, Siddhartha: \href{https://doi.org/10.1007/s10817-019-09523-1}{Homogeneous {L}ength {F}unctions on {G}roups: {I}ntertwined
+{C}omputer and {H}uman {P}roofs}, \emph{J. Automat. Reason.} {\bf 64} (2020), 677--688.
+\item Garani, Shayan Srinivasa and Seshadri, Harish: \href{https://doi.org/10.1080/17459737.2019.1604845}{An algorithmic approach to {S}outh {I}ndian classical music}, \emph{J.
+Math.
+Music} {\bf 13} (2019), 107--134.
+\item Gaussier, Herv\'{e} and Seshadri, Harish: \href{https://doi.org/10.1090/proc/14217}{Holomorphic motions and complex geometry}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 301--313.
+\item Ghara, Soumitra and Kumar, Surjit: \href{https://doi.org/10.1016/j.jmaa.2018.09.048}{On the sum of two subnormal kernels}, \emph{J. Math. Anal. Appl.} {\bf 469} (2019), 1015--1027.
+\item Gudi, Thirupathi and Majumder, Papri: \href{https://doi.org/10.1515/cmam-2019-0057}{Crouzeix-{R}aviart finite element approximation for the
+parabolic obstacle problem}, \emph{Comput. Methods Appl. Math.} {\bf 20} (2020), 273--292.
+\item Gudi, Thirupathi and Majumder, Papri: \href{https://doi.org/10.1016/j.cam.2019.02.026}{Convergence analysis of finite element method for a parabolic
+obstacle problem}, \emph{J. Comput. Appl. Math.} {\bf 357} (2019), 85--102.
+\item Gudi, Thirupathi and Majumder, Papri: \href{https://doi.org/10.1016/j.camwa.2019.06.022}{Conforming and discontinuous {G}alerkin {FEM} in space for
+solving parabolic obstacle problem}, \emph{Comput. Math. Appl.} {\bf 78} (2019), 3896--3915.
+\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: \href{https://doi.org/10.1016/j.jmaa.2020.124032}{Unitary equivalence of operator-valued multishifts}, \emph{J.
 Math.
 Anal.
-Appl.} {\bf 457} (2018), 67--76, DOI 10.1016/j.jmaa.2017.07.070, \url{https://doi.org/10.1016/j.jmaa.2017.07.070}.
-\item Sain, Debmalya, {\em Smooth points in operator spaces and some
-{B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces}, Oper. Matrices} {\bf 13} (2019), 433--445, DOI 10.7153/oam-2019-13-32, \url{https://doi.org/10.7153/oam-2019-13-32}.
+Appl.} {\bf 487} (2020), 124032, 23.
+\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: \href{https://doi.org/10.1090/proc/14410}{Von {N}eumann's inequality for commuting operator-valued
+multishifts}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.
+\item Gupta, Subhojoy: \href{https://doi.org/10.1090/tran/7777}{Limits of harmonic maps and crowned hyperbolic surfaces}, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 7573--7596.
+\item Gupta, Subhojoy and Mj, Mahan: \href{https://doi.org/10.1090/proc/14866}{Monodromy representations of meromorphic projective
+structures}, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 2069--2078.
+\item Gupta, Subhojoy and Seshadri, Harish: \href{https://doi.org/10.1093/imrn/rny204}{On domains biholomorphic to {T}eichm\"{u}ller spaces}, \emph{Int.
+Math.
+Res.
+Not.
+IMRN} {\bf } (2020), 2542--2560.
+\item Gupta, Subhojoy and Wolf, Michael: \href{https://doi.org/10.1007/s00208-018-1674-z}{Meromorphic quadratic differentials and measured foliations on
+a {R}iemann surface}, \emph{Math. Ann.} {\bf 373} (2019), 73--118.
+\item Hatui, Sumana: \href{https://doi.org/10.1515/jgth-2019-0045}{Schur multipliers of special {$p$}-groups of rank 2}, \emph{J. Group Theory} {\bf 23} (2020), 85--95.
+\item Hazra, Somnath: \href{https://doi.org/10.1007/s11785-018-0822-5}{Homogeneous 2-shifts}, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.
+\item Jha, Abhash Kumar and Juyal, Abhishek and Pandey, Manish
+Kumar: On simultaneous non-vanishing of twisted {$L$}-functions
+associated to newforms on {$\Gamma_0(N)$}, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.
+\item Jha, Abhash Kumar and Sahu, Brundaban: \href{https://doi.org/10.1142/S1793042119500490}{Rankin-{C}ohen brackets on {J}acobi forms of several variables
+and special values of certain {D}irichlet series}, \emph{Int. J. Number Theory} {\bf 15} (2019), 925--933.
+\item Jha, Abhash Kumar and Sahu, Brundaban: \href{https://doi.org/10.1090/conm/732/14793}{Differential operators on {J}acobi forms and special values of
+certain {D}irichlet series}, \emph{Automorphic forms and related topics} {\bf 732} (2019), 91--99.
+\item Kashyap, G.
+A.
+R.
+S.
+R.
+K.
+and Bapat, D.
+and Das, D.
+and Gowaikar, R.
+D.
+and  Amritkar, R.
+E.
+and Rangarajan, G.
+and V.
+Ravindranath and G.
+Ambika: Synapse loss and progress of Alzheimers disease - A network model, \emph{Scientific Reports} {\bf 9} (2019).
+\item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan: \href{https://doi.org/10.1080/07362994.2018.1538803}{On the convolution of {M}ittag-{L}effler distributions and its
+applications to fractional point processes}, \emph{Stoch. Anal. Appl.} {\bf 37} (2019), 115--122.
+\item Khan, Mohammad Yasir Feroz and Biswas, Rahul and Sau, Ramesh
+Chandra: Instability of {L}agrange interpolation on {$H^1(\Omega)\cap
+C(\overline\Omega)$}, \emph{Math. Student} {\bf 88} (2019), 153--158.
+\item Khare, Apoorva and Tikaradze, Akaki: \href{https://doi.org/10.1016/j.laa.2018.05.035}{A {C}arlitz--von {S}taudt type theorem for finite rings}, \emph{Linear Algebra Appl.} {\bf 568} (2019), 106--126.
+\item Lin, X.
+and Kulkarni, P.
+and Bocci, F.
+and Schafer, N.
+and Roy, S.
+and Tsai, M-Y.
+and He, Y.
+and Chen, Y and Rajagopalan, K.
+and Mooney, S.
+and Zeng, Y.
+and Weninger, K.
+and Grishaev, A.
+and Onuchic, J.
+and Levine, H.
+and Wolynes, P.
+and Salgia, R.
+and Rangarajan, G.
+and Uversky, V.
+and Orban, J.
+and Jolly, M.
+K.: Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level, \emph{Biomolecules} {\bf 9} (2019), 77.
+\item Mahajan, Prachi and Verma, Kaushal: \href{https://doi.org/10.1142/S0129167X19500125}{A comparison of two biholomorphic invariants}, \emph{Internat. J. Math.} {\bf 30} (2019), 1950012, 16.
+\item Maiti, Arun: \href{https://doi.org/10.1016/j.disc.2020.111911}{Quasi-vertex-transitive maps on the plane}, \emph{Discrete Math.} {\bf 343} (2020), 111911, 7.
+\item Maitra, Anwoy: \href{https://doi.org/10.1090/proc/15038}{On the continuous extension of {K}obayashi isometries}, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.
+\item Maitra, Anwoy: \href{https://doi.org/10.1016/j.jmaa.2019.123694}{A form of {S}chwarz's lemma and a bound for the {K}obayashi
+metric on convex domains}, \emph{J. Math. Anal. Appl.} {\bf 484} (2020), 123694, 16.
+\item Maity, Dipendu: \href{https://doi.org/10.1007/s13366-018-0405-7}{Pentagonal maps on the torus and the plane}, \emph{Beitr. Algebra Geom.} {\bf 60} (2019), 17--37.
+\item Maity, Dipendu and Upadhyay, Ashish Kumar: On centrally symmetric manifolds, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.
+\item Mal, Arpita and Paul, Kallol and Rao, T. S. S. R. K. and Sain,
+Debmalya: \href{https://doi.org/10.1007/s00605-019-01289-3}{Approximate {B}irkhoff-{J}ames orthogonality and smoothness in
+the space of bounded linear operators}, \emph{Monatsh. Math.} {\bf 190} (2019), 549--558.
+\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: \href{https://doi.org/10.1215/17358787-2018-0021}{On some geometric properties of operator spaces}, \emph{Banach J.
+Math.
+Anal.} {\bf 13} (2019), 174--191.
+\item Manfio, F. and Turgay, N. C. and Upadhyay, A.: \href{https://doi.org/10.1007/s12220-018-9990-9}{Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
+{$\Bbb{H}^n\times\Bbb{R}$}}, \emph{J. Geom. Anal.} {\bf 29} (2019), 283--298.
+\item Misra, Gadadhar: Operators in the {C}owen-{D}ouglas class and related topics, \emph{Handbook of analytic operator theory} {\bf } (2019), 87--137.
+\item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian: \href{https://doi.org/10.7900/jot.2018jun13.2225}{Contractivity and complete contractivity for finite
+dimensional {B}anach spaces}, \emph{J. Operator Theory} {\bf 82} (2019), 23--47.
+\item Misra, Gadadhar and Reza, Md. Ramiz: \href{https://doi.org/10.1215/00192082-7768711}{Curvature inequalities and extremal operators}, \emph{Illinois J. Math.} {\bf 63} (2019), 193--217.
+\item Mukherjee, Sajal Kumar and Bera, Sudip: \href{https://doi.org/10.1016/j.disc.2019.02.013}{Combinatorial proofs of the {N}ewton-{G}irard and
+{C}hapman-{C}ostas-{S}antos identities}, \emph{Discrete Math.} {\bf 342} (2019), 1577--1580.
+\item Nikolov, Nikolai and Verma, Kaushal: \href{https://doi.org/10.1007/s12220-019-00237-9}{On the squeezing function and {F}ridman invariants}, \emph{J. Geom. Anal.} {\bf 30} (2020), 1218--1225.
+\item Pal, Chandan and Pradhan, Somnath: \href{https://doi.org/10.1080/17442508.2018.1521413}{Risk sensitive control of pure jump processes on a general
+state space}, \emph{Stochastics} {\bf 91} (2019), 155--174.
+\item Paul, Kallol and Sain, Debmalya: Birkhoff-{J}ames orthogonality and its application in the
+study of geometry of {B}anach space, \emph{Advanced topics in mathematical analysis} {\bf } (2019), 245--284.
+\item Paul, Kallol and Sain, Debmalya and Ghosh, Puja: Symmetry of {B}irkhoff-{J}ames orthogonality of bounded linear
+operators, \emph{Ulam type stability} {\bf } (2019), 331--344.
+\item Pingali, Vamsi P.: \href{https://doi.org/10.1080/17476933.2018.1454914}{A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE}}, \emph{Complex Var. Elliptic Equ.} {\bf 64} (2019), 503--518.
+\item Pingali, Vamsi Pritham: \href{https://doi.org/10.1016/j.aim.2019.106921}{A vector bundle version of the {M}onge-{A}mp\`ere equation}, \emph{Adv. Math.} {\bf 360} (2020), 106921, 40.
+\item Pingali, Vamsi Pritham: \href{https://doi.org/10.1007/s11005-020-01279-9}{Quillen metrics and perturbed equations}, \emph{Lett. Math. Phys.} {\bf 110} (2020), 1861--1875.
+\item Poria, Anirudha: \href{https://doi.org/10.1080/01630563.2020.1728771}{Positive weight function and classification of {$g$}-frames}, \emph{Numer. Funct. Anal. Optim.} {\bf 41} (2020), 950--968.
+\item Quddus, Safdar: \href{https://doi.org/10.4171/JNCG/320}{Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
+spheres}, \emph{J. Noncommut. Geom.} {\bf 13} (2019), 257--267.
+\item Reddy, Nanda Kishore: \href{https://doi.org/10.1093/imrn/rnx134}{Equality of {L}yapunov and stability exponents for products of
+isotropic random matrices}, \emph{Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624.
+\item Roth, Julien and Upadhyay, Abhitosh: \href{https://doi.org/10.1007/s00013-019-01315-8}{On compact anisotropic {W}eingarten hypersurfaces in
+{E}uclidean space}, \emph{Arch. Math. (Basel)} {\bf 113} (2019), 213--224.
+\item Roth, Julien and Upadhyay, Abhitosh: \href{https://doi.org/10.1017/s0004972719000935}{On almost stable {CMC} hypersurfaces in manifolds of bounded
+sectional curvature}, \emph{Bull. Aust. Math. Soc.} {\bf 101} (2020), 333--338.
+\item Roy, Krishanu and Venkatesh, R.: \href{https://doi.org/10.1007/s00031-018-9510-9}{Maximal closed subroot systems of real affine root systems}, \emph{Transform.
+Groups} {\bf 24} (2019), 1261--1308.
+\item Sain, Debmalya: \href{https://doi.org/10.1215/20088752-2018-0014}{On extreme contractions and the norm attainment set of a
+bounded linear operator}, \emph{Ann. Funct. Anal.} {\bf 10} (2019), 135--143.
+\item Sain, Debmalya: \href{https://doi.org/10.1007/s13226-020-0393-9}{On the norm attainment set of a bounded linear operator and
+semi-inner-products in normed spaces}, \emph{Indian J. Pure Appl. Math.} {\bf 51} (2020), 179--186.
+\item Sain, Debmalya: \href{https://doi.org/10.7153/oam-2019-13-32}{Smooth points in operator spaces and some
+{B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces}, \emph{Oper. Matrices} {\bf 13} (2019), 433--445.
+\item Sain, Debmalya and Mal, Arpita and Paul, Kallol: \href{https://doi.org/10.1016/j.exmath.2019.01.001}{Some remarks on {B}irkhoff-{J}ames orthogonality of linear
+operators}, \emph{Expo. Math.} {\bf 38} (2020), 138--147.
 \item Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag,
-Santanu, {\em On the numerical index of polyhedral {B}anach spaces}, Linear Algebra Appl.} {\bf 577} (2019), 121--133, DOI 10.1016/j.laa.2019.04.024, \url{https://doi.org/10.1016/j.laa.2019.04.024}.
-\item Sain, Debmalya and Paul, Kallol and Mal, Arpita, {\em A complete characterization of {B}irkhoff-{J}ames
-orthogonality in infinite dimensional normed space}, J. Operator Theory} {\bf 80} (2018), 399--413.
-\item Sain, Debmalya and Paul, Kallol and Mal, Arpita, {\em On approximate {B}irkhoff-{J}ames orthogonality and normal
-cones in a normed space}, J. Convex Anal.} {\bf 26} (2019), 341--351.
-\item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas, {\em On two extremum problems related to the norm of a bounded
-linear operator}, Oper. Matrices} {\bf 13} (2019), 421--432, DOI 10.7153/oam-2019-13-31, \url{https://doi.org/10.7153/oam-2019-13-31}.
-\item Sain, Debmalya and Ray, Anubhab and Paul, Kallol, {\em Extreme contractions on finite-dimensional polygonal {B}anach
-spaces}, J. Convex Anal.} {\bf 26} (2019), 877--885.
-\item Sanki, Bidyut, {\em Filling of closed surfaces}, J. Topol. Anal.} {\bf 10} (2018), 897--913, DOI 10.1142/S1793525318500309, \url{https://doi.org/10.1142/S1793525318500309}.
-\item Sanki, Bidyut and Gadgil, Siddhartha, {\em Graphs of systoles on hyperbolic surfaces}, J.
-Topol.
-Anal.} {\bf 11} (2019), 1--20, DOI 10.1142/S1793525319500018, \url{https://doi.org/10.1142/S1793525319500018}.
-\item Seshadri, Harish, {\em Differential geometry in {I}ndia}, Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799, DOI 10.1007/s13226-019-0355-2, \url{https://doi.org/10.1007/s13226-019-0355-2}.
-\item Seshadri, Harish and Verma, Kaushal, {\em Some aspects of the automorphism groups of domains}, Handbook of group actions. {V}ol. {III}} {\bf 40} (2018), 145--174.
-\item Thangavelu, Sundaram, {\em An analogue of {P}fannschmidt's theorem for the {H}eisenberg
-group}, J. Anal.} {\bf 26} (2018), 235--244, DOI 10.1007/s41478-018-0147-9, \url{https://doi.org/10.1007/s41478-018-0147-9}.
-\item Thangavelu, Sundaram and Naidu Dogga, Venku, {\em {$L^p$}-{$L^2$} estimates for solutions of the wave equation
-associated to the {G}rushin operator}, Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92, DOI 10.1515/apam-2017-0042, \url{https://doi.org/10.1515/apam-2017-0042}.
-\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh, {\em On biconservative hypersurfaces in 4-dimensional {R}iemannian
-space forms}, Math. Nachr.} {\bf 292} (2019), 905--921, DOI 10.1002/mana.201700328, \url{https://doi.org/10.1002/mana.201700328}.
-\item Urbina-Romero, Wilfredo, {\em Gaussian harmonic analysis}, } {\bf } (2019), xix+477, DOI 10.1007/978-3-030-05597-4, \url{https://doi.org/10.1007/978-3-030-05597-4}.
-\item Verma, Kaushal, {\em Notes on the boundaries of quadrature domains}, Anal. Math. Phys.} {\bf 9} (2019), 617--638, DOI 10.1007/s13324-018-0221-0, \url{https://doi.org/10.1007/s13324-018-0221-0}.
+Santanu: \href{https://doi.org/10.1016/j.laa.2019.04.024}{On the numerical index of polyhedral {B}anach spaces}, \emph{Linear Algebra Appl.} {\bf 577} (2019), 121--133.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: On approximate {B}irkhoff-{J}ames orthogonality and normal
+cones in a normed space, \emph{J. Convex Anal.} {\bf 26} (2019), 341--351.
+\item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas: \href{https://doi.org/10.7153/oam-2019-13-31}{On two extremum problems related to the norm of a bounded
+linear operator}, \emph{Oper. Matrices} {\bf 13} (2019), 421--432.
+\item Sain, Debmalya and Ray, Anubhab and Paul, Kallol: Extreme contractions on finite-dimensional polygonal {B}anach
+spaces, \emph{J. Convex Anal.} {\bf 26} (2019), 877--885.
+\item Sanki, Bidyut and Gadgil, Siddhartha: \href{https://doi.org/10.1142/S1793525319500018}{Graphs of systoles on hyperbolic surfaces}, \emph{J. Topol. Anal.} {\bf 11} (2019), 1--20.
+\item Sarkar, Amar Deep and Verma, Kaushal: \href{https://doi.org/10.1007/s40315-020-00303-2}{Boundary behaviour of some conformal invariants on planar
+domains}, \emph{Comput. Methods Funct. Theory} {\bf 20} (2020), 145--158.
+\item Seshadri, Harish: \href{https://doi.org/10.1007/s13226-019-0355-2}{Differential geometry in {I}ndia}, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799.
+\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh: \href{https://doi.org/10.1002/mana.201700328}{On biconservative hypersurfaces in 4-dimensional {R}iemannian
+space forms}, \emph{Math. Nachr.} {\bf 292} (2019), 905--921.
+\item Urbina-Romero, Wilfredo: \href{https://doi.org/10.1007/978-3-030-05597-4}{Gaussian harmonic analysis}, \emph{} {\bf } (2019), xix+477.
+\item Verma, Kaushal: \href{https://doi.org/10.1007/s13324-018-0221-0}{Notes on the boundaries of quadrature domains}, \emph{Anal. Math. Phys.} {\bf 9} (2019), 617--638.
 \item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan,
-Govindan, {\em On the role of four-wave mixing effect in the interactions
+Govindan: \href{https://doi.org/10.1063/1.5121245}{On the role of four-wave mixing effect in the interactions
 between nonlinear modes of coupled generalized nonlinear
-{S}chr\"{o}dinger equation}, Chaos} {\bf 29} (2019), 123135, 14, DOI 10.1063/1.5121245, \url{https://doi.org/10.1063/1.5121245}.
+{S}chr\"{o}dinger equation}, \emph{Chaos} {\bf 29} (2019), 123135, 14.
 \item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, Govindan
-and Lakshmanan, M., {\em On symmetry preserving and symmetry broken bright, dark and
+and Lakshmanan, M.: \href{https://doi.org/10.1016/j.physleta.2018.10.011}{On symmetry preserving and symmetry broken bright, dark and
 antidark soliton solutions of nonlocal nonlinear {S}chr\"{o}dinger
-equation}, Phys. Lett. A} {\bf 383} (2019), 15--26, DOI 10.1016/j.physleta.2018.10.011, \url{https://doi.org/10.1016/j.physleta.2018.10.011}.
+equation}, \emph{Phys. Lett. A} {\bf 383} (2019), 15--26.
 \end{enumerate}

### 2020-08-10 data/draft-sections.tex
hyperlinks with title

@@
 \item Julian D'Costa, IISc did his/her KVPY summer project under the guidance of Siddhartha Gadgil during May, June 2019
+\end{enumerate}
+
+\subsection{List of Visitors to the Department}
+
+\begin{enumerate}
+\item Dr.~Malabika Pramanik, University of British Columbia, Vancouver, Canada, August 2, 2017--August 2, 2017.
+\item Dr.~Jugal Verma, IIT Bombay, September 5, 2017--September 5, 2017.
+\item Dr.~Anirban Basak, Weizmann Institute, Rehovot, Israel, October 5, 2017--October 8, 2017.
+\item Dr.~Neeraj Kayal, Microsoft Research, Bangalore, October 6, 2017--October 6, 2017.
+\item Dr.~Nishant Chandgotia, Tel Aviv University, Israel, October 7, 2017--October 10, 2017.
+\item Dr.~Krishanu Roy, IMSc, Chennai, November 20, 2017--November 24, 2017.
+\item Dr.~Patrice Philippon, CNRS, Paris, France, November 22, 2017--November 22, 2017.
+\item Dr.~Kyoung-Seog Lee, Center for Geometry and Physics, Institute for Basic Science (IBS) Pohang, Republic of Korea, December 4, 2017--December 4, 2017.
+\item Dr.~Ved Datar, University of California, Berkeley, USA, January 3, 2018--January 3, 2018.
+\item Dr.~Moumanti Podder, Georgia Institute of Technology, Atlanta, USA, January 7, 2018--January 12, 2018.
+\item Dr.~Augusto Visintin, Universita' degli Studi di Trento, Italy, January 10, 2018--January 13, 2018.
+\item Dr.~Alexander Bufetov, CNRS, Marseilles, France; and Steklov Mathematical Institute, Moscow, Russia, January 11, 2018--January 20, 2018.
+\item Dr.~Shreedevi K. Masuti, IMSc, Chennai, January 11, 2018--January 11, 2018.
+\item Dr.~Jayadev Athreya, University of Washington, Seattle, USA, January 17, 2018--January 17, 2018.
+\item Dr.~Krishna B. Athreya, Iowa State University, Ames, USA, January 19, 2018--January 19, 2018.
+\item Dr.~Pranav Pandit, IHES, Bures-sur-Yvette, France, January 31, 2018--January 31, 2018.
+\item Dr.~Svante Linusson, KTH, Stockholm, Sweden, February 3, 2018--February 11, 2018.
+\item Dr.~Samu Potka, KTH, Stockholm, Sweden, February 3, 2018--February 11, 2018.
+\item Dr.~Dominique Guillot, University of Delaware, Newark, USA, February 4, 2018--February 16, 2018.
+\item Dr.~Aprameyan Parthasarathy, Universität Paderborn, Germany, March 1, 2018--April 27, 2018.
+\item Dr.~Mahesh Kakde, King's College, London, UK, March 2, 2018--March 2, 2018.
+\item Dr.~Arnab Saha, Australian National University, Canberra, Australia, March 4, 2018--March 10, 2018.
+\item Dr.~Koushik Ramachandran, Oklahoma State University, Stillwater, USA, March 6, 2018--March 7, 2018.
+\item Dr.~Vikas Krishnamurthy, Schrodinger Institute, Vienna, Austria, March 6, 2018--March 6, 2018.
+\item Dr.~Subhajit Goswami, IHES, Bures-sur-Yvette, France, March 19, 2018--March 19, 2018.
+\item Dr.~Sarang Sane, IIT Madras, March 23, 2018--March 23, 2018.
+\item Dr.~Siegfried Böcherer, Universität Mannheim, Germany, March 24, 2018--April 8, 2018.
+\item Dr.~Ananthnarayan Hariharan, IIT Bombay, April 6, 2018--April 7, 2018.
+\item Dr.~C. S. Aravinda, TIFR-CAM, Bangalore, April 6, 2018--April 6, 2018.
+\item Dr.~Bidyut Sanki, IMSc, Chennai, April 24, 2018--April 29, 2018.
+\item Dr.~Satyajit Guin, IISER Mohali, April 25, 2018--April 25, 2018.
+\item Dr.~Prashant Jha, Louisiana State University, Baton Rouge, USA, May 1, 2018--May 1, 2018.
+\item Dr.~Ramesh Kasilingam, ISI Bangalore, May 4, 2018--May 4, 2018.
+\item Dr.~Radhika Ganapathy, TIFR, Mumbai, May 24, 2018--May 24, 2018.
+\item Dr.~Luz Roncal, BCAM, Bilbao, Spain, June 1, 2018--August 31, 2018.
+\item Dr.~Terrence George, Brown University, Providence, USA, June 2, 2018--June 30, 2018.
+\item Dr.~Aprameyan Parthasarathy, Universität Paderborn, Germany, June 3, 2018--June 23, 2018.
+\item Dr.~Sudhir Ghorpade, IIT Bombay, June 4, 2018--June 4, 2018.
+\item Dr.~Yifei Chen, Chinese Academy of Sciences, Beijing, China, June 5, 2018--June 12, 2018.
+\item Dr.~Rajeeva L. Karandikar, CMI, Chennai, June 27, 2018--June 28, 2018.
+\item Dr.~Soumyashant Nayak, University of Pennsylvania, Philadelphia, USA, June 27, 2018--June 27, 2018.
+\item Dr.~M. S. Raghunathan, CBS, Mumbai, June 28, 2018--June 29, 2018.
+\item Dr.~Shubham Sinha, UCSD, San Diego, USA, July 1, 2018--July 30, 2018.
+\item Dr.~Terrence George, Brown University, Providence, USA, July 2, 2018--August 8, 2018.
+\item Dr.~Anand Deopurkar, Australian National University, Canberra, Australia, July 2, 2018--July 4, 2018.
+\item Dr.~Asilata Bapat, Australian National University, Canberra, Australia, July 2, 2018--July 4, 2018.
+\item Dr.~Mizanur Rahaman, University of Waterloo, Canada, July 9, 2018--July 11, 2018.
+\item Dr.~Kunal Datta, INRIA, Sophia-Antipolis, France, July 23, 2018--July 25, 2018.
+\item Dr.~Sumana Hatui, HRI, Allahabad, July 23, 2018--July 23, 2018.
+\item Dr.~Neha Prabhu, Queen's University, Kingston, Canada, July 23, 2018--July 23, 2018.
+\item Dr.~Bhimarthi Ravinder, CMI, Chennai, July 26, 2018--July 27, 2018.
+\item Dr.~Tulasi Ram Reddy, NYU Abu Dhabi, UAE, July 31, 2018--August 12, 2018.
+\item Dr.~Ravi Raghunathan, IIT Bombay, August 3, 2018--August 3, 2018.
+\item Dr.~Jayadev Athreya, University of Washington, Seattle, USA, August 10, 2018--August 10, 2018.
+\item Dr.~Stephan Baier, RKMVU, Belur, August 26, 2018--August 27, 2018.
+\item Dr.~A. Raghuram, IISER Pune, September 24, 2018--September 26, 2018.
+\item Dr.~Bharatram Rangarajan, Hebrew University, Jerusalem, Israel, September 26, 2018--September 26, 2018.
+\item Dr.~Amritanshu Prasad, IMSc, Chennai, September 27, 2018--September 28, 2018.
+\item Dr.~Jean Baptiste Gatsinzi, Botswana University of Science and Technology, Botswana, October 1, 2018--October 31, 2018.
+\item Dr.~Dootika Vats, University of Warwick, UK, October 3, 2018--October 4, 2018.
+\item Dr.~Ashutosh Kumar, NUS, Singapore, October 9, 2018--October 12, 2018.
+\item Dr.~Dhruv Ranganathan, IAS Princeton, MIT Boston (USA); CMI (Chennai); Cambridge (UK), October 29, 2018--November 2, 2018.
+\item Dr.~K. N. Raghavan, IMSc, Chennai, November 9, 2018--November 9, 2018.
+\item Dr.~Daniel Seco, ICMAT, Madrid, Spain, November 13, 2018--November 14, 2018.
+\item Dr.~Purvi Gupta, Rutgers University, New Brunswick, USA, November 18, 2018--November 23, 2018.
+\item Dr.~Anuradha Sharma, IIIT Delhi, December 3, 2018--December 3, 2018.
+\item Dr.~Harald Upmeier, Universität Marburg, Germany, December 4, 2018--February 28, 2019.
+\item Dr.~Sameer Chavan, IIT Kanpur, December 10, 2018--December 13, 2018.
+\item Dr.~Katharina Jochemko, KTH, Stockholm, Sweden, December 11, 2018--December 14, 2018.
+\item Dr.~Alexander Belton, University of Lancaster, UK, December 12, 2018--December 21, 2018.
+\item Dr.~Gopal Srinivasan, IIT Bombay, December 13, 2018--December 13, 2018.
+\item Dr.~Thorsten Heidersdorf, Max Planck Institut, Bonn, Germany, December 18, 2018--December 20, 2018.
+\item Dr.~Rongwei Yang, SUNY Albany, USA, December 19, 2018--December 21, 2018.
+\item Dr.~Prasad Tetali, Georgia Institute of Technology, Atlanta, USA, January 1, 2019--January 1, 2019.
+\item Dr.~T. V. H. Prathamesh, University of Innsbruck, Austria, January 3, 2019--January 4, 2019.
+\item Dr.~Oscar Ciaurri, Universidad de la Rioja, Logronyo, Spain, January 7, 2019--January 25, 2019.
+\item Dr.~Dominique Guillot, University of Delaware, Newark, USA, January 10, 2019--January 17, 2019.
+\item Dr.~Ramesh Gangolli, University of Washington, Seattle, USA, January 13, 2019--January 26, 2019.
+\item Dr.~Sanjay Ramassamy, École Normale Supériure, Paris, France, January 13, 2019--January 26, 2019.
+\item Dr.~Hiroshige Shiga, Tokyo Institute of Technology, Japan, January 17, 2019--January 26, 2019.
+\item Dr.~Pranav Pandit, ICTS Bangalore, January 21, 2019--January 21, 2019.
+\item Dr.~Niranjan Balachandran, IIT Bombay, January 29, 2019--January 30, 2019.
+\item Dr.~Siegfried Böcherer, Universität Mannheim, Germany, January 31, 2019--February 10, 2019.
+\item Dr.~Mohan R., ISI Bangalore, February 8, 2019--February 8, 2019.
+\item Dr.~Nishant Chandgotia, Hebrew University, Jerusalem, Israel, February 11, 2019--February 12, 2019.
+\item Dr.~Arpan Kabiraj, CMI, Chennai, February 11, 2019--February 11, 2019.
+\item Dr.~Nishad Kothari, University of Campinas, São Paulo, Brazil, February 13, 2019--February 13, 2019.
+\item Dr.~James Cann, University College London, UK, February 15, 2019--March 10, 2019.
+\item Dr.~Klas Pettersson, University of Tromsø – The Arctic University of Norway, February 26, 2019--February 26, 2019.
+\item Dr.~Parthanil Roy, ISI Bangalore, March 1, 2019--March 1, 2019.
+\item Dr.~Xavier Viennot, CNRS and LaBRI, France, March 6, 2019--March 9, 2019.
+\item Dr.~Agnid Banerjee, TIFR-CAM, Bangalore, March 8, 2019--March 8, 2019.
+\item Dr.~Ravi A. Rao, TIFR, Mumbai, March 9, 2019--March 15, 2019.
+\item Dr.~Soma Maity, IISER Kolkata, March 10, 2019--March 12, 2019.
+\item Dr.~Agnid Banerjee, TIFR-CAM, Bangalore, March 15, 2019--March 15, 2019.
+\item Dr.~Soumya Bhattachrarya, IISER Kolkata, March 17, 2019--March 23, 2019.
+\item Dr.~Sayan Chakraborty, ISI Kolkata, April 8, 2019--April 8, 2019.
+\item Dr.~Jyotirmoy Ganguly, IISER Pune, April 14, 2019--April 19, 2019.
+\item Dr.~Siegfried Böcherer, Universität Mannheim, Germany, April 22, 2019--April 22, 2019.
+\item Dr.~Indrava Roy, IMSc, Chennai, April 28, 2019--April 30, 2019.
+\item Dr.~Vineeth Chintala, IIT Bombay, May 1, 2019--May 1, 2019.
+\item Dr.~Sankaran Viswanath, IMSc, Chennai, May 3, 2019--May 7, 2019.
+\item Dr.~Amritanshu Prasad, IMSc, Chennai, May 8, 2019--May 8, 2019.
+\item Dr.~Sudipto Choudhury, IIT Bombay, May 20, 2019--May 22, 2019.
+\item Dr.~Siddhartha Sahi, Rutgers University, New Brunswick, USA, June 2, 2019--June 6, 2019.
+\item Dr.~Sanjay P. K., NIT Calicut, June 5, 2019--June 30, 2019.
+\item Dr.~Sanjay Parui, NISER, Bhubaneswar, June 9, 2019--June 24, 2019.
+\item Dr.~Sasmita Patnaik, IIT Kanpur, June 23, 2019--June 28, 2019.
+\item Dr.~Shubham Sinha, UCSD, San Diego, USA, June 24, 2019--July 2, 2019.
+\item Dr.~Subhajit Goswami, IHES, Bures-sur-Yvette, France, July 24, 2019--July 27, 2019.
+\item Dr.~Marc Hubert-Nicole, University of Marseilles, France, July 28, 2019--September 2, 2019.
+\item Dr.~Rakesh, University of Delaware, Newark, USA, August 2, 2019--August 2, 2019.
+\item Dr.~Terrence George, Brown University, Providence, USA, August 7, 2019--August 7, 2019.
+\item Dr.~Akashdeep Dey, Princeton University, Princeton, USA, August 12, 2019--August 16, 2019.
+\item Dr.~Hariharan Narayanan, TIFR, Mumbai, August 14, 2019--August 14, 2019.
+\item Dr.~Piyush Srivastava, TIFR, Mumbai, August 14, 2019--August 14, 2019.
+\item Dr.~Nikhil Srivastava, University of California, Berkeley, USA, August 16, 2019--August 16, 2019.
+\item Dr.~Mahan Mj, TIFR, Mumbai, August 25, 2019--August 31, 2019.
+\item Dr.~T. V. H. Prathamesh, KREA University, Sricity, August 28, 2019--August 30, 2019.
+\item Dr.~Soumyashant Nayak, University of Pennsylvania, Philadelphia, USA, August 28, 2019--August 29, 2019.
+\item Dr.~Soumik Pal, University of Washington, Seattle, USA, August 30, 2019--August 30, 2019.
+\item Dr.~Chandan Dalawat, HRI, Allahabad, September 2, 2019--September 6, 2019.
+\item Dr.~Guhan Venkat, Université Laval, Quebec, Canada; Morningside Center of Mathematics, Beijing, China, September 4, 2019--September 7, 2019.
+\item Dr.~Senthil Raani, IISER Berhampur, September 6, 2019--September 11, 2019.
+\item Dr.~Jean-Marie de Koninck, Université Laval, Quebec, Canada, September 11, 2019--September 13, 2019.
+\item Dr.~Rekha Biswal, Max Planck Institut, Bonn, Germany, September 13, 2019--September 17, 2019.
+\item Dr.~Prasad Tetali, Georgia Institute of Technology, Atlanta, USA, September 13, 2019--September 13, 2019.
+\item Dr.~Kartick Adhikari, Technion, Haifa, Israel, September 15, 2019--September 20, 2019.
+\item Dr.~Martin Kreuzer, Universität Passau, Germany, September 16, 2019--October 1, 2019.
+\item Dr.~Anantha Padmanabha, IMSc, Chennai, September 18, 2019--September 20, 2019.
+\item Dr.~Santosh Nadimpalli, Radboud University, Nijmegen, Netherlands, September 19, 2019--September 21, 2019.
+\item Dr.~Divyang Bhimani, TIFR-CAM, Bangalore, September 20, 2019--September 20, 2019.
+\item Dr.~Sushmita Venugopalan, IMSc, Chennai, September 21, 2019--September 29, 2019.
+\item Dr.~Rajeeva L. Karandikar, CMI, Chennai, September 27, 2019--September 27, 2019.
+\item Dr.~Gianluca Faraco, TIFR, Mumbai, October 7, 2019--October 10, 2019.
+\item Dr.~Atul Dixit, IIT Gandhinagar, October 9, 2019--October 11, 2019.
+\item Dr.~Aswin Balasubramanian, Rutgers University, New Brunswick, USA, October 14, 2019--October 14, 2019.
+\item Dr.~Uri Onn, Australian National University, Canberra, Australia, October 23, 2019--October 30, 2019.
+\item Dr.~Souvik Pal, HRI, Allahabad, October 24, 2019--November 2, 2019.
+\item Dr.~Sorin Dumitrescu, Université Côte d'Azur, Nice, October 26, 2019--October 30, 2019.
+\item Dr.~Indranil Biswas, TIFR Mumbai, October 26, 2019--October 30, 2019.
+\item Dr.~Ramesh Manna, TIFR-CAM, Bangalore, October 30, 2019--October 30, 2019.
+\item Dr.~Tathagata Basak, Iowa State University, Ames, USA, November 4, 2019--November 4, 2019.
+\item Dr.~Apratim Chakraborty, ISI Bangalore, November 4, 2019--November 4, 2019.
+\item Dr.~Chandrasheel Bhagwat, IISER Pune, November 6, 2019--November 6, 2019.
+\item Dr.~Klas Pettersson, UiT – The Arctic University of Norway, Narvik, Norway, November 6, 2019--November 6, 2019.
+\item Dr.~Harald Upmeier, Universität Marburg, Germany, November 7, 2019--March 15, 2020.
+\item Dr.~Uri Onn, Australian National University, Canberra, Australia, November 8, 2019--November 9, 2019.
+\item Dr.~Bernhard Heim, German University of Technology, Oman, November 14, 2019--November 14, 2019.
+\item Dr.~Luz Roncal, BCAM, Bilbao, Spain, November 21, 2019--December 7, 2019.
+\item Dr.~Sugata Mondal, TIFR, Mumbai, November 21, 2019--November 21, 2019.
+\item Dr.~Pavol Hell, Simon Fraser University, Canada, November 22, 2019--November 22, 2019.
+\item Dr.~Gianluca Faraco, TIFR, Mumbai, November 26, 2019--December 4, 2019.
+\item Dr.~Indranath Sengupta, IIT Gandhinagar, November 27, 2019--November 29, 2019.
+\item Dr.~Vyjayanthi Chari, University of California, Riverside, USA, December 1, 2019--December 31, 2019.
+\item Dr.~John Meakin, University of Nebraska, Lincoln, USA, December 3, 2019--December 4, 2019.
+\item Dr.~Anne Schilling, University of California, Davis, USA, December 14, 2019--December 16, 2019.
+\item Dr.~Amritanshu Prasad, IMSc, Chennai, December 14, 2019--December 16, 2019.
+\item Dr.~Sankaran Viswanath, IMSc, Chennai, December 14, 2019--December 16, 2019.
+\item Dr.~K. N. Raghavan, IMSc, Chennai, December 14, 2019--December 16, 2019.
+\item Dr.~Tanushree Khandai, IISER Mohali, December 14, 2019--December 16, 2019.
+\item Dr.~Bhimarthi Ravinder, IIT Tirupati, December 14, 2019--December 16, 2019.
+\item Dr.~Sachin Sharma, IIT Kanpur, December 14, 2019--December 16, 2019.
+\item Dr.~Sunil Chhita, Durham University, December 16, 2019--December 19, 2019.
+\item Dr.~Ken Ono, University of Virginia, Charlottesville, USA, December 18, 2019--December 18, 2019.
+\item Dr.~Sujatha Ramdorai, University of British Columbia, Vancouver, Canada, December 20, 2019--December 20, 2019.
+\item Dr.~Akshaa Vatwani, IIT, Gandhinagar, February 26, 2020--February 26, 2020.
+\item Dr.~Arijit Chakrabarty, ISI, Kolkata, February 26, 2020--.
+\item Dr.~Debapratim Banerjee, ISI, Kolkata, March 9, 2020--March 11, 2020.
 \end{enumerate}

### 2020-08-10 data/reports.tex
hyperlinks with title

@@
 
-In a joint work with Pritam Ganguly  we have investigated the $ L^p $  boundedness of the lacunary maximal function $ M_{\H^n}^\lac $ associated to the spherical means $ A_r f$  taken over Koranyi spheres on the Heisenberg group.
+In a joint work with Pritam Ganguly  we have investigated the $ L^p $  boundedness of the lacunary maximal function $ M_{\mathbb{H}^n}^l $ associated to the spherical means $ A_r f$  taken over Koranyi spheres on the Heisenberg group.
 Closely following an approach used by M.

### 2020-08-10 ugc/src/Data.scala

@@ -31,10 +31,10 @@ object Data {
     .map(pad(_))
 
   lazy val visitorData = os.read
-    .lines(os.resource / "ugc2020.tsv")
+    .lines(os.resource / "visitors.tsv")
     .toVector
     .tail
-    .map(_.split("\t").toVector.tail.map(_.trim))
+    .map(_.split("\t").toVector.map(_.trim))
     .map(pad(_, 5))
 
   lazy val summerStudents = data.flatMap(
@@ -69,6 +69,12 @@ object Data {
 \\begin{enumerate}
 ${summerStudents.map(s => "\\item " + s).mkString("\n")}
 \\end{enumerate}
+
+
+\\subsection{List of Visitors to the Department}
+
+${enumString(visitors)}
+
 """
   lazy val facultyData: Vector[FacultyData] =
     data.map(l => FacultyData.get(l)).sortBy(_.name)
@@ -165,6 +171,30 @@ ${enumString(other)}
     )
     .map(_.tex))
 
+  lazy val papersLinked = facultyData
+    .flatMap(f => f.papers)
+    .filter(
+      p => Set("Published", "Accepted for publication").contains(p.status)
+    )
+    .map(_.tex) ++ (postDocData
+    .flatMap(f => f.papers)
+    .filter(
+      p => Set("Published", "Accepted for publication").contains(p.status)
+    )
+    .map(_.texLinked))
+
+  lazy val preprintsLinked = facultyData
+    .flatMap(f => f.papers)
+    .filter(
+      p => Set("Preprint", "Submitted").contains(p.status)
+    )
+    .map(_.tex) ++ (postDocData
+    .flatMap(f => f.papers)
+    .filter(
+      p => Set("Preprint", "Submitted").contains(p.status)
+    )
+    .map(_.texLinked))
+
   lazy val confPapers = facultyData.flatMap(f => f.confs.map(_.tex)) ++ postDocData
     .flatMap(f => f.confs.map(_.tex))
 
@@ -180,9 +210,11 @@ ${enumString(other)}
     s"""
 \\subsection{Papers in Journals}
 
-\\begin{enumerate}
-${papers.mkString("\n")}
-\\end{enumerate}
+${enumString(papers)}
+
+\\subsection{Papers in Journals with links}
+
+${enumString(papersLinked)}
 
 \\subsection{Papers in Conference proceedings}
 
@@ -198,21 +230,25 @@ ${enumString(bookChapters)}
 
 \\subsection{Preprints}
 
[…]

### 2020-08-10 ugc/src/Publications.scala

@@ -17,7 +17,7 @@ object Publications {
       case (k, v) => k.getValue.toLowerCase -> v.toUserString
     })
     .toVector
-    .filter(m => Set("2018", "2019").contains(m("year")))
+    .filter(m => Set("2019", "2020").contains(m("year")))
 
   import net.jcazevedo.moultingyaml._
   import net.jcazevedo.moultingyaml.DefaultYamlProtocol._
@@ -40,7 +40,7 @@ object Publications {
       .filter(m => Set("2019", "2020").contains(m("year"))))
     .sortBy(m => m("author"))
 
-  def tex(m: Map[String, String]) = {
+  def texPair(m: Map[String, String]) = {
     val author = m("author")
     val title = m("title")
     val journal = m.get("journal").orElse(m.get("booktitle")).getOrElse("")
@@ -51,9 +51,11 @@ object Publications {
     val urlOpt = m.get("url")
     val doiText = doiOpt.map(s =>s", DOI $s").getOrElse("")
     val urlText = urlOpt.map(s => s", \\url{$s}").getOrElse("")
-    s"\\item $author: $title, \\emph{$journal} {\\bf $volume} ($year)${preComma(pages)}$doiText$urlText."
+    val titleString = urlOpt.map(url =>  s"\\href{$url}{$title}").getOrElse(title)
+    (s"\\item $author: $title, \\emph{$journal} {\\bf $volume} ($year)${preComma(pages)}.",
+    s"\\item $author: $titleString, \\emph{$journal} {\\bf $volume} ($year)${preComma(pages)}.")
   }
 
-  lazy val pubItems = allPubs.map(tex)
+  lazy val pubItems = allPubs.map(texPair)
 
 }

### 2020-08-10 data/draft-publications.tex
improvements for next year

@@
 Banerjee: Spectra as universal objects in categories of supports in {\em Banach Center Publications(Quantum Dynamics Proceedings)} Ludwik Dabrowski, Ryszard Nest, Adam Skalski (ed.) , Banach Center Publications , IMPAN, Warsaw, Poland (2020), (accepted).
-\item IMPAN, Warsaw, Poland: 2020 in {\em (accepted)} No (ed.)   ().
 \item S.
@@
 (ed.) , Operator Theory: Advances and Applications , Birkhauser (2020).
-\item Birkhauser: 2020 in {\em } Yes (ed.) , Gadadhar Misra , Decomposition of the tensor product of two Hilbert modules (Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G.
-Douglas Memorial Volume), R.
+\item Gadadhar Misra: Decomposition of the tensor product of two Hilbert modules in {\em Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G.
+Douglas Memorial Volume} R.
 Curto, W.
@@
 Yang, G.
-Yu.
-\item Decomposition of the tensor product of two Hilbert modules: Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G.
-Douglas Memorial Volume in {\em R.
-Curto, W.
-Helton, H.
-Lin, X.
-Tang, R.
-Yang, G.
-Yu} Operator Theory: Advances and Applications (ed.) , Birkhauser , 2020 (), No.
-\item 2020:  in {\em No}  (ed.)   ().
+Yu (ed.) , Operator Theory: Advances and Applications , Birkhauser (2020).
 \end{enumerate}

### 2020-08-10 data/publications_2018-20.tex
improvements for next year

\subsubsection{\!\!\!{\sl Publications}}

\subsubsection*{{\small $(i)$ {\sc Research Papers in Refereed Journals}}}
\medskip

\begin{center}
	\begin{longtable}{|c|c|c|c|}

		\hline
		                    &                   &                   &                            \\[-4mm]
		{\bf Year}          & {\bf Thrust Area} & {\bf Other Areas} & {\bf Total}                \\[.4mm]\hline
		\endfirsthead

		\hline
		                    &                   &                   &                            \\[-4mm]
		{\bf Year}          & {\bf Thrust Area} & {\bf Other Areas} & {\bf Total} \hspace{1.1cm} \\[.4mm]\hline
		\endhead

		                    &                   &                   &                            \\[-4mm]
		{\em 2018--19}      & 72                & 34                & 106                        \\[.4mm]\hline
		                    &                   &                   &                            \\[-4mm]
		{\em Accepted for}  & 13                & 7                 & 20                         \\
		{\em publication}   &                   &                   &                            \\[0.4mm]\hline
		                    &                   &                   &                            \\[-4mm]
		{\em Submitted} for & 17                & 12                & 29                         \\
		{\em Publication}   &                   &                   &                            \\[0.4mm]\hline
		                    &                   &                   &                            \\[-4mm]
		{\bf Total}         & {\bf 102}         & {\bf 53}          & {\bf 155}                  \\[0.4mm]\hline
	\end{longtable}
\end{center}

\noindent{{\small $(i\text{-}a)$ {\sc Published in the period under review}}}
\medskip

%% YEAR 1 LISTING %%%%%
\noindent{{\small {\bf April 2018--March 2019:}}}
\medskip

\noindent{{\small {\sl In the identified thrust area:}}}\vspace{-2.5mm}
\begin{enumerate}[leftmargin=27pt]

	\item Aiyappan, S. and Nandakumaran, A.K. and Prakash, Ravi: Generalization of unfolding operator for highly oscillating
	      smooth boundary domains and homogenization, {\em Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art.~86, 30.

	\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish: A gap theorem for positive {E}instein metrics on the
	      four-sphere, {\em Math. Ann.} {\bf 373} (2019), 1329--1339.

	\item\label{ayyer:exclusion-process} Ayyer, A. and Finn, C. and Roy, D.: Matrix product solution of a left-permeable two-species asymmetric exclusion process, {\em Physical Review E} {\bf 97} (2018), 5225.

	\item\label{ayyer:multispecies-juggling} Ayyer, Arvind and Bouttier, J\'{e}r\'{e}mie and Corteel, Sylvie and
	      Linusson, Svante and Nunzi, Fran\c{c}ois: Bumping sequences and multispecies juggling, {\em Adv. in Appl. Math.} {\bf 98} (2018), 100--126.

	\item   Ayyer, Arvind and Finn, Caley and Roy, Dipankar: The phase diagram for a multispecies left-permeable asymmetric
	      exclusion process, {\em J. Stat. Phys.} {\bf 174} (2019), 605--621.

	\item\label{ayyer:Hilbert-Galton} Ayyer, Arvind and Ramassamy, Sanjay: The {H}ilbert--{G}alton board, {\em ALEA Lat. Am. J. Probab. Math. Stat.} {\bf 15} (2018), 755--774.

	\item Bagchi, Sayan and  Thangavelu, Sundaram: Weighted norm inequalities for {W}eyl multipliers and Fourier multipliers on the {H}eisenberg group, {\em J. Anal. Math.} {\bf 136} (2018), 1--29.

	\item Baklouti, Ali and Thangavelu, Sundaram: Hardy and {M}iyachi theorems for {H}eisenberg motion groups, {\em Nagoya Math. J.} {\bf 229} (2018), 1--20.

	\item Balhara, Rakesh: Hardy's inequality for the fractional powers of the {G}rushin
	      operator, {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art.~33, 25.

	\item\label{ghosh:political-business-cycle} Basak, G. K. and Ghosh, M. K. and Mukherjee, D.: A stochastic model with inflation,
	      growth and technology for the political business cycle, {\em Journal of Computational Economics} {\bf 53} (2019), 125-140.

	\item Basu, Arnab and Ghosh, Mrinal K.: Nonzero-sum risk-sensitive stochastic games on a countable
	      state space, {\em Math. Oper. Res.} {\bf 43} (2018), 516--532.

	\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
	      and Putinar, Mihai: Simultaneous kernels of matrix {H}adamard powers, {\em Linear Algebra Appl.} {\bf 576} (2019), 142--157.

	\item Bera, Sayani and Verma, Kaushal: Some aspects of shift-like automorphisms of {$\mathbb C^k$},
	      {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 128} (2018), Art.~10, 48.

	\item Bhattacharyya, Tirthankar and Sau, Haripada: Holomorphic functions on the symmetrized
	      bidisk\,---\,realization, interpolation and extension, {\em J. Funct. Anal.} {\bf 274} (2018), 504--524.

	\item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
	      Sundaram: Hermite multipliers on modulation spaces, {\em Analysis and partial differential equations:
			      perspectives from developing countries} {\bf 275} (2019), 42--64.

	\item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and Pingali, Vamsi P.: Rational cuspidal
	      curves on del-{P}ezzo surfaces, {\em J. Singul.} {\bf 17} (2018), 91--107.

	\item Biswas, Indranil and Pingali, Vamsi Pritham: A characterization of finite vector bundles on
		      {G}auduchon astheno-{K}\"{a}hler manifolds, {\em \'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art.~6, 13.

	\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi: Edge patch-wise local projection stabilized nonconforming
		      {FEM} for the {O}seen problem, {\em Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214.

	\item\label{Misra:symm-polydisc} Biswas, Shibananda and Ghosh, Gargi and Misra, Gadadhar and
	      Shyam Roy, Subrata: On reducing submodules
	      of {H}ilbert modules with {${S}_n$}-invariant kernels, {\em J. Funct. Anal.} {\bf 276} (2019), 751--784.

	\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal: Comments on the {G}reen's function of a
	      planar domain, {\em Anal. Math. Phys.} {\bf 8} (2018), 383--414.

	\item Brenner, Susanne C. and Gudi, Thirupathi and Porwal, Kamana
	      and Sung, Li-Yeng: A {M}orley finite element method for an elliptic distributed
	      optimal control problem with pointwise state and control
	      constraints, {\em ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206.

	\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella: Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
	      indefinite second-order linear elliptic problems, {\em Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.

	\item Chandel, Vikramjeet Singh: The three-point {P}ick--{N}evanlinna interpolation problem on
	      the polydisc, {\em Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352.

	\item\label{rangarajan:Granger-causality} Chopra, R. and Murthy, C. R. and Rangarajan, G.: Statistical tests for detecting Granger causality, {\em IEEE Transactions on Signal Processing} {\bf } (2018), 5803--5816.

	\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram: Hardy-type inequalities for fractional powers
	      of the {D}unkl-{H}ermite operator, {\em Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544.

	\item Dond, Asha K. and Gudi, Thirupathi: Patch-wise local projection stabilized finite element methods
	      for convection-diffusion-reaction problems, {\em Numer. Methods Partial Differential Equations}
		      {\bf 35} (2019), 638--663.

	\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh Ch.: An error analysis of discontinuous finite element
	      methods for the optimal control problems governed by {S}tokes equation, {\em Numer. Funct. Anal. Optim.}
		      {\bf 40} (2019), 421--460.

	\item Gaddam, Sharat and Gudi, Thirupathi: Inhomogeneous {D}irichlet boundary condition in the {\it a
			      posteriori} error control of the obstacle problem, {\em Comput. Math. Appl.} {\bf 75} (2018), 2311--2327.

	\item Gaddam, Sharat and Gudi, Thirupathi: Bubbles enriched quadratic finite element method for the
	      3{D}-elliptic obstacle problem, {\em Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236.

	\item Gaussier, Herv\'{e} and Seshadri, Harish: Holomorphic motions and complex geometry,
	      {\em Proc. Amer. Math. Soc.} {\bf 147} (2019), 301--313.

	\item Gaussier, Herv\'{e} and Seshadri, Harish, On the {G}romov hyperbolicity of convex domains in {$\mathbb
				      C^n$}, {\em Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641.

	\item Ghara, Soumitra and Kumar, Surjit: On the sum of two subnormal kernels, {\em J. Math. Anal. Appl.}
		      {\bf 469} (2019), 1015--1027.

	\item Ghara, Soumitra: The orbit of a bounded operator under the M{\"o}bius group modulo similarity equivalence.

	\item Ghosh, Mrinal K. and Pradhan, Somnath: Risk-sensitive stochastic differential games with reflecting
	      diffusions, {\em Stoch. Anal. Appl.} {\bf 36} (2018), 1--27.

	\item Gudi, Thirupathi and Majumder, Papri: Convergence analysis of finite element method for a parabolic
	      obstacle problem, {\em J. Comput. Appl. Math.} {\bf 357} (2019), 85--102.

	\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: Von {N}eumann's inequality for commuting
	      operator-valued multishifts, {\em Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.

	\item Gupta, Rajeev and Ramiz Reza, Md.: Operator space structures on {$\ell^1(n)$}, {\em Houston J. Math.}
		      {\bf 44} (2018), 1205--1212.

	\item Hazra, Somnath: Homogeneous 2-shifts, {\em Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.

	\item\label{iyer:connection-model} Iyer, Srikanth K.: The random connection model: connectivity, edge lengths,
	      and degree distributions, {\em Random Structures Algorithms} {\bf 52} (2018), 283--300.

	\item Kashyap, G. and Bapat, D. and Das, D. and Gowaikar, R.D. and  Amritkar, R.E. and Rangarajan, G. and V. Ravindranath and G. Ambika: Synapse loss and progress of Alzheimer's disease\,--\,A network model,
	      {\em Scientific Reports} {\bf 9} (2019).

	\item Khare, Apoorva and Tao, Terence: Schur polynomials, entrywise positivity preservers, and weak
	      majorization, {\em S\'em. Lothar. Combin.} {\bf 80B,} (2018).

	\item Lin, X. and Kulkarni, P. and Bocci, F. and Schafer, N. and Roy, S. and Tsai, M-Y. and He, Y. and Chen, Y and Rajagopalan, K. and Mooney, S. and Zeng, Y. and Weninger, K. and Grishaev, A. and Onuchic, J. and Levine, H. and Wolynes, P. and Salgia, R. and Rangarajan, G. and Uversky, V. and Orban, J. and Jolly, M. K.: Structural and
	      dynamical order of a disordered protein: molecular insights into conformational
	      switching of PAGE4 at the systems level, {\em Biomolecules} {\bf 9} (2019), 77.

	\item\label{rangarajan:prostate-cancer} Lin, X. and Roy, S. and Jolly, M. K. and Bocci, F. and Schafer, N. P. and Tsai, M.-Y. and Chen, Y. and He, Y. and Grishaev, A. and Weninger, K. and Orban, J. and Kulkarni, P. and Rangarajan, G. and Levine, H. and J. N. Onuchic: PAGE4 and conformational switching: Insights from molecular dynamics simulations and implications for
	      prostate cancer, {\em Journal of Molecular Biology} {\bf 430} (2018), 2422--2438.

	\item Mahajan, Prachi and Verma, Kaushal: A comparison of two biholomorphic invariants, {\em Internat. J. Math.} {\bf 30} (2019), 1950012, 16 pp.

	\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: On some geometric properties of operator spaces, {\em Banach J. Math. Anal.} {\bf 13} (2019), 174--191.

	\item Manfio, F. and Turgay, N. C. and Upadhyay, A.: Biconservative submanifolds in
		      {$\mathbb{S}^n\times\mathbb{R}$} and
		      {$\mathbb{H}^n\times\mathbb{R}$}, {\em J. Geom. Anal.} {\bf 29} (2019), 283--298.

	\item Manikandan, K. and Vishnu Priya, N. and Senthilvelan, M. and
	      Sankaranarayanan, R.: Deformation of dark solitons in a {$\mathcal{PT}$}-invariant
	      variable coefficients nonlocal nonlinear {S}chr\"{o}dinger
	      equation, {\em Chaos} {\bf 28} (2018), 083103, 12.

	\item Misra, Gadadhar and Pal, Avijit: Curvature inequalities for operators in the {C}owen--{D}ouglas
	      class and localization of the {W}allach set, {\em J. Anal. Math.} {\bf 136} (2018), 31--54.

	\item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian: Contractivity and complete contractivity for finite dimensional Banach spaces, {\em J. Operator Theory} {\bf 82} (2019), 23--47.

	\item Pal, Chandan and Pradhan, Somnath: Risk sensitive control of pure jump processes on a general
	      state space, {\em Stochastics} {\bf 91} (2019), 155--174.

	\item Pal, Ratna and Verma, Kaushal: Ergodic properties of families of {H}\'{e}non maps, {\em Ann. Polon. Math.}
		      {\bf 121} (2018), 45--71.

	\item Paul, Kallol and Sain, Debmalya: Birkhoff--{J}ames orthogonality and its application in the
	      study of geometry of {B}anach space, {\em Advanced topics in mathematical analysis} {\bf } (2019), 245--284.

	\item Paul, Kallol and Sain, Debmalya and Mal, Arpita: Approximate {B}irkhoff--{J}ames orthogonality in the space of
	      bounded linear operators, {\em Linear Algebra Appl.} {\bf 537} (2018), 348--357.

	\item Paul, Kallol and Sain, Debmalya and Mal, Arpita and Mandal,
	      Kalidas: Orthogonality of bounded linear operators on complex {B}anach
	      spaces, {\em Adv. Oper. Theory} {\bf 3} (2018), 699--709.

	\item Pingali, Vamsi P.: A note on the deformed {H}ermitian {Y}ang--{M}ills {PDE}, {\em Complex Var. Elliptic Equ.}
		      {\bf 64} (2019), 503--518.

	\item Pingali, Vamsi Pritham: A note on higher extremal metrics, {\em Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010.

	\item Pingali, Vamsi Pritham: Representability of {C}hern--{W}eil forms, {\em Math. Z.} {\bf 288} (2018), 629--641.

	\item Pritham Pingali, Vamsi: Existence of coupled {K}\"{a}hler--{E}instein metrics using the
	      continuity method, {\em Internat. J. Math.} {\bf 29} (2018), 1850041, 8.

	\item Reddy, Nanda Kishore: Equality of {L}yapunov and stability exponents for products of
	      isotropic random matrices, {\em Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624.

	\item Reza, Md. Ramiz: Curvature inequalities for operators in the {C}owen--{D}ouglas
	      class of a planar domain, {\em Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279.

	\item Sain, Debmalya: On extreme contractions and the norm attainment set of a
	      bounded linear operator, {\em Ann. Funct. Anal.} {\bf 10} (2019), 135--143.

	\item Sain, Debmalya: On the norm attainment set of a bounded linear operator, {\em J. Math. Anal. Appl.} {\bf 457} (2018), 67--76.

	\item Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag,
	      Santanu: On the numerical index of polyhedral {B}anach spaces, {\em Linear Algebra Appl.} {\bf 577} (2019), 121--133.

	\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: A complete characterization of {B}irkhoff--{J}ames
	      orthogonality in infinite dimensional normed space, {\em J. Operator Theory} {\bf 80} (2018), 399--413.

	\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: On approximate {B}irkhoff--{J}ames orthogonality and normal
	      cones in a normed space, {\em J. Convex Anal.} {\bf 26} (2019), 341--351.

	\item\label{rangarajan:microtremor-method} Sant, D.A. and Parvez, I. A. and Rangarajan, G. and Patel, S. J. and Salam, T. A. S. and Bhatt, M. N.: Subsurface imaging of brown coal bearing Tertiary sedimentaries\,---\,Deccan Trap
	      interface using microtremor method, {\em Journal of Applied Geophysics} {\bf 159} (2018), 362--373.

	\item Seshadri, Harish and Verma, Kaushal: Some aspects of the automorphism groups of domains {\em Handbook of group actions, {V}ol.~{III}} {\bf 40} (2018), 145--174.

	\item Thangavelu, Sundaram: An analogue of {P}fannschmidt's theorem for the {H}eisenberg
	      group, {\em J. Anal.} {\bf 26} (2018), 235--244.

	\item Thangavelu, Sundaram and Naidu Dogga, Venku: {$L^p$}-{$L^2$} estimates for solutions of the wave equation
	      associated to the {G}rushin operator, {\em Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92.

	\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh: On biconservative hypersurfaces in 4-dimensional {R}iemannian
	      space forms, {\em Math. Nachr.} {\bf 292} (2019), 905--921.

	\item Verma, Kaushal: Notes on the boundaries of quadrature domains, {\em Anal. Math. Phys.} {\bf 9} (2019), 617--638.

	\item Vishnu Priya, N. and Senthilvelan, M. and  Rangarajan, Govindan
	      and Lakshmanan, M.: On symmetry preserving and symmetry broken bright, dark and
	      antidark soliton solutions of nonlocal nonlinear {S}chr\"{o}dinger
	      equation, {\em Phys. Lett. A} {\bf 383} (2019), 15--26.
\end{enumerate}

\noindent{{\small {\sl In other areas:}}}\vspace{-2.5mm}

\begin{enumerate}[resume, leftmargin=27pt]
	\item Anamby, Pramath and Das, Soumya: Distinguishing {H}ermitian cusp forms of degree 2 by
	      a certain subset of all {F}ourier coefficients, {\em Publ. Mat.} {\bf 63} (2019), 307--341.

	\item Anamby, Pramath and Das, Soumya: Bounds for the {P}etersson norms of the pullbacks of
		      {S}aito-{K}urokawa lifts, {\em J. Number Theory} {\bf 191} (2018), 289--304.

	\item Arunkumar, G. and Kus, Deniz and Venkatesh, R.: Root multiplicities for {B}orcherds
	      algebras and graph coloring, {\em J. Algebra} {\bf 499} (2018), 538--569.

	\item\label{ayyer:plane-partitions} Ayyer, Arvind and Behrend, Roger E.: Factorization theorems for classical group characters,
	      with applications to alternating sign matrices and plane
	      partitions, {\em J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.

	\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven: Odd partitions in {Y}oung's lattice,
	      {\em S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.

	\item Balodi, Mamta and Palcoux, Sebastien: On {B}oolean intervals of finite groups, {\em J. Combin. Theory Ser. A} {\bf 157}
	      (2018), 49--69.

	\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
	      Christopher R.H. and Harris, Pamela E. and Khare, Apoorva and
	      Morales, Alejandro H. and Yip, Martha: The volume of the caracol polytope, {\em S\'{e}m. Lothar. Combin.}
	      {\bf 80B} (2018), Art.~87, 12.

	\item Bhosle, Usha N.: Hitchin pairs on reducible curves, {\em Internat. J. Math.} {\bf 29}
	      (2018), 1850015, 49.

	\item B\"{o}cherer, Siegfried and Das, Soumya: Cuspidality and the growth of {F}ourier coefficients of
	      modular forms, {\em J. Reine Angew. Math.} {\bf 741} (2018), 161--178.

	\item B\"{o}cherer, Siegfried and Das, Soumya: Petersson norms of not necessarily cuspidal {J}acobi
	      modular forms and applications, {\em Adv. Math.} {\bf 336} (2018), 335--376.

	\item Banerjee, Abhishek: On {A}uslander's formula and cohereditary torsion pairs, {\em Commun. Contemp. Math.} {\bf 20} (2018),
	      1750071, 27.

	\item Banerjee, Abhishek: Modular {H}ecke algebras over {M}\"{o}bius categories, {\em J. Geom. Phys.} {\bf 131} (2018), 23--40.

	\item Banerjee, Abhishek: A topological {N}ullstellensatz for tensor-triangulated
	      categories, {\em C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375.

	\item Banerjee, Abhishek: Quasimodular {H}ecke algebras and {H}opf actions, {\em J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080.

	\item Banerjee, Abhishek: Completions of monoid objects and descent results, {\em J. Algebra} {\bf 507} (2018), 362--399.

	\item Burton, Benjamin A. and Datta, Basudeb and Singh, Nitin and
	      Spreer, Jonathan: A construction principle for tight and minimal triangulations
	      of manifolds, {\em Exp. Math.} {\bf 27} (2018), 22--36.

	\item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
	      K. C.: A note on linear preservers of semipositive and minimally
	      semipositive matrices, {\em Electron. J. Linear Algebra} {\bf 34} (2018), 687--694.

	\item Das, Soumya and Khan, Rizwanur: The third moment of symmetric square {$L$}-functions, {\em Q. J. Math.} {\bf 69} (2018),
	      1063--1087.

	\item Das, Soumya and Kohnen, Winfried: On sign changes of eigenvalues of {S}iegel cusp forms of genus
	      2 in prime powers, {\em Acta Arith.} {\bf 183} (2018), 167--172.

	\item Datta, Basudeb and Maity, Dipendu: Semi-equivelar maps on the torus and the {K}lein bottle are
		      {A}rchimedean, {\em Discrete Math.} {\bf 341} (2018), 3296--3309.

	\item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P. and Silberman, Lior and Tao, Terence: Homogeneous length functions on groups, {\em Algebra Number Theory} {\bf 12} (2018), 1773--1786.

	\item\label{gupta:measured-foliations} Gupta, Subhojoy and Wolf, Michael: Meromorphic quadratic differentials and measured foliations on a Riemann surface, {\em Math Ann.} {\bf 373} (2019), 73--118.

	\item Jha, Abhash Kumar and Sahu, Brundaban: Rankin--{C}ohen brackets on {J}acobi forms of several variables
	      and special values of certain {D}irichlet series, {\em Int. J. Number Theory} {\bf 15} (2019), 925--933.

	\item Khare, Apoorva: Generalized nil-{C}oxeter algebras over discrete complex
	      reflection groups, {\em Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999.

	\item Khare, Apoorva: Generalized nil-Coxeter algebras, {\em S\'em Lothar. Combin.} {\bf 80B,} (2018), No.~29.

	\item Khare, Apoorva and Tikaradze, Akaki: A {C}arlitz--von {S}taudt type theorem for finite rings,
	      {\em Linear Algebra Appl.} {\bf 568} (2019), 106--126.

	\item Krakovski, Roi and Onn, Uri and Singla, Pooja: Regular characters of groups of type {$A_n$} over
	      discrete valuation rings, {\em J. Algebra} {\bf 496} (2018), 116--137.

	\item Maity, Dipendu: Pentagonal maps on the torus and the plane, {\em Beitr. Algebra Geom.} {\bf 60} (2019), 17--37.

	\item Maity, Dipendu and Upadhyay, Ashish Kumar: On centrally symmetric manifolds, {\em J. Ramanujan Math. Soc.} {\bf 34}
	      (2019), 21--27.

	\item Mukherjee, Sajal Kumar and Bera, Sudip: Combinatorial proofs of the {N}ewton--{G}irard and
		      {C}hapman--{C}ostas--{S}antos identities, {\em Discrete Math.} {\bf 342} (2019), 1577--1580.

	\item Narayanan, E. K. and Singla, Pooja: On monomial representations of finitely generated nilpotent
	      groups, {\em Comm. Algebra} {\bf 46} (2018), 2319--2331.

	\item Quddus, Safdar: Invariants of the {$\mathbb Z_2$} orbifolds of the {P}odle\'{s} two
	      spheres, {\em J. Noncommut. Geom.} {\bf 13} (2019), 257--267.

	\item Sanki, Bidyut: Filling of closed surfaces, {\em J. Topol. Anal.} {\bf 10} (2018), 897--913.

	\item Sanki, Bidyut and Gadgil, Siddhartha: Graphs of systoles on hyperbolic surfaces, {\em J. Topol. Anal.}
		      {\bf 11} (2019), 1--20.

\end{enumerate}
\vspace{0.5mm}

%% YEAR 2 LISTING %%%%%
\noindent{{\small {\bf April 2019--March 2020:}}}
\medskip

\noindent{{\small {\sl In the identified thrust area:}}}\vspace{-2.5mm}

\begin{enumerate}[resume, leftmargin=27pt]
	\item Aas, Erik and Ayyer, Arvind and Linusson, Svante and Potka,
	      Samu: \href{https://doi.org/10.1088/1751-8121/ab2e96}{The exact phase diagram for a
		      semipermeable {TASEP} with nonlocal boundary jumps}, \emph{J. Phys. A} {\bf 52} (2019),
	      355001, 19.

	\item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
	      Nandakumaran, A. K.: \href{https://doi.org/10.3233/asy-191526}{Control problem on a rough
		      circular domain and homogenization}, \emph{Asymptot. Anal.} {\bf 115} (2019), 19--46.

	\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1007/s10231-019-00848-7}{Locally periodic unfolding operator for highly oscillating
		      rough domains}, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954.

	\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1142/S0219199719500299}{Semi-linear optimal control problem on a smooth oscillating
		      domain}, \emph{Commun. Contemp. Math.} {\bf 22} (2020), 1950029, 26.

	\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu: \href{https://doi.org/10.1002/mma.5748}{Asymptotic analysis of a boundary optimal control problem on a general branched structure}, \emph{Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434.

	\item Aiyappan, S. and Sardar, Bidhan Chandra: \href{https://doi.org/10.1080/00036811.2018.1471207}{Biharmonic equation in a highly oscillating domain and
		      homogenization of an associated control problem}, \emph{Appl. Anal.} {\bf 98} (2019), 2783--2801.

	\item Anand, Jatin and Bhattacharyya, Tirthankar and Srivastava,
	      Sachi: \href{https://doi.org/10.1007/s00013-019-01406-6}{Some thoughts on composition operators on subspaces of the
			      {H}ardy space}, \emph{Arch. Math. (Basel)} {\bf 114} (2020), 431--444.

	\item Ayyer, Arvind and Behrend, Roger E. and Fischer, Ilse: \href{https://doi.org/10.1016/j.aim.2020.107125}{Extreme diagonally and antidiagonally symmetric alternating
		      sign matrices of odd order}, \emph{Adv. Math.} {\bf 367} (2020), 107125, 56.

	\item Ayyer, Arvind and Behrend, Roger E.: \href{https://doi.org/10.1016/j.jcta.2019.01.001}{Factorization theorems for classical group characters, with
		      applications to alternating sign matrices and plane
		      partitions}, \emph{J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.

	\item Ayyer, Arvind and Fischer, Ilse: \href{https://doi.org/10.1016/j.jcta.2020.105241}{Bijective proofs of skew {S}chur polynomial factorizations}, \emph{J. Combin. Theory Ser. A} {\bf 174} (2020), 105241, 40.

	\item Ayyer, Arvind and Linusson, Svante: \href{https://doi.org/10.1002/rsa.20825}{Reverse juggling processes}, \emph{Random Structures Algorithms} {\bf 55} (2019), 56--72.

	\item\label{ayyer-singla:commutative-rings} Ayyer, Arvind and Singla, Pooja:
	      \href{https://doi.org/10.1007/s10468-019-09864-w}{Random motion on finite rings, {I}: commutative
		      rings}, \emph{Algebr. Represent. Theory} {\bf 23} (2020), 583--604.

	\item Ayyer, Arvind: \href{https://doi.org/10.1007/s00026-019-00480-5}{Squareness for the {M}onopole-{D}imer model}, \emph{Ann. Comb.} {\bf 24} (2020), 237--255.

	\item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
	      Verma, Kaushal: \href{https://doi.org/10.1090/proc/14421}{Remarks on the higher dimensional {S}uita conjecture}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411.

	\item Bera, Sayani and Pal, Ratna and Verma, Kaushal: \href{https://doi.org/10.1007/s40879-019-00326-7}{A rigidity theorem for {H}\'{e}non maps}, \emph{Eur. J. Math.} {\bf 6} (2020), 508--532.

	\item Bharali, Gautam and Chandel, Vikramjeet Singh: \href{https://doi.org/10.1007/s11785-017-0701-5}{Pick interpolation on the polydisc: small families of
		      sufficient kernels}, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093.

	\item Bharali, Gautam: \href{https://doi.org/10.1007/s12220-019-00342-9}{On the growth of the {B}ergman metric near a point of infinite
		      type}, \emph{J. Geom. Anal.} {\bf 30} (2020), 1238--1258.

	\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107.

	\item\label{Bhattacharyya:symm-bidisc} Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz
	      operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} (2020).

	\item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K.: \href{https://doi.org/10.1007/s13226-019-0345-4}{Survey of last ten years of work done in {I}ndia in some
		      selected areas of functional analysis and operator theory}, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617.

	\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram: \href{https://doi.org/10.3934/cpaa.2019116}{On extension problem, trace {H}ardy and {H}ardy's inequalities
		      for some fractional {L}aplacians}, \emph{Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605.

	\item Chakraborty, Atlanta and Chandru, Vijay and Rao, M. R.: \href{https://doi.org/10.1007/s10479-019-03186-2}{A linear programming primer: from {F}ourier to {K}armarkar}, \emph{Ann. Oper. Res.} {\bf 287} (2020), 593--616.

	\item Chandel, Vikramjeet Singh: \href{https://doi.org/10.1007/s12220-018-00123-w}{The 3-point spectral pick interpolation problem and an
		      application to holomorphic correspondences}, \emph{J. Geom. Anal.} {\bf 30} (2020), 551--572.

	\item Cicuttin, Matteo and Ern, Alexandre and Gudi, Thirupathi: \href{https://doi.org/10.1007/s10915-020-01195-z}{Hybrid high-order methods for the elliptic obstacle problem}, \emph{J. Sci. Comput.} {\bf 83} (2020), Paper No. 8, 18.

	\item Gudi, Thirupathi and Majumder, Papri: \href{https://doi.org/10.1016/j.camwa.2019.06.022}{Conforming and discontinuous {G}alerkin {FEM} in space for
	      solving parabolic obstacle problem}, \emph{Comput. Math. Appl.} {\bf 78} (2019), 3896--3915.

	\item Gudi, Thirupathi and Majumder, Papri: \href{https://doi.org/10.1515/cmam-2019-0057}{Crouzeix-{R}aviart finite element approximation for the
	      parabolic obstacle problem}, \emph{Comput. Methods Appl. Math.} {\bf 20} (2020), 273--292.

	\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: \href{https://doi.org/10.1090/proc/14410}{Von {N}eumann's inequality for commuting operator-valued
		      multishifts}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.

	\item Iyer, S. K. and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897.

	\item K. Murali, A. K. Nandakumaran, Turgurt Durduran, Hari M Varma: Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements, \emph{Biomedical Optics Express 5395} {\bf 10} (2019).

	\item Kashyap, G. A. R. S. R. K. and Bapat, D. and Das, D. and Gowaikar, R. D. and  Amritkar, R. E. and Rangarajan, G. and V. Ravindranath and G. Ambika: Synapse loss and progress of Alzheimers disease - A network model, \emph{Scientific Reports} {\bf 9} (2019).

	\item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan: \href{https://doi.org/10.1080/07362994.2018.1538803}{On the convolution of {M}ittag-{L}effler distributions and its
	      applications to fractional point processes}, \emph{Stoch. Anal. Appl.} {\bf 37} (2019), 115--122.

	\item Khan, Mohammad Yasir Feroz and Biswas, Rahul and Sau, Ramesh
	      Chandra: Instability of {L}agrange interpolation on {$H^1(\Omega)\cap
				      C(\overline\Omega)$}, \emph{Math. Student} {\bf 88} (2019), 153--158.

	\item Khare, Apoorva and Tikaradze, Akaki: \href{https://doi.org/10.1016/j.laa.2018.05.035}{A {C}arlitz--von {S}taudt type theorem for finite rings}, \emph{Linear Algebra Appl.} {\bf 568} (2019), 106--126.
	\item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric semigroups, \emph{Advances in Operator Theory (Special issue in honor of Rajendra Bhatia)} {\bf 5} (2020), 779-795.

	\item Kor\'{a}nyi, Adam and Misra, Gadadhar: Homogeneous Hermitian holomorphic vector bundles and the Cowen-Douglas class over bounded symmetric domains, \emph{Adv. Math.} {\bf 351} (2019), 1105 - 1138.

	\item Maitra, Anwoy: On the continuous extension of Kobayashi isometries, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.

	\item Maitra, Anwoy: \href{https://doi.org/10.1016/j.jmaa.2019.123694}{A form of {S}chwarz's lemma and a bound for the {K}obayashi
		      metric on convex domains}, \emph{J. Math. Anal. Appl.} {\bf 484} (2020), 123694, 16.
	\item Mal, Arpita and Paul, Kallol and Rao, T. S. S. R. K. and Sain,
	      Debmalya: \href{https://doi.org/10.1007/s00605-019-01289-3}{Approximate {B}irkhoff-{J}ames orthogonality and smoothness in
	      the space of bounded linear operators}, \emph{Monatsh. Math.} {\bf 190} (2019), 549--558.

	\item Maitra, Anwoy: \href{https://doi.org/10.1090/proc/15038}{On the continuous extension of {K}obayashi isometries}, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.

	\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: \href{https://projecteuclid.org/euclid.bjma/1543914019}{On some geometric properties of operator spaces}, \emph{Banach J. Math. Anal.} {\bf 13} (2019), 174-191.

	\item Misra, Gadadhar and Reza, Md. Ramiz: \href{https://doi.org/10.1215/00192082-7768711}{Curvature inequalities and extremal operators}, \emph{Illinois J. Math.} {\bf 63} (2019), 193--217.

	\item Nikolov, Nikolai and Verma, Kaushal: \href{https://doi.org/10.1007/s12220-019-00237-9}{On the squeezing function and {F}ridman invariants}, \emph{J. Geom. Anal.} {\bf 30} (2020), 1218--1225.

	\item Paul, Kallol and Sain, Debmalya and Ghosh, Puja: Symmetry of {B}irkhoff-{J}ames orthogonality of bounded linear
	      operators, \emph{Ulam type stability} {\bf } (2019), 331--344.

	\item Poria, Anirudha: \href{https://doi.org/10.1080/01630563.2020.1728771}{Positive weight function and classification of {$g$}-frames}, \emph{Numer. Funct. Anal. Optim.} {\bf 41} (2020), 950--968.

	\item Roth, Julien and Upadhyay, Abhitosh: \href{https://doi.org/10.1007/s00013-019-01315-8}{On compact anisotropic {W}eingarten hypersurfaces in
			      {E}uclidean space}, \emph{Arch. Math. (Basel)} {\bf 113} (2019), 213--224.

	\item Roth, Julien and Upadhyay, Abhitosh: \href{https://doi.org/10.1017/s0004972719000935}{On almost stable {CMC} hypersurfaces in manifolds of bounded
		      sectional curvature}, \emph{Bull. Aust. Math. Soc.} {\bf 101} (2020), 333--338.

	\item Roth, Julien and Upadhyay, Abhitosh: \href{https://link.springer.com/article/10.1007/s00025-019-1142-4?shared-article-renderer#citeas}{f-Biharmonic Submanifolds of Generalized Space Forms}, \emph{Results in Mathematics} {\bf 75} (2020).

	\item Roth, Julien and Upadhyay, Abhitosh: \href{https://www.cambridge.org/core/journals/bulletin-of-the-australian-mathematical-society/article/on-almost-stable-cmc-hypersurfaces-in-manifolds-of-bounded-sectional-curvature/E0BF84D4D46C82F6D75CDCEAAF5DEE94}{On almost stable CMC hypersurfaces in manifolds of bounded sectional curvature}, \emph{Bulletin of the Australian Mathematical Society} {\bf 101} (2020), 333-338.

	\item Sain, Debmalya and Mal, Arpita and Paul, Kallol: \href{https://doi.org/10.1016/j.exmath.2019.01.001}{Some remarks on {B}irkhoff-{J}ames orthogonality of linear
	      operators}, \emph{Expo. Math.} {\bf 38} (2020), 138--147.

	\item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas: \href{https://doi.org/10.7153/oam-2019-13-31}{On two extremum problems related to the norm of a bounded
		      linear operator}, \emph{Oper. Matrices} {\bf 13} (2019), 421--432.

	\item Sain, Debmalya and Ray, Anubhab and Paul, Kallol: Extreme contractions on finite-dimensional polygonal {B}anach
	      spaces, \emph{J. Convex Anal.} {\bf 26} (2019), 877--885.

	\item Sain, Debmalya: \href{https://doi.org/10.1007/s13226-020-0393-9}{On the norm attainment set of a bounded linear
		      operator and
		      semi-inner-products in normed spaces}, \emph{Indian J. Pure Appl. Math.} {\bf 51} (2020), 179--186.

	\item Sain, Debmalya: \href{https://doi.org/10.7153/oam-2019-13-32}{Smooth points in operator spaces and some
		      {B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces}, \emph{Oper. Matrices} {\bf 13} (2019), 433--445.

	\item Sarkar, Amar Deep and Verma, Kaushal: A submultiplicative property of the Carath\'{e}odory metric on planar domains, \emph{Proc. Indian Acad. Sci. (Math. Sci.)} {\bf 130} (2020).

	\item Sarkar, Amar Deep and Verma, Kaushal: \href{https://doi.org/10.1007/s40315-020-00303-2}{Boundary behaviour of some conformal invariants on planar
		      domains}, \emph{Comput. Methods Funct. Theory} {\bf 20} (2020), 145--158.

	\item Vishnu Priya, N. and Senthilvelan, M. and  Rangarajan, G. and Lakshmanan, M: On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation, \emph{Physics Letters A} {\bf 383} (2019), 15-26.

	\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan,
	      Govindan: \href{https://doi.org/10.1063/1.5121245}{On the role of four-wave mixing effect in the interactions
	      between nonlinear modes of coupled generalized nonlinear
		      {S}chr\"{o}dinger equation}, \emph{Chaos} {\bf 29} (2019), 123135, 14.

	\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, G.: On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, \emph{Chaos} {\bf 29} (2019), 123135.\end{enumerate}

\noindent{{\small {\sl In other areas:}}}\vspace{-2.5mm}

\begin{enumerate}[resume, leftmargin=27pt]

	\item Anamby, Pramath and Das, Soumya: \href{https://doi.org/10.5565/PUBLMAT6311911}{Distinguishing
			      {H}ermitian cusp forms of degree 2 by a certain subset of all {F}ourier coefficients},
	      \emph{Publ. Mat.} {\bf 63} (2019), 307--341.

	\item Banerjee, Abhishek and Kour, Surjeet: \href{https://doi.org/10.1007/s10231-019-00844-x}{{$(A,\delta)$}-modules, {H}ochschild homology and higher
		      derivations}, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802.

	\item Banerjee, Abhishek: \href{https://doi.org/10.4153/s0008439518000656}{On differential torsion theories and rings with
		      several objects}, \emph{Canad. Math. Bull.} {\bf 62} (2019), 703--714.

	\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
	      Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
	      Morales, Alejandro H. and Yip, Martha: \href{https://doi.org/10.1090/tran/7743}{A combinatorial model for computing volumes of flow polytopes}, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 3369--3404.

	\item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy: Branched projective structures on a {R}iemann surface and
	      logarithmic connections, \emph{Doc. Math.} {\bf 24} (2019), 2299--2337.

	\item Carstensen, C. and Mallik, G. and Nataraj, N.: \href{https://doi.org/10.1093/imanum/drz071}{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, \emph{IMA Journal of Numerical Analysis} {\bf } (2020).

	\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala: On Baker's explicit abc-conjecture, \emph{Publ. Math. Debrecen} {\bf 94} (2019), 435–453.

	\item Choudhury, Projesh Nath and Tsatsomeros Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic Detection and Construction of N-matrices}, \emph{Linear Algebra and Its Applications} {\bf 602} (2020), 46-56.

	\item Choudhury, Projesh Nath and Tsatsomeros, Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic detection and construction of {N}-matrices}, \emph{Linear Algebra Appl.} {\bf 602} (2020), 46--56.

	\item Das, Soumya and Jha, Abhash Kumar: \href{https://doi.org/10.1007/s12188-019-00206-7}{Analytic properties of twisted real-analytic {H}ermitian
	      {K}lingen type {E}isenstein series and applications}, \emph{Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116.

	\item Das, Soumya and Pal, Ritwik: \href{https://doi.org/10.1007/s40993-019-0158-x}{The first negative eigenvalue of {Y}oshida lifts}, \emph{Res. Number Theory} {\bf 5} (2019), Paper No. 20, 9.

	\item Datt, Gopal and Kumar, Sanjay: \href{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}{A criterion for quasinormality in $\mathbb{C}^n$}, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Paper No. 11, 13 pp.

	\item Datta, B. and Maity, D.: Correction to: Semi-equivelar and vertex-transitive maps on the torus, \emph{Beitr Algebra Geom} {\bf 61} (2020), 187--188.

	\item Datta, B. and Sarkar, S.: Equilibrium triangulations of some quasitoric 4-manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57--78.

	\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor: Higher Chern Classes in Iwasawa Theory, \emph{American Journal of Mathematics} {\bf 142} (2020), 627--682.

	\item Gadgil, Siddhartha: \href{https://doi.org/10.1007/s10817-019-09523-1}{Homogeneous {L}ength {F}unctions on {G}roups: {I}ntertwined
	      {C}omputer and {H}uman {P}roofs}, \emph{J. Automat. Reason.} {\bf 64} (2020), 677--688.

	\item Garani, Shayan Srinivasa and Seshadri, Harish: \href{https://doi.org/10.1080/17459737.2019.1604845}{An algorithmic approach to {S}outh {I}ndian classical music}, \emph{J. Math. Music} {\bf 13} (2019), 107--134.

	\item Gupta, Subhojoy and Mj, Mahan: \href{https://doi.org/10.1090/proc/14866}{Monodromy representations of meromorphic projective
		      structures}, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 2069--2078.

	\item Gupta, Subhojoy and Seshadri, Harish: \href{https://doi.org/10.1093/imrn/rny204}{On domains biholomorphic to {T}eichm\"{u}ller spaces}, \emph{Int. Math. Res. Not. IMRN} {\bf } (2020), 2542--2560.

	\item Gupta, Subhojoy and Wolf, Michael: \href{https://doi.org/10.1007/s00208-018-1674-z}{Meromorphic quadratic differentials and measured foliations on
		      a {R}iemann surface}, \emph{Math. Ann.} {\bf 373} (2019), 73--118.

	\item Gupta, Subhojoy: \href{https://doi.org/10.1090/tran/7777}{Limits of harmonic maps and crowned hyperbolic surfaces}, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 7573--7596.

	\item Hatui, Sumana: \href{https://doi.org/10.1515/jgth-2019-0045}{Schur multipliers of special {$p$}-groups of rank 2}, \emph{J. Group Theory} {\bf 23} (2020), 85--95.

	\item Hatui, Sumana: \href{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}{Schur multipliers of special p-groups of rank 2}, \emph{Journal of Group Theory} {\bf 23} (2020), 85-95.

	\item Jha, Abhash Kumar and Juyal, Abhishek and Pandey, Manish
	      Kumar: On simultaneous non-vanishing of twisted {$L$}-functions
	      associated to newforms on {$\Gamma_0(N)$}, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.

	\item Jha, Abhash Kumar and Sahu, Brundaban: \href{https://doi.org/10.1090/conm/732/14793}{Differential operators on {J}acobi forms and special values of
		      certain {D}irichlet series}, \emph{Automorphic forms and related topics} {\bf 732} (2019), 91--99.

	\item Jha, Abhash Kumar and Sahu, Brundaban: \href{https://doi.org/10.1142/S1793042119500490}{Rankin-{C}ohen brackets on {J}acobi forms of several variables
	      and special values of certain {D}irichlet series}, \emph{Int. J. Number Theory} {\bf 15} (2019), 925--933.

	\item Maiti, Arun: \href{https://doi.org/10.1016/j.disc.2020.111911}{Quasi-vertex-transitive maps on the plane}, \emph{Discrete Math.} {\bf 343} (2020), 111911, 7.

	\item Maiti, Arun: \href{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}{Quasi-vertex-transitive maps on the plane}, \emph{Discrete Mathematics} {\bf 343} (2020), 111911-111917.

	\item Maity, Dipendu: \href{https://doi.org/10.1007/s13366-018-0405-7}{Pentagonal maps on the torus and the plane}, \emph{Beitr. Algebra Geom.} {\bf 60} (2019), 17--37.
	\item Maity, Dipendu and Upadhyay, Ashish Kumar: On centrally symmetric manifolds, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.

	\item Mukherjee, Sajal Kumar and Bera, Sudip: \href{https://doi.org/10.1016/j.disc.2019.02.013}{Combinatorial proofs of the {N}ewton-{G}irard and
		      {C}hapman-{C}ostas-{S}antos identities}, \emph{Discrete Math.} {\bf 342} (2019), 1577--1580.

	\item Pingali, Vamsi Pritham: \href{https://doi.org/10.1007/s11005-020-01279-9}{Quillen metrics and perturbed equations}, \emph{Lett. Math. Phys.} {\bf 110} (2020), 1861--1875.

	\item Pingali, Vamsi Pritham: \href{https://doi.org/10.1016/j.aim.2019.106921}{A vector bundle version of the {M}onge-{A}mp\`ere equation}, \emph{Adv. Math.} {\bf 360} (2020), 106921, 40.

	\item Pradhan, P. and Sahu, B.: \href{https://doi.org/10.1016/j.disc.2020.112044}{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, \emph{Discrete Mathematics} {\bf 343} (2020).

	\item Quddus, Safdar: \href{https://doi.org/10.4171/JNCG/320}{Invariants of the {$\mathbb{Z}_2$} orbifolds of the {P}odle\'{s} two
	      spheres}, \emph{J. Noncommut. Geom.} {\bf 13} (2019), 257--267.

	\item Roy, Krishanu and Venkatesh, R.: \href{https://doi.org/10.1007/s00031-018-9510-9}{Maximal closed subroot systems of real affine root systems}, \emph{Transform. Groups} {\bf 24} (2019), 1261--1308.

	\item Seshadri, Harish: \href{https://doi.org/10.1007/s13226-019-0355-2}{Differential geometry in {I}ndia}, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799.

\end{enumerate}
\vspace{0.5mm}

\noindent{{\small $(i\text{-}b)$ {\sc Accepted for publication at the time of reporting}}}
\medskip

%%THIS LIST IS NOT ORGANISED BY YEAR %%%%%
%\noindent{{\small {\bf  April 2018--March 2019:}}}
%\medskip

\noindent{{\small {\sl In the identified thrust area:}}}\vspace{-2.5mm}

\begin{enumerate}[resume, leftmargin=27pt]
	\item Basu, R. and Ganguly, S. and Hegde, M. and Krishnapur, M.: Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation, to appear in \emph{Israel Journal of Mathematics}.

	\item\label{bharali:Wolff-Denjoy} Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility,
	      a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}.

	\item\label{sen:models-at-criticality} Dhara, Souvik and van der Hofstad, Remco and van Leeuwaarden, Johan S.H. and Sen, Sanchayan: Heavy-tailed configuration models at criticality, to appear in {\em Annales de l'Institut Henri
			      Poincar\'e (B) Probabilit\'es et Statistiques}.

	\item Ghosh, M. K. and K. Suresh Kumar and C. Pal and S. Pradhan: Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications, to appear in \emph{Stochastic Analysis and Applications}.

	\item Ghosh, M. K. and Pradhan, S.: Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant, to appear in \emph{ESIAM: Control, Optimization and Calculus of Variations}.

	\item Ghosh, Subhajit: Total variation cutoff for the transpose top-2 with random shuffle, to appear in {\em Journal of Theoretical Probability}.

	\item Gudi, Thirupathi and  Sau, Ramesh Ch.: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim. Calc. Var}.

	\item\label{iyer:heterogeneous-populations} Nair, Gokul and Athmanathan, Senthil and Iyer, Srikanth K. and Guttal, Vishwesha: Fission-fusion dynamics and group-size-dependent composition in heterogeneous populations,
	      to appear in {\em Physical Review E}.

	\item\label{thangavelu:H-type-groups} Roncal, Luz and Thangavelu, Sundaram: An extension problem and trace Hardy
	      inequality for the sublaplacian on H-type groups, to appear in {\em International Mathematical Research Notices}.

	\item\label{iyer:wireless-networks} Vaze, Rahul and Iyer, Srikanth K., Capacity of cellular wireless networks,
	      to appear in {\em IEEE Transactions on Wireless Communications}.

\end{enumerate}

\noindent{{\small {\sl In other areas:}}}\vspace{-2.5mm}

\begin{enumerate}[resume, leftmargin=27pt]
	\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein-Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.

	\item Balodi, M. and Banerjee, A. and Ray, S.: Cohomology of modules over H-categories and co-H-categories, to appear in \emph{Canadian Journal of Mathematics}.

	\item Balodi, M. and Banerjee, A. and Ray, S.: Entwined modules over linear categories and Galois extensions, to appear in \emph{Israel Journal of Mathematics}.

	\item Banerjee, A.: On Noetherian schemes over $(\mathcal C,\otimes,1)$ and the category of quasi-coherent sheaves, to appear in \emph{Indiana University Mathematics Journal}.

	\item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable CMC free-boundary surfaces in a strictly convex domain of a bi-invariant Lie group, to appear in \emph{International Journal of Mathematics}.

	\item Choudhury, Projesh Nath and Sivakumar, K.C.: \href{https://doi.org/10.1080/03081087.2019.1602588}{Matrices with Positive Semidefinite Real Part}, to appear in \emph{Linear and Multilinear Algebra}.

	\item\label{datta-gupta:hyperbolic-plane} Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane,
	      to appear in \emph{Discrete and Computational Geometry}.

	\item Gupta, Subhojoy: Harmonic maps and wild Teichm{\"u}ller spaces, to appear in {\em Journal of Topology and
			      Analysis}.

	\item Kreuzer, M. and Patil, D. Patil: Computational aspects of Burnside rings part II: important maps, to appear in \emph{Beitr\"age zur Algebra und Geometrie / Contributions to Algebra and Geometry}.

	\item\label{pingali:algebraic-hypersurfaces} Pingali, Vamsi Pritham and Varolin, Dror: Non-uniformly flat affine algebraic hypersurfaces, to appear in {\em Nagoya Mathematical Journal}.

	\item Ray, Samarpita: Closure operations, Continuous valuations on monoids and Spectral spaces, to appear in {\em Journal of algebra and its applications}.
\end{enumerate}
\vspace{0.5mm}

\noindent{{\small $(i\text{-}c)$ {\sc Submitted/preprints at the time of reporting}}}
\medskip

%% THIS LIST IS NOT ORGANISED BY YEAR%%%%%
%\noindent{{\small {\bf April 2018--March 2019:}}}
%\medskip

\noindent{{\small {\sl In the identified thrust area:}}}\vspace{-2.5mm}

\begin{enumerate}[resume, leftmargin=27pt]
	\item\label{sen:random-3-regular-graph} Addario-Berry, Louigi and Sen, Sanchayan: Geometry of the minimal spanning tree of a random 3-regular graph.

	\item\label{ayyer:partial-cyclic-orders} Ayyer, Arvind and Josuat-Verg\`es, Matthieu and Ramassamy, Sanjay: Extensions of partial cyclic orders and consecutive coordinate polytopes.

	\item\label{ayyer:Coxeter-groups} Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven: Macdonald trees and
	      determinants of representations for finite Coxeter groups.

	\item Ayyer, Arvind and Sinha, Shubham: The size of t-cores and hook lengths of random cells in random partitions.

	\item Ayyer, Arvind: A simple symmetric exclusion process driven by an asymmetric tracer particle.

	\item\label{ayyer-singla:noncommutative-rings} Ayyer, Arvind and Singla, Pooja: Random motion on finite rings, II:
	      Noncommutative rings.

	\item\label{thangavelu:Heisenberg-group} Bagchi, Sayan and  Hait, Sourav and  Roncal, Luz and Thangavelu, Sundaram: On the lacunary spherical maximal function on the Heisenberg group.

	\item Bera, Sudip: Enumeration of weighted paths on a digraph and block hook determinant.

	\item Behera, Kiran Kumar: \href{https://arxiv.org/abs/1909.12548}{Self-inversive polynomials from rational transformation of linear functionals}.

	\item\label{bhattacharyya:pseudo-extensions} Bhattacharyya, Tirthankar and Das, B. Krishna  and Sau, Haripada: Toeplitz operators
	      and pseudo-extensions.

	\item Bhattacharyya, Tirthankar and Kumar, Poornendu and Sau, Haripada: Distinguished Varieties Through the Berger--Coburn--Lebow Theorem.

	\item Bhattacharyya, T. and  Biswas, A. and Maitra, A.: An unbounded realization of the symmetrized bidisc.

	\item Bhattacharyya, Tirthankar and  Roy, Subrata Shyam and Yadav, Tapesh: The Agler--Young Class.

	\item B{\"o}cherer, Siegfried and Das, Soumya: On fundamental Fourier coefficients of Siegel modular forms.

	\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: \href{https://arxiv.org/abs/1812.05435}{Multiplicities, invariant subspaces and an additive formula.}.

	\item\label{datar:K3-surfaces} Datar, Ved and Jacob,Adam and Zhang, Yuguang: Adiabatic limits of anti-self-dual
	      connections on collapsed K3 surfaces, to appear in \emph{Journal of differential geometry}.

	\item\label{datar-pingali:Kahler-metrics} Datar, Ved and Pingali, Vamsi Pritham: On coupled constant scalar curvature Kaehler
	      metrics, to appear in \emph{Journal of symplectic geometry}.

	\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita: $K$-homogeneous tuple of operators on bounded symmetric domains.

	\item Gupta, Purvi and Wawrzyniak, Chloe Urbanski: STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$.

	\item\label{khare:schur-polynomial-identities} Khare, Apoorva: Smooth entrywise positivity preservers, a
	      Horn-Loewner master theorem, and Schur polynomial identities.

	\item Ganguly, Pritam and Thangavelu,Sundaram: On lacunary spherical maximal function on Heisenberg groups.

	\item Khare, Apoorva: The non-compact normed space of norms on a finite-dimensional Banach space.

	\item Khare, Apoorva: Sharp nonzero lower bounds for the Schur product theorem.

	\item L\"ubeck, Frank and Prasad, Dipendra and Ayyer, Arvind: A character relationship between symmetric group and hyperoctahedral group.

	\item Maiti, Arun: Loop products on level homology and closed geodesics.

	\item Miermont, Gr\'egory and Sen, Sanchayan: On breadth-first constructions of scaling limits of random graphs and random unicellular maps.

	\item\label{Misra:Jordan-Keppler} Misra, Gadadhar and Upmeier, Harald: Singular Hilbert modules on
	      Jordan--Keppler varieties.

	\item Poria, Anirudha: \href{https://arxiv.org/abs/2004.04184}{Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms}.

	\item Poria, Anirudha: \href{https://arxiv.org/abs/2005.14274}{Uncertainty principles for the Opdam-Cherednik transform on modulation spaces}.

	\item Toft, J. and Gumber, A. and Manna, R. and Ratnakumar, P. K.: \href{https://arxiv.org/abs/2004.02430v1}{Translation and modulation invariant Hilbert spaces}.
\end{enumerate}

\noindent{{\small {\sl In other areas:}}}\vspace{-2.5mm}

\begin{enumerate}[resume, leftmargin=27pt]

	\item Balodi, Mamta and Banerjee, Abhishek: Cycles over DGH-semicategories and pairings in categorical Hopf-cyclic cohomology.

	\item Balodi, Mamta: Morita invariance of equivariant and Hopf-cyclic cohomology of module algebras over Hopf algebroids.

	\item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter: Surface group representations in $SL(2,\mathbb{C})$ with finite mapping class orbits.

	\item David Burns, Mahesh Kakde: On Weil-Etale Cohomology and Artin L-series.

	\item\label{khare:matrices-tree}  Choudhury, Projesh Nath and Khare, Apoorva: Distance matrices of a tree: two
	      more invariants, and in a unified framework.
	\item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian: Gravitating vortices with positive curvature.

	\item Gupta, Subhojoy and Mj, Mahan: Meromorphic projective structures, grafting and the monodromy map.

	\item Gupta, Subhojoy: Monodromy groups of $CP^1$-structures on punctured surfaces.

	\item\label{singla:compact-linear-groups} Hassain, M. and Singla, Pooja; Representation Growth of Special Compact Linear Groups of Order Two.

	\item Hatui, Sumana and Singla Pooja: \href{https://arxiv.org/abs/1909.06589}{On Schur multiplier and Projective representations of Heisenberg groups}.

	\item Kus, Deniz and Venkatesh, R: Borel--de Siebenthal theory for affine reflection systems.

	\item Maiti, Arun: Optimal index growth of closed geodesics.

	\item\label{singla:discrete-valuation-rings} Patel, Shiv Prakash and Singla, Pooja: A multiplicity one theorem for groups of type $A_n$ over discrete valuation rings.

	\item Patil, Dilip P.: On the connectedness of the fiber product of two connected finte free affine schemes.

	\item Pingali, Vamsi Pritham: The deformed Hermitian Yang-Mills equation on three-folds.

	\item\label{pingali:Monge-Ampere-equation} Pingali, Vamsi Pritham: A vector bundle version of the Monge--Ampere equation.

	\item Quddus, Safdar: \href{https://arxiv.org/abs/2002.02192}{Equivariant Cartan Homotopy Formula for $DG$-algebra.}.

	\item Radhika Ganapathy: A Hecke algebra isomorphism over close local fields.

	\item Reif, Shifra and Venkatesh, R.: On tensor products of irreducible integrable representations.

\end{enumerate}

\subsubsection*{{\small $(ii)$ {\sc Research Papers in Conference Proceedings}}}

%% YEAR 1 LISTING %%%%%
\noindent{{\small {\bf April 2018--March 2019:}}}\vspace{-1mm}

\renewcommand{\theenumi}{C.\arabic{enumi}}
\begin{enumerate}%[leftmargin=27pt]

	\item Kanukurthi, Bhavana and Obbattu, Sai Lakshmi Bhavana and
	      Sekar, Sruthi: Non-malleable randomness encoders and their applications, {\em Advances in
	      Cryptology\,---\,\linebreak{EUROCRYPT} 2018: {P}art {III}} {\bf 10822} (2018), 589--617.

	\item S. Ghara and G. Misra: Decomposition of the tensor product of two Hilbert modules in {\em Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G. Douglas Memorial Volume} Curto, R.E., Helton, W., Lin, H., Tang, X., Yang, R., Yu, G. (ed.), Operator Theory: Advances and Applications , Birkhauser (2020).

	\item Gadadhar Misra: Decomposition of the tensor product of two Hilbert modules in {\em Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G. Douglas Memorial Volume} R. Curto, W. Helton, H. Lin, X. Tang, R. Yang, G. Yu (ed.), Operator Theory: Advances and Applications , Birkhauser (2020).

	\item\label{patil:Nullstellensaetze} Goel, Kriti and Patil, Dilip P. and Verma, Jugal: Nullstellens\"atze and Applications, {\em Proceedings of the International Conference on Mathematics and Centenary Celebrations of Ramjas College}, forthcoming.

	\item\label{patil:generalized-trace-forms} Patil, Dilip P.  and Verma, Jugal: Rational points and generalized trace forms on a finite algebra over a real closed field, {\em Proceedings of the International Conference on Computational Mathematics,  Banasthali Vidyapeeth}.
\end{enumerate}

%% YEAR 2 LISTING %%%%%
\noindent{{\small {\bf April 2019--March 2020:}}}\vspace{-1mm}

\begin{enumerate}[resume]%[leftmargin=27pt]

	\item Banerjee, A.: Spectra as universal objects in categories of supports in {\em Banach Center Publications(Quantum Dynamics Proceedings)} Ludwik Dabrowski, Ryszard Nest, Adam Skalski (ed.), Banach Center Publications , IMPAN, Warsaw, Poland (2020).

\end{enumerate}

\subsubsection*{{\small $(iii)$ {\sc Books \& Monographs}}}\vspace{-1mm}

%% YEAR 1 LISTING %%%%%
\noindent{{\small {\bf April 2018--March 2019:}}}

\renewcommand{\theenumi}{B.\arabic{enumi}}
\begin{enumerate}%[leftmargin=27pt]

	\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva and Putinar, Mihai: A panorama of positivity: I.
	      Dimension, in {\em Analysis of Operators on Function Spaces (The Serguei Shimorin Memorial Volume)}, eds.
	      A.~Aleman, H.~Hedenmalm, D.~Khavinson, M.~Putinar, Trends in Mathematics,  Birkhauser, pages 117--165, 2019.

	\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva and Putinar, Mihai: A panorama of positivity: II.
	      Fixed dimension, in {\em Complex Analysis and Spectral Theory}, eds.  G.~Dales, D.~Khavinson, J.~Mashreghi, Eds.,
	      CRM Proceedings, AMS  Contemporary Mathematics, American Mathematical Society, 2019.

\end{enumerate}

%% YEAR 2 LISTING %%%%%
\noindent{{\small {\bf April 2019--March 2020:}}}

\begin{enumerate}[resume]%[leftmargin=27pt]

	\item Gupta, Subhojoy and Seshadri, Harish: Complex geometry of Teichm{\"u}ller domains in {\em Handbook
			      of Teichm{\"u}ller Theory} Papadopoulos, Athanase (ed.), IRMA Lect. Math. Theor. Phys, Eur. Math. Soc., Z{\"u}rich
	      (2020), 26.

	\item Gupta, Subhojoy: Holomorphic quadratic differentials in Teichm{\"u}ller theory in {\em Handbook
			      of Teichm{\"u}ller Theory} Papadopoulos, Athanase (ed.), IRMA Lect. Math. Theor. Phys., Eur. Math. Soc., Z{\"u}rich
	      (2020), 36.

	\item Misra, Gadadhar: Operators in the {C}owen-{D}ouglas class and related topics, \emph{Handbook of analytic operator theory} {\bf } (2019), 87--137.
\end{enumerate}

### 2020-08-10 ugc/src/Data.scala

@@ -174,14 +174,26 @@ ${enumString(other)}
   lazy val papersLinked = facultyData
     .flatMap(f => f.papers)
     .filter(
-      p => Set("Published", "Accepted for publication").contains(p.status)
+      p => Set("Published").contains(p.status)
     )
     .map(_.tex) ++ (postDocData
     .flatMap(f => f.papers)
     .filter(
-      p => Set("Published", "Accepted for publication").contains(p.status)
+      p => Set("Published").contains(p.status)
     )
-    .map(_.texLinked))
+    .map(_.texLinked)).sorted
+
+  lazy val acceptedLinked = facultyData
+    .flatMap(f => f.papers)
+    .filter(
+      p => Set("Accepted for publication").contains(p.status)
+    )
+    .map(_.tex) ++ (postDocData
+    .flatMap(f => f.papers)
+    .filter(
+      p => Set("Accepted for publication").contains(p.status)
+    )
+    .map(_.texLinked)).sorted
 
   lazy val preprintsLinked = facultyData
     .flatMap(f => f.papers)
@@ -193,28 +205,28 @@ ${enumString(other)}
     .filter(
       p => Set("Preprint", "Submitted").contains(p.status)
     )
-    .map(_.texLinked))
+    .map(_.texLinked)).sorted
 
   lazy val confPapers = facultyData.flatMap(f => f.confs.map(_.tex)) ++ postDocData
-    .flatMap(f => f.confs.map(_.tex))
+    .flatMap(f => f.confs.map(_.tex)).sorted
 
   lazy val books = facultyData.flatMap(f => f.books.map(_.tex)) ++ postDocData
-    .flatMap(f => f.books.map(_.tex))
+    .flatMap(f => f.books.map(_.tex)).sorted
 
   lazy val bookChapters = facultyData.flatMap(f => f.bookChapters.map(_.tex)) ++ postDocData
-    .flatMap(f => f.bookChapters.map(_.tex))
+    .flatMap(f => f.bookChapters.map(_.tex)).sorted
 
   lazy val visitors = visitorData.map(Visitor.get(_).tex)
 
   lazy val draftPubs =
     s"""
-\\subsection{Papers in Journals}
-
-${enumString(papers)}
-
-\\subsection{Papers in Journals with links}
+\\subsection{Papers in Journals (with links)}
 
 ${enumString(papersLinked)}
+
+\\subsection{Accepted Papers}
+
+${enumString(acceptedLinked)}
[…]

### 2020-08-10 ugc/src/Data.scala
sorting helper

@@ -37,6 +37,20 @@ object Data {
     .map(_.split("\t").toVector.map(_.trim))
     .map(pad(_, 5))
 
+  def sortFile() =
+    os.write.over(
+      os.pwd / "sorted.tex",
+      os.read(os.pwd / "data" / "to-sort.tex")
+        .split("\\\\item")
+        .toVector
+        .tail
+        .sorted
+        .map(
+          s => "\\item " + s.trim()
+        )
+        .mkString("\n\n")
+    )
+
   lazy val summerStudents = data.flatMap(
     l =>
       SummerStudent.getAll(l).map { stu =>
@@ -101,7 +115,8 @@ ${grantsItems.mkString("\n").replace("&", "\\&")}
     .map(d => s"\\subsection{${d.name}}\n\n${d.researchHighlights}")
     .mkString("\n\n\n")
 
-  lazy val awards = facultyData.flatMap(f => f.awards.awardOpt(f.name)) ++ (postDocData.flatMap(f => f.awardOpt(f.name)))
+  lazy val awards = facultyData.flatMap(f => f.awards.awardOpt(f.name)) ++ (postDocData
+    .flatMap(f => f.awardOpt(f.name)))
 
   lazy val fellows = facultyData.flatMap(f => f.awards.fellowOpt(f.name)) ++ postDocData
     .flatMap(f => f.fellowOpt(f.name))
@@ -181,7 +196,8 @@ ${enumString(other)}
     .filter(
       p => Set("Published").contains(p.status)
     )
-    .map(_.texLinked)).sorted
+    .map(_.texLinked))
+    .sorted
 
   lazy val acceptedLinked = facultyData
     .flatMap(f => f.papers)
@@ -193,7 +209,8 @@ ${enumString(other)}
     .filter(
       p => Set("Accepted for publication").contains(p.status)
     )
-    .map(_.texLinked)).sorted
+    .map(_.texLinked))
+    .sorted
 
   lazy val preprintsLinked = facultyData
     .flatMap(f => f.papers)
@@ -205,16 +222,20 @@ ${enumString(other)}
     .filter(
       p => Set("Preprint", "Submitted").contains(p.status)
     )
-    .map(_.texLinked)).sorted
+    .map(_.texLinked))
+    .sorted
 
   lazy val confPapers = facultyData.flatMap(f => f.confs.map(_.tex)) ++ postDocData
-    .flatMap(f => f.confs.map(_.tex)).sorted
+    .flatMap(f => f.confs.map(_.tex))
+    .sorted
 
[…]

### 2020-08-10 data/to-sort.tex
clean up; multi-line strings with indentation

--- 2020-08-10 data/publications_2018-20.tex
@@
-\subsubsection{\!\!\!{\sl Publications}}
-
-\subsubsection*{{\small $(i)$ {\sc Research Papers in Refereed Journals}}}
-\medskip
-
-\begin{center}
-	\begin{longtable}{|c|c|c|c|}
-
-		\hline
-		                    &                   &                   &                            \\[-4mm]
-		{\bf Year}          & {\bf Thrust Area} & {\bf Other Areas} & {\bf Total}                \\[.4mm]\hline
-		\endfirsthead
-
-		\hline
-		                    &                   &                   &                            \\[-4mm]
-		{\bf Year}          & {\bf Thrust Area} & {\bf Other Areas} & {\bf Total} \hspace{1.1cm} \\[.4mm]\hline
-		\endhead
-
-		                    &                   &                   &                            \\[-4mm]
-		{\em 2018--19}      & 72                & 34                & 106                        \\[.4mm]\hline
-		                    &                   &                   &                            \\[-4mm]
-		{\em Accepted for}  & 13                & 7                 & 20                         \\
-		{\em publication}   &                   &                   &                            \\[0.4mm]\hline
-		                    &                   &                   &                            \\[-4mm]
-		{\em Submitted} for & 17                & 12                & 29                         \\
-		{\em Publication}   &                   &                   &                            \\[0.4mm]\hline
-		                    &                   &                   &                            \\[-4mm]
-		{\bf Total}         & {\bf 102}         & {\bf 53}          & {\bf 155}                  \\[0.4mm]\hline
-	\end{longtable}
-\end{center}
-
-\noindent{{\small $(i\text{-}a)$ {\sc Published in the period under review}}}
-\medskip
-
-%% YEAR 1 LISTING %%%%%
-\noindent{{\small {\bf April 2018--March 2019:}}}
-\medskip
-
-\noindent{{\small {\sl In the identified thrust area:}}}\vspace{-2.5mm}
-\begin{enumerate}[leftmargin=27pt]
-
-	\item Aiyappan, S. and Nandakumaran, A.K. and Prakash, Ravi: Generalization of unfolding operator for highly oscillating
-	      smooth boundary domains and homogenization, {\em Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art.~86, 30.
-
-	\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish: A gap theorem for positive {E}instein metrics on the
-	      four-sphere, {\em Math. Ann.} {\bf 373} (2019), 1329--1339.
-
-	\item\label{ayyer:exclusion-process} Ayyer, A.
-and Finn, C.
-and Roy, D.: Matrix product solution of a left-permeable two-species asymmetric exclusion process, {\em Physical Review E} {\bf 97} (2018), 5225.
-
-	\item\label{ayyer:multispecies-juggling} Ayyer, Arvind and Bouttier, J\'{e}r\'{e}mie and Corteel, Sylvie and
-	      Linusson, Svante and Nunzi, Fran\c{c}ois: Bumping sequences and multispecies juggling, {\em Adv. in Appl. Math.} {\bf 98} (2018), 100--126.
-
-	\item   Ayyer, Arvind and Finn, Caley and Roy, Dipankar: The phase diagram for a multispecies left-permeable asymmetric
-	      exclusion process, {\em J. Stat. Phys.} {\bf 174} (2019), 605--621.
-
-	\item\label{ayyer:Hilbert-Galton} Ayyer, Arvind and Ramassamy, Sanjay: The {H}ilbert--{G}alton board, {\em ALEA Lat. Am. J. Probab. Math. Stat.} {\bf 15} (2018), 755--774.
-
-	\item Bagchi, Sayan and  Thangavelu, Sundaram: Weighted norm inequalities for {W}eyl multipliers and Fourier multipliers on the {H}eisenberg group, {\em J. Anal. Math.} {\bf 136} (2018), 1--29.
-
-	\item Baklouti, Ali and Thangavelu, Sundaram: Hardy and {M}iyachi theorems for {H}eisenberg motion groups, {\em Nagoya Math. J.} {\bf 229} (2018), 1--20.
-
-	\item Balhara, Rakesh: Hardy's inequality for the fractional powers of the {G}rushin
-	      operator, {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art.~33, 25.
-
-	\item\label{ghosh:political-business-cycle} Basak, G. K. and Ghosh, M. K. and Mukherjee, D.: A stochastic model with inflation,
-	      growth and technology for the political business cycle, {\em Journal of Computational Economics} {\bf 53} (2019), 125-140.
-
-	\item Basu, Arnab and Ghosh, Mrinal K.: Nonzero-sum risk-sensitive stochastic games on a countable
-	      state space, {\em Math. Oper. Res.} {\bf 43} (2018), 516--532.
-
-	\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
-	      and Putinar, Mihai: Simultaneous kernels of matrix {H}adamard powers, {\em Linear Algebra Appl.} {\bf 576} (2019), 142--157.
-
-	\item Bera, Sayani and Verma, Kaushal: Some aspects of shift-like automorphisms of {$\mathbb C^k$},
-	      {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 128} (2018), Art.~10, 48.
-
-	\item Bhattacharyya, Tirthankar and Sau, Haripada: Holomorphic functions on the symmetrized
-	      bidisk\,---\,realization, interpolation and extension, {\em J. Funct. Anal.} {\bf 274} (2018), 504--524.
-
-	\item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
-	      Sundaram: Hermite multipliers on modulation spaces, {\em Analysis and partial differential equations:
-			      perspectives from developing countries} {\bf 275} (2019), 42--64.
-
-	\item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and Pingali, Vamsi P.: Rational cuspidal
-	      curves on del-{P}ezzo surfaces, {\em J. Singul.} {\bf 17} (2018), 91--107.
-
-	\item Biswas, Indranil and Pingali, Vamsi Pritham: A characterization of finite vector bundles on
-		      {G}auduchon astheno-{K}\"{a}hler manifolds, {\em \'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art.~6, 13.
-
-	\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi: Edge patch-wise local projection stabilized nonconforming
-		      {FEM} for the {O}seen problem, {\em Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214.
-
-	\item\label{Misra:symm-polydisc} Biswas, Shibananda and Ghosh, Gargi and Misra, Gadadhar and
-	      Shyam Roy, Subrata: On reducing submodules
-	      of {H}ilbert modules with {${S}_n$}-invariant kernels, {\em J. Funct. Anal.} {\bf 276} (2019), 751--784.
-
-	\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal: Comments on the {G}reen's function of a
-	      planar domain, {\em Anal. Math. Phys.} {\bf 8} (2018), 383--414.
-
-	\item Brenner, Susanne C. and Gudi, Thirupathi and Porwal, Kamana
-	      and Sung, Li-Yeng: A {M}orley finite element method for an elliptic distributed
-	      optimal control problem with pointwise state and control
-	      constraints, {\em ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206.
-
-	\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella: Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
-	      indefinite second-order linear elliptic problems, {\em Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.
-
-	\item Chandel, Vikramjeet Singh: The three-point {P}ick--{N}evanlinna interpolation problem on
-	      the polydisc, {\em Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352.
-
-	\item\label{rangarajan:Granger-causality} Chopra, R.
-and Murthy, C.
-R.
-and Rangarajan, G.: Statistical tests for detecting Granger causality, {\em IEEE Transactions on Signal Processing} {\bf } (2018), 5803--5816.
-
-	\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram: Hardy-type inequalities for fractional powers
-	      of the {D}unkl-{H}ermite operator, {\em Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544.
-
-	\item Dond, Asha K. and Gudi, Thirupathi: Patch-wise local projection stabilized finite element methods
-	      for convection-diffusion-reaction problems, {\em Numer. Methods Partial Differential Equations}
-		      {\bf 35} (2019), 638--663.
-
-	\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh Ch.: An error analysis of discontinuous finite element
-	      methods for the optimal control problems governed by {S}tokes equation, {\em Numer. Funct. Anal. Optim.}
-		      {\bf 40} (2019), 421--460.
-
-	\item Gaddam, Sharat and Gudi, Thirupathi: Inhomogeneous {D}irichlet boundary condition in the {\it a
-			      posteriori} error control of the obstacle problem, {\em Comput. Math. Appl.} {\bf 75} (2018), 2311--2327.
-
-	\item Gaddam, Sharat and Gudi, Thirupathi: Bubbles enriched quadratic finite element method for the
-	      3{D}-elliptic obstacle problem, {\em Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236.
-
-	\item Gaussier, Herv\'{e} and Seshadri, Harish: Holomorphic motions and complex geometry,
-	      {\em Proc. Amer. Math. Soc.} {\bf 147} (2019), 301--313.
-
-	\item Gaussier, Herv\'{e} and Seshadri, Harish, On the {G}romov hyperbolicity of convex domains in {$\mathbb
-				      C^n$}, {\em Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641.
-
-	\item Ghara, Soumitra and Kumar, Surjit: On the sum of two subnormal kernels, {\em J. Math. Anal. Appl.}
-		      {\bf 469} (2019), 1015--1027.
-
-	\item Ghara, Soumitra: The orbit of a bounded operator under the M{\"o}bius group modulo similarity equivalence.
-
-	\item Ghosh, Mrinal K. and Pradhan, Somnath: Risk-sensitive stochastic differential games with reflecting
-	      diffusions, {\em Stoch. Anal. Appl.} {\bf 36} (2018), 1--27.
-
-	\item Gudi, Thirupathi and Majumder, Papri: Convergence analysis of finite element method for a parabolic
-	      obstacle problem, {\em J. Comput. Appl. Math.} {\bf 357} (2019), 85--102.
-
-	\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: Von {N}eumann's inequality for commuting
-	      operator-valued multishifts, {\em Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.
-
-	\item Gupta, Rajeev and Ramiz Reza, Md.: Operator space structures on {$\ell^1(n)$}, {\em Houston J. Math.}
-		      {\bf 44} (2018), 1205--1212.
-
-	\item Hazra, Somnath: Homogeneous 2-shifts, {\em Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.
-
-	\item\label{iyer:connection-model} Iyer, Srikanth K.: The random connection model: connectivity, edge lengths,
-	      and degree distributions, {\em Random Structures Algorithms} {\bf 52} (2018), 283--300.
-
-	\item Kashyap, G.
-and Bapat, D.
-and Das, D.
-and Gowaikar, R.D.
-and  Amritkar, R.E.
-and Rangarajan, G.
-and V.
-Ravindranath and G.
-Ambika: Synapse loss and progress of Alzheimer's disease\,--\,A network model,
-	      {\em Scientific Reports} {\bf 9} (2019).
-
-	\item Khare, Apoorva and Tao, Terence: Schur polynomials, entrywise positivity preservers, and weak
-	      majorization, {\em S\'em. Lothar. Combin.} {\bf 80B,} (2018).
-
-	\item Lin, X.
-and Kulkarni, P.
-and Bocci, F.
-and Schafer, N.
-and Roy, S.
-and Tsai, M-Y.
-and He, Y.
-and Chen, Y and Rajagopalan, K.
-and Mooney, S.
-and Zeng, Y.
-and Weninger, K.
-and Grishaev, A.
-and Onuchic, J.
-and Levine, H.
-and Wolynes, P.
-and Salgia, R.
-and Rangarajan, G.
-and Uversky, V.
-and Orban, J.
-and Jolly, M.
-K.: Structural and
-	      dynamical order of a disordered protein: molecular insights into conformational
-	      switching of PAGE4 at the systems level, {\em Biomolecules} {\bf 9} (2019), 77.
-
-	\item\label{rangarajan:prostate-cancer} Lin, X.
-and Roy, S.
-and Jolly, M.
-K.
-and Bocci, F.
-and Schafer, N.
-P.
-and Tsai, M.-Y.
-and Chen, Y.
-and He, Y.
-and Grishaev, A.
-and Weninger, K.
-and Orban, J.
-and Kulkarni, P.
-and Rangarajan, G.
-and Levine, H.
-and J.
-N.
-Onuchic: PAGE4 and conformational switching: Insights from molecular dynamics simulations and implications for
-	      prostate cancer, {\em Journal of Molecular Biology} {\bf 430} (2018), 2422--2438.
-
-	\item Mahajan, Prachi and Verma, Kaushal: A comparison of two biholomorphic invariants, {\em Internat. J. Math.} {\bf 30} (2019), 1950012, 16 pp.
-
-	\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: On some geometric properties of operator spaces, {\em Banach J. Math. Anal.} {\bf 13} (2019), 174--191.
-
-	\item Manfio, F. and Turgay, N. C. and Upadhyay, A.: Biconservative submanifolds in
-		      {$\mathbb{S}^n\times\mathbb{R}$} and
-		      {$\mathbb{H}^n\times\mathbb{R}$}, {\em J. Geom. Anal.} {\bf 29} (2019), 283--298.
-
-	\item Manikandan, K. and Vishnu Priya, N. and Senthilvelan, M. and
-	      Sankaranarayanan, R.: Deformation of dark solitons in a {$\mathcal{PT}$}-invariant
-	      variable coefficients nonlocal nonlinear {S}chr\"{o}dinger
-	      equation, {\em Chaos} {\bf 28} (2018), 083103, 12.
-
-	\item Misra, Gadadhar and Pal, Avijit: Curvature inequalities for operators in the {C}owen--{D}ouglas
-	      class and localization of the {W}allach set, {\em J. Anal. Math.} {\bf 136} (2018), 31--54.
-
-	\item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian: Contractivity and complete contractivity for finite dimensional Banach spaces, {\em J. Operator Theory} {\bf 82} (2019), 23--47.
-
-	\item Pal, Chandan and Pradhan, Somnath: Risk sensitive control of pure jump processes on a general
-	      state space, {\em Stochastics} {\bf 91} (2019), 155--174.
-
-	\item Pal, Ratna and Verma, Kaushal: Ergodic properties of families of {H}\'{e}non maps, {\em Ann. Polon. Math.}
-		      {\bf 121} (2018), 45--71.
-
-	\item Paul, Kallol and Sain, Debmalya: Birkhoff--{J}ames orthogonality and its application in the
-	      study of geometry of {B}anach space, {\em Advanced topics in mathematical analysis} {\bf } (2019), 245--284.
-
-	\item Paul, Kallol and Sain, Debmalya and Mal, Arpita: Approximate {B}irkhoff--{J}ames orthogonality in the space of
-	      bounded linear operators, {\em Linear Algebra Appl.} {\bf 537} (2018), 348--357.
-
-	\item Paul, Kallol and Sain, Debmalya and Mal, Arpita and Mandal,
-	      Kalidas: Orthogonality of bounded linear operators on complex {B}anach
-	      spaces, {\em Adv. Oper. Theory} {\bf 3} (2018), 699--709.
-
-	\item Pingali, Vamsi P.: A note on the deformed {H}ermitian {Y}ang--{M}ills {PDE}, {\em Complex Var. Elliptic Equ.}
-		      {\bf 64} (2019), 503--518.
-
-	\item Pingali, Vamsi Pritham: A note on higher extremal metrics, {\em Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010.
-
-	\item Pingali, Vamsi Pritham: Representability of {C}hern--{W}eil forms, {\em Math. Z.} {\bf 288} (2018), 629--641.
-
-	\item Pritham Pingali, Vamsi: Existence of coupled {K}\"{a}hler--{E}instein metrics using the
-	      continuity method, {\em Internat. J. Math.} {\bf 29} (2018), 1850041, 8.
-
-	\item Reddy, Nanda Kishore: Equality of {L}yapunov and stability exponents for products of
-	      isotropic random matrices, {\em Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624.
-
-	\item Reza, Md. Ramiz: Curvature inequalities for operators in the {C}owen--{D}ouglas
-	      class of a planar domain, {\em Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279.
-
-	\item Sain, Debmalya: On extreme contractions and the norm attainment set of a
-	      bounded linear operator, {\em Ann. Funct. Anal.} {\bf 10} (2019), 135--143.
-
-	\item Sain, Debmalya: On the norm attainment set of a bounded linear operator, {\em J. Math. Anal. Appl.} {\bf 457} (2018), 67--76.
-
-	\item Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag,
-	      Santanu: On the numerical index of polyhedral {B}anach spaces, {\em Linear Algebra Appl.} {\bf 577} (2019), 121--133.
-
-	\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: A complete characterization of {B}irkhoff--{J}ames
-	      orthogonality in infinite dimensional normed space, {\em J. Operator Theory} {\bf 80} (2018), 399--413.
-
-	\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: On approximate {B}irkhoff--{J}ames orthogonality and normal
-	      cones in a normed space, {\em J. Convex Anal.} {\bf 26} (2019), 341--351.
-
-	\item\label{rangarajan:microtremor-method} Sant, D.A.
-and Parvez, I.
-A.
-and Rangarajan, G.
-and Patel, S.
-J.
-and Salam, T.
-A.
-S.
-and Bhatt, M.
-N.: Subsurface imaging of brown coal bearing Tertiary sedimentaries\,---\,Deccan Trap
-	      interface using microtremor method, {\em Journal of Applied Geophysics} {\bf 159} (2018), 362--373.
-
-	\item Seshadri, Harish and Verma, Kaushal: Some aspects of the automorphism groups of domains {\em Handbook of group actions, {V}ol.~{III}} {\bf 40} (2018), 145--174.
-
-	\item Thangavelu, Sundaram: An analogue of {P}fannschmidt's theorem for the {H}eisenberg
-	      group, {\em J. Anal.} {\bf 26} (2018), 235--244.
-
-	\item Thangavelu, Sundaram and Naidu Dogga, Venku: {$L^p$}-{$L^2$} estimates for solutions of the wave equation
-	      associated to the {G}rushin operator, {\em Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92.
-
-	\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh: On biconservative hypersurfaces in 4-dimensional {R}iemannian
-	      space forms, {\em Math. Nachr.} {\bf 292} (2019), 905--921.
-
-	\item Verma, Kaushal: Notes on the boundaries of quadrature domains, {\em Anal. Math. Phys.} {\bf 9} (2019), 617--638.
-
-	\item Vishnu Priya, N. and Senthilvelan, M. and  Rangarajan, Govindan
-	      and Lakshmanan, M.: On symmetry preserving and symmetry broken bright, dark and
-	      antidark soliton solutions of nonlocal nonlinear {S}chr\"{o}dinger
-	      equation, {\em Phys. Lett. A} {\bf 383} (2019), 15--26.
-\end{enumerate}
-
-\noindent{{\small {\sl In other areas:}}}\vspace{-2.5mm}
-
-\begin{enumerate}[resume, leftmargin=27pt]
-	\item Anamby, Pramath and Das, Soumya: Distinguishing {H}ermitian cusp forms of degree 2 by
-	      a certain subset of all {F}ourier coefficients, {\em Publ. Mat.} {\bf 63} (2019), 307--341.
-
-	\item Anamby, Pramath and Das, Soumya: Bounds for the {P}etersson norms of the pullbacks of
-		      {S}aito-{K}urokawa lifts, {\em J. Number Theory} {\bf 191} (2018), 289--304.
-
-	\item Arunkumar, G. and Kus, Deniz and Venkatesh, R.: Root multiplicities for {B}orcherds
-	      algebras and graph coloring, {\em J. Algebra} {\bf 499} (2018), 538--569.
-
-	\item\label{ayyer:plane-partitions} Ayyer, Arvind and Behrend, Roger E.: Factorization theorems for classical group characters,
-	      with applications to alternating sign matrices and plane
-	      partitions, {\em J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.
-
-	\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven: Odd partitions in {Y}oung's lattice,
-	      {\em S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
-
-	\item Balodi, Mamta and Palcoux, Sebastien: On {B}oolean intervals of finite groups, {\em J. Combin. Theory Ser. A} {\bf 157}
-	      (2018), 49--69.
-
-	\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
-	      Christopher R.H. and Harris, Pamela E. and Khare, Apoorva and
-	      Morales, Alejandro H. and Yip, Martha: The volume of the caracol polytope, {\em S\'{e}m. Lothar. Combin.}
-	      {\bf 80B} (2018), Art.~87, 12.
-
-	\item Bhosle, Usha N.: Hitchin pairs on reducible curves, {\em Internat. J. Math.} {\bf 29}
-	      (2018), 1850015, 49.
-
-	\item B\"{o}cherer, Siegfried and Das, Soumya: Cuspidality and the growth of {F}ourier coefficients of
-	      modular forms, {\em J. Reine Angew. Math.} {\bf 741} (2018), 161--178.
-
-	\item B\"{o}cherer, Siegfried and Das, Soumya: Petersson norms of not necessarily cuspidal {J}acobi
-	      modular forms and applications, {\em Adv. Math.} {\bf 336} (2018), 335--376.
-
-	\item Banerjee, Abhishek: On {A}uslander's formula and cohereditary torsion pairs, {\em Commun. Contemp. Math.} {\bf 20} (2018),
-	      1750071, 27.
-
-	\item Banerjee, Abhishek: Modular {H}ecke algebras over {M}\"{o}bius categories, {\em J. Geom. Phys.} {\bf 131} (2018), 23--40.
-
-	\item Banerjee, Abhishek: A topological {N}ullstellensatz for tensor-triangulated
-	      categories, {\em C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375.
-
-	\item Banerjee, Abhishek: Quasimodular {H}ecke algebras and {H}opf actions, {\em J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080.
-
-	\item Banerjee, Abhishek: Completions of monoid objects and descent results, {\em J. Algebra} {\bf 507} (2018), 362--399.
-
-	\item Burton, Benjamin A. and Datta, Basudeb and Singh, Nitin and
-	      Spreer, Jonathan: A construction principle for tight and minimal triangulations
-	      of manifolds, {\em Exp. Math.} {\bf 27} (2018), 22--36.
-
-	\item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
-	      K. C.: A note on linear preservers of semipositive and minimally
-	      semipositive matrices, {\em Electron. J. Linear Algebra} {\bf 34} (2018), 687--694.
-
-	\item Das, Soumya and Khan, Rizwanur: The third moment of symmetric square {$L$}-functions, {\em Q. J. Math.} {\bf 69} (2018),
-	      1063--1087.
-
-	\item Das, Soumya and Kohnen, Winfried: On sign changes of eigenvalues of {S}iegel cusp forms of genus
-	      2 in prime powers, {\em Acta Arith.} {\bf 183} (2018), 167--172.
-
-	\item Datta, Basudeb and Maity, Dipendu: Semi-equivelar maps on the torus and the {K}lein bottle are
-		      {A}rchimedean, {\em Discrete Math.} {\bf 341} (2018), 3296--3309.
-
-	\item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P.
-and Silberman, Lior and Tao, Terence: Homogeneous length functions on groups, {\em Algebra Number Theory} {\bf 12} (2018), 1773--1786.
-
-	\item\label{gupta:measured-foliations} Gupta, Subhojoy and Wolf, Michael: Meromorphic quadratic differentials and measured foliations on a Riemann surface, {\em Math Ann.} {\bf 373} (2019), 73--118.
-
-	\item Jha, Abhash Kumar and Sahu, Brundaban: Rankin--{C}ohen brackets on {J}acobi forms of several variables
-	      and special values of certain {D}irichlet series, {\em Int. J. Number Theory} {\bf 15} (2019), 925--933.
-
-	\item Khare, Apoorva: Generalized nil-{C}oxeter algebras over discrete complex
-	      reflection groups, {\em Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999.
-
-	\item Khare, Apoorva: Generalized nil-Coxeter algebras, {\em S\'em Lothar. Combin.} {\bf 80B,} (2018), No.~29.
-
-	\item Khare, Apoorva and Tikaradze, Akaki: A {C}arlitz--von {S}taudt type theorem for finite rings,
-	      {\em Linear Algebra Appl.} {\bf 568} (2019), 106--126.
-
-	\item Krakovski, Roi and Onn, Uri and Singla, Pooja: Regular characters of groups of type {$A_n$} over
-	      discrete valuation rings, {\em J. Algebra} {\bf 496} (2018), 116--137.
-
-	\item Maity, Dipendu: Pentagonal maps on the torus and the plane, {\em Beitr. Algebra Geom.} {\bf 60} (2019), 17--37.
-
-	\item Maity, Dipendu and Upadhyay, Ashish Kumar: On centrally symmetric manifolds, {\em J. Ramanujan Math. Soc.} {\bf 34}
-	      (2019), 21--27.
-
-	\item Mukherjee, Sajal Kumar and Bera, Sudip: Combinatorial proofs of the {N}ewton--{G}irard and
-		      {C}hapman--{C}ostas--{S}antos identities, {\em Discrete Math.} {\bf 342} (2019), 1577--1580.
-
-	\item Narayanan, E. K. and Singla, Pooja: On monomial representations of finitely generated nilpotent
-	      groups, {\em Comm. Algebra} {\bf 46} (2018), 2319--2331.
-
-	\item Quddus, Safdar: Invariants of the {$\mathbb Z_2$} orbifolds of the {P}odle\'{s} two
-	      spheres, {\em J. Noncommut. Geom.} {\bf 13} (2019), 257--267.
-
-	\item Sanki, Bidyut: Filling of closed surfaces, {\em J. Topol. Anal.} {\bf 10} (2018), 897--913.
-
-	\item Sanki, Bidyut and Gadgil, Siddhartha: Graphs of systoles on hyperbolic surfaces, {\em J. Topol. Anal.}
-		      {\bf 11} (2019), 1--20.
-
-\end{enumerate}
-\vspace{0.5mm}
-
-%% YEAR 2 LISTING %%%%%
-\noindent{{\small {\bf April 2019--March 2020:}}}
-\medskip
-
-\noindent{{\small {\sl In the identified thrust area:}}}\vspace{-2.5mm}
-
-\begin{enumerate}[resume, leftmargin=27pt]
-	\item Aas, Erik and Ayyer, Arvind and Linusson, Svante and Potka,
-	      Samu: \href{https://doi.org/10.1088/1751-8121/ab2e96}{The exact phase diagram for a
-		      semipermeable {TASEP} with nonlocal boundary jumps}, \emph{J. Phys. A} {\bf 52} (2019),
-	      355001, 19.
-
-	\item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
-	      Nandakumaran, A. K.: \href{https://doi.org/10.3233/asy-191526}{Control problem on a rough
-		      circular domain and homogenization}, \emph{Asymptot. Anal.} {\bf 115} (2019), 19--46.
-
-	\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1007/s10231-019-00848-7}{Locally periodic unfolding operator for highly oscillating
-		      rough domains}, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954.
-
-	\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1142/S0219199719500299}{Semi-linear optimal control problem on a smooth oscillating
-		      domain}, \emph{Commun. Contemp. Math.} {\bf 22} (2020), 1950029, 26.
-
-	\item Aiyappan, S.
-and Nandakumaran, A.
-K.
-and Sufian, Abu: \href{https://doi.org/10.1002/mma.5748}{Asymptotic analysis of a boundary optimal control problem on a general branched structure}, \emph{Math.
-Methods Appl.
-Sci.} {\bf 42} (2019), 6407--6434.
-
-	\item Aiyappan, S. and Sardar, Bidhan Chandra: \href{https://doi.org/10.1080/00036811.2018.1471207}{Biharmonic equation in a highly oscillating domain and
-		      homogenization of an associated control problem}, \emph{Appl. Anal.} {\bf 98} (2019), 2783--2801.
-
-	\item Anand, Jatin and Bhattacharyya, Tirthankar and Srivastava,
-	      Sachi: \href{https://doi.org/10.1007/s00013-019-01406-6}{Some thoughts on composition operators on subspaces of the
-			      {H}ardy space}, \emph{Arch. Math. (Basel)} {\bf 114} (2020), 431--444.
-
-	\item Ayyer, Arvind and Behrend, Roger E. and Fischer, Ilse: \href{https://doi.org/10.1016/j.aim.2020.107125}{Extreme diagonally and antidiagonally symmetric alternating
-		      sign matrices of odd order}, \emph{Adv. Math.} {\bf 367} (2020), 107125, 56.
-
-	\item Ayyer, Arvind and Behrend, Roger E.: \href{https://doi.org/10.1016/j.jcta.2019.01.001}{Factorization theorems for classical group characters, with
-		      applications to alternating sign matrices and plane
-		      partitions}, \emph{J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.
-
-	\item Ayyer, Arvind and Fischer, Ilse: \href{https://doi.org/10.1016/j.jcta.2020.105241}{Bijective proofs of skew {S}chur polynomial factorizations}, \emph{J.
-Combin.
-Theory Ser.
-A} {\bf 174} (2020), 105241, 40.
-
-	\item Ayyer, Arvind and Linusson, Svante: \href{https://doi.org/10.1002/rsa.20825}{Reverse juggling processes}, \emph{Random Structures Algorithms} {\bf 55} (2019), 56--72.
-
-	\item\label{ayyer-singla:commutative-rings} Ayyer, Arvind and Singla, Pooja:
-	      \href{https://doi.org/10.1007/s10468-019-09864-w}{Random motion on finite rings, {I}: commutative
-		      rings}, \emph{Algebr. Represent. Theory} {\bf 23} (2020), 583--604.
-
-	\item Ayyer, Arvind: \href{https://doi.org/10.1007/s00026-019-00480-5}{Squareness for the {M}onopole-{D}imer model}, \emph{Ann. Comb.} {\bf 24} (2020), 237--255.
-
-	\item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
-	      Verma, Kaushal: \href{https://doi.org/10.1090/proc/14421}{Remarks on the higher dimensional {S}uita conjecture}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411.
-
-	\item Bera, Sayani and Pal, Ratna and Verma, Kaushal: \href{https://doi.org/10.1007/s40879-019-00326-7}{A rigidity theorem for {H}\'{e}non maps}, \emph{Eur. J. Math.} {\bf 6} (2020), 508--532.
-
-	\item Bharali, Gautam and Chandel, Vikramjeet Singh: \href{https://doi.org/10.1007/s11785-017-0701-5}{Pick interpolation on the polydisc: small families of
-		      sufficient kernels}, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093.
-
-	\item Bharali, Gautam: \href{https://doi.org/10.1007/s12220-019-00342-9}{On the growth of the {B}ergman metric near a point of infinite
-		      type}, \emph{J. Geom. Anal.} {\bf 30} (2020), 1238--1258.
-
-	\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107.
-
-	\item\label{Bhattacharyya:symm-bidisc} Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz
-	      operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} (2020).
-
-	\item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K.: \href{https://doi.org/10.1007/s13226-019-0345-4}{Survey of last ten years of work done in {I}ndia in some
-		      selected areas of functional analysis and operator theory}, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617.
-
-	\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram: \href{https://doi.org/10.3934/cpaa.2019116}{On extension problem, trace {H}ardy and {H}ardy's inequalities
-		      for some fractional {L}aplacians}, \emph{Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605.
-
-	\item Chakraborty, Atlanta and Chandru, Vijay and Rao, M.
-R.: \href{https://doi.org/10.1007/s10479-019-03186-2}{A linear programming primer: from {F}ourier to {K}armarkar}, \emph{Ann.
-Oper.
-Res.} {\bf 287} (2020), 593--616.
-
-	\item Chandel, Vikramjeet Singh: \href{https://doi.org/10.1007/s12220-018-00123-w}{The 3-point spectral pick interpolation problem and an
-		      application to holomorphic correspondences}, \emph{J. Geom. Anal.} {\bf 30} (2020), 551--572.
-
-	\item Cicuttin, Matteo and Ern, Alexandre and Gudi, Thirupathi: \href{https://doi.org/10.1007/s10915-020-01195-z}{Hybrid high-order methods for the elliptic obstacle problem}, \emph{J.
-Sci.
-Comput.} {\bf 83} (2020), Paper No.
-8, 18.
-
-	\item Gudi, Thirupathi and Majumder, Papri: \href{https://doi.org/10.1016/j.camwa.2019.06.022}{Conforming and discontinuous {G}alerkin {FEM} in space for
-	      solving parabolic obstacle problem}, \emph{Comput. Math. Appl.} {\bf 78} (2019), 3896--3915.
-
-	\item Gudi, Thirupathi and Majumder, Papri: \href{https://doi.org/10.1515/cmam-2019-0057}{Crouzeix-{R}aviart finite element approximation for the
-	      parabolic obstacle problem}, \emph{Comput. Methods Appl. Math.} {\bf 20} (2020), 273--292.
-
-	\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: \href{https://doi.org/10.1090/proc/14410}{Von {N}eumann's inequality for commuting operator-valued
-		      multishifts}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.
-
-	\item Iyer, S.
-K.
-and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897.
-
-	\item K.
-Murali, A.
-K.
-Nandakumaran, Turgurt Durduran, Hari M Varma: Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements, \emph{Biomedical Optics Express 5395} {\bf 10} (2019).
-
-	\item Kashyap, G.
-A.
-R.
-S.
-R.
-K.
-and Bapat, D.
-and Das, D.
-and Gowaikar, R.
-D.
-and  Amritkar, R.
-E.
-and Rangarajan, G.
-and V.
-Ravindranath and G.
-Ambika: Synapse loss and progress of Alzheimers disease - A network model, \emph{Scientific Reports} {\bf 9} (2019).
-
-	\item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan: \href{https://doi.org/10.1080/07362994.2018.1538803}{On the convolution of {M}ittag-{L}effler distributions and its
-	      applications to fractional point processes}, \emph{Stoch. Anal. Appl.} {\bf 37} (2019), 115--122.
-
-	\item Khan, Mohammad Yasir Feroz and Biswas, Rahul and Sau, Ramesh
-	      Chandra: Instability of {L}agrange interpolation on {$H^1(\Omega)\cap
-				      C(\overline\Omega)$}, \emph{Math. Student} {\bf 88} (2019), 153--158.
-
-	\item Khare, Apoorva and Tikaradze, Akaki: \href{https://doi.org/10.1016/j.laa.2018.05.035}{A {C}arlitz--von {S}taudt type theorem for finite rings}, \emph{Linear Algebra Appl.} {\bf 568} (2019), 106--126.
-	\item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric semigroups, \emph{Advances in Operator Theory (Special issue in honor of Rajendra Bhatia)} {\bf 5} (2020), 779-795.
-
-	\item Kor\'{a}nyi, Adam and Misra, Gadadhar: Homogeneous Hermitian holomorphic vector bundles and the Cowen-Douglas class over bounded symmetric domains, \emph{Adv.
-Math.} {\bf 351} (2019), 1105 - 1138.
-
-	\item Maitra, Anwoy: On the continuous extension of Kobayashi isometries, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.
-
-	\item Maitra, Anwoy: \href{https://doi.org/10.1016/j.jmaa.2019.123694}{A form of {S}chwarz's lemma and a bound for the {K}obayashi
-		      metric on convex domains}, \emph{J. Math. Anal. Appl.} {\bf 484} (2020), 123694, 16.
-	\item Mal, Arpita and Paul, Kallol and Rao, T. S. S. R. K. and Sain,
-	      Debmalya: \href{https://doi.org/10.1007/s00605-019-01289-3}{Approximate {B}irkhoff-{J}ames orthogonality and smoothness in
-	      the space of bounded linear operators}, \emph{Monatsh. Math.} {\bf 190} (2019), 549--558.
-
-	\item Maitra, Anwoy: \href{https://doi.org/10.1090/proc/15038}{On the continuous extension of {K}obayashi isometries}, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.
-
-	\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: \href{https://projecteuclid.org/euclid.bjma/1543914019}{On some geometric properties of operator spaces}, \emph{Banach J.
-Math.
-Anal.} {\bf 13} (2019), 174-191.
-
-	\item Misra, Gadadhar and Reza, Md. Ramiz: \href{https://doi.org/10.1215/00192082-7768711}{Curvature inequalities and extremal operators}, \emph{Illinois J. Math.} {\bf 63} (2019), 193--217.
-
-	\item Nikolov, Nikolai and Verma, Kaushal: \href{https://doi.org/10.1007/s12220-019-00237-9}{On the squeezing function and {F}ridman invariants}, \emph{J. Geom. Anal.} {\bf 30} (2020), 1218--1225.
-
-	\item Paul, Kallol and Sain, Debmalya and Ghosh, Puja: Symmetry of {B}irkhoff-{J}ames orthogonality of bounded linear
-	      operators, \emph{Ulam type stability} {\bf } (2019), 331--344.
-
-	\item Poria, Anirudha: \href{https://doi.org/10.1080/01630563.2020.1728771}{Positive weight function and classification of {$g$}-frames}, \emph{Numer. Funct. Anal. Optim.} {\bf 41} (2020), 950--968.
-
-	\item Roth, Julien and Upadhyay, Abhitosh: \href{https://doi.org/10.1007/s00013-019-01315-8}{On compact anisotropic {W}eingarten hypersurfaces in
-			      {E}uclidean space}, \emph{Arch. Math. (Basel)} {\bf 113} (2019), 213--224.
-
-	\item Roth, Julien and Upadhyay, Abhitosh: \href{https://doi.org/10.1017/s0004972719000935}{On almost stable {CMC} hypersurfaces in manifolds of bounded
-		      sectional curvature}, \emph{Bull. Aust. Math. Soc.} {\bf 101} (2020), 333--338.
-
-	\item Roth, Julien and Upadhyay, Abhitosh: \href{https://link.springer.com/article/10.1007/s00025-019-1142-4?shared-article-renderer#citeas}{f-Biharmonic Submanifolds of Generalized Space Forms}, \emph{Results in Mathematics} {\bf 75} (2020).
-
-	\item Roth, Julien and Upadhyay, Abhitosh: \href{https://www.cambridge.org/core/journals/bulletin-of-the-australian-mathematical-society/article/on-almost-stable-cmc-hypersurfaces-in-manifolds-of-bounded-sectional-curvature/E0BF84D4D46C82F6D75CDCEAAF5DEE94}{On almost stable CMC hypersurfaces in manifolds of bounded sectional curvature}, \emph{Bulletin of the Australian Mathematical Society} {\bf 101} (2020), 333-338.
-
-	\item Sain, Debmalya and Mal, Arpita and Paul, Kallol: \href{https://doi.org/10.1016/j.exmath.2019.01.001}{Some remarks on {B}irkhoff-{J}ames orthogonality of linear
-	      operators}, \emph{Expo. Math.} {\bf 38} (2020), 138--147.
-
-	\item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas: \href{https://doi.org/10.7153/oam-2019-13-31}{On two extremum problems related to the norm of a bounded
-		      linear operator}, \emph{Oper. Matrices} {\bf 13} (2019), 421--432.
-
-	\item Sain, Debmalya and Ray, Anubhab and Paul, Kallol: Extreme contractions on finite-dimensional polygonal {B}anach
-	      spaces, \emph{J. Convex Anal.} {\bf 26} (2019), 877--885.
-
-	\item Sain, Debmalya: \href{https://doi.org/10.1007/s13226-020-0393-9}{On the norm attainment set of a bounded linear
-		      operator and
-		      semi-inner-products in normed spaces}, \emph{Indian J. Pure Appl. Math.} {\bf 51} (2020), 179--186.
-
-	\item Sain, Debmalya: \href{https://doi.org/10.7153/oam-2019-13-32}{Smooth points in operator spaces and some
-		      {B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces}, \emph{Oper. Matrices} {\bf 13} (2019), 433--445.
-
-	\item Sarkar, Amar Deep and Verma, Kaushal: A submultiplicative property of the Carath\'{e}odory metric on planar domains, \emph{Proc. Indian Acad. Sci. (Math. Sci.)} {\bf 130} (2020).
-
-	\item Sarkar, Amar Deep and Verma, Kaushal: \href{https://doi.org/10.1007/s40315-020-00303-2}{Boundary behaviour of some conformal invariants on planar
-		      domains}, \emph{Comput. Methods Funct. Theory} {\bf 20} (2020), 145--158.
-
-	\item Vishnu Priya, N.
-and Senthilvelan, M.
-and  Rangarajan, G.
-and Lakshmanan, M: On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation, \emph{Physics Letters A} {\bf 383} (2019), 15-26.
-
-	\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan,
-	      Govindan: \href{https://doi.org/10.1063/1.5121245}{On the role of four-wave mixing effect in the interactions
-	      between nonlinear modes of coupled generalized nonlinear
-		      {S}chr\"{o}dinger equation}, \emph{Chaos} {\bf 29} (2019), 123135, 14.
-
-	\item Vishnu Priya, N.
-and Senthilvelan, M.
-and Rangarajan, G.: On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, \emph{Chaos} {\bf 29} (2019), 123135.\end{enumerate}
-
-\noindent{{\small {\sl In other areas:}}}\vspace{-2.5mm}
-
-\begin{enumerate}[resume, leftmargin=27pt]
-
-	\item Anamby, Pramath and Das, Soumya: \href{https://doi.org/10.5565/PUBLMAT6311911}{Distinguishing
-			      {H}ermitian cusp forms of degree 2 by a certain subset of all {F}ourier coefficients},
-	      \emph{Publ. Mat.} {\bf 63} (2019), 307--341.
-
-	\item Banerjee, Abhishek and Kour, Surjeet: \href{https://doi.org/10.1007/s10231-019-00844-x}{{$(A,\delta)$}-modules, {H}ochschild homology and higher
-		      derivations}, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802.
-
-	\item Banerjee, Abhishek: \href{https://doi.org/10.4153/s0008439518000656}{On differential torsion theories and rings with
-		      several objects}, \emph{Canad. Math. Bull.} {\bf 62} (2019), 703--714.
-
-	\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
-	      Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
-	      Morales, Alejandro H.
-and Yip, Martha: \href{https://doi.org/10.1090/tran/7743}{A combinatorial model for computing volumes of flow polytopes}, \emph{Trans.
-Amer.
-Math.
-Soc.} {\bf 372} (2019), 3369--3404.
-
-	\item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy: Branched projective structures on a {R}iemann surface and
-	      logarithmic connections, \emph{Doc. Math.} {\bf 24} (2019), 2299--2337.
-
-	\item Carstensen, C.
-and Mallik, G.
-and Nataraj, N.: \href{https://doi.org/10.1093/imanum/drz071}{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, \emph{IMA Journal of Numerical Analysis} {\bf } (2020).
-
-	\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala: On Baker's explicit abc-conjecture, \emph{Publ. Math. Debrecen} {\bf 94} (2019), 435–453.
-
-	\item Choudhury, Projesh Nath and Tsatsomeros Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic Detection and Construction of N-matrices}, \emph{Linear Algebra and Its Applications} {\bf 602} (2020), 46-56.
-
-	\item Choudhury, Projesh Nath and Tsatsomeros, Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic detection and construction of {N}-matrices}, \emph{Linear Algebra Appl.} {\bf 602} (2020), 46--56.
-
-	\item Das, Soumya and Jha, Abhash Kumar: \href{https://doi.org/10.1007/s12188-019-00206-7}{Analytic properties of twisted real-analytic {H}ermitian
-	      {K}lingen type {E}isenstein series and applications}, \emph{Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116.
-
-	\item Das, Soumya and Pal, Ritwik: \href{https://doi.org/10.1007/s40993-019-0158-x}{The first negative eigenvalue of {Y}oshida lifts}, \emph{Res. Number Theory} {\bf 5} (2019), Paper No. 20, 9.
-
-	\item Datt, Gopal and Kumar, Sanjay: \href{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}{A criterion for quasinormality in $\mathbb{C}^n$}, \emph{Proc.
-Indian Acad.
-Sci.
-Math.
-Sci.} {\bf 129} (2019), Paper No.
-11, 13 pp.
-
-	\item Datta, B. and Maity, D.: Correction to: Semi-equivelar and vertex-transitive maps on the torus, \emph{Beitr Algebra Geom} {\bf 61} (2020), 187--188.
-
-	\item Datta, B. and Sarkar, S.: Equilibrium triangulations of some quasitoric 4-manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57--78.
-
-	\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor: Higher Chern Classes in Iwasawa Theory, \emph{American Journal of Mathematics} {\bf 142} (2020), 627--682.
-
-	\item Gadgil, Siddhartha: \href{https://doi.org/10.1007/s10817-019-09523-1}{Homogeneous {L}ength {F}unctions on {G}roups: {I}ntertwined
-	      {C}omputer and {H}uman {P}roofs}, \emph{J. Automat. Reason.} {\bf 64} (2020), 677--688.
-
-	\item Garani, Shayan Srinivasa and Seshadri, Harish: \href{https://doi.org/10.1080/17459737.2019.1604845}{An algorithmic approach to {S}outh {I}ndian classical music}, \emph{J.
-Math.
-Music} {\bf 13} (2019), 107--134.
-
-	\item Gupta, Subhojoy and Mj, Mahan: \href{https://doi.org/10.1090/proc/14866}{Monodromy representations of meromorphic projective
-		      structures}, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 2069--2078.
-
-	\item Gupta, Subhojoy and Seshadri, Harish: \href{https://doi.org/10.1093/imrn/rny204}{On domains biholomorphic to {T}eichm\"{u}ller spaces}, \emph{Int.
-Math.
-Res.
-Not.
-IMRN} {\bf } (2020), 2542--2560.
-
-	\item Gupta, Subhojoy and Wolf, Michael: \href{https://doi.org/10.1007/s00208-018-1674-z}{Meromorphic quadratic differentials and measured foliations on
-		      a {R}iemann surface}, \emph{Math. Ann.} {\bf 373} (2019), 73--118.
-
-	\item Gupta, Subhojoy: \href{https://doi.org/10.1090/tran/7777}{Limits of harmonic maps and crowned hyperbolic surfaces}, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 7573--7596.
-
-	\item Hatui, Sumana: \href{https://doi.org/10.1515/jgth-2019-0045}{Schur multipliers of special {$p$}-groups of rank 2}, \emph{J. Group Theory} {\bf 23} (2020), 85--95.
-
-	\item Hatui, Sumana: \href{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}{Schur multipliers of special p-groups of rank 2}, \emph{Journal of Group Theory} {\bf 23} (2020), 85-95.
-
-	\item Jha, Abhash Kumar and Juyal, Abhishek and Pandey, Manish
-	      Kumar: On simultaneous non-vanishing of twisted {$L$}-functions
-	      associated to newforms on {$\Gamma_0(N)$}, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.
-
-	\item Jha, Abhash Kumar and Sahu, Brundaban: \href{https://doi.org/10.1090/conm/732/14793}{Differential operators on {J}acobi forms and special values of
-		      certain {D}irichlet series}, \emph{Automorphic forms and related topics} {\bf 732} (2019), 91--99.
-
-	\item Jha, Abhash Kumar and Sahu, Brundaban: \href{https://doi.org/10.1142/S1793042119500490}{Rankin-{C}ohen brackets on {J}acobi forms of several variables
-	      and special values of certain {D}irichlet series}, \emph{Int. J. Number Theory} {\bf 15} (2019), 925--933.
-
-	\item Maiti, Arun: \href{https://doi.org/10.1016/j.disc.2020.111911}{Quasi-vertex-transitive maps on the plane}, \emph{Discrete Math.} {\bf 343} (2020), 111911, 7.
-
-	\item Maiti, Arun: \href{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}{Quasi-vertex-transitive maps on the plane}, \emph{Discrete Mathematics} {\bf 343} (2020), 111911-111917.
-
-	\item Maity, Dipendu: \href{https://doi.org/10.1007/s13366-018-0405-7}{Pentagonal maps on the torus and the plane}, \emph{Beitr. Algebra Geom.} {\bf 60} (2019), 17--37.
-	\item Maity, Dipendu and Upadhyay, Ashish Kumar: On centrally symmetric manifolds, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 21--27.
-
-	\item Mukherjee, Sajal Kumar and Bera, Sudip: \href{https://doi.org/10.1016/j.disc.2019.02.013}{Combinatorial proofs of the {N}ewton-{G}irard and
-		      {C}hapman-{C}ostas-{S}antos identities}, \emph{Discrete Math.} {\bf 342} (2019), 1577--1580.
-
-	\item Pingali, Vamsi Pritham: \href{https://doi.org/10.1007/s11005-020-01279-9}{Quillen metrics and perturbed equations}, \emph{Lett. Math. Phys.} {\bf 110} (2020), 1861--1875.
-
-	\item Pingali, Vamsi Pritham: \href{https://doi.org/10.1016/j.aim.2019.106921}{A vector bundle version of the {M}onge-{A}mp\`ere equation}, \emph{Adv. Math.} {\bf 360} (2020), 106921, 40.
-
-	\item Pradhan, P.
-and Sahu, B.: \href{https://doi.org/10.1016/j.disc.2020.112044}{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, \emph{Discrete Mathematics} {\bf 343} (2020).
-
-	\item Quddus, Safdar: \href{https://doi.org/10.4171/JNCG/320}{Invariants of the {$\mathbb{Z}_2$} orbifolds of the {P}odle\'{s} two
-	      spheres}, \emph{J. Noncommut. Geom.} {\bf 13} (2019), 257--267.
-
-	\item Roy, Krishanu and Venkatesh, R.: \href{https://doi.org/10.1007/s00031-018-9510-9}{Maximal closed subroot systems of real affine root systems}, \emph{Transform.
-Groups} {\bf 24} (2019), 1261--1308.
-
-	\item Seshadri, Harish: \href{https://doi.org/10.1007/s13226-019-0355-2}{Differential geometry in {I}ndia}, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799.
-
-\end{enumerate}
-\vspace{0.5mm}
-
-\noindent{{\small $(i\text{-}b)$ {\sc Accepted for publication at the time of reporting}}}
-\medskip
-
-%%THIS LIST IS NOT ORGANISED BY YEAR %%%%%
-%\noindent{{\small {\bf  April 2018--March 2019:}}}
-%\medskip
-
-\noindent{{\small {\sl In the identified thrust area:}}}\vspace{-2.5mm}
-
-\begin{enumerate}[resume, leftmargin=27pt]
 \item Basu, R.
@@
 and Krishnapur, M.: Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation, to appear in \emph{Israel Journal of Mathematics}.
+
+\item Gudi, Thirupathi and  Sau, Ramesh Ch.: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim.
+Calc.
+Var}.
+
+\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein–Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.
 
@@
 
-	\item Ghosh, M.
-K.
-and Pradhan, S.: Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant, to appear in \emph{ESIAM: Control, Optimization and Calculus of Variations}.
+\item Ghosh, Subhajit: Total Variation Cutoff for the Transpose Top-2 with Random Shuffle, to appear in \emph{Journal of Theoretical Probability}.
 
 \item Ghosh, Subhajit: Total variation cutoff for the transpose top-2 with random shuffle, to appear in {\em Journal of Theoretical Probability}.
-
-	\item Gudi, Thirupathi and  Sau, Ramesh Ch.: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim.
-Calc.
-Var}.
 
@@
       to appear in {\em Physical Review E}.
+
+\item\label{pingali:algebraic-hypersurfaces} Pingali, Vamsi Pritham and Varolin, Dror: Non-uniformly flat affine algebraic hypersurfaces, to appear in {\em Nagoya Mathematical Journal}.
 
@@
       to appear in {\em IEEE Transactions on Wireless Communications}.
-
-\end{enumerate}
-
-\noindent{{\small {\sl In other areas:}}}\vspace{-2.5mm}
-
-\begin{enumerate}[resume, leftmargin=27pt]
-	\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein-Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.
-
-	\item Balodi, M. and Banerjee, A. and Ray, S.: Cohomology of modules over H-categories and co-H-categories, to appear in \emph{Canadian Journal of Mathematics}.
-
-	\item Balodi, M. and Banerjee, A. and Ray, S.: Entwined modules over linear categories and Galois extensions, to appear in \emph{Israel Journal of Mathematics}.
-
-	\item Banerjee, A.: On Noetherian schemes over $(\mathcal C,\otimes,1)$ and the category of quasi-coherent sheaves, to appear in \emph{Indiana University Mathematics Journal}.
-
-	\item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable CMC free-boundary surfaces in a strictly convex domain of a bi-invariant Lie group, to appear in \emph{International Journal of Mathematics}.
-
-	\item Choudhury, Projesh Nath and Sivakumar, K.C.: \href{https://doi.org/10.1080/03081087.2019.1602588}{Matrices with Positive Semidefinite Real Part}, to appear in \emph{Linear and Multilinear Algebra}.
-
-	\item\label{datta-gupta:hyperbolic-plane} Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane,
-	      to appear in \emph{Discrete and Computational Geometry}.
-
-	\item Gupta, Subhojoy: Harmonic maps and wild Teichm{\"u}ller spaces, to appear in {\em Journal of Topology and
-			      Analysis}.
-
-	\item Kreuzer, M.
-and Patil, D.
-Patil: Computational aspects of Burnside rings part II: important maps, to appear in \emph{Beitr\"age zur Algebra und Geometrie / Contributions to Algebra and Geometry}.
-
-	\item\label{pingali:algebraic-hypersurfaces} Pingali, Vamsi Pritham and Varolin, Dror: Non-uniformly flat affine algebraic hypersurfaces, to appear in {\em Nagoya Mathematical Journal}.
-
-	\item Ray, Samarpita: Closure operations, Continuous valuations on monoids and Spectral spaces, to appear in {\em Journal of algebra and its applications}.
-\end{enumerate}
-\vspace{0.5mm}
-
-\noindent{{\small $(i\text{-}c)$ {\sc Submitted/preprints at the time of reporting}}}
-\medskip
-
-%% THIS LIST IS NOT ORGANISED BY YEAR%%%%%
-%\noindent{{\small {\bf April 2018--March 2019:}}}
-%\medskip
-
-\noindent{{\small {\sl In the identified thrust area:}}}\vspace{-2.5mm}
-
-\begin{enumerate}[resume, leftmargin=27pt]
-	\item\label{sen:random-3-regular-graph} Addario-Berry, Louigi and Sen, Sanchayan: Geometry of the minimal spanning tree of a random 3-regular graph.
-
-	\item\label{ayyer:partial-cyclic-orders} Ayyer, Arvind and Josuat-Verg\`es, Matthieu and Ramassamy, Sanjay: Extensions of partial cyclic orders and consecutive coordinate polytopes.
-
-	\item\label{ayyer:Coxeter-groups} Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven: Macdonald trees and
-	      determinants of representations for finite Coxeter groups.
-
-	\item Ayyer, Arvind and Sinha, Shubham: The size of t-cores and hook lengths of random cells in random partitions.
-
-	\item Ayyer, Arvind: A simple symmetric exclusion process driven by an asymmetric tracer particle.
-
-	\item\label{ayyer-singla:noncommutative-rings} Ayyer, Arvind and Singla, Pooja: Random motion on finite rings, II:
-	      Noncommutative rings.
-
-	\item\label{thangavelu:Heisenberg-group} Bagchi, Sayan and  Hait, Sourav and  Roncal, Luz and Thangavelu, Sundaram: On the lacunary spherical maximal function on the Heisenberg group.
-
-	\item Bera, Sudip: Enumeration of weighted paths on a digraph and block hook determinant.
-
-	\item Behera, Kiran Kumar: \href{https://arxiv.org/abs/1909.12548}{Self-inversive polynomials from rational transformation of linear functionals}.
-
-	\item\label{bhattacharyya:pseudo-extensions} Bhattacharyya, Tirthankar and Das, B. Krishna  and Sau, Haripada: Toeplitz operators
-	      and pseudo-extensions.
-
-	\item Bhattacharyya, Tirthankar and Kumar, Poornendu and Sau, Haripada: Distinguished Varieties Through the Berger--Coburn--Lebow Theorem.
-
-	\item Bhattacharyya, T. and  Biswas, A. and Maitra, A.: An unbounded realization of the symmetrized bidisc.
-
-	\item Bhattacharyya, Tirthankar and  Roy, Subrata Shyam and Yadav, Tapesh: The Agler--Young Class.
-
-	\item B{\"o}cherer, Siegfried and Das, Soumya: On fundamental Fourier coefficients of Siegel modular forms.
-
-	\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: \href{https://arxiv.org/abs/1812.05435}{Multiplicities, invariant subspaces and an additive formula.}.
-
-	\item\label{datar:K3-surfaces} Datar, Ved and Jacob,Adam and Zhang, Yuguang: Adiabatic limits of anti-self-dual
-	      connections on collapsed K3 surfaces, to appear in \emph{Journal of differential geometry}.
-
-	\item\label{datar-pingali:Kahler-metrics} Datar, Ved and Pingali, Vamsi Pritham: On coupled constant scalar curvature Kaehler
-	      metrics, to appear in \emph{Journal of symplectic geometry}.
-
-	\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita: $K$-homogeneous tuple of operators on bounded symmetric domains.
-
-	\item Gupta, Purvi and Wawrzyniak, Chloe Urbanski: STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$.
-
-	\item\label{khare:schur-polynomial-identities} Khare, Apoorva: Smooth entrywise positivity preservers, a
-	      Horn-Loewner master theorem, and Schur polynomial identities.
-
-	\item Ganguly, Pritam and Thangavelu,Sundaram: On lacunary spherical maximal function on Heisenberg groups.
-
-	\item Khare, Apoorva: The non-compact normed space of norms on a finite-dimensional Banach space.
-
-	\item Khare, Apoorva: Sharp nonzero lower bounds for the Schur product theorem.
-
-	\item L\"ubeck, Frank and Prasad, Dipendra and Ayyer, Arvind: A character relationship between symmetric group and hyperoctahedral group.
-
-	\item Maiti, Arun: Loop products on level homology and closed geodesics.
-
-	\item Miermont, Gr\'egory and Sen, Sanchayan: On breadth-first constructions of scaling limits of random graphs and random unicellular maps.
-
-	\item\label{Misra:Jordan-Keppler} Misra, Gadadhar and Upmeier, Harald: Singular Hilbert modules on
-	      Jordan--Keppler varieties.
-
-	\item Poria, Anirudha: \href{https://arxiv.org/abs/2004.04184}{Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms}.
-
-	\item Poria, Anirudha: \href{https://arxiv.org/abs/2005.14274}{Uncertainty principles for the Opdam-Cherednik transform on modulation spaces}.
-
-	\item Toft, J. and Gumber, A. and Manna, R. and Ratnakumar, P. K.: \href{https://arxiv.org/abs/2004.02430v1}{Translation and modulation invariant Hilbert spaces}.
-\end{enumerate}
-
-\noindent{{\small {\sl In other areas:}}}\vspace{-2.5mm}
-
-\begin{enumerate}[resume, leftmargin=27pt]
-
-	\item Balodi, Mamta and Banerjee, Abhishek: Cycles over DGH-semicategories and pairings in categorical Hopf-cyclic cohomology.
-
-	\item Balodi, Mamta: Morita invariance of equivariant and Hopf-cyclic cohomology of module algebras over Hopf algebroids.
-
-	\item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter: Surface group representations in $SL(2,\mathbb{C})$ with finite mapping class orbits.
-
-	\item David Burns, Mahesh Kakde: On Weil-Etale Cohomology and Artin L-series.
-
-	\item\label{khare:matrices-tree}  Choudhury, Projesh Nath and Khare, Apoorva: Distance matrices of a tree: two
-	      more invariants, and in a unified framework.
-	\item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian: Gravitating vortices with positive curvature.
-
-	\item Gupta, Subhojoy and Mj, Mahan: Meromorphic projective structures, grafting and the monodromy map.
-
-	\item Gupta, Subhojoy: Monodromy groups of $CP^1$-structures on punctured surfaces.
-
-	\item\label{singla:compact-linear-groups} Hassain, M. and Singla, Pooja; Representation Growth of Special Compact Linear Groups of Order Two.
-
-	\item Hatui, Sumana and Singla Pooja: \href{https://arxiv.org/abs/1909.06589}{On Schur multiplier and Projective representations of Heisenberg groups}.
-
-	\item Kus, Deniz and Venkatesh, R: Borel--de Siebenthal theory for affine reflection systems.
-
-	\item Maiti, Arun: Optimal index growth of closed geodesics.
-
-	\item\label{singla:discrete-valuation-rings} Patel, Shiv Prakash and Singla, Pooja: A multiplicity one theorem for groups of type $A_n$ over discrete valuation rings.
-
-	\item Patil, Dilip P.: On the connectedness of the fiber product of two connected finte free affine schemes.
-
-	\item Pingali, Vamsi Pritham: The deformed Hermitian Yang-Mills equation on three-folds.
-
-	\item\label{pingali:Monge-Ampere-equation} Pingali, Vamsi Pritham: A vector bundle version of the Monge--Ampere equation.
-
-	\item Quddus, Safdar: \href{https://arxiv.org/abs/2002.02192}{Equivariant Cartan Homotopy Formula for $DG$-algebra.}.
-
-	\item Radhika Ganapathy: A Hecke algebra isomorphism over close local fields.
-
-	\item Reif, Shifra and Venkatesh, R.: On tensor products of irreducible integrable representations.
-
-\end{enumerate}
-
-\subsubsection*{{\small $(ii)$ {\sc Research Papers in Conference Proceedings}}}
-
-%% YEAR 1 LISTING %%%%%
-\noindent{{\small {\bf April 2018--March 2019:}}}\vspace{-1mm}
-
-\renewcommand{\theenumi}{C.\arabic{enumi}}
-\begin{enumerate}%[leftmargin=27pt]
-
-	\item Kanukurthi, Bhavana and Obbattu, Sai Lakshmi Bhavana and
-	      Sekar, Sruthi: Non-malleable randomness encoders and their applications, {\em Advances in
-	      Cryptology\,---\,\linebreak{EUROCRYPT} 2018: {P}art {III}} {\bf 10822} (2018), 589--617.
-
-	\item S.
-Ghara and G.
-Misra: Decomposition of the tensor product of two Hilbert modules in {\em Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G.
-Douglas Memorial Volume} Curto, R.E., Helton, W., Lin, H., Tang, X., Yang, R., Yu, G.
-(ed.), Operator Theory: Advances and Applications , Birkhauser (2020).
-
-	\item Gadadhar Misra: Decomposition of the tensor product of two Hilbert modules in {\em Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G.
-Douglas Memorial Volume} R.
-Curto, W.
-Helton, H.
-Lin, X.
-Tang, R.
-Yang, G.
-Yu (ed.), Operator Theory: Advances and Applications , Birkhauser (2020).
-
-	\item\label{patil:Nullstellensaetze} Goel, Kriti and Patil, Dilip P.
-and Verma, Jugal: Nullstellens\"atze and Applications, {\em Proceedings of the International Conference on Mathematics and Centenary Celebrations of Ramjas College}, forthcoming.
-
-	\item\label{patil:generalized-trace-forms} Patil, Dilip P.
-and Verma, Jugal: Rational points and generalized trace forms on a finite algebra over a real closed field, {\em Proceedings of the International Conference on Computational Mathematics,  Banasthali Vidyapeeth}.
-\end{enumerate}
-
-%% YEAR 2 LISTING %%%%%
-\noindent{{\small {\bf April 2019--March 2020:}}}\vspace{-1mm}
-
-\begin{enumerate}[resume]%[leftmargin=27pt]
-
-	\item Banerjee, A.: Spectra as universal objects in categories of supports in {\em Banach Center Publications(Quantum Dynamics Proceedings)} Ludwik Dabrowski, Ryszard Nest, Adam Skalski (ed.), Banach Center Publications , IMPAN, Warsaw, Poland (2020).
-
-\end{enumerate}
-
-\subsubsection*{{\small $(iii)$ {\sc Books \& Monographs}}}\vspace{-1mm}
-
-%% YEAR 1 LISTING %%%%%
-\noindent{{\small {\bf April 2018--March 2019:}}}
-
-\renewcommand{\theenumi}{B.\arabic{enumi}}
-\begin{enumerate}%[leftmargin=27pt]
-
-	\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva and Putinar, Mihai: A panorama of positivity: I.
-	      Dimension, in {\em Analysis of Operators on Function Spaces (The Serguei Shimorin Memorial Volume)}, eds.
-	      A.~Aleman, H.~Hedenmalm, D.~Khavinson, M.~Putinar, Trends in Mathematics,  Birkhauser, pages 117--165, 2019.
-
-	\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva and Putinar, Mihai: A panorama of positivity: II.
-	      Fixed dimension, in {\em Complex Analysis and Spectral Theory}, eds.  G.~Dales, D.~Khavinson, J.~Mashreghi, Eds.,
-	      CRM Proceedings, AMS  Contemporary Mathematics, American Mathematical Society, 2019.
-
-\end{enumerate}
-
-%% YEAR 2 LISTING %%%%%
-\noindent{{\small {\bf April 2019--March 2020:}}}
-
-\begin{enumerate}[resume]%[leftmargin=27pt]
-
-	\item Gupta, Subhojoy and Seshadri, Harish: Complex geometry of Teichm{\"u}ller domains in {\em Handbook
-			      of Teichm{\"u}ller Theory} Papadopoulos, Athanase (ed.), IRMA Lect. Math. Theor. Phys, Eur. Math. Soc., Z{\"u}rich
-	      (2020), 26.
-
-	\item Gupta, Subhojoy: Holomorphic quadratic differentials in Teichm{\"u}ller theory in {\em Handbook
-			      of Teichm{\"u}ller Theory} Papadopoulos, Athanase (ed.), IRMA Lect. Math. Theor. Phys., Eur. Math. Soc., Z{\"u}rich
-	      (2020), 36.
-
-	\item Misra, Gadadhar: Operators in the {C}owen-{D}ouglas class and related topics, \emph{Handbook of analytic operator theory} {\bf } (2019), 87--137.
-\end{enumerate}

### 2020-08-10 sorted.tex
clean up; multi-line strings with indentation

--- 2020-08-10 data/to-sort.tex
@@
+\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein–Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.
+
 \item Basu, R.
@@
 and Krishnapur, M.: Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation, to appear in \emph{Israel Journal of Mathematics}.
-
-\item Gudi, Thirupathi and  Sau, Ramesh Ch.: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim.
-Calc.
-Var}.
-
-\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein–Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.
-
-\item\label{bharali:Wolff-Denjoy} Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility,
-      a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}.
-
-\item\label{sen:models-at-criticality} Dhara, Souvik and van der Hofstad, Remco and van Leeuwaarden, Johan S.H.
-and Sen, Sanchayan: Heavy-tailed configuration models at criticality, to appear in {\em Annales de l'Institut Henri
-              Poincar\'e (B) Probabilit\'es et Statistiques}.
 
@@
 
-\item\label{iyer:heterogeneous-populations} Nair, Gokul and Athmanathan, Senthil and Iyer, Srikanth K.
+\item Gudi, Thirupathi and  Sau, Ramesh Ch.: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim.
+Calc.
+Var}.
+
+\item \label{bharali:Wolff-Denjoy} Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility,
+      a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}.
+
+\item \label{iyer:heterogeneous-populations} Nair, Gokul and Athmanathan, Senthil and Iyer, Srikanth K.
 and Guttal, Vishwesha: Fission-fusion dynamics and group-size-dependent composition in heterogeneous populations,
@@
 
-\item\label{pingali:algebraic-hypersurfaces} Pingali, Vamsi Pritham and Varolin, Dror: Non-uniformly flat affine algebraic hypersurfaces, to appear in {\em Nagoya Mathematical Journal}.
+\item \label{iyer:wireless-networks} Vaze, Rahul and Iyer, Srikanth K., Capacity of cellular wireless networks,
+      to appear in {\em IEEE Transactions on Wireless Communications}.
 
-\item\label{thangavelu:H-type-groups} Roncal, Luz and Thangavelu, Sundaram: An extension problem and trace Hardy
+\item \label{pingali:algebraic-hypersurfaces} Pingali, Vamsi Pritham and Varolin, Dror: Non-uniformly flat affine algebraic hypersurfaces, to appear in {\em Nagoya Mathematical Journal}.
+
+\item \label{sen:models-at-criticality} Dhara, Souvik and van der Hofstad, Remco and van Leeuwaarden, Johan S.H.
+and Sen, Sanchayan: Heavy-tailed configuration models at criticality, to appear in {\em Annales de l'Institut Henri
+              Poincar\'e (B) Probabilit\'es et Statistiques}.
+
+\item \label{thangavelu:H-type-groups} Roncal, Luz and Thangavelu, Sundaram: An extension problem and trace Hardy
       inequality for the sublaplacian on H-type groups, to appear in {\em International Mathematical Research Notices}.
-
-\item\label{iyer:wireless-networks} Vaze, Rahul and Iyer, Srikanth K., Capacity of cellular wireless networks,
-      to appear in {\em IEEE Transactions on Wireless Communications}.

### 2020-08-10 ugc/src/Data.scala

@@ -77,19 +77,16 @@ object Data {
     )
 
   lazy val summerTeX =
-    s"""
-\\subsection{Summer Students}
+    s"""|\\subsection{Summer Students}
+      |
+      |${enumString(summerStudents)}
+      |
+      |\\subsection{List of Visitors to the Department}
+      |
+      |${enumString(visitors)}
+      |
+      |""".stripMargin
 
-\\begin{enumerate}
-${summerStudents.map(s => "\\item " + s).mkString("\n")}
-\\end{enumerate}
-
-
-\\subsection{List of Visitors to the Department}
-
-${enumString(visitors)}
-
-"""
   lazy val facultyData: Vector[FacultyData] =
     data.map(l => FacultyData.get(l)).sortBy(_.name)
 
@@ -101,13 +98,12 @@ ${enumString(visitors)}
   lazy val grantsItems = facultyData.flatMap(f => f.grantTeX)
 
   lazy val grants =
-    s"""
-\\section{Resource Generation}
-
-\\begin{enumerate}
-${grantsItems.mkString("\n").replace("&", "\\&")}
-\\end{enumerate}
-"""
+    s"""|\\section{Resource Generation}
+      |
+      |\\begin{enumerate}
+      |${grantsItems.mkString("\n").replace("&", "\\&")}
+      |\\end{enumerate}
+      |""".stripMargin
 
   lazy val reports = facultyData
     .map(d => s"\\subsection{${d.name}}\n\n${d.researchHighlights}")
@@ -139,28 +135,27 @@ ${grantsItems.mkString("\n").replace("&", "\\&")}
              |""".stripMargin
 
   lazy val draftSections =
-    s"""
-$summerTeX
-
-$grants
-
-\\subsection{Awards}
-
-${enumString(awards)}
-
-\\subsection{Fellowships of Academies}
-
-${enumString(fellows)}
-
-\\subsection{Editorial boards}
-${enumString(editors)}
-
-\\subsection{Other Activities: 2018-19}
-${enumString(otherOld)}
-
-\\subsection{Other Activities: 2019-20}
-${enumString(other)}
-"""
+    s"""|$summerTeX
+        |
+        |$grants
+        |
+        |\\subsection{Awards}
+        |
+        |${enumString(awards)}
+        |
+        |\\subsection{Fellowships of Academies}
+        |
+        |${enumString(fellows)}
+        |
+        |\\subsection{Editorial boards}
+        |${enumString(editors)}
+        |
+        |\\subsection{Other Activities: 2018-19}
[…]

### 2021-08-19 data/draft-publications.tex
publications for DST-FIST, timetable

@@
-\subsection{Papers in Journals}
+\subsection{Papers in Journals (with links)}
 
@@
 \item S Aiyappan, Editha C. Jose, Ivy Carol B. Lomerio and A. K. Nandakumaran: Control Problem on a Rough Circular Domain and Homogenization, \emph{Asymptotic Analysis} {\bf 115} (2019), 19-46.
-\item M. Balodi, A. Banerjee, S. Ray: Cohomology of modules over H-categories and co-H-categories, to appear in \emph{Canadian Journal of Mathematics}.
-\item M. Balodi, A. Banerjee, S. Ray: Entwined modules over linear categories and Galois extensions, to appear in \emph{Israel Journal of Mathematics (Accepted)}.
-\item A. Banerjee: On Noetherian schemes over $(\mathcal C,\otimes,1)$ and the category of quasi-coherent sheaves, to appear in \emph{Indiana University Mathematics Journal}.
 \item A. Banerjee: On differential torsion theories and rings with several objects, \emph{Canadian Math Bulletin} {\bf 62} (2019), 703--714.
 \item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric semigroups, \emph{Advances in Operator Theory (Special issue in honor of Rajendra Bhatia)} {\bf 5} (2020), 779-795.
-\item Ghosh, Subhajit: Total Variation Cutoff for the Transpose Top-2 with Random Shuffle, to appear in \emph{Journal of Theoretical Probability}.
-\item Datta, B. and Gupta, S.: Semi-regular tilings of the hyperbolic plane \label{bdsg_2019}, to appear in \emph{Discrete Comput Geom}.
 \item Datta, B. and Sarkar, S.: Equilibrium triangulations of some quasitoric 4-manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57--78.
 \item Datta, B. and Maity, D.: Correction to: Semi-equivelar and vertex-transitive maps on the torus, \emph{Beitr Algebra Geom} {\bf 61} (2020), 187--188.
-\item Martin Kreuzer and Dilip P.
-Patil: COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS, to appear in \emph{Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry}.
 \item Gadadhar Misra: Professor, \emph{Adv. Math.} {\bf 351} (2019), 1105 - 1138.
-\item Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}.
 \item Maitra, Anwoy: On the continuous extension of Kobayashi isometries, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.
@@
 \item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor: Higher Chern Classes in Iwasawa Theory, \emph{American Journal of Mathematics} {\bf 142} (2020), 627-682.
+\item Iyer, S.
+K.
+and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897.
+\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107..
+\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} {\bf } ().
+\item Arun Maiti: \href{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}{Quasi-vertex-transitive maps on the plane}, \emph{Discrete Mathematics} {\bf 343} (2020), 111911-111917.
+\item Carstensen, C.
+and Mallik, G.
+and Nataraj, N.: \href{https://doi.org/10.1093/imanum/drz071}{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, \emph{IMA Journal of Numerical Analysis} {\bf } (2020).
+\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala: On Baker's explicit abc-conjecture, \emph{Publ. Math. Debrecen} {\bf 94} (2019), 435–453.
+\item Choudhury, Projesh Nath and Tsatsomeros Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic Detection and Construction of N-matrices}, \emph{Linear Algebra and Its Applications} {\bf 602} (2020), 46-56.
+\item Datt, Gopal and Kumar, Sanjay: \href{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}{A criterion for quasinormality in $\mathbb{C}^n$}, \emph{Proc.
+Indian Acad.
+Sci.
+Math.
+Sci.} {\bf 129} (2019), Paper No.
+11, 13 pp..
+\item Hatui, Sumana: \href{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}{Schur multipliers of special p-groups of rank 2}, \emph{Journal of Group Theory} {\bf 23} (2020), 85-95.
+\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: \href{https://projecteuclid.org/euclid.bjma/1543914019}{On some geometric properties of operator spaces}, \emph{Banach J.
+Math.
+Anal.} {\bf 13} (2019), 174-191.
+\item Pradhan, P.
+and Sahu, B.: \href{https://doi.org/10.1016/j.disc.2020.112044}{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, \emph{Discrete Mathematics} {\bf 343} (2020).
+\item Roth, Julien and Upadhyay, Abhitosh: \href{https://link.springer.com/article/10.1007/s00025-019-1142-4?shared-article-renderer#citeas}{f-Biharmonic Submanifolds of Generalized Space Forms}, \emph{Results in Mathematics} {\bf 75} (2020).
+\item Roth, Julien and Upadhyay, Abhitosh: \href{https://www.cambridge.org/core/journals/bulletin-of-the-australian-mathematical-society/article/on-almost-stable-cmc-hypersurfaces-in-manifolds-of-bounded-sectional-curvature/E0BF84D4D46C82F6D75CDCEAAF5DEE94}{On almost stable CMC hypersurfaces in manifolds of bounded sectional curvature}, \emph{Bulletin of the Australian Mathematical Society} {\bf 101} (2020), 333-338.
+\end{enumerate}
+
+\subsection{Accepted Papers}
+
+\begin{enumerate}
+\item M. Balodi, A. Banerjee, S. Ray: Cohomology of modules over H-categories and co-H-categories, to appear in \emph{Canadian Journal of Mathematics}.
+\item M. Balodi, A. Banerjee, S. Ray: Entwined modules over linear categories and Galois extensions, to appear in \emph{Israel Journal of Mathematics (Accepted)}.
+\item A. Banerjee: On Noetherian schemes over $(\mathcal C,\otimes,1)$ and the category of quasi-coherent sheaves, to appear in \emph{Indiana University Mathematics Journal}.
+\item Ghosh, Subhajit: Total Variation Cutoff for the Transpose Top-2 with Random Shuffle, to appear in \emph{Journal of Theoretical Probability}.
+\item Datta, B. and Gupta, S.: Semi-regular tilings of the hyperbolic plane \label{bdsg_2019}, to appear in \emph{Discrete Comput Geom}.
+\item Martin Kreuzer and Dilip P.
+Patil: COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS, to appear in \emph{Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry}.
+\item Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}.
 \item Basu, R.
@@
 Pradhan: Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications, to appear in \emph{Stochastic Analysis and Applications}.
-\item Iyer, S.
-K.
-and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897.
 \item Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane, to appear in \emph{Discrete and Computational Geometry}.
@@
 Var}.
-\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107..
-\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} {\bf } ().
 \item Pingali, Vamsi Pritham and Varolin, Dror: Nonuniformly flat affine algebraic hypersurfaces, to appear in \emph{Nagoya Mathematical Journal}.
@@
 \item Datar, Ved and Pingali, Vamsi Pritham: On coupled constant scalar curvature Kaehler metrics, to appear in \emph{Journal of symplectic geometry}.
-\item Pradhan, P. and Sahu, B.: A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd, \emph{Discrete Mathematics} {\bf 343} (2020).
-\item Arun Maiti: Quasi-vertex-transitive maps on the plane, \emph{Discrete Mathematics} {\bf 343} (2020), 111911-111917.
-\item Datt, Gopal and Kumar, Sanjay: A criterion for quasinormality in $\mathbb{C}^n$, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Paper No. 11, 13 pp..
-\item Hatui, Sumana: Schur multipliers of special p-groups of rank 2, \emph{Journal of Group Theory} {\bf 23} (2020), 85-95.
-\item Choudhury, Projesh Nath and Tsatsomeros Michael J.: Algorithmic Detection and Construction of N-matrices, \emph{Linear Algebra and Its Applications} {\bf 602} (2020), 46-56.
-\item Choudhury, Projesh Nath and Sivakumar, K.C.: Matrices with Positive Semidefinite Real Part, to appear in \emph{Linear and Multilinear Algebra}.
-\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala: On Baker's explicit abc-conjecture, \emph{Publ. Math. Debrecen} {\bf 94} (2019), 435–453.
-\item Carstensen, C.
-and Mallik, G.
-and Nataraj, N.: Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity, \emph{IMA Journal of Numerical Analysis} {\bf } (2020).
-\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: On some geometric properties of operator spaces, \emph{Banach J. Math. Anal.} {\bf 13} (2019), 174-191.
-\item Roth, Julien and Upadhyay, Abhitosh: On almost stable CMC hypersurfaces in manifolds of bounded sectional curvature, \emph{Bulletin of the Australian Mathematical Society} {\bf 101} (2020), 333-338.
-\item Roth, Julien and Upadhyay, Abhitosh: f-Biharmonic Submanifolds of Generalized Space Forms, \emph{Results in Mathematics} {\bf 75} (2020).
 \item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable CMC free-boundary surfaces in a strictly convex domain of a bi-invariant Lie group, to appear in \emph{International Journal of Mathematics}.
-\end{enumerate}
-
-\subsection{Papers in Journals with links}
-
-\begin{enumerate}
-\item S Aiyappan, A.
-K.
-Nandakumaran and Abu Sufian: Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure, \emph{Mathematical Methods in the Applied Sciences} {\bf 42} (2019.
-DOI: 10.1002/mma.5748), 6407-6434.
-\item K.
-Murali, A.
-K.
-Nandakumaran, Turgurt Durduran, Hari M Varma: Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements, \emph{Biomedical Optics Express 5395} {\bf 10} (2019).
-\item S Aiyappan, A.
-K.
-Nandakumaran and Ravi Prakash: Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains, \emph{Annali di Matematica Pura ed Applicata} {\bf 198} (2019), 1931-1954.
-\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash: Semi-linear optimal control problem on a smooth oscillating domain, \emph{Communications in Contemporary Mathematics} {\bf } (2019), 1-26.
-\item S Aiyappan, Editha C. Jose, Ivy Carol B. Lomerio and A. K. Nandakumaran: Control Problem on a Rough Circular Domain and Homogenization, \emph{Asymptotic Analysis} {\bf 115} (2019), 19-46.
-\item M. Balodi, A. Banerjee, S. Ray: Cohomology of modules over H-categories and co-H-categories, to appear in \emph{Canadian Journal of Mathematics}.
-\item M. Balodi, A. Banerjee, S. Ray: Entwined modules over linear categories and Galois extensions, to appear in \emph{Israel Journal of Mathematics (Accepted)}.
-\item A. Banerjee: On Noetherian schemes over $(\mathcal C,\otimes,1)$ and the category of quasi-coherent sheaves, to appear in \emph{Indiana University Mathematics Journal}.
-\item A. Banerjee: On differential torsion theories and rings with several objects, \emph{Canadian Math Bulletin} {\bf 62} (2019), 703--714.
-\item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric semigroups, \emph{Advances in Operator Theory (Special issue in honor of Rajendra Bhatia)} {\bf 5} (2020), 779-795.
-\item Ghosh, Subhajit: Total Variation Cutoff for the Transpose Top-2 with Random Shuffle, to appear in \emph{Journal of Theoretical Probability}.
-\item Datta, B. and Gupta, S.: Semi-regular tilings of the hyperbolic plane \label{bdsg_2019}, to appear in \emph{Discrete Comput Geom}.
-\item Datta, B. and Sarkar, S.: Equilibrium triangulations of some quasitoric 4-manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57--78.
-\item Datta, B. and Maity, D.: Correction to: Semi-equivelar and vertex-transitive maps on the torus, \emph{Beitr Algebra Geom} {\bf 61} (2020), 187--188.
-\item Martin Kreuzer and Dilip P.
-Patil: COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS, to appear in \emph{Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry}.
-\item Gadadhar Misra: Professor, \emph{Adv. Math.} {\bf 351} (2019), 1105 - 1138.
-\item Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}.
-\item Maitra, Anwoy: On the continuous extension of Kobayashi isometries, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.
-\item Vishnu Priya, N.
-and Senthilvelan, M.
-and  Rangarajan, G.
-and Lakshmanan, M: On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation, \emph{Physics Letters A} {\bf 383} (2019), 15-26.
-\item Kashyap, G.
-A.
-R.
-S.
-R.
-K.
-and Bapat, D.
-and Das, D.
-and Gowaikar, R.
-D.
-and Amritkar, R.
-E.
-and Rangarajan, G.
-and Ravindranath, V.
-and Ambika, G: Synapse loss and progress of Alzheimer’s disease - A network model, \emph{Scientific Reports} {\bf 9} (2019), 6555.
-\item Vishnu Priya, N.
-and Senthilvelan, M.
-and Rangarajan, G.: On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, \emph{Chaos} {\bf 29} (2019), 123135.
-\item Sarkar, Amar Deep and Verma, Kaushal: A submultiplicative property of the Carath\'{e}odory metric on planar domains, \emph{Proc. Indian Acad. Sci. (Math. Sci.)} {\bf } ().
-\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor: Higher Chern Classes in Iwasawa Theory, \emph{American Journal of Mathematics} {\bf 142} (2020), 627-682.
-\item Basu, R.
-and Ganguly, S.
-and Hegde, M.
-and Krishnapur, M.: Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation, to appear in \emph{Israel Journal of Mathematics}.
-\item M.
-K.
-Ghosh and S.
-Pradhan: Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant, to appear in \emph{ESIAM: Control, Optimization and Calculus of Variations}.
-\item M.
-K.
-Ghosh, K.
-Suresh Kumar, C.
-Pal and S.
-Pradhan: Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications, to appear in \emph{Stochastic Analysis and Applications}.
-\item Iyer, S.
-K.
-and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897.
-\item Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane, to appear in \emph{Discrete and Computational Geometry}.
-\item Thirupathi Gudi, Ramesh Ch.
-Sau: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim.
-Calc.
-Var}.
-\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107..
-\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} {\bf } ().
-\item Pingali, Vamsi Pritham and Varolin, Dror: Nonuniformly flat affine algebraic hypersurfaces, to appear in \emph{Nagoya Mathematical Journal}.
-\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein–Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.
-\item Datar, Ved and Jacob,Adam and Zhang, Yuguang: Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces, to appear in \emph{Journal of differential geometry}.
-\item Datar, Ved and Pingali, Vamsi Pritham: On coupled constant scalar curvature Kaehler metrics, to appear in \emph{Journal of symplectic geometry}.
-\item Pradhan, P.
-and Sahu, B.: \href{https://doi.org/10.1016/j.disc.2020.112044}{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, \emph{Discrete Mathematics} {\bf 343} (2020).
-\item Arun Maiti: \href{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}{Quasi-vertex-transitive maps on the plane}, \emph{Discrete Mathematics} {\bf 343} (2020), 111911-111917.
-\item Datt, Gopal and Kumar, Sanjay: \href{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}{A criterion for quasinormality in $\mathbb{C}^n$}, \emph{Proc.
-Indian Acad.
-Sci.
-Math.
-Sci.} {\bf 129} (2019), Paper No.
-11, 13 pp..
-\item Hatui, Sumana: \href{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}{Schur multipliers of special p-groups of rank 2}, \emph{Journal of Group Theory} {\bf 23} (2020), 85-95.
-\item Choudhury, Projesh Nath and Tsatsomeros Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic Detection and Construction of N-matrices}, \emph{Linear Algebra and Its Applications} {\bf 602} (2020), 46-56.
 \item Choudhury, Projesh Nath and Sivakumar, K.C.: \href{https://doi.org/10.1080/03081087.2019.1602588}{Matrices with Positive Semidefinite Real Part}, to appear in \emph{Linear and Multilinear Algebra}.
-\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala: On Baker's explicit abc-conjecture, \emph{Publ. Math. Debrecen} {\bf 94} (2019), 435–453.
-\item Carstensen, C.
-and Mallik, G.
-and Nataraj, N.: \href{https://doi.org/10.1093/imanum/drz071}{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, \emph{IMA Journal of Numerical Analysis} {\bf } (2020).
-\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: \href{https://projecteuclid.org/euclid.bjma/1543914019}{On some geometric properties of operator spaces}, \emph{Banach J.
-Math.
-Anal.} {\bf 13} (2019), 174-191.
-\item Roth, Julien and Upadhyay, Abhitosh: \href{https://www.cambridge.org/core/journals/bulletin-of-the-australian-mathematical-society/article/on-almost-stable-cmc-hypersurfaces-in-manifolds-of-bounded-sectional-curvature/E0BF84D4D46C82F6D75CDCEAAF5DEE94}{On almost stable CMC hypersurfaces in manifolds of bounded sectional curvature}, \emph{Bulletin of the Australian Mathematical Society} {\bf 101} (2020), 333-338.
-\item Roth, Julien and Upadhyay, Abhitosh: \href{https://link.springer.com/article/10.1007/s00025-019-1142-4?shared-article-renderer#citeas}{f-Biharmonic Submanifolds of Generalized Space Forms}, \emph{Results in Mathematics} {\bf 75} (2020).
-\item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable CMC free-boundary surfaces in a strictly convex domain of a bi-invariant Lie group, to appear in \emph{International Journal of Mathematics}.
 \end{enumerate}
@@
 
-\subsection{Preprints}
-
-\begin{enumerate}
-\item Khare, Apoorva: Sharp nonzero lower bounds for the Schur product theorem, submitted for publication.
-\item Lübeck, Frank and Prasad, Dipendra and Ayyer, Arvind: A character relationship between symmetric group and hyperoctahedral group, preprint.
-\item Ayyer, Arvind and Sinha, Shubham: The size of t-cores and hook lengths of random cells in random partitions, preprint.
-\item Ayyer, Arvind: A simple symmetric exclusion process driven by an asymmetric tracer particle, preprint.
-\item David Burns, Mahesh Kakde: On Weil-Etale Cohomology and Artin L-series, preprint.
-\item Gupta, Purvi and Wawrzyniak, Chloe Urbanski: STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$, submitted for publication.
-\item Radhika Ganapathy: A Hecke algebra isomorphism over close local fields, preprint.
-\item Miermont, Grégory and Sen, Sanchayan: On breadth-first constructions of scaling limits of random graphs and random unicellular maps, submitted for publication.
-\item Gupta, Subhojoy and Mj, Mahan: Meromorphic projective structures, grafting and the monodromy map, preprint.
-\item Gupta, Subhojoy: Monodromy groups of $CP^1$-structures on punctured surfaces, preprint.
-\item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter: Surface group representations in SL(2,C) with finite mapping class orbits, preprint.
-\item Ganguly, Pritam and Thangavelu,Sundaram: On lacunary spherical maximal function on Heisenberg groups, preprint.
-\item Bhattacharyya, Tirthankar and Kumar, Poornendu and Sau, Haripada: Distinguished Varieties Through the Berger--Coburn--Lebow Theorem, submitted for publication.
-\item Bhattacharyya, T. and  Biswas, A. and Maitra, A.: An unbounded realization of the symmetrized bidisc, submitted for publication.
-\item Pingali, Vamsi Pritham: The deformed Hermitian Yang-Mills equation on three-folds, preprint.
-\item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian: Gravitating vortices with positive curvature, preprint.
-\item Quddus, Safdar: Equivariant Cartan Homotopy Formula for $DG$-algebra., preprint.
-\item Arun Maiti: OPTIMAL INDEX GROWTH OF CLOSED GEODESICS, submitted for publication.
-\item Poria, Anirudha: Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms, submitted for publication.
-\item Poria, Anirudha: Uncertainty principles for the Opdam-Cherednik transform on modulation spaces, submitted for publication.
-\item Bera, Sudip: ENUMERATION OF WEIGHTED PATHS ON A DIGRAPH AND BLOCK HOOK DETERMINANT, submitted for publication.
-\item Behera, Kiran Kumar: Self-inversive polynomials from rational transformation of linear functionals, submitted for publication.
-\item Hatui, Sumana and Singla Pooja: On Schur multiplier and Projective representations of Heisenberg groups, submitted for publication.
-\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: Multiplicities, invariant subspaces and an additive formula., preprint.
-\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita: $K$-homogeneous tuple of operators on bounded symmetric domains, preprint.
-\item Toft, J. and Gumber, A. and Manna, R. and Ratnakumar, P. K.: Translation and modulation invariant Hilbert spaces, submitted for publication.
-\end{enumerate}
-
 \subsection{Preprints with links}
@@
 \item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian: Gravitating vortices with positive curvature, preprint.
-\item Quddus, Safdar: \href{https://arxiv.org/abs/2002.02192}{Equivariant Cartan Homotopy Formula for $DG$-algebra.}, preprint.
 \item Arun Maiti: OPTIMAL INDEX GROWTH OF CLOSED GEODESICS, submitted for publication.
+\item Behera, Kiran Kumar: \href{https://arxiv.org/abs/1909.12548}{Self-inversive polynomials from rational transformation of linear functionals}, submitted for publication.
+\item Bera, Sudip: ENUMERATION OF WEIGHTED PATHS ON A DIGRAPH AND BLOCK HOOK DETERMINANT, submitted for publication.
+\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: \href{https://arxiv.org/abs/1812.05435}{Multiplicities, invariant subspaces and an additive formula.}, preprint.
+\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita: $K$-homogeneous tuple of operators on bounded symmetric domains, preprint.
+\item Hatui, Sumana and Singla Pooja: \href{https://arxiv.org/abs/1909.06589}{On Schur multiplier and Projective representations of Heisenberg groups}, submitted for publication.
 \item Poria, Anirudha: \href{https://arxiv.org/abs/2004.04184}{Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms}, submitted for publication.
 \item Poria, Anirudha: \href{https://arxiv.org/abs/2005.14274}{Uncertainty principles for the Opdam-Cherednik transform on modulation spaces}, submitted for publication.
-\item Bera, Sudip: ENUMERATION OF WEIGHTED PATHS ON A DIGRAPH AND BLOCK HOOK DETERMINANT, submitted for publication.
-\item Behera, Kiran Kumar: \href{https://arxiv.org/abs/1909.12548}{Self-inversive polynomials from rational transformation of linear functionals}, submitted for publication.
-\item Hatui, Sumana and Singla Pooja: \href{https://arxiv.org/abs/1909.06589}{On Schur multiplier and Projective representations of Heisenberg groups}, submitted for publication.
-\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: \href{https://arxiv.org/abs/1812.05435}{Multiplicities, invariant subspaces and an additive formula.}, preprint.
-\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita: $K$-homogeneous tuple of operators on bounded symmetric domains, preprint.
+\item Quddus, Safdar: \href{https://arxiv.org/abs/2002.02192}{Equivariant Cartan Homotopy Formula for $DG$-algebra.}, preprint.
 \item Toft, J. and Gumber, A. and Manna, R. and Ratnakumar, P. K.: \href{https://arxiv.org/abs/2004.02430v1}{Translation and modulation invariant Hilbert spaces}, submitted for publication.
@@
 nonlocal boundary jumps, \emph{J. Phys. A} {\bf 52} (2019), 355001, 19.
+\item Adhikari, Kartick and Kishore Reddy, Nanda and Ram Reddy,
+Tulasi and Saha, Koushik: Determinantal point processes in the plane from products of
+random matrices, \emph{Ann. Inst. Henri Poincar\'{e} Probab. Stat.} {\bf 52} (2016), 16--46.
+\item Adhikari, Kartick and Reddy, Nanda Kishore: Hole probabilities for finite and infinite {G}inibre
+ensembles, \emph{Int. Math. Res. Not. IMRN} {\bf } (2017), 6694--6730.
+\item Adimurthi and Ratnakumar, P. K. and Sohani, Vijay Kumar: A {H}ardy-{S}obolev inequality for the twisted {L}aplacian, \emph{Proc. Roy. Soc. Edinburgh Sect. A} {\bf 147} (2017), 1--23.
 \item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
 Nandakumaran, A. K.: Control problem on a rough circular domain and homogenization, \emph{Asymptot. Anal.} {\bf 115} (2019), 19--46.
+\item Aiyappan, S. and Nandakumaran, A. K.: Optimal control problem in a domain with branched structure
+and homogenization, \emph{Math. Methods Appl. Sci.} {\bf 40} (2017), 3173--3189.
 \item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: Semi-linear optimal control problem on a smooth oscillating
@@
 rough domains, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954.
+\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: Generalization of unfolding operator for highly oscillating
+smooth boundary domains and homogenization, \emph{Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30.
 \item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu: Asymptotic analysis of a boundary optimal control problem on a
@@
 subset of all {F}ourier coefficients, \emph{Publ. Mat.} {\bf 63} (2019), 307--341.
+\item Anamby, Pramath and Das, Soumya: Bounds for the {P}etersson norms of the pullbacks of
+{S}aito-{K}urokawa lifts, \emph{J. Number Theory} {\bf 191} (2018), 289--304.
 \item Anand, Jatin and Bhattacharyya, Tirthankar and Srivastava,
@@
 {H}ardy space, \emph{Arch. Math. (Basel)} {\bf 114} (2020), 431--444.
+\item Arunkumar, G. and Kus, Deniz and Venkatesh, R.: Root multiplicities for {B}orcherds algebras and graph
+coloring, \emph{J. Algebra} {\bf 499} (2018), 538--569.
+\item Ayyer, Arvind: Full current statistics for a disordered open exclusion
+process, \emph{J. Phys. A} {\bf 49} (2016), 155003, 10.
 \item Ayyer, Arvind: Squareness for the {M}onopole-{D}imer model, \emph{Ann. Comb.} {\bf 24} (2020), 237--255.
@@
 sign matrices of odd order, \emph{Adv. Math.} {\bf 367} (2020), 107125, 56.
+\item Ayyer, Arvind and Bouttier, J\'{e}r\'{e}mie and Corteel, Sylvie and
+Linusson, Svante and Nunzi, Fran\c{c}ois: Bumping sequences and multispecies juggling, \emph{Adv. in Appl. Math.} {\bf 98} (2018), 100--126.
+\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar: Matrix product solution of a left-permeable two-species
+asymmetric exclusion process, \emph{Phys. Rev. E} {\bf 97} (2018), 012151, 10.
 \item Ayyer, Arvind and Finn, Caley and Roy, Dipankar: The phase diagram for a multispecies left-permeable asymmetric
@@
 \item Ayyer, Arvind and Fischer, Ilse: Bijective proofs of skew {S}chur polynomial factorizations, \emph{J. Combin. Theory Ser. A} {\bf 174} (2020), 105241, 40.
+\item Ayyer, Arvind and Josuat-Verg\`es, Matthieu and Ramassamy,
+Sanjay: Extensions of partial cyclic orders and consecutive coordinate
+polytopes, \emph{Ann. H. Lebesgue} {\bf 3} (2020), 275--297.
+\item Ayyer, Arvind and Linusson, Svante: Correlations in the multispecies {TASEP} and a conjecture by
+{L}am, \emph{Trans. Amer. Math. Soc.} {\bf 369} (2017), 1097--1125.
 \item Ayyer, Arvind and Linusson, Svante: Reverse juggling processes, \emph{Random Structures Algorithms} {\bf 55} (2019), 56--72.
+\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven: Odd partitions in {Y}oung's lattice, \emph{S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
+\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven: Representations of symmetric groups with non-trivial
+determinant, \emph{J. Combin. Theory Ser. A} {\bf 150} (2017), 208--232.
+\item Ayyer, Arvind and Ramassamy, Sanjay: The {H}ilbert-{G}alton board, \emph{ALEA Lat. Am. J. Probab. Math. Stat.} {\bf 15} (2018), 755--774.
+\item Ayyer, Arvind and Schilling, Anne and Thi\'{e}ry, Nicolas M.: Spectral gap for random-to-random shuffling on linear
+extensions, \emph{Exp. Math.} {\bf 26} (2017), 22--30.
 \item Ayyer, Arvind and Singla, Pooja: Random motion on finite rings, {I}: commutative rings, \emph{Algebr. Represent. Theory} {\bf 23} (2020), 583--604.
+\item Ayyer, Arvind and Sinha, Shubham: Random {$t$}-cores and hook lengths in random partitions, \emph{S\'{e}m. Lothar. Combin.} {\bf 84B} (2020), Art. 58, 11.
+\item Ayyer, Arvind and Steinberg, Benjamin: Random walks on rings and modules, \emph{Algebr. Comb.} {\bf 3} (2020), 309--329.
+\item B\"{o}cherer, Siegfried and Das, Soumya: Cuspidality and the growth of {F}ourier coefficients: small
+weights, \emph{Math. Z.} {\bf 283} (2016), 539--553.
+\item B\"{o}cherer, Siegfried and Das, Soumya: Cuspidality and the growth of {F}ourier coefficients of
+modular forms, \emph{J. Reine Angew. Math.} {\bf 741} (2018), 161--178.
+\item B\"{o}cherer, Siegfried and Das, Soumya: Petersson norms of not necessarily cuspidal {J}acobi modular
+forms and applications, \emph{Adv. Math.} {\bf 336} (2018), 335--376.
+\item Bagchi, Bhaskar and Burton, Benjamin A. and Datta, Basudeb and
+Singh, Nitin and Spreer, Jonathan: Efficient algorithms to decide tightness, \emph{32nd {I}nternational {S}ymposium on {C}omputational
+{G}eometry} {\bf 51} (2016), Art. 12, 15.
+\item Bagchi, Bhaskar and Datta, Basudeb and Spreer, Jonathan: A characterization of tightly triangulated 3-manifolds, \emph{European J. Combin.} {\bf 61} (2017), 133--137.
+\item Bagchi, Bhaskar and Datta, Basudeb and Spreer, Jonathan: Tight triangulations of closed 3-manifolds, \emph{European J. Combin.} {\bf 54} (2016), 103--120.
+\item Bagchi, Sayan and Thangavelu, Sundaram: Weighted norm inequalities for {W}eyl multipliers and fourier
+multipliers on the {H}eisenberg group, \emph{J. Anal. Math.} {\bf 136} (2018), 1--29.
+\item Baklouti, Ali and Thangavelu, Sundaram: Hardy and {M}iyachi theorems for {H}eisenberg motion groups, \emph{Nagoya Math. J.} {\bf 229} (2018), 1--20.
+\item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
+Verma, Kaushal: Further remarks on the higher dimensional {S}uita conjecture, \emph{Ann. Polon. Math.} {\bf 125} (2020), 101--115.
 \item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
@@
 operator, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25.
+\item Balodi, Mamta and Banerjee, Abhishek and Naolekar, Anita: B{V}-operators and the secondary {H}ochschild complex, \emph{C. R. Math. Acad. Sci. Paris} {\bf 358} (2020), 1239--1258.
+\item Balodi, Mamta and Banerjee, Abhishek and Ray, Samarpita: Cohomology of modules over {$H$}-categories and
+co-{$H$}-categories, \emph{Canad. J. Math.} {\bf 72} (2020), 1352--1385.
+\item Balodi, Mamta and Huang, Hua-Lin and Kumar, Shiv Datt: On the classification of finite quasi-quantum groups, \emph{Rev. Math. Phys.} {\bf 29} (2017), 1730003, 20.
+\item Balodi, Mamta and Palcoux, Sebastien: On {B}oolean intervals of finite groups, \emph{J. Combin. Theory Ser. A} {\bf 157} (2018), 49--69.
+\item Banerjee, Abhishek: On some spectral spaces associated to tensor triangulated
+categories, \emph{Arch. Math. (Basel)} {\bf 108} (2017), 581--591.
+\item Banerjee, Abhishek: On {A}uslander's formula and cohereditary torsion pairs, \emph{Commun. Contemp. Math.} {\bf 20} (2018), 1750071, 27.
+\item Banerjee, Abhishek: Modular {H}ecke algebras over {M}\"{o}bius categories, \emph{J. Geom. Phys.} {\bf 131} (2018), 23--40.
+\item Banerjee, Abhishek: Closure operators in abelian categories and spectral spaces, \emph{Theory Appl. Categ.} {\bf 32} (2017), Paper No. 20, 719--735.
+\item Banerjee, Abhishek: Noetherian schemes over abelian symmetric monoidal categories, \emph{Internat. J. Math.} {\bf 28} (2017), 1750051, 34.
 \item Banerjee, Abhishek: On differential torsion theories and rings with several
 objects, \emph{Canad. Math. Bull.} {\bf 62} (2019), 703--714.
+\item Banerjee, Abhishek: Une note sur les d\'erivations localement nilpotentes dans les
+cat\'egories mono\"\i dales sym\'etriques, \emph{Bull. Belg. Math. Soc. Simon Stevin} {\bf 23} (2016), 151--160.
+\item Banerjee, Abhishek: Realizations of pairs and {O}ka families in tensor
+triangulated categories, \emph{Eur. J. Math.} {\bf 2} (2016), 760--797.
+\item Banerjee, Abhishek: Homologie de {H}ochschild et espaces alg\'ebriques, \emph{Math. Scand.} {\bf 118} (2016), 33--42.
+\item Banerjee, Abhishek: A topological {N}ullstellensatz for tensor-triangulated
+categories, \emph{C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375.
+\item Banerjee, Abhishek: Some remarks on a theorem of {B}ergman, \emph{C. R. Math. Acad. Sci. Paris} {\bf 354} (2016), 665--670.
+\item Banerjee, Abhishek: Monoidal semifilters and arrays of prime ideals, \emph{Fund. Math.} {\bf 237} (2017), 281--296.
+\item Banerjee, Abhishek: Schemes over symmetric monoidal categories and torsion
+theories, \emph{J. Pure Appl. Algebra} {\bf 220} (2016), 3017--3047.
+\item Banerjee, Abhishek: Quasimodular {H}ecke algebras and {H}opf actions, \emph{J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080.
+\item Banerjee, Abhishek: Completions of monoid objects and descent results, \emph{J. Algebra} {\bf 507} (2018), 362--399.
 \item Banerjee, Abhishek and Kour, Surjeet: {$(A,\delta)$}-modules, {H}ochschild homology and higher
 derivations, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802.
+\item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable {CMC} free-boundary surfaces in a strictly convex
+domain of a bi-invariant {L}ie group, \emph{Internat. J. Math.} {\bf 31} (2020), 2050086, 9.
+\item Basak, Biplab: An algorithmic approach to construct crystallizations of
+3-manifolds from presentations of fundamental groups, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 126} (2016), 629--653.
+\item Basak, Biplab and Casali, Maria Rita: Lower bounds for regular genus and gem-complexity of {PL}
+4-manifolds, \emph{Forum Math.} {\bf 29} (2017), 761--773.
+\item Basak, Biplab and Spreer, Jonathan: Simple crystallizations of 4-manifolds, \emph{Adv. Geom.} {\bf 16} (2016), 111--130.
+\item Basak, Gopal K. and Ghosh, Mrinal K. and Mukherjee, Diganta: A mean-reverting stochastic model for the political business
+cycle, \emph{Stoch. Anal. Appl.} {\bf 34} (2016), 96--116.
+\item Basu, Arnab and Ghosh, Mrinal K.: Nonzero-sum risk-sensitive stochastic games on a countable
+state space, \emph{Math. Oper. Res.} {\bf 43} (2018), 516--532.
 \item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
@@
 Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
+Morales, Alejandro H. and Yip, Martha: The volume of the caracol polytope, \emph{S\'{e}m. Lothar. Combin.} {\bf 80B} (2018), Art. 87, 12.
+\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
+Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
 Morales, Alejandro H. and Yip, Martha: A combinatorial model for computing volumes of flow polytopes, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 3369--3404.
+\item Bennett, Nathan and Iyer, Srikanth K. and Jammalamadaka, S.
+Rao: Analysis of gamma and {W}eibull lifetime data under a general
+censoring scheme and in the presence of covariates, \emph{Comm. Statist. Theory Methods} {\bf 46} (2017), 2277--2289.
+\item Bera, Sayani and Pal, Ratna: Dynamics of semigroups of entire maps of {$\Bbb{C}^k$}, \emph{Complex Anal. Synerg.} {\bf 2} (2016), Paper No. 2, 22.
+\item Bera, Sayani and Pal, Ratna and Verma, Kaushal: Examples of non-autonomous basins of attraction, \emph{Illinois J. Math.} {\bf 61} (2017), 531--567.
 \item Bera, Sayani and Pal, Ratna and Verma, Kaushal: A rigidity theorem for {H}\'{e}non maps, \emph{Eur. J. Math.} {\bf 6} (2020), 508--532.
+\item Bera, Sayani and Verma, Kaushal: Some aspects of shift-like automorphisms of {$\Bbb C^k$}, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 128} (2018), Art. 10, 48.
+\item Bera, Sudip and Mukherjee, Sajal Kumar: Generalized power sum and {N}ewton-{G}irard identities, \emph{Graphs Combin.} {\bf 36} (2020), 1957--1964.
+\item Bhamidi, Shankar and Dhara, Souvik and van der Hofstad, Remco
+and Sen, Sanchayan: Universality for critical heavy-tailed network models: metric
+structure of maximal components, \emph{Electron. J. Probab.} {\bf 25} (2020), Paper No. 47, 57.
+\item Bhamidi, Shankar and Sen, Sanchayan: Geometry of the vacant set left by random walk on random
+graphs, {W}right's constants, and critical random graphs with
+prescribed degrees, \emph{Random Structures Algorithms} {\bf 56} (2020), 676--721.
+\item Bharali, Gautam: Complex geodesics, their boundary regularity, and a
+{H}ardy-{L}ittlewood-type lemma, \emph{Ann. Acad. Sci. Fenn. Math.} {\bf 41} (2016), 253--263.
 \item Bharali, Gautam: On the growth of the {B}ergman metric near a point of infinite
 type, \emph{J. Geom. Anal.} {\bf 30} (2020), 1238--1258.
+\item Bharali, Gautam and Biswas, Indranil and Divakaran, Divakaran
+and Janardhanan, Jaikrishnan: Proper holomorphic mappings onto symmetric products of a
+{R}iemann surface, \emph{Doc. Math.} {\bf 23} (2018), 1291--1311.
+\item Bharali, Gautam and Biswas, Indranil and Schumacher, Georg: A criterion for a degree-one holomorphic map to be a
+biholomorphism, \emph{Complex Var. Elliptic Equ.} {\bf 62} (2017), 914--918.
 \item Bharali, Gautam and Chandel, Vikramjeet Singh: Pick interpolation on the polydisc: small families of
 sufficient kernels, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093.
+\item Bharali, Gautam and Sridharan, Shrihari: Holomorphic correspondences related to finitely generated
+rational semigroups, \emph{Internat. J. Math.} {\bf 28} (2017), 1750108, 25.
+\item Bharali, Gautam and Sridharan, Shrihari: The dynamics of holomorphic correspondences of {$\Bbb P^1$}:
+invariant measures and the normality set, \emph{Complex Var. Elliptic Equ.} {\bf 61} (2016), 1587--1613.
+\item Bharali, Gautam and Zimmer, Andrew: Goldilocks domains, a weak notion of visibility, and
+applications, \emph{Adv. Math.} {\bf 310} (2017), 377--425.
+\item Bhatia, Manan: Moderate deviation and exit time estimates for stationary last
+passage percolation, \emph{J. Stat. Phys.} {\bf 181} (2020), 1410--1432.
+\item Bhattacharjee, M. and Eschmeier, J. and Keshari, Dinesh K. and
+Sarkar, Jaydeb: Dilations, wandering subspaces, and inner functions, \emph{Linear Algebra Appl.} {\bf 523} (2017), 263--280.
+\item Bhattacharjee, Monojit and Sarkar, Jaydeb: Operator positivity and analytic models of commuting tuples of
+operators, \emph{Studia Math.} {\bf 232} (2016), 155--171.
+\item Bhattacharyya, T. and Narayanan, E. K. and Sarkar, Jaydeb: Analytic model of doubly commuting contractions, \emph{Oper. Matrices} {\bf 11} (2017), 101--113.
+\item Bhattacharyya, T. and Sau, H.: Explicit and unique construction of tetrablock unitary
+dilation in a certain case, \emph{Complex Anal. Oper. Theory} {\bf 10} (2016), 749--768.
+\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel,
+Vikramjeet Singh: On the {N}evanlinna problem: characterization of all
+{S}chur-{A}gler class solutions affiliated with a given
+kernel, \emph{Studia Math.} {\bf 255} (2020), 83--107.
 \item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K.: Survey of last ten years of work done in {I}ndia in some
 selected areas of functional analysis and operator theory, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617.
+\item Bhattacharyya, Tirthankar and Sau, Haripada: {$\Gamma$}-unitaries, dilation and a natural example, \emph{Publ. Res. Inst. Math. Sci.} {\bf 53} (2017), 261--285.
+\item Bhattacharyya, Tirthankar and Sau, Haripada: Holomorphic functions on the symmetrized bidisk---realization,
+interpolation and extension, \emph{J. Funct. Anal.} {\bf 274} (2018), 504--524.
 \item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
@@
 developing countries} {\bf 275} (2019), 42--64.
+\item Bhosle, Usha N.: Hitchin pairs on reducible curves, \emph{Internat. J. Math.} {\bf 29} (2018), 1850015, 49.
+\item Bhosle, Usha N.: On a conjecture of {B}utler, \emph{Analytic and algebraic geometry} {\bf } (2017), 29--48.
+\item Bhosle, Usha N. and Biswas, Indranil: Moduli spaces of vector bundles on a singular rational ruled
+surface, \emph{Geom. Dedicata} {\bf 180} (2016), 399--413.
+\item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and
+Pingali, Vamsi P.: Rational cuspidal curves on del-{P}ezzo surfaces, \emph{J. Singul.} {\bf 17} (2018), 91--107.
 \item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy: Branched projective structures on a {R}iemann surface and
 logarithmic connections, \emph{Doc. Math.} {\bf 24} (2019), 2299--2337.
+\item Biswas, Indranil and Pingali, Vamsi Pritham: A characterization of finite vector bundles on {G}auduchon
+astheno-{K}\"{a}hler manifolds, \emph{\'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art. 6, 13.
+\item Biswas, Indranil and Pingali, Vamsi Pritham: Metric properties of parabolic ample bundles, \emph{Int. Math. Res. Not. IMRN} {\bf } (2020), 9336--9369.
+\item Biswas, Indranil and Seshadri, Harish: Chern scalar curvature and symmetric products of compact
+{R}iemann surfaces, \emph{Pure Appl. Math. Q.} {\bf 12} (2016), 463--471.
+\item Biswas, Indranil and Seshadri, Harish: Quot schemes and {R}icci semipositivity, \emph{C. R. Math. Acad. Sci. Paris} {\bf 355} (2017), 577--581.
 \item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi: Edge patch-wise local projection stabilized nonconforming
@@
 {${S}_n$}-invariant kernels, \emph{J. Funct. Anal.} {\bf 276} (2019), 751--784.
+\item Bleher, F. M. and Chinburg, T. and Greenberg, R. and Kakde, M.
+and Pappas, G. and Sharifi, R. and Taylor, M. J.: Higher {C}hern classes in {I}wasawa theory, \emph{Amer. J. Math.} {\bf 142} (2020), 627--682.
+\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram: Mixed norm estimates for the {C}es\`aro means associated with
+{D}unkl-{H}ermite expansions, \emph{Trans. Amer. Math. Soc.} {\bf 369} (2017), 7021--7047.
 \item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram: On extension problem, trace {H}ardy and {H}ardy's inequalities
 for some fractional {L}aplacians, \emph{Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605.
+\item Boggarapu, Pradeep and Thangavelu, S.: On the chaotic behavior of the {D}unkl heat semigroup on
+weighted {$L^p$} spaces, \emph{Israel J. Math.} {\bf 217} (2017), 57--92.
+\item Boggarapu, Pradeep and Thangavelu, S.: Mixed norm estimates for the {R}iesz transforms on {$SU(2)$}, \emph{Publ. Mat.} {\bf 60} (2016), 171--190.
+\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal: Comments on the {G}reen's function of a planar domain, \emph{Anal. Math. Phys.} {\bf 8} (2018), 383--414.
+\item Brenner, Susanne C. and Gudi, Thirupathi and Porwal, Kamana
+and Sung, Li-Yeng: A {M}orley finite element method for an elliptic distributed
+optimal control problem with pointwise state and control
+constraints, \emph{ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206.
+\item Burton, Benjamin A. and Datta, Basudeb and Singh, Nitin and
+Spreer, Jonathan: A construction principle for tight and minimal triangulations
+of manifolds, \emph{Exp. Math.} {\bf 27} (2018), 22--36.
 \item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella: Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
 indefinite second-order linear elliptic problems, \emph{Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.
+\item Chakrabarti, A. and Mondal, Sumita Rani: On approximate numerical method of solution of {F}redholm
+integral equations, \emph{Int. J. Appl. Math. Anal. Appl.} {\bf 11} (2016), 153--162.
 \item Chakraborty, Atlanta and Chandru, Vijay and Rao, M. R.: A linear programming primer: from {F}ourier to {K}armarkar, \emph{Ann. Oper. Res.} {\bf 287} (2020), 593--616.
+\item Chan, Chun Lam and Fernandes, Winston and Kashyap, Navin and
+Krishnapur, Manjunath: Phase transitions for the uniform distribution in the pattern
+maximum likelihood problem and its {B}ethe approximation, \emph{SIAM J. Discrete Math.} {\bf 31} (2017), 597--631.
+\item Chandel, Vikramjeet Singh: The three-point {P}ick-{N}evanlinna interpolation problem on
+the polydisc, \emph{Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352.
 \item Chandel, Vikramjeet Singh: The 3-point spectral pick interpolation problem and an
 application to holomorphic correspondences, \emph{J. Geom. Anal.} {\bf 30} (2020), 551--572.
+\item Chas, Moira and Gadgil, Siddhartha: The extended {G}oldman bracket determines intersection numbers
+for surfaces and orbifolds, \emph{Algebr. Geom. Topol.} {\bf 16} (2016), 2813--2838.
+\item Chatterjee, Esha and Hassan, Sk. Sarif: On the asymptotic character of a generalized rational
+difference equation, \emph{Discrete Contin. Dyn. Syst.} {\bf 38} (2018), 1707--1718.
+\item Chattopadhyay, Arup and Sain, Debmalya and Senapati, Tanusri: A study of non-positive operators between real normed linear
+spaces, \emph{Acta Sci. Math. (Szeged)} {\bf 86} (2020), 449--466.
+\item Choudhary, A. and Martha, S. C. and Chakrabarti, A.: Modified method for the solution of dual trigonometric series
+relations, \emph{Proc. Nat. Acad. Sci. India Sect. A} {\bf 90} (2020), 437--445.
+\item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
+K. C.: A note on linear preservers of semipositive and minimally
+semipositive matrices, \emph{Electron. J. Linear Algebra} {\bf 34} (2018), 687--694.
 \item Choudhury, Projesh Nath and Tsatsomeros, Michael J.: Algorithmic detection and construction of {N}-matrices, \emph{Linear Algebra Appl.} {\bf 602} (2020), 46--56.
+\item Chowdhury, Sudipto and Gudi, Thirupathi: A {$C^0$} interior penalty method for the {D}irichlet control
+problem governed by biharmonic operator, \emph{J. Comput. Appl. Math.} {\bf 317} (2017), 290--306.
+\item Chowdhury, Sudipto and Gudi, Thirupathi and Nandakumaran, A.
+K.: Error bounds for a {D}irichlet boundary control problem based
+on energy spaces, \emph{Math. Comp.} {\bf 86} (2017), 1103--1126.
+\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram: Hardy-type inequalities for fractional powers of the
+{D}unkl-{H}ermite operator, \emph{Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544.
 \item Cicuttin, Matteo and Ern, Alexandre and Gudi, Thirupathi: Hybrid high-order methods for the elliptic obstacle problem, \emph{J. Sci. Comput.} {\bf 83} (2020), Paper No. 8, 18.
+\item Cui, Jintao and Gudi, Thirupathi: Finite element approximation of a free boundary plasma
+problem, \emph{Adv. Comput. Math.} {\bf 43} (2017), 517--535.
+\item Das, Soumya: Cuspidality and the growth of {F}ourier coefficients of
+modular forms: a survey, \emph{Indian J. Pure Appl. Math.} {\bf 47} (2016), 9--22.
+\item Das, Soumya and Ganguly, Satadal: A note on small gaps between nonzero {F}ourier coefficients of
+cusp forms, \emph{Proc. Amer. Math. Soc.} {\bf 144} (2016), 2301--2305.
 \item Das, Soumya and Jha, Abhash Kumar: Analytic properties of twisted real-analytic {H}ermitian
 {K}lingen type {E}isenstein series and applications, \emph{Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116.
+\item Das, Soumya and Khan, Rizwanur: The third moment of symmetric square {$L$}-functions, \emph{Q. J. Math.} {\bf 69} (2018), 1063--1087.
+\item Das, Soumya and Kohnen, Winfried: On sign changes of eigenvalues of {S}iegel cusp forms of genus
+2 in prime powers, \emph{Acta Arith.} {\bf 183} (2018), 167--172.
 \item Das, Soumya and Pal, Ritwik: The first negative eigenvalue of {Y}oshida lifts, \emph{Res. Number Theory} {\bf 5} (2019), Paper No. 20, 9.
+\item Das, Soumya and Pal, Ritwik: Jacobi forms and differential operators: odd weights, \emph{J. Number Theory} {\bf 179} (2017), 113--125.
+\item Datar, Ved V. and Pingali, Vamsi Pritham: On coupled constant scalar curvature {K}\"{a}hler metrics, \emph{J. Symplectic Geom.} {\bf 18} (2020), 961--994.
+\item Datta, Basudeb and Maity, Dipendu: Correction to: {S}emi-equivelar and vertex-transitive maps on
+the torus, \emph{Beitr. Algebra Geom.} {\bf 61} (2020), 187--188.
+\item Datta, Basudeb and Maity, Dipendu: Semi-equivelar and vertex-transitive maps on the torus, \emph{Beitr. Algebra Geom.} {\bf 58} (2017), 617--634.
+\item Datta, Basudeb and Maity, Dipendu: Semi-equivelar maps on the torus and the {K}lein bottle are
+{A}rchimedean, \emph{Discrete Math.} {\bf 341} (2018), 3296--3309.
+\item Datta, Basudeb and Murai, Satoshi: On stacked triangulated manifolds, \emph{Electron. J. Combin.} {\bf 24} (2017), Paper 4.12, 14.
+\item Datta, Basudeb and Sarkar, Soumen: On equilibrium triangulations of quasitoric manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57-56.
+\item Dhanya, R. and Prashanth, S. and Tiwari, Sweta and Sreenadh,
+K.: Elliptic problems in {${\Bbb R}^N$} with critical and singular
+discontinuous nonlinearities, \emph{Complex Var. Elliptic Equ.} {\bf 61} (2016), 1668--1688.
+\item Dhanya, R. and Sarkar, Abhishek: Isolated singularities of polyharmonic operator in even
+dimension, \emph{Complex Var. Elliptic Equ.} {\bf 61} (2016), 55--66.
+\item Dhara, Souvik and van der Hofstad, Remco and van Leeuwaarden,
+Johan S. H. and Sen, Sanchayan: Heavy-tailed configuration models at criticality, \emph{Ann. Inst. Henri Poincar\'{e} Probab. Stat.} {\bf 56} (2020), 1515--1558.
+\item Dhillon, Gurbir and Khare, Apoorva: Faces of highest weight modules and the universal {W}eyl
+polyhedron, \emph{Adv. Math.} {\bf 319} (2017), 111--152.
 \item Dond, Asha K. and Gudi, Thirupathi: Patch-wise local projection stabilized finite element methods
 for convection-diffusion-reaction problems, \emph{Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663.
+\item Dond, Asha K. and Gudi, Thirupathi and Nataraj, Neela: A nonconforming finite element approximation for optimal
+control of an obstacle problem, \emph{Comput. Methods Appl. Math.} {\bf 16} (2016), 653--666.
 \item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH.: An error analysis of discontinuous finite element methods for
 the optimal control problems governed by {S}tokes equation, \emph{Numer. Funct. Anal. Optim.} {\bf 40} (2019), 421--460.
+\item Fern\'{o}s, Talia and Singla, Pooja: On images of real representations of special linear groups
+over complete discrete valuation rings, \emph{Glasg. Math. J.} {\bf 58} (2016), 263--272.
+\item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P.
+and Silberman, Lior and Tao, Terence: Homogeneous length functions on groups, \emph{Algebra Number Theory} {\bf 12} (2018), 1773--1786.
+\item Gaddam, Sharat and Gudi, Thirupathi: Inhomogeneous {D}irichlet boundary condition in the {\it a
+posteriori} error control of the obstacle problem, \emph{Comput. Math. Appl.} {\bf 75} (2018), 2311--2327.
+\item Gaddam, Sharat and Gudi, Thirupathi: Bubbles enriched quadratic finite element method for the
+3{D}-elliptic obstacle problem, \emph{Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236.
 \item Gadgil, Siddhartha: Homogeneous {L}ength {F}unctions on {G}roups: {I}ntertwined
 {C}omputer and {H}uman {P}roofs, \emph{J. Automat. Reason.} {\bf 64} (2020), 677--688.
+\item Gadgil, Siddhartha and Kulkarni, Dheeraj: Relative symplectic caps, 4-genus and fibered knots, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 126} (2016), 261--275.
 \item Garani, Shayan Srinivasa and Seshadri, Harish: An algorithmic approach to {S}outh {I}ndian classical music, \emph{J. Math. Music} {\bf 13} (2019), 107--134.
+\item Gaussier, Herv\'{e} and Seshadri, Harish: Metric geometry of the {K}obayashi metric, \emph{Eur. J. Math.} {\bf 3} (2017), 1030--1044.
 \item Gaussier, Herv\'{e} and Seshadri, Harish: Holomorphic motions and complex geometry, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 301--313.
+\item Gaussier, Herv\'{e} and Seshadri, Harish: On the {G}romov hyperbolicity of convex domains in {$\Bbb
+C^n$}, \emph{Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641.
+\item Gauttam, Sunil Kumar and Kumar, K. Suresh and Pal, Chandan: Risk-sensitive control of reflected diffusion processes on
+orthrant, \emph{Pure Appl. Funct. Anal.} {\bf 2} (2017), 477--510.
+\item Gayen, R. and Gupta, Sourav and Chakrabarti, A.: Approximate solution of the problem of scattering of surface
+water waves by a partially immersed rigid plane vertical
+barrier, \emph{Appl. Math. Lett.} {\bf 58} (2016), 19--25.
+\item Ghara, Soumitra: The orbit of a bounded operator under the {M}\"{o}bius group
+modulo similarity equivalence, \emph{Israel J. Math.} {\bf 238} (2020), 167--207.
 \item Ghara, Soumitra and Kumar, Surjit: On the sum of two subnormal kernels, \emph{J. Math. Anal. Appl.} {\bf 469} (2019), 1015--1027.
+\item Ghosh, Mrinal K. and Kumar, K. Suresh and Pal, Chandan: Zero-sum risk-sensitive stochastic games for continuous time
+{M}arkov chains, \emph{Stoch. Anal. Appl.} {\bf 34} (2016), 835--851.
+\item Ghosh, Mrinal K. and Pradhan, Somnath: Risk-sensitive stochastic differential games with reflecting
+diffusions, \emph{Stoch. Anal. Appl.} {\bf 36} (2018), 1--27.
+\item Ghosh, Mrinal Kanti and Pradhan, Somnath: Zero-sum risk-sensitive stochastic differential games with
+reflecting diffusions in the orthant, \emph{ESAIM Control Optim. Calc. Var.} {\bf 26} (2020), Paper No. 114, 33.
+\item Ghosh, Puja and Paul, Kallol and Sain, Debmalya: Symmetric properties of orthogonality of linear operators on
+{$(\Bbb R^n,\|\cdot\|_1)$}, \emph{Novi Sad J. Math.} {\bf 47} (2017), 41--46.
+\item Ghosh, Puja and Sain, Debmalya and Paul, Kallol: On symmetry of {B}irkhoff-{J}ames orthogonality of linear
+operators, \emph{Adv. Oper. Theory} {\bf 2} (2017), 428--434.
+\item Ghosh, Subhajit: Total variation cutoff for the transpose top-2 with random
+shuffle, \emph{J. Theoret. Probab.} {\bf 33} (2020), 1832--1854.
+\item Ghosh, Subhajit: Cutoff for the warp-transpose top with random shuffle, \emph{S\'{e}m. Lothar. Combin.} {\bf 84B} (2020), Art. 69, 12.
+\item Ghosh, Subhroshekhar and Krishnapur, Manjunath and Peres,
+Yuval: Continuum percolation for {G}aussian zeroes and {G}inibre
+eigenvalues, \emph{Ann. Probab.} {\bf 44} (2016), 3357--3384.
 \item Gudi, Thirupathi and Majumder, Papri: Crouzeix-{R}aviart finite element approximation for the
@@
 solving parabolic obstacle problem, \emph{Comput. Math. Appl.} {\bf 78} (2019), 3896--3915.
+\item Gudi, Thirupathi and Porwal, Kamana: A {$C^0$} interior penalty method for a fourth-order
+variational inequality of the second kind, \emph{Numer. Methods Partial Differential Equations} {\bf 32} (2016), 36--59.
+\item Gudi, Thirupathi and Porwal, Kamana: A posteriori error estimates of discontinuous {G}alerkin
+methods for the {S}ignorini problem, \emph{J. Comput. Appl. Math.} {\bf 292} (2016), 257--278.
+\item Gudi, Thirupathi and Sau, Ramesh Ch.: Finite element analysis of the constrained {D}irichlet
+boundary control problem governed by the diffusion problem, \emph{ESAIM Control Optim. Calc. Var.} {\bf 26} (2020), Paper No. 78, 19.
+\item Gupta, Rajeev: An improvement on the bound for {$C_2(n)$}, \emph{Acta Sci. Math. (Szeged)} {\bf 83} (2017), 263--269.
 \item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: Unitary equivalence of operator-valued multishifts, \emph{J. Math. Anal. Appl.} {\bf 487} (2020), 124032, 23.
@@
 multishifts, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.
+\item Gupta, Rajeev and Misra, Gadadhar: The {C}arath\'{e}odory-{F}ej\'{e}r interpolation on the polydisc, \emph{Studia Math.} {\bf 254} (2020), 265--293.
+\item Gupta, Rajeev and Ramiz Reza, Md.: Operator space structures on {$\ell^1(n)$}, \emph{Houston J. Math.} {\bf 44} (2018), 1205--1212.
+\item Gupta, S. C.: The classical {S}tefan problem, \emph{} {\bf } (2018), xxiii+726.
 \item Gupta, Subhojoy: Limits of harmonic maps and crowned hyperbolic surfaces, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 7573--7596.
@@
 a {R}iemann surface, \emph{Math. Ann.} {\bf 373} (2019), 73--118.
+\item Gupta, Subhojoy and Wolf, Michael: Quadratic differentials, half-plane structures, and harmonic
+maps to trees, \emph{Comment. Math. Helv.} {\bf 91} (2016), 317--356.
+\item Gupta, Subhojoy and Wolf, Michael: Meromorphic quadratic differentials with complex residues and
+spiralling foliations, \emph{In the tradition of {A}hlfors-{B}ers. {VII}} {\bf 696} (2017), 153--181.
 \item Hatui, Sumana: Schur multipliers of special {$p$}-groups of rank 2, \emph{J. Group Theory} {\bf 23} (2020), 85--95.
 \item Hazra, Somnath: Homogeneous 2-shifts, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.
+\item Iyer, Srikanth K.: The random connection model: connectivity, edge lengths, and
+degree distributions, \emph{Random Structures Algorithms} {\bf 52} (2018), 283--300.
+\item Iyer, Srikanth K. and Vaze, Rahul and Narasimha, Dheeraj: Autoregressive cascades on random networks, \emph{Phys. A} {\bf 447} (2016), 345--354.
+\item Iyer, Srikanth K. and Yogeshwaran, D.: Thresholds for vanishing of `isolated' faces in random \v{C}ech
+and {V}ietoris-{R}ips complexes, \emph{Ann. Inst. Henri Poincar\'{e} Probab. Stat.} {\bf 56} (2020), 1869--1897.
+\item Iyer, Srikanth and Vaze, Rahul: Achieving nonzero information velocity in wireless networks, \emph{Ann. Appl. Probab.} {\bf 27} (2017), 48--64.
 \item Jha, Abhash Kumar and Juyal, Abhishek and Pandey, Manish
@@
 associated to newforms on {$\Gamma_0(N)$}, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.
+\item Jha, Abhash Kumar and Kumar, Arvind: Construction of cusp forms using {R}ankin-{C}ohen brackets, \emph{Analytic number theory, modular forms and {$q$}-hypergeometric
+series} {\bf 221} (2017), 329--341.
 \item Jha, Abhash Kumar and Sahu, Brundaban: Rankin-{C}ohen brackets on {J}acobi forms of several variables
@@
 certain {D}irichlet series, \emph{Automorphic forms and related topics} {\bf 732} (2019), 91--99.
+\item Ji, Kui and Jiang, Chunlan and Keshari, Dinesh Kumar and
+Misra, Gadadhar: Rigidity of the flag structure for a class of
+{C}owen-{D}ouglas operators, \emph{J. Funct. Anal.} {\bf 272} (2017), 2899--2932.
+\item Jiang, Chunlan and Ji, Kui and Misra, Gadadhar: Classification of quasi-homogeneous holomorphic curves and
+operators in the {C}owen-{D}ouglas class, \emph{J. Funct. Anal.} {\bf 273} (2017), 2870--2915.
+\item Kabiraj, Arpan: Center of the {G}oldman {L}ie algebra, \emph{Algebr. Geom. Topol.} {\bf 16} (2016), 2839--2849.
+\item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
+Sekar, Sruthi: Four-state non-malleable codes with explicit constant rate, \emph{J. Cryptology} {\bf 33} (2020), 1044--1079.
+\item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
+Sekar, Sruthi: Four-state non-malleable codes with explicit constant rate, \emph{Theory of cryptography. {P}art {II}} {\bf 10678} (2017), 344--375.
+\item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
+Sekar, Sruthi: Non-malleable randomness encoders and their applications, \emph{Advances in cryptology---{EUROCRYPT} 2018. {P}art {III}} {\bf 10822} (2018), 589--617.
 \item Kashyap, G.
@@
 Ravindranath and G.
-Ambika: Synapse loss and progress of Alzheimers disease - A network model, \emph{Scientific Reports} {\bf 9} (2019).
+Ambika: Synapse loss and progress of Alzheimer&rsquo;s disease - A network model, \emph{Scientific Reports} {\bf 9} (2019).
 \item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan: On the convolution of {M}ittag-{L}effler distributions and its
 applications to fractional point processes, \emph{Stoch. Anal. Appl.} {\bf 37} (2019), 115--122.
+\item Kaur, Amandeep and Martha, S. C. and Chakrabarti, A.: An algebraic method of solution of a water wave scattering
+problem involving an asymmetrical trench, \emph{Comput. Appl. Math.} {\bf 39} (2020), Paper No. 229, 19.
 \item Khan, Mohammad Yasir Feroz and Biswas, Rahul and Sau, Ramesh
@@
 C(\overline\Omega)$}, \emph{Math. Student} {\bf 88} (2019), 153--158.
+\item Khare, Apoorva: Generalized nil-{C}oxeter algebras over discrete complex
+reflection groups, \emph{Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999.
+\item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric
+semigroups, \emph{Adv. Oper. Theory} {\bf 5} (2020), 779--795.
+\item Khare, Apoorva and Rajaratnam, Bala: The {H}offmann-{J}\o rgensen inequality in metric semigroups, \emph{Ann. Probab.} {\bf 45} (2017), 4101--4111.
 \item Khare, Apoorva and Tikaradze, Akaki: A {C}arlitz--von {S}taudt type theorem for finite rings, \emph{Linear Algebra Appl.} {\bf 568} (2019), 106--126.
+\item Khurana, Divya and Roy, Saikat and Sain, Debmalya: Symmetric points in spaces of linear operators between
+{B}anach spaces, \emph{Acta Sci. Math. (Szeged)} {\bf 86} (2020), 617--634.
+\item Kor\'{a}nyi, Adam and Misra, Gadadhar: Homogeneous {H}ermitian holomorphic vector bundles and the
+{C}owen-{D}ouglas class over bounded symmetric domains, \emph{Adv. Math.} {\bf 351} (2019), 1105--1138.
+\item Kor\'{a}nyi, Adam and Misra, Gadadhar: Homogeneous {H}ermitian holomorphic vector bundles and the
+{C}owen-{D}ouglas class over bounded symmetric domains, \emph{C. R. Math. Acad. Sci. Paris} {\bf 354} (2016), 291--295.
+\item Krakovski, Roi and Onn, Uri and Singla, Pooja: Regular characters of groups of type {$\ssf A_n$} over
+discrete valuation rings, \emph{J. Algebra} {\bf 496} (2018), 116--137.
+\item Kreuzer, Martin and Patil, Dilip P.: Computational aspects of {B}urnside rings, part {I}: the ring
+structure, \emph{Beitr. Algebra Geom.} {\bf 58} (2017), 427--452.
+\item Krishna, M. and Krishnapur, Manjunath: Persistence probabilities in centered, stationary, {G}aussian
+processes in discrete time, \emph{Indian J. Pure Appl. Math.} {\bf 47} (2016), 183--194.
+\item Krishnapur, Manjunath and Rider, Brian and Vir\'{a}g, B\'{a}lint: Universality of the stochastic {A}iry operator, \emph{Comm. Pure Appl. Math.} {\bf 69} (2016), 145--199.
+\item Kundu, S. and Aggarwal, Manisha and Hazra, Somnath: Finitely chainable and totally bounded metric spaces:
+equivalent characterizations, \emph{Topology Appl.} {\bf 216} (2017), 59--73.
 \item Lin, X.
@@
 K.: Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level, \emph{Biomolecules} {\bf 9} (2019), 77.
+\item Mahadevan, Rajesh and Nandakumaran, A. K. and Prakash, Ravi: Homogenization of an elliptic equation in a domain with
+oscillating boundary with non-homogeneous non-linear boundary
+conditions, \emph{Appl. Math. Optim.} {\bf 82} (2020), 245--278.
 \item Mahajan, Prachi and Verma, Kaushal: A comparison of two biholomorphic invariants, \emph{Internat. J. Math.} {\bf 30} (2019), 1950012, 16.
@@
 \item Mal, Arpita and Sain, Debmalya and Paul, Kallol: On some geometric properties of operator spaces, \emph{Banach J. Math. Anal.} {\bf 13} (2019), 174--191.
+\item Manchanda, Kaustubh and Bose, Amitabha and Ramaswamy,
+Ramakrishna: Collective dynamics in heterogeneous networks of neuronal
+cellular automata, \emph{Phys. A} {\bf 487} (2017), 111--124.
+\item Mandal, S. and Sahoo, T. and Chakrabarti, A.: Characteristics of eigen-system for flexural gravity wave
+problems, \emph{Geophys. Astrophys. Fluid Dyn.} {\bf 111} (2017), 249--281.
 \item Manfio, F. and Turgay, N. C. and Upadhyay, A.: Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
 {$\Bbb{H}^n\times\Bbb{R}$}, \emph{J. Geom. Anal.} {\bf 29} (2019), 283--298.
+\item Manikandan, K. and Vishnu Priya, N. and Senthilvelan, M. and
+Sankaranarayanan, R.: Deformation of dark solitons in a {$\Cal{PT}$}-invariant
+variable coefficients nonlocal nonlinear {S}chr\"{o}dinger
+equation, \emph{Chaos} {\bf 28} (2018), 083103, 12.
 \item Misra, Gadadhar: Operators in the {C}owen-{D}ouglas class and related topics, \emph{Handbook of analytic operator theory} {\bf } (2019), 87--137.
+\item Misra, Gadadhar and Pal, Avijit: Curvature inequalities for operators in the {C}owen-{D}ouglas
+class and localization of the {W}allach set, \emph{J. Anal. Math.} {\bf 136} (2018), 31--54.
 \item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian: Contractivity and complete contractivity for finite
@@
 \item Misra, Gadadhar and Reza, Md. Ramiz: Curvature inequalities and extremal operators, \emph{Illinois J. Math.} {\bf 63} (2019), 193--217.
+\item Misra, Gadadhar and Upmeier, Harald: Homogeneous vector bundles and intertwining operators for
+symmetric domains, \emph{Adv. Math.} {\bf 303} (2016), 1077--1121.
 \item Mukherjee, Sajal Kumar and Bera, Sudip: Combinatorial proofs of the {N}ewton-{G}irard and
 {C}hapman-{C}ostas-{S}antos identities, \emph{Discrete Math.} {\bf 342} (2019), 1577--1580.
+\item Nandakumaran, A. K. and Datti, P. S. and George, Raju K.: Ordinary differential equations, \emph{} {\bf } (2017), xviii+328.
+\item Nandakumaran, A. K. and Sili, Ali: Homogenization of a hyperbolic equation with highly
+contrasting diffusivity coefficients, \emph{Differential Integral Equations} {\bf 29} (2016), 37--54.
+\item Nandakumaran, Akambadath and Prakash, Ravi and Sardar, Bidhan
+Chandra: Asymptotic analysis of {N}eumann periodic optimal boundary
+control problem, \emph{Math. Methods Appl. Sci.} {\bf 39} (2016), 4354--4374.
+\item Narayanan, E. K. and Singla, Pooja: On monomial representations of finitely generated nilpotent
+groups, \emph{Comm. Algebra} {\bf 46} (2018), 2319--2331.
 \item Nikolov, Nikolai and Verma, Kaushal: On the squeezing function and {F}ridman invariants, \emph{J. Geom. Anal.} {\bf 30} (2020), 1218--1225.
@@
 state space, \emph{Stochastics} {\bf 91} (2019), 155--174.
+\item Pal, Ratna and Verma, Kaushal: Ergodic properties of families of {H}\'{e}non maps, \emph{Ann. Polon. Math.} {\bf 121} (2018), 45--71.
+\item Pal, Ritwik: On the signs of {F}ourier coefficients of {H}ilbert cusp
+forms, \emph{Ramanujan J.} {\bf 53} (2020), 467--481.
+\item Panda, Srikumar and Martha, S. C. and Chakrabarti, A.: An alternative approach to study nonlinear inviscid flow over
+arbitrary bottom topography, \emph{Appl. Math. Comput.} {\bf 273} (2016), 165--177.
+\item Patil, D. P.: Affine one dimensional domains which are not {E}uclidean
+domains, \emph{Int. Rev. Pure Appl. Math.} {\bf 12} (2016), 45--50.
 \item Paul, Kallol and Sain, Debmalya: Birkhoff-{J}ames orthogonality and its application in the
@@
 operators, \emph{Ulam type stability} {\bf } (2019), 331--344.
+\item Paul, Kallol and Sain, Debmalya and Mal, Arpita: Approximate {B}irkhoff-{J}ames orthogonality in the space of
+bounded linear operators, \emph{Linear Algebra Appl.} {\bf 537} (2018), 348--357.
+\item Paul, Kallol and Sain, Debmalya and Mal, Arpita and Mandal,
+Kalidas: Orthogonality of bounded linear operators on complex {B}anach
+spaces, \emph{Adv. Oper. Theory} {\bf 3} (2018), 699--709.
+\item Pingali, Vamsi P.: {$C^{2,\alpha}$} estimates and existence results for a
+nonconcave {PDE}, \emph{Electron. J. Differential Equations} {\bf } (2016), Paper No. 168, 10.
 \item Pingali, Vamsi P.: A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE}, \emph{Complex Var. Elliptic Equ.} {\bf 64} (2019), 503--518.
 \item Pingali, Vamsi Pritham: A vector bundle version of the {M}onge-{A}mp\`ere equation, \emph{Adv. Math.} {\bf 360} (2020), 106921, 40.
+\item Pingali, Vamsi Pritham: A note on higher extremal metrics, \emph{Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010.
 \item Pingali, Vamsi Pritham: Quillen metrics and perturbed equations, \emph{Lett. Math. Phys.} {\bf 110} (2020), 1861--1875.
+\item Pingali, Vamsi Pritham: Representability of {C}hern-{W}eil forms, \emph{Math. Z.} {\bf 288} (2018), 629--641.
 \item Poria, Anirudha: Positive weight function and classification of {$g$}-frames, \emph{Numer. Funct. Anal. Optim.} {\bf 41} (2020), 950--968.
+\item Pradhan, Puspendu and Sahu, Bikramaditya: A characterization of the family of secant lines to a
+hyperbolic quadric in {${\rm PG} (3,q)$}, {$q$} odd, \emph{Discrete Math.} {\bf 343} (2020), 112044, 8.
+\item Prasad, Phoolan: Ray equations of a weak shock in a hyperbolic system of
+conservation laws in multi-dimensions, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 126} (2016), 199--206.
+\item Prasad, Phoolan: Propagation of multidimensional nonlinear waves and
+kinematical conservation laws, \emph{} {\bf } (2017), xi+159.
+\item Prasad, Phoolan: Kinematical conservation laws in a space of arbitrary
+dimensions, \emph{Indian J. Pure Appl. Math.} {\bf 47} (2016), 641--653.
+\item Pritham Pingali, Vamsi: Existence of coupled {K}\"{a}hler-{E}instein metrics using the
+continuity method, \emph{Internat. J. Math.} {\bf 29} (2018), 1850041, 8.
 \item Quddus, Safdar: Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
 spheres, \emph{J. Noncommut. Geom.} {\bf 13} (2019), 257--267.
+\item Ram, Samrith: Counting zero kernel pairs over a finite field, \emph{Linear Algebra Appl.} {\bf 495} (2016), 1--10.
+\item Ray, Anubhab and Roy, Saikat and Bagchi, Satya and Sain,
+Debmalya: Extreme contractions on finite-dimensional polygonal {B}anach
+spaces. {II}, \emph{J. Operator Theory} {\bf 84} (2020), 127--137.
+\item Ray, Samarpita: Closure operations, continuous valuations on monoids and
+spectral spaces, \emph{J. Algebra Appl.} {\bf 19} (2020), 2050006, 27.
 \item Reddy, Nanda Kishore: Equality of {L}yapunov and stability exponents for products of
 isotropic random matrices, \emph{Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624.
+\item Reza, Md. Ramiz: Curvature inequalities for operators in the {C}owen-{D}ouglas
+class of a planar domain, \emph{Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279.
+\item Richard, Thomas and Seshadri, Harish: Positive isotropic curvature and self-duality in dimension 4, \emph{Manuscripta Math.} {\bf 149} (2016), 443--457.
+\item Roncal, Luz and Thangavelu, Sundaram: An extension problem and trace {H}ardy inequality for the
+sub-{L}aplacian on {$H$}-type groups, \emph{Int. Math. Res. Not. IMRN} {\bf } (2020), 4238--4294.
+\item Roncal, Luz and Thangavelu, Sundaram: Hardy's inequality for fractional powers of the sublaplacian
+on the {H}eisenberg group, \emph{Adv. Math.} {\bf 302} (2016), 106--158.
 \item Roth, Julien and Upadhyay, Abhitosh: On compact anisotropic {W}eingarten hypersurfaces in
@@
 sectional curvature, \emph{Bull. Aust. Math. Soc.} {\bf 101} (2020), 333--338.
+\item Roy, Dipankar and Pandit, Rahul: One-dimensional {K}ardar-{P}arisi-{Z}hang and
+{K}uramoto-{S}ivashinsky universality class: limit
+distributions, \emph{Phys. Rev. E} {\bf 101} (2020), 030103(R), 6.
 \item Roy, Krishanu and Venkatesh, R.: Maximal closed subroot systems of real affine root systems, \emph{Transform. Groups} {\bf 24} (2019), 1261--1308.
@@
 bounded linear operator, \emph{Ann. Funct. Anal.} {\bf 10} (2019), 135--143.
+\item Sain, Debmalya: On a generalization of a complementary triangle inequality in
+{H}ilbert spaces and {B}anach spaces, \emph{Indian J. Pure Appl. Math.} {\bf 51} (2020), 1815--1827.
+\item Sain, Debmalya: On the norm attainment set of a bounded linear operator, \emph{J. Math. Anal. Appl.} {\bf 457} (2018), 67--76.
 \item Sain, Debmalya: On the norm attainment set of a bounded linear operator and
@@
 Santanu: On the numerical index of polyhedral {B}anach spaces, \emph{Linear Algebra Appl.} {\bf 577} (2019), 121--133.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: A complete characterization of {B}irkhoff-{J}ames
+orthogonality in infinite dimensional normed space, \emph{J. Operator Theory} {\bf 80} (2018), 399--413.
 \item Sain, Debmalya and Paul, Kallol and Mal, Arpita: On approximate {B}irkhoff-{J}ames orthogonality and normal
 cones in a normed space, \emph{J. Convex Anal.} {\bf 26} (2019), 341--351.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita and Ray,
+Anubhab: A complete characterization of smoothness in the space of
+bounded linear operators, \emph{Linear Multilinear Algebra} {\bf 68} (2020), 2484--2494.
 \item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas: On two extremum problems related to the norm of a bounded
@@
 spaces, \emph{J. Convex Anal.} {\bf 26} (2019), 877--885.
+\item Sain, Debmalya and Tanaka, Ryotaro: Modular {B}irkhoff-{J}ames orthogonality in {$B(\Bbb{X,Y})$}
+and {$K(\Bbb{X,Y})$}, \emph{Banach J. Math. Anal.} {\bf 14} (2020), 1347--1362.
+\item Sanki, Bidyut: Filling of closed surfaces, \emph{J. Topol. Anal.} {\bf 10} (2018), 897--913.
 \item Sanki, Bidyut and Gadgil, Siddhartha: Graphs of systoles on hyperbolic surfaces, \emph{J. Topol. Anal.} {\bf 11} (2019), 1--20.
+\item Sarkar, Amar Deep and Verma, Kaushal: A submultiplicative property of the {C}arath\'{e}odory metric on
+planar domains, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 130} (2020), Paper No. 35, 6.
 \item Sarkar, Amar Deep and Verma, Kaushal: Boundary behaviour of some conformal invariants on planar
 domains, \emph{Comput. Methods Funct. Theory} {\bf 20} (2020), 145--158.
+\item Sen, Suparna: Segal-{B}argmann transform and {P}aley-{W}iener theorems on
+{H}eisenberg motion groups, \emph{Adv. Pure Appl. Math.} {\bf 7} (2016), 13--28.
+\item Senthil Raani, K. S.: {$L^p$}-{F}ourier asymptotics, {H}ardy-type inequality and
+fractal measures, \emph{Monatsh. Math.} {\bf 184} (2017), 459--487.
 \item Seshadri, Harish: Differential geometry in {I}ndia, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799.
+\item Seshadri, Harish and Verma, Kaushal: Some aspects of the automorphism groups of domains, \emph{Handbook of group actions. {V}ol. {III}} {\bf 40} (2018), 145--174.
+\item Tanaka, Ryotaro and Sain, Debmalya: On symmetry of strong {B}irkhoff orthogonality in {$B(\Cal
+H,\Cal K)$} and {$K(\Cal H,\Cal K)$}, \emph{Ann. Funct. Anal.} {\bf 11} (2020), 693--704.
+\item Thangavelu, Sundaram: An analogue of {P}fannschmidt's theorem for the {H}eisenberg
+group, \emph{J. Anal.} {\bf 26} (2018), 235--244.
+\item Thangavelu, Sundaram and Naidu Dogga, Venku: {$L^p$}-{$L^2$} estimates for solutions of the wave equation
+associated to the {G}rushin operator, \emph{Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92.
 \item Turgay, Nurettin Cenk and Upadhyay, Abhitosh: On biconservative hypersurfaces in 4-dimensional {R}iemannian
@@
 \item Verma, Kaushal: Notes on the boundaries of quadrature domains, \emph{Anal. Math. Phys.} {\bf 9} (2019), 617--638.
+\item Verma, Kaushal: Remembering {R}. {R}. {S}imha, \emph{Math. Newsl.} {\bf 27} (2017), 16--20.
 \item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan,
@@
 equation, \emph{Phys. Lett. A} {\bf 383} (2019), 15--26.
+\item Yadav, Avinash Chand and Manchanda, Kaustubh and Ramaswamy,
+Ramakrishna: Emergent organization in a model market, \emph{Phys. A} {\bf 482} (2017), 118--126.
 \end{enumerate}
@@
 nonlocal boundary jumps}, \emph{J. Phys. A} {\bf 52} (2019), 355001, 19.
+\item Adhikari, Kartick and Kishore Reddy, Nanda and Ram Reddy,
+Tulasi and Saha, Koushik: \href{https://doi.org/10.1214/14-AIHP632}{Determinantal point processes in the plane from products of
+random matrices}, \emph{Ann. Inst. Henri Poincar\'{e} Probab. Stat.} {\bf 52} (2016), 16--46.
+\item Adhikari, Kartick and Reddy, Nanda Kishore: \href{https://doi.org/10.1093/imrn/rnw207}{Hole probabilities for finite and infinite {G}inibre
+ensembles}, \emph{Int. Math. Res. Not. IMRN} {\bf } (2017), 6694--6730.
+\item Adimurthi and Ratnakumar, P.
+K.
+and Sohani, Vijay Kumar: \href{https://doi.org/10.1017/S0308210516000081}{A {H}ardy-{S}obolev inequality for the twisted {L}aplacian}, \emph{Proc.
+Roy.
+Soc.
+Edinburgh Sect.
+A} {\bf 147} (2017), 1--23.
 \item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
 Nandakumaran, A. K.: \href{https://doi.org/10.3233/asy-191526}{Control problem on a rough circular domain and homogenization}, \emph{Asymptot. Anal.} {\bf 115} (2019), 19--46.
+\item Aiyappan, S. and Nandakumaran, A. K.: \href{https://doi.org/10.1002/mma.4231}{Optimal control problem in a domain with branched structure
+and homogenization}, \emph{Math. Methods Appl. Sci.} {\bf 40} (2017), 3173--3189.
 \item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1142/S0219199719500299}{Semi-linear optimal control problem on a smooth oscillating
@@
 rough domains}, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954.
+\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1007/s00526-018-1354-6}{Generalization of unfolding operator for highly oscillating
+smooth boundary domains and homogenization}, \emph{Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30.
 \item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu: \href{https://doi.org/10.1002/mma.5748}{Asymptotic analysis of a boundary optimal control problem on a
@@
 subset of all {F}ourier coefficients}, \emph{Publ. Mat.} {\bf 63} (2019), 307--341.
+\item Anamby, Pramath and Das, Soumya: \href{https://doi.org/10.1016/j.jnt.2018.03.011}{Bounds for the {P}etersson norms of the pullbacks of
+{S}aito-{K}urokawa lifts}, \emph{J. Number Theory} {\bf 191} (2018), 289--304.
 \item Anand, Jatin and Bhattacharyya, Tirthankar and Srivastava,
@@
 {H}ardy space}, \emph{Arch. Math. (Basel)} {\bf 114} (2020), 431--444.
+\item Arunkumar, G. and Kus, Deniz and Venkatesh, R.: \href{https://doi.org/10.1016/j.jalgebra.2017.11.050}{Root multiplicities for {B}orcherds algebras and graph
+coloring}, \emph{J. Algebra} {\bf 499} (2018), 538--569.
+\item Ayyer, Arvind: \href{https://doi.org/10.1088/1751-8113/49/15/155003}{Full current statistics for a disordered open exclusion
+process}, \emph{J. Phys. A} {\bf 49} (2016), 155003, 10.
 \item Ayyer, Arvind: \href{https://doi.org/10.1007/s00026-019-00480-5}{Squareness for the {M}onopole-{D}imer model}, \emph{Ann. Comb.} {\bf 24} (2020), 237--255.
@@
 sign matrices of odd order}, \emph{Adv. Math.} {\bf 367} (2020), 107125, 56.
+\item Ayyer, Arvind and Bouttier, J\'{e}r\'{e}mie and Corteel, Sylvie and
+Linusson, Svante and Nunzi, Fran\c{c}ois: \href{https://doi.org/10.1016/j.aam.2018.03.001}{Bumping sequences and multispecies juggling}, \emph{Adv. in Appl. Math.} {\bf 98} (2018), 100--126.
+\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar: \href{https://doi.org/10.1103/physreve.97.012151}{Matrix product solution of a left-permeable two-species
+asymmetric exclusion process}, \emph{Phys. Rev. E} {\bf 97} (2018), 012151, 10.
 \item Ayyer, Arvind and Finn, Caley and Roy, Dipankar: \href{https://doi.org/10.1007/s10955-018-2183-x}{The phase diagram for a multispecies left-permeable asymmetric
@@
 A} {\bf 174} (2020), 105241, 40.
+\item Ayyer, Arvind and Josuat-Verg\`es, Matthieu and Ramassamy,
+Sanjay: \href{https://doi.org/10.5802/ahl.33}{Extensions of partial cyclic orders and consecutive coordinate
+polytopes}, \emph{Ann. H. Lebesgue} {\bf 3} (2020), 275--297.
+\item Ayyer, Arvind and Linusson, Svante: \href{https://doi.org/10.1090/tran/6806}{Correlations in the multispecies {TASEP} and a conjecture by
+{L}am}, \emph{Trans. Amer. Math. Soc.} {\bf 369} (2017), 1097--1125.
 \item Ayyer, Arvind and Linusson, Svante: \href{https://doi.org/10.1002/rsa.20825}{Reverse juggling processes}, \emph{Random Structures Algorithms} {\bf 55} (2019), 56--72.
+\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven: Odd partitions in {Y}oung's lattice, \emph{S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
+\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven: \href{https://doi.org/10.1016/j.jcta.2017.03.004}{Representations of symmetric groups with non-trivial
+determinant}, \emph{J. Combin. Theory Ser. A} {\bf 150} (2017), 208--232.
+\item Ayyer, Arvind and Ramassamy, Sanjay: \href{https://doi.org/10.30757/alea.v15-28}{The {H}ilbert-{G}alton board}, \emph{ALEA Lat. Am. J. Probab. Math. Stat.} {\bf 15} (2018), 755--774.
+\item Ayyer, Arvind and Schilling, Anne and Thi\'{e}ry, Nicolas M.: \href{https://doi.org/10.1080/10586458.2015.1107868}{Spectral gap for random-to-random shuffling on linear
+extensions}, \emph{Exp. Math.} {\bf 26} (2017), 22--30.
 \item Ayyer, Arvind and Singla, Pooja: \href{https://doi.org/10.1007/s10468-019-09864-w}{Random motion on finite rings, {I}: commutative rings}, \emph{Algebr.
@@
 Theory} {\bf 23} (2020), 583--604.
+\item Ayyer, Arvind and Sinha, Shubham: Random {$t$}-cores and hook lengths in random partitions, \emph{S\'{e}m. Lothar. Combin.} {\bf 84B} (2020), Art. 58, 11.
+\item Ayyer, Arvind and Steinberg, Benjamin: \href{https://doi.org/10.5802/alco.94}{Random walks on rings and modules}, \emph{Algebr. Comb.} {\bf 3} (2020), 309--329.
+\item B\"{o}cherer, Siegfried and Das, Soumya: \href{https://doi.org/10.1007/s00209-015-1609-2}{Cuspidality and the growth of {F}ourier coefficients: small
+weights}, \emph{Math. Z.} {\bf 283} (2016), 539--553.
+\item B\"{o}cherer, Siegfried and Das, Soumya: \href{https://doi.org/10.1515/crelle-2015-0075}{Cuspidality and the growth of {F}ourier coefficients of
+modular forms}, \emph{J. Reine Angew. Math.} {\bf 741} (2018), 161--178.
+\item B\"{o}cherer, Siegfried and Das, Soumya: \href{https://doi.org/10.1016/j.aim.2018.07.033}{Petersson norms of not necessarily cuspidal {J}acobi modular
+forms and applications}, \emph{Adv. Math.} {\bf 336} (2018), 335--376.
+\item Bagchi, Bhaskar and Burton, Benjamin A. and Datta, Basudeb and
+Singh, Nitin and Spreer, Jonathan: Efficient algorithms to decide tightness, \emph{32nd {I}nternational {S}ymposium on {C}omputational
+{G}eometry} {\bf 51} (2016), Art. 12, 15.
+\item Bagchi, Bhaskar and Datta, Basudeb and Spreer, Jonathan: \href{https://doi.org/10.1016/j.ejc.2016.10.005}{A characterization of tightly triangulated 3-manifolds}, \emph{European J.
+Combin.} {\bf 61} (2017), 133--137.
+\item Bagchi, Bhaskar and Datta, Basudeb and Spreer, Jonathan: \href{https://doi.org/10.1016/j.ejc.2015.12.006}{Tight triangulations of closed 3-manifolds}, \emph{European J.
+Combin.} {\bf 54} (2016), 103--120.
+\item Bagchi, Sayan and Thangavelu, Sundaram: \href{https://doi.org/10.1007/s11854-018-0053-8}{Weighted norm inequalities for {W}eyl multipliers and fourier
+multipliers on the {H}eisenberg group}, \emph{J. Anal. Math.} {\bf 136} (2018), 1--29.
+\item Baklouti, Ali and Thangavelu, Sundaram: \href{https://doi.org/10.1017/nmj.2016.58}{Hardy and {M}iyachi theorems for {H}eisenberg motion groups}, \emph{Nagoya Math. J.} {\bf 229} (2018), 1--20.
+\item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
+Verma, Kaushal: \href{https://doi.org/10.4064/ap200203-21-4}{Further remarks on the higher dimensional {S}uita conjecture}, \emph{Ann. Polon. Math.} {\bf 125} (2020), 101--115.
 \item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
@@
 operator}, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25.
+\item Balodi, Mamta and Banerjee, Abhishek and Naolekar, Anita: \href{https://doi.org/10.5802/crmath.157}{B{V}-operators and the secondary {H}ochschild complex}, \emph{C.
+R.
+Math.
+Acad.
+Sci.
+Paris} {\bf 358} (2020), 1239--1258.
+\item Balodi, Mamta and Banerjee, Abhishek and Ray, Samarpita: \href{https://doi.org/10.4153/s0008414x19000403}{Cohomology of modules over {$H$}-categories and
+co-{$H$}-categories}, \emph{Canad. J. Math.} {\bf 72} (2020), 1352--1385.
+\item Balodi, Mamta and Huang, Hua-Lin and Kumar, Shiv Datt: \href{https://doi.org/10.1142/S0129055X17300035}{On the classification of finite quasi-quantum groups}, \emph{Rev.
+Math.
+Phys.} {\bf 29} (2017), 1730003, 20.
+\item Balodi, Mamta and Palcoux, Sebastien: \href{https://doi.org/10.1016/j.jcta.2018.02.004}{On {B}oolean intervals of finite groups}, \emph{J. Combin. Theory Ser. A} {\bf 157} (2018), 49--69.
+\item Banerjee, Abhishek: \href{https://doi.org/10.1007/s00013-017-1025-4}{On some spectral spaces associated to tensor triangulated
+categories}, \emph{Arch. Math. (Basel)} {\bf 108} (2017), 581--591.
+\item Banerjee, Abhishek: \href{https://doi.org/10.1142/S0219199717500717}{On {A}uslander's formula and cohereditary torsion pairs}, \emph{Commun. Contemp. Math.} {\bf 20} (2018), 1750071, 27.
+\item Banerjee, Abhishek: \href{https://doi.org/10.1016/j.geomphys.2018.04.008}{Modular {H}ecke algebras over {M}\"{o}bius categories}, \emph{J. Geom. Phys.} {\bf 131} (2018), 23--40.
+\item Banerjee, Abhishek: Closure operators in abelian categories and spectral spaces, \emph{Theory Appl. Categ.} {\bf 32} (2017), Paper No. 20, 719--735.
+\item Banerjee, Abhishek: \href{https://doi.org/10.1142/S0129167X17500513}{Noetherian schemes over abelian symmetric monoidal categories}, \emph{Internat. J. Math.} {\bf 28} (2017), 1750051, 34.
 \item Banerjee, Abhishek: \href{https://doi.org/10.4153/s0008439518000656}{On differential torsion theories and rings with several
 objects}, \emph{Canad. Math. Bull.} {\bf 62} (2019), 703--714.
+\item Banerjee, Abhishek: \href{http://projecteuclid.org/euclid.bbms/1457560860}{Une note sur les d\'erivations localement nilpotentes dans les
+cat\'egories mono\"\i dales sym\'etriques}, \emph{Bull. Belg. Math. Soc. Simon Stevin} {\bf 23} (2016), 151--160.
+\item Banerjee, Abhishek: \href{http://dx.doi.org/10.1007/s40879-016-0108-2}{Realizations of pairs and {O}ka families in tensor
+triangulated categories}, \emph{Eur. J. Math.} {\bf 2} (2016), 760--797.
+\item Banerjee, Abhishek: \href{http://dx.doi.org/10.7146/math.scand.a-23294}{Homologie de {H}ochschild et espaces alg\'ebriques}, \emph{Math. Scand.} {\bf 118} (2016), 33--42.
+\item Banerjee, Abhishek: \href{https://doi.org/10.1016/j.crma.2018.02.012}{A topological {N}ullstellensatz for tensor-triangulated
+categories}, \emph{C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375.
+\item Banerjee, Abhishek: \href{http://dx.doi.org/10.1016/j.crma.2016.05.005}{Some remarks on a theorem of {B}ergman}, \emph{C. R. Math. Acad. Sci. Paris} {\bf 354} (2016), 665--670.
+\item Banerjee, Abhishek: \href{https://doi.org/10.4064/fm218-8-2016}{Monoidal semifilters and arrays of prime ideals}, \emph{Fund. Math.} {\bf 237} (2017), 281--296.
+\item Banerjee, Abhishek: \href{http://dx.doi.org/10.1016/j.jpaa.2016.02.001}{Schemes over symmetric monoidal categories and torsion
+theories}, \emph{J. Pure Appl. Algebra} {\bf 220} (2016), 3017--3047.
+\item Banerjee, Abhishek: \href{https://doi.org/10.4171/JNCG/297}{Quasimodular {H}ecke algebras and {H}opf actions}, \emph{J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080.
+\item Banerjee, Abhishek: \href{https://doi.org/10.1016/j.jalgebra.2018.04.022}{Completions of monoid objects and descent results}, \emph{J. Algebra} {\bf 507} (2018), 362--399.
 \item Banerjee, Abhishek and Kour, Surjeet: \href{https://doi.org/10.1007/s10231-019-00844-x}{{$(A,\delta)$}-modules, {H}ochschild homology and higher
 derivations}, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802.
+\item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: \href{https://doi.org/10.1142/S0129167X2050086X}{On stable {CMC} free-boundary surfaces in a strictly convex
+domain of a bi-invariant {L}ie group}, \emph{Internat. J. Math.} {\bf 31} (2020), 2050086, 9.
+\item Basak, Biplab: \href{https://doi.org/10.1007/s12044-016-0302-7}{An algorithmic approach to construct crystallizations of
+3-manifolds from presentations of fundamental groups}, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 126} (2016), 629--653.
+\item Basak, Biplab and Casali, Maria Rita: \href{https://doi.org/10.1515/forum-2015-0080}{Lower bounds for regular genus and gem-complexity of {PL}
+4-manifolds}, \emph{Forum Math.} {\bf 29} (2017), 761--773.
+\item Basak, Biplab and Spreer, Jonathan: \href{https://doi.org/10.1515/advgeom-2015-0043}{Simple crystallizations of 4-manifolds}, \emph{Adv. Geom.} {\bf 16} (2016), 111--130.
+\item Basak, Gopal K. and Ghosh, Mrinal K. and Mukherjee, Diganta: \href{https://doi.org/10.1080/07362994.2015.1106321}{A mean-reverting stochastic model for the political business
+cycle}, \emph{Stoch. Anal. Appl.} {\bf 34} (2016), 96--116.
+\item Basu, Arnab and Ghosh, Mrinal K.: \href{https://doi.org/10.1287/moor.2017.0870}{Nonzero-sum risk-sensitive stochastic games on a countable
+state space}, \emph{Math. Oper. Res.} {\bf 43} (2018), 516--532.
 \item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
 and Putinar, Mihai: \href{https://doi.org/10.1016/j.laa.2018.03.035}{Simultaneous kernels of matrix {H}adamard powers}, \emph{Linear Algebra Appl.} {\bf 576} (2019), 142--157.
+\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
+Christopher R. H. and Harris, Pamela E. and Khare, Apoorva and
+Morales, Alejandro H. and Yip, Martha: The volume of the caracol polytope, \emph{S\'{e}m. Lothar. Combin.} {\bf 80B} (2018), Art. 87, 12.
 \item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
@@
 Soc.} {\bf 372} (2019), 3369--3404.
+\item Bennett, Nathan and Iyer, Srikanth K. and Jammalamadaka, S.
+Rao: \href{https://doi.org/10.1080/03610926.2015.1041981}{Analysis of gamma and {W}eibull lifetime data under a general
+censoring scheme and in the presence of covariates}, \emph{Comm. Statist. Theory Methods} {\bf 46} (2017), 2277--2289.
+\item Bera, Sayani and Pal, Ratna: \href{https://doi.org/10.1186/s40627-016-0006-x}{Dynamics of semigroups of entire maps of {$\Bbb{C}^k$}}, \emph{Complex Anal.
+Synerg.} {\bf 2} (2016), Paper No.
+2, 22.
+\item Bera, Sayani and Pal, Ratna and Verma, Kaushal: \href{https://projecteuclid.org/euclid.ijm/1534924839}{Examples of non-autonomous basins of attraction}, \emph{Illinois J.
+Math.} {\bf 61} (2017), 531--567.
 \item Bera, Sayani and Pal, Ratna and Verma, Kaushal: \href{https://doi.org/10.1007/s40879-019-00326-7}{A rigidity theorem for {H}\'{e}non maps}, \emph{Eur. J. Math.} {\bf 6} (2020), 508--532.
+\item Bera, Sayani and Verma, Kaushal: \href{https://doi.org/10.1007/s12044-018-0388-1}{Some aspects of shift-like automorphisms of {$\Bbb C^k$}}, \emph{Proc.
+Indian Acad.
+Sci.
+Math.
+Sci.} {\bf 128} (2018), Art.
+10, 48.
+\item Bera, Sudip and Mukherjee, Sajal Kumar: \href{https://doi.org/10.1007/s00373-020-02223-3}{Generalized power sum and {N}ewton-{G}irard identities}, \emph{Graphs Combin.} {\bf 36} (2020), 1957--1964.
+\item Bhamidi, Shankar and Dhara, Souvik and van der Hofstad, Remco
+and Sen, Sanchayan: \href{https://doi.org/10.1214/19-ejp408}{Universality for critical heavy-tailed network models: metric
+structure of maximal components}, \emph{Electron. J. Probab.} {\bf 25} (2020), Paper No. 47, 57.
+\item Bhamidi, Shankar and Sen, Sanchayan: \href{https://doi.org/10.1002/rsa.20880}{Geometry of the vacant set left by random walk on random
+graphs, {W}right's constants, and critical random graphs with
+prescribed degrees}, \emph{Random Structures Algorithms} {\bf 56} (2020), 676--721.
+\item Bharali, Gautam: \href{https://doi.org/10.5186/aasfm.2016.4116}{Complex geodesics, their boundary regularity, and a
+{H}ardy-{L}ittlewood-type lemma}, \emph{Ann. Acad. Sci. Fenn. Math.} {\bf 41} (2016), 253--263.
 \item Bharali, Gautam: \href{https://doi.org/10.1007/s12220-019-00342-9}{On the growth of the {B}ergman metric near a point of infinite
 type}, \emph{J. Geom. Anal.} {\bf 30} (2020), 1238--1258.
+\item Bharali, Gautam and Biswas, Indranil and Divakaran, Divakaran
+and Janardhanan, Jaikrishnan: Proper holomorphic mappings onto symmetric products of a
+{R}iemann surface, \emph{Doc. Math.} {\bf 23} (2018), 1291--1311.
+\item Bharali, Gautam and Biswas, Indranil and Schumacher, Georg: \href{https://doi.org/10.1080/17476933.2016.1252342}{A criterion for a degree-one holomorphic map to be a
+biholomorphism}, \emph{Complex Var. Elliptic Equ.} {\bf 62} (2017), 914--918.
 \item Bharali, Gautam and Chandel, Vikramjeet Singh: \href{https://doi.org/10.1007/s11785-017-0701-5}{Pick interpolation on the polydisc: small families of
 sufficient kernels}, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093.
+\item Bharali, Gautam and Sridharan, Shrihari: \href{https://doi.org/10.1142/S0129167X17501087}{Holomorphic correspondences related to finitely generated
+rational semigroups}, \emph{Internat. J. Math.} {\bf 28} (2017), 1750108, 25.
+\item Bharali, Gautam and Sridharan, Shrihari: \href{https://doi.org/10.1080/17476933.2016.1185419}{The dynamics of holomorphic correspondences of {$\Bbb P^1$}:
+invariant measures and the normality set}, \emph{Complex Var. Elliptic Equ.} {\bf 61} (2016), 1587--1613.
+\item Bharali, Gautam and Zimmer, Andrew: \href{https://doi.org/10.1016/j.aim.2017.02.005}{Goldilocks domains, a weak notion of visibility, and
+applications}, \emph{Adv. Math.} {\bf 310} (2017), 377--425.
+\item Bhatia, Manan: \href{https://doi.org/10.1007/s10955-020-02632-x}{Moderate deviation and exit time estimates for stationary last
+passage percolation}, \emph{J. Stat. Phys.} {\bf 181} (2020), 1410--1432.
+\item Bhattacharjee, M. and Eschmeier, J. and Keshari, Dinesh K. and
+Sarkar, Jaydeb: \href{https://doi.org/10.1016/j.laa.2017.02.032}{Dilations, wandering subspaces, and inner functions}, \emph{Linear Algebra Appl.} {\bf 523} (2017), 263--280.
+\item Bhattacharjee, Monojit and Sarkar, Jaydeb: Operator positivity and analytic models of commuting tuples of
+operators, \emph{Studia Math.} {\bf 232} (2016), 155--171.
+\item Bhattacharyya, T.
+and Narayanan, E.
+K.
+and Sarkar, Jaydeb: \href{https://doi.org/10.7153/oam-11-07}{Analytic model of doubly commuting contractions}, \emph{Oper.
+Matrices} {\bf 11} (2017), 101--113.
+\item Bhattacharyya, T. and Sau, H.: \href{https://doi.org/10.1007/s11785-015-0472-9}{Explicit and unique construction of tetrablock unitary
+dilation in a certain case}, \emph{Complex Anal. Oper. Theory} {\bf 10} (2016), 749--768.
+\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel,
+Vikramjeet Singh: \href{https://doi.org/10.4064/sm190505-8-10}{On the {N}evanlinna problem: characterization of all
+{S}chur-{A}gler class solutions affiliated with a given
+kernel}, \emph{Studia Math.} {\bf 255} (2020), 83--107.
 \item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K.: \href{https://doi.org/10.1007/s13226-019-0345-4}{Survey of last ten years of work done in {I}ndia in some
 selected areas of functional analysis and operator theory}, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617.
+\item Bhattacharyya, Tirthankar and Sau, Haripada: \href{https://doi.org/10.4171/PRIMS/53-2-2}{{$\Gamma$}-unitaries, dilation and a natural example}, \emph{Publ.
+Res.
+Inst.
+Math.
+Sci.} {\bf 53} (2017), 261--285.
+\item Bhattacharyya, Tirthankar and Sau, Haripada: \href{https://doi.org/10.1016/j.jfa.2017.09.013}{Holomorphic functions on the symmetrized bidisk---realization,
+interpolation and extension}, \emph{J. Funct. Anal.} {\bf 274} (2018), 504--524.
 \item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
@@
 developing countries} {\bf 275} (2019), 42--64.
+\item Bhosle, Usha N.: \href{https://doi.org/10.1142/S0129167X18500155}{Hitchin pairs on reducible curves}, \emph{Internat. J. Math.} {\bf 29} (2018), 1850015, 49.
+\item Bhosle, Usha N.: On a conjecture of {B}utler, \emph{Analytic and algebraic geometry} {\bf } (2017), 29--48.
+\item Bhosle, Usha N. and Biswas, Indranil: \href{https://doi.org/10.1007/s10711-015-0108-2}{Moduli spaces of vector bundles on a singular rational ruled
+surface}, \emph{Geom. Dedicata} {\bf 180} (2016), 399--413.
+\item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and
+Pingali, Vamsi P.: Rational cuspidal curves on del-{P}ezzo surfaces, \emph{J. Singul.} {\bf 17} (2018), 91--107.
 \item Biswas, Indranil and Dumitrescu, Sorin and Gupta, Subhojoy: Branched projective structures on a {R}iemann surface and
 logarithmic connections, \emph{Doc. Math.} {\bf 24} (2019), 2299--2337.
+\item Biswas, Indranil and Pingali, Vamsi Pritham: A characterization of finite vector bundles on {G}auduchon
+astheno-{K}\"{a}hler manifolds, \emph{\'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art. 6, 13.
+\item Biswas, Indranil and Pingali, Vamsi Pritham: \href{https://doi.org/10.1093/imrn/rny259}{Metric properties of parabolic ample bundles}, \emph{Int. Math. Res. Not. IMRN} {\bf } (2020), 9336--9369.
+\item Biswas, Indranil and Seshadri, Harish: \href{https://doi.org/10.4310/PAMQ.2016.v12.n4.a1}{Chern scalar curvature and symmetric products of compact
+{R}iemann surfaces}, \emph{Pure Appl. Math. Q.} {\bf 12} (2016), 463--471.
+\item Biswas, Indranil and Seshadri, Harish: \href{https://doi.org/10.1016/j.crma.2017.03.012}{Quot schemes and {R}icci semipositivity}, \emph{C. R. Math. Acad. Sci. Paris} {\bf 355} (2017), 577--581.
 \item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi: \href{https://doi.org/10.1515/cmam-2018-0020}{Edge patch-wise local projection stabilized nonconforming
@@
 {${S}_n$}-invariant kernels}, \emph{J. Funct. Anal.} {\bf 276} (2019), 751--784.
+\item Bleher, F. M. and Chinburg, T. and Greenberg, R. and Kakde, M.
+and Pappas, G. and Sharifi, R. and Taylor, M. J.: \href{https://doi.org/10.1353/ajm.2020.0017}{Higher {C}hern classes in {I}wasawa theory}, \emph{Amer. J. Math.} {\bf 142} (2020), 627--682.
+\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram: \href{https://doi.org/10.1090/tran/6861}{Mixed norm estimates for the {C}es\`aro means associated with
+{D}unkl-{H}ermite expansions}, \emph{Trans. Amer. Math. Soc.} {\bf 369} (2017), 7021--7047.
 \item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram: \href{https://doi.org/10.3934/cpaa.2019116}{On extension problem, trace {H}ardy and {H}ardy's inequalities
 for some fractional {L}aplacians}, \emph{Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605.
+\item Boggarapu, Pradeep and Thangavelu, S.: \href{https://doi.org/10.1007/s11856-017-1438-6}{On the chaotic behavior of the {D}unkl heat semigroup on
+weighted {$L^p$} spaces}, \emph{Israel J. Math.} {\bf 217} (2017), 57--92.
+\item Boggarapu, Pradeep and Thangavelu, S.: \href{http://projecteuclid.org/euclid.pm/1450818486}{Mixed norm estimates for the {R}iesz transforms on {$SU(2)$}}, \emph{Publ.
+Mat.} {\bf 60} (2016), 171--190.
+\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal: \href{https://doi.org/10.1007/s13324-017-0177-5}{Comments on the {G}reen's function of a planar domain}, \emph{Anal.
+Math.
+Phys.} {\bf 8} (2018), 383--414.
+\item Brenner, Susanne C. and Gudi, Thirupathi and Porwal, Kamana
+and Sung, Li-Yeng: \href{https://doi.org/10.1051/cocv/2017031}{A {M}orley finite element method for an elliptic distributed
+optimal control problem with pointwise state and control
+constraints}, \emph{ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206.
+\item Burton, Benjamin A. and Datta, Basudeb and Singh, Nitin and
+Spreer, Jonathan: \href{https://doi.org/10.1080/10586458.2016.1212747}{A construction principle for tight and minimal triangulations
+of manifolds}, \emph{Exp. Math.} {\bf 27} (2018), 22--36.
 \item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella: \href{https://doi.org/10.1515/cmam-2019-0034}{Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
 indefinite second-order linear elliptic problems}, \emph{Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.
+\item Chakrabarti, A. and Mondal, Sumita Rani: On approximate numerical method of solution of {F}redholm
+integral equations, \emph{Int. J. Appl. Math. Anal. Appl.} {\bf 11} (2016), 153--162.
 \item Chakraborty, Atlanta and Chandru, Vijay and Rao, M.
@@
 Res.} {\bf 287} (2020), 593--616.
+\item Chan, Chun Lam and Fernandes, Winston and Kashyap, Navin and
+Krishnapur, Manjunath: \href{https://doi.org/10.1137/15M1028819}{Phase transitions for the uniform distribution in the pattern
+maximum likelihood problem and its {B}ethe approximation}, \emph{SIAM J. Discrete Math.} {\bf 31} (2017), 597--631.
+\item Chandel, Vikramjeet Singh: \href{https://doi.org/10.1080/17476933.2017.1370461}{The three-point {P}ick-{N}evanlinna interpolation problem on
+the polydisc}, \emph{Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352.
 \item Chandel, Vikramjeet Singh: \href{https://doi.org/10.1007/s12220-018-00123-w}{The 3-point spectral pick interpolation problem and an
 application to holomorphic correspondences}, \emph{J. Geom. Anal.} {\bf 30} (2020), 551--572.
+\item Chas, Moira and Gadgil, Siddhartha: \href{https://doi.org/10.2140/agt.2016.16.2813}{The extended {G}oldman bracket determines intersection numbers
+for surfaces and orbifolds}, \emph{Algebr. Geom. Topol.} {\bf 16} (2016), 2813--2838.
+\item Chatterjee, Esha and Hassan, Sk. Sarif: \href{https://doi.org/10.3934/dcds.2018070}{On the asymptotic character of a generalized rational
+difference equation}, \emph{Discrete Contin. Dyn. Syst.} {\bf 38} (2018), 1707--1718.
+\item Chattopadhyay, Arup and Sain, Debmalya and Senapati, Tanusri: \href{https://doi.org/10.14232/actasm-019-554-z}{A study of non-positive operators between real normed linear
+spaces}, \emph{Acta Sci. Math. (Szeged)} {\bf 86} (2020), 449--466.
+\item Choudhary, A. and Martha, S. C. and Chakrabarti, A.: \href{https://doi.org/10.1007/s40010-019-00600-z}{Modified method for the solution of dual trigonometric series
+relations}, \emph{Proc. Nat. Acad. Sci. India Sect. A} {\bf 90} (2020), 437--445.
+\item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
+K. C.: \href{https://doi.org/10.13001/1081-3810.3864}{A note on linear preservers of semipositive and minimally
+semipositive matrices}, \emph{Electron. J. Linear Algebra} {\bf 34} (2018), 687--694.
 \item Choudhury, Projesh Nath and Tsatsomeros, Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic detection and construction of {N}-matrices}, \emph{Linear Algebra Appl.} {\bf 602} (2020), 46--56.
+\item Chowdhury, Sudipto and Gudi, Thirupathi: \href{https://doi.org/10.1016/j.cam.2016.12.005}{A {$C^0$} interior penalty method for the {D}irichlet control
+problem governed by biharmonic operator}, \emph{J. Comput. Appl. Math.} {\bf 317} (2017), 290--306.
+\item Chowdhury, Sudipto and Gudi, Thirupathi and Nandakumaran, A.
+K.: \href{https://doi.org/10.1090/mcom/3125}{Error bounds for a {D}irichlet boundary control problem based
+on energy spaces}, \emph{Math. Comp.} {\bf 86} (2017), 1103--1126.
+\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram: \href{https://doi.org/10.1017/s0013091517000311}{Hardy-type inequalities for fractional powers of the
+{D}unkl-{H}ermite operator}, \emph{Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544.
 \item Cicuttin, Matteo and Ern, Alexandre and Gudi, Thirupathi: \href{https://doi.org/10.1007/s10915-020-01195-z}{Hybrid high-order methods for the elliptic obstacle problem}, \emph{J.
@@
 8, 18.
+\item Cui, Jintao and Gudi, Thirupathi: \href{https://doi.org/10.1007/s10444-016-9495-7}{Finite element approximation of a free boundary plasma
+problem}, \emph{Adv. Comput. Math.} {\bf 43} (2017), 517--535.
+\item Das, Soumya: \href{https://doi.org/10.1007/s13226-015-0165-0}{Cuspidality and the growth of {F}ourier coefficients of
+modular forms: a survey}, \emph{Indian J. Pure Appl. Math.} {\bf 47} (2016), 9--22.
+\item Das, Soumya and Ganguly, Satadal: \href{https://doi.org/10.1090/proc/12887}{A note on small gaps between nonzero {F}ourier coefficients of
+cusp forms}, \emph{Proc. Amer. Math. Soc.} {\bf 144} (2016), 2301--2305.
 \item Das, Soumya and Jha, Abhash Kumar: \href{https://doi.org/10.1007/s12188-019-00206-7}{Analytic properties of twisted real-analytic {H}ermitian
 {K}lingen type {E}isenstein series and applications}, \emph{Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116.
+\item Das, Soumya and Khan, Rizwanur: \href{https://doi.org/10.1093/qmath/hay012}{The third moment of symmetric square {$L$}-functions}, \emph{Q. J. Math.} {\bf 69} (2018), 1063--1087.
+\item Das, Soumya and Kohnen, Winfried: \href{https://doi.org/10.4064/aa170419-4-11}{On sign changes of eigenvalues of {S}iegel cusp forms of genus
+2 in prime powers}, \emph{Acta Arith.} {\bf 183} (2018), 167--172.
 \item Das, Soumya and Pal, Ritwik: \href{https://doi.org/10.1007/s40993-019-0158-x}{The first negative eigenvalue of {Y}oshida lifts}, \emph{Res. Number Theory} {\bf 5} (2019), Paper No. 20, 9.
+\item Das, Soumya and Pal, Ritwik: \href{https://doi.org/10.1016/j.jnt.2017.03.021}{Jacobi forms and differential operators: odd weights}, \emph{J. Number Theory} {\bf 179} (2017), 113--125.
+\item Datar, Ved V.
+and Pingali, Vamsi Pritham: \href{https://doi.org/10.4310/JSG.2020.v18.n4.a1}{On coupled constant scalar curvature {K}\"{a}hler metrics}, \emph{J.
+Symplectic Geom.} {\bf 18} (2020), 961--994.
+\item Datta, Basudeb and Maity, Dipendu: \href{https://doi.org/10.1007/s13366-019-00458-7}{Correction to: {S}emi-equivelar and vertex-transitive maps on
+the torus}, \emph{Beitr. Algebra Geom.} {\bf 61} (2020), 187--188.
+\item Datta, Basudeb and Maity, Dipendu: \href{https://doi.org/10.1007/s13366-017-0332-z}{Semi-equivelar and vertex-transitive maps on the torus}, \emph{Beitr.
+Algebra Geom.} {\bf 58} (2017), 617--634.
+\item Datta, Basudeb and Maity, Dipendu: \href{https://doi.org/10.1016/j.disc.2018.08.016}{Semi-equivelar maps on the torus and the {K}lein bottle are
+{A}rchimedean}, \emph{Discrete Math.} {\bf 341} (2018), 3296--3309.
+\item Datta, Basudeb and Murai, Satoshi: On stacked triangulated manifolds, \emph{Electron. J. Combin.} {\bf 24} (2017), Paper 4.12, 14.
+\item Datta, Basudeb and Sarkar, Soumen: \href{https://doi.org/10.1007/jhep01(2020)036}{On equilibrium triangulations of quasitoric manifolds}, \emph{Southeast Asian Bull.
+Math.} {\bf 44} (2020), 57-56.
+\item Dhanya, R. and Prashanth, S. and Tiwari, Sweta and Sreenadh,
+K.: \href{https://doi.org/10.1080/17476933.2016.1198787}{Elliptic problems in {${\Bbb R}^N$} with critical and singular
+discontinuous nonlinearities}, \emph{Complex Var. Elliptic Equ.} {\bf 61} (2016), 1668--1688.
+\item Dhanya, R. and Sarkar, Abhishek: \href{https://doi.org/10.1080/17476933.2015.1055735}{Isolated singularities of polyharmonic operator in even
+dimension}, \emph{Complex Var. Elliptic Equ.} {\bf 61} (2016), 55--66.
+\item Dhara, Souvik and van der Hofstad, Remco and van Leeuwaarden,
+Johan S.
+H.
+and Sen, Sanchayan: \href{https://doi.org/10.1214/19-AIHP980}{Heavy-tailed configuration models at criticality}, \emph{Ann.
+Inst.
+Henri Poincar\'{e} Probab.
+Stat.} {\bf 56} (2020), 1515--1558.
+\item Dhillon, Gurbir and Khare, Apoorva: \href{https://doi.org/10.1016/j.aim.2017.08.005}{Faces of highest weight modules and the universal {W}eyl
+polyhedron}, \emph{Adv. Math.} {\bf 319} (2017), 111--152.
 \item Dond, Asha K. and Gudi, Thirupathi: \href{https://doi.org/10.1002/num.22317}{Patch-wise local projection stabilized finite element methods
 for convection-diffusion-reaction problems}, \emph{Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663.
+\item Dond, Asha K. and Gudi, Thirupathi and Nataraj, Neela: \href{https://doi.org/10.1515/cmam-2016-0024}{A nonconforming finite element approximation for optimal
+control of an obstacle problem}, \emph{Comput. Methods Appl. Math.} {\bf 16} (2016), 653--666.
 \item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh CH.: \href{https://doi.org/10.1080/01630563.2018.1538158}{An error analysis of discontinuous finite element methods for
 the optimal control problems governed by {S}tokes equation}, \emph{Numer. Funct. Anal. Optim.} {\bf 40} (2019), 421--460.
+\item Fern\'{o}s, Talia and Singla, Pooja: \href{https://doi.org/10.1017/S001708951500018X}{On images of real representations of special linear groups
+over complete discrete valuation rings}, \emph{Glasg. Math. J.} {\bf 58} (2016), 263--272.
+\item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P.
+and Silberman, Lior and Tao, Terence: \href{https://doi.org/10.2140/ant.2018.12.1773}{Homogeneous length functions on groups}, \emph{Algebra Number Theory} {\bf 12} (2018), 1773--1786.
+\item Gaddam, Sharat and Gudi, Thirupathi: \href{https://doi.org/10.1016/j.camwa.2017.12.010}{Inhomogeneous {D}irichlet boundary condition in the {\it a
+posteriori} error control of the obstacle problem}, \emph{Comput. Math. Appl.} {\bf 75} (2018), 2311--2327.
+\item Gaddam, Sharat and Gudi, Thirupathi: \href{https://doi.org/10.1515/cmam-2017-0018}{Bubbles enriched quadratic finite element method for the
+3{D}-elliptic obstacle problem}, \emph{Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236.
 \item Gadgil, Siddhartha: \href{https://doi.org/10.1007/s10817-019-09523-1}{Homogeneous {L}ength {F}unctions on {G}roups: {I}ntertwined
 {C}omputer and {H}uman {P}roofs}, \emph{J. Automat. Reason.} {\bf 64} (2020), 677--688.
+\item Gadgil, Siddhartha and Kulkarni, Dheeraj: \href{https://doi.org/10.1007/s12044-016-0278-3}{Relative symplectic caps, 4-genus and fibered knots}, \emph{Proc.
+Indian Acad.
+Sci.
+Math.
+Sci.} {\bf 126} (2016), 261--275.
 \item Garani, Shayan Srinivasa and Seshadri, Harish: \href{https://doi.org/10.1080/17459737.2019.1604845}{An algorithmic approach to {S}outh {I}ndian classical music}, \emph{J.
@@
 Music} {\bf 13} (2019), 107--134.
+\item Gaussier, Herv\'{e} and Seshadri, Harish: \href{https://doi.org/10.1007/s40879-017-0177-x}{Metric geometry of the {K}obayashi metric}, \emph{Eur. J. Math.} {\bf 3} (2017), 1030--1044.
 \item Gaussier, Herv\'{e} and Seshadri, Harish: \href{https://doi.org/10.1090/proc/14217}{Holomorphic motions and complex geometry}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 301--313.
+\item Gaussier, Herv\'{e} and Seshadri, Harish: \href{https://doi.org/10.1007/s40315-018-0243-5}{On the {G}romov hyperbolicity of convex domains in {$\Bbb
+C^n$}}, \emph{Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641.
+\item Gauttam, Sunil Kumar and Kumar, K. Suresh and Pal, Chandan: Risk-sensitive control of reflected diffusion processes on
+orthrant, \emph{Pure Appl. Funct. Anal.} {\bf 2} (2017), 477--510.
+\item Gayen, R. and Gupta, Sourav and Chakrabarti, A.: \href{https://doi.org/10.1016/j.aml.2016.01.018}{Approximate solution of the problem of scattering of surface
+water waves by a partially immersed rigid plane vertical
+barrier}, \emph{Appl. Math. Lett.} {\bf 58} (2016), 19--25.
+\item Ghara, Soumitra: \href{https://doi.org/10.1007/s11856-020-2016-x}{The orbit of a bounded operator under the {M}\"{o}bius group
+modulo similarity equivalence}, \emph{Israel J. Math.} {\bf 238} (2020), 167--207.
 \item Ghara, Soumitra and Kumar, Surjit: \href{https://doi.org/10.1016/j.jmaa.2018.09.048}{On the sum of two subnormal kernels}, \emph{J. Math. Anal. Appl.} {\bf 469} (2019), 1015--1027.
+\item Ghosh, Mrinal K. and Kumar, K. Suresh and Pal, Chandan: \href{https://doi.org/10.1080/07362994.2016.1180995}{Zero-sum risk-sensitive stochastic games for continuous time
+{M}arkov chains}, \emph{Stoch. Anal. Appl.} {\bf 34} (2016), 835--851.
+\item Ghosh, Mrinal K. and Pradhan, Somnath: \href{https://doi.org/10.1080/07362994.2017.1356732}{Risk-sensitive stochastic differential games with reflecting
+diffusions}, \emph{Stoch. Anal. Appl.} {\bf 36} (2018), 1--27.
+\item Ghosh, Mrinal Kanti and Pradhan, Somnath: \href{https://doi.org/10.1051/cocv/2020029}{Zero-sum risk-sensitive stochastic differential games with
+reflecting diffusions in the orthant}, \emph{ESAIM Control Optim. Calc. Var.} {\bf 26} (2020), Paper No. 114, 33.
+\item Ghosh, Puja and Paul, Kallol and Sain, Debmalya: \href{https://doi.org/10.30755/nsjom.04671}{Symmetric properties of orthogonality of linear operators on
+{$(\Bbb R^n,\|\cdot\|_1)$}}, \emph{Novi Sad J. Math.} {\bf 47} (2017), 41--46.
+\item Ghosh, Puja and Sain, Debmalya and Paul, Kallol: \href{https://doi.org/10.22034/aot.1703-1137}{On symmetry of {B}irkhoff-{J}ames orthogonality of linear
+operators}, \emph{Adv. Oper. Theory} {\bf 2} (2017), 428--434.
+\item Ghosh, Subhajit: \href{https://doi.org/10.1007/s10959-019-00945-6}{Total variation cutoff for the transpose top-2 with random
+shuffle}, \emph{J. Theoret. Probab.} {\bf 33} (2020), 1832--1854.
+\item Ghosh, Subhajit: Cutoff for the warp-transpose top with random shuffle, \emph{S\'{e}m. Lothar. Combin.} {\bf 84B} (2020), Art. 69, 12.
+\item Ghosh, Subhroshekhar and Krishnapur, Manjunath and Peres,
+Yuval: \href{https://doi.org/10.1214/15-AOP1051}{Continuum percolation for {G}aussian zeroes and {G}inibre
+eigenvalues}, \emph{Ann. Probab.} {\bf 44} (2016), 3357--3384.
 \item Gudi, Thirupathi and Majumder, Papri: \href{https://doi.org/10.1515/cmam-2019-0057}{Crouzeix-{R}aviart finite element approximation for the
@@
 solving parabolic obstacle problem}, \emph{Comput. Math. Appl.} {\bf 78} (2019), 3896--3915.
+\item Gudi, Thirupathi and Porwal, Kamana: \href{https://doi.org/10.1002/num.21983}{A {$C^0$} interior penalty method for a fourth-order
+variational inequality of the second kind}, \emph{Numer. Methods Partial Differential Equations} {\bf 32} (2016), 36--59.
+\item Gudi, Thirupathi and Porwal, Kamana: \href{https://doi.org/10.1016/j.cam.2015.07.008}{A posteriori error estimates of discontinuous {G}alerkin
+methods for the {S}ignorini problem}, \emph{J. Comput. Appl. Math.} {\bf 292} (2016), 257--278.
+\item Gudi, Thirupathi and Sau, Ramesh Ch.: \href{https://doi.org/10.1051/cocv/2019068}{Finite element analysis of the constrained {D}irichlet
+boundary control problem governed by the diffusion problem}, \emph{ESAIM Control Optim. Calc. Var.} {\bf 26} (2020), Paper No. 78, 19.
+\item Gupta, Rajeev: \href{https://doi.org/10.14232/actasm-015-088-4}{An improvement on the bound for {$C_2(n)$}}, \emph{Acta Sci. Math. (Szeged)} {\bf 83} (2017), 263--269.
 \item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: \href{https://doi.org/10.1016/j.jmaa.2020.124032}{Unitary equivalence of operator-valued multishifts}, \emph{J.
@@
 multishifts}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.
+\item Gupta, Rajeev and Misra, Gadadhar: \href{https://doi.org/10.4064/sm190314-18-8}{The {C}arath\'{e}odory-{F}ej\'{e}r interpolation on the polydisc}, \emph{Studia Math.} {\bf 254} (2020), 265--293.
+\item Gupta, Rajeev and Ramiz Reza, Md.: Operator space structures on {$\ell^1(n)$}, \emph{Houston J. Math.} {\bf 44} (2018), 1205--1212.
+\item Gupta, S. C.: The classical {S}tefan problem, \emph{} {\bf } (2018), xxiii+726.
 \item Gupta, Subhojoy: \href{https://doi.org/10.1090/tran/7777}{Limits of harmonic maps and crowned hyperbolic surfaces}, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 7573--7596.
@@
 a {R}iemann surface}, \emph{Math. Ann.} {\bf 373} (2019), 73--118.
+\item Gupta, Subhojoy and Wolf, Michael: \href{https://doi.org/10.4171/CMH/388}{Quadratic differentials, half-plane structures, and harmonic
+maps to trees}, \emph{Comment. Math. Helv.} {\bf 91} (2016), 317--356.
+\item Gupta, Subhojoy and Wolf, Michael: \href{https://doi.org/10.1090/conm/696/14021}{Meromorphic quadratic differentials with complex residues and
+spiralling foliations}, \emph{In the tradition of {A}hlfors-{B}ers. {VII}} {\bf 696} (2017), 153--181.
 \item Hatui, Sumana: \href{https://doi.org/10.1515/jgth-2019-0045}{Schur multipliers of special {$p$}-groups of rank 2}, \emph{J. Group Theory} {\bf 23} (2020), 85--95.
 \item Hazra, Somnath: \href{https://doi.org/10.1007/s11785-018-0822-5}{Homogeneous 2-shifts}, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.
+\item Iyer, Srikanth K.: \href{https://doi.org/10.1002/rsa.20741}{The random connection model: connectivity, edge lengths, and
+degree distributions}, \emph{Random Structures Algorithms} {\bf 52} (2018), 283--300.
+\item Iyer, Srikanth K.
+and Vaze, Rahul and Narasimha, Dheeraj: \href{https://doi.org/10.1016/j.physa.2015.12.030}{Autoregressive cascades on random networks}, \emph{Phys.
+A} {\bf 447} (2016), 345--354.
+\item Iyer, Srikanth K. and Yogeshwaran, D.: \href{https://doi.org/10.1214/19-AIHP1020}{Thresholds for vanishing of `isolated' faces in random \v{C}ech
+and {V}ietoris-{R}ips complexes}, \emph{Ann. Inst. Henri Poincar\'{e} Probab. Stat.} {\bf 56} (2020), 1869--1897.
+\item Iyer, Srikanth and Vaze, Rahul: \href{https://doi.org/10.1214/16-AAP1196}{Achieving nonzero information velocity in wireless networks}, \emph{Ann. Appl. Probab.} {\bf 27} (2017), 48--64.
 \item Jha, Abhash Kumar and Juyal, Abhishek and Pandey, Manish
@@
 associated to newforms on {$\Gamma_0(N)$}, \emph{J. Ramanujan Math. Soc.} {\bf 34} (2019), 245--252.
+\item Jha, Abhash Kumar and Kumar, Arvind: Construction of cusp forms using {R}ankin-{C}ohen brackets, \emph{Analytic number theory, modular forms and {$q$}-hypergeometric
+series} {\bf 221} (2017), 329--341.
 \item Jha, Abhash Kumar and Sahu, Brundaban: \href{https://doi.org/10.1142/S1793042119500490}{Rankin-{C}ohen brackets on {J}acobi forms of several variables
@@
 certain {D}irichlet series}, \emph{Automorphic forms and related topics} {\bf 732} (2019), 91--99.
+\item Ji, Kui and Jiang, Chunlan and Keshari, Dinesh Kumar and
+Misra, Gadadhar: \href{https://doi.org/10.1016/j.jfa.2016.12.019}{Rigidity of the flag structure for a class of
+{C}owen-{D}ouglas operators}, \emph{J. Funct. Anal.} {\bf 272} (2017), 2899--2932.
+\item Jiang, Chunlan and Ji, Kui and Misra, Gadadhar: \href{https://doi.org/10.1016/j.jfa.2017.06.015}{Classification of quasi-homogeneous holomorphic curves and
+operators in the {C}owen-{D}ouglas class}, \emph{J. Funct. Anal.} {\bf 273} (2017), 2870--2915.
+\item Kabiraj, Arpan: \href{https://doi.org/10.2140/agt.2016.16.2839}{Center of the {G}oldman {L}ie algebra}, \emph{Algebr. Geom. Topol.} {\bf 16} (2016), 2839--2849.
+\item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
+Sekar, Sruthi: \href{https://doi.org/10.1007/s00145-019-09339-7}{Four-state non-malleable codes with explicit constant rate}, \emph{J. Cryptology} {\bf 33} (2020), 1044--1079.
+\item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
+Sekar, Sruthi: Four-state non-malleable codes with explicit constant rate, \emph{Theory of cryptography. {P}art {II}} {\bf 10678} (2017), 344--375.
+\item Kanukurthi, Bhavana and Bhavana Obbattu, Sai Lakshmi and
+Sekar, Sruthi: Non-malleable randomness encoders and their applications, \emph{Advances in cryptology---{EUROCRYPT} 2018. {P}art {III}} {\bf 10822} (2018), 589--617.
 \item Kashyap, G.
@@
 Ravindranath and G.
-Ambika: Synapse loss and progress of Alzheimers disease - A network model, \emph{Scientific Reports} {\bf 9} (2019).
+Ambika: Synapse loss and progress of Alzheimer&rsquo;s disease - A network model, \emph{Scientific Reports} {\bf 9} (2019).
 \item Kataria, Kuldeep Kumar and Vellaisamy, Palaniappan: \href{https://doi.org/10.1080/07362994.2018.1538803}{On the convolution of {M}ittag-{L}effler distributions and its
 applications to fractional point processes}, \emph{Stoch. Anal. Appl.} {\bf 37} (2019), 115--122.
+\item Kaur, Amandeep and Martha, S. C. and Chakrabarti, A.: \href{https://doi.org/10.1007/s40314-020-01255-y}{An algebraic method of solution of a water wave scattering
+problem involving an asymmetrical trench}, \emph{Comput. Appl. Math.} {\bf 39} (2020), Paper No. 229, 19.
 \item Khan, Mohammad Yasir Feroz and Biswas, Rahul and Sau, Ramesh
@@
 C(\overline\Omega)$}, \emph{Math. Student} {\bf 88} (2019), 153--158.
+\item Khare, Apoorva: \href{https://doi.org/10.1090/tran/7304}{Generalized nil-{C}oxeter algebras over discrete complex
+reflection groups}, \emph{Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999.
+\item Khare, Apoorva and Rajaratnam, Bala: \href{https://doi.org/10.1007/s43036-020-00048-8}{Probability inequalities and tail estimates for metric
+semigroups}, \emph{Adv. Oper. Theory} {\bf 5} (2020), 779--795.
+\item Khare, Apoorva and Rajaratnam, Bala: \href{https://doi.org/10.1214/16-AOP1160}{The {H}offmann-{J}\o rgensen inequality in metric semigroups}, \emph{Ann. Probab.} {\bf 45} (2017), 4101--4111.
 \item Khare, Apoorva and Tikaradze, Akaki: \href{https://doi.org/10.1016/j.laa.2018.05.035}{A {C}arlitz--von {S}taudt type theorem for finite rings}, \emph{Linear Algebra Appl.} {\bf 568} (2019), 106--126.
+\item Khurana, Divya and Roy, Saikat and Sain, Debmalya: \href{https://doi.org/10.14232/actasm-020-420-6}{Symmetric points in spaces of linear operators between
+{B}anach spaces}, \emph{Acta Sci. Math. (Szeged)} {\bf 86} (2020), 617--634.
+\item Kor\'{a}nyi, Adam and Misra, Gadadhar: \href{https://doi.org/10.1016/j.aim.2019.05.018}{Homogeneous {H}ermitian holomorphic vector bundles and the
+{C}owen-{D}ouglas class over bounded symmetric domains}, \emph{Adv. Math.} {\bf 351} (2019), 1105--1138.
+\item Kor\'{a}nyi, Adam and Misra, Gadadhar: \href{https://doi.org/10.1016/j.crma.2015.11.002}{Homogeneous {H}ermitian holomorphic vector bundles and the
+{C}owen-{D}ouglas class over bounded symmetric domains}, \emph{C. R. Math. Acad. Sci. Paris} {\bf 354} (2016), 291--295.
+\item Krakovski, Roi and Onn, Uri and Singla, Pooja: \href{https://doi.org/10.1016/j.jalgebra.2017.10.018}{Regular characters of groups of type {$\ssf A_n$} over
+discrete valuation rings}, \emph{J. Algebra} {\bf 496} (2018), 116--137.
+\item Kreuzer, Martin and Patil, Dilip P.: \href{https://doi.org/10.1007/s13366-016-0324-4}{Computational aspects of {B}urnside rings, part {I}: the ring
+structure}, \emph{Beitr. Algebra Geom.} {\bf 58} (2017), 427--452.
+\item Krishna, M. and Krishnapur, Manjunath: \href{https://doi.org/10.1007/s13226-016-0183-6}{Persistence probabilities in centered, stationary, {G}aussian
+processes in discrete time}, \emph{Indian J. Pure Appl. Math.} {\bf 47} (2016), 183--194.
+\item Krishnapur, Manjunath and Rider, Brian and Vir\'{a}g, B\'{a}lint: \href{https://doi.org/10.1002/cpa.21573}{Universality of the stochastic {A}iry operator}, \emph{Comm.
+Pure Appl.
+Math.} {\bf 69} (2016), 145--199.
+\item Kundu, S. and Aggarwal, Manisha and Hazra, Somnath: \href{https://doi.org/10.1016/j.topol.2016.11.008}{Finitely chainable and totally bounded metric spaces:
+equivalent characterizations}, \emph{Topology Appl.} {\bf 216} (2017), 59--73.
 \item Lin, X.
@@
 K.: Structural and Dynamical Order of a Disordered Protein: Molecular Insights into Conformational Switching of PAGE4 at the Systems Level, \emph{Biomolecules} {\bf 9} (2019), 77.
+\item Mahadevan, Rajesh and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1007/s00245-018-9499-4}{Homogenization of an elliptic equation in a domain with
+oscillating boundary with non-homogeneous non-linear boundary
+conditions}, \emph{Appl. Math. Optim.} {\bf 82} (2020), 245--278.
 \item Mahajan, Prachi and Verma, Kaushal: \href{https://doi.org/10.1142/S0129167X19500125}{A comparison of two biholomorphic invariants}, \emph{Internat. J. Math.} {\bf 30} (2019), 1950012, 16.
@@
 Anal.} {\bf 13} (2019), 174--191.
+\item Manchanda, Kaustubh and Bose, Amitabha and Ramaswamy,
+Ramakrishna: \href{https://doi.org/10.1016/j.physa.2017.06.021}{Collective dynamics in heterogeneous networks of neuronal
+cellular automata}, \emph{Phys. A} {\bf 487} (2017), 111--124.
+\item Mandal, S. and Sahoo, T. and Chakrabarti, A.: \href{https://doi.org/10.1080/03091929.2017.1318129}{Characteristics of eigen-system for flexural gravity wave
+problems}, \emph{Geophys. Astrophys. Fluid Dyn.} {\bf 111} (2017), 249--281.
 \item Manfio, F. and Turgay, N. C. and Upadhyay, A.: \href{https://doi.org/10.1007/s12220-018-9990-9}{Biconservative submanifolds in {$\Bbb{S}^n\times\Bbb{R}$} and
 {$\Bbb{H}^n\times\Bbb{R}$}}, \emph{J. Geom. Anal.} {\bf 29} (2019), 283--298.
+\item Manikandan, K. and Vishnu Priya, N. and Senthilvelan, M. and
+Sankaranarayanan, R.: \href{https://doi.org/10.1063/1.5039901}{Deformation of dark solitons in a {$\Cal{PT}$}-invariant
+variable coefficients nonlocal nonlinear {S}chr\"{o}dinger
+equation}, \emph{Chaos} {\bf 28} (2018), 083103, 12.
 \item Misra, Gadadhar: Operators in the {C}owen-{D}ouglas class and related topics, \emph{Handbook of analytic operator theory} {\bf } (2019), 87--137.
+\item Misra, Gadadhar and Pal, Avijit: \href{https://doi.org/10.1007/s11854-018-0054-7}{Curvature inequalities for operators in the {C}owen-{D}ouglas
+class and localization of the {W}allach set}, \emph{J. Anal. Math.} {\bf 136} (2018), 31--54.
 \item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian: \href{https://doi.org/10.7900/jot.2018jun13.2225}{Contractivity and complete contractivity for finite
@@
 \item Misra, Gadadhar and Reza, Md. Ramiz: \href{https://doi.org/10.1215/00192082-7768711}{Curvature inequalities and extremal operators}, \emph{Illinois J. Math.} {\bf 63} (2019), 193--217.
+\item Misra, Gadadhar and Upmeier, Harald: \href{https://doi.org/10.1016/j.aim.2016.08.036}{Homogeneous vector bundles and intertwining operators for
+symmetric domains}, \emph{Adv. Math.} {\bf 303} (2016), 1077--1121.
 \item Mukherjee, Sajal Kumar and Bera, Sudip: \href{https://doi.org/10.1016/j.disc.2019.02.013}{Combinatorial proofs of the {N}ewton-{G}irard and
 {C}hapman-{C}ostas-{S}antos identities}, \emph{Discrete Math.} {\bf 342} (2019), 1577--1580.
+\item Nandakumaran, A. K. and Datti, P. S. and George, Raju K.: \href{https://doi.org/10.1017/9781108236843}{Ordinary differential equations}, \emph{} {\bf } (2017), xviii+328.
+\item Nandakumaran, A. K. and Sili, Ali: \href{http://projecteuclid.org/euclid.die/1448323252}{Homogenization of a hyperbolic equation with highly
+contrasting diffusivity coefficients}, \emph{Differential Integral Equations} {\bf 29} (2016), 37--54.
+\item Nandakumaran, Akambadath and Prakash, Ravi and Sardar, Bidhan
+Chandra: \href{https://doi.org/10.1002/mma.3865}{Asymptotic analysis of {N}eumann periodic optimal boundary
+control problem}, \emph{Math. Methods Appl. Sci.} {\bf 39} (2016), 4354--4374.
+\item Narayanan, E. K. and Singla, Pooja: \href{https://doi.org/10.1080/00927872.2017.1378894}{On monomial representations of finitely generated nilpotent
+groups}, \emph{Comm. Algebra} {\bf 46} (2018), 2319--2331.
 \item Nikolov, Nikolai and Verma, Kaushal: \href{https://doi.org/10.1007/s12220-019-00237-9}{On the squeezing function and {F}ridman invariants}, \emph{J. Geom. Anal.} {\bf 30} (2020), 1218--1225.
@@
 state space}, \emph{Stochastics} {\bf 91} (2019), 155--174.
+\item Pal, Ratna and Verma, Kaushal: \href{https://doi.org/10.4064/ap170928-2-4}{Ergodic properties of families of {H}\'{e}non maps}, \emph{Ann. Polon. Math.} {\bf 121} (2018), 45--71.
+\item Pal, Ritwik: \href{https://doi.org/10.1007/s11139-019-00206-4}{On the signs of {F}ourier coefficients of {H}ilbert cusp
+forms}, \emph{Ramanujan J.} {\bf 53} (2020), 467--481.
+\item Panda, Srikumar and Martha, S. C. and Chakrabarti, A.: \href{https://doi.org/10.1016/j.amc.2015.09.086}{An alternative approach to study nonlinear inviscid flow over
+arbitrary bottom topography}, \emph{Appl. Math. Comput.} {\bf 273} (2016), 165--177.
+\item Patil, D. P.: Affine one dimensional domains which are not {E}uclidean
+domains, \emph{Int. Rev. Pure Appl. Math.} {\bf 12} (2016), 45--50.
 \item Paul, Kallol and Sain, Debmalya: Birkhoff-{J}ames orthogonality and its application in the
@@
 operators, \emph{Ulam type stability} {\bf } (2019), 331--344.
+\item Paul, Kallol and Sain, Debmalya and Mal, Arpita: \href{https://doi.org/10.1016/j.laa.2017.10.008}{Approximate {B}irkhoff-{J}ames orthogonality in the space of
+bounded linear operators}, \emph{Linear Algebra Appl.} {\bf 537} (2018), 348--357.
+\item Paul, Kallol and Sain, Debmalya and Mal, Arpita and Mandal,
+Kalidas: \href{https://doi.org/10.15352/aot.1712-1268}{Orthogonality of bounded linear operators on complex {B}anach
+spaces}, \emph{Adv. Oper. Theory} {\bf 3} (2018), 699--709.
+\item Pingali, Vamsi P.: {$C^{2,\alpha}$} estimates and existence results for a
+nonconcave {PDE}, \emph{Electron. J. Differential Equations} {\bf } (2016), Paper No. 168, 10.
 \item Pingali, Vamsi P.: \href{https://doi.org/10.1080/17476933.2018.1454914}{A note on the deformed {H}ermitian {Y}ang-{M}ills {PDE}}, \emph{Complex Var. Elliptic Equ.} {\bf 64} (2019), 503--518.
 \item Pingali, Vamsi Pritham: \href{https://doi.org/10.1016/j.aim.2019.106921}{A vector bundle version of the {M}onge-{A}mp\`ere equation}, \emph{Adv. Math.} {\bf 360} (2020), 106921, 40.
+\item Pingali, Vamsi Pritham: \href{https://doi.org/10.1090/tran/7416}{A note on higher extremal metrics}, \emph{Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010.
 \item Pingali, Vamsi Pritham: \href{https://doi.org/10.1007/s11005-020-01279-9}{Quillen metrics and perturbed equations}, \emph{Lett. Math. Phys.} {\bf 110} (2020), 1861--1875.
+\item Pingali, Vamsi Pritham: \href{https://doi.org/10.1007/s00209-017-1903-2}{Representability of {C}hern-{W}eil forms}, \emph{Math. Z.} {\bf 288} (2018), 629--641.
 \item Poria, Anirudha: \href{https://doi.org/10.1080/01630563.2020.1728771}{Positive weight function and classification of {$g$}-frames}, \emph{Numer. Funct. Anal. Optim.} {\bf 41} (2020), 950--968.
+\item Pradhan, Puspendu and Sahu, Bikramaditya: \href{https://doi.org/10.1016/j.disc.2020.112044}{A characterization of the family of secant lines to a
+hyperbolic quadric in {${\rm PG} (3,q)$}, {$q$} odd}, \emph{Discrete Math.} {\bf 343} (2020), 112044, 8.
+\item Prasad, Phoolan: \href{https://doi.org/10.1007/s12044-016-0275-6}{Ray equations of a weak shock in a hyperbolic system of
+conservation laws in multi-dimensions}, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 126} (2016), 199--206.
+\item Prasad, Phoolan: \href{https://doi.org/10.1007/978-981-10-7581-0}{Propagation of multidimensional nonlinear waves and
+kinematical conservation laws}, \emph{} {\bf } (2017), xi+159.
+\item Prasad, Phoolan: \href{https://doi.org/10.1007/s13226-016-0197-0}{Kinematical conservation laws in a space of arbitrary
+dimensions}, \emph{Indian J. Pure Appl. Math.} {\bf 47} (2016), 641--653.
+\item Pritham Pingali, Vamsi: \href{https://doi.org/10.1142/S0129167X18500416}{Existence of coupled {K}\"{a}hler-{E}instein metrics using the
+continuity method}, \emph{Internat. J. Math.} {\bf 29} (2018), 1850041, 8.
 \item Quddus, Safdar: \href{https://doi.org/10.4171/JNCG/320}{Invariants of the {$\Bbb Z_2$} orbifolds of the {P}odle\'{s} two
 spheres}, \emph{J. Noncommut. Geom.} {\bf 13} (2019), 257--267.
+\item Ram, Samrith: \href{https://doi.org/10.1016/j.laa.2016.01.029}{Counting zero kernel pairs over a finite field}, \emph{Linear Algebra Appl.} {\bf 495} (2016), 1--10.
+\item Ray, Anubhab and Roy, Saikat and Bagchi, Satya and Sain,
+Debmalya: \href{https://doi.org/10.7900/jot}{Extreme contractions on finite-dimensional polygonal {B}anach
+spaces. {II}}, \emph{J. Operator Theory} {\bf 84} (2020), 127--137.
+\item Ray, Samarpita: \href{https://doi.org/10.1142/S0219498820500061}{Closure operations, continuous valuations on monoids and
+spectral spaces}, \emph{J. Algebra Appl.} {\bf 19} (2020), 2050006, 27.
 \item Reddy, Nanda Kishore: \href{https://doi.org/10.1093/imrn/rnx134}{Equality of {L}yapunov and stability exponents for products of
 isotropic random matrices}, \emph{Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624.
+\item Reza, Md. Ramiz: \href{https://doi.org/10.1512/iumj.2018.67.7320}{Curvature inequalities for operators in the {C}owen-{D}ouglas
+class of a planar domain}, \emph{Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279.
+\item Richard, Thomas and Seshadri, Harish: \href{https://doi.org/10.1007/s00229-015-0790-2}{Positive isotropic curvature and self-duality in dimension 4}, \emph{Manuscripta Math.} {\bf 149} (2016), 443--457.
+\item Roncal, Luz and Thangavelu, Sundaram: \href{https://doi.org/10.1093/imrn/rny137}{An extension problem and trace {H}ardy inequality for the
+sub-{L}aplacian on {$H$}-type groups}, \emph{Int. Math. Res. Not. IMRN} {\bf } (2020), 4238--4294.
+\item Roncal, Luz and Thangavelu, Sundaram: \href{https://doi.org/10.1016/j.aim.2016.07.010}{Hardy's inequality for fractional powers of the sublaplacian
+on the {H}eisenberg group}, \emph{Adv. Math.} {\bf 302} (2016), 106--158.
 \item Roth, Julien and Upadhyay, Abhitosh: \href{https://doi.org/10.1007/s00013-019-01315-8}{On compact anisotropic {W}eingarten hypersurfaces in
@@
 sectional curvature}, \emph{Bull. Aust. Math. Soc.} {\bf 101} (2020), 333--338.
+\item Roy, Dipankar and Pandit, Rahul: One-dimensional {K}ardar-{P}arisi-{Z}hang and
+{K}uramoto-{S}ivashinsky universality class: limit
+distributions, \emph{Phys. Rev. E} {\bf 101} (2020), 030103(R), 6.
 \item Roy, Krishanu and Venkatesh, R.: \href{https://doi.org/10.1007/s00031-018-9510-9}{Maximal closed subroot systems of real affine root systems}, \emph{Transform.
@@
 bounded linear operator}, \emph{Ann. Funct. Anal.} {\bf 10} (2019), 135--143.
+\item Sain, Debmalya: \href{https://doi.org/10.1007/s13226-020-0498-1}{On a generalization of a complementary triangle inequality in
+{H}ilbert spaces and {B}anach spaces}, \emph{Indian J. Pure Appl. Math.} {\bf 51} (2020), 1815--1827.
+\item Sain, Debmalya: \href{https://doi.org/10.1016/j.jmaa.2017.07.070}{On the norm attainment set of a bounded linear operator}, \emph{J. Math. Anal. Appl.} {\bf 457} (2018), 67--76.
 \item Sain, Debmalya: \href{https://doi.org/10.1007/s13226-020-0393-9}{On the norm attainment set of a bounded linear operator and
@@
 Santanu: \href{https://doi.org/10.1016/j.laa.2019.04.024}{On the numerical index of polyhedral {B}anach spaces}, \emph{Linear Algebra Appl.} {\bf 577} (2019), 121--133.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: A complete characterization of {B}irkhoff-{J}ames
+orthogonality in infinite dimensional normed space, \emph{J. Operator Theory} {\bf 80} (2018), 399--413.
 \item Sain, Debmalya and Paul, Kallol and Mal, Arpita: On approximate {B}irkhoff-{J}ames orthogonality and normal
 cones in a normed space, \emph{J. Convex Anal.} {\bf 26} (2019), 341--351.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita and Ray,
+Anubhab: \href{https://doi.org/10.1080/03081087.2019.1586824}{A complete characterization of smoothness in the space of
+bounded linear operators}, \emph{Linear Multilinear Algebra} {\bf 68} (2020), 2484--2494.
 \item Sain, Debmalya and Paul, Kallol and Mandal, Kalidas: \href{https://doi.org/10.7153/oam-2019-13-31}{On two extremum problems related to the norm of a bounded
@@
 spaces, \emph{J. Convex Anal.} {\bf 26} (2019), 877--885.
+\item Sain, Debmalya and Tanaka, Ryotaro: \href{https://doi.org/10.1007/s43037-020-00064-z}{Modular {B}irkhoff-{J}ames orthogonality in {$B(\Bbb{X,Y})$}
+and {$K(\Bbb{X,Y})$}}, \emph{Banach J. Math. Anal.} {\bf 14} (2020), 1347--1362.
+\item Sanki, Bidyut: \href{https://doi.org/10.1142/S1793525318500309}{Filling of closed surfaces}, \emph{J. Topol. Anal.} {\bf 10} (2018), 897--913.
 \item Sanki, Bidyut and Gadgil, Siddhartha: \href{https://doi.org/10.1142/S1793525319500018}{Graphs of systoles on hyperbolic surfaces}, \emph{J. Topol. Anal.} {\bf 11} (2019), 1--20.
+\item Sarkar, Amar Deep and Verma, Kaushal: \href{https://doi.org/10.1007/s12044-020-00565-9}{A submultiplicative property of the {C}arath\'{e}odory metric on
+planar domains}, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 130} (2020), Paper No. 35, 6.
 \item Sarkar, Amar Deep and Verma, Kaushal: \href{https://doi.org/10.1007/s40315-020-00303-2}{Boundary behaviour of some conformal invariants on planar
 domains}, \emph{Comput. Methods Funct. Theory} {\bf 20} (2020), 145--158.
+\item Sen, Suparna: \href{https://doi.org/10.1515/apam-2015-0010}{Segal-{B}argmann transform and {P}aley-{W}iener theorems on
+{H}eisenberg motion groups}, \emph{Adv. Pure Appl. Math.} {\bf 7} (2016), 13--28.
+\item Senthil Raani, K. S.: \href{https://doi.org/10.1007/s00605-017-1081-7}{{$L^p$}-{F}ourier asymptotics, {H}ardy-type inequality and
+fractal measures}, \emph{Monatsh. Math.} {\bf 184} (2017), 459--487.
 \item Seshadri, Harish: \href{https://doi.org/10.1007/s13226-019-0355-2}{Differential geometry in {I}ndia}, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 795--799.
+\item Seshadri, Harish and Verma, Kaushal: Some aspects of the automorphism groups of domains, \emph{Handbook of group actions. {V}ol. {III}} {\bf 40} (2018), 145--174.
+\item Tanaka, Ryotaro and Sain, Debmalya: \href{https://doi.org/10.1007/s43034-019-00048-7}{On symmetry of strong {B}irkhoff orthogonality in {$B(\Cal
+H,\Cal K)$} and {$K(\Cal H,\Cal K)$}}, \emph{Ann. Funct. Anal.} {\bf 11} (2020), 693--704.
+\item Thangavelu, Sundaram: \href{https://doi.org/10.1007/s41478-018-0147-9}{An analogue of {P}fannschmidt's theorem for the {H}eisenberg
+group}, \emph{J. Anal.} {\bf 26} (2018), 235--244.
+\item Thangavelu, Sundaram and Naidu Dogga, Venku: \href{https://doi.org/10.1515/apam-2017-0042}{{$L^p$}-{$L^2$} estimates for solutions of the wave equation
+associated to the {G}rushin operator}, \emph{Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92.
 \item Turgay, Nurettin Cenk and Upadhyay, Abhitosh: \href{https://doi.org/10.1002/mana.201700328}{On biconservative hypersurfaces in 4-dimensional {R}iemannian
@@
 \item Verma, Kaushal: \href{https://doi.org/10.1007/s13324-018-0221-0}{Notes on the boundaries of quadrature domains}, \emph{Anal. Math. Phys.} {\bf 9} (2019), 617--638.
+\item Verma, Kaushal: Remembering {R}. {R}. {S}imha, \emph{Math. Newsl.} {\bf 27} (2017), 16--20.
 \item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan,
@@
 equation}, \emph{Phys. Lett. A} {\bf 383} (2019), 15--26.
+\item Yadav, Avinash Chand and Manchanda, Kaustubh and Ramaswamy,
+Ramakrishna: \href{https://doi.org/10.1016/j.physa.2017.04.029}{Emergent organization in a model market}, \emph{Phys. A} {\bf 482} (2017), 118--126.
 \end{enumerate}

### 2021-08-19 ugc/src/Publications.scala

@@ -17,7 +17,7 @@ object Publications {
       case (k, v) => k.getValue.toLowerCase -> v.toUserString
     })
     .toVector
-    .filter(m => Set("2019", "2020").contains(m("year")))
+    .filter(m => Set("2016", "2017", "2018", "2019", "2020").contains(m("year")))
 
   import net.jcazevedo.moultingyaml._
   import net.jcazevedo.moultingyaml.DefaultYamlProtocol._

### 2021-08-20 data/draft-publications.tex
filter corrected

@@
 nonlocal boundary jumps, \emph{J. Phys. A} {\bf 52} (2019), 355001, 19.
+\item Addario-Berry, Louigi and Bhamidi, Shankar and Sen, Sanchayan: A probabilistic approach to the leader problem in random
+graphs, \emph{Random Structures Algorithms} {\bf 58} (2021), 34--67.
 \item Adhikari, Kartick and Kishore Reddy, Nanda and Ram Reddy,
@@
 ensembles, \emph{Int. Math. Res. Not. IMRN} {\bf } (2017), 6694--6730.
+\item Adhikari, Saswata and Anoop, V. P. and Parui, Sanjay: Existence of extremals of {D}unkl-type {S}obolev inequality
+and of {S}tein-{W}eiss inequality for {D}unkl {R}iesz
+potential, \emph{Complex Anal. Oper. Theory} {\bf 15} (2021), Paper No. 28, 34.
 \item Adimurthi and Ratnakumar, P. K. and Sohani, Vijay Kumar: A {H}ardy-{S}obolev inequality for the twisted {L}aplacian, \emph{Proc. Roy. Soc. Edinburgh Sect. A} {\bf 147} (2017), 1--23.
@@
 {H}ardy space, \emph{Arch. Math. (Basel)} {\bf 114} (2020), 431--444.
+\item Anoop, V. P. and Parui, Sanjay: Improved fractional {H}ardy inequalities for {D}unkl gradient, \emph{Math. Inequal. Appl.} {\bf 24} (2021), 129--155.
+\item Arunkumar, G.: Chromatic symmetric function of graphs from {B}orcherds
+algebras, \emph{J. Combin. Theory Ser. A} {\bf 183} (2021), Paper No. 105492, 28.
 \item Arunkumar, G. and Kus, Deniz and Venkatesh, R.: Root multiplicities for {B}orcherds algebras and graph
@@
 \item Balodi, Mamta and Banerjee, Abhishek and Naolekar, Anita: B{V}-operators and the secondary {H}ochschild complex, \emph{C. R. Math. Acad. Sci. Paris} {\bf 358} (2020), 1239--1258.
+\item Balodi, Mamta and Banerjee, Abhishek and Ray, Samarpita: Entwined modules over linear categories and {G}alois
+extensions, \emph{Israel J. Math.} {\bf 241} (2021), 623--692.
 \item Balodi, Mamta and Banerjee, Abhishek and Ray, Samarpita: Cohomology of modules over {$H$}-categories and
@@
 \item Banerjee, Abhishek: Completions of monoid objects and descent results, \emph{J. Algebra} {\bf 507} (2018), 362--399.
+\item Banerjee, Abhishek: {$FI$}-modules over preadditive categories and torsion
+theories, \emph{J. Pure Appl. Algebra} {\bf 225} (2021), 106595, 29.
 \item Banerjee, Abhishek and Kour, Surjeet: {$(A,\delta)$}-modules, {H}ochschild homology and higher
 derivations, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802.
+\item Banerjee, Agnid and Garofalo, Nicola and Manna, Ramesh: A strong unique continuation property for the heat operator
+with {H}ardy type potential, \emph{J. Geom. Anal.} {\bf 31} (2021), 5480--5504.
 \item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable {CMC} free-boundary surfaces in a strictly convex
@@
 cycle, \emph{Stoch. Anal. Appl.} {\bf 34} (2016), 96--116.
+\item Basak, Riju and Garg, Rahul and Thangavelu, Sundaram: Homogeneous {F}ourier and {W}eyl multipliers on {S}obolev
+spaces related to the {H}eisenberg group, \emph{J. Funct. Anal.} {\bf 281} (2021), Paper No. 109154, 45.
 \item Basu, Arnab and Ghosh, Mrinal K.: Nonzero-sum risk-sensitive stochastic games on a countable
 state space, \emph{Math. Oper. Res.} {\bf 43} (2018), 516--532.
+\item Basu, Riddhipratim and Ganguly, Shirshendu and Hegde, Milind
+and Krishnapur, Manjunath: Lower deviations in {$\beta$}-ensembles and law of iterated
+logarithm in last passage percolation, \emph{Israel J. Math.} {\bf 242} (2021), 291--324.
+\item Behera, Kiran Kumar: A generalized inverse eigenvalue problem and {$m$}-functions, \emph{Linear Algebra Appl.} {\bf 622} (2021), 46--65.
 \item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
@@
 \item Bera, Sayani and Verma, Kaushal: Some aspects of shift-like automorphisms of {$\Bbb C^k$}, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 128} (2018), Art. 10, 48.
+\item Bera, Sudip: Enumeration of weighted paths on a digraph and block hook
+determinant, \emph{Spec. Matrices} {\bf 9} (2021), 197--211.
+\item Bera, Sudip and Dey, Hiranya Kishore and Mukherjee, Sajal
+Kumar: On the connectivity of enhanced power graphs of finite groups, \emph{Graphs Combin.} {\bf 37} (2021), 591--603.
 \item Bera, Sudip and Mukherjee, Sajal Kumar: Generalized power sum and {N}ewton-{G}irard identities, \emph{Graphs Combin.} {\bf 36} (2020), 1957--1964.
@@
 kernel, \emph{Studia Math.} {\bf 255} (2020), 83--107.
+\item Bhattacharyya, Tirthankar and Das, B. Krishna and Sau,
+Haripada: Toeplitz operators on the symmetrized bidisc, \emph{Int. Math. Res. Not. IMRN} {\bf } (2021), 8492--8520.
 \item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K.: Survey of last ten years of work done in {I}ndia in some
@@
 surface, \emph{Geom. Dedicata} {\bf 180} (2016), 399--413.
+\item Biswas, Anindya and Maitra, Anwoy: A characterization of the bidisc by a subgroup of its
+automorphism group, \emph{J. Math. Anal. Appl.} {\bf 504} (2021), Paper No. 125434, 10.
 \item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and
@@
 indefinite second-order linear elliptic problems, \emph{Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.
+\item Carstensen, Carsten and Mallik, Gouranga and Nataraj, Neela: Nonconforming finite element discretization for semilinear
+problems with trilinear nonlinearity, \emph{IMA J. Numer. Anal.} {\bf 41} (2021), 164--205.
 \item Chakrabarti, A. and Mondal, Sumita Rani: On approximate numerical method of solution of {F}redholm
@@
 spaces, \emph{Acta Sci. Math. (Szeged)} {\bf 86} (2020), 449--466.
+\item Chattopadhyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: Multiplicities, invariant subspaces and an additive formula, \emph{Proc. Edinb. Math. Soc. (2)} {\bf 64} (2021), 279--297.
+\item Chmieli\'{n}ski, Jacek and Khurana, Divya and Sain, Debmalya: Local approximate symmetry of {B}irkhoff-{J}ames orthogonality
+in normed linear spaces, \emph{Results Math.} {\bf 76} (2021), Paper No. 136, 26.
 \item Choudhary, A. and Martha, S. C. and Chakrabarti, A.: Modified method for the solution of dual trigonometric series
 relations, \emph{Proc. Nat. Acad. Sci. India Sect. A} {\bf 90} (2020), 437--445.
+\item Choudhury, Projesh Nath and Eagambaram, N. and Sivakumar, K.
+C. and Sushmitha, P.: On the matrix class {$Q_0$} and inverse monotonicity
+properties of bordered matrices, \emph{Linear Algebra Appl.} {\bf 612} (2021), 206--222.
+\item Choudhury, Projesh Nath and Kannan, M. Rajesh: Interval hulls of {$N$}-matrices and almost {$P$}-matrices, \emph{Linear Algebra Appl.} {\bf 617} (2021), 27--38.
 \item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
@@
 semipositive matrices, \emph{Electron. J. Linear Algebra} {\bf 34} (2018), 687--694.
+\item Choudhury, Projesh Nath and Sivakumar, K. C.: Matrices with positive semidefinite real part, \emph{Linear Multilinear Algebra} {\bf 69} (2021), 448--470.
 \item Choudhury, Projesh Nath and Tsatsomeros, Michael J.: Algorithmic detection and construction of {N}-matrices, \emph{Linear Algebra Appl.} {\bf 602} (2020), 46--56.
@@
 \item Datar, Ved V. and Pingali, Vamsi Pritham: On coupled constant scalar curvature {K}\"{a}hler metrics, \emph{J. Symplectic Geom.} {\bf 18} (2020), 961--994.
+\item Datar, Ved and Jacob, Adam and Zhang, Yuguang: Adiabatic limits of anti-self-dual connections on collapsed
+{$K3$} surfaces, \emph{J. Differential Geom.} {\bf 118} (2021), 223--296.
+\item Datar, Ved and Seshadri, Harish and Song, Jian: Metric rigidity of {K}\"{a}hler manifolds with lower {R}icci
+bounds and almost maximal volume, \emph{Proc. Amer. Math. Soc.} {\bf 149} (2021), 3569--3574.
+\item Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane, \emph{Discrete Comput. Geom.} {\bf 65} (2021), 531--553.
 \item Datta, Basudeb and Maity, Dipendu: Correction to: {S}emi-equivelar and vertex-transitive maps on
@@
 \item Datta, Basudeb and Sarkar, Soumen: On equilibrium triangulations of quasitoric manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57-56.
+\item Deb, Prahllad: On unitary invariants of quotient {H}ilbert modules along
+smooth complex analytic sets, \emph{Bull. Sci. Math.} {\bf 169} (2021), Paper No. 102977, 42.
 \item Dhanya, R. and Prashanth, S. and Tiwari, Sweta and Sreenadh,
@@
 polyhedron, \emph{Adv. Math.} {\bf 319} (2017), 111--152.
+\item Dias, Kealey and Gupta, Subhojoy and Trnkova, Maria: Quadratic differentials, measured foliations, and metric
+graphs on punctured surfaces, \emph{Illinois J. Math.} {\bf 65} (2021), 417--454.
 \item Dond, Asha K. and Gudi, Thirupathi: Patch-wise local projection stabilized finite element methods
@@
 \item Gadgil, Siddhartha and Kulkarni, Dheeraj: Relative symplectic caps, 4-genus and fibered knots, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 126} (2016), 261--275.
+\item Ganguly, Pritam and Thangavelu, Sundaram: On the lacunary spherical maximal function on the {H}eisenberg
+group, \emph{J. Funct. Anal.} {\bf 280} (2021), 108832, 32.
+\item Ganguly, Pritam and Thangavelu, Sundaram: Theorems of {C}hernoff and {I}ngham for certain eigenfunction
+expansions, \emph{Adv. Math.} {\bf 386} (2021), Paper No. 107815, 31.
 \item Garani, Shayan Srinivasa and Seshadri, Harish: An algorithmic approach to {S}outh {I}ndian classical music, \emph{J. Math. Music} {\bf 13} (2019), 107--134.
@@
 diffusions, \emph{Stoch. Anal. Appl.} {\bf 36} (2018), 1--27.
+\item Ghosh, Mrinal K. and Suresh Kumar, K. and Pal, Chandan and
+Pradhan, Somnath: Nonzero-sum risk-sensitive stochastic differential games with
+discounted costs, \emph{Stoch. Anal. Appl.} {\bf 39} (2021), 306--326.
 \item Ghosh, Mrinal Kanti and Pradhan, Somnath: Zero-sum risk-sensitive stochastic differential games with
@@
 \item Gupta, S. C.: The classical {S}tefan problem, \emph{} {\bf } (2018), xxiii+726.
+\item Gupta, Subhojoy: Harmonic maps and wild {T}eichm\"{u}ller spaces, \emph{J. Topol. Anal.} {\bf 13} (2021), 349--393.
 \item Gupta, Subhojoy: Limits of harmonic maps and crowned hyperbolic surfaces, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 7573--7596.
+\item Gupta, Subhojoy and Mj, Mahan: Meromorphic projective structures, grafting and the monodromy
+map, \emph{Adv. Math.} {\bf 383} (2021), Paper No. 107673, 49.
 \item Gupta, Subhojoy and Mj, Mahan: Monodromy representations of meromorphic projective
@@
 \item Hatui, Sumana: Schur multipliers of special {$p$}-groups of rank 2, \emph{J. Group Theory} {\bf 23} (2020), 85--95.
+\item Hatui, Sumana and Singla, Pooja: On {S}chur multiplier and projective representations of
+{H}eisenberg groups, \emph{J. Pure Appl. Algebra} {\bf 225} (2021), Paper No. 106742, 16.
 \item Hazra, Somnath: Homogeneous 2-shifts, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.
@@
 reflection groups, \emph{Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999.
+\item Khare, Apoorva and Pingali, Vamsi Pritham: On an asymptotic characterisation of {G}riffiths
+semipositivity, \emph{Bull. Sci. Math.} {\bf 167} (2021), Paper No. 102956, 7.
 \item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric
 semigroups, \emph{Adv. Oper. Theory} {\bf 5} (2020), 779--795.
+\item Khare, Apoorva and Rajaratnam, Bala: Differential calculus on the space of countable labelled
+graphs, \emph{Adv. Oper. Theory} {\bf 6} (2021), Paper No. 12, 28.
 \item Khare, Apoorva and Rajaratnam, Bala: The {H}offmann-{J}\o rgensen inequality in metric semigroups, \emph{Ann. Probab.} {\bf 45} (2017), 4101--4111.
@@
 {B}anach spaces, \emph{Acta Sci. Math. (Szeged)} {\bf 86} (2020), 617--634.
+\item Khurana, Divya and Sain, Debmalya: Norm derivatives and geometry of bilinear operators, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 49, 19.
 \item Kor\'{a}nyi, Adam and Misra, Gadadhar: Homogeneous {H}ermitian holomorphic vector bundles and the
@@
 structure, \emph{Beitr. Algebra Geom.} {\bf 58} (2017), 427--452.
+\item Kreuzer, Martin and Patil, Dilip P.: Computational aspects of {B}urnside rings part {II}: important
+maps, \emph{Beitr. Algebra Geom.} {\bf 62} (2021), 475--494.
 \item Krishna, M. and Krishnapur, Manjunath: Persistence probabilities in centered, stationary, {G}aussian
@@
 equivalent characterizations, \emph{Topology Appl.} {\bf 216} (2017), 59--73.
+\item Lai, King-Fai and Longhi, Ignazio and Suzuki, Takashi and Tan,
+Ki-Seng and Trihan, Fabien: On the {$\mu$}-invariants of abelian varieties over function
+fields of positive characteristic, \emph{Algebra Number Theory} {\bf 15} (2021), 863--907.
 \item Lin, X.
@@
 equation, \emph{Chaos} {\bf 28} (2018), 083103, 12.
+\item Manna, Ramesh and Shrivastava, Saurabh and Shuin, Kalachand: Weighted estimates for maximal functions associated with
+finite type curves in {$\Bbb R^2$}, \emph{Nonlinear Anal.} {\bf 205} (2021), 112225, 24.
 \item Misra, Gadadhar: Operators in the {C}owen-{D}ouglas class and related topics, \emph{Handbook of analytic operator theory} {\bf } (2019), 87--137.
@@
 contrasting diffusivity coefficients, \emph{Differential Integral Equations} {\bf 29} (2016), 37--54.
+\item Nandakumaran, A. K. and Sufian, Abu: Oscillating {PDE} in a rough domain with a curved interface:
+homogenization of an optimal control problem, \emph{ESAIM Control Optim. Calc. Var.} {\bf 27} (2021), Paper No. S4, 37.
+\item Nandakumaran, A. K. and Sufian, Abu: Strong contrasting diffusivity in general oscillating domains:
+homogenization of optimal control problems, \emph{J. Differential Equations} {\bf 291} (2021), 57--89.
 \item Nandakumaran, Akambadath and Prakash, Ravi and Sardar, Bidhan
@@
 \item Pingali, Vamsi Pritham: Representability of {C}hern-{W}eil forms, \emph{Math. Z.} {\bf 288} (2018), 629--641.
+\item Pingali, Vamsi Pritham and Varolin, Dror: Nonuniformly flat affine algebraic hypersurfaces, \emph{Nagoya Math. J.} {\bf 241} (2021), 1--43.
+\item Poria, Anirudha: Uncertainty principles for the {O}pdam-{C}herednik transform
+on modulation spaces, \emph{Integral Transforms Spec. Funct.} {\bf 32} (2021), 191--206.
 \item Poria, Anirudha: Positive weight function and classification of {$g$}-frames, \emph{Numer. Funct. Anal. Optim.} {\bf 41} (2020), 950--968.
@@
 hyperbolic quadric in {${\rm PG} (3,q)$}, {$q$} odd, \emph{Discrete Math.} {\bf 343} (2020), 112044, 8.
+\item Pradhan, Somnath: Risk-sensitive ergodic control of reflected diffusion
+processes in orthant, \emph{Appl. Math. Optim.} {\bf 83} (2021), 1739--1764.
 \item Prasad, Phoolan: Ray equations of a weak shock in a hyperbolic system of
@@
 \item Roy, Krishanu and Venkatesh, R.: Maximal closed subroot systems of real affine root systems, \emph{Transform. Groups} {\bf 24} (2019), 1261--1308.
+\item Roy, Saikat and Senapati, Tanusri and Sain, Debmalya: Orthogonality of bilinear forms and application to matrices, \emph{Linear Algebra Appl.} {\bf 615} (2021), 104--111.
 \item Sain, Debmalya: On extreme contractions and the norm attainment set of a
@@
 {B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces, \emph{Oper. Matrices} {\bf 13} (2019), 433--445.
+\item Sain, Debmalya: Orthogonality and smoothness induced by the norm derivatives, \emph{Rev. R. Acad. Cienc. Exactas F\'{\i}s. Nat. Ser. A Mat. RACSAM} {\bf 115} (2021), Paper No. 120, 10.
+\item Sain, Debmalya and Bhunia, Pintu and Bhanja, Aniket and Paul,
+Kallol: On a new norm on {$\Cal B(\Cal H)$} and its applications to
+numerical radius inequalities, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 51, 25.
+\item Sain, Debmalya and Mal, Arpita and Bhunia, Pintu and Paul,
+Kallol: On numerical radius and {C}rawford number attainment sets of a
+bounded linear operator, \emph{J. Convex Anal.} {\bf 28} (2021), 67--80.
+\item Sain, Debmalya and Mal, Arpita and Mandal, Kalidas and Paul,
+Kallol: On uniform {B}ishop-{P}helps-{B}ollob\'{a}s type approximations of
+linear operators and preservation of geometric properties, \emph{J. Math. Anal. Appl.} {\bf 494} (2021), 124582, 22.
 \item Sain, Debmalya and Mal, Arpita and Paul, Kallol: Some remarks on {B}irkhoff-{J}ames orthogonality of linear
@@
 Santanu: On the numerical index of polyhedral {B}anach spaces, \emph{Linear Algebra Appl.} {\bf 577} (2019), 121--133.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: On extreme contractions between real {B}anach spaces, \emph{Expo. Math.} {\bf 39} (2021), 33--47.
 \item Sain, Debmalya and Paul, Kallol and Mal, Arpita: A complete characterization of {B}irkhoff-{J}ames
@@
 domains, \emph{Comput. Methods Funct. Theory} {\bf 20} (2020), 145--158.
+\item Sebastian, Geethika and Daniel, Sukumar: A weaker {G}leason-{K}ahane-\.{Z}elazko theorem for modules and
+applications to {H}ardy spaces, \emph{Colloq. Math.} {\bf 164} (2021), 273--282.
+\item Sen, Jeet and Sain, Debmalya and Paul, Kallol: Orthogonality and norm attainment of operators in
+semi-{H}ilbertian spaces, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 17, 12.
+\item Sen, Jeet and Sain, Debmalya and Paul, Kallol: On approximate orthogonality and symmetry of operators in
+semi-{H}ilbertian structure, \emph{Bull. Sci. Math.} {\bf 170} (2021), Paper No. 102997, 22.
 \item Sen, Suparna: Segal-{B}argmann transform and {P}aley-{W}iener theorems on
@@
 Ramakrishna: Emergent organization in a model market, \emph{Phys. A} {\bf 482} (2017), 118--126.
+\item \'{A}lvarez-C\'{o}nsul, Luis and Garcia-Fernandez, Mario and
+Garc\'{\i}a-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the {E}instein-{B}ogomol'nyi
+equations, \emph{Math. Ann.} {\bf 379} (2021), 1651--1684.
 \end{enumerate}
@@
 nonlocal boundary jumps}, \emph{J. Phys. A} {\bf 52} (2019), 355001, 19.
+\item Addario-Berry, Louigi and Bhamidi, Shankar and Sen, Sanchayan: \href{https://doi.org/10.1002/rsa.20966}{A probabilistic approach to the leader problem in random
+graphs}, \emph{Random Structures Algorithms} {\bf 58} (2021), 34--67.
 \item Adhikari, Kartick and Kishore Reddy, Nanda and Ram Reddy,
@@
 ensembles}, \emph{Int. Math. Res. Not. IMRN} {\bf } (2017), 6694--6730.
+\item Adhikari, Saswata and Anoop, V. P. and Parui, Sanjay: \href{https://doi.org/10.1007/s11785-020-01068-1}{Existence of extremals of {D}unkl-type {S}obolev inequality
+and of {S}tein-{W}eiss inequality for {D}unkl {R}iesz
+potential}, \emph{Complex Anal. Oper. Theory} {\bf 15} (2021), Paper No. 28, 34.
 \item Adimurthi and Ratnakumar, P.
@@
 {H}ardy space}, \emph{Arch. Math. (Basel)} {\bf 114} (2020), 431--444.
+\item Anoop, V.
+P.
+and Parui, Sanjay: \href{https://doi.org/10.7153/mia-2021-24-10}{Improved fractional {H}ardy inequalities for {D}unkl gradient}, \emph{Math.
+Inequal.
+Appl.} {\bf 24} (2021), 129--155.
+\item Arunkumar, G.: \href{https://doi.org/10.1016/j.jcta.2021.105492}{Chromatic symmetric function of graphs from {B}orcherds
+algebras}, \emph{J. Combin. Theory Ser. A} {\bf 183} (2021), Paper No. 105492, 28.
 \item Arunkumar, G. and Kus, Deniz and Venkatesh, R.: \href{https://doi.org/10.1016/j.jalgebra.2017.11.050}{Root multiplicities for {B}orcherds algebras and graph
@@
 Paris} {\bf 358} (2020), 1239--1258.
+\item Balodi, Mamta and Banerjee, Abhishek and Ray, Samarpita: \href{https://doi.org/10.1007/s11856-021-2108-2}{Entwined modules over linear categories and {G}alois
+extensions}, \emph{Israel J. Math.} {\bf 241} (2021), 623--692.
 \item Balodi, Mamta and Banerjee, Abhishek and Ray, Samarpita: \href{https://doi.org/10.4153/s0008414x19000403}{Cohomology of modules over {$H$}-categories and
@@
 \item Banerjee, Abhishek: \href{https://doi.org/10.1016/j.jalgebra.2018.04.022}{Completions of monoid objects and descent results}, \emph{J. Algebra} {\bf 507} (2018), 362--399.
+\item Banerjee, Abhishek: \href{https://doi.org/10.1016/j.jpaa.2020.106595}{{$FI$}-modules over preadditive categories and torsion
+theories}, \emph{J. Pure Appl. Algebra} {\bf 225} (2021), 106595, 29.
 \item Banerjee, Abhishek and Kour, Surjeet: \href{https://doi.org/10.1007/s10231-019-00844-x}{{$(A,\delta)$}-modules, {H}ochschild homology and higher
 derivations}, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802.
+\item Banerjee, Agnid and Garofalo, Nicola and Manna, Ramesh: \href{https://doi.org/10.1007/s12220-020-00487-y}{A strong unique continuation property for the heat operator
+with {H}ardy type potential}, \emph{J. Geom. Anal.} {\bf 31} (2021), 5480--5504.
 \item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: \href{https://doi.org/10.1142/S0129167X2050086X}{On stable {CMC} free-boundary surfaces in a strictly convex
@@
 cycle}, \emph{Stoch. Anal. Appl.} {\bf 34} (2016), 96--116.
+\item Basak, Riju and Garg, Rahul and Thangavelu, Sundaram: \href{https://doi.org/10.1016/j.jfa.2021.109154}{Homogeneous {F}ourier and {W}eyl multipliers on {S}obolev
+spaces related to the {H}eisenberg group}, \emph{J. Funct. Anal.} {\bf 281} (2021), Paper No. 109154, 45.
 \item Basu, Arnab and Ghosh, Mrinal K.: \href{https://doi.org/10.1287/moor.2017.0870}{Nonzero-sum risk-sensitive stochastic games on a countable
 state space}, \emph{Math. Oper. Res.} {\bf 43} (2018), 516--532.
+\item Basu, Riddhipratim and Ganguly, Shirshendu and Hegde, Milind
+and Krishnapur, Manjunath: \href{https://doi.org/10.1007/s11856-021-2135-z}{Lower deviations in {$\beta$}-ensembles and law of iterated
+logarithm in last passage percolation}, \emph{Israel J. Math.} {\bf 242} (2021), 291--324.
+\item Behera, Kiran Kumar: \href{https://doi.org/10.1016/j.laa.2021.03.025}{A generalized inverse eigenvalue problem and {$m$}-functions}, \emph{Linear Algebra Appl.} {\bf 622} (2021), 46--65.
 \item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
@@
 10, 48.
+\item Bera, Sudip: \href{https://doi.org/10.1515/spma-2020-0130}{Enumeration of weighted paths on a digraph and block hook
+determinant}, \emph{Spec. Matrices} {\bf 9} (2021), 197--211.
+\item Bera, Sudip and Dey, Hiranya Kishore and Mukherjee, Sajal
+Kumar: \href{https://doi.org/10.1007/s00373-020-02267-5}{On the connectivity of enhanced power graphs of finite groups}, \emph{Graphs Combin.} {\bf 37} (2021), 591--603.
 \item Bera, Sudip and Mukherjee, Sajal Kumar: \href{https://doi.org/10.1007/s00373-020-02223-3}{Generalized power sum and {N}ewton-{G}irard identities}, \emph{Graphs Combin.} {\bf 36} (2020), 1957--1964.
@@
 kernel}, \emph{Studia Math.} {\bf 255} (2020), 83--107.
+\item Bhattacharyya, Tirthankar and Das, B. Krishna and Sau,
+Haripada: \href{https://doi.org/10.1093/imrn/rnz333}{Toeplitz operators on the symmetrized bidisc}, \emph{Int. Math. Res. Not. IMRN} {\bf } (2021), 8492--8520.
 \item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K.: \href{https://doi.org/10.1007/s13226-019-0345-4}{Survey of last ten years of work done in {I}ndia in some
@@
 surface}, \emph{Geom. Dedicata} {\bf 180} (2016), 399--413.
+\item Biswas, Anindya and Maitra, Anwoy: \href{https://doi.org/10.1016/j.jmaa.2021.125434}{A characterization of the bidisc by a subgroup of its
+automorphism group}, \emph{J. Math. Anal. Appl.} {\bf 504} (2021), Paper No. 125434, 10.
 \item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and
@@
 indefinite second-order linear elliptic problems}, \emph{Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.
+\item Carstensen, Carsten and Mallik, Gouranga and Nataraj, Neela: \href{https://doi.org/10.1093/imanum/drz071}{Nonconforming finite element discretization for semilinear
+problems with trilinear nonlinearity}, \emph{IMA J. Numer. Anal.} {\bf 41} (2021), 164--205.
 \item Chakrabarti, A. and Mondal, Sumita Rani: On approximate numerical method of solution of {F}redholm
@@
 spaces}, \emph{Acta Sci. Math. (Szeged)} {\bf 86} (2020), 449--466.
+\item Chattopadhyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: \href{https://doi.org/10.1017/S0013091521000146}{Multiplicities, invariant subspaces and an additive formula}, \emph{Proc.
+Edinb.
+Math.
+Soc.
+(2)} {\bf 64} (2021), 279--297.
+\item Chmieli\'{n}ski, Jacek and Khurana, Divya and Sain, Debmalya: \href{https://doi.org/10.1007/s00025-021-01437-y}{Local approximate symmetry of {B}irkhoff-{J}ames orthogonality
+in normed linear spaces}, \emph{Results Math.} {\bf 76} (2021), Paper No. 136, 26.
 \item Choudhary, A. and Martha, S. C. and Chakrabarti, A.: \href{https://doi.org/10.1007/s40010-019-00600-z}{Modified method for the solution of dual trigonometric series
 relations}, \emph{Proc. Nat. Acad. Sci. India Sect. A} {\bf 90} (2020), 437--445.
+\item Choudhury, Projesh Nath and Eagambaram, N. and Sivakumar, K.
+C. and Sushmitha, P.: \href{https://doi.org/10.1016/j.laa.2020.10.041}{On the matrix class {$Q_0$} and inverse monotonicity
+properties of bordered matrices}, \emph{Linear Algebra Appl.} {\bf 612} (2021), 206--222.
+\item Choudhury, Projesh Nath and Kannan, M.
+Rajesh: \href{https://doi.org/10.1016/j.laa.2021.01.005}{Interval hulls of {$N$}-matrices and almost {$P$}-matrices}, \emph{Linear Algebra Appl.} {\bf 617} (2021), 27--38.
 \item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
@@
 semipositive matrices}, \emph{Electron. J. Linear Algebra} {\bf 34} (2018), 687--694.
+\item Choudhury, Projesh Nath and Sivakumar, K.
+C.: \href{https://doi.org/10.1080/03081087.2019.1602588}{Matrices with positive semidefinite real part}, \emph{Linear Multilinear Algebra} {\bf 69} (2021), 448--470.
 \item Choudhury, Projesh Nath and Tsatsomeros, Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic detection and construction of {N}-matrices}, \emph{Linear Algebra Appl.} {\bf 602} (2020), 46--56.
@@
 Symplectic Geom.} {\bf 18} (2020), 961--994.
+\item Datar, Ved and Jacob, Adam and Zhang, Yuguang: \href{https://doi.org/10.4310/jdg/1622743140}{Adiabatic limits of anti-self-dual connections on collapsed
+{$K3$} surfaces}, \emph{J. Differential Geom.} {\bf 118} (2021), 223--296.
+\item Datar, Ved and Seshadri, Harish and Song, Jian: \href{https://doi.org/10.1090/proc/15473}{Metric rigidity of {K}\"{a}hler manifolds with lower {R}icci
+bounds and almost maximal volume}, \emph{Proc. Amer. Math. Soc.} {\bf 149} (2021), 3569--3574.
+\item Datta, Basudeb and Gupta, Subhojoy: \href{https://doi.org/10.1007/s00454-019-00156-0}{Semi-regular tilings of the hyperbolic plane}, \emph{Discrete Comput. Geom.} {\bf 65} (2021), 531--553.
 \item Datta, Basudeb and Maity, Dipendu: \href{https://doi.org/10.1007/s13366-019-00458-7}{Correction to: {S}emi-equivelar and vertex-transitive maps on
@@
 Math.} {\bf 44} (2020), 57-56.
+\item Deb, Prahllad: \href{https://doi.org/10.1016/j.bulsci.2021.102977}{On unitary invariants of quotient {H}ilbert modules along
+smooth complex analytic sets}, \emph{Bull. Sci. Math.} {\bf 169} (2021), Paper No. 102977, 42.
 \item Dhanya, R. and Prashanth, S. and Tiwari, Sweta and Sreenadh,
@@
 polyhedron}, \emph{Adv. Math.} {\bf 319} (2017), 111--152.
+\item Dias, Kealey and Gupta, Subhojoy and Trnkova, Maria: \href{https://doi.org/10.1215/00192082-8827639}{Quadratic differentials, measured foliations, and metric
+graphs on punctured surfaces}, \emph{Illinois J. Math.} {\bf 65} (2021), 417--454.
 \item Dond, Asha K. and Gudi, Thirupathi: \href{https://doi.org/10.1002/num.22317}{Patch-wise local projection stabilized finite element methods
@@
 Sci.} {\bf 126} (2016), 261--275.
+\item Ganguly, Pritam and Thangavelu, Sundaram: \href{https://doi.org/10.1016/j.jfa.2020.108832}{On the lacunary spherical maximal function on the {H}eisenberg
+group}, \emph{J. Funct. Anal.} {\bf 280} (2021), 108832, 32.
+\item Ganguly, Pritam and Thangavelu, Sundaram: \href{https://doi.org/10.1016/j.aim.2021.107815}{Theorems of {C}hernoff and {I}ngham for certain eigenfunction
+expansions}, \emph{Adv. Math.} {\bf 386} (2021), Paper No. 107815, 31.
 \item Garani, Shayan Srinivasa and Seshadri, Harish: \href{https://doi.org/10.1080/17459737.2019.1604845}{An algorithmic approach to {S}outh {I}ndian classical music}, \emph{J.
@@
 diffusions}, \emph{Stoch. Anal. Appl.} {\bf 36} (2018), 1--27.
+\item Ghosh, Mrinal K. and Suresh Kumar, K. and Pal, Chandan and
+Pradhan, Somnath: \href{https://doi.org/10.1080/07362994.2020.1796707}{Nonzero-sum risk-sensitive stochastic differential games with
+discounted costs}, \emph{Stoch. Anal. Appl.} {\bf 39} (2021), 306--326.
 \item Ghosh, Mrinal Kanti and Pradhan, Somnath: \href{https://doi.org/10.1051/cocv/2020029}{Zero-sum risk-sensitive stochastic differential games with
@@
 \item Gupta, S. C.: The classical {S}tefan problem, \emph{} {\bf } (2018), xxiii+726.
+\item Gupta, Subhojoy: \href{https://doi.org/10.1142/S1793525320500156}{Harmonic maps and wild {T}eichm\"{u}ller spaces}, \emph{J. Topol. Anal.} {\bf 13} (2021), 349--393.
 \item Gupta, Subhojoy: \href{https://doi.org/10.1090/tran/7777}{Limits of harmonic maps and crowned hyperbolic surfaces}, \emph{Trans. Amer. Math. Soc.} {\bf 372} (2019), 7573--7596.
+\item Gupta, Subhojoy and Mj, Mahan: \href{https://doi.org/10.1016/j.aim.2021.107673}{Meromorphic projective structures, grafting and the monodromy
+map}, \emph{Adv. Math.} {\bf 383} (2021), Paper No. 107673, 49.
 \item Gupta, Subhojoy and Mj, Mahan: \href{https://doi.org/10.1090/proc/14866}{Monodromy representations of meromorphic projective
@@
 \item Hatui, Sumana: \href{https://doi.org/10.1515/jgth-2019-0045}{Schur multipliers of special {$p$}-groups of rank 2}, \emph{J. Group Theory} {\bf 23} (2020), 85--95.
+\item Hatui, Sumana and Singla, Pooja: \href{https://doi.org/10.1016/j.jpaa.2021.106742}{On {S}chur multiplier and projective representations of
+{H}eisenberg groups}, \emph{J. Pure Appl. Algebra} {\bf 225} (2021), Paper No. 106742, 16.
 \item Hazra, Somnath: \href{https://doi.org/10.1007/s11785-018-0822-5}{Homogeneous 2-shifts}, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.
@@
 reflection groups}, \emph{Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999.
+\item Khare, Apoorva and Pingali, Vamsi Pritham: \href{https://doi.org/10.1016/j.bulsci.2021.102956}{On an asymptotic characterisation of {G}riffiths
+semipositivity}, \emph{Bull. Sci. Math.} {\bf 167} (2021), Paper No. 102956, 7.
 \item Khare, Apoorva and Rajaratnam, Bala: \href{https://doi.org/10.1007/s43036-020-00048-8}{Probability inequalities and tail estimates for metric
 semigroups}, \emph{Adv. Oper. Theory} {\bf 5} (2020), 779--795.
+\item Khare, Apoorva and Rajaratnam, Bala: \href{https://doi.org/10.1007/s43036-020-00111-4}{Differential calculus on the space of countable labelled
+graphs}, \emph{Adv. Oper. Theory} {\bf 6} (2021), Paper No. 12, 28.
 \item Khare, Apoorva and Rajaratnam, Bala: \href{https://doi.org/10.1214/16-AOP1160}{The {H}offmann-{J}\o rgensen inequality in metric semigroups}, \emph{Ann. Probab.} {\bf 45} (2017), 4101--4111.
@@
 {B}anach spaces}, \emph{Acta Sci. Math. (Szeged)} {\bf 86} (2020), 617--634.
+\item Khurana, Divya and Sain, Debmalya: \href{https://doi.org/10.1007/s43034-021-00134-9}{Norm derivatives and geometry of bilinear operators}, \emph{Ann.
+Funct.
+Anal.} {\bf 12} (2021), Paper No.
+49, 19.
 \item Kor\'{a}nyi, Adam and Misra, Gadadhar: \href{https://doi.org/10.1016/j.aim.2019.05.018}{Homogeneous {H}ermitian holomorphic vector bundles and the
@@
 structure}, \emph{Beitr. Algebra Geom.} {\bf 58} (2017), 427--452.
+\item Kreuzer, Martin and Patil, Dilip P.: \href{https://doi.org/10.1007/s13366-020-00520-9}{Computational aspects of {B}urnside rings part {II}: important
+maps}, \emph{Beitr. Algebra Geom.} {\bf 62} (2021), 475--494.
 \item Krishna, M. and Krishnapur, Manjunath: \href{https://doi.org/10.1007/s13226-016-0183-6}{Persistence probabilities in centered, stationary, {G}aussian
@@
 equivalent characterizations}, \emph{Topology Appl.} {\bf 216} (2017), 59--73.
+\item Lai, King-Fai and Longhi, Ignazio and Suzuki, Takashi and Tan,
+Ki-Seng and Trihan, Fabien: \href{https://doi.org/10.2140/ant.2021.15.863}{On the {$\mu$}-invariants of abelian varieties over function
+fields of positive characteristic}, \emph{Algebra Number Theory} {\bf 15} (2021), 863--907.
 \item Lin, X.
@@
 equation}, \emph{Chaos} {\bf 28} (2018), 083103, 12.
+\item Manna, Ramesh and Shrivastava, Saurabh and Shuin, Kalachand: \href{https://doi.org/10.1016/j.na.2020.112225}{Weighted estimates for maximal functions associated with
+finite type curves in {$\Bbb R^2$}}, \emph{Nonlinear Anal.} {\bf 205} (2021), 112225, 24.
 \item Misra, Gadadhar: Operators in the {C}owen-{D}ouglas class and related topics, \emph{Handbook of analytic operator theory} {\bf } (2019), 87--137.
@@
 contrasting diffusivity coefficients}, \emph{Differential Integral Equations} {\bf 29} (2016), 37--54.
+\item Nandakumaran, A. K. and Sufian, Abu: \href{https://doi.org/10.1051/cocv/2020045}{Oscillating {PDE} in a rough domain with a curved interface:
+homogenization of an optimal control problem}, \emph{ESAIM Control Optim. Calc. Var.} {\bf 27} (2021), Paper No. S4, 37.
+\item Nandakumaran, A. K. and Sufian, Abu: \href{https://doi.org/10.1016/j.jde.2021.04.031}{Strong contrasting diffusivity in general oscillating domains:
+homogenization of optimal control problems}, \emph{J. Differential Equations} {\bf 291} (2021), 57--89.
 \item Nandakumaran, Akambadath and Prakash, Ravi and Sardar, Bidhan
@@
 \item Pingali, Vamsi Pritham: \href{https://doi.org/10.1007/s00209-017-1903-2}{Representability of {C}hern-{W}eil forms}, \emph{Math. Z.} {\bf 288} (2018), 629--641.
+\item Pingali, Vamsi Pritham and Varolin, Dror: \href{https://doi.org/10.1017/nmj.2019.2}{Nonuniformly flat affine algebraic hypersurfaces}, \emph{Nagoya Math. J.} {\bf 241} (2021), 1--43.
+\item Poria, Anirudha: \href{https://doi.org/10.1080/10652469.2020.1813129}{Uncertainty principles for the {O}pdam-{C}herednik transform
+on modulation spaces}, \emph{Integral Transforms Spec. Funct.} {\bf 32} (2021), 191--206.
 \item Poria, Anirudha: \href{https://doi.org/10.1080/01630563.2020.1728771}{Positive weight function and classification of {$g$}-frames}, \emph{Numer. Funct. Anal. Optim.} {\bf 41} (2020), 950--968.
@@
 hyperbolic quadric in {${\rm PG} (3,q)$}, {$q$} odd}, \emph{Discrete Math.} {\bf 343} (2020), 112044, 8.
+\item Pradhan, Somnath: \href{https://doi.org/10.1007/s00245-019-09606-w}{Risk-sensitive ergodic control of reflected diffusion
+processes in orthant}, \emph{Appl. Math. Optim.} {\bf 83} (2021), 1739--1764.
 \item Prasad, Phoolan: \href{https://doi.org/10.1007/s12044-016-0275-6}{Ray equations of a weak shock in a hyperbolic system of
@@
 Groups} {\bf 24} (2019), 1261--1308.
+\item Roy, Saikat and Senapati, Tanusri and Sain, Debmalya: \href{https://doi.org/10.1016/j.laa.2020.12.032}{Orthogonality of bilinear forms and application to matrices}, \emph{Linear Algebra Appl.} {\bf 615} (2021), 104--111.
 \item Sain, Debmalya: \href{https://doi.org/10.1215/20088752-2018-0014}{On extreme contractions and the norm attainment set of a
@@
 {B}ishop-{P}helps-{B}ollob\'{a}s type theorems in {B}anach spaces}, \emph{Oper. Matrices} {\bf 13} (2019), 433--445.
+\item Sain, Debmalya: \href{https://doi.org/10.1007/s13398-021-01060-0}{Orthogonality and smoothness induced by the norm derivatives}, \emph{Rev.
+R.
+Acad.
+Cienc.
+Exactas F\'{\i}s.
+Nat.
+Ser.
+A Mat.
+RACSAM} {\bf 115} (2021), Paper No.
+120, 10.
+\item Sain, Debmalya and Bhunia, Pintu and Bhanja, Aniket and Paul,
+Kallol: \href{https://doi.org/10.1007/s43034-021-00138-5}{On a new norm on {$\Cal B(\Cal H)$} and its applications to
+numerical radius inequalities}, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 51, 25.
+\item Sain, Debmalya and Mal, Arpita and Bhunia, Pintu and Paul,
+Kallol: On numerical radius and {C}rawford number attainment sets of a
+bounded linear operator, \emph{J. Convex Anal.} {\bf 28} (2021), 67--80.
+\item Sain, Debmalya and Mal, Arpita and Mandal, Kalidas and Paul,
+Kallol: \href{https://doi.org/10.1016/j.jmaa.2020.124582}{On uniform {B}ishop-{P}helps-{B}ollob\'{a}s type approximations of
+linear operators and preservation of geometric properties}, \emph{J. Math. Anal. Appl.} {\bf 494} (2021), 124582, 22.
 \item Sain, Debmalya and Mal, Arpita and Paul, Kallol: \href{https://doi.org/10.1016/j.exmath.2019.01.001}{Some remarks on {B}irkhoff-{J}ames orthogonality of linear
@@
 Santanu: \href{https://doi.org/10.1016/j.laa.2019.04.024}{On the numerical index of polyhedral {B}anach spaces}, \emph{Linear Algebra Appl.} {\bf 577} (2019), 121--133.
+\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: \href{https://doi.org/10.1016/j.exmath.2019.09.004}{On extreme contractions between real {B}anach spaces}, \emph{Expo.
+Math.} {\bf 39} (2021), 33--47.
 \item Sain, Debmalya and Paul, Kallol and Mal, Arpita: A complete characterization of {B}irkhoff-{J}ames
@@
 domains}, \emph{Comput. Methods Funct. Theory} {\bf 20} (2020), 145--158.
+\item Sebastian, Geethika and Daniel, Sukumar: \href{https://doi.org/10.4064/cm8015-9-2019}{A weaker {G}leason-{K}ahane-\.{Z}elazko theorem for modules and
+applications to {H}ardy spaces}, \emph{Colloq. Math.} {\bf 164} (2021), 273--282.
+\item Sen, Jeet and Sain, Debmalya and Paul, Kallol: \href{https://doi.org/10.1007/s43034-020-00104-7}{Orthogonality and norm attainment of operators in
+semi-{H}ilbertian spaces}, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 17, 12.
+\item Sen, Jeet and Sain, Debmalya and Paul, Kallol: \href{https://doi.org/10.1016/j.bulsci.2021.102997}{On approximate orthogonality and symmetry of operators in
+semi-{H}ilbertian structure}, \emph{Bull. Sci. Math.} {\bf 170} (2021), Paper No. 102997, 22.
 \item Sen, Suparna: \href{https://doi.org/10.1515/apam-2015-0010}{Segal-{B}argmann transform and {P}aley-{W}iener theorems on
@@
 Ramakrishna: \href{https://doi.org/10.1016/j.physa.2017.04.029}{Emergent organization in a model market}, \emph{Phys. A} {\bf 482} (2017), 118--126.
+\item \'{A}lvarez-C\'{o}nsul, Luis and Garcia-Fernandez, Mario and
+Garc\'{\i}a-Prada, Oscar and Pingali, Vamsi Pritham: \href{https://doi.org/10.1007/s00208-020-01964-z}{Gravitating vortices and the {E}instein-{B}ogomol'nyi
+equations}, \emph{Math. Ann.} {\bf 379} (2021), 1651--1684.
 \end{enumerate}

### 2021-08-20 ugc/src/Publications.scala

@@ -17,7 +17,7 @@ object Publications {
       case (k, v) => k.getValue.toLowerCase -> v.toUserString
     })
     .toVector
-    .filter(m => Set("2016", "2017", "2018", "2019", "2020").contains(m("year")))
+    .filter(m => Set("2016", "2017", "2018", "2019", "2020", "2021").contains(m("year")))
 
   import net.jcazevedo.moultingyaml._
   import net.jcazevedo.moultingyaml.DefaultYamlProtocol._
